### 2014-09-06 docs/questioning.tex
initial commit

\documentclass[conference]{IEEEtran}

\usepackage{hyperref}
%\usepackage{graphicx}
\usepackage{fancyhdr}
%\usepackage{lastpage}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{color}
\usepackage{url}
%\usepackage{moreverb}
\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{mathptmx}
\usepackage{dingbat}
\usepackage{pifont}
\usepackage{acronym}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{supertabular}
\usepackage{listings}
\usepackage{threeparttable}
\usepackage{pdflscape}
\usepackage{array}
\usepackage{multirow}
\usepackage{subfigure}

\usepackage[numbers,sort]{natbib}

\renewcommand{\algorithmiccomment}[1]{\hfill {\tt //} #1}
\newcommand{\tick}{\ding{52}}
\newcommand{\xmark}{\ding{56}}

\date{}
\begin{document}

\author{
\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
Panos Louridas,\IEEEauthorrefmark{2} and Angelos Keromytis\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
Network Security Lab\\
Department of Computer Scinence\\
Columbia University\\
\{dimitro, angelos\}@cs.columbia.edu\\
\IEEEauthorrefmark{2}
Software Engineering and Security Lab\\
Department of Management Science and Technology\\
Athens University of Economics and Business\\
louridas@aueb.gr
}}

\title{Questioning how Researchers Develop and Present IDS}

\maketitle
\begin{abstract}
In this paper we examine how intrusion-detection
systems developed to counter a specific category
of application attacks are developed and presented to
the research community.
\end{abstract}

\begin{IEEEkeywords}
Security and Protection, Intrusion-Detection Systems, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

Introduction~\cite{I05}. Also see~\cite{A00}.

Requirements:
\begin{itemize}
	\item {\bf Flexibility} We check if an approach
can be adjusted in order to detect different {\sc cia} categories.
	\item {\bf Ease of use} We examine if the mechanism that
implements an approach is practical and can be easily adopted
by security experts.
	\item {\bf Effectiveness} As long as we examine security
mechanisms that detect either attacks or defects,
the non-existence of false positive and negative alarms
is a reasonable requirement.
	\item {\bf Efficiency} Finally, we examine
the computational overhead of the mechanisms that affect the experience of
a web user who actually uses the protected application.
	\item {\bf Security} How resilient is the system to
attacks made to to circumvent it.
\end{itemize}
All the aforementioned requirements are considered critical
when building security mechanisms that protect
applications~\cite{A01,A00}.

\section{Covered Area}

We decided to narrow down our
research to countermeasures developed to
detect attacks that target applications. Such attacks include
buffer overflow attacks~\cite{K11}, {\sc sql} injection
attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
attacks~\cite{LZRL09} and others.
Such attacks top the vulnerability lists of numerous bulletin providers for several
years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
(Open Web Application Security Project)
Top Ten project whose main goal is to raise awareness about
web application security by identifying some of the most critical risks facing
organizations which is referenced by numerous researchers.
In its three consecutive Top Ten lists (2007, 2010, 2013), different
source code-driven injection attacks dominate the top five positions.
This indicates that
apart from the fact that malicious users find new ways to bypass
defense mechanisms by using a variety of techniques despite the numerous
countermeasures that are being introduced.
Note that the number of systems developed to counter {\sc sql}
injection attacks until 2006 was more than twenty~\cite{HVO06}.
Since then the number has doubled.
In our research we focus on the top {\sc tba} systems that counter
application attacks, in terms of citations.

\section{Analysis}

\begin{table*}
%\tbl{Performance of System Prototype. Time is Measured in $\mu$s.}{
\centering
    \begin{threeparttable}
    \begin{small}
\scalebox{0.93}{
    \begin{tabular}{l|c|cc|c}
    \hline
    \bf{Approach}
	& \bf{Mechanism}
    & \multicolumn{2}{|c|}{Requirements}
	& \bf{Attack Vector} \\
	&& \bf{FP/FN}
	& \bf{Computational Overhead}\tnote{4} & \\
    \hline
	\multirow{11}{*}{Runtime Tainting}
	&  	{\it SigFree}~\cite{WPLZ10} & \xmark,\xmark & 10\% & {\it binary code} \\
	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & {\sc sql} \\
	&  	{\it {\sc lift}}~\cite{QWLKZW06} & \tick,\tick & 6.2\% & {\it binary code} \\ 
	&  	{\it Haldar et al.}~\cite{HCF05} & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
	&  	{\it SecuriFly}~\cite{MLL05} & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
	&  	{\it Xu et al.}~\cite{XBS06} & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
	&  	{\it Vogt et al.}~\cite{VFJKKV07} & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
	%& {\it Lekies et al.}~\cite{LSJ13} & & & \\
	\hline
	\hline      
	\multirow{3}{*}{{\sc isr}}
	&  {\it {\sc sql}rand}~\cite{BK04} & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
	&  {\it Noncespaces}~\cite{GC09} & \tick,\tick &  10.3\% & {\sc xss} \\ 
    &  {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\
	\hline
	\hline    
	\multirow{11}{*}{Policy Enforcement}
	&  {\it {\sc dsi}}~\cite{NSS06} & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
	&  {\it BrowserShield}~\cite{RDWDE07} & \tick,\tick & 8\% & {\sc xss} \\ 
	&  {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & {\sc xss} \\ 
	&  {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
	&  {\it ConScript}~\cite{ML10} & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
	&  {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
    &  {\it {\sc beep}}~\cite{TNH07}  & \tick,\tick & 14.4\% & {\sc xss} \\
	&  {\it {\sc csp}} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
    &  {\it Google Caja} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
	&  {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
	& {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
	\hline
	\hline  
        \multirow{12}{*}{Training}
	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & {\sc sql} \\ 
	&   {\it {\sc didafit}}~\cite{LLW02} & \xmark,\xmark & {\bf ?} & {\sc sql} \\
	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
	& 	{\it Mattos et al.}~\cite{MSM13} & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
	& 	{\it {\sc sm}ask}~\cite{JB07} & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
	& 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
    & 	{\it {\sc xssds}}~\cite{JEP08}  & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5---24\% & {\sc xss} \\
	\hline
    \end{tabular}}
    \begin{tablenotes}
	\begin{footnotesize}
       \item[1] {\it Flexibility} indicates if the approach can be adjusted
	in order to detect different {\sc cia} categories.
       \item[4] {\it User Experience} is affected if the mechanism suffers
	from runtime overhead.
	\end{footnotesize}
    \end{tablenotes}
    \caption{Dynamic Detection: Comparison summary of mechanisms developed to counter {\sc cia}s.}
    \label{tab:comp2}
    \end{small}
    \end{threeparttable}
\end{table*}

\bibliographystyle{IEEEtran}
\bibliography{questioning}

\end{document}

### 2014-09-12 docs/questioning.tex
added one entry
added another entry
more entries
minor changes

@@
 
-\title{Questioning how Researchers Develop and Present IDS}
+\title{Questioning how Researchers Develop and Present Intrusion Detection Systems}
 
@@
     \hline
-	\multirow{11}{*}{Runtime Tainting}
+	\multirow{13}{*}{Runtime Tainting}
+	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
+	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
 	&  	{\it SigFree}~\cite{WPLZ10} & \xmark,\xmark & 10\% & {\it binary code} \\
@@
 	\hline    
-	\multirow{11}{*}{Policy Enforcement}
+	\multirow{14}{*}{Policy Enforcement}
 	&  {\it {\sc dsi}}~\cite{NSS06} & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
@@
 	&  {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & {\sc xss} \\ 
+	&  {\it WebJail}~\cite{VDDPJ11} & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
 	&  {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
 	&  {\it ConScript}~\cite{ML10} & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
+	&  {\it {\sc js}and}~\cite{AVBPDP12} & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
 	&  {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
@@
     &  {\it Google Caja} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
-	&  {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
-	& {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
+    &  {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
+    &  {\it TreeHouse}~\cite{IW12} & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
+    &  {\it Dhawan et al.}~\cite{DSG12} & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\
 	\hline
@@
     \end{tablenotes}
-    \caption{Dynamic Detection: Comparison summary of mechanisms developed to counter {\sc cia}s.}
+    \caption{Comparison summary of mechanisms developed to counter application attacks.}
     \label{tab:comp2}

### 2014-09-16 docs/questioning.tex
adding some definitions

@@
 applications~\cite{A01,A00}.
+
+\section{Intrusion Detection Accuracy}
+
+An intrusion detection system examines some software artifact and
+reports vulnerabilities. The value an intrusion detection system can
+be measured in terms of its \emph{accuracy}, which gauges the quality
+of its output. An intrusion detection system makes predictions for
+vulnerabilities. The following may happen:
+\begin{itemize}
+\item A prediction about a vulnerability is true. That is a \emph{true
+    positive}. 
+\item A prediction about a vulnerability is false; intrusion
+  detection reported something that in reality is not vulnerability.
+  That is a \emph{false positive}.
+\item A prediction about the absence of a vulnerability is true. That
+  is a \emph{true negative}: intrusion detection evaluated something
+  as being safe, and it is.
+\item A prediction about the absence of a vulnerability is false. That
+  is a \emph{false negative}: intrusion detection missed a
+  vulnerability.
+\end{itemize}
+In terms of the above, the \emph{Positive Predictive Value} (PPV) is
+defined as the ratio of true positives over all reported positives,
+while the \emph{Negative Predictive Value} (NPV) is defined as the
+ratio of true negatives over all reported negatives. In intrusion
+detection, the PPV is an indicator of how much we should be worried
+about a reported vulnerability being true. Conversely, the NPV is an
+indicator of how much we should be reassured when no vulnerabilities
+are reported.
+
+What we need to proceed:
+\begin{itemize}
+\item Do the studies report the sample size? Note that we must be
+  careful with what we mean by sample size. A single item in the
+  sample is something that can be vulnerable or not. 
+\item Do the studies report true positives, false positives, true
+  negatives, false negatives?
+\end{itemize}
 

### 2014-09-18 docs/questioning.tex
Change of definitions + requirements

@@
 
+The evaluation of
+
+\section{Analysis Dimensions}
+
+\begin{itemize}
+\item {\bf Sensitivity}, the probability that an attack will be
+  caught.
+\item {\bf Specificity}, the probability that a normal interaction
+  will test negative.
+\item {\bf Positive Predictive Value} (PPV), the probability that a
+  reported attack is a real attack.
+\item {\bf Negative Predictive Value} (NPV), the probability that if
+  nothing is reported no attack has taken place.
+\end{itemize}
+
+To do any meaningful calculation of the above, we need to define
+precisely the following in our methodology:
+\begin{itemize}
+\item True Positive (TP)
+\item False Positive (FP)
+\item True Negative (TN)
+\item False Negative (FN)
+\end{itemize}
+
 \section{Intrusion Detection Accuracy}
@@
 be measured in terms of its \emph{accuracy}, which gauges the quality
-of its output. An intrusion detection system makes predictions for
-vulnerabilities. The following may happen:
+of its output. An intrusion detection system:
 \begin{itemize}

### 2014-09-18 docs/questioning.tex
added number of citations

@@
 \scalebox{0.93}{
-    \begin{tabular}{l|c|cc|c}
+    \begin{tabular}{l|c|c|cc|c}
     \hline
@@
 	& \bf{Mechanism}
+	& \bf{\# of Citations}
     & \multicolumn{2}{|c|}{Requirements}
 	& \bf{Attack Vector} \\
-	&& \bf{FP/FN}
+	&&& \bf{TP,TN,FP,FN}
 	& \bf{Computational Overhead}\tnote{4} & \\
     \hline
-	\multirow{13}{*}{Runtime Tainting}
-	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
-	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
-	&  	{\it SigFree}~\cite{WPLZ10} & \xmark,\xmark & 10\% & {\it binary code} \\
-	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & {\sc sql} \\
-	&  	{\it {\sc lift}}~\cite{QWLKZW06} & \tick,\tick & 6.2\% & {\it binary code} \\ 
-	&  	{\it Haldar et al.}~\cite{HCF05} & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
-	&  	{\it SecuriFly}~\cite{MLL05} & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
-    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07} & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
+	\multirow{11}{*}{Runtime Tainting}
+%	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
+%	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
+	&  	{\it SigFree}~\cite{WPLZ10} & 111 & \xmark,\xmark & 10\% & {\it binary code} \\
+	&  	{\sc csse}~\cite{PB05} & 0 & \xmark,\xmark & 2--10\% & {\sc sql} \\
+	&  	{\it {\sc lift}}~\cite{QWLKZW06} & 268 & \tick,\tick & 6.2\% & {\it binary code} \\ 
+	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
+	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
+    &  	{\it {\sc wasc}}~\cite{NLC07} & 0 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 0 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
+	&   {\it Noxes}~\cite{KJKV09} & 40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
 	%& {\it Lekies et al.}~\cite{LSJ13} & & & \\
@@
 	\multirow{3}{*}{{\sc isr}}
-	&  {\it {\sc sql}rand}~\cite{BK04} & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
-	&  {\it Noncespaces}~\cite{GC09} & \tick,\tick &  10.3\% & {\sc xss} \\ 
-    &  {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\
+	&  {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
+	&  {\it Noncespaces}~\cite{GC09} & 109 & \tick,\tick &  10.3\% & {\sc xss} \\ 
+    &  {\it x{\sc js}}~\cite{APKLM10} & 18 & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\
 	\hline
 	\hline    
-	\multirow{14}{*}{Policy Enforcement}
-	&  {\it {\sc dsi}}~\cite{NSS06} & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
-	&  {\it BrowserShield}~\cite{RDWDE07} & \tick,\tick & 8\% & {\sc xss} \\ 
-	&  {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & {\sc xss} \\ 
-	&  {\it WebJail}~\cite{VDDPJ11} & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
-	&  {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
-	&  {\it ConScript}~\cite{ML10} & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
-	&  {\it {\sc js}and}~\cite{AVBPDP12} & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
-	&  {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
-    &  {\it {\sc beep}}~\cite{TNH07}  & \tick,\tick & 14.4\% & {\sc xss} \\
-	&  {\it {\sc csp}} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
-    &  {\it Google Caja} & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
-    &  {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
-    &  {\it TreeHouse}~\cite{IW12} & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
-    &  {\it Dhawan et al.}~\cite{DSG12} & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\
+	\multirow{11}{*}{Policy Enforcement}
+	&  {\it {\sc dsi}}~\cite{NSS06} & 135 & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
+	&  {\it BrowserShield}~\cite{RDWDE07} & 219 & \tick,\tick & 8\% & {\sc xss} \\ 
+	&  {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
+	&  {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
+	&  {\it CoreScript}~\cite{YCIS07} & 181 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
+	&  {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
+	&  {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
+	&  {\it {\sc met}}~\cite{ELX07} & 58 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
+    &  {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
+	&  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
+    % &  {\it Google Caja} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
+    % &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
+    &  {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
+    % &  {\it Dhawan et al.}~\cite{DSG12} & 7 & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\
 	\hline
@@
         \multirow{12}{*}{Training}
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & {\sc sql} \\ 
-	&   {\it {\sc didafit}}~\cite{LLW02} & \xmark,\xmark & {\bf ?} & {\sc sql} \\
-	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
-	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
-	& 	{\it Mattos et al.}~\cite{MSM13} & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
-	& 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
-    & 	{\it {\sc xssds}}~\cite{JEP08}  & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
-    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5---24\% & {\sc xss} \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 376 & \tick,\tick & {\bf ?} & {\sc sql} \\ 
+	&   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} \\
+	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
+	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
+	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 40 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
+	& 	{\it Mattos et al.}~\cite{MSM13} & 2 & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
+	& 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
+    & 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5---24\% & {\sc xss} \\
 	\hline

### 2014-09-19 docs/questioning.tex
added a csrf entry
completed citations

@@
 	&  	{\it SigFree}~\cite{WPLZ10} & 111 & \xmark,\xmark & 10\% & {\it binary code} \\
-	&  	{\sc csse}~\cite{PB05} & 0 & \xmark,\xmark & 2--10\% & {\sc sql} \\
 	&  	{\it {\sc lift}}~\cite{QWLKZW06} & 268 & \tick,\tick & 6.2\% & {\it binary code} \\ 
+	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} \\
 	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
@@
 	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
-    &  	{\it {\sc wasc}}~\cite{NLC07} & 0 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 0 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
+    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
 	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
 	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
-	&   {\it Noxes}~\cite{KJKV09} & 40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
+	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
 	%& {\it Lekies et al.}~\cite{LSJ13} & & & \\
@@
 	\hline    
-	\multirow{11}{*}{Policy Enforcement}
+	\multirow{13}{*}{Policy Enforcement}
 	&  {\it {\sc dsi}}~\cite{NSS06} & 135 & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
@@
     &  {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
-	&  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
+	% &  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
     % &  {\it Google Caja} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
-    % &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
+     &  {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
     &  {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
     % &  {\it Dhawan et al.}~\cite{DSG12} & 7 & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\
+    & {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
+    & {\it j{\sc csrf}}~\cite{PS11} & 2 & 2,7,0,0 & 2ms & {\sc csrf} \\
 	\hline
@@
 	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 40 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20,5 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
+	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
 	& 	{\it Mattos et al.}~\cite{MSM13} & 2 & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\

### 2014-09-19 docs/questioning.tex
citations for AMNESIA, buffer overflow detectors out
minor corrections
minor changes
availability table

@@
 
-\section{Analysis}
-
-\begin{table*}
+\begin{landscape}
+\begin{table}
 %\tbl{Performance of System Prototype. Time is Measured in $\mu$s.}{
@@
     \begin{small}
-\scalebox{0.93}{
+\scalebox{0.99}{
     \begin{tabular}{l|c|c|cc|c}
@@
     & \multicolumn{2}{|c|}{Requirements}
-	& \bf{Attack Vector} \\
+	& \bf{Attack} \\
 	&&& \bf{TP,TN,FP,FN}
@@
     \hline
-	\multirow{11}{*}{Runtime Tainting}
-%	&   {\it Kiriansky et al.~\cite{KBA02}} & {\bf ?},{\bf ?} & $\sim$1\% & {\it binary code} \\
-%	&   {\it {\sc cfi}~\cite{ABEL05}} & {\bf ?},{\bf ?} & 0.09--26.78\% & {\it binary code} \\
-	&  	{\it SigFree}~\cite{WPLZ10} & 111 & \xmark,\xmark & 10\% & {\it binary code} \\
-	&  	{\it {\sc lift}}~\cite{QWLKZW06} & 268 & \tick,\tick & 6.2\% & {\it binary code} \\ 
-	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} \\
-	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} \\ 
-	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql}, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql}, {\sc xss} \\ 
-    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql}, {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql}, {\sc xss}, {\sc php} \\
+	\multirow{9}{*}{Runtime Tainting}
+	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\
+	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} injection \\ 
+	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql} injection, {\sc xss} \\ 
+    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql} injection, {\sc xss} \\
 	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7-17\% & {\sc xss} \\
 	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
-	%& {\it Lekies et al.}~\cite{LSJ13} & & & \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7--17\% & {\sc xss} \\
 	\hline
@@
 	\multirow{3}{*}{{\sc isr}}
-	&  {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} \\ 
+	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} injection \\ 
 	&   {\it Noncespaces}~\cite{GC09} & 109 & \tick,\tick &  10.3\% & {\sc xss} \\ 
@@
 	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & \tick,\tick & 8\% & {\sc xss} \\ 
-	&  {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
-	&  {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
 	&   {\it CoreScript}~\cite{YCIS07} & 181 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
-	&  {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
-	&  {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
 	&   {\it {\sc met}}~\cite{ELX07} & 58 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
     &   {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
-	% &  {\it {\sc csp}} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\ 
-    % &  {\it Google Caja} & 0 & {\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
+    &   {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
+	&   {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
 	&   {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
-    &  {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–--1218ms & {\sc xss} \\
-    % &  {\it Dhawan et al.}~\cite{DSG12} & 7 & \xmark,{\bf ?} & 16---114\% & {\sc xss} \\
-    & {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
+	&   {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
+	&   {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
 	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & 2,7,0,0 & 2ms & {\sc csrf} \\
+    &   {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–-1218ms & {\sc xss} \\
+   	&   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
 	\hline
@@
         \multirow{12}{*}{Training}
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 376 & \tick,\tick & {\bf ?} & {\sc sql} \\ 
-	&   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} \\
-	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} \\
-	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql}, No{\sc sql} \\
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09} & 20,5 & \tick,\tick & 39\% & {\sc sql}, {\sc xp}ath \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql}, {\sc xp}ath \\
-	& 	{\it Mattos et al.}~\cite{MSM13} & 2 & \tick,{\bf ?} &  {\bf ?} & {\sc xml}, {\sc xp}ath \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql}, {\sc xss} \\
+    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} injection \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & \tick,\tick & {\bf ?} & {\sc sql} injection \\ 
+	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} injection \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} injection \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql} injection, {\sc xss} \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5--24\% & {\sc xss} \\
     & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
-    & 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
-    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5---24\% & {\sc xss} \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & \tick,\tick & 39\% & {\sc sql} and {\sc xp}ath injection \\
+	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
+	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
     \end{threeparttable}
+\end{table}
+\end{landscape}
+
+\begin{table*}
+\centering
+    \begin{threeparttable}
+    \begin{small}
+\scalebox{0.99}{
+    \begin{tabular}{l|c|ccc}
+    \hline
+    \bf{Approach}
+	& \bf{Mechanism}
+    & \multicolumn{3}{|c|}{Availability} \\
+	&& \bf{Source Code}
+	& \bf{Executable}\tnote{4}
+	& \bf{Testbed} \\
+    \hline
+	\multirow{9}{*}{Runtime Tainting}
+	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & - \\
+	&  	{\it Haldar et al.}~\cite{HCF05}  & {\bf ?},{\bf ?} & \xmark & - \\ 
+	&  	{\it SecuriFly}~\cite{MLL05}  & \xmark,\tick & 9--125\% & - \\ 
+	&  	{\it Xu et al.}~\cite{XBS06}  & \tick,\xmark & 76\% & - \\ 
+    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & - \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & \xmark,{\bf ?} & {\bf ?} & - \\
+	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & - \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & - \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7--17\% & - \\
+	\hline
+	\hline      
+	\multirow{3}{*}{{\sc isr}}
+	&   {\it {\sc sql}rand}~\cite{BK04}  & {\bf ?},{\bf ?} & 6.5{\it ms} & - \\ 
+	&   {\it Noncespaces}~\cite{GC09}  & \tick,\tick &  10.3\% & - \\ 
+    &   {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & - \\
+	\hline
+	\hline    
+	\multirow{13}{*}{Policy Enforcement}
+	&   {\it {\sc dsi}}~\cite{NSS06}  & \xmark,\xmark & 1.85\% & - \\ 
+	&   {\it BrowserShield}~\cite{RDWDE07}  & \tick,\tick & 8\% & - \\ 
+	&   {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
+	&   {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
+    &   {\it {\sc beep}}~\cite{TNH07} & \tick,\tick & 14.4\% & - \\
+    &   {\it {\sc soma}}~\cite{OWVS08}  & 5,0,0,0 & 5.58\% & - \\
+	&   {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & - \\ 
+	&   {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & - \\
+	&   {\it WebJail}~\cite{VDDPJ11}  & {\bf ?},{\bf ?} & $\sim$7ms & - \\ 
+	&   {\it ConScript}~\cite{ML10}  & {\bf ?},{\bf ?} & 7\% & - \\
+	&   {\it j{\sc csrf}}~\cite{PS11}  & 2,7,0,0 & 2ms & - \\
+    &   {\it TreeHouse}~\cite{IW12}  & {\bf ?},{\bf ?} & 757–-1218ms & - \\
+   	&   {\it {\sc js}and}~\cite{AVBPDP12}  & {\bf ?},{\bf ?} & up to 365\% & - \\
+	\hline
+	\hline  
+        \multirow{12}{*}{Training}
+    &   {\it {\sc didafit}}~\cite{LLW02}  & \xmark,\xmark & {\bf ?} & - \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & - \\ 
+	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & - \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & - \\
+	& 	{\it {\sc sm}ask}~\cite{JB07}  & \xmark,\xmark & {\bf ?} & - \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & \xmark,\xmark & {\bf ?} & - \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5--24\% & - \\
+    & 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & - \\ 
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick,\tick & 39\% & - \\
+	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & - \\
+	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & - \\
+	\hline
+    \end{tabular}}
+    \begin{tablenotes}
+	\begin{footnotesize}
+       \item[1] {\it Flexibility} indicates if the approach can be adjusted
+	in order to detect different {\sc cia} categories.
+       \item[4] {\it User Experience} is affected if the mechanism suffers
+	from runtime overhead.
+	\end{footnotesize}
+    \end{tablenotes}
+    \caption{Availability of the corresponding mechanisms.}
+    \label{tab:comp2}
+    \end{small}
+    \end{threeparttable}
 \end{table*}

### 2014-09-19 docs/questioning.tex
minor changes

@@
 	&& \bf{Source Code}
-	& \bf{Executable}\tnote{4}
+	& \bf{Executable}
 	& \bf{Testbed} \\
@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & \xmark,\xmark & 2--10\% & - \\
-	&  	{\it Haldar et al.}~\cite{HCF05}  & {\bf ?},{\bf ?} & \xmark & - \\ 
-	&  	{\it SecuriFly}~\cite{MLL05}  & \xmark,\tick & 9--125\% & - \\ 
-	&  	{\it Xu et al.}~\cite{XBS06}  & \tick,\xmark & 76\% & - \\ 
-    &  	{\it {\sc wasc}}~\cite{NLC07} & \xmark,\xmark & 30\% & - \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & \xmark,{\bf ?} & {\bf ?} & - \\
-	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & - \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & \xmark,\xmark & 2.2$\times$ & - \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0.09\%,\xmark & 7--17\% & - \\
+	&  	{\sc csse}~\cite{PB05} & - & - & - \\
+	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 
+	&  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
+	&  	{\it Xu et al.}~\cite{XBS06}  & - & - & - \\
+    &  	{\it {\sc wasc}}~\cite{NLC07} & - & - & - \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & - & - & - \\
+	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & - & - & - \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & - & - & - \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & - & - & - \\
 	\hline
@@
 	\multirow{3}{*}{{\sc isr}}
-	&   {\it {\sc sql}rand}~\cite{BK04}  & {\bf ?},{\bf ?} & 6.5{\it ms} & - \\ 
-	&   {\it Noncespaces}~\cite{GC09}  & \tick,\tick &  10.3\% & - \\ 
-    &   {\it x{\sc js}}~\cite{APKLM10} & \tick,\tick & 1.6--40{\it ms} & - \\
+	&   {\it {\sc sql}rand}~\cite{BK04} & - & - & - \\
+	&   {\it Noncespaces}~\cite{GC09} & - & - & - \\ 
+    &   {\it x{\sc js}}~\cite{APKLM10} & - & - & - \\
 	\hline
@@
 	\multirow{13}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06}  & \xmark,\xmark & 1.85\% & - \\ 
-	&   {\it BrowserShield}~\cite{RDWDE07}  & \tick,\tick & 8\% & - \\ 
-	&   {\it CoreScript}~\cite{YCIS07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
-	&   {\it {\sc met}}~\cite{ELX07} & {\bf ?},{\bf ?} &  {\bf ?} & - \\ 
-    &   {\it {\sc beep}}~\cite{TNH07} & \tick,\tick & 14.4\% & - \\
-    &   {\it {\sc soma}}~\cite{OWVS08}  & 5,0,0,0 & 5.58\% & - \\
-	&   {\it Blueprint}~\cite{LV09} & \tick/\tick & 13.6\% & - \\ 
-	&   {\it Phung et al.}~\cite{PSC09} & \xmark,{\bf ?} & 5.37\% & - \\
-	&   {\it WebJail}~\cite{VDDPJ11}  & {\bf ?},{\bf ?} & $\sim$7ms & - \\ 
-	&   {\it ConScript}~\cite{ML10}  & {\bf ?},{\bf ?} & 7\% & - \\
-	&   {\it j{\sc csrf}}~\cite{PS11}  & 2,7,0,0 & 2ms & - \\
-    &   {\it TreeHouse}~\cite{IW12}  & {\bf ?},{\bf ?} & 757–-1218ms & - \\
-   	&   {\it {\sc js}and}~\cite{AVBPDP12}  & {\bf ?},{\bf ?} & up to 365\% & - \\
+	&   {\it {\sc dsi}}~\cite{NSS06} & - & - & - \\ 
+	&   {\it BrowserShield}~\cite{RDWDE07} & - & - & - \\
+	&   {\it CoreScript}~\cite{YCIS07} & - & - & - \\
+	&   {\it {\sc met}}~\cite{ELX07} & - & - & - \\ 
+    &   {\it {\sc beep}}~\cite{TNH07} & - & - & - \\
+    &   {\it {\sc soma}}~\cite{OWVS08} & - & - & - \\
+	&   {\it Blueprint}~\cite{LV09} & - & - & - \\
+	&   {\it Phung et al.}~\cite{PSC09} & - & - & - \\
+	&   {\it WebJail}~\cite{VDDPJ11} & - & - & - \\
+	&   {\it ConScript}~\cite{ML10} & - & - & - \\
+	&   {\it j{\sc csrf}}~\cite{PS11} & - & - & - \\
+    &   {\it TreeHouse}~\cite{IW12} & - & - & - \\
+   	&   {\it {\sc js}and}~\cite{AVBPDP12} & - & - & - \\
 	\hline
@@
         \multirow{12}{*}{Training}
-    &   {\it {\sc didafit}}~\cite{LLW02}  & \xmark,\xmark & {\bf ?} & - \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & \tick,\tick & {\bf ?} & - \\ 
-	&   {\it Valeur et al.}~\cite{VMV05} & 0.37\%,{\bf ?} & 1{\it ms} & - \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\bf ?},{\bf ?} & 3\% & - \\
-	& 	{\it {\sc sm}ask}~\cite{JB07}  & \xmark,\xmark & {\bf ?} & - \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & \xmark,\xmark & {\bf ?} & - \\
-    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\bf ?},\xmark & 5--24\% & - \\
-    & 	{\it {\sc swap}}~\cite{WPLKK09} & \tick,\tick & $\sim$180\% & - \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick,\tick & 39\% & - \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & \xmark,\xmark  & \xmark & - \\
-	& 	{\it Diglossia}~\cite{SMS13} & \xmark,\xmark  & 13\% & - \\
+    &   {\it {\sc didafit}}~\cite{LLW02} & - & - & - \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & - & - & - \\ 
+	&   {\it Valeur et al.}~\cite{VMV05} & - & - & - \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & - & - & - \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
+    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & - & - & - \\
+	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
+	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
 	\hline
     \end{tabular}}
-    \begin{tablenotes}
-	\begin{footnotesize}
-       \item[1] {\it Flexibility} indicates if the approach can be adjusted
-	in order to detect different {\sc cia} categories.
-       \item[4] {\it User Experience} is affected if the mechanism suffers
-	from runtime overhead.
-	\end{footnotesize}
-    \end{tablenotes}
     \caption{Availability of the corresponding mechanisms.}

### 2014-09-20 docs/questioning.tex
started with the metadata

@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\
+	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc na},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\
 	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} injection \\ 
@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & - & - & - \\
+	&  	{\sc csse}~\cite{PB05} & \xmark & \xmark & \xmark \\
 	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 

### 2014-09-21 docs/questioning.tex
adding content, filling the tables.

--- 2014-09-19 docs/questioning.tex
@@
 application attacks, in terms of citations.
+% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
 
@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & 312 & \xmark,\xmark & 2--10\% & {\sc sql} injection \\
-	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & {\bf ?},{\bf ?} & \xmark & {\sc sql} injection \\ 
-	&  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & \tick,\xmark & 76\% & {\sc sql} injection, {\sc xss} \\ 
-    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & \xmark,\xmark & 30\% & {\sc sql} injection, {\sc xss} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & \xmark,{\bf ?} & {\bf ?} & {\sc xss} \\
-	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & {\bf ?},{\bf ?},{\bf ?},{\bf ?} & {\bf ?} & {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & \xmark,\xmark & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & 0.09\%,\xmark & 7--17\% & {\sc xss} \\
+	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\
+	&  	{\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
+	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss}, Buffer Overflows \\ 
+    &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
+	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (15,{\sc nq},{\sc nq},{\sc nq})\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
 	\hline
@@
 	\multirow{3}{*}{{\sc isr}}
-	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & {\bf ?},{\bf ?} & 6.5{\it ms} & {\sc sql} injection \\ 
-	&   {\it Noncespaces}~\cite{GC09} & 109 & \tick,\tick &  10.3\% & {\sc xss} \\ 
-    &   {\it x{\sc js}}~\cite{APKLM10} & 18 & \tick,\tick & 1.6--40{\it ms} & {\sc xss} \\
+	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
+	&   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
+    &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
 	\hline
 	\hline    
-	\multirow{13}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06} & 135 & \xmark,\xmark & 1.85\% & {\sc xss} \\ 
-	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & \tick,\tick & 8\% & {\sc xss} \\ 
-	&   {\it CoreScript}~\cite{YCIS07} & 181 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
-	&   {\it {\sc met}}~\cite{ELX07} & 58 & {\bf ?},{\bf ?} &  {\bf ?} & {\sc xss} \\ 
-    &   {\it {\sc beep}}~\cite{TNH07} & 282 & \tick,\tick & 14.4\% & {\sc xss} \\
-    &   {\it {\sc soma}}~\cite{OWVS08} & 46 & 5,0,0,0 & 5.58\% & {\sc xss}, {\sc csrf}\\
-	&   {\it Blueprint}~\cite{LV09} & 110 & \tick/\tick & 13.6\% & {\sc xss} \\ 
-	&   {\it Phung et al.}~\cite{PSC09} & 75 & \xmark,{\bf ?} & 5.37\% & {\sc xss} \\
-	&   {\it WebJail}~\cite{VDDPJ11} & 25 & {\bf ?},{\bf ?} & $\sim$7ms & {\sc xss} \\ 
-	&   {\it ConScript}~\cite{ML10} & 122 & {\bf ?},{\bf ?} & 7\% & {\sc xss} \\
-	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & 2,7,0,0 & 2ms & {\sc csrf} \\
-    &   {\it TreeHouse}~\cite{IW12} & 18 & {\bf ?},{\bf ?} & 757–-1218ms & {\sc xss} \\
-   	&   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & {\bf ?},{\bf ?} & up to 365\% & {\sc xss}\\
+	\multirow{12}{*}{Policy Enforcement}
+	&   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
+	&   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\ 
+	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
+    &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
+    &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
+	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
+	&   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
+	&   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\ 
+	&   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
+    &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
+   	% TODO@dimitro: discuss this with Panos?
 	\hline
@@
         \multirow{12}{*}{Training}
-    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & \xmark,\xmark & {\bf ?} & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & \tick,\tick & {\bf ?} & {\sc sql} injection \\ 
-	&   {\it Valeur et al.}~\cite{VMV05} & 226 & 0.37\%,{\bf ?} & 1{\it ms} & {\sc sql} injection \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & {\bf ?},{\bf ?} & 3\% & {\sc sql} injection \\
+    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\bf ?} & {\sc sql} injection \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,0,0,0)\_a & {\bf ?} & {\sc sql} injection \\ 
+	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
 	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql} injection, {\sc xss} \\
@@
 
+\section{Analysis}
+
+{\sc na} means that a requirement is not even mentioned in the paper.
+{\sc nq} indicates that a requirement is mentioned in the publication
+but it is not quantified.
+
+Notes on taint tools:
+\begin{enumerate}
+\item The accuracy testing of {\sc csse}~\cite{PB05} was based on 
+defects found in the security mailing
+list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
+\item During their evaluation, the authors of~\cite{HCF05} have only performed
+two attacks in one synthetic benchmark ({\sc owasp}'s
+{\it WebGoat}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_WebGoat_Project}}).
+\item The testing in~\cite{XBS06} was made based on
+defects with specific {\sc cve id}s.
+\item The authors of {\it {\sc wasc}}~\cite{NLC07}
+mention the vulnerabilities (specific {\sc cve id}s)
+exploited and the corresponding applications but they do not explicitly
+state how many attacks they launched (``{\it [...] launched a variety of
+attacks against it}").
+\item The authors of~\cite{VFJKKV07} do the same.
+However, even if they do not mention specific {\sc cve id}s,
+they browsed applications without performing attacks.
+\item Even if the authors of {\it Noxes}~\cite{KKVJ06,KJKV09} state in
+both papers that ``{\it [...] we are planning to make the tool available as
+a freeware utility}." the tool cannot be found anywhere on the Internet.
+The vulnerabilities exploited during testing were reported
+by {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
+\item {\it {\sc php} Aspis}~\cite{PMP11} was tested on only one
+application (Wordpress 2.9.2) with multiple vulnerabilities (specific {\sc cve id}s).
+\item During their initial tests, the authors of
+managed to bypass the browser-based {\sc xss} filters of the
+73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
+Then they proposed an approach that detected all the attacks they
+found (1169). This is a complex paper --- we need to elaborate.
+\end{enumerate}
+
+Notes on {\sc isr} mechanisms:
+\begin{enumerate}
+\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve}.
+\item {\it Noncespaces}~\cite{GC09} was only tested on one
+known vulnerable application (TikiWiki). The authors mention that they performed
+a number of attacks but they do not state how many.
+\item The authors of {\it x{\sc js}}~\cite{APKLM10}, have tested
+their mechanisms based on real-world attacks coming from
+{\sc xss}ed.com.\footnote{www.xssed.com}
+\end{enumerate}
+
+Notes on policy enforcement tools:
+\begin{enumerate}
+\item Just like the authors of {\it x{\sc js}~\cite{APKLM10},
+the authors of {\sc dsi}}~\cite{NSS06}, have tested
+their mechanisms based on real-world attacks coming from
+{\sc xss}ed.com.\footnote{www.xssed.com}
+\item The testing of {\it BrowserShield}~\cite{RDWDE07}
+involved {\sc xss} vulnerabilities reported by Microsoft
+in 2005.\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
+The link currently shows defects for 2014.
+\item {\it CoreScript}~\cite{YCIS07} is more of a programming
+language\footnote{``[...] uses program instrumentation for
+JavaScript where untrusted JavaScript
+code goes through a rewriting process according to a security policy
+before executing them in the browser"~\cite{PSC09}.}
+than an {\sc IDS}.
+\item Surprisingly, {\sc met}~\cite{ELX07} was not tested at all.
+\item {\sc beep}~\cite{TNH07}'s test suite was based on 61 {\sc xss}
+attack vectors published by \url{ha.ckers.org}.
+\item {\sc soma}~\cite{OWVS08} --- all synthetics.
+\item The attacks used for the testing of {\it Blueprint}~\cite{LV09},
+came from \url{ha.ckers.org}.
+\item {\it Phung et al.}~\cite{PSC09} also utilized \url{ha.ckers.org}.
+\item {\it WebJail}~\cite{VDDPJ11} --- not tested at all.
+\item {\it ConScript}~\cite{ML10} --- not tested at all. A scheme
+similar to {\it CoreScript}~\cite{YCIS07}.
+\item {\it j{\sc csrf}}~\cite{PS11} --- based on {\sc csrf}
+defects with specific {\sc cve id}s.
+\item The authors of {\it TreeHouse}~\cite{IW12} have tested
+only the overhead and how easy is to incorporate the mechanism
+into an application.
+\end{enumerate}
+
+Notes on training-based mechanisms:
+\begin{enumerate}
+\item {\it {\sc didafit}}~\cite{LLW02} is one of
+the first {\sc ids}.
+\item {\sc amnesia}~\cite{HO05,HO06,HO05b} was tested
+on applications with known vulnerabilities taken
+from \url{http://gotocode.com} plus two synthetic benchmarks.
+Interestingly, in one of the papers~\cite{HO06},
+the authors mention that the tool can produce both {\sc fp} and
+{\sc fn}.
+\item {\it libAnomaly}~\cite{VMV05} --- one application tested ({\sc php}-Nuke).
+\item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
+\end{enumerate}
+
 \begin{table*}
@@
 	& \bf{Mechanism}
-    & \multicolumn{3}{|c|}{Availability} \\
+    & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
 	&& \bf{Source Code}
@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & - & - & - \\
-	&  	{\it Haldar et al.}~\cite{HCF05}  & - & - & - \\ 
-	&  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
-	&  	{\it Xu et al.}~\cite{XBS06}  & - & - & - \\
-    &  	{\it {\sc wasc}}~\cite{NLC07} & - & - & - \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & - & - & - \\
-	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & - & - & - \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & - & - & - \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & - & - & - \\
+	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
+	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
+	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
+    &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline
@@
 	\multirow{3}{*}{{\sc isr}}
-	&   {\it {\sc sql}rand}~\cite{BK04} & - & - & - \\
-	&   {\it Noncespaces}~\cite{GC09} & - & - & - \\ 
-    &   {\it x{\sc js}}~\cite{APKLM10} & - & - & - \\
+	&   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
+    &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline
 	\hline    
-	\multirow{13}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06} & - & - & - \\ 
-	&   {\it BrowserShield}~\cite{RDWDE07} & - & - & - \\
-	&   {\it CoreScript}~\cite{YCIS07} & - & - & - \\
-	&   {\it {\sc met}}~\cite{ELX07} & - & - & - \\ 
-    &   {\it {\sc beep}}~\cite{TNH07} & - & - & - \\
-    &   {\it {\sc soma}}~\cite{OWVS08} & - & - & - \\
-	&   {\it Blueprint}~\cite{LV09} & - & - & - \\
-	&   {\it Phung et al.}~\cite{PSC09} & - & - & - \\
-	&   {\it WebJail}~\cite{VDDPJ11} & - & - & - \\
-	&   {\it ConScript}~\cite{ML10} & - & - & - \\
-	&   {\it j{\sc csrf}}~\cite{PS11} & - & - & - \\
-    &   {\it TreeHouse}~\cite{IW12} & - & - & - \\
-   	&   {\it {\sc js}and}~\cite{AVBPDP12} & - & - & - \\
+	\multirow{12}{*}{Policy Enforcement}
+	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
+	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
+    &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
+    &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
+	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
+	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
+	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
+    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
+   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline
@@
         \multirow{12}{*}{Training}
-    &   {\it {\sc didafit}}~\cite{LLW02} & - & - & - \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & - & - & - \\ 
-	&   {\it Valeur et al.}~\cite{VMV05} & - & - & - \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & - & - & - \\
+    &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
+	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
+	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
 	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
@@
     & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & - & - & - \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
 	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
@@
     \end{tabular}}
+        \begin{tablenotes}
+	\begin{footnotesize}
+       \item[1] The check mark (\tick) indicates that some point within
+       the publication there is a homepage where the reader can refer to, to
+       download the corresponding software. {\sc ao} (Available On-line) suggests
+       that the software is available on-line but the
+       address was not mentioned in the paper, which probably indicates that
+       the authors made it available after the publication. The question ({\bf ?})
+       mark, indicates that the a homepage for the software was included
+       in the publication but now it is not available.
+	\end{footnotesize}
+    \end{tablenotes}
     \caption{Availability of the corresponding mechanisms.}

### 2014-09-21 docs/questioning.tex
filled all tables.

@@
 	\hline  
-        \multirow{12}{*}{Training}
+        \multirow{11}{*}{Training}
     &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\bf ?} & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,0,0,0)\_a & {\bf ?} & {\sc sql} injection \\ 
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\bf ?} & {\sc sql} injection \\ 
 	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
 	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & \xmark,\xmark & {\bf ?} & {\sc sql} injection, {\sc xss} \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & \xmark,\xmark & {\bf ?} &  {\sc xss} \\
-    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & {\bf ?},\xmark & 5--24\% & {\sc xss} \\
-    & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & \tick,\tick & $\sim$180\% & {\sc xss} \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & \tick,\tick & 39\% & {\sc sql} and {\sc xp}ath injection \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-	& 	{\it Diglossia}~\cite{SMS13} & 3 & \xmark,\xmark  & 13\% & {\sc sql} and No{\sc sql} injection \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\bf ?} & {\sc sql} injection, {\sc xss} \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\bf ?} &  {\sc xss} \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
+    & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
+	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
+	& 	{\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
 \begin{enumerate}
-\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve}.
+\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve} --- though
+this is not mentioned in the publication.
 \item {\it Noncespaces}~\cite{GC09} was only tested on one
@@
 \item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
+\item {\sc sm}ask~\cite{JB07} was tested on real-world applications
+with exploits from {\sc cve} --- though this is not mentioned in the publication.
+\item {\sc xssds}~\cite{JEP08} --- testing was based on 
+defects found in the security mailing
+list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
+The authors provide multiple {\sc fp} rates depending on the experiment.
+\item {\sc xss-guard}~\cite{BV08} was tested on real-world applications
+with exploits from {\sc cve}.
+\item {\sc swap}~\cite{WPLKK09} was tested on a real-world application ({\sc phpbb})
+with exploits from {\sc cve} --- though this is not mentioned in the publication.
+%\item {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} have developed a
+%mechanism to detect {\sc sql} and {\sc xp}ath injection attacks
+%only on web services. Their testing involve a real-world benchmark
+%({\sc tpc}-app).\footnote{\url{http://www.tpc.org/}}
+\item {\it Diglossia}~\cite{SMS13} was tested on real-world applications
+with exploits from {\sc cve}.
 \end{enumerate}
@@
 	\hline  
-        \multirow{12}{*}{Training}
+        \multirow{11}{*}{Training}
     &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & - & - & - \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & - & - & - \\
-    & 	{\it {\sc xss-guard}}~\cite{BV08} & - & - & - \\
-    & 	{\it {\sc swap}}~\cite{WPLKK09} & - & - & - \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
+    & 	{\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
+    & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
 	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
-	& 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & - & - & - \\
-	& 	{\it Diglossia}~\cite{SMS13} & - & - & - \\
+	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
+	& 	{\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline

### 2014-09-22 docs/questioning.tex
some additions - changes

@@
 
-\title{Questioning how Researchers Develop and Present Intrusion Detection Systems}
+\title{Questioning how Researchers Present Intrusion Detection Systems}
 
@@
 	& \bf{\# of Citations}
-    & \multicolumn{2}{|c|}{Requirements}
+    & \multicolumn{2}{|c|}{Requirements\tnote{1}}
 	& \bf{Attack} \\
 	&&& \bf{TP,TN,FP,FN}
-	& \bf{Computational Overhead}\tnote{4} & \\
+	& \bf{Computational Overhead} & \\
     \hline
@@
         \multirow{11}{*}{Training}
-    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\bf ?} & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\bf ?} & {\sc sql} injection \\ 
+    &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} & {\sc sql} injection \\ 
 	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
 	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\bf ?} & {\sc sql} injection, {\sc xss} \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\bf ?} &  {\sc xss} \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\
     & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
@@
 	\begin{footnotesize}
-       \item[1] {\it Flexibility} indicates if the approach can be adjusted
-	in order to detect different {\sc cia} categories.
-       \item[4] {\it User Experience} is affected if the mechanism suffers
-	from runtime overhead.
+       \item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.
+	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
+	but it is not quantified.
 	\end{footnotesize}
@@
 \section{Analysis}
-
-{\sc na} means that a requirement is not even mentioned in the paper.
-{\sc nq} indicates that a requirement is mentioned in the publication
-but it is not quantified.
 

### 2014-09-23 docs/questioning.tex
new title (SoK is a mandatory prefix)
we need to define our terms

@@
 
-\title{Questioning how Researchers Present Intrusion Detection Systems}
+\title{SoK: Application Attack Defenses (in Question)}
 
@@
 \begin{abstract}
-In this paper we examine how intrusion-detection
-systems developed to counter a specific category
-of application attacks are developed and presented to
+In this paper we examine how application attack defense
+mechanism are developed and presented to
 the research community.
@@
 \begin{IEEEkeywords}
-Security and Protection, Intrusion-Detection Systems, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
+Security and Protection, Application Security, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
 \end{IEEEkeywords}
@@
 
-\section{Intrusion Detection Accuracy}
+\section{Application Attack Defense Mechanisms Accuracy}
+% @Panos: we need to change our terminology. Instead of intrusion-detection
+% systems we need to move to something like application attack defences.
+% Intrusion detection is very broad and we are currently
+% surveying mechanisms that detect attacks coming from a specific catefory.
 

### 2014-09-23 docs/questioning.tex
better definitions and discussion

@@
 
-The evaluation of
+\section{Methodological Background}
 
-\section{Analysis Dimensions}
-
+As in medical diagnostic tests, application attack defense mechanisms
+must demonstrate the presence of an attack. This, however, does not
+make an application attack defense mechanism immediately useful. In
+order for a detection mechanism to be useful it must accurate, easy to
+use, and economical. The accuracy of a detection mechanism is gauged
+with the following metrics:
 \begin{itemize}
@@
 
-To do any meaningful calculation of the above, we need to define
-precisely the following in our methodology:
+For example, a simple announcement that an attach defense mechanism
+catches an attack says very little about the usability and
+applicability of the mechanism. There may be some value in indicating
+that detection \emph{per se} is possible, if that has been considered
+infeasible in the past. Most value, though, comes from knowing the
+answers to questions like the following, which correspond to the
+previous metrics:
 \begin{itemize}
-\item True Positive (TP)
-\item False Positive (FP)
-\item True Negative (TN)
-\item False Negative (FN)
+\item Does it catch all the attacks? If not, how many of them?
+\item Does it catch only attacks? If not, how many false alarms would
+  we expect?
+\item How much should we be worried if we do get an alarm?
+\item How much at ease should we be if no alarm is raised?
 \end{itemize}
 
-\section{Application Attack Defense Mechanisms Accuracy}
-% @Panos: we need to change our terminology. Instead of intrusion-detection
-% systems we need to move to something like application attack defences.
-% Intrusion detection is very broad and we are currently
-% surveying mechanisms that detect attacks coming from a specific catefory.
+Sensitivity, specificity, PPV, and NPV, are defined precisely by way
+of the $2\times 2$ Table~\ref{tab:attacks-outcomes}. In the cells of
+the table we distinguish:
+\begin{itemize}
+\item True Positive (TP), a real attack that raises an alarm.
+\item False Positive (FP), an event that although it is not an attack
+  raises an alarm.
+\item True Negative (TN), an event that is not an attack and that does
+  not raise an alarm.
+\item False Negative (FN), an event that although is as attack does
+  not raise an alarm.
+\end{itemize}
 
-An intrusion detection system examines some software artifact and
-reports vulnerabilities. The value an intrusion detection system can
-be measured in terms of its \emph{accuracy}, which gauges the quality
-of its output. An intrusion detection system:
-\begin{itemize}
-\item A prediction about a vulnerability is true. That is a \emph{true
-    positive}. 
-\item A prediction about a vulnerability is false; intrusion
-  detection reported something that in reality is not vulnerability.
-  That is a \emph{false positive}.
-\item A prediction about the absence of a vulnerability is true. That
-  is a \emph{true negative}: intrusion detection evaluated something
-  as being safe, and it is.
-\item A prediction about the absence of a vulnerability is false. That
-  is a \emph{false negative}: intrusion detection missed a
-  vulnerability.
-\end{itemize}
-In terms of the above, the \emph{Positive Predictive Value} (PPV) is
-defined as the ratio of true positives over all reported positives,
-while the \emph{Negative Predictive Value} (NPV) is defined as the
-ratio of true negatives over all reported negatives. In intrusion
-detection, the PPV is an indicator of how much we should be worried
-about a reported vulnerability being true. Conversely, the NPV is an
-indicator of how much we should be reassured when no vulnerabilities
-are reported.
+With these we can calculate:
 
-What we need to proceed:
-\begin{itemize}
-\item Do the studies report the sample size? Note that we must be
-  careful with what we mean by sample size. A single item in the
-  sample is something that can be vulnerable or not. 
-\item Do the studies report true positives, false positives, true
-  negatives, false negatives?
-\end{itemize}
+\begin{equation}
+\textrm{sensitivity} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{TN}}
+\end{equation}
+
+\begin{equation}
+\textrm{specificity} = \frac{\textrm{TP}}{\textrm{TN} + \textrm{FP}}
+\end{equation}
+
+\begin{equation}
+\textrm{PPV} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}}
+\end{equation}
+
+\begin{equation}
+\textrm{NPV} = \frac{\textrm{TN}}{\textrm{TN} + \textrm{FN}}
+\end{equation}
+
+\begin{table}[ht]
+
+\caption{Attacks and Test Outcomes}
+\label{tab:attacks-outcomes}
+
+\begin{tabular}{l|l|c|c|}
+\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} \\ \cline{3-4}
+\multicolumn{2}{c|}{} & Yes & No \\ \cline{2-4}
+\multirow{2}{*}{Result} &  Yes &  True Positive & False Positive \\
+& No & False Negative & True Negative \\ \cline{2-4}
+\end{tabular}
+
+\end{table}
+
+Sensitivity and specificity can be calculated based on test results
+alone. To calculate the sensitivity, we run the test on a controlled
+environment where we allow only attack events to reach the system. The
+ratio of reported attacks over all events will give us the
+sensitivity. Similarly, to calculate the specificity we can run the
+test on a controlled environment where we allow only innocuous events
+to reach the system. The ratio of non-reported events over all events
+will give us the specificity.
+
+The calculation of PPV and NPV requires that we evaluate the attack
+defense mechanism on a real operational environment where the events
+are a mix of attacks and innocuous events and, moreover, the mix ratio
+is the ratio of attacks over harmless events that exists in actual
+operations. Too few or too many attacks will skew metrics calculations.
+
+The last requirement may seem cumbersome, but consider that, in actual
+operations, PPV is what would determine our actions. Administrators
+will limited resources need to allocate their attention judiciously.
+They may need to prioritize responses to emergency warnings; the PPV
+value will indicate them what priority to give to a raised alarm.
 

### 2014-09-23 docs/questioning.tex
small caps where needed, fixed two typos

@@
 make an application attack defense mechanism immediately useful. In
-order for a detection mechanism to be useful it must accurate, easy to
+order for a detection mechanism to be useful it must be accurate, easy to
 use, and economical. The accuracy of a detection mechanism is gauged
@@
   will test negative.
-\item {\bf Positive Predictive Value} (PPV), the probability that a
+\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
   reported attack is a real attack.
-\item {\bf Negative Predictive Value} (NPV), the probability that if
+\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
   nothing is reported no attack has taken place.
@@
 
-For example, a simple announcement that an attach defense mechanism
+For example, a simple announcement that an attack defense mechanism
 catches an attack says very little about the usability and
@@
 
-Sensitivity, specificity, PPV, and NPV, are defined precisely by way
+Sensitivity, specificity, {\sc ppv}, and {\sc npv}, are defined precisely by way
 of the $2\times 2$ Table~\ref{tab:attacks-outcomes}. In the cells of
@@
 \begin{itemize}
-\item True Positive (TP), a real attack that raises an alarm.
-\item False Positive (FP), an event that although it is not an attack
+\item True Positive ({\sc tp}), a real attack that raises an alarm.
+\item True Negative ({\sc tn}), an event that is not an attack and that does
+  not raise an alarm.
+\item False Positive ({\sc fp}), an event that although it is not an attack
   raises an alarm.
-\item True Negative (TN), an event that is not an attack and that does
-  not raise an alarm.
-\item False Negative (FN), an event that although is as attack does
+\item False Negative ({\sc fn}), an event that although is as attack does
   not raise an alarm.
@@
 
+\noindent
 With these we can calculate:
@@
 \begin{equation}
-\textrm{sensitivity} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{TN}}
+\textrm{Sensitivity} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tp}} + \textrm{{\sc tn}}}
 \end{equation}
@@
 \begin{equation}
-\textrm{specificity} = \frac{\textrm{TP}}{\textrm{TN} + \textrm{FP}}
+\textrm{Specificity} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tn}} + \textrm{{\sc fp}}}
 \end{equation}
@@
 \begin{equation}
-\textrm{PPV} = \frac{\textrm{TP}}{\textrm{TP} + \textrm{FP}}
+\textrm{{\sc ppv}} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tp}} + \textrm{{\sc fp}}}
 \end{equation}
@@
 \begin{equation}
-\textrm{NPV} = \frac{\textrm{TN}}{\textrm{TN} + \textrm{FN}}
+\textrm{{\sc npv}} = \frac{\textrm{{\sc tn}}}{\textrm{{\sc tn}} + \textrm{{\sc fn}}}
 \end{equation}
@@
 
-The calculation of PPV and NPV requires that we evaluate the attack
+The calculation of {\sc ppv} and {\sc npv} requires that we evaluate the attack
 defense mechanism on a real operational environment where the events
@@
 The last requirement may seem cumbersome, but consider that, in actual
-operations, PPV is what would determine our actions. Administrators
+operations, {\sc ppv} is what would determine our actions. Administrators
 will limited resources need to allocate their attention judiciously.
-They may need to prioritize responses to emergency warnings; the PPV
+They may need to prioritize responses to emergency warnings; the {\sc ppv}
 value will indicate them what priority to give to a raised alarm.

### 2014-09-23 docs/questioning.tex
added a note for the suffixes
added one bibtex entry

@@
 use, and economical. The accuracy of a detection mechanism is gauged
-with the following metrics:
+with the following metrics~\cite{GFDLS06,A00}:
 \begin{itemize}
@@
 	& \bf{Attack} \\
-	&&& \bf{TP,TN,FP,FN}
+	&&& \bf{TP,TN,FP,FN}\tnote{2}
 	& \bf{Computational Overhead} & \\
@@
 	but it is not quantified.
+		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
+	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).
+	If no testing has taken place we add a question mark ({\bf ?}).
 	\end{footnotesize}

### 2014-10-07 docs/questioning.tex
various additions and better definitions

@@
 use, and economical. The accuracy of a detection mechanism is gauged
-with the following metrics~\cite{GFDLS06,A00}:
+with the following metrics~\cite{TDR2013,GFDLS06,A00}:
 \begin{itemize}
@@
 \item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
-  reported attack is a real attack.
+  reported attack is a real attack. It is the conditional probability
+  that an event is an attack if the detection mechanism flags it as
+  such. 
 \item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
-  nothing is reported no attack has taken place.
+  nothing is reported no attack has taken place. It is the conditional
+  probability that an event is not an attack given that the detection
+  mechanism flags it as normal.
 \end{itemize}
 
-For example, a simple announcement that an attack defense mechanism
-catches an attack says very little about the usability and
-applicability of the mechanism. There may be some value in indicating
-that detection \emph{per se} is possible, if that has been considered
-infeasible in the past. Most value, though, comes from knowing the
-answers to questions like the following, which correspond to the
-previous metrics:
-\begin{itemize}
-\item Does it catch all the attacks? If not, how many of them?
-\item Does it catch only attacks? If not, how many false alarms would
-  we expect?
-\item How much should we be worried if we do get an alarm?
-\item How much at ease should we be if no alarm is raised?
-\end{itemize}
-
-Sensitivity, specificity, {\sc ppv}, and {\sc npv}, are defined precisely by way
-of the $2\times 2$ Table~\ref{tab:attacks-outcomes}. In the cells of
+Sensitivity and specifity are defined by way of the $2\times 2$
+Table~\ref{tab:sensitivity-specificity}~\cite{linn2004}. 
+In the cells of
 the table we distinguish:
 \begin{itemize}
-\item True Positive ({\sc tp}), a real attack that raises an alarm.
-\item True Negative ({\sc tn}), an event that is not an attack and that does
+\item True Positive ($a$), a real attack that raises an alarm.
+\item True Negative ($d$), an event that is not an attack and that does
   not raise an alarm.
-\item False Positive ({\sc fp}), an event that although it is not an attack
+\item False Positive ($b$), an event that although it is not an attack
   raises an alarm.
-\item False Negative ({\sc fn}), an event that although is as attack does
+\item False Negative ($c$), an event that although is as attack does
   not raise an alarm.
@@
 \begin{equation}
-\textrm{Sensitivity} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tp}} + \textrm{{\sc tn}}}
+\textrm{SE} = \textrm{Sensitivity} = \frac{a}{a + c}
 \end{equation}
@@
 \begin{equation}
-\textrm{Specificity} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tn}} + \textrm{{\sc fp}}}
+\textrm{SP} = \textrm{Specificity} = \frac{d}{b + d}
 \end{equation}
 
-\begin{equation}
-\textrm{{\sc ppv}} = \frac{\textrm{{\sc tp}}}{\textrm{{\sc tp}} + \textrm{{\sc fp}}}
-\end{equation}
-
-\begin{equation}
-\textrm{{\sc npv}} = \frac{\textrm{{\sc tn}}}{\textrm{{\sc tn}} + \textrm{{\sc fn}}}
-\end{equation}
+Sensitivity and specificity can be calculated based on test
+data alone. To calculate the sensitivity, we run the test on a
+controlled environment where we allow only attack events to reach the
+system. The ratio of reported attacks over all attacks will give us
+the sensitivity. Similarly, to calculate the specificity we can run
+the test on a controlled environment where we allow only innocuous
+events to reach the system. The ratio of non-reported events over all
+events will give us the specificity.
 
@@
 
-\caption{Attacks and Test Outcomes}
-\label{tab:attacks-outcomes}
+\caption{Attacks and Test Outcomes in Test Environment}
+\label{tab:sensitivity-specificity}
 
@@
 \multicolumn{2}{c|}{} & Yes & No \\ \cline{2-4}
-\multirow{2}{*}{Result} &  Yes &  True Positive & False Positive \\
-& No & False Negative & True Negative \\ \cline{2-4}
+\multirow{2}{*}{Result} &  Yes &  $a = \textrm{True Positive}$ & 
+$b = \textrm{False Positive}$ \\
+& No & $c = \textrm{False Negative}$ & $d = \textrm{True Negative}$ \\ 
+\cline{2-4}
+\multicolumn{2}{r|}{Total} & $a + c$ & $b + d$ \\
+\cline{3-4}
 \end{tabular}
@@
 
-Sensitivity and specificity can be calculated based on test results
-alone. To calculate the sensitivity, we run the test on a controlled
-environment where we allow only attack events to reach the system. The
-ratio of reported attacks over all events will give us the
-sensitivity. Similarly, to calculate the specificity we can run the
-test on a controlled environment where we allow only innocuous events
-to reach the system. The ratio of non-reported events over all events
-will give us the specificity.
+Note that the calculations are carried out vertically; the ratio of
+attack events to normal events does not enter into sensitivity and
+specificity. This is what allows us to derive them based on test data,
+without using data from a real production environment. At the same
+time, however, this is what limits their usefulness. When we obtain a
+test result in a production environment, be it negative or positive,
+we really want to know how much we should be worried. In other words,
+if an attack is detected in a production environment, how much should
+we be worried? If no attack is detected in a production environment,
+how relaxed should we be that no attack has indeed taken place?
 
-The calculation of {\sc ppv} and {\sc npv} requires that we evaluate the attack
-defense mechanism on a real operational environment where the events
-are a mix of attacks and innocuous events and, moreover, the mix ratio
-is the ratio of attacks over harmless events that exists in actual
-operations. Too few or too many attacks will skew metrics calculations.
+\begin{table}[ht]
 
-The last requirement may seem cumbersome, but consider that, in actual
-operations, {\sc ppv} is what would determine our actions. Administrators
-will limited resources need to allocate their attention judiciously.
-They may need to prioritize responses to emergency warnings; the {\sc ppv}
-value will indicate them what priority to give to a raised alarm.
+\caption{Attacks and Test Outcomes in Real Environment}
+\label{tab:ppv-npv}
+
+\begin{tabular}{l|l|c|c|c}
+\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} & \\ \cline{3-4}
+\multicolumn{2}{c|}{} & Yes & No & Total \\ \cline{2-5}
+\multirow{2}{*}{Result} &  Yes &  $A = \textrm{True Positive}$ & 
+$B = \textrm{False Positive}$ & \multicolumn{1}{c|}{$A + B$}\\
+& No & $C = \textrm{False Negative}$ & $D = \textrm{True Negative}$ &
+\multicolumn{1}{c|}{$C + D$}\\ 
+\cline{2-5}
+\end{tabular}
+
+\end{table}
+
+The answer to these questions is given by the \textsc{ppv} and the
+\textsc{npv}. These depend not only on the test results, but also on
+the \emph{prevalence} of attacks in real environments. In particular,
+we can calculate them using Table~\ref{tab:ppv-npv}, which tabulates
+results in a real environment, or in an environment where the
+prevalence of attacks is equal to what we expect in the real world. To
+indicate the difference with Table~\ref{tab:sensitivity-specificity}
+we use capital letters for the entries in the table~\cite{linn2004}.
+With this table, \textsc{ppv} and \textsc{npv} are given by the
+following equations:
+
+\begin{equation}
+\textrm{PPV} = \frac{A}{A + C}
+\end{equation}
+
+\begin{equation}
+\textrm{NPV} = \frac{D}{B + D}
+\end{equation}
+
+This time the ratios are taken horizontally; the ratio of attacks to
+innocuous events affects the calculations. In fact, if PR is the real
+probability that an attack happens, the prevalence, then we
+have~\cite{linn2004,altman1994}:
+
+\begin{equation}
+\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
+\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 - \textrm{PR})}
+\end{equation}
+
+\begin{equation}
+\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
+(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 - \textrm{PR})}
+\end{equation}
+
+The prevalence is the prior probability that an event is an attack,
+based on our understanding of the volume and frequency of attacks; the
+\textsc{ppv} and \textsc{npv} are the revised estimates of the
+probability based on the results of the detection
+mechanism~\cite{altman1994}.
 

### 2014-10-07 docs/questioning.tex
more on methodology

@@
 mechanism~\cite{altman1994}.
+
+In what follows we evaluate published research in attack detection
+mechanism based on the following:
+\begin{itemize}
+\item Reporting of values for True Positives ($a$), False Positives
+  ($b$), False Negatives ($c$), True Negatives ($d$), on test
+  environments.
+\item Reporting of values for True Positives ($A$), False Positives
+  ($B$), False Negatives ($C$), True Negatives ($D$), on the
+  performance of the mechanism on environment with real attack
+  profiles.
+\end{itemize}
 

### 2014-10-07 docs/questioning.tex
some more on methodology
typo

@@
 probability based on the results of the detection
-mechanism~\cite{altman1994}.
+mechanism~\cite{altman1994}. The lower the prevalence of an attack,
+the more confident we can be that a negative test result indicates
+that no attack has taken place and the less sure we can be that a
+positive test result indicates a real attack.
 
@@
   ($B$), False Negatives ($C$), True Negatives ($D$), on the
-  performance of the mechanism on environment with real attack
+  performance of the mechanism on environments with real attack
   profiles.

### 2014-10-07 docs/questioning.tex
some rephrasing
more fixes

@@
 
-Note that the calculations are carried out vertically; the ratio of
-attack events to normal events does not enter into sensitivity and
-specificity. This is what allows us to derive them based on test data,
-without using data from a real production environment. At the same
-time, however, this is what limits their usefulness. When we obtain a
-test result in a production environment, be it negative or positive,
-we really want to know how much we should be worried. In other words,
-if an attack is detected in a production environment, how much should
-we be worried? If no attack is detected in a production environment,
-how relaxed should we be that no attack has indeed taken place?
+Note that the calculations are carried out vertically in
+Table~\ref{tab:sensitivity-specificity}; the ratio of attack events to
+normal events does not enter into sensitivity and specificity. This is
+what allows us to derive them based on test data, without using data
+from a real production environment. At the same time, however, this is
+what limits their usefulness. When we obtain a test result in a
+production environment, be it negative or positive, we really want to
+know how much we should be worried, or relaxed. In other words, if an
+attack is detected in a production environment, how much should we be
+worried? If no attack is detected in a production environment, how
+relaxed should we be that no attack has indeed taken place?
 
@@
 This time the ratios are taken horizontally; the ratio of attacks to
-innocuous events affects the calculations. In fact, if PR is the real
-probability that an attack happens, the prevalence, then we
+innocuous events affects the calculations. In fact, if PR is the
+probability of attacks in the real world, the prevalence, then we
 have~\cite{linn2004,altman1994}:

### 2014-10-07 docs/questioning.tex
added attack section

@@
 \usepackage{hyperref}
-%\usepackage{graphicx}
+\usepackage{graphicx}
 \usepackage{fancyhdr}
@@
 
-\title{SoK: Application Attack Defenses (in Question)}
+\title{SoK: Web Application Attack Defenses (in Question)}
 
@@
 applications~\cite{A01,A00}.
+
+\section{Attacks}
+\label{sec:attacks}
+
+The basic problem behind web application attacks involves
+the absence of input validation. By taking advantage of
+this, attackers can inject either code into
+applications to perform malicious tasks. Such
+an exploit can have different forms depending on the
+execution context of the application and the location
+of the programming flaw that leads to the attack.
+
+Bratus et al.~\cite{BLSPS11} portray the issue in a generic fashion:
+{\it ``unexpected (and unexpectedly powerful) computational models
+inside targeted systems, which turn a part of the target into a
+so-called ``weird machine" programmable by the attacker via crafted inputs
+(a.k.a. ``exploits")"}.
+An example of the above definition is the
+following: The code fragment below, defines the operation of
+addition in the Scheme programming language~\cite{AS96,D09}:
+
+\begin{verbatim}
+(define (add x y) (+ x y))
+\end{verbatim}
+
+\noindent
+Consider the case where instead of a number, a function that leads to an
+endless loop is passed as an argument by the user. This will cause
+the interpreter to enter
+an endless loop and lead to a denial of service.
+% Keep in mind that a {\sc cia} does not require a programming
+% language with first-class functions.
+The intuition here is that {\it ``every application that copies
+untrusted input verbatim into an output
+program is vulnerable to code injection"}.
+Ray and Ligatti~\cite{RL12b} actually proved the above
+claim based on formal language theory.
+
+\begin{figure}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.37]{attack-tree-uml.pdf}
+\end{center}
+\caption{\label{fig:taxonomy}A taxonomy of code injection attacks.
+In our research we have excluded the defenses that deal with
+the subcategories that are illustrated in grey color.}
+\end{figure}
+
+Figure \ref{fig:taxonomy} presents a taxonomy of code injection attacks divided
+into two categories. The first involves binary code and the second
+executable source code.
+
+\subsection{Binary Code Injection}
+
+Binary code injection attacks involve
+the insertion of binary code into an application
+to alter its execution flow and execute malicious
+compiled code. This category involves buffer-overflow
+attacks~\cite{CPMHWBBGWZ98,K11}, a staple of security problems.
+An extensive survey on binary code
+injection attacks can be found in reference~\cite{LC03}.
+Furthermore, specific advances in exploiting such vulnerabilities
+(i.e. ``heap smashing", ``arc injection" and others)
+have been presented in reference~\cite{PB04}.
+Finally, the countermeasures used to detect
+such defects have already been surveyed~\cite{YJP12}
+(many of them are also included in a book:~\cite{DKZ12}
+-- Section 13.8), thus we do not include them in our work.
+
+\subsection{Executable Source Code Injection}
+
+Code injection also includes the use of source code, either of a
+Domain Specific Language ({\sc dsl})
+or a Dynamic Language. Note that binary code injection
+attacks can only occur when the target system is implemented in
+languages lacking array bounds checking, like
+{\sc c} and {\sc c}++. Contrariwise, source code-driven
+injection attacks can target applications written in various
+programming languages with different features and characteristics.
+
+Application attacks that involve {\sc dsl}s,
+constitute an important subset of the code injection problem,
+as {\sc dsl}s like {\sc sql} and {\sc xml} play an
+significant role in the development of either web or mobile
+applications. For example, many applications have interfaces
+where a user enters input to interact with the
+application's data, thereby interacting with the
+underlying {\it Relational Database Management System}
+({\sc rdbms}).
+This input can become part of an
+{\sc sql} query and executed on the target {\sc rdbms}.
+A code injection attack that exploits the vulnerabilities of these
+interfaces by taking advantage of input validation issues like
+incorrectly passed parameters or incorrect type handling,
+is called an ``{\sc sql} injection
+attack''~\cite{CERT02,MS09,HVO06,SW06}.
+By using similar techniques malicious users
+can perform other exploits based on {\sc dsl}s,
+like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and
+{\sc xml}~\cite{MSM13} injection attacks.
+
+A recent class of {\sc cia}s involve
+dynamic languages like Python, Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
+In particular, JavaScript injection attacks comprise a wide subset of dynamic
+language-driven attacks. Such attacks are manifested when a web application
+accepts and redisplays data of uncertain origin without appropriate validation
+and filtering. Based on this flaw, an attacker can
+manage to inject a script in the JavaScript engine of a browser and alter its
+execution flow~\cite{ELX07}. JavaScript injection attacks are considered as a
+critical issue in web application security mainly because they are
+associated with major vulnerabilities such as:
+{\sc xss} attacks~\cite{SG07},
+{\sc csrf} attacks~\cite{LZRL09}
+and ``Cross-Channel Scripting"
+({\sc xcs}) attacks~\cite{W10,BBB09}.
+
+\section{Defenses for Detecting Web Application Attacks}
+
+There are four main defensive approaches to counter
+web application attacks, namely: {\it tainting},
+{\it instruction set randomization} ({{\sc isr}}),
+{\it policy enforcement} and {\it training}.
 

### 2014-10-07 docs/questioning.tex
better requirements

@@
 \textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
-\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 - \textrm{PR})}
+\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 -
+\textrm{PR})}
+\label{eq:ppv-se-sp}
 \end{equation}
@@
 \textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
-(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 - \textrm{PR})}
+(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 -
+\textrm{PR})}
+\label{eq:npv-se-sp}
 \end{equation}
@@
 \begin{itemize}
-\item Reporting of values for True Positives ($a$), False Positives
-  ($b$), False Negatives ($c$), True Negatives ($d$), on test
-  environments.
-\item Reporting of values for True Positives ($A$), False Positives
-  ($B$), False Negatives ($C$), True Negatives ($D$), on the
-  performance of the mechanism on environments with real attack
-  profiles.
+\item \textbf{Sensitivity, Specificity}: Reporting of values for True
+  Positives ($a$), False Positives ($b$), False Negatives ($c$), True
+  Negatives ($d$), on test environments.
+\item \textbf{\textsc{ppv}, \textsc{npv}}: Reporting of values for True
+  Positives ($A$), False Positives ($B$), False Negatives ($C$), True
+  Negatives ($D$), on the performance of the mechanism on environments
+  with real attack profiles. Alternatively, since from
+  equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} \textsc{ppv}
+  and \textsc{npv} can be calculated by the sensitity and specifity
+  given the prevalence, reporting of prevalance, sensitivity,
+  specificity.
 \end{itemize}

### 2014-10-08 docs/questioning.tex
minor change

@@
 	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection \\
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
 	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss}, Buffer Overflows \\ 
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss} \\ 
     &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\

### 2014-10-08 docs/questioning.tex
minor fixes
minor typo

@@
 the absence of input validation. By taking advantage of
-this, attackers can inject either code into
+this, attackers can inject their code into
 applications to perform malicious tasks. Such
@@
   & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 20,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\

### 2014-10-09 docs/questioning.tex
correction
new subcategory and entry

@@
 ({\sc xcs}) attacks~\cite{W10,BBB09}.
+
+% {\sc html} injection --- such attacks pose no threat to cookies and session IDs.
 
@@
     \hline
-	\multirow{9}{*}{Runtime Tainting}
+	\multirow{8}{*}{Runtime Tainting}
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
@@
 	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
-	&   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (15,{\sc nq},{\sc nq},{\sc nq})\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
 	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
@@
   \hline
+  \multirow{3}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+	\hline
+	\hline    
 	\multirow{12}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
 	&   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
@@
 	\hline  
-        \multirow{11}{*}{Training}
+        \multirow{10}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
@@
 	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
 	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\

### 2014-10-10 docs/questioning.tex
minor changes

@@
 \IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
-Panos Louridas,\IEEEauthorrefmark{2} and Angelos Keromytis\IEEEauthorrefmark{1}}
+Panos Louridas,\IEEEauthorrefmark{2},
+Michalis Polychronakis,\IEEEauthorrefmark{1}
+and Angelos Keromytis\IEEEauthorrefmark{1}}
 \IEEEauthorblockA{\IEEEauthorrefmark{1}
@@
   \hline
-  \multirow{3}{*}{Parse-Tree Validation}
+  \multirow{2}{*}{Parse-Tree Validation}
   &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
   &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
 	\hline
 	\hline   
-	\multirow{12}{*}{Policy Enforcement}
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
+  \multirow{3}{*}{Code Rewriting}
   &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
   &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
+  \hline
+  \hline 
+	\multirow{10}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
 	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
@@
 	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
-	&   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
 	&   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\ 
@@
     \hline
-	\multirow{9}{*}{Runtime Tainting}
+	\multirow{8}{*}{Runtime Tainting}
 	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
 	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
@@
 	\hline
-	\multirow{12}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
+  \hline  
+  \hline 
+  \hline
+  \multirow{3}{*}{Code Rewriting}
   &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
   &   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
+  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
+  \hline 
+	\multirow{10}{*}{Policy Enforcement}
+	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
 	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	&   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
 	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	\hline  
-        \multirow{11}{*}{Training}
+        \multirow{10}{*}{Training}
     &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	& 	{\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
 	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\

### 2014-10-10 docs/questioning.tex
new category and entry
another entry

@@
   \hline 
-	\multirow{10}{*}{Policy Enforcement}
+  \multirow{5}{*}{Securing Mashups}
+  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
+  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
+  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+  \hline
+  \hline 
+	\multirow{7}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
@@
 	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
-	&   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\ 
-	&   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
 	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
-  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
   % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
@@
   \hline
-	\multirow{10}{*}{Policy Enforcement}
+  \hline 
+  \multirow{5}{*}{Securing Mashups}
+  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline
+	\multirow{7}{*}{Policy Enforcement}
 	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	&   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
 	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
-    &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
    	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\

### 2014-10-12 docs/questioning.tex
minor change
initial figure with the attack model(s)

@@
 like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and
-{\sc xml}~\cite{MSM13} injection attacks.
+{\sc xml}~\cite{MSM13}.
 
@@
 % {\sc html} injection --- such attacks pose no threat to cookies and session IDs.
+
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.57]{attacks-steps.pdf}
+\end{center}
+\caption{\label{fig:taxonomy}Attack model demonstrating web
+application attacks that involve code injection.}
+\end{figure*}
 
@@
     \hline
-	\multirow{8}{*}{Runtime Tainting}
+	\multirow{9}{*}{Runtime Tainting}
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
@@
 	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
+  &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
 	\hline  
-  \multirow{10}{*}{Training}
+  \multirow{9}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
@@
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-	& 	{\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
     \hline
-	\multirow{8}{*}{Runtime Tainting}
+	\multirow{9}{*}{Runtime Tainting}
 	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline
@@
 	\hline  
-        \multirow{10}{*}{Training}
+        \multirow{9}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	& 	{\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline

### 2014-10-12 docs/questioning.tex
defense categorisation

@@
 \begin{abstract}
-In this paper we examine how application attack defense
-mechanism are developed and presented to
-the research community.
+Web application attacks, can have different forms depending on the
+execution context of the application and the location
+of the programming flaw that leads to the attack.
+Some of the most dangerous web application attacks,
+like Cross-Site Scripting and {\sc sql} injection,
+involve the exploitation of the following weakness:
+programmers tend to develop applications that may
+accept and process data of uncertain origin without
+appropriate validation and / or filtering.
+Such attacks have been constantly topping the lists
+of the various security bulletin providers despite
+the numerous countermeasures that have been proposed
+over the past 15 years.
+
+%In this paper we examine how application attack defense
+%mechanism are developed and presented to
+%the research community.
 \end{abstract}
@@
 \section{Introduction}
+
+% Notes
+The attacks we examine include
+{\sc sql} injection
+attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
+attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
+attacks~\cite{LZRL09} and others.
+Such attacks top the vulnerability lists of numerous bulletin providers for several
+years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
+Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
+(Open Web Application Security Project)
+Top Ten project whose main goal is to raise awareness about
+web application security by identifying some of the most critical risks facing
+organizations which is referenced by numerous researchers.
+In its three consecutive Top Ten lists (2007, 2010, 2013), different
+source code-driven injection attacks dominate the top five positions.
+This indicates that
+apart from the fact that malicious users find new ways to bypass
+defense mechanisms by using a variety of techniques despite the numerous
+countermeasures that are being introduced.
+Note that the number of systems developed to counter {\sc sql}
+injection attacks until 2006 was more than twenty~\cite{HVO06}.
+Since then the number has doubled.
+In our research we focus on the top {\sc tba} systems that counter
+application attacks, in terms of citations.
+% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
 
@@
 
-The basic problem behind web application attacks involves
+The basic problem behind the most dangerous
+web application attacks involves
 the absence of input validation. By taking advantage of
@@
 \caption{\label{fig:taxonomy}Attack model demonstrating web
-application attacks that involve code injection.}
+application attacks that involve code injection ({\sc draft}).}
 \end{figure*}
@@
 {\it policy enforcement} and {\it training}.
+
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.57]{defenses.pdf}
+\end{center}
+\caption{\label{fig:taxonomy}The basic categories of web application
+attack countermeasures ({\sc draft}).}
+\end{figure*}
 
@@
 \end{itemize}
-
-\section{Covered Area}
-
-We decided to narrow down our
-research to countermeasures developed to
-detect attacks that target applications. Such attacks include
-buffer overflow attacks~\cite{K11}, {\sc sql} injection
-attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
-attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
-attacks~\cite{LZRL09} and others.
-Such attacks top the vulnerability lists of numerous bulletin providers for several
-years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
-Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-(Open Web Application Security Project)
-Top Ten project whose main goal is to raise awareness about
-web application security by identifying some of the most critical risks facing
-organizations which is referenced by numerous researchers.
-In its three consecutive Top Ten lists (2007, 2010, 2013), different
-source code-driven injection attacks dominate the top five positions.
-This indicates that
-apart from the fact that malicious users find new ways to bypass
-defense mechanisms by using a variety of techniques despite the numerous
-countermeasures that are being introduced.
-Note that the number of systems developed to counter {\sc sql}
-injection attacks until 2006 was more than twenty~\cite{HVO06}.
-Since then the number has doubled.
-In our research we focus on the top {\sc tba} systems that counter
-application attacks, in terms of citations.
-% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
 

### 2014-10-22 docs/questioning.tex
started describing defences

@@
 
-\title{SoK: Web Application Attack Defenses (in Question)}
+\title{SoK: The Evolution of Web Application Attack Defenses}
 
@@
 
-\section{Introduction}
+\section{Introduction Remarks}
 
@@
 
-\section{Attacks}
+\section{Attacks and Background}
 \label{sec:attacks}
@@
 \end{center}
-\caption{\label{fig:taxonomy}Attack model demonstrating web
+\caption{\label{fig:attacks}Attack model demonstrating web
 application attacks that involve code injection ({\sc draft}).}
@@
 
-\section{Defenses for Detecting Web Application Attacks}
+\section{Web Application Attacks Defenses}
+\label{sec:defs}
 
-There are four main defensive approaches to counter
-web application attacks, namely: {\it tainting},
-{\it instruction set randomization} ({{\sc isr}}),
-{\it policy enforcement} and {\it training}.
+Figure~\ref{fig:defenses} presents a taxonomy of the
+approaches that counter web application attacks based on
+code injection vulnerabilities.
+We can identify two main approaches, namely:
+{\it protection} and {\it detection}.
+The former involves mechanisms that make applications
+immune to different attack vectors by design~\cite{JL75,L81}.
+The latter incorporates a variety of methods and
+schemes that inspect the behavior of applications
+and detect attacks based on specific criteria~\cite{D76,A00}.
+
+\subsection{Protection}
+\label{sec:prot}
+
+Here we analyze the three different protection approaches.
+
+\subsubsection{Parse-Tree Validation}
+
+\subsubsection{Securing Mashups}
+
+\subsubsection{Instruction Set Randomization --- ISR}
+
+{\sc isr} is a method that contrary to the previous
+two approaches, has been applied to counter
+different kinds of application attacks~\cite{K09b,KKP03}.
+
+\subsection{Detection}
+
+% {\it tainting},
+% {\it instruction set randomization} ({{\sc isr}}),
+% {\it policy enforcement} and {\it training}.
 
@@
 \end{center}
-\caption{\label{fig:taxonomy}The basic categories of web application
+\caption{\label{fig:defenses}The basic categories of web application
 attack countermeasures ({\sc draft}).}
@@
     \hline
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
+  \hline
+  \hline
+  \multirow{5}{*}{Securing Mashups}
+  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
+  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
+  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+  \hline
+  \hline
+  \multirow{3}{*}{{\sc isr}}
+  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
+  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
+  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
+  \hline
+  \hline
+  \hline
+  \hline
 	\multirow{9}{*}{Runtime Tainting}
@@
 	\hline         
-	\multirow{3}{*}{{\sc isr}}
-	&   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
-	&   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
-  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
-  \hline
-  \hline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
-	\hline
-	\hline   
   \multirow{3}{*}{Code Rewriting}
@@
   &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
-  \hline
-  \hline 
-  \multirow{5}{*}{Securing Mashups}
-  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
-  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
-  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
   \hline

### 2014-10-22 docs/questioning.tex
describing ISR and implementations

@@
 {\sc isr} is a method that contrary to the previous
-two approaches, has been applied to counter
+two, has been applied to counter
 different kinds of application attacks~\cite{K09b,KKP03}.
+The main idea behind the method, is to
+separate code from data by randomizing the legitimate code's 
+execution environment. In this way, the malicious code
+injected by the attackers who do not know the randomization
+algorithm, will not get executed.
+
+{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
+to detect {\sc sql} injections in the following manner:
+initially, it allows programmers to create {\sc sql} statements
+using randomized instructions instead of standard keywords.
+The modified queries are either reconstructed at runtime using
+the same key that is inaccessible to the malicious user,
+or the user input is tagged with delimiters that allow
+an augmented {\sc sql} grammar to detect the
+attack.
+
+In the case of {\sc xss} attacks that are based on JavaScript,
+consider a {\sc xor} function that encodes all JavaScript source of a web
+page on the server-side and then, on the client-side, the web browser decodes the
+source by applying the same function again.
+Variations of this approach include:
+{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
 

### 2014-10-22 docs/questioning.tex
adding more material especially for training methods

@@
 Columbia University\\
-\{dimitro, angelos\}@cs.columbia.edu\\
+\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
 \IEEEauthorrefmark{2}
@@
 
-% {\it tainting},
-% {\it instruction set randomization} ({{\sc isr}}),
-% {\it policy enforcement} and {\it training}.
+\subsubsection{Runtime Tainting}
+
+Runtime tainting is based on data-flow analysis.
+In practice, it enforces security policies by marking untrusted
+(``tainted") data and tracing its flow through the program.
+Since information flow in a system cannot be verified by examining
+a single execution trace of the system, the results of taint
+analysis will necessarily reflect approximate information regarding
+the information flow characteristics of the system to which it is applied.
+
+\subsubsection{Policy Enforcement}
+
+In this method, developers must define
+specific security policies on the server side.
+Then the policies are enforced either in the user's
+browser at runtime or in a server-side proxy that
+intercepts server responses.
+
+\subsubsection{Code Rewriting}
+
+\subsubsection{Training}
+
+Training techniques are based on the ideas of Denning's original
+intrusion detection framework~\cite{Den87}.
+In particular, a training mechanism,
+registers all valid legitimate code statements
+during a training phase, most of the time in the form of signatures.
+This can be done in various ways according to the implementation.
+Then, only those will be accepted, approved or recognized during
+production.
+
+Training methods that detect JavaScript-driven {\sc xss} attacks
+generate and store valid JavaScript code in various
+forms, and detect attacks as outliers from the set of valid code statements.
+{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
+original application. Then, a JavaScript detection component placed in a web proxy
+searches for injected scripts in the server's responses. If no injected scripts
+are found, the proxy decodes the legitimate scripts and sends them to the
+client.
+% dimitro: more mechanisms TBA.
+
+In the case of {\sc dsl}-driven injection attacks
+the various countermeasures follow a similar pattern.
+An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
+{\sc sql} injection attacks by recording all database transactions.
+Subsequent refinements by Valeur et al.~\cite{VMV05}
+tagged each transaction with the corresponding application
+as an extension of their anomaly detection framework called
+{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
+Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
+injection attacks by associating a query model with the location of every
+{\sc sql} statement within the application. Then at runtime,
+monitors the application's execution to detect when {\sc sql} statements
+diverge from the expected model.
+{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
+mechanism that prevents
+{\sc sql} and {\sc xp}ath injection attacks against web applications. 
+The signatures generated during a training phase,
+are based on features that can depend either on the
+code statement or on its execution environment (i.e. the stack trace).
+Then, at runtime, the mechanism checks all statements for compliance
+and can block code statements containing injected elements.
+By associating a complete stack trace with the root of an {\sc sql} statement, 
+the mechanism can correlate {\sc sql} statements with their call sites.  
+This increases the specificity of the stored signatures and 
+avoids false alarms. 
+% dimitro: more mechanisms TBA.
 

### 2014-10-23 docs/questioning.tex
abstract draft, some rearrangements

@@
 
+In this paper we first systematize the existing knowledge
+regarding the various defense mechanisms by setting up
+a model for application attacks that are based on
+source code injection vulnerabilities. This model
+highlights the key weakness behind such attacks
+and helps us observe defenses from a common
+perspective.
+
+We then categorize and analyze the various
+defense mechanisms that have been developed.
+Our analysis is based on dimensions such as accuracy,
+performance, deployment and security.
+Especially notable for a key category is accuracy,
+as our findings show that there are many
+defense mechanisms that are tested in a poor manner.
+
+By comparing the existing defenses and identifying their
+common characteristics, we help: a) researchers
+and practitioners to choose or modify a mechanism
+according to their needs, and b) designers of
+new approaches in developing more efficient mechanisms.
+% @dimitro: change the above accordingly.
+
 %In this paper we examine how application attack defense
@@
 \begin{IEEEkeywords}
-Security and Protection, Application Security, Code injection Attacks, Cyber Security Experiments, Effectivenes, Efficiency.
+Security and Protection, Application Security, Code injection Attacks.
 \end{IEEEkeywords}
@@
 
-\section{Attacks and Background}
+\section{Background}
 \label{sec:attacks}
@@
 
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.57]{attacks-steps.pdf}
-\end{center}
-\caption{\label{fig:attacks}Attack model demonstrating web
-application attacks that involve code injection ({\sc draft}).}
-\end{figure*}
-
-\section{Web Application Attacks Defenses}
-\label{sec:defs}
-
-Figure~\ref{fig:defenses} presents a taxonomy of the
-approaches that counter web application attacks based on
-code injection vulnerabilities.
-We can identify two main approaches, namely:
-{\it protection} and {\it detection}.
-The former involves mechanisms that make applications
-immune to different attack vectors by design~\cite{JL75,L81}.
-The latter incorporates a variety of methods and
-schemes that inspect the behavior of applications
-and detect attacks based on specific criteria~\cite{D76,A00}.
-
-\subsection{Protection}
-\label{sec:prot}
-
-Here we analyze the three different protection approaches.
-
-\subsubsection{Parse-Tree Validation}
-
-\subsubsection{Securing Mashups}
-
-\subsubsection{Instruction Set Randomization --- ISR}
-
-{\sc isr} is a method that contrary to the previous
-two, has been applied to counter
-different kinds of application attacks~\cite{K09b,KKP03}.
-The main idea behind the method, is to
-separate code from data by randomizing the legitimate code's 
-execution environment. In this way, the malicious code
-injected by the attackers who do not know the randomization
-algorithm, will not get executed.
-
-{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
-to detect {\sc sql} injections in the following manner:
-initially, it allows programmers to create {\sc sql} statements
-using randomized instructions instead of standard keywords.
-The modified queries are either reconstructed at runtime using
-the same key that is inaccessible to the malicious user,
-or the user input is tagged with delimiters that allow
-an augmented {\sc sql} grammar to detect the
-attack.
-
-In the case of {\sc xss} attacks that are based on JavaScript,
-consider a {\sc xor} function that encodes all JavaScript source of a web
-page on the server-side and then, on the client-side, the web browser decodes the
-source by applying the same function again.
-Variations of this approach include:
-{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
-
-\subsection{Detection}
-
-\subsubsection{Runtime Tainting}
-
-Runtime tainting is based on data-flow analysis.
-In practice, it enforces security policies by marking untrusted
-(``tainted") data and tracing its flow through the program.
-Since information flow in a system cannot be verified by examining
-a single execution trace of the system, the results of taint
-analysis will necessarily reflect approximate information regarding
-the information flow characteristics of the system to which it is applied.
-
-\subsubsection{Policy Enforcement}
-
-In this method, developers must define
-specific security policies on the server side.
-Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that
-intercepts server responses.
-
-\subsubsection{Code Rewriting}
-
-\subsubsection{Training}
-
-Training techniques are based on the ideas of Denning's original
-intrusion detection framework~\cite{Den87}.
-In particular, a training mechanism,
-registers all valid legitimate code statements
-during a training phase, most of the time in the form of signatures.
-This can be done in various ways according to the implementation.
-Then, only those will be accepted, approved or recognized during
-production.
-
-Training methods that detect JavaScript-driven {\sc xss} attacks
-generate and store valid JavaScript code in various
-forms, and detect attacks as outliers from the set of valid code statements.
-{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
-original application. Then, a JavaScript detection component placed in a web proxy
-searches for injected scripts in the server's responses. If no injected scripts
-are found, the proxy decodes the legitimate scripts and sends them to the
-client.
-% dimitro: more mechanisms TBA.
-
-In the case of {\sc dsl}-driven injection attacks
-the various countermeasures follow a similar pattern.
-An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
-{\sc sql} injection attacks by recording all database transactions.
-Subsequent refinements by Valeur et al.~\cite{VMV05}
-tagged each transaction with the corresponding application
-as an extension of their anomaly detection framework called
-{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
-Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
-injection attacks by associating a query model with the location of every
-{\sc sql} statement within the application. Then at runtime,
-monitors the application's execution to detect when {\sc sql} statements
-diverge from the expected model.
-{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
-mechanism that prevents
-{\sc sql} and {\sc xp}ath injection attacks against web applications. 
-The signatures generated during a training phase,
-are based on features that can depend either on the
-code statement or on its execution environment (i.e. the stack trace).
-Then, at runtime, the mechanism checks all statements for compliance
-and can block code statements containing injected elements.
-By associating a complete stack trace with the root of an {\sc sql} statement, 
-the mechanism can correlate {\sc sql} statements with their call sites.  
-This increases the specificity of the stored signatures and 
-avoids false alarms. 
-% dimitro: more mechanisms TBA.
-
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.57]{defenses.pdf}
-\end{center}
-\caption{\label{fig:defenses}The basic categories of web application
-attack countermeasures ({\sc draft}).}
-\end{figure*}
-
-\section{Methodological Background}
+\section{Dimensions of Study}
 
@@
 
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.53]{attacks-steps.pdf}
+\end{center}
+\caption{\label{fig:attacks}Attack model demonstrating web
+application attacks based on code injection vulnerabilities
+({\sc draft}).}
+\end{figure*}
+
+\section{Web Application Attacks Defenses}
+\label{sec:defs}
+
+Figure~\ref{fig:defenses} presents a taxonomy of the
+approaches that counter web application attacks based on
+code injection vulnerabilities.
+We can identify two main approaches, namely:
+{\it protection} and {\it detection}.
+The former involves mechanisms that make applications
+immune to different attack vectors by design~\cite{JL75,L81}.
+The latter incorporates a variety of methods and
+schemes that inspect the behavior of applications
+and detect attacks based on specific criteria~\cite{D76,A00}.
+
+\subsection{Protection}
+\label{sec:prot}
+
+Here we analyze the three different protection approaches.
+
+\subsubsection{Parse-Tree Validation}
+
+The mechanism based on this method compare the parse tree of a
+query before the inclusion of user input with the one resulting after
+the inclusion of user input. If the trees diverge, the application
+is probably under attack.
+
+\subsubsection{Securing Mashups}
+
+\subsubsection{Instruction Set Randomization --- ISR}
+
+{\sc isr} is a method that contrary to the previous
+two, has been applied to counter
+different kinds of application attacks~\cite{K09b,KKP03}.
+The main idea behind the method, is to
+separate code from data by randomizing the legitimate code's 
+execution environment. In this way, the malicious code
+injected by the attackers who do not know the randomization
+algorithm, will not get executed.
+
+{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
+to detect {\sc sql} injections in the following manner:
+initially, it allows programmers to create {\sc sql} statements
+using randomized instructions instead of standard keywords.
+The modified queries are either reconstructed at runtime using
+the same key that is inaccessible to the malicious user,
+or the user input is tagged with delimiters that allow
+an augmented {\sc sql} grammar to detect the
+attack.
+
+In the case of {\sc xss} attacks that are based on JavaScript,
+consider a {\sc xor} function that encodes all JavaScript source of a web
+page on the server-side and then, on the client-side, the web browser decodes the
+source by applying the same function again.
+Variations of this approach include:
+{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
+
+\subsection{Detection}
+
+\subsubsection{Runtime Tainting}
+
+Runtime tainting is based on data-flow analysis.
+In practice, it enforces security policies by marking untrusted
+(``tainted") data and tracing its flow through the program.
+Since information flow in a system cannot be verified by examining
+a single execution trace of the system, the results of taint
+analysis will necessarily reflect approximate information regarding
+the information flow characteristics of the system to which it is applied.
+
+\subsubsection{Policy Enforcement}
+
+In this method, developers must define
+specific security policies on the server side.
+Then the policies are enforced either in the user's
+browser at runtime or in a server-side proxy that
+intercepts server responses.
+
+\subsubsection{Code Rewriting}
+
+\subsubsection{Training}
+
+Training techniques are based on the ideas of Denning's original
+intrusion detection framework~\cite{Den87}.
+In particular, a training mechanism,
+registers all valid legitimate code statements
+during a training phase, most of the time in the form of signatures.
+This can be done in various ways according to the implementation.
+Then, only those will be accepted, approved or recognized during
+production.
+
+Training methods that detect JavaScript-driven {\sc xss} attacks
+generate and store valid JavaScript code in various
+forms, and detect attacks as outliers from the set of valid code statements.
+{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
+original application. Then, a JavaScript detection component placed in a web proxy
+searches for injected scripts in the server's responses. If no injected scripts
+are found, the proxy decodes the legitimate scripts and sends them to the
+client.
+% dimitro: more mechanisms TBA.
+
+In the case of {\sc dsl}-driven injection attacks
+the various countermeasures follow a similar pattern.
+An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
+{\sc sql} injection attacks by recording all database transactions.
+Subsequent refinements by Valeur et al.~\cite{VMV05}
+tagged each transaction with the corresponding application
+as an extension of their anomaly detection framework called
+{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
+Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
+injection attacks by associating a query model with the location of every
+{\sc sql} statement within the application. Then at runtime,
+monitors the application's execution to detect when {\sc sql} statements
+diverge from the expected model.
+{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
+mechanism that prevents
+{\sc sql} and {\sc xp}ath injection attacks against web applications. 
+The signatures generated during a training phase,
+are based on features that can depend either on the
+code statement or on its execution environment (i.e. the stack trace).
+Then, at runtime, the mechanism checks all statements for compliance
+and can block code statements containing injected elements.
+By associating a complete stack trace with the root of an {\sc sql} statement, 
+the mechanism can correlate {\sc sql} statements with their call sites.  
+This increases the specificity of the stored signatures and 
+avoids false alarms. 
+% dimitro: more mechanisms TBA.
+
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.57]{defenses.pdf}
+\end{center}
+\caption{\label{fig:defenses}The basic categories of web application
+attack countermeasures ({\sc draft}).}
+\end{figure*}
+
 \begin{landscape}
 \begin{table}
-%\tbl{Performance of System Prototype. Time is Measured in $\mu$s.}{
 \centering

### 2014-10-23 docs/questioning.tex
first steps in introduction

@@
 
-% Notes
-The attacks we examine include
-{\sc sql} injection
-attacks~\cite{RL12b}, cross-site scripting ({\sc xss})
-attacks~\cite{SG07}, cross-site request forgery ({\sc csrf})
-attacks~\cite{LZRL09} and others.
-Such attacks top the vulnerability lists of numerous bulletin providers for several
-years.\footnote{\url{http://www.sans.org/top-cyber-security-risks/}, \url{http://cwe.mitre.org/top25/}}
-Consider the {\sc owasp}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-(Open Web Application Security Project)
-Top Ten project whose main goal is to raise awareness about
-web application security by identifying some of the most critical risks facing
-organizations which is referenced by numerous researchers.
-In its three consecutive Top Ten lists (2007, 2010, 2013), different
-source code-driven injection attacks dominate the top five positions.
-This indicates that
-apart from the fact that malicious users find new ways to bypass
-defense mechanisms by using a variety of techniques despite the numerous
+Web application attacks may involve security misconfigurations,
+broken authentication and session management, and other issues.
+Some of the most dangerous web application attacks though
+are associated with the processing of external input data
+that may contain malicious code, a vulnerability known as
+code injection.
+
+Such attacks include Cross-Site Scripting ({\sc xss})
+attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
+Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}
+and others. Attacks like these top the vulnerability
+lists of numerous bulletin providers like
+the Open Web Application Security
+Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
+({\sc owasp}) and {\sc mitre}\footnote{\url{http://cwe.mitre.org/top25/}}
+for several years. Consider the case of {\sc owasp}'s Top
+Ten project whose main goal is to raise awareness about
+web application security by identifying some of the most
+critical risks facing organizations which is referenced by
+numerous researchers. In its three consecutive Top Ten lists
+(2007, 2010, 2013), different source code-driven injection attacks
+dominate the top five positions. This indicates that apart from
+the fact that malicious users find new ways to bypass defense
+mechanisms by using a variety of techniques despite the numerous
 countermeasures that are being introduced.

### 2014-10-23 docs/questioning.tex
reshaping section 2

@@
 
-\title{SoK: The Evolution of Web Application Attack Defenses}
+\title{SoK: The Evolution of Defenses Against Web Application Attacks}
 
@@
 a model for application attacks that are based on
-source code injection vulnerabilities. This model
+executable source code injection vulnerabilities. This model
 highlights the key weakness behind such attacks
@@
 numerous researchers. In its three consecutive Top Ten lists
-(2007, 2010, 2013), different source code-driven injection attacks
-dominate the top five positions. This indicates that apart from
-the fact that malicious users find new ways to bypass defense
+(2007, 2010, 2013), different executable source code-driven
+injection attacks dominate the top five positions.
+This indicates that apart from the fact that malicious
+users find new ways to bypass defense
 mechanisms by using a variety of techniques despite the numerous
@@
 
-\section{Background}
+\section{Attacks}
 \label{sec:attacks}
@@
 \leavevmode
-\includegraphics[scale=0.37]{attack-tree-uml.pdf}
+\includegraphics[scale=0.47]{attack-tree-uml.pdf}
 \end{center}
-\caption{\label{fig:taxonomy}A taxonomy of code injection attacks.
-In our research we have excluded the defenses that deal with
-the subcategories that are illustrated in grey color.}
+\caption{\label{fig:taxonomy}A taxonomy of executable source
+code injection attacks.}
 \end{figure}
 
-Figure \ref{fig:taxonomy} presents a taxonomy of code injection attacks divided
-into two categories. The first involves binary code and the second
-executable source code.
-
-\subsection{Binary Code Injection}
-
-Binary code injection attacks involve
-the insertion of binary code into an application
-to alter its execution flow and execute malicious
-compiled code. This category involves buffer-overflow
-attacks~\cite{CPMHWBBGWZ98,K11}, a staple of security problems.
+Code injection attacks can be divided into two categories.
+The first involves binary code and the second executable source code.
 An extensive survey on binary code
@@
 -- Section 13.8), thus we do not include them in our work.
+In this paper, we focus on the defenses that protect
+applications against application attacks based on
+the executable source code injection category.
 
@@
 
-Code injection also includes the use of source code, either of a
+Figure~\ref{fig:taxonomy} presents a taxonomy of executable source
+code injection attacks. Such attacks may involve source code, either of a
 Domain Specific Language ({\sc dsl})
@@
 incorrectly passed parameters or incorrect type handling,
-is called an ``{\sc sql} injection
-attack''~\cite{CERT02,MS09,HVO06,SW06}.
+is called an {\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}.
 By using similar techniques malicious users
 can perform other exploits based on {\sc dsl}s,
-like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and
-{\sc xml}~\cite{MSM13}.
+like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}.
+With this kind of attacks, a malicious user can view sensitive
+information, destroy or modify protected data, or even crash the entire
+application.
 
@@
 dynamic languages like Python, Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
-In particular, JavaScript injection attacks comprise a wide subset of dynamic
+JavaScript injection attacks in particular, comprise a wide subset of dynamic
 language-driven attacks. Such attacks are manifested when a web application
@@
 {\sc csrf} attacks~\cite{LZRL09}
-and ``Cross-Channel Scripting"
+and Cross-Channel Scripting
 ({\sc xcs}) attacks~\cite{W10,BBB09}.
@@
 % {\sc html} injection --- such attacks pose no threat to cookies and session IDs.
+
+\subsection{Exploitation Model}
+
+In this section we provide a step-by-step exploitation
+model
+
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.55]{attacks-steps.pdf}
+\end{center}
+\caption{\label{fig:attacks}Attack model demonstrating web
+application attacks based on executable source
+code injection vulnerabilities ({\sc draft}).}
+\end{figure*}
 
@@
 \end{itemize}
-
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.53]{attacks-steps.pdf}
-\end{center}
-\caption{\label{fig:attacks}Attack model demonstrating web
-application attacks based on code injection vulnerabilities
-({\sc draft}).}
-\end{figure*}
 

### 2014-10-23 docs/questioning.tex
more on section 2

@@
 
-\subsection{Executable Source Code Injection}
+\subsection{Executable Source Code Injection Vulnerabilities}
 
@@
 In this section we provide a step-by-step exploitation
-model
+model to understand the process of carrying out
+application attacks based on executable source code injection
+vulnerabilities. Figure~\ref{fig:attacks} presents the steps
+of different application attacks. For the most part,
+the steps are common for each attack. This is because
+they are based on similar attack vectors as we described in
+the previous section. We base the analysis of the
+existing defenses on this model. Figure~\ref{fig:attacks} also
+illustrates in which step the defenses detect corresponding
+attacks ({\sc todo}).
+
+An attack starts with the malicious user sending an
+request either to the server or to a web user.
+In the first case the attacker
+could upload data containing a specially crafted script
+(in a blog comment) or create a request with
+additional {\sc sql} code.
 

### 2014-10-24 docs/questioning.tex
changes in Section 4

@@
 Figure~\ref{fig:defenses} presents a taxonomy of the
-approaches that counter web application attacks based on
+approaches that protect web applications against attacks based on
 code injection vulnerabilities.
 We can identify two main approaches, namely:
-{\it protection} and {\it detection}.
+{\it design-based} and {\it behavior-based}.
 The former involves mechanisms that make applications
@@
 
-\subsection{Protection}
+\subsection{Design-Based}
 \label{sec:prot}
@@
 
+\subsubsection{Code Rewriting}
+
 \subsubsection{Instruction Set Randomization --- ISR}
@@
 {\sc isr} is a method that contrary to the previous
-two, has been applied to counter
+three, has been applied to counter
 different kinds of application attacks~\cite{K09b,KKP03}.
@@
 
-\subsection{Detection}
+\subsection{Behavior-Based}
 
@@
 intercepts server responses.
-
-\subsubsection{Code Rewriting}
 
@@
   \hline         
+  \multirow{3}{*}{Code Rewriting}
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
   \hline
   \hline
-	\multirow{9}{*}{Runtime Tainting}
+  \hline
+  \hline
+	\multirow{8}{*}{Runtime Tainting}
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
@@
   &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
-	\hline
-	\hline         
-  \multirow{3}{*}{Code Rewriting}
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
   \hline

### 2014-10-24 docs/questioning.tex
ammendments in first two sections

@@
 \begin{abstract}
-Web application attacks, can have different forms depending on the
-execution context of the application and the location
-of the programming flaw that leads to the attack.
-Some of the most dangerous web application attacks,
-like Cross-Site Scripting and {\sc sql} injection,
-involve the exploitation of the following weakness:
-programmers tend to develop applications that may
-accept and process data of uncertain origin without
-appropriate validation and / or filtering.
-Such attacks have been constantly topping the lists
-of the various security bulletin providers despite
-the numerous countermeasures that have been proposed
-over the past 15 years.
 
-In this paper we first systematize the existing knowledge
-regarding the various defense mechanisms by setting up
-a model for application attacks that are based on
-executable source code injection vulnerabilities. This model
-highlights the key weakness behind such attacks
-and helps us observe defenses from a common
-perspective.
+  Some of the most dangerous web application attacks, like Cross-Site
+  Scripting and {\sc sql} injection, exploit the oversight of
+  programmers that develop applications which may accept and process
+  data of uncertain origin without appropriate validation and / or
+  filtering. Such attacks, relying on source code injection
+  vulnerabilities, have been constantly topping the lists of the
+  various security bulletin providers despite the numerous
+  countermeasures that have been proposed over the past 15 years.
 
-We then categorize and analyze the various
-defense mechanisms that have been developed.
-Our analysis is based on dimensions such as accuracy,
-performance, deployment and security.
-Especially notable for a key category is accuracy,
-as our findings show that there are many
-defense mechanisms that are tested in a poor manner.
+  In this paper we systematize the existing knowledge regarding
+  various defense mechanisms against source code injection by setting
+  up a model that highlights the key weaknesses behind such attacks and
+  helps us observe defenses from a common perspective.
 
-By comparing the existing defenses and identifying their
-common characteristics, we help: a) researchers
-and practitioners to choose or modify a mechanism
-according to their needs, and b) designers of
+  We then categorize and analyze the various defense mechanisms that
+  have been developed. Our analysis is based on dimensions such as
+  accuracy, performance, deployment and security. Especially notable
+  for a key category is accuracy, as our findings show that there are
+  many defense mechanisms that are tested in a poor manner.
+
+  By comparing the existing defenses and identifying their common
+  characteristics, we help: a) researchers and practitioners to choose
+  or modify a mechanism according to their needs, and b) designers of
   new approaches in developing more efficient mechanisms.
@@
 Web application attacks may involve security misconfigurations,
-broken authentication and session management, and other issues.
-Some of the most dangerous web application attacks though
+broken authentication and session management, or other issues.
+Some of the most dangerous web application attacks, though,
 are associated with the processing of external input data
@@
 attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
-Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}
-and others. Attacks like these top the vulnerability
-lists of numerous bulletin providers like
-the Open Web Application Security
+Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
+others. Attacks like these have been topping the vulnerability lists
+of numerous bulletin providers like the Open Web Application Security
 Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-({\sc owasp}) and {\sc mitre}\footnote{\url{http://cwe.mitre.org/top25/}}
-for several years. Consider the case of {\sc owasp}'s Top
-Ten project whose main goal is to raise awareness about
-web application security by identifying some of the most
-critical risks facing organizations which is referenced by
-numerous researchers. In its three consecutive Top Ten lists
-(2007, 2010, 2013), different executable source code-driven
-injection attacks dominate the top five positions.
-This indicates that apart from the fact that malicious
-users find new ways to bypass defense
-mechanisms by using a variety of techniques despite the numerous
-countermeasures that are being introduced.
-Note that the number of systems developed to counter {\sc sql}
-injection attacks until 2006 was more than twenty~\cite{HVO06}.
-Since then the number has doubled.
-In our research we focus on the top {\sc tba} systems that counter
-application attacks, in terms of citations.
+({\sc owasp}) and {\sc
+  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
+years. Consider the case of {\sc owasp}'s Top Ten project whose main
+goal is to raise awareness about web application security by
+identifying some of the most critical risks facing organizations which
+is referenced by numerous researchers. In its three consecutive Top
+Ten lists (2007, 2010, 2013), different executable source code-driven
+injection attacks dominate the top five positions. Malicious users
+find new ways to bypass defense mechanisms by using a variety of
+techniques despite the numerous countermeasures that are being
+introduced. Note that the number of systems developed to counter {\sc
+  sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
+Since then the number has doubled. In our research we focus on the top
+{\sc tba} systems that counter application attacks, in terms of
+citations.
 % TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
@@
 inside targeted systems, which turn a part of the target into a
-so-called ``weird machine" programmable by the attacker via crafted inputs
-(a.k.a. ``exploits")"}.
+so-called `weird machine' programmable by the attacker via crafted inputs
+(a.k.a. `exploits')''}.
 An example of the above definition is the
-following: The code fragment below, defines the operation of
+following: The code fragment below defines the operation of
 addition in the Scheme programming language~\cite{AS96,D09}:
@@
 untrusted input verbatim into an output
-program is vulnerable to code injection"}.
+program is vulnerable to code injection''}.
 Ray and Ligatti~\cite{RL12b} actually proved the above
@@
 
-Code injection attacks can be divided into two categories.
-The first involves binary code and the second executable source code.
-An extensive survey on binary code
-injection attacks can be found in reference~\cite{LC03}.
-Furthermore, specific advances in exploiting such vulnerabilities
-(i.e. ``heap smashing", ``arc injection" and others)
-have been presented in reference~\cite{PB04}.
-Finally, the countermeasures used to detect
-such defects have already been surveyed~\cite{YJP12}
-(many of them are also included in a book:~\cite{DKZ12}
--- Section 13.8), thus we do not include them in our work.
-In this paper, we focus on the defenses that protect
-applications against application attacks based on
-the executable source code injection category.
+Code injection attacks can be divided into two categories. The first
+involves binary code and the second executable source code. An
+extensive survey on binary code injection attacks can be found
+in~\cite{LC03}. Specific advances in exploiting such vulnerabilities
+(i.e. ``heap smashing", ``arc injection" and others) have been
+presented in~\cite{PB04}. The countermeasures used to detect such
+defects have already been surveyed~\cite{YJP12} (many of them are also
+included in a book:~\cite{DKZ12} -- Section 13.8). In the present work
+we do not include binary code injection, focusing instead on defenses
+that protect applications against application attacks based on the
+executable source code injection category.
 
@@
 Domain Specific Language ({\sc dsl})
-or a Dynamic Language. Note that binary code injection
-attacks can only occur when the target system is implemented in
-languages lacking array bounds checking, like
-{\sc c} and {\sc c}++. Contrariwise, source code-driven
-injection attacks can target applications written in various
-programming languages with different features and characteristics.
+or a Dynamic Language.
 
-Application attacks that involve {\sc dsl}s,
-constitute an important subset of the code injection problem,
-as {\sc dsl}s like {\sc sql} and {\sc xml} play an
-significant role in the development of either web or mobile
-applications. For example, many applications have interfaces
-where a user enters input to interact with the
-application's data, thereby interacting with the
-underlying {\it Relational Database Management System}
-({\sc rdbms}).
-This input can become part of an
-{\sc sql} query and executed on the target {\sc rdbms}.
-A code injection attack that exploits the vulnerabilities of these
-interfaces by taking advantage of input validation issues like
-incorrectly passed parameters or incorrect type handling,
-is called an {\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}.
-By using similar techniques malicious users
-can perform other exploits based on {\sc dsl}s,
-like {\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}.
-With this kind of attacks, a malicious user can view sensitive
-information, destroy or modify protected data, or even crash the entire
+Application attacks that involve {\sc dsl}s constitute an important
+subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
+{\sc xml} play an significant role in the development of either web or
+mobile applications. For example, many applications have interfaces
+where a user enters input to interact with the application's data,
+thereby interacting with the underlying Relational Database Management
+System ({\sc rdbms}). This input can become part of an {\sc sql} query
+and executed on the target {\sc rdbms}. A code injection attack that
+exploits the vulnerabilities of these interfaces by taking advantage
+of input validation issues like incorrectly passed parameters or
+incorrect type handling, is called an {\sc sql} injection
+attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
+malicious users can perform other exploits based on {\sc dsl}s, like
+{\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}. With
+this kind of attacks, a malicious user can view sensitive information,
+destroy or modify protected data, or even crash the entire
 application.
 
-A recent class of {\sc cia}s involve
-dynamic languages like Python, Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
-JavaScript injection attacks in particular, comprise a wide subset of dynamic
-language-driven attacks. Such attacks are manifested when a web application
-accepts and redisplays data of uncertain origin without appropriate validation
-and filtering. Based on this flaw, an attacker can
-manage to inject a script in the JavaScript engine of a browser and alter its
-execution flow~\cite{ELX07}. JavaScript injection attacks are considered as a
-critical issue in web application security mainly because they are
-associated with major vulnerabilities such as:
-{\sc xss} attacks~\cite{SG07},
-{\sc csrf} attacks~\cite{LZRL09}
-and Cross-Channel Scripting
-({\sc xcs}) attacks~\cite{W10,BBB09}.
+A recent class of {\sc cia}s involve dynamic languages like Python,
+Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
+injection attacks, in particular, make up a large subset of dynamic
+language-driven attacks. Such attacks are manifested when a web
+application accepts and redisplays data of uncertain origin without
+appropriate validation and filtering. Based on this flaw, an attacker
+can manage to inject a script in the JavaScript engine of a browser
+and alter its execution flow~\cite{ELX07}. JavaScript injection
+attacks are considered as a critical issue in web application security
+mainly because they are associated with major vulnerabilities such as:
+{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{LZRL09} and
+Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
 
@@
 
-In this section we provide a step-by-step exploitation
-model to understand the process of carrying out
-application attacks based on executable source code injection
-vulnerabilities. Figure~\ref{fig:attacks} presents the steps
-of different application attacks. For the most part,
-the steps are common for each attack. This is because
-they are based on similar attack vectors as we described in
-the previous section. We base the analysis of the
-existing defenses on this model. Figure~\ref{fig:attacks} also
-illustrates in which step the defenses detect corresponding
-attacks ({\sc todo}).
+In this section we provide a step-by-step exploitation model to
+understand the process of carrying out application attacks based on
+executable source code injection vulnerabilities.
+Figure~\ref{fig:attacks} presents the steps of different application
+attacks. For the most part, the steps are common in all attacks. This
+is because they are based on similar attack vectors as we described in
+the previous section. We base the analysis of the existing defenses on
+this model. Figure~\ref{fig:attacks} also illustrates in which step
+the defenses detect corresponding attacks ({\sc todo}).
 
-An attack starts with the malicious user sending an
-request either to the server or to a web user.
-In the first case the attacker
-could upload data containing a specially crafted script
-(in a blog comment) or create a request with
-additional {\sc sql} code.
+An attack starts with the malicious user sending an request either to
+the server or to a web user. In the first case the attacker could
+upload data containing a specially crafted script (for example, in a
+blog comment) or create a request with additional {\sc sql} code.
 

### 2014-10-24 docs/questioning.tex
more ammendments on the rest of the paper

@@
 
-\section{Dimensions of Study}
+\section{Web Application Attacks Defenses}
+\label{sec:defs}
+
+Figure~\ref{fig:defenses} presents a taxonomy of the
+approaches that protect web applications against attacks based on
+code injection vulnerabilities.
+We can identify two main approaches, namely:
+{\it design-based} and {\it behavior-based}.
+The former involves mechanisms that make applications
+immune to different attack vectors by design~\cite{JL75,L81}.
+The latter incorporates a variety of methods and
+schemes that inspect the behavior of applications
+and detect attacks based on specific criteria~\cite{D76,A00}.
+
+\subsection{Design-Based}
+\label{sec:prot}
+
+Here we analyze the three different protection approaches.
+
+\subsubsection{Parse-Tree Validation}
+
+The mechanism based on this method compare the parse tree of a
+query before the inclusion of user input with the one resulting after
+the inclusion of user input. If the trees diverge, the application
+is probably under attack.
+
+\subsubsection{Securing Mashups}
+
+\subsubsection{Code Rewriting}
+
+\subsubsection{Instruction Set Randomization --- ISR}
+
+{\sc isr} is a method that contrary to the previous
+three, has been applied to counter
+different kinds of application attacks~\cite{K09b,KKP03}.
+The main idea behind the method, is to
+separate code from data by randomizing the legitimate code's 
+execution environment. In this way, the malicious code
+injected by the attackers who do not know the randomization
+algorithm, will not get executed.
+
+{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
+to detect {\sc sql} injections in the following manner:
+initially, it allows programmers to create {\sc sql} statements
+using randomized instructions instead of standard keywords.
+The modified queries are either reconstructed at runtime using
+the same key that is inaccessible to the malicious user,
+or the user input is tagged with delimiters that allow
+an augmented {\sc sql} grammar to detect the
+attack.
+
+In the case of {\sc xss} attacks that are based on JavaScript,
+consider a {\sc xor} function that encodes all JavaScript source of a web
+page on the server-side and then, on the client-side, the web browser decodes the
+source by applying the same function again.
+Variations of this approach include:
+{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
+
+\subsection{Behavior-Based}
+
+\subsubsection{Runtime Tainting}
+
+Runtime tainting is based on data-flow analysis.
+In practice, it enforces security policies by marking untrusted
+(``tainted") data and tracing its flow through the program.
+Since information flow in a system cannot be verified by examining
+a single execution trace of the system, the results of taint
+analysis will necessarily reflect approximate information regarding
+the information flow characteristics of the system to which it is applied.
+
+\subsubsection{Policy Enforcement}
+
+In this method, developers must define
+specific security policies on the server side.
+Then the policies are enforced either in the user's
+browser at runtime or in a server-side proxy that
+intercepts server responses.
+
+\subsubsection{Training}
+
+Training techniques are based on the ideas of Denning's original
+intrusion detection framework~\cite{Den87}. In particular, a training
+mechanism registers all valid legitimate code statements during a
+training phase, most of the time in the form of signatures. This can
+be done in various ways according to the implementation. Then, only
+those will be accepted, approved or recognized during production.
+
+Training methods that detect JavaScript-driven {\sc xss} attacks
+generate and store valid JavaScript code in various
+forms, and detect attacks as outliers from the set of valid code statements.
+{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
+original application. Then, a JavaScript detection component placed in a web proxy
+searches for injected scripts in the server's responses. If no injected scripts
+are found, the proxy decodes the legitimate scripts and sends them to the
+client.
+% dimitro: more mechanisms TBA.
+
+In the case of {\sc dsl}-driven injection attacks
+the various countermeasures follow a similar pattern.
+An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
+{\sc sql} injection attacks by recording all database transactions.
+Subsequent refinements by Valeur et al.~\cite{VMV05}
+tagged each transaction with the corresponding application
+as an extension of their anomaly detection framework called
+{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
+Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
+injection attacks by associating a query model with the location of every
+{\sc sql} statement within the application. Then at runtime,
+monitors the application's execution to detect when {\sc sql} statements
+diverge from the expected model.
+{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
+mechanism that prevents
+{\sc sql} and {\sc xp}ath injection attacks against web applications. 
+The signatures generated during a training phase,
+are based on features that can depend either on the
+code statement or on its execution environment (i.e. the stack trace).
+Then, at runtime, the mechanism checks all statements for compliance
+and can block code statements containing injected elements.
+By associating a complete stack trace with the root of an {\sc sql} statement, 
+the mechanism can correlate {\sc sql} statements with their call sites.  
+This increases the specificity of the stored signatures and 
+avoids false alarms. 
+% dimitro: more mechanisms TBA.
+
+\begin{figure*}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.57]{defenses.pdf}
+\end{center}
+\caption{\label{fig:defenses}The basic categories of web application
+attack countermeasures ({\sc draft}).}
+\end{figure*}
+
+\begin{landscape}
+\begin{table}
+\centering
+    \begin{threeparttable}
+    \begin{small}
+\scalebox{0.99}{
+    \begin{tabular}{l|c|c|cc|c}
+    \hline
+    \bf{Approach}
+	& \bf{Mechanism}
+	& \bf{\# of Citations}
+  & \multicolumn{2}{|c|}{Requirements\tnote{1}}
+	& \bf{Attack} \\
+	&&& \bf{TP,TN,FP,FN}\tnote{2}
+	& \bf{Computational Overhead} & \\
+    \hline
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
+  \hline
+  \hline
+  \multirow{5}{*}{Securing Mashups}
+  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
+  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
+  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+  \hline
+  \hline
+  \multirow{3}{*}{{\sc isr}}
+  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
+  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
+  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
+  \hline
+  \hline         
+  \multirow{3}{*}{Code Rewriting}
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
+  \hline
+  \hline
+  \hline
+  \hline
+	\multirow{8}{*}{Runtime Tainting}
+  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
+	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss} \\ 
+  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
+  &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
+  \hline
+  \hline 
+	\multirow{7}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
+	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
+  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
+	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
+	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
+  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
+  % TODO@dimitro: discuss this with Panos?
+	\hline
+	\hline  
+  \multirow{9}{*}{Training}
+  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} & {\sc sql} injection \\ 
+	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
+	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\
+  & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
+  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
+	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
+	\hline
+    \end{tabular}}
+    \begin{tablenotes}
+	\begin{footnotesize}
+       	\item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.
+	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
+	but it is not quantified.
+		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
+	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).
+	If no testing has taken place we add a question mark ({\bf ?}).
+	\end{footnotesize}
+    \end{tablenotes}
+    \caption{Comparison summary of mechanisms developed to counter application attacks.}
+    \label{tab:comp2}
+    \end{small}
+    \end{threeparttable}
+\end{table}
+\end{landscape}
+
+\section{Analysis Dimensions}
+
+\subsection{Diagnostic Performance}
 
@@
 
-In what follows we evaluate published research in attack detection
-mechanism based on the following:
+If published research does not include figures for Sensitivity and
+Specificity or values for ($a$)--($d$), on test environments, then it
+is not possible to judge the accuracy of the research at all. Even if
+we do have such figures, a good research tool is not necessarily a
+good practical tool. Even if a research tool scores well on
+Sensitivity and Specificity, it may not be very useful in the real
+world if the prevalence of the caught attacks is so low that a
+positive test result is not likely to indicate a real attack.
+
+To sum up, we evaluate diagnostic performance on two criteria:
+
 \begin{itemize}
-\item \textbf{Sensitivity, Specificity}: Reporting of values for True
-  Positives ($a$), False Positives ($b$), False Negatives ($c$), True
-  Negatives ($d$), on test environments.
-\item \textbf{\textsc{ppv}, \textsc{npv}}: Reporting of values for True
-  Positives ($A$), False Positives ($B$), False Negatives ($C$), True
-  Negatives ($D$), on the performance of the mechanism on environments
-  with real attack profiles. Alternatively, since from
-  equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} \textsc{ppv}
-  and \textsc{npv} can be calculated by the sensitity and specifity
-  given the prevalence, reporting of prevalance, sensitivity,
-  specificity.
+\item Reporting of Sensitivity and Specifity, either directly, or
+  indirectly from published values of $a$--$d$.
+\item Reporting of \textsc{ppv} and \textsc{npv}. This can be direct
+  reporting of their values, or indirect from published values of
+  $A$--$D$. Also, since from equations~\ref{eq:ppv-se-sp}
+  and~\ref{eq:npv-se-sp} \textsc{ppv} and \textsc{npv} can be
+  calculated by the sensitity and specifity given the prevalence, it
+  can be via reporting prevalance, sensitivity, specificity.
 \end{itemize}
 
-\section{Web Application Attacks Defenses}
-\label{sec:defs}
+\subsection{Computational Performance}
 
-Figure~\ref{fig:defenses} presents a taxonomy of the
-approaches that protect web applications against attacks based on
-code injection vulnerabilities.
-We can identify two main approaches, namely:
-{\it design-based} and {\it behavior-based}.
-The former involves mechanisms that make applications
-immune to different attack vectors by design~\cite{JL75,L81}.
-The latter incorporates a variety of methods and
-schemes that inspect the behavior of applications
-and detect attacks based on specific criteria~\cite{D76,A00}.
+\subsection{Ease of Use}
 
-\subsection{Design-Based}
-\label{sec:prot}
-
-Here we analyze the three different protection approaches.
-
-\subsubsection{Parse-Tree Validation}
-
-The mechanism based on this method compare the parse tree of a
-query before the inclusion of user input with the one resulting after
-the inclusion of user input. If the trees diverge, the application
-is probably under attack.
-
-\subsubsection{Securing Mashups}
-
-\subsubsection{Code Rewriting}
-
-\subsubsection{Instruction Set Randomization --- ISR}
-
-{\sc isr} is a method that contrary to the previous
-three, has been applied to counter
-different kinds of application attacks~\cite{K09b,KKP03}.
-The main idea behind the method, is to
-separate code from data by randomizing the legitimate code's 
-execution environment. In this way, the malicious code
-injected by the attackers who do not know the randomization
-algorithm, will not get executed.
-
-{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
-to detect {\sc sql} injections in the following manner:
-initially, it allows programmers to create {\sc sql} statements
-using randomized instructions instead of standard keywords.
-The modified queries are either reconstructed at runtime using
-the same key that is inaccessible to the malicious user,
-or the user input is tagged with delimiters that allow
-an augmented {\sc sql} grammar to detect the
-attack.
-
-In the case of {\sc xss} attacks that are based on JavaScript,
-consider a {\sc xor} function that encodes all JavaScript source of a web
-page on the server-side and then, on the client-side, the web browser decodes the
-source by applying the same function again.
-Variations of this approach include:
-{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
-
-\subsection{Behavior-Based}
-
-\subsubsection{Runtime Tainting}
-
-Runtime tainting is based on data-flow analysis.
-In practice, it enforces security policies by marking untrusted
-(``tainted") data and tracing its flow through the program.
-Since information flow in a system cannot be verified by examining
-a single execution trace of the system, the results of taint
-analysis will necessarily reflect approximate information regarding
-the information flow characteristics of the system to which it is applied.
-
-\subsubsection{Policy Enforcement}
-
-In this method, developers must define
-specific security policies on the server side.
-Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that
-intercepts server responses.
-
-\subsubsection{Training}
-
-Training techniques are based on the ideas of Denning's original
-intrusion detection framework~\cite{Den87}.
-In particular, a training mechanism,
-registers all valid legitimate code statements
-during a training phase, most of the time in the form of signatures.
-This can be done in various ways according to the implementation.
-Then, only those will be accepted, approved or recognized during
-production.
-
-Training methods that detect JavaScript-driven {\sc xss} attacks
-generate and store valid JavaScript code in various
-forms, and detect attacks as outliers from the set of valid code statements.
-{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
-original application. Then, a JavaScript detection component placed in a web proxy
-searches for injected scripts in the server's responses. If no injected scripts
-are found, the proxy decodes the legitimate scripts and sends them to the
-client.
-% dimitro: more mechanisms TBA.
-
-In the case of {\sc dsl}-driven injection attacks
-the various countermeasures follow a similar pattern.
-An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
-{\sc sql} injection attacks by recording all database transactions.
-Subsequent refinements by Valeur et al.~\cite{VMV05}
-tagged each transaction with the corresponding application
-as an extension of their anomaly detection framework called
-{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
-Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
-injection attacks by associating a query model with the location of every
-{\sc sql} statement within the application. Then at runtime,
-monitors the application's execution to detect when {\sc sql} statements
-diverge from the expected model.
-{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
-mechanism that prevents
-{\sc sql} and {\sc xp}ath injection attacks against web applications. 
-The signatures generated during a training phase,
-are based on features that can depend either on the
-code statement or on its execution environment (i.e. the stack trace).
-Then, at runtime, the mechanism checks all statements for compliance
-and can block code statements containing injected elements.
-By associating a complete stack trace with the root of an {\sc sql} statement, 
-the mechanism can correlate {\sc sql} statements with their call sites.  
-This increases the specificity of the stored signatures and 
-avoids false alarms. 
-% dimitro: more mechanisms TBA.
-
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.57]{defenses.pdf}
-\end{center}
-\caption{\label{fig:defenses}The basic categories of web application
-attack countermeasures ({\sc draft}).}
-\end{figure*}
-
-\begin{landscape}
-\begin{table}
-\centering
-    \begin{threeparttable}
-    \begin{small}
-\scalebox{0.99}{
-    \begin{tabular}{l|c|c|cc|c}
-    \hline
-    \bf{Approach}
-	& \bf{Mechanism}
-	& \bf{\# of Citations}
-  & \multicolumn{2}{|c|}{Requirements\tnote{1}}
-	& \bf{Attack} \\
-	&&& \bf{TP,TN,FP,FN}\tnote{2}
-	& \bf{Computational Overhead} & \\
-    \hline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
-  \hline
-  \hline
-  \multirow{5}{*}{Securing Mashups}
-  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
-  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
-  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
-  \hline
-  \hline
-  \multirow{3}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
-  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
-  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
-  \hline
-  \hline         
-  \multirow{3}{*}{Code Rewriting}
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
-  \hline
-  \hline
-  \hline
-  \hline
-	\multirow{8}{*}{Runtime Tainting}
-  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
-	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss} \\ 
-  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
-  \hline
-  \hline 
-	\multirow{7}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
-	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
-	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\ 
-	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
-  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
-  % TODO@dimitro: discuss this with Panos?
-	\hline
-	\hline  
-  \multirow{9}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} & {\sc sql} injection \\ 
-	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\
-  & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
-  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
-	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-	\hline
-    \end{tabular}}
-    \begin{tablenotes}
-	\begin{footnotesize}
-       	\item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.
-	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
-	but it is not quantified.
-		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
-	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).
-	If no testing has taken place we add a question mark ({\bf ?}).
-	\end{footnotesize}
-    \end{tablenotes}
-    \caption{Comparison summary of mechanisms developed to counter application attacks.}
-    \label{tab:comp2}
-    \end{small}
-    \end{threeparttable}
-\end{table}
-\end{landscape}
+\subsection{Availability}
 

### 2014-10-24 docs/questioning.tex
add two dimensions + move back
more on subsection II.B

@@
 \subsection{Exploitation Model}
+\label{sec:model}
 
@@
 attacks. For the most part, the steps are common in all attacks. This
-is because they are based on similar attack vectors as we described in
-the previous section. We base the analysis of the existing defenses on
-this model. Figure~\ref{fig:attacks} also illustrates in which step
+is because they are based on similar attack vectors as we mentioned in
+the previous section. Most importantly,
+Figure~\ref{fig:attacks} also illustrates in which step
 the defenses detect corresponding attacks ({\sc todo}).
@@
 An attack starts with the malicious user sending an request either to
-the server or to a web user. In the first case the attacker could
-upload data containing a specially crafted script (for example, in a
-blog comment) or create a request with additional {\sc sql} code.
+the server or to a web user.
+In the first case 
+consider a web application that accepts and redisplays data of
+uncertain origin without appropriate validation and / or filtering.
+An attacker could upload data containing a specially
+crafted script (for example, in a blog comment)
+to steal the cookies of the visiting users
+or embed malicious {\sc sql} code to retrieve all
+the password entries from a database.
+In the second case, the attacker crafts a malicious script
+into a {\sc url} and then tricks an end user to click on it
+via social engineering (i.e. phishing). In this way
+an unauthorized command is transmitted from a user to a
+website where a user is considered as legitimate.
+
+Then, the injected code reaches the vulnerable
+application where it probably becomes a part of a value
+represented by a program variable.
+In the next step, the code becomes a part of a query which
+finally reaches the database where it is executed.
+Attacks like {\sc sql} injection and {\sc csrf}
+end right there.
+
+Before we proceed with the {\sc xss} attack path,
+we should mention here that there are two basic
+{\sc xss} attack categories, namely:
+{\it non-persistent} and {\it persistent}.
+Non-persistent {\sc xss} attacks take place when the data provided
+by a user, is used immediately by server-side scripts to parse
+and display a page of results for and to that user, without
+properly sanitizing the request. In the case of a
+persistent {\sc xss} attack, malicious code
+is saved by the server, and then permanently
+displayed on the web site's pages that are displayed
+to other users.
+
+% A {\sc persistent} {\sc xss} attack though would
+% continue
+% An {\sc xss} attack that belongs to the {\it non-persistent}
+% {\sc xss} category could have followed a different path.
+% This is because
 
@@
 \end{figure*}
+
+\section{Analysis Dimensions}
+
+\subsection{Diagnostic Performance}
+
+As in medical diagnostic tests, application attack defense mechanisms
+must demonstrate the presence of an attack. This, however, does not
+make an application attack defense mechanism immediately useful. In
+order for a detection mechanism to be useful it must be accurate, easy to
+use, and economical. The accuracy of a detection mechanism is gauged
+with the following metrics~\cite{TDR2013,GFDLS06,A00}:
+\begin{itemize}
+\item {\bf Sensitivity}, the probability that an attack will be
+  caught.
+\item {\bf Specificity}, the probability that a normal interaction
+  will test negative.
+\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
+  reported attack is a real attack. It is the conditional probability
+  that an event is an attack if the detection mechanism flags it as
+  such. 
+\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
+  nothing is reported no attack has taken place. It is the conditional
+  probability that an event is not an attack given that the detection
+  mechanism flags it as normal.
+\end{itemize}
+
+Sensitivity and specifity are defined by way of the $2\times 2$
+Table~\ref{tab:sensitivity-specificity}~\cite{linn2004}. 
+In the cells of
+the table we distinguish:
+\begin{itemize}
+\item True Positive ($a$), a real attack that raises an alarm.
+\item True Negative ($d$), an event that is not an attack and that does
+  not raise an alarm.
+\item False Positive ($b$), an event that although it is not an attack
+  raises an alarm.
+\item False Negative ($c$), an event that although is as attack does
+  not raise an alarm.
+\end{itemize}
+
+\noindent
+With these we can calculate:
+
+\begin{equation}
+\textrm{SE} = \textrm{Sensitivity} = \frac{a}{a + c}
+\end{equation}
+
+\begin{equation}
+\textrm{SP} = \textrm{Specificity} = \frac{d}{b + d}
+\end{equation}
+
+Sensitivity and specificity can be calculated based on test
+data alone. To calculate the sensitivity, we run the test on a
+controlled environment where we allow only attack events to reach the
+system. The ratio of reported attacks over all attacks will give us
+the sensitivity. Similarly, to calculate the specificity we can run
+the test on a controlled environment where we allow only innocuous
+events to reach the system. The ratio of non-reported events over all
+events will give us the specificity.
+
+\begin{table}[ht]
+
+\caption{Attacks and Test Outcomes in Test Environment}
+\label{tab:sensitivity-specificity}
+
+\begin{tabular}{l|l|c|c|}
+\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} \\ \cline{3-4}
+\multicolumn{2}{c|}{} & Yes & No \\ \cline{2-4}
+\multirow{2}{*}{Result} &  Yes &  $a = \textrm{True Positive}$ & 
+$b = \textrm{False Positive}$ \\
+& No & $c = \textrm{False Negative}$ & $d = \textrm{True Negative}$ \\ 
+\cline{2-4}
+\multicolumn{2}{r|}{Total} & $a + c$ & $b + d$ \\
+\cline{3-4}
+\end{tabular}
+
+\end{table}
+
+Note that the calculations are carried out vertically in
+Table~\ref{tab:sensitivity-specificity}; the ratio of attack events to
+normal events does not enter into sensitivity and specificity. This is
+what allows us to derive them based on test data, without using data
+from a real production environment. At the same time, however, this is
+what limits their usefulness. When we obtain a test result in a
+production environment, be it negative or positive, we really want to
+know how much we should be worried, or relaxed. In other words, if an
+attack is detected in a production environment, how much should we be
+worried? If no attack is detected in a production environment, how
+relaxed should we be that no attack has indeed taken place?
+
+\begin{table}[ht]
+
+\caption{Attacks and Test Outcomes in Real Environment}
+\label{tab:ppv-npv}
+
+\begin{tabular}{l|l|c|c|c}
+\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} & \\ \cline{3-4}
+\multicolumn{2}{c|}{} & Yes & No & Total \\ \cline{2-5}
+\multirow{2}{*}{Result} &  Yes &  $A = \textrm{True Positive}$ & 
+$B = \textrm{False Positive}$ & \multicolumn{1}{c|}{$A + B$}\\
+& No & $C = \textrm{False Negative}$ & $D = \textrm{True Negative}$ &
+\multicolumn{1}{c|}{$C + D$}\\ 
+\cline{2-5}
+\end{tabular}
+
+\end{table}
+
+The answer to these questions is given by the \textsc{ppv} and the
+\textsc{npv}. These depend not only on the test results, but also on
+the \emph{prevalence} of attacks in real environments. In particular,
+we can calculate them using Table~\ref{tab:ppv-npv}, which tabulates
+results in a real environment, or in an environment where the
+prevalence of attacks is equal to what we expect in the real world. To
+indicate the difference with Table~\ref{tab:sensitivity-specificity}
+we use capital letters for the entries in the table~\cite{linn2004}.
+With this table, \textsc{ppv} and \textsc{npv} are given by the
+following equations:
+
+\begin{equation}
+\textrm{PPV} = \frac{A}{A + C}
+\end{equation}
+
+\begin{equation}
+\textrm{NPV} = \frac{D}{B + D}
+\end{equation}
+
+This time the ratios are taken horizontally; the ratio of attacks to
+innocuous events affects the calculations. In fact, if PR is the
+probability of attacks in the real world, the prevalence, then we
+have~\cite{linn2004,altman1994}:
+
+\begin{equation}
+\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
+\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 -
+\textrm{PR})}
+\label{eq:ppv-se-sp}
+\end{equation}
+
+\begin{equation}
+\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
+(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 -
+\textrm{PR})}
+\label{eq:npv-se-sp}
+\end{equation}
+
+The prevalence is the prior probability that an event is an attack,
+based on our understanding of the volume and frequency of attacks; the
+\textsc{ppv} and \textsc{npv} are the revised estimates of the
+probability based on the results of the detection
+mechanism~\cite{altman1994}. The lower the prevalence of an attack,
+the more confident we can be that a negative test result indicates
+that no attack has taken place and the less sure we can be that a
+positive test result indicates a real attack.
+
+If published research does not include figures for Sensitivity and
+Specificity or values for ($a$)--($d$), on test environments, then it
+is not possible to judge the accuracy of the research at all. Even if
+we do have such figures, a good research tool is not necessarily a
+good practical tool. Even if a research tool scores well on
+Sensitivity and Specificity, it may not be very useful in the real
+world if the prevalence of the caught attacks is so low that a
+positive test result is not likely to indicate a real attack.
+
+To sum up, we evaluate diagnostic performance on two criteria:
+
+\begin{itemize}
+\item Reporting of Sensitivity and Specifity, either directly, or
+  indirectly from published values of $a$--$d$.
+\item Reporting of \textsc{ppv} and \textsc{npv}. This can be direct
+  reporting of their values, or indirect from published values of
+  $A$--$D$. Also, since from equations~\ref{eq:ppv-se-sp}
+  and~\ref{eq:npv-se-sp} \textsc{ppv} and \textsc{npv} can be
+  calculated by the sensitity and specifity given the prevalence, it
+  can be via reporting prevalance, sensitivity, specificity.
+\end{itemize}
+
+\subsection{Computational Performance}
+
+\subsection{Ease of Use}
+
+\subsection{Availability}
+
+\subsection{Detection Locus}
+
+\subsection{Detection Circumvention}
 
@@
 
-\section{Analysis Dimensions}
-
-\subsection{Diagnostic Performance}
-
-As in medical diagnostic tests, application attack defense mechanisms
-must demonstrate the presence of an attack. This, however, does not
-make an application attack defense mechanism immediately useful. In
-order for a detection mechanism to be useful it must be accurate, easy to
-use, and economical. The accuracy of a detection mechanism is gauged
-with the following metrics~\cite{TDR2013,GFDLS06,A00}:
-\begin{itemize}
-\item {\bf Sensitivity}, the probability that an attack will be
-  caught.
-\item {\bf Specificity}, the probability that a normal interaction
-  will test negative.
-\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
-  reported attack is a real attack. It is the conditional probability
-  that an event is an attack if the detection mechanism flags it as
-  such. 
-\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
-  nothing is reported no attack has taken place. It is the conditional
-  probability that an event is not an attack given that the detection
-  mechanism flags it as normal.
-\end{itemize}
-
-Sensitivity and specifity are defined by way of the $2\times 2$
-Table~\ref{tab:sensitivity-specificity}~\cite{linn2004}. 
-In the cells of
-the table we distinguish:
-\begin{itemize}
-\item True Positive ($a$), a real attack that raises an alarm.
-\item True Negative ($d$), an event that is not an attack and that does
-  not raise an alarm.
-\item False Positive ($b$), an event that although it is not an attack
-  raises an alarm.
-\item False Negative ($c$), an event that although is as attack does
-  not raise an alarm.
-\end{itemize}
-
-\noindent
-With these we can calculate:
-
-\begin{equation}
-\textrm{SE} = \textrm{Sensitivity} = \frac{a}{a + c}
-\end{equation}
-
-\begin{equation}
-\textrm{SP} = \textrm{Specificity} = \frac{d}{b + d}
-\end{equation}
-
-Sensitivity and specificity can be calculated based on test
-data alone. To calculate the sensitivity, we run the test on a
-controlled environment where we allow only attack events to reach the
-system. The ratio of reported attacks over all attacks will give us
-the sensitivity. Similarly, to calculate the specificity we can run
-the test on a controlled environment where we allow only innocuous
-events to reach the system. The ratio of non-reported events over all
-events will give us the specificity.
-
-\begin{table}[ht]
-
-\caption{Attacks and Test Outcomes in Test Environment}
-\label{tab:sensitivity-specificity}
-
-\begin{tabular}{l|l|c|c|}
-\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} \\ \cline{3-4}
-\multicolumn{2}{c|}{} & Yes & No \\ \cline{2-4}
-\multirow{2}{*}{Result} &  Yes &  $a = \textrm{True Positive}$ & 
-$b = \textrm{False Positive}$ \\
-& No & $c = \textrm{False Negative}$ & $d = \textrm{True Negative}$ \\ 
-\cline{2-4}
-\multicolumn{2}{r|}{Total} & $a + c$ & $b + d$ \\
-\cline{3-4}
-\end{tabular}
-
-\end{table}
-
-Note that the calculations are carried out vertically in
-Table~\ref{tab:sensitivity-specificity}; the ratio of attack events to
-normal events does not enter into sensitivity and specificity. This is
-what allows us to derive them based on test data, without using data
-from a real production environment. At the same time, however, this is
-what limits their usefulness. When we obtain a test result in a
-production environment, be it negative or positive, we really want to
-know how much we should be worried, or relaxed. In other words, if an
-attack is detected in a production environment, how much should we be
-worried? If no attack is detected in a production environment, how
-relaxed should we be that no attack has indeed taken place?
-
-\begin{table}[ht]
-
-\caption{Attacks and Test Outcomes in Real Environment}
-\label{tab:ppv-npv}
-
-\begin{tabular}{l|l|c|c|c}
-\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} & \\ \cline{3-4}
-\multicolumn{2}{c|}{} & Yes & No & Total \\ \cline{2-5}
-\multirow{2}{*}{Result} &  Yes &  $A = \textrm{True Positive}$ & 
-$B = \textrm{False Positive}$ & \multicolumn{1}{c|}{$A + B$}\\
-& No & $C = \textrm{False Negative}$ & $D = \textrm{True Negative}$ &
-\multicolumn{1}{c|}{$C + D$}\\ 
-\cline{2-5}
-\end{tabular}
-
-\end{table}
-
-The answer to these questions is given by the \textsc{ppv} and the
-\textsc{npv}. These depend not only on the test results, but also on
-the \emph{prevalence} of attacks in real environments. In particular,
-we can calculate them using Table~\ref{tab:ppv-npv}, which tabulates
-results in a real environment, or in an environment where the
-prevalence of attacks is equal to what we expect in the real world. To
-indicate the difference with Table~\ref{tab:sensitivity-specificity}
-we use capital letters for the entries in the table~\cite{linn2004}.
-With this table, \textsc{ppv} and \textsc{npv} are given by the
-following equations:
-
-\begin{equation}
-\textrm{PPV} = \frac{A}{A + C}
-\end{equation}
-
-\begin{equation}
-\textrm{NPV} = \frac{D}{B + D}
-\end{equation}
-
-This time the ratios are taken horizontally; the ratio of attacks to
-innocuous events affects the calculations. In fact, if PR is the
-probability of attacks in the real world, the prevalence, then we
-have~\cite{linn2004,altman1994}:
-
-\begin{equation}
-\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
-\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 -
-\textrm{PR})}
-\label{eq:ppv-se-sp}
-\end{equation}
-
-\begin{equation}
-\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
-(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 -
-\textrm{PR})}
-\label{eq:npv-se-sp}
-\end{equation}
-
-The prevalence is the prior probability that an event is an attack,
-based on our understanding of the volume and frequency of attacks; the
-\textsc{ppv} and \textsc{npv} are the revised estimates of the
-probability based on the results of the detection
-mechanism~\cite{altman1994}. The lower the prevalence of an attack,
-the more confident we can be that a negative test result indicates
-that no attack has taken place and the less sure we can be that a
-positive test result indicates a real attack.
-
-If published research does not include figures for Sensitivity and
-Specificity or values for ($a$)--($d$), on test environments, then it
-is not possible to judge the accuracy of the research at all. Even if
-we do have such figures, a good research tool is not necessarily a
-good practical tool. Even if a research tool scores well on
-Sensitivity and Specificity, it may not be very useful in the real
-world if the prevalence of the caught attacks is so low that a
-positive test result is not likely to indicate a real attack.
-
-To sum up, we evaluate diagnostic performance on two criteria:
-
-\begin{itemize}
-\item Reporting of Sensitivity and Specifity, either directly, or
-  indirectly from published values of $a$--$d$.
-\item Reporting of \textsc{ppv} and \textsc{npv}. This can be direct
-  reporting of their values, or indirect from published values of
-  $A$--$D$. Also, since from equations~\ref{eq:ppv-se-sp}
-  and~\ref{eq:npv-se-sp} \textsc{ppv} and \textsc{npv} can be
-  calculated by the sensitity and specifity given the prevalence, it
-  can be via reporting prevalance, sensitivity, specificity.
-\end{itemize}
-
-\subsection{Computational Performance}
-
-\subsection{Ease of Use}
-
-\subsection{Availability}
-
 \section{Analysis}

### 2014-10-25 docs/questioning.tex
exploitation model text ready

@@
 Then, the injected code reaches the vulnerable
-application where it probably becomes a part of a value
+application where it becomes a part of a value
 represented by a program variable.
-In the next step, the code becomes a part of a query which
+In the next step, the code becomes a part of a query that
 finally reaches the database where it is executed.
@@
 Before we proceed with the {\sc xss} attack path,
-we should mention here that there are two basic
+we should mention that there are two basic
 {\sc xss} attack categories, namely:
@@
 displayed on the web site's pages that are displayed
-to other users.
-
-% A {\sc persistent} {\sc xss} attack though would
-% continue
-% An {\sc xss} attack that belongs to the {\it non-persistent}
-% {\sc xss} category could have followed a different path.
-% This is because
+to other users. Thus, in a non-persistent {\sc xss}
+attack the injected code never reaches the database
+and immediately becomes a part of the content that is
+sent back to a web user. In the case of a persistent
+{\sc xss}, the injected code that is stored on the server-side
+re-enters the application's execution flow and afterwards it
+becomes a part of the content that is actually sent back to
+the user.
 
@@
 
+\section{Conclusions}
+
+% Cite~\cite{HNSHS12}.
+
 \bibliographystyle{IEEEtran}

### 2014-10-25 docs/questioning.tex
minor addition on Section 1, Section 2 draft ready

@@
 techniques despite the numerous countermeasures that are being
-introduced. Note that the number of systems developed to counter {\sc
-  sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
-Since then the number has doubled. In our research we focus on the top
+introduced. Note that the number of systems developed to counter
+{\sc sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
+Since then the number has doubled.
+Researchers have also indicated that the number of such attacks
+is steadily increasing in recent years~\cite{SSL12}.
+
+In our research we focus on the top
 {\sc tba} systems that counter application attacks, in terms of
@@
 code injection attacks. Such attacks may involve source code, either of a
-Domain Specific Language ({\sc dsl})
-or a Dynamic Language.
+Domain Specific Language ({\sc dsl}) or a Dynamic Language.
 
@@
 destroy or modify protected data, or even crash the entire
-application.
+application. {\sc html} is another {\sc dsl} that can be used
+for malicious purposes when an application does not properly
+handle user supplied data. Based on this vulnerability
+an attacker can supply valid {\sc html},
+typically via a parameter value, and inject their own
+content into the page. {\sc html} injection is mainly associated
+with {\sc xss} defects.
 
-A recent class of {\sc cia}s involve dynamic languages like Python,
-Perl, JavaScript, and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
+A recent class of {\sc cia}s involve dynamic languages like
+JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
 injection attacks, in particular, make up a large subset of dynamic
@@
 Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
+In many cases {\sc xss} attacks involve the injection of
+both {\sc html} and JavaScript code.
 

### 2014-10-26 docs/questioning.tex
clarifications on related work and covered area in section 1

@@
 
+There is already a survey on mitigating
+software vulnerabilities in general~\cite{SZ12}.
+The scope of that research is pretty wide and leaves
+out many approaches and mechanisms that we report here.
+This is mainly because this work includes countermeasures
+that detect such vulnerabilities via program analysis
+(which is done during development or testing), while
+we include protection mechanisms that counter
+such attacks when they take place.
+Also, countermeasures that prevent {\sc sql}
+injection attacks~\cite{HVO06}, have already been surveyed.
+However, this survey is quite old and since then
+the number of countermeasures that detect {\sc sql}
+injection attacks alone, has been drastically increased
+as we mentioned in the previous paragraph.
 In our research we focus on the top
@@
 citations.
+
 % TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
@@
 
-Here we analyze the three different protection approaches.
+Here we analyze the {\sc tba} different protection approaches.
 

### 2014-10-26 docs/questioning.tex
minor additions, changes

@@
 Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-({\sc owasp}) and {\sc
-  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
+({\sc owasp}) and
+{\sc mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
 years. Consider the case of {\sc owasp}'s Top Ten project whose main
@@
 In our research we focus on the top
-{\sc tba} systems that counter application attacks, in terms of
-citations.
+{\sc tba} systems that counter application attacks,
+in terms of citations.
 
@@
 \begin{itemize}
-\item {\bf Flexibility} We check if an approach
-can be adjusted in order to detect different {\sc cia} categories.
-\item {\bf Ease of use} We examine if the mechanism that
-implements an approach is practical and can be easily adopted
-by security experts.
-\item {\bf Effectiveness} As long as we examine security
-mechanisms that detect either attacks or defects,
-the non-existence of false positive and negative alarms
-is a reasonable requirement.
-\item {\bf Efficiency} Finally, we examine
-the computational overhead of the mechanisms that affect the experience of
-a web user who actually uses the protected application.
-\item {\bf Security} How resilient is the system to
-attacks made to to circumvent it.
+\item {\it Diagnostic Performance} As long
+as we examine protection mechanisms that detect
+attacks, the non-existence of false positive and
+negative alarms is a reasonable requirement.
+\item {\it Computational Performance} We examine
+the overhead of the mechanisms
+that affect the experience of a web user who actually
+uses the protected application.
+\item {\it Ease of use} We examine if the protection
+mechanism is practical in terms of deployment
+and can be easily adopted by security experts.
+\item {\it Security} How resilient is the system to
+attackers that know how it works and wants to circumvent it.
+\item {\it Detection Locus}
+\item {\it Availability}
 \end{itemize}
+
 All the aforementioned requirements are considered critical
@@
 \section{Analysis Dimensions}
+\label{sec:dimensions}
 
@@
 
-\subsection{Availability}
+\subsection{Security}
 
@@
 
-\subsection{Detection Circumvention}
+\subsection{Availability}
 
@@
 and detect attacks based on specific criteria~\cite{D76,A00}.
+
+Both categories involve more than one subcategories.
+For every subcategory we provide elements regarding
+every dimension we described in
+Section~\ref{sec:dimensions}.
 
@@
   \hline
-  \hline
-  \hline
 	\multirow{8}{*}{Runtime Tainting}
@@
 		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
-	based on real-world applications known to be vulnerable ({\it r}), synthetic benchmarks ({\it s}) or both ({\it a}).
+	based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic benchmarks ({\it s}), c) both ({\it a}).
 	If no testing has taken place we add a question mark ({\bf ?}).

### 2014-10-27 docs/questioning.tex
rewrite Figure 2 description

@@
 
-An attack starts with the malicious user sending an request either to
-the server or to a web user.
-In the first case 
-consider a web application that accepts and redisplays data of
-uncertain origin without appropriate validation and / or filtering.
-An attacker could upload data containing a specially
-crafted script (for example, in a blog comment)
-to steal the cookies of the visiting users
-or embed malicious {\sc sql} code to retrieve all
-the password entries from a database.
-In the second case, the attacker crafts a malicious script
-into a {\sc url} and then tricks an end user to click on it
-via social engineering (i.e. phishing). In this way
-an unauthorized command is transmitted from a user to a
-website where a user is considered as legitimate.
+A malicious user can initiate the attack through two different routes.
+The attacker may use the browser of an innocent user as an attack
+vehicle, through which the code will be injected in the application.
+For example, the attacker could craft a malicious script into a {\sc url}
+and then trick an end user to click on it via social engineering
+(i.e., phishing). Alternatively, the attacker may be able to inject
+directly the malicious code in the application. For example, consider
+a web application that accepts and redisplays data of uncertain origin
+without appropriate validation or filtering. An attacker could
+upload data containing a specially crafted script (for example, in a
+blog comment) to steal the cookies of the visiting users or embed
+malicious {\sc sql} code to retrieve all the password entries from a
+database.
 
-Then, the injected code reaches the vulnerable
-application where it becomes a part of a value
-represented by a program variable.
-In the next step, the code becomes a part of a query that
+Once the injected code reaches the vulnerable application, it becomes
+a part of a value represented by a program variable. The target of the
+attack determines the route from now on. In {\sc sql} injection and
+{\sc csrf} attacks the injected code becomes part of a query that
 finally reaches the database where it is executed.
-Attacks like {\sc sql} injection and {\sc csrf}
-end right there.
 
-Before we proceed with the {\sc xss} attack path,
-we should mention that there are two basic
-{\sc xss} attack categories, namely:
-{\it non-persistent} and {\it persistent}.
-Non-persistent {\sc xss} attacks take place when the data provided
-by a user, is used immediately by server-side scripts to parse
-and display a page of results for and to that user, without
-properly sanitizing the request. In the case of a
-persistent {\sc xss} attack, malicious code
-is saved by the server, and then permanently
-displayed on the web site's pages that are displayed
-to other users. Thus, in a non-persistent {\sc xss}
-attack the injected code never reaches the database
-and immediately becomes a part of the content that is
-sent back to a web user. In the case of a persistent
-{\sc xss}, the injected code that is stored on the server-side
-re-enters the application's execution flow and afterwards it
-becomes a part of the content that is actually sent back to
-the user.
+{\sc xss} attacks fall ino two categories, {\it non-persistent} and
+{\it persistent}. Non-persistent {\sc xss} attacks take place when the
+data provided by a user is used immediately by server-side scripts to
+parse and display a page of results, without properly sanitizing the
+request. Thus, in a non-persistent {\sc xss} attack the injected code
+never reaches the database and immediately becomes a part of the
+content that is sent back to a web user.
+
+In persistent {\sc xss} attacks malicious code is saved by the server.
+The injected code that is stored on the server-side re-enters the
+application's execution flow and becomes part of the content that is
+actually sent back afterwards to the user.
 

### 2014-10-27 docs/questioning.tex
updated Figure 2
more on figure 2

@@
 Figure~\ref{fig:attacks} presents the steps of different application
-attacks. For the most part, the steps are common in all attacks. This
+attacks. For every arrow there is a
+corresponding tuple that includes the step number for
+every attack. For the most part, the steps are common in all attacks. This
 is because they are based on similar attack vectors as we mentioned in
@@
 application attacks based on executable source
-code injection vulnerabilities ({\sc draft}).}
+code injection vulnerabilities. For every arrow there is a
+corresponding tuple that includes the step number for
+every attack. {\sc p-xss} stands for a persistent {\sc xss}
+attack and {\sc n-xss} stands for a non persistent {\sc xss}
+attack. Note that {\sc xss} attacks can also involve
+{\it phishing}. Every {\it locus} indicates a step where mechanisms
+detect attacks. For every locus we provide the corresponding
+references: ({\sc draft}).}
 \end{figure*}
@@
 
-\section{Web Application Attacks Defenses}
+\section{Approaches}
 \label{sec:defs}

### 2014-10-28 docs/questioning.tex
more on Section IV

@@
 and detect attacks based on specific criteria~\cite{D76,A00}.
-
 Both categories involve more than one subcategories.
 For every subcategory we provide elements regarding
-every dimension we described in
-Section~\ref{sec:dimensions}.
+every dimension described in Section~\ref{sec:dimensions}.
+
+Table~\ref{tab:comp} groups the various subcategories
+and for every mechanism provides the following:
+
+\begin{enumerate}
+\item The number of citations of the publication(s) where
+the mechanism was presented.
+\item Quadruples that show the values of true
+positives ({\sc tp}), true negatives ({\sc tn}),
+false positives ({\sc fp}), and false negatives
+({\sc tn}). For every quadruple there is a corresponding
+suffix that indicates whether the testbed was based
+on: real-world applications known to be vulnerable
+(r), synthetic benchmarks (s), both (a).
+If no testing has taken place we add a question
+mark (?).
+\item The computational overhead of the
+mechanism as stated in the publication.
+\item The attacks that the mechanism detects.
+\end{enumerate}
+
+\noindent
+{\sc na} (Not Available) means that a requirement is not
+mentioned in the paper. {\sc nq} (Not Quantified)
+indicates that a requirement is mentioned in the publication
+but it is not quantified.
+
+Table~\ref{tab:avail} presents
+our findings regarding the availability of the mechanism
+in terms of: source code and corresponding executables.
+We also examined the availability of the testbeds mentioned in the paper.
+The check mark (\tick) indicates that at some point within the publication,
+there is a homepage where the reader can refer to, to download the
+corresponding software. {\sc ao} (Available On-line) suggests that
+the software is available on-line but the address was not mentioned
+in the paper, which probably indicates that the authors made
+it available after the publication. The question mark (?),
+indicates that the a homepage for the software was included
+in the publication but now it is not available.
+
+Finally, as we mentioned in Subsection~\ref{sec:model},
+Figure~\ref{fig:attacks} illustrates in which step
+the mechanisms detect corresponding attacks.
 
@@
 \leavevmode
-\includegraphics[scale=0.57]{defenses.pdf}
+\includegraphics[scale=0.52]{defenses.pdf}
 \end{center}
@@
 \begin{table}
+    \caption{Comparison summary of mechanisms developed to counter application attacks.}
+    \label{tab:comp}
 \centering
@@
 	\begin{footnotesize}
-       	\item[1] {\sc na} (Not Available) means that a requirement is not even mentioned in the paper.
+       	\item[1] {\sc na} (Not Available) means that a requirement is not mentioned in the paper.
 	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
@@
     \end{tablenotes}
-    \caption{Comparison summary of mechanisms developed to counter application attacks.}
-    \label{tab:comp2}
     \end{small}
@@
 \begin{table*}
+\caption{Availability of the corresponding mechanisms.}
+    \label{tab:avail}
 \centering
@@
 	\begin{footnotesize}
-       \item[1] The check mark (\tick) indicates that some point within
-       the publication there is a homepage where the reader can refer to, to
+       \item[1] The check mark (\tick) indicates that the publication
+       includes a homepage where the reader can refer to, to
        download the corresponding software. {\sc ao} (Available On-line) suggests
@@
     \end{tablenotes}
-    \caption{Availability of the corresponding mechanisms.}
-    \label{tab:comp2}
     \end{small}

### 2014-10-28 docs/questioning.tex
more on Section the attack model

@@
 code injection attacks. Such attacks may involve source code, either of a
-Domain Specific Language ({\sc dsl}) or a Dynamic Language.
+{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
 
@@
 For example, the attacker could craft a malicious script into a {\sc url}
-and then trick an end user to click on it via social engineering
-(i.e., phishing). Alternatively, the attacker may be able to inject
+and then trick an end user to click on it via social engineering (i.e., phishing).
+({\sc step}: {\sc csrf} 1 \text{\textbar} {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1).
+Alternatively, the attacker may be able to inject
 directly the malicious code in the application. For example, consider
-a web application that accepts and redisplays data of uncertain origin
-without appropriate validation or filtering. An attacker could
+a web application that accepts and redisplays user input
+without appropriate validation. An attacker could
 upload data containing a specially crafted script (for example, in a
@@
 malicious {\sc sql} code to retrieve all the password entries from a
-database.
+database ({\sc step}: {\sc dsl} 1 \text{\textbar}
+{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
+Note that an {\sc xss} attack can start from both routes.
 
@@
 parse and display a page of results, without properly sanitizing the
-request. Thus, in a non-persistent {\sc xss} attack the injected code
+request ({\sc step}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
+Thus, in a non-persistent {\sc xss} attack the injected code
 never reaches the database and immediately becomes a part of the
@@
 If no testing has taken place we add a question
-mark (?).
+mark ({\bf ?}).
 \item The computational overhead of the
@@
 in the paper, which probably indicates that the authors made
-it available after the publication. The question mark (?),
+it available after the publication. The question mark ({\bf ?}),
 indicates that the a homepage for the software was included
@@
 Figure~\ref{fig:attacks} illustrates in which step
-the mechanisms detect corresponding attacks.
+of out attack model the mechanisms detect attacks.
 

### 2014-10-28 docs/questioning.tex
minor changes

@@
 and then trick an end user to click on it via social engineering (i.e., phishing).
-({\sc step}: {\sc csrf} 1 \text{\textbar} {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1).
+({\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
 Alternatively, the attacker may be able to inject
@@
 corresponding tuple that includes the step number for
-every attack. {\sc p-xss} stands for a persistent {\sc xss}
-attack and {\sc n-xss} stands for a non persistent {\sc xss}
-attack. Note that {\sc xss} attacks can also involve
+every attack. Note that {\sc xss} attacks can also involve
 {\it phishing}. Every {\it locus} indicates a step where mechanisms
@@
 
-\section{Approaches}
+\section{Defenses}
 \label{sec:defs}
@@
 Figure~\ref{fig:defenses} presents a taxonomy of the
-approaches that protect web applications against attacks based on
+defenses that protect web applications against attacks based on
 code injection vulnerabilities.

### 2014-10-28 docs/questioning.tex
ISR draft ready

@@
 Here we analyze the {\sc tba} different protection approaches.
+Note that most mechanisms that belong to this category have
+not been extensively tested in terms of diagnostic performance.
 
@@
 an augmented {\sc sql} grammar to detect the
-attack.
-
-In the case of {\sc xss} attacks that are based on JavaScript,
-consider a {\sc xor} function that encodes all JavaScript source of a web
+attack. {\sc sql}rand is one of the few mechanisms that
+detect {\sc sql} injection attacks on the database
+level (locus $\Omega$).
+
+In the case of {\sc xss} attacks that are based on JavaScript
+or {\sc html}, consider a {\sc xor} function that encodes all source of a web
 page on the server-side and then, on the client-side, the web browser decodes the
-source by applying the same function again.
+source by applying the same function again (locus {\sc x}).
 Variations of this approach include:
-{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}.
+{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
+which randomize the instruction set of {\sc html} and
+JavaScript respectively.
+
+{\sc isr} is a deterministic approach that can be applied
+to detect different attacks in an efficient manner.
+However, Sovarel et al.~\cite{SEP05}
+have investigated thoroughly the effectiveness
+of {\sc isr} and showed that a malicious user
+may be able to circumvent {\sc isr} by determining
+the randomization key and their results
+indicate that doing {\sc isr} in a way that
+provides a certain degree of security against a motivated
+attacker is more difficult than previously thought.
+
+In the case of Noncespaces, administrators must set
+specific policies in a manner similar to a firewall
+configuration language. This brings up questions
+concerning the diagnostic performance of the mechanism
+since the corresponding testing is insufficient
+(see Table~\ref{tab:comp}).
+
+Even though the above implementations impose a low
+computational overhead, they impose an infrastructure
+overhead. In particular, in the case of {\sc sql}rand
+the integration of a proxy within the database server
+is required while Noncespaces and x{\sc js} require
+modifications on both the server and the client.
 

### 2014-10-28 docs/questioning.tex
some changes

@@
 For example, the attacker could craft a malicious script into a {\sc url}
-and then trick an end user to click on it via social engineering (i.e., phishing).
-({\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
+and then trick an end user to click on it via social engineering (i.e., phishing ---
+{\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
 Alternatively, the attacker may be able to inject
@@
 our findings regarding the availability of the mechanism
-in terms of: source code and corresponding executables.
+in terms of source code and corresponding executables.
 We also examined the availability of the testbeds mentioned in the paper.
@@
 Finally, as we mentioned in Subsection~\ref{sec:model},
-Figure~\ref{fig:attacks} illustrates in which step
-of out attack model the mechanisms detect attacks.
+Figure~\ref{fig:attacks} illustrates the point where
+mechanisms detect attacks.
 
@@
 of {\sc isr} and showed that a malicious user
-may be able to circumvent {\sc isr} by determining
+may be able to circumvent it by determining
 the randomization key and their results

### 2014-10-28 docs/questioning.tex
paragraph change
work on training subcategory

@@
 \leavevmode
-\includegraphics[scale=0.55]{attacks-steps.pdf}
+\includegraphics[scale=0.57]{attacks-steps.pdf}
 \end{center}
@@
 JavaScript respectively.
+Contrary to x{\sc js}, in Noncespaces administrators must set
+specific policies in a manner similar to a firewall
+configuration language. This brings up questions
+concerning the diagnostic performance of the mechanism
+since the corresponding testing is insufficient
+(see Table~\ref{tab:comp}).
 
@@
 
-In the case of Noncespaces, administrators must set
-specific policies in a manner similar to a firewall
-configuration language. This brings up questions
-concerning the diagnostic performance of the mechanism
-since the corresponding testing is insufficient
-(see Table~\ref{tab:comp}).
-
 Even though the above implementations impose a low
@@
 
-Training methods that detect JavaScript-driven {\sc xss} attacks
-generate and store valid JavaScript code in various
-forms, and detect attacks as outliers from the set of valid code statements.
-{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
-original application. Then, a JavaScript detection component placed in a web proxy
-searches for injected scripts in the server's responses. If no injected scripts
-are found, the proxy decodes the legitimate scripts and sends them to the
-client.
-% dimitro: more mechanisms TBA.
-
-In the case of {\sc dsl}-driven injection attacks
-the various countermeasures follow a similar pattern.
+Training methods that detect {\sc dsl}-driven injection attacks
+generate and store valid code statements (i.e. {\sc sql}
+or {\sc xp}ath queries) in various forms, and detect attacks
+as outliers from the set of valid code statements.
 An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
@@
 as an extension of their anomaly detection framework called
-{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
+{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09} is
+a signature-based mechanism that prevents {\sc sql} and
+{\sc xp}ath injection attacks. The signatures generated
+during a training phase, are based on features that can
+depend either on the code statement or on its execution
+environment (i.e. the stack trace).
+Then, at runtime, the mechanism checks all statements for compliance
+and can block code statements containing injected elements (locus {\sc z}).
+% By associating a complete stack trace with the root of an {\sc sql} statement, 
+% the mechanism can correlate {\sc sql} statements with their call sites.  
+% This increases the specificity of the stored signatures and avoids false alarms.
 Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
@@
 diverge from the expected model.
-{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
-mechanism that prevents
-{\sc sql} and {\sc xp}ath injection attacks against web applications. 
-The signatures generated during a training phase,
-are based on features that can depend either on the
-code statement or on its execution environment (i.e. the stack trace).
-Then, at runtime, the mechanism checks all statements for compliance
-and can block code statements containing injected elements.
-By associating a complete stack trace with the root of an {\sc sql} statement, 
-the mechanism can correlate {\sc sql} statements with their call sites.  
-This increases the specificity of the stored signatures and 
-avoids false alarms. 
+% dimitro: more mechanisms TBA.
+
+In the case of JavaScript-driven {\sc xss} attacks
+the various countermeasures follow a similar pattern.
+{\it {\sc swap}}~\cite{WPLKK09} follows a similar approach
+with {\sc didafit} and creates a unique identifier
+({\it script {\sc id}}) for every legitimate script on the server.
+Then, a JavaScript detection component placed in a
+web proxy (locus {\sc y}) searches for injected scripts
+with no corresponding {\sc id} in the server's responses.
+If no injected scripts are found, the proxy forwards the
+request to the client.
 % dimitro: more mechanisms TBA.

### 2014-10-28 docs/questioning.tex
minor change

@@
 
-In the case of JavaScript-driven {\sc xss} attacks
-the various countermeasures follow a similar pattern.
-{\it {\sc swap}}~\cite{WPLKK09} follows a similar approach
-with {\sc didafit} and creates a unique identifier
-({\it script {\sc id}}) for every legitimate script on the server.
+In the case of {\sc xss} attacks the various countermeasures
+follow a similar pattern. {\it {\sc swap}}~\cite{WPLKK09}
+creates a unique identifier ({\it script {\sc id}}) for
+every legitimate script on the server.
 Then, a JavaScript detection component placed in a

### 2014-10-29 docs/questioning.tex
training draft ready

@@
 \usepackage[numbers,sort]{natbib}
+\lstset{columns=flexible,showstringspaces=false}
 
@@
 \subsubsection{Parse-Tree Validation}
+\label{sec:tree}
 
@@
 
-\subsubsection{Code Rewriting}
-
 \subsubsection{Instruction Set Randomization --- ISR}
 
-{\sc isr} is a method that contrary to the previous
-three, has been applied to counter
+{\sc isr} is a method that has been applied to counter
 different kinds of application attacks~\cite{K09b,KKP03}.
-The main idea behind the method, is to
+The main idea behind the it, is to
 separate code from data by randomizing the legitimate code's 
@@
 
+\subsubsection{Code Rewriting}
+
+{\it {\sc sm}ask}~\cite{JB07} is a mechanism that detects
+both {\sc sql} injection attacks and {\sc xss} attacks.
+To do this, it identifies malicious
+code by automatically separating user input from legitimate code.
+This is done by introducing specific syntactic constructs
+that handle server-side languages used for data management
+separately.
+
 \subsection{Behavior-Based}
@@
 An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
-{\sc sql} injection attacks by recording all database transactions.
+{\sc sql} injection (locus $\Omega$) attacks by recording all database transactions.
 Subsequent refinements by Valeur et al.~\cite{VMV05}
@@
 and can block code statements containing injected elements (locus {\sc z}).
-% By associating a complete stack trace with the root of an {\sc sql} statement, 
-% the mechanism can correlate {\sc sql} statements with their call sites.  
-% This increases the specificity of the stored signatures and avoids false alarms.
-Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
-injection attacks by associating a query model with the location of every
-{\sc sql} statement within the application. Then at runtime,
-monitors the application's execution to detect when {\sc sql} statements
-diverge from the expected model.
-% dimitro: more mechanisms TBA.
+Furthermore, {\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool
+that also detects {\sc sql} injection attacks (locus {\sc z})
+by associating a query model with the location of every
+{\sc sql} statement within the application.
+Then at runtime, monitors the application's execution to
+detect when {\sc sql} statements diverge from the expected model.
 
@@
 If no injected scripts are found, the proxy forwards the
-request to the client.
-% dimitro: more mechanisms TBA.
+request to the client. This mechanism is relatively
+inflexible since it does not support dynamic scripts.
+In addition it imposes a significant overhead (see Table~\ref{tab:comp}).
+The authors of {\it {\sc xssds}}~\cite{JEP08}
+have implemented a similar mechanism that also supports
+dynamic and external scripts. Specifically,
+during training phase they build a list of all benign scripts.
+In the case of external scripts they keep a white list
+of all the valid domain names that contain scripts
+used by the application.
+
+The training subcategory, includes some mechanisms
+that can be easily circumvented. For example,
+consider an application that will send the password 
+for a forgetful user via email by executing
+the following query:
+\bgroup
+\lstset{language=SQL}
+\begin{small}
+\begin{lstlisting}
+SELECT password from userdata WHERE id = 'Alice'
+\end{lstlisting}
+\end{small}
+\egroup
+\noindent
+This same application could allow users to lock their terminal,
+but allow the unlocking either with the user's password or with
+the administrator password (the 4.3 {\sc bsd} {\em lock} command
+behaved in this peculiar way).
+The corresponding query to verify the password on the locked
+workstation would be as follows:
+\bgroup
+\lstset{language=SQL}
+\begin{small}
+\begin{lstlisting}
+SELECT password from userdata WHERE id = 'Alice' OR
+id = 'admin'
+\end{lstlisting}
+\end{small}
+\egroup
+\noindent
+A traditional {\sc sql} injection attack protection system like {\sc didafit},
+could be easily escaped since a malicious user, could obtain the
+administrator's password by email by entering on the password retrieval form
+as his user identifier the following:
+\bgroup
+\lstset{language=SQL}
+\begin{small}
+\begin{lstlisting}
+nosuchuser' OR id = 'admin
+\end{lstlisting}
+\end{small}
+\egroup
+\noindent
+However, mechanisms that create signatures that involve
+elements not only associated with the code statements
+(i.e. {\sc amnesia} and {\sc sd}river)
+could detect such attacks. Specifically,
+{\sc sd}river associates a complete stack trace with the
+root of an {\sc sql} statement, thus it can correlate
+queries with their call sites and detect attacks
+like the aforementioned one.
+In a similar manner, training tools that detect
+{\sc xss} attacks based on JavaScript injection
+would fail to detect a mimicry attack like the
+one mentioned in Subsubsection~\ref{sec:tree}.
+
+In general, the detection accuracy of training approaches is
+heavily based on the coverage that is achieved during the
+training phase. If the coverage is insufficient the
+production of false alarms is very likely.
+In addition, when a code statement is altered, a new
+training phase is necessary.
+
+All the above mechanisms are relatively easy to deploy.
+{\sc dsl} injection attack countermeasures
+can be retrofitted to a system typically by changing
+some configuration files. This does not apply
+to {\sc amnesia} though, since significant source code
+modifications are required for every query that exists
+in the application. Finally, {\sc swap} and {\sc xssds}
+are implemented within a proxy on the server-side.
 
@@
 \begin{table}
-    \caption{Comparison summary of mechanisms developed to counter application attacks.}
+    \caption{Comparison summary of mechanisms developed to counter application attacks based on executable source code injection.}
     \label{tab:comp}
@@
     \hline
-  \multirow{2}{*}{Parse-Tree Validation}
+  \multirow{3}{*}{Parse-Tree Validation}
   &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
   &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
+  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
   \hline
@@
   \hline         
-  \multirow{3}{*}{Code Rewriting}
+  \multirow{4}{*}{Code Rewriting}
   &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
   &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
   &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
@@
 	\hline  
-  \multirow{9}{*}{Training}
+  \multirow{7}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
@@
 	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
 	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\
-  & 	{\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
   & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
@@
   &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
-  \hline  
-  \hline 
-  \hline
-  \multirow{3}{*}{Code Rewriting}
+  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline  
+  \hline 
+  \hline
+  \multirow{4}{*}{Code Rewriting}
   &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
   &   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
   &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
@@
 	\hline  
-        \multirow{9}{*}{Training}
+        \multirow{7}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
@@
 	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	& 	{\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
 	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
-  & 	{\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
   & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\

### 2014-10-29 docs/questioning.tex
started parse-tree validation

@@
 \leavevmode
-\includegraphics[scale=0.57]{attacks-steps.pdf}
+\includegraphics[scale=0.61]{attacks-steps.pdf}
 \end{center}
@@
 
-The mechanism based on this method compare the parse tree of a
-query before the inclusion of user input with the one resulting after
-the inclusion of user input. If the trees diverge, the application
-is probably under attack.
+The key idea behind this approach, is to compare
+the tree representation of the abstract syntactic
+structure of the executable source code that is
+about to be executed with the one hat was originally intended.
+If the trees diverge, the application is probably under attack.
+
+In the case of {\sc dsl} injection attacks, mechanisms check 
+the query before the inclusion of user input with the one
+resulting after the inclusion of user input.
 
@@
 
-\subsubsection{Instruction Set Randomization --- ISR}
+\subsubsection{Instruction Set Randomization (ISR)}
 

### 2014-10-29 docs/questioning.tex
first draft of parse-tree validation, also added new subsection: Hybrid

@@
 
+\begin{figure*} [ht]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.62]{defenses.pdf}
+\end{center}
+\caption{\label{fig:defenses}The basic categories of web application
+attack countermeasures ({\sc draft}).}
+\end{figure*}
+
 Figure~\ref{fig:defenses} presents a taxonomy of the
@@
 code injection vulnerabilities.
-We can identify two main approaches, namely:
-{\it design-based} and {\it behavior-based}.
-The former involves mechanisms that make applications
+We can identify three main approaches, namely:
+{\it design-based}, {\it behavior-based}
+and {\it hybrid}.
+The design-based category involves mechanisms that make applications
 immune to different attack vectors by design~\cite{JL75,L81}.
-The latter incorporates a variety of methods and
+The behavior-based incorporates a variety of methods and
 schemes that inspect the behavior of applications
@@
 Both categories involve more than one subcategories.
+The hybrid category borrows elements from more than one subcategories.
 For every subcategory we provide elements regarding
@@
 the tree representation of the abstract syntactic
-structure of the executable source code that is
-about to be executed with the one hat was originally intended.
-If the trees diverge, the application is probably under attack.
+structure of the executable source code
+with the one that was originally intended.
+If the trees diverge, the application is probably
+under attack.
 
@@
 resulting after the inclusion of user input.
+Both mechanisms that implement this approach,
+{\sc sqlg}uard~\cite{BWS05} and
+{\sc sql}check~\cite{SW06} are pretty similar
+and detect the attack before a query reaches the
+database (locus {\sc z}).
+Contrary to {\sc sqlg}uard~\cite{BWS05} (and many other
+mechanisms), {\sc sql}check~\cite{SW06} has been
+extensively tested in terms of diagnostic performance
+as seen in Table~\ref{tab:comp}. A disadvantage of
+those mechanisms is that the application must be modified
+every time a query is about to be sent to a database
+for execution.
+
+As we will see in Subsection~\ref{sec:hybrid},
+there are mechanisms that borrow elements from
+this approach and examine the syntax trees
+of scripts to detect JavaScript-driven {\sc xss}.
 
@@
 using randomized instructions instead of standard keywords.
-The modified queries are either reconstructed at runtime using
-the same key that is inaccessible to the malicious user,
-or the user input is tagged with delimiters that allow
-an augmented {\sc sql} grammar to detect the
-attack. {\sc sql}rand is one of the few mechanisms that
+The modified queries are reconstructed at runtime using
+the same key that is inaccessible to the malicious user.
+{\sc sql}rand is one of the few mechanisms that
 detect {\sc sql} injection attacks on the database
@@
 attacker is more difficult than previously thought.
+Furthermore, developers who wish to use
+such mechanisms must follow good coding practices
+and never show a randomized code statement in any case
+(i.e. an exception error) because in this way
+they will reveal the encoding key.
 
@@
 
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.52]{defenses.pdf}
-\end{center}
-\caption{\label{fig:defenses}The basic categories of web application
-attack countermeasures ({\sc draft}).}
-\end{figure*}
+\subsection{Hybrid}
+\label{sec:hybrid}
+
+{\sc xss-guard}~\cite{BV08}
+maps legitimate scripts to {\sc http} responses.
 
@@
   \multirow{3}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & +6.5{\it ms} & {\sc sql} injection \\ 
+  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} & {\sc sql} injection \\ 
   &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
@@
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
+  \hline
+  \hline
+  \multirow{1}{*}{Hybrid}
+  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
 	\hline

### 2014-10-29 docs/questioning.tex
some changes

@@
 and detect attacks based on specific criteria~\cite{D76,A00}.
-Both categories involve more than one subcategories.
-The hybrid category borrows elements from more than one subcategories.
-For every subcategory we provide elements regarding
-every dimension described in Section~\ref{sec:dimensions}.
-
+Hybrid mechanisms borrow characteristics from both categories.
 Table~\ref{tab:comp} groups the various subcategories
@@
 
+\subsubsection{Policy Enforcement}
+
+In this method, developers must define
+specific security policies on the server side.
+Then the policies are enforced either in the user's
+browser at runtime or in a server-side proxy that
+intercepts server responses.
+
 \subsubsection{Instruction Set Randomization (ISR)}
@@
 
-\subsubsection{Code Rewriting}
-
-{\it {\sc sm}ask}~\cite{JB07} is a mechanism that detects
-both {\sc sql} injection attacks and {\sc xss} attacks.
-To do this, it identifies malicious
-code by automatically separating user input from legitimate code.
-This is done by introducing specific syntactic constructs
-that handle server-side languages used for data management
-separately.
-
 \subsection{Behavior-Based}
@@
 the information flow characteristics of the system to which it is applied.
-
-\subsubsection{Policy Enforcement}
-
-In this method, developers must define
-specific security policies on the server side.
-Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that
-intercepts server responses.
 
@@
 would fail to detect a mimicry attack like the
-one mentioned in Subsubsection~\ref{sec:tree}.
+one mentioned in Subsubsection {\sc tba}.
 
@@
 \label{sec:hybrid}
+
+{\it {\sc sm}ask}~\cite{JB07} is a mechanism that detects
+both {\sc sql} injection attacks and {\sc xss} attacks.
+To do this, it identifies malicious
+code by automatically separating user input from legitimate code.
+This is done by introducing specific syntactic constructs
+that handle server-side languages used for data management
+separately.
 
@@
     \hline
-  \multirow{3}{*}{Parse-Tree Validation}
+  \multirow{2}{*}{Parse-Tree Validation}
   &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
   &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
-  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
   \hline
@@
   \hline
-  \multirow{3}{*}{{\sc isr}}
+  \multirow{4}{*}{{\sc isr}}
   &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} & {\sc sql} injection \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
   &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
   &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
-  \hline
-  \hline         
-  \multirow{4}{*}{Code Rewriting}
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
   \hline
@@
   \hline 
-	\multirow{7}{*}{Policy Enforcement}
+	\multirow{10}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
@@
   &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
   &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
 	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
 	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\

### 2014-10-30 docs/questioning.tex
work on policy enforcement

@@
 
-\subsubsection{Securing Mashups}
-
 \subsubsection{Policy Enforcement}
 
-In this method, developers must define
+This approach is used to detect attacks that target web users.
+When using a framework that implements
+this approach, developers must define
 specific security policies on the server side.
 Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that
-intercepts server responses.
+browser at runtime or in a server-side proxy that intercepts
+server responses. Policy enforcement is one of the two
+approaches (the other is Securing Mashups) that is
+used to prevent {\sc csrf} attacks.
+
+A number of the frameworks define policies
+based on information and features provided by
+the Document Object Model ({\sc dom}) of a web page.
+Specifically, developers must place all legitimate
+scripts inside {\sc html} elements like {\tt div}.
+The web browser (locus {\sc x}), parses the
+{\sc dom} tree and executes scripts only when they
+are contained in such elements. All other scripts
+are treated according to the policies defined
+on the server. Frameworks that support the
+above functionality are {\sc beep}~\cite{TNH07}
+and {\sc dsi}~\cite{NSS06}.
+The main problem with the above mechanisms is
+that they are vulnerable to non-persistent {\sc xss}
+attacks that alter the {\sc dom} of an already rendered
+page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
+~\cite{APKLM10}.
+
+% There are also frameworks that introduce
+% policies directly in the scripts that exist in the server.
+
+% controlling information flows: {\sc soma}~\cite{OWVS08}
+% and Noxes~\cite{KKVJ06,KJKV09} (the client defines policies).
+
+\subsubsection{Securing Mashups}
 
@@
 
+{\it Blueprint}~\cite{LV09}.
+
 \begin{landscape}
@@
   \hline
-  \multirow{4}{*}{{\sc isr}}
+  \multirow{3}{*}{{\sc isr}}
   &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} & {\sc sql} injection \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
   &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
@@
   \hline 
-	\multirow{10}{*}{Policy Enforcement}
+	\multirow{9}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
@@
   &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
-	&   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\
   &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
@@
   \hline
-  \multirow{1}{*}{Hybrid}
+  \multirow{3}{*}{Hybrid}
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
   &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
+  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\
 	\hline

### 2014-10-30 docs/questioning.tex
minor addition
more on policy enforcement

@@
 attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
-malicious users can perform other exploits based on {\sc dsl}s, like
-{\sc xp}ath~\cite{SW06,CDL07,MKS09} and {\sc xml}~\cite{MSM13}. With
-this kind of attacks, a malicious user can view sensitive information,
+malicious users can perform other exploits based on {\sc dsl}s,
+like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
+and No{\sc sql}~\cite{SMS13}. With this kind of attacks,
+a malicious user can view sensitive information,
 destroy or modify protected data, or even crash the entire
@@
 this approach and examine the syntax trees
-of scripts to detect JavaScript-driven {\sc xss}.
+of scripts to detect JavaScript-driven {\sc xss} attacks.
 
@@
 are treated according to the policies defined
-on the server. Frameworks that support the
-above functionality are {\sc beep}~\cite{TNH07}
-and {\sc dsi}~\cite{NSS06}.
-The main problem with the above mechanisms is
-that they are vulnerable to non-persistent {\sc xss}
-attacks that alter the {\sc dom} of an already rendered
+on the server. Frameworks that support this
+functionality are {\sc beep}~\cite{TNH07}
+and {\sc dsi}~\cite{NSS06}. The main problem with
+the above mechanisms is that they are vulnerable
+to non-persistent {\sc xss} attacks that alter
+the {\sc dom} of an already rendered
 page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
@@
 
-% There are also frameworks that introduce
-% policies directly in the scripts that exist in the server.
+Another policy enforcement approach introduces
+policies directly either in {\sc html} or JavaScript code
+to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
+acts as a proxy on the server side (locus {\sc y}) to
+parse the {\sc html} of server responses and identifies
+scripts. Then, it rewrites them into safe equivalents
+and protect the web user from exploitations
+that are based on reported browser vulnerabilities.
+{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
+and the framework by {\it Phung et al.}~\cite{PSC09}
+extend JavaScript with new primitive functions to
+provide safe methods to protect potentially vulnerable
+JavaScript functions. In both cases, policy enforcement takes
+place on the JavaScript engine of the browser (locus {\sc x}).
+In this way, {\sc xxs} attacks that take advantage
+functions like {\tt eval} and {\tt write} that are
+used to assemble innocuous-looking parts into harmful
+strings would fail. A critical issue regarding
+the above frameworks is that they cannot
+define policies that restrict the behavior of third-party
+scripts introduced by script inclusion and {\tt iframe}
+tags. For instance, consider a web page ({\tt foo.net})
+that prints the value of the a query parameter ({\tt query})
+from the page's {\sc url} in the web page's content
+without escaping the value. A malicious user
+can take advantage of this and inject JavaScript code
+into the page to steal the user's cookie for this particular
+page and send it via an image request to a web site
+that he or she controls ({\tt malicious.com}).
+This could be achieved by including the following
+code fragment to the malicious web site:
+
+\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
+\begin{lstlisting}
+<iframe style="position:absolute;top:-9999px"
+    src="http://foo.net/vulnerable.html?query=
+    <script>document.write(
+    '<img src=\"http://malicious.com/?c=
+    '+encodeURIComponent(document.cookie)+'\">')
+    </script>"></iframe>
+\end{lstlisting}
+
+\noindent
+By using the {\tt iframe} tag, the web user will not
+realise the redirection. 
+This problem is actually solved by the architectures
+presented in Subsubsection~~\ref{sec:mashups}.
+
+%{\it j{\sc csrf}}~\cite{PS11}.
 
@@
 \subsubsection{Securing Mashups}
+\label{sec:mashups}
+
+{\it WebJail}~\cite{VDDPJ11}, overcomes this issue
+by containing the functionality of third-party scripts.
 
@@
   \hline
-  \multirow{5}{*}{Securing Mashups}
+  \multirow{9}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
+  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
+  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
+  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
+  \hline
+  \hline 
+  \multirow{3}{*}{Securing Mashups}
   &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
   &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
   &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
-  &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
   \hline
@@
 	\hline  
-	\multirow{9}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
-	&   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
-	&   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
-  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
-  % TODO@dimitro: discuss this with Panos?
-	\hline
-	\hline  
-  \multirow{7}{*}{Training}
+  \multirow{6}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\

### 2014-10-30 docs/questioning.tex
some corrections

@@
 without escaping the value. A malicious user
-can take advantage of this and inject JavaScript code
-into the page to steal the user's cookie for this particular
-page and send it via an image request to a web site
+can take advantage of this and inject an {\tt iframe}
+into the page to steal the user's cookie and
+send it via an image request to a web site
 that he or she controls ({\tt malicious.com}).
 This could be achieved by including the following
-code fragment to the malicious web site:
+link to the malicious web site (or send it via phishing)
+and induce the user to click on it:
 
@@
 \begin{lstlisting}
-<iframe style="position:absolute;top:-9999px"
-    src="http://foo.net/vulnerable.html?query=
-    <script>document.write(
+http://foo.net/vulnerable.html?query=
+<iframe src="javascript:document.body.innerHTML=+
 '<img src=\"http://malicious.com/?c=
-    '+encodeURIComponent(document.cookie)+'\">')
-    </script>"></iframe>
+'+encodeURIComponent(document.cookie)+'\">'">
+</iframe>
 \end{lstlisting}
@@
 \noindent
-By using the {\tt iframe} tag, the web user will not
-realise the redirection. 
-This problem is actually solved by the architectures
-presented in Subsubsection~~\ref{sec:mashups}.
+{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
+can actually detect such an attack (along with some architectures
+presented in Subsubsection~~\ref{sec:mashups}).
+To achieve this, {\sc soma} requires site administrators
+to specify legitimate, external domains for sending
+or receiving information in order to approve interactions
+between them and the protected web site.
 

### 2014-10-31 docs/questioning.tex
new CSRF defences
updated the availability table

@@
 there is a homepage where the reader can refer to, to download the
-corresponding software. {\sc ao} (Available On-line) suggests that
+corresponding software. {\bf AO} (Available On-line) suggests that
 the software is available on-line but the address was not mentioned
@@
 or receiving information in order to approve interactions
-between them and the protected web site.
+between them and the protected web site. As a result,
+{\sc soma} can also detect {\sc csrf} attacks.
 
@@
   \hline
-  \multirow{9}{*}{Policy Enforcement}
+  \multirow{12}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
+  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\bf ?} & {\sc csrf} \\
   &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
@@
   &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf}\\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf} \\
+  &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
   &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
   &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & & & {\bf ?} & {\sc csrf} \\
   &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
@@
     \hline
-	\multirow{9}{*}{Runtime Tainting}
-	&  	{\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
-	% &  	{\it SecuriFly}~\cite{MLL05}  & - & - & - \\
-	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
-  &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\sc ao} & {\sc na} & {\sc ao} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
+  \hline  
+  \hline
+  \multirow{12}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it NoForge}~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it CoreScript}~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
+  &   {\it ConScript}~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
+  &   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
+    % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline 
+  \multirow{3}{*}{Securing Mashups}
+  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
   \hline
@@
   \hline 
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\sc ao} & {\sc ao} & {\sc na} \\
-  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline  
-  \hline 
-  \hline
-  \multirow{4}{*}{Code Rewriting}
-  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it CoreScript}~\cite{YCIS07} & {\sc ao} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
-  \hline
-  \hline 
-  \multirow{5}{*}{Securing Mashups}
-  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it ConScript}~\cite{ML10} & {\sc ao} & {\sc na} & {\sc na} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline
-	\multirow{7}{*}{Policy Enforcement}
-	&   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	&   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
-   	% &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
-	\hline
-	\hline  
-        \multirow{7}{*}{Training}
+	\multirow{8}{*}{Runtime Tainting}
+	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
+  &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline 
+  \multirow{6}{*}{Training}
   &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\sc ao} & {\sc na} \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
 	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
@@
 	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
-	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  \hline
+  \hline
+  \multirow{3}{*}{Hybrid}
+  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
 	\hline
@@
        includes a homepage where the reader can refer to, to
-       download the corresponding software. {\sc ao} (Available On-line) suggests
+       download the corresponding software. {\bf AO} (Available On-line) suggests
        that the software is available on-line but the

### 2014-10-31 docs/questioning.tex
More work on policy enforcement

@@
 server responses. Policy enforcement is one of the two
-approaches (the other is Securing Mashups) that is
+approaches (the other is Securing Mashups --- see
+Subsubsection~\ref{sec:mashups}) that is
 used to prevent {\sc csrf} attacks.
+
+{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
+framework that partially allows the web
+user to specify policies to prevent {\sc xss} attacks.
+The key idea behind Noxes is to parse
+the {\sc html} that reaches the browser to
+find static {\sc url} references. Then, based on
+a set of policies it allows or blocks
+the request (locus {\sc x}). Such policies
+are provided either by the user or by
+the framework itself. Noxes does not
+deal with JavaScript-driven {\sc xss}
+attacks and it is a rather simplistic approach.
 
@@
 This could be achieved by including the following
-link to the malicious web site (or send it via phishing)
-and induce the user to click on it:
+link to the malicious web site (or send it via phishing
+email) and induce the user to click on it:
 
@@
 
-{\it WebJail}~\cite{VDDPJ11}, overcomes this issue
-by containing the functionality of third-party scripts.
+% {\it WebJail}~\cite{VDDPJ11}, overcomes this issue
+% by containing the functionality of third-party scripts.
 
@@
 	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 3 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline

### 2014-10-31 docs/questioning.tex
policy enforcement draft ready

@@
 as we mentioned in the previous paragraph.
+
 In our research we focus on the top
-{\sc tba} systems that counter application attacks,
-in terms of citations.
+{\sc tba} systems that and are presented
+in publications cited more than twenty times.
+For the sake of our study, we choose
+to make some exceptions and include some latest mechanisms
+that were presented in top security conferences even if
+the corresponding publications have been cited less than
+twenty times.
 
@@
 mainly because they are associated with major vulnerabilities such as:
-{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{LZRL09} and
+{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{BJM08,LZRL09} and
 Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
@@
 \leavevmode
-\includegraphics[scale=0.62]{defenses.pdf}
+\includegraphics[scale=0.65]{defenses.pdf}
 \end{center}
@@
 
-%{\it j{\sc csrf}}~\cite{PS11}.
-
-% controlling information flows: {\sc soma}~\cite{OWVS08}
-% and Noxes~\cite{KKVJ06,KJKV09} (the client defines policies).
+Policy enforcement mechanisms that detect {\sc csrf}
+attacks are usually implemented in the form of a
+server-side proxy (locus {\sc y})
+interposing on the client-server communication, and modifying
+it. {\it NoForge}~\cite{JKK06a}
+parses the {\sc html} server responses
+and adds a token to every {\sc url} referring to this
+server. Then it associates the token with the cookie
+representing the session {\sc id} for the application.
+When a request is received, the mechanism checks
+if the request contains the token related
+to the session {\sc id}. A disadvantage of NoForge
+is that {\sc html} that is dynamically created within
+the browser will not include the token.
+Thus, sites that create their {\sc html} on the client
+will remain vulnerable. In addition, it does not
+support cross-origin requests.
+{\it j{\sc csrf}}~\cite{PS11}
+has a very similar functionality and meanwhile
+addresses the above problems.
+Finally, {\it CsFire}~\cite{DDHPJ10}
+examines cross-domain interactions,
+to design a cross-domain policy.
+The policy is based on the concept of a relaxed
+same-origin policy that allows communication between
+sub-domains of the same registered domain.
+
+Most of the aforementioned frameworks, involve
+several deployment issues since they
+require significant source modifications by the web
+developers in order to introduce their policies.
 
@@
   \hline
-  \multirow{12}{*}{Policy Enforcement}
+  \multirow{11}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
@@
   &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf} \\
-  &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
+  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
   &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
@@
 
+ We need to mention that there are mechanisms that
+ do not need to be established purely through testing
+ Since they provide systematic arguments as to why
+ the design is secure against attacks.
+
 \begin{table*}
@@
   \hline
-  \multirow{12}{*}{Policy Enforcement}
+  \multirow{11}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
@@
   &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
   &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\

### 2014-11-01 docs/questioning.tex
some changes

@@
 
-Here we analyze the {\sc tba} different protection approaches.
-Note that most mechanisms that belong to this category have
-not been extensively tested in terms of diagnostic performance.
+Here we analyze the three basic design-based approaches
+used to protect web applications from the attacks we
+discussed in Section~\ref{sec:attacks}.
 
@@
 browser at runtime or in a server-side proxy that intercepts
-server responses. Policy enforcement is one of the two
-approaches (the other is Securing Mashups --- see
-Subsubsection~\ref{sec:mashups}) that is
-used to prevent {\sc csrf} attacks.
+server responses.
 
@@
 the {\sc dom} of an already rendered
-page\footnote{\url{https://www.owasp.org/index.php/DOM_Based_XSS}}
-~\cite{APKLM10}.
+page~\cite{APKLM10}.
 
@@
 \noindent
-{\sc soma}~\cite{OWVS08} is a policy enforcement framework that
-can actually detect such an attack (along with some architectures
-presented in Subsubsection~~\ref{sec:mashups}).
+{\it WebJail}~\cite{VDDPJ11}, and
+{\sc soma}~\cite{OWVS08} are two frameworks that
+can actually detect such an attack (locus {\sc x}).
 To achieve this, {\sc soma} requires site administrators
@@
 {\sc soma} can also detect {\sc csrf} attacks.
+WebJail contains the functionality of third-party scripts
+by introducing a web component integrator that restricts
+the access that these scripts may have to either the data
+or the functionality of other components.
 
@@
 developers in order to introduce their policies.
-
-\subsubsection{Securing Mashups}
-\label{sec:mashups}
-
-% {\it WebJail}~\cite{VDDPJ11}, overcomes this issue
-% by containing the functionality of third-party scripts.
 
@@
   \hline
-  \multirow{11}{*}{Policy Enforcement}
+  \multirow{12}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
@@
   &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
   % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
-  \hline
-  \hline 
-  \multirow{3}{*}{Securing Mashups}
-  &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
-  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
+  % \hline
+  % \hline 
+  % \multirow{3}{*}{Securing Mashups}
+  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
+  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
   \hline
@@
 
- We need to mention that there are mechanisms that
+Notes:
+\begin{enumerate}
+\item Note that most mechanisms that implement design-based
+approaches have not been extensively tested in terms of
+diagnostic performance.
+\item We need to mention that there are mechanisms that
 do not need to be established purely through testing
@@
 the design is secure against attacks.
+\item Policy enforcement is the
+only approach that is
+used to prevent {\sc csrf} attacks.
+\item See j{\sc csrf} for {\sc soma}'s drawbacks.
+\end{enumerate}
 
@@
   \hline
-  \multirow{11}{*}{Policy Enforcement}
+  \multirow{12}{*}{Policy Enforcement}
   &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
@@
   &   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
     % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline 
-  \multirow{3}{*}{Securing Mashups}
-  &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+  % \hline
+  % \hline 
+  % \multirow{3}{*}{Securing Mashups}
+  % &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
   % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\

### 2014-11-02 docs/questioning.tex
work on runtime tainting

@@
 
-Runtime tainting is based on data-flow analysis.
-In practice, it enforces security policies by marking untrusted
-(``tainted") data and tracing its flow through the program.
-Since information flow in a system cannot be verified by examining
-a single execution trace of the system, the results of taint
-analysis will necessarily reflect approximate information regarding
-the information flow characteristics of the system to which it is applied.
+A runtime tainting scheme marks untrusted
+(``tainted") data (for instance, a variable set
+by a field in a web form) and traces its flow through
+the program. If the variable is used in an expression
+that sets another variable, that variable is also
+marked as untrusted and so on. If any of these variables
+is used to execute a potentially risky command (``sink") the
+scheme may act accordingly.
+
+Runtime tainting is provided as a feature in some
+programming languages, such as Perl and Ruby.
+By enabling the feature, Perl would refuse to run code
+vulnerable to an {\sc sql} injection attack
+(consider a tainted variable being used in a query)
+and exit with an error message.
+
+There are different implementations of these approach
+in terms of how the tainted data is marked and observed,
+and how attacks are detected.
+For example, {\it Haldar et al.}~\cite{HCF05} have implemented
+their scheme for the Java Virtual Machine ({\sc jvm})
+where they instrument various classes. When a
+tainted string is used as an argument to a sink method
+then an exception is raised (locus {\sc z}). However, this is a simplistic
+approach that may lead to many false positives.
+{\sc csse}~\cite{PB05} and the scheme by {\it Xu et al.}~\cite{XBS06}
+apply further checks when they identify that tainted data
+have reached a sink. In particular, {\sc csse} associates
+tainted data with specific metadata. Such metadata include
+the origins of tainted data, its propagation within the application
+and other. When tainted data reaches a sink {\sc csse} performs
+syntactic checks it based on the aforementioned metadata
+(locus {\sc z}).
+
+% As the author of {\sc csse} state~\cite{PB05}, the prevention
+% of {\sc xss} attack requires a more complex analysis.
 

### 2014-11-02 docs/questioning.tex
more on tainting

@@
 require significant source modifications by the web
-developers in order to introduce their policies.
+developers in order to introduce policies.
 
@@
 approach that may lead to many false positives.
-{\sc csse}~\cite{PB05} and the scheme by {\it Xu et al.}~\cite{XBS06}
+{\sc csse}~\cite{PB05} and the system by {\it Xu et al.}~\cite{XBS06}
 apply further checks when they identify that tainted data
-have reached a sink. In particular, {\sc csse} associates
+have reached a sink. In particular, {\it Xu et al.}~\cite{XBS06}
+tracks taint information at the level of bytes in memory.
+To distinguish between legitimate and malicious uses
+of untrusted data that reach a sink,
+they search the data for suspicious symbols by using
+regular expressions. {\sc csse} associates
 tainted data with specific metadata. Such metadata include
@@
 syntactic checks it based on the aforementioned metadata
-(locus {\sc z}).
+(locus {\sc z}). {\it Xu et al.}~\cite{XBS06}
+have proposed a 
+In the case of {\sc dsl}-driven injection attacks,
+the above implementations can be efficient. However, this
+does not apply in the case of JavaScript injection.
+Currently, with the wide use of JavaScript these mechanisms
+would produce numerous false alarms because instead
+of checking for tainted variables ``in" scripts,
+they look inside {\sc html} responses ``for" scripts.
 

### 2014-11-03 docs/questioning.tex
runtime tainting draft ready

@@
 used to assemble innocuous-looking parts into harmful
-strings would fail. A critical issue regarding
+strings would fail.
+
+A critical issue regarding
 the above frameworks is that they cannot
@@
 tainted string is used as an argument to a sink method
-then an exception is raised (locus {\sc z}). However, this is a simplistic
-approach that may lead to many false positives.
-{\sc csse}~\cite{PB05} and the system by {\it Xu et al.}~\cite{XBS06}
-apply further checks when they identify that tainted data
-have reached a sink. In particular, {\it Xu et al.}~\cite{XBS06}
+then an exception is raised (locus {\sc z}).
+However, this is a simplistic approach that may
+lead to many false positives.
+
+The following schemes apply further checks when
+they identify that tainted data have reached a sink.
+In particular, {\it Xu et al.}~\cite{XBS06}
 tracks taint information at the level of bytes in memory.
@@
 they search the data for suspicious symbols by using
-regular expressions. {\sc csse} associates
+regular expressions. {\sc csse}~\cite{PB05} associates
 tainted data with specific metadata. Such metadata include
@@
 syntactic checks it based on the aforementioned metadata
-(locus {\sc z}). {\it Xu et al.}~\cite{XBS06}
-have proposed a 
-In the case of {\sc dsl}-driven injection attacks,
-the above implementations can be efficient. However, this
-does not apply in the case of JavaScript injection.
-Currently, with the wide use of JavaScript these mechanisms
-would produce numerous false alarms because instead
-of checking for tainted variables ``in" scripts,
-they look inside {\sc html} responses ``for" scripts.
-
+(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
+in a similar way. To obtain metadata, it takes advantage
+of specific features provided by {\sc php}.
+Note that the above schemes detect potential attacks
+in locus {\sc z}. This automatically means that they
+cannot detect non-persistent JavaScript-driven
+{\sc xss} attacks. {\sc wasc}~\cite{NLC07} 
+though, can deal with such attacks because it
+analyzes {\sc html} responses to check
+if there are tainted data that contain scripts (locus {\sc y}).
+A recent study showed that there are ways to circumvent
+the majority of the above schemes~\cite{NBR14}.
+Furthermore, most of them are hard to deploy since
+the majority of input vectors, string operations
+and output vectors must be instrumented.
+
+{\it Vogt et al.}~\cite{VFJKKV07}
+have developed a tainting scheme that follows a different
+approach. Contrary to the aforementioned schemes that
+operate on the server side, they track taint sensitive
+information on the client side (locus {\sc x}).
+This is a form of positive taint tracking, where
+taint data is considered to be legitimate.
+In essence, they detect JavaScript-driven {\sc xss}
+attacks by ensuring that a script can send sensitive
+user data only to the site from which it came from.
+This though, may lead to false alarms.
+{\it Stock et al.}~\cite{SLMS14} propose a scheme
+that also operates in the browser (locus {\sc x}).
+The scheme focuses on the detection of
+{\sc dom}-based {\sc xss} attacks.
+In such an attack, the malicious payload is
+executed as a result of the modification of the
+{\sc dom} environment so that the client-side
+code runs in an unanticipated manner even if the
+{\sc http} response that triggers the injection seems legitimate.
+The scheme is different to the previous one because it
+marks and observes data that are considered harmful.
+Specifically, it employs a taint-enhanced JavaScript
+engine that tracks the flow of attacker-controlled data.
+To detect potential attacks the scheme utilizes
+{\sc html} and JavaScript parsers that can
+identify the generation of code coming from
+tainted data.
+
+% @dimitro: move this to the analysis Section:
+% This scheme is an efficient scheme that focuses
+% on a specific category of {\sc xss} attacks and
+% takes into consideration many attack vectors
+% that many of the previous schemes do not.
+% Also: 
 % As the author of {\sc csse} state~\cite{PB05}, the prevention
@@
 like the aforementioned one.
-In a similar manner, training tools that detect
-{\sc xss} attacks based on JavaScript injection
-would fail to detect a mimicry attack like the
-one mentioned in Subsubsection {\sc tba}.
 
@@
 {\it Blueprint}~\cite{LV09}.
+
+{\it Diglossia}~\cite{SMS13} performs positive taint tracking and
+parse-tree validation.
 
@@
   &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & & & {\bf ?} & {\sc csrf} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{3} & {\bf ?} & {\sc csrf} \\
   &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
@@
   \hline
-	\multirow{8}{*}{Runtime Tainting}
+	\multirow{7}{*}{Runtime Tainting}
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
@@
 	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
   \hline
-  \multirow{3}{*}{Hybrid}
+  \multirow{4}{*}{Hybrid}
   &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
@@
   &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
 	If no testing has taken place we add a question mark ({\bf ?}).
+    \item[3] The number involve requests.
 	\end{footnotesize}
@@
   \hline 
-	\multirow{8}{*}{Runtime Tainting}
+	\multirow{7}{*}{Runtime Tainting}
 	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
@@
 	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
   \hline
@@
   \hline
-  \multirow{3}{*}{Hybrid}
+  \multirow{4}{*}{Hybrid}
   &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
@@
   &   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
 	\hline

### 2014-11-03 docs/questioning.tex
minor change

@@
 \subsubsection{Policy Enforcement}
+\label{sec:policy}
 
@@
 page~\cite{APKLM10}.
+In addition, a recent variation of JavaScript
+injection attacks known as return-to-JavaScript
+attack~\cite{APKLM10} can be use to bypass
+the above mechanisms. Such attacks share
+many similarities with the {\it return-to-lib}
+attack~\cite{SPPGMMB04}. When performing an
+attack like this the malicious user transfers the
+execution to points that contain script
+code which in turn is used to perform the attack.
 
@@
 \subsection{Behavior-Based}
+
+In this section we examine the two main behavior-based
+approaches.
 
@@
 like the aforementioned one.
+Furthermore, training tools that detect
+{\sc xss} attacks based on JavaScript injection
+would fail to detect a return-to-JavaScript attack
+like the one mentioned in Subsubsection~\ref{sec:policy}.
 

### 2014-11-03 docs/questioning.tex
SMasK goes to ISR

@@
 (see Table~\ref{tab:comp}).
+{\it {\sc sm}ask}~\cite{JB07} is another framework
+that was inspired by {\sc isr}. To detect {\sc xss}
+attacks it searches for {\sc html} and JavaScript
+keywords within the application's legitimate code.
+This is done before the processing of an {\sc http}
+request. When it finds one it adds a token to it.
+This results to a ``code mask". Then,
+before sending the resulting {\sc html} data to the
+web user, the framework searches the data for
+illegal code by using the same keywords.
+Since all legitimate code has been ``masked",
+the injected code can be identified.
+The pre- and post-processing of the code though,
+may add a significant overhead to the application.
+Unfortunately, the authors of {\sc sm}ask
+did not provide measurements regarding the
+computational performance of the tool (see Table~\ref{tab:comp}).
 
@@
 lead to many false positives.
-
 The following schemes apply further checks when
@@
 taint data is considered to be legitimate.
-In essence, they detect JavaScript-driven {\sc xss}
+Their scheme detects JavaScript-driven {\sc xss}
 attacks by ensuring that a script can send sensitive
@@
 
-{\it {\sc sm}ask}~\cite{JB07} is a mechanism that detects
-both {\sc sql} injection attacks and {\sc xss} attacks.
-To do this, it identifies malicious
-code by automatically separating user input from legitimate code.
-This is done by introducing specific syntactic constructs
-that handle server-side languages used for data management
-separately.
-
 {\sc xss-guard}~\cite{BV08}
@@
   \hline
-  \multirow{3}{*}{{\sc isr}}
+  \multirow{4}{*}{{\sc isr}}
   &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} & {\sc sql} injection \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
   &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
@@
   \hline
-  \multirow{4}{*}{Hybrid}
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
+  \multirow{3}{*}{Hybrid}
   &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
@@
   \hline
-  \multirow{3}{*}{{\sc isr}}
+  \multirow{4}{*}{{\sc isr}}
   &   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
   &   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
@@
   \hline
-  \multirow{4}{*}{Hybrid}
-  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
+  \multirow{3}{*}{Hybrid}
   &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\

### 2014-11-03 docs/questioning.tex
work on the hybrid category

@@
 web user, the framework searches the data for
-illegal code by using the same keywords.
+illegal code by using the same keywords (locus {\sc y}).
 Since all legitimate code has been ``masked",
@@
 
-{\sc xss-guard}~\cite{BV08}
-maps legitimate scripts to {\sc http} responses.
-
-{\it Blueprint}~\cite{LV09}.
+This category includes mechanisms that borrow
+characteristics from more than one of the above categories.
+
+{\sc xss-guard}~\cite{BV08} is a training scheme
+that also employs parse-tree validation.
+During training, the scheme maps legitimate scripts
+to {\sc http} responses. During production
+{\sc xss-guard} retrieves for every script included
+in a response its parse-tree and checks if it
+is one of those previously mapped to this response.
+Apart from the  comparison of the parsed-trees, {\sc xss-guard}
+checks also for an exact match of lexical entities.
+To achieve this, the scheme utilizes that data structures
+of Firefox's JavaScript engine (locus {\sc x}).
+However, string literals are not compared literally
+thus, a possible false negative result could occur if an
+adversary performed a mimicry attack~\cite{WS02}.
+For example, consider a banner rotator that
+every time it runs, it creates a value that depends on
+the current date and the length of the array that
+contains the references of the various images to be displayed.
+Then, based on this value it shows a specific
+image to a user. In a vulnerable web site that allows
+users to post data and contains this banner
+rotator, a malicious user could create and store a script
+that has the same code structure, with the same JavaScript
+keywords like the above. In this script the
+attacker could also include references to tiny
+images hosted on a web server that is maintained by him in order
+to retrieve the {\sc ip} addresses of the
+users that visit the vulnerable site.
+
+{\it Blueprint}~\cite{LV09} is a policy
+enforcement mechanism that also utilizes parsed-trees.
 

### 2014-11-03 docs/questioning.tex
Section 4 draft ready

@@
 injection attacks known as return-to-JavaScript
-attack~\cite{APKLM10} can be use to bypass
+attack~\cite{APKLM10} can be used to bypass
 the above mechanisms. Such attacks share
@@
 
-\subsubsection{Runtime Tainting}
-
-A runtime tainting scheme marks untrusted
+\subsubsection{Taint Tracking}
+\label{sec:taint}
+
+A taint tracking scheme marks untrusted
 (``tainted") data (for instance, a variable set
@@
 
-Runtime tainting is provided as a feature in some
+Taint tracking is provided as a feature in some
 programming languages, such as Perl and Ruby.
@@
 cannot detect non-persistent JavaScript-driven
-{\sc xss} attacks. {\sc wasc}~\cite{NLC07} 
+{\sc xss} attacks. Although they can be
+modified to do so. {\sc wasc}~\cite{NLC07} 
 though, can deal with such attacks because it
@@
 characteristics from more than one of the above categories.
+Two of them focus on the detection of {\sc xss}
+attacks and one of them focuses on {\sc dsl} code
+injection attacks.
 
@@
 {\it Blueprint}~\cite{LV09} is a policy
-enforcement mechanism that also utilizes parsed-trees.
-
-{\it Diglossia}~\cite{SMS13} performs positive taint tracking and
-parse-tree validation.
+enforcement framework that also utilizes parsed-trees
+to detect {\sc xss} attacks. To guarantee
+that untrusted content is not executed, Blueprint generates
+on the server-side a parse-tree from untrusted {\sc html}
+to ensure that it does not contain any dynamic content.
+Then the parsed-tree is transfered to the document
+generator of the browser (locus {\sc x}) where untrusted
+browser parsing behavior is ruled out.
+Blueprint is an efficient countermeasure but it
+imposes a significant overhead due to its
+extensive parsing (see Table~\ref{tab:comp}).
+
+{\it Diglossia}~\cite{SMS13} combines positive taint tracking
+(see Subsubsection~\ref{sec:taint}) together with
+parse-tree validation. Diglossia was based on the
+theory of Ray and Ligatti~\cite{RL12b} (also see
+Section~\ref{sec:attacks}) to detect {\sc dsl}
+code injection attacks. In addition, it is actually
+the first, and so far the only framework that detects
+No{\sc sql} injection attacks.
+When an application computes an output string (query),
+Diglossia computes a ``shadow" of this string.
+Specifically, it maps all characters introduced by
+the application to a shadow character set.
+This set does not contain any characters coming
+from the tainted input. Then, the scheme
+creates the parse-tree of the query that
+is about to be executed with the parse-tree
+of the ``shadow" and compares them (locus {\sc z}).
+If the trees are not equal the application is probably
+under attacks. Diglossia can be bypassed in the same
+way as other taint tracking approaches~\cite{NBR14}.
 
@@
   \hline
-	\multirow{7}{*}{Runtime Tainting}
+	\multirow{7}{*}{Taint Tracking}
   &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
@@
   \hline 
-	\multirow{7}{*}{Runtime Tainting}
+	\multirow{7}{*}{Taint Tracking}
 	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\

### 2014-11-04 docs/questioning.tex
more work

@@
 detect attacks. For every locus we provide the corresponding
-references: ({\sc draft}).}
+references:
+locus {\sc x}~\cite{KKVJ06,KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
+locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
+locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,MKS09,HO05,HO06,HO05b,SMS13},
+locus $\Omega$~\cite{BK04,LLW02}.}
 \end{figure*}
@@
 \end{center}
-\caption{\label{fig:defenses}The basic categories of web application
-attack countermeasures ({\sc draft}).}
+\caption{\label{fig:defenses}The basic categories of countermeasures
+against web application
+attacks, based on executable source code injectiion. For each approach
+we provide the references that present corresponding mechanisms:
+{\bf 1}~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
+{\bf 2}~\cite{BK04,JB07,GC09,APKLM10},
+{\bf 3}~\cite{BWS05,SW06},
+{\bf 4}~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
+{\bf 5}~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
+{\bf 6}~\cite{BV08,LV09,SMS13}.}
 \end{figure*}
@@
 Finally, {\it CsFire}~\cite{DDHPJ10}
-examines cross-domain interactions,
-to design a cross-domain policy.
+examines cross-domain interactions, to design a
+cross-domain policy on the client's side (locus {\sc x}).
 The policy is based on the concept of a relaxed
@@
 The following schemes apply further checks when
-they identify that tainted data have reached a sink.
+they identify that tainted data have reached a sink
+(locus {\sc z}).
 In particular, {\it Xu et al.}~\cite{XBS06}
@@
 of specific features provided by {\sc php}.
-Note that the above schemes detect potential attacks
-in locus {\sc z}. This automatically means that they
-cannot detect non-persistent JavaScript-driven
-{\sc xss} attacks. Although they can be
-modified to do so. {\sc wasc}~\cite{NLC07} 
-though, can deal with such attacks because it
-analyzes {\sc html} responses to check
+% Note that the above schemes detect potential attacks
+% in locus {\sc z}. This automatically means that they
+% cannot detect non-persistent JavaScript-driven
+% {\sc xss} attacks. Although they can be
+% modified to do so.
+{\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
 if there are tainted data that contain scripts (locus {\sc y}).

### 2014-11-04 docs/questioning.tex
more on the intro and abstract

@@
   accuracy, performance, deployment and security. Especially notable
-  for a key category is accuracy, as our findings show that there are
+  is accuracy, as our findings show that there are
   many defense mechanisms that are tested in a poor manner.
+  In addition, we observe that there are many protection mechanisms
+  that can be bypassed by attackers that know how the mechanisms
+  work. Finally, we see that researchers tend to not make
+  their mechanisms available to the community.
 
@@
 \section{Introduction Remarks}
+
+%Introduction~\cite{I05}. Also see~\cite{A00}.
 
@@
 
-There is already a survey on mitigating
-software vulnerabilities in general~\cite{SZ12}.
-The scope of that research is pretty wide and leaves
-out many approaches and mechanisms that we report here.
-This is mainly because this work includes countermeasures
-that detect such vulnerabilities via program analysis
-(which is done during development or testing), while
-we include protection mechanisms that counter
-such attacks when they take place.
-Also, countermeasures that prevent {\sc sql}
-injection attacks~\cite{HVO06}, have already been surveyed.
-However, this survey is quite old and since then
-the number of countermeasures that detect {\sc sql}
-injection attacks alone, has been drastically increased
-as we mentioned in the previous paragraph.
-
-In our research we focus on the top
-{\sc tba} systems that and are presented
-in publications cited more than twenty times.
+In this paper we initially show how the above attacks can be seen from
+a {\it common perspective}. We achieve this by providing
+an exploitation model that highlights the following fact:
+the majority of the steps needed to perform application attacks
+based on executable source code injection are
+common.\footnote{Note that we leave out attacks that are based on
+binary code injection (i.e. buffer
+overflows --- see Section~\ref{sec:attacks}).}
+This is validated by the fact that there are
+protection mechanisms that can detect more than
+one of these attacks. Then, we {\it categorize}
+the top 34 protection mechanisms that detect such attacks and
+are presented in publications cited more than twenty times.
 For the sake of our study, we choose
-to make some exceptions and include some latest mechanisms
-that were presented in top security conferences even if
-the corresponding publications have been cited less than
-twenty times.
-
-% TODO@dimitro: explain why you leave out {\it SecuriFly}~\cite{MLL05}.
-
-Introduction~\cite{I05}. Also see~\cite{A00}.
-
-Requirements:
+to make some exceptions and include some of the
+latest mechanisms that were presented in top security
+conferences even if the corresponding publications have
+been cited less than twenty times. Finally, we {\it analyze}
+each mechanism based on the following dimensions:
 \begin{itemize}
@@
 
+\noindent
 All the aforementioned requirements are considered critical
 when building security mechanisms that protect
-applications~\cite{A01,A00}.
+applications~\cite{A01,A00}. Based on this analysis
+we can identify the advantages and disadvantages of the
+various mechanisms and enumerate some of their common
+characteristics. We can also draw useful conclusions
+about the various categories and see how they compare
+to each other. A worrying observation is that sometimes,
+researchers test the diagnostic performance of their
+mechanisms in a poor manner. This turns out as very
+critical because some of these mechanisms can actually
+be bypassed. In addition, researchers do
+not make their mechanisms available to the community,
+thus no one can either use their mechanism,
+or replicate their experiments.
+
+There is already a survey on mitigating software vulnerabilities
+in general~\cite{SZ12}. The scope of that
+research is pretty wide and leaves out the majority of the
+approaches and mechanisms that we report here.
+This is mainly because this work includes countermeasures
+that detect such vulnerabilities via program analysis
+(which is done during development or testing), while
+we include protection mechanisms that counter
+such attacks when they take place.
+Also, countermeasures that prevent {\sc sql}
+injection attacks~\cite{HVO06}, have already been surveyed.
+However, this survey is quite old and since then
+the number of countermeasures that detect {\sc sql}
+injection attacks alone, has been drastically increased
+as we mentioned in the previous paragraph.
+
+The main contributions of this paper are the following:
+
+\begin{enumerate}
+\item We provide an exploitation model that puts
+application attacks based on executable source code injection
+under a common perspective.
+\item We categorize and analyze previously proposed
+defenses based on criteria that are considered critical
+when building protection mechanisms.
+\item We discuss some serious issues raised from our
+findings. Such can be the main reasons why
+the mechanisms are not adopted in practice.
+\item We discuss what are the necessary criteria
+for new mechanisms and how our work can help
+researchers to design new countermeasures.
+\end{enumerate}
+
+The rest of the paper is organized as follows. {\sc tba}.
+
+% In the last 15 years there are numerous mechanisms that have
+% been developed to detect one or more of the attacks mentioned
+% above. However, the majority of them are not used in practice.
+% This is due to the following reasons:
+% a) the mechanisms have not been extensively tested in terms
+% of accuracy,
+% b) are hard to deploy because they require many modifications
+% either on the client-side, the server-side, or both,
+% c) they add significant overhead, and
+% d) can be bypassed by attackers that know how they work.
+% The motivation behind this research is to systematize
+% and analyze previously proposed protection mechanisms.
+% In this way we can highlight the advantages
+% and disadvantages of each mechanism, enlist them
+% into different categories, and see how they compare to each other.
 

### 2014-11-04 docs/questioning.tex
changes to Section III

@@
 
-Web application attacks may involve security misconfigurations,
-broken authentication and session management, or other issues.
-Some of the most dangerous web application attacks, though,
-are associated with the processing of external input data
-that may contain malicious code, a vulnerability known as
-code injection.
+Web application attacks may involve security misconfigurations, broken
+authentication and session management, or other issues. Some of the
+most dangerous web application attacks are associated with the
+processing of external input data that can contain malicious code, a
+vulnerability known as code injection.
 
@@
 Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-({\sc owasp}) and
-{\sc mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
+({\sc owasp}) and {\sc
+  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
 years. Consider the case of {\sc owasp}'s Top Ten project whose main
 goal is to raise awareness about web application security by
-identifying some of the most critical risks facing organizations which
-is referenced by numerous researchers. In its three consecutive Top
-Ten lists (2007, 2010, 2013), different executable source code-driven
-injection attacks dominate the top five positions. Malicious users
-find new ways to bypass defense mechanisms by using a variety of
-techniques despite the numerous countermeasures that are being
-introduced. Note that the number of systems developed to counter
-{\sc sql} injection attacks until 2006 was more than twenty~\cite{HVO06}.
-Since then the number has doubled.
-Researchers have also indicated that the number of such attacks
-is steadily increasing in recent years~\cite{SSL12}.
+identifying some of the most critical risks facing organizations. The
+Top Ten project is popular, referenced by numerous researchers. In its
+three consecutive Top Ten lists (2007, 2010, 2013), different
+executable source code-driven injection attacks dominate the top five
+positions. Malicious users find new ways to bypass defense mechanisms
+by using a variety of techniques despite the numerous countermeasures
+that are being introduced. Note that the number of systems developed
+to counter {\sc sql} injection attacks until 2006 was more than
+twenty~\cite{HVO06}. Since then the number has doubled. Researchers
+have also indicated that the number of such attacks is steadily
+increasing in recent years~\cite{SSL12}.
 
 In this paper we initially show how the above attacks can be seen from
-a {\it common perspective}. We achieve this by providing
-an exploitation model that highlights the following fact:
-the majority of the steps needed to perform application attacks
-based on executable source code injection are
-common.\footnote{Note that we leave out attacks that are based on
-binary code injection (i.e. buffer
-overflows --- see Section~\ref{sec:attacks}).}
-This is validated by the fact that there are
-protection mechanisms that can detect more than
-one of these attacks. Then, we {\it categorize}
-the top 34 protection mechanisms that detect such attacks and
-are presented in publications cited more than twenty times.
-For the sake of our study, we choose
-to make some exceptions and include some of the
-latest mechanisms that were presented in top security
-conferences even if the corresponding publications have
-been cited less than twenty times. Finally, we {\it analyze}
-each mechanism based on the following dimensions:
+a {\it common perspective}. We achieve this by providing an
+exploitation model that highlights the following fact: the majority of
+the steps needed to perform application attacks based on executable
+source code injection are common.\footnote{Note that we leave out
+  attacks that are based on binary code injection (i.e. buffer
+  overflows --- see Section~\ref{sec:attacks}).} This is validated by
+the fact that there are protection mechanisms that can detect more
+than one of these attacks. Then, we {\it categorize} a selection of
+these protection mechanisms. The selection comprises protection
+mechanisms that detect such attacks and are presented in publications
+cited more than twenty times, and some of the latest mechanisms that
+have been presented in top security conferences that have been cited
+less than twenty times. We included the second group so that we would
+not penalize recent research. Finally, we {\it analyze} each mechanism based
+on the following dimensions:
 \begin{itemize}
-\item {\it Diagnostic Performance} As long
-as we examine protection mechanisms that detect
-attacks, the non-existence of false positive and
-negative alarms is a reasonable requirement.
+\item {\it Diagnostic Performance} Protection mechanisms are as good
+  as their detection capability; this requires low false positive and
+  false negative rates.
 \item {\it Computational Performance} We examine
@@
 about the various categories and see how they compare
-to each other. A worrying observation is that sometimes,
-researchers test the diagnostic performance of their
-mechanisms in a poor manner. This turns out as very
-critical because some of these mechanisms can actually
-be bypassed. In addition, researchers do
-not make their mechanisms available to the community,
-thus no one can either use their mechanism,
-or replicate their experiments.
+to each other.
 
@@
 \begin{enumerate}
-\item We provide an exploitation model that puts
-application attacks based on executable source code injection
-under a common perspective.
-\item We categorize and analyze previously proposed
-defenses based on criteria that are considered critical
-when building protection mechanisms.
-\item We discuss some serious issues raised from our
-findings. Such can be the main reasons why
-the mechanisms are not adopted in practice.
-\item We discuss what are the necessary criteria
-for new mechanisms and how our work can help
-researchers to design new countermeasures.
+\item We provide an exploitation model that puts application attacks
+  based on executable source code injection under a common
+  perspective.
+\item We categorize and analyze previously proposed defenses based on
+  criteria that are considered critical when building protection
+  mechanisms.
+\item A worrying observation is that sometimes researchers test the
+  diagnostic performance of their mechanisms in a poor manner. This
+  turns out as very critical because some of these mechanisms can
+  actually be bypassed.
+\item Also worrying is that researchers do not make their mechanisms
+  available to the community, thus no one can either use their
+  mechanism, or replicate their experiments.
+\item We discuss how our observations may be the main reasons why the
+  mechanisms are not adopted in practice.
+\item We discuss what are the necessary criteria for new mechanisms
+  and how our work can help researchers to design new countermeasures.
 \end{enumerate}
@@
   inside targeted systems, which turn a part of the target into a
-so-called `weird machine' programmable by the attacker via crafted inputs
-(a.k.a. `exploits')''}.
-An example of the above definition is the
-following: The code fragment below defines the operation of
-addition in the Scheme programming language~\cite{AS96,D09}:
-
-\begin{verbatim}
-(define (add x y) (+ x y))
-\end{verbatim}
-
-\noindent
-Consider the case where instead of a number, a function that leads to an
-endless loop is passed as an argument by the user. This will cause
-the interpreter to enter
-an endless loop and lead to a denial of service.
-% Keep in mind that a {\sc cia} does not require a programming
-% language with first-class functions.
-The intuition here is that {\it ``every application that copies
-untrusted input verbatim into an output
-program is vulnerable to code injection''}.
-Ray and Ligatti~\cite{RL12b} actually proved the above
-claim based on formal language theory.
+  so-called `weird machine' programmable by the attacker via crafted
+  inputs (a.k.a. `exploits')''}. In particular, {\it ``every
+  application that copies untrusted input verbatim into an output
+  program is vulnerable to code injection''}. Ray and
+Ligatti~\cite{RL12b} actually proved the above claim based on formal
+language theory.
 
@@
 Thus, in a non-persistent {\sc xss} attack the injected code
-never reaches the database and immediately becomes a part of the
+is never saved on the server and immediately becomes part of the
 content that is sent back to a web user.

### 2014-11-04 docs/questioning.tex
some work on analysis - testing

@@
 references:
-locus {\sc x}~\cite{KKVJ06,KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
+locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
 locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,MKS09,HO05,HO06,HO05b,SMS13},
+locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,HO06,HO05b,SMS13},
 locus $\Omega$~\cite{BK04,LLW02}.}
@@
 \caption{\label{fig:defenses}The basic categories of countermeasures
-against web application
-attacks, based on executable source code injectiion. For each approach
-we provide the references that present corresponding mechanisms:
+against web application attacks, based on executable source code
+injectiion. For each approach we provide the references
+that present corresponding mechanisms:
 {\bf 1}~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
@@
 as an extension of their anomaly detection framework called
-{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09} is
+{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} is
 a signature-based mechanism that prevents {\sc sql} and
@@
 
+\begin{table*}
+\caption{Availability of the corresponding mechanisms.}
+    \label{tab:avail}
+\centering
+    \begin{threeparttable}
+    \begin{small}
+\scalebox{0.99}{
+    \begin{tabular}{l|c|ccc}
+    \hline
+    \bf{Approach}
+  & \bf{Mechanism}
+  & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
+  && \bf{Source Code}
+  & \bf{Executable}
+  & \bf{Testbed} \\
+    \hline
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
+  \hline  
+  \hline
+  \multirow{12}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it NoForge}~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it CoreScript}~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
+  &   {\it ConScript}~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
+  &   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+    % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
+  % \hline
+  % \hline 
+  % \multirow{3}{*}{Securing Mashups}
+  % &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
+  % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline
+  \multirow{4}{*}{{\sc isr}}
+  &   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline 
+  \multirow{7}{*}{Taint Tracking}
+  &   {\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc php} Aspis}~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
+  &   {\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+  \hline 
+  \multirow{6}{*}{Training}
+  &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
+  &   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  &   {\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
+  \hline
+  \hline
+  \multirow{3}{*}{Hybrid}
+  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
+  \hline
+    \end{tabular}}
+    \begin{tablenotes}
+  \begin{footnotesize}
+       \item[1] The check mark (\tick) indicates that the publication
+       includes a homepage where the reader can refer to, to
+       download the corresponding software. {\bf AO} (Available On-line) suggests
+       that the software is available on-line but the
+       address was not mentioned in the paper, which probably indicates that
+       the authors made it available after the publication. The question ({\bf ?})
+       mark, indicates that the a homepage for the software was included
+       in the publication but now it is not available.
+  \end{footnotesize}
+    \end{tablenotes}
+    \end{small}
+    \end{threeparttable}
+\end{table*}
+
 \section{Analysis}
+
+\subsection{Testing}
+
+\begin{figure}
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.47]{defect-percentages.png}
+\end{center}
+\caption{\label{fig:defect_sources}A pie showing where the
+authors reffered to, to find vulnerabilities to test
+their mechanims. We also provide which source was used
+by which publication:
+{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
+{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09},
+{\sc xss}ed.com~\cite{NSS06,APKLM10},
+ha.ckers.org~\cite{TNH07,PSC09,LV09},
+Microsoft~\cite{RDWDE07}.}
+\end{figure}
+
+Table~\ref{tab:comp} indicates that 27 out of
+34 mechanisms were tested on real-world applications
+known to be vulnerable. The vulnerabilities
+associated with these applications are enlisted
+in the following providers: the Common Vulnerabilities
+and Exposures ({\sc cve})
+database,\footnote{\url{https://cve.mitre.org/}}
+the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
+security mailing list, the
+{\sc xss}ed.com\footnote{\url{www.xssed.com}}
+security bulletin provider, Microsoft's security
+bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
+and the ha.ckers.org\footnote{\url{www.xssed.com}}
+security bulletin provider. Figure~\ref{fig:defect_sources}
+presents how many (in terms of percentages) and which
+(in the figure's caption) authors referred to which source.
+In numerous occassions authors performed tests based
+on the same applications. For instance, 12 mechanisms
+were tested on a vulnerable version of
+{\sc phpbb}.\footnote{https://www.phpbb.com/}
+
+\subsection{Trade-offs}
+
+\subsection{Designing New Mechanisms}
 
@@
 
-\begin{table*}
-\caption{Availability of the corresponding mechanisms.}
-    \label{tab:avail}
-\centering
-    \begin{threeparttable}
-    \begin{small}
-\scalebox{0.99}{
-    \begin{tabular}{l|c|ccc}
-    \hline
-    \bf{Approach}
-	& \bf{Mechanism}
-  & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
-	&& \bf{Source Code}
-	& \bf{Executable}
-	& \bf{Testbed} \\
-    \hline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
-  \hline  
-  \hline
-  \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it NoForge}~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it CoreScript}~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
-  &   {\it ConScript}~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
-  &   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
-    % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
-  % \hline
-  % \hline 
-  % \multirow{3}{*}{Securing Mashups}
-  % &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline
-  \multirow{4}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline 
-	\multirow{7}{*}{Taint Tracking}
-	&  	{\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
-  &  	{\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline 
-  \multirow{6}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
-	&   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
-  & 	{\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
-  \hline
-  \hline
-  \multirow{3}{*}{Hybrid}
-  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
-	\hline
-    \end{tabular}}
-    \begin{tablenotes}
-	\begin{footnotesize}
-       \item[1] The check mark (\tick) indicates that the publication
-       includes a homepage where the reader can refer to, to
-       download the corresponding software. {\bf AO} (Available On-line) suggests
-       that the software is available on-line but the
-       address was not mentioned in the paper, which probably indicates that
-       the authors made it available after the publication. The question ({\bf ?})
-       mark, indicates that the a homepage for the software was included
-       in the publication but now it is not available.
-	\end{footnotesize}
-    \end{tablenotes}
-    \end{small}
-    \end{threeparttable}
-\end{table*}
-
 \section{Conclusions}

### 2014-11-04 docs/questioning.tex
some additions - changes

@@
 We can identify three main approaches, namely:
-{\it design-based}, {\it behavior-based}
-and {\it hybrid}.
+{\it design-based}, {\it behavior-based} and {\it hybrid}.
 The design-based category involves mechanisms that make applications
@@
 {\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
-{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09},
+{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
 {\sc xss}ed.com~\cite{NSS06,APKLM10},
@@
 In numerous occassions authors performed tests based
-on the same applications. For instance, 12 mechanisms
+on the same applications. For example, 12 mechanisms
 were tested on a vulnerable version of
 {\sc phpbb}.\footnote{https://www.phpbb.com/}
+
+There are also authors that took a different approach.
+For instance, during their initial tests,
+Stock et al.~\cite{SLMS14} managed to bypass
+the browser-based {\sc xss} filters of the
+73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
+These vulnerabilities were actually found during
+their previous research~\cite{LSJ13}.
 

### 2014-11-04 docs/questioning.tex
more work on the analysis section / ease of use

@@
 their previous research~\cite{LSJ13}.
+Furthermore, in the publications that
+{\sc amnesia}~\cite{HO05,HO06,HO05b}
+and {\sc sd}river~\cite{MS09,MKS09,MKLS11} were presented,
+authors managed to break existing application suites
+and then test the diagnostic performance of their tools on them.
+
+% Comment: The above are some extra findings that
+% indicate that there is no standard way to
+% test such mechanisms. Perhaps, forming a
+% standard way to test such tools in terms
+% of diagnostic and computational performance
+% would be one of the reasons of adopting them.
+
+\subsection{Ease of Use}
+
+Consider the majority of mechanisms coming from
+the policy enforcement category. In most cases
+developers should modify multiple components
+to use each mechanism. Specifically, mechanisms like
+BrowserShield, and {\sc beep} require modifications
+both on the server and the client side.
+Thus, it would be difficult for them to be adopted by
+both browser vendors and application developers.
 

### 2014-11-05 docs/questioning.tex
multiple corrections in Section 4

@@
 we do not include binary code injection, focusing instead on defenses
-that protect applications against application attacks based on the
+that protect applications against attacks based on the
 executable source code injection category.
@@
 code injection vulnerabilities.
-We can identify three main approaches, namely:
+We can identify three approaches, namely:
 {\it design-based}, {\it behavior-based} and {\it hybrid}.
@@
 immune to different attack vectors by design~\cite{JL75,L81}. 
-The behavior-based incorporates a variety of methods and
+The behavior-based category incorporates a variety of
 schemes that inspect the behavior of applications
@@
 Finally, as we mentioned in Subsection~\ref{sec:model},
-Figure~\ref{fig:attacks} illustrates the point where
-mechanisms detect attacks.
+Figure~\ref{fig:attacks} illustrates for each mechanism
+(found in the figure's caption), the point where
+it detects attacks.
 
@@
 the tree representation of the abstract syntactic
-structure of the executable source code
-with the one that was originally intended.
+structure of the source code that is about to be
+executed with the one that was originally intended.
 If the trees diverge, the application is probably
@@
 database (locus {\sc z}).
-Contrary to {\sc sqlg}uard~\cite{BWS05} (and many other
-mechanisms), {\sc sql}check~\cite{SW06} has been
+Contrary to {\sc sqlg}uard (and other
+mechanisms as we sill observe), {\sc sql}check has been
 extensively tested in terms of diagnostic performance
-as seen in Table~\ref{tab:comp}. A disadvantage of
-those mechanisms is that the application must be modified
-every time a query is about to be sent to a database
-for execution.
+as it can be seen in Table~\ref{tab:comp}.
+A disadvantage of those mechanisms is that the
+application must be modified in every code fragment
+that sends an {\sc sql} query to the database for execution.
 
@@
 of scripts to detect JavaScript-driven {\sc xss} attacks.
+
+Parse-tree validation seems to be an efficient approach
+to detect {\sc dsl} code injection attack,
+especially in the case of the {\sc sql}check
+implementation. This however does not apply in
+the case of the mechanisms that utilize
+this approach to detect JavaScript-driven {\sc xss} attacks
+as we will see in Subsection~\ref{sec:hybrid}.
 
@@
 find static {\sc url} references. Then, based on
-a set of policies it allows or blocks
+a set of policies Noxes allows or blocks
 the request (locus {\sc x}). Such policies
-are provided either by the user or by
-the framework itself. Noxes does not
-deal with JavaScript-driven {\sc xss}
-attacks and it is a rather simplistic approach.
+can be also provided by the server (i.e. ``never
+follow a link that leads to the malicious.com
+web site"). Noxes does not deal with
+JavaScript-driven {\sc xss} attacks and it is a rather
+simplistic approach.
 
@@
 and the framework by {\it Phung et al.}~\cite{PSC09}
-extend JavaScript with new primitive functions to
+extend JavaScript with new primitive functions that
 provide safe methods to protect potentially vulnerable
@@
 In this way, {\sc xxs} attacks that take advantage
-functions like {\tt eval} and {\tt write} that are
+functions like {\tt write} and {\tt eval}, which are
 used to assemble innocuous-looking parts into harmful
-strings would fail.
+strings,\footnote{The infamous Sammy worm that
+infected MySpace in 2005~\cite{SP07,ELX07}
+utilized the {\tt eval} function to assemble a
+script with malicious behavior.} would fail.
 
@@
 scripts introduced by script inclusion and {\tt iframe}
-tags. For instance, consider a web page ({\tt foo.net})
-that prints the value of the a query parameter ({\tt query})
+tags. For instance, consider a web page (foo.net)
+that prints the value of a query parameter ({\tt query})
 from the page's {\sc url} in the web page's content
@@
 send it via an image request to a web site
-that he or she controls ({\tt malicious.com}).
+that he or she controls (malicious.com).
 This could be achieved by including the following
@@
 several deployment issues since they
-require significant source modifications by the web
-developers in order to introduce policies.
+require significant source modifications by the
+developers on the server-side, in order to
+introduce the policies.
 
@@
 different kinds of application attacks~\cite{K09b,KKP03}.
-The main idea behind the it, is to
-separate code from data by randomizing the legitimate code's 
+The main idea behind it, is to separate code from
+data by randomizing the legitimate code's 
 execution environment. In this way, the malicious code
@@
 
-{\it {\sc sql}rand}~\cite{BK04} is based on {\sc isr}
-to detect {\sc sql} injections in the following manner:
+{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr}
+to detect {\sc sql} injection attacks. It works in the following manner:
 initially, it allows programmers to create {\sc sql} statements
@@
 specific policies in a manner similar to a firewall
-configuration language. This brings up questions
-concerning the diagnostic performance of the mechanism
-since the corresponding testing is insufficient
-(see Table~\ref{tab:comp}).
+configuration language. This fact, together with the
+insufficient testing of the mechanism (see Table~\ref{tab:comp})
+brings up questions concerning its diagnostic performance.
 {\it {\sc sm}ask}~\cite{JB07} is another framework
@@
 
-There are different implementations of these approach
+There are different implementations of this approach
 in terms of how the tainted data is marked and observed,
@@
 lead to many false positives.
+
 The following schemes apply further checks when
@@
 the origins of tainted data, its propagation within the application
-and other. When tainted data reaches a sink {\sc csse} performs
-syntactic checks it based on the aforementioned metadata
+and others. When tainted data reaches a sink {\sc csse} performs
+syntactic checks based on the aforementioned metadata
 (locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
@@
 % modified to do so.
-{\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
+Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
 if there are tainted data that contain scripts (locus {\sc y}).
@@
 the majority of the above schemes~\cite{NBR14}.
-Furthermore, most of them are hard to deploy since
+Furthermore, most of them are not easy to deploy since
 the majority of input vectors, string operations
-and output vectors must be instrumented.
+and output vectors of the application must be instrumented.
 
@@
 approach. Contrary to the aforementioned schemes that
-operate on the server side, they track taint sensitive
+operate on the server side, they track sensitive
 information on the client side (locus {\sc x}).
@@
 {\sc http} response that triggers the injection seems legitimate.
-The scheme is different to the previous one because it
+The scheme is different from the previous one because it
 marks and observes data that are considered harmful.
@@
 mechanism registers all valid legitimate code statements during a
-training phase, most of the time in the form of signatures. This can
+training phase (mostly in the form of signatures). This can
 be done in various ways according to the implementation. Then, only
-those will be accepted, approved or recognized during production.
+those will be recognized and approved for execution
+during production.
 
@@
 {\sc xss-guard} retrieves for every script included
-in a response its parse-tree and checks if it
+in a response its parsed tree and checks if it
 is one of those previously mapped to this response.
-Apart from the comparison of the parsed-trees, {\sc xss-guard}
+Apart from the comparison of the parsed trees, {\sc xss-guard}
 checks also for an exact match of lexical entities.
@@
 thus, a possible false negative result could occur if an
-adversary performed a mimicry attack~\cite{WS02}.
+adversary performs a mimicry attack~\cite{WS02}.
 For example, consider a banner rotator that
@@
 {\it Blueprint}~\cite{LV09} is a policy
-enforcement framework that also utilizes parsed-trees
+enforcement framework that also utilizes parsed trees
 to detect {\sc xss} attacks. To guarantee
 that untrusted content is not executed, Blueprint generates
-on the server-side a parse-tree from untrusted {\sc html}
+on the server-side a parsed tree from untrusted {\sc html}
 to ensure that it does not contain any dynamic content.
-Then the parsed-tree is transfered to the document
+Then the parsed tree is transfered to the document
 generator of the browser (locus {\sc x}) where untrusted
@@
 from the tainted input. Then, the scheme
-creates the parse-tree of the query that
-is about to be executed with the parse-tree
-of the ``shadow" and compares them (locus {\sc z}).
+creates the tree of the query that
+is about to be executed and compares it with the parsed tree
+of the ``shadow" (locus {\sc z}).
 If the trees are not equal the application is probably
-under attacks. Diglossia can be bypassed in the same
+under attack. Note that, Diglossia can be bypassed in the same
 way as other taint tracking approaches~\cite{NBR14}.
@@
 
-% Comment: The above are some extra findings that
+% Comment 1: Regarding the frameworks that were
+% not tested in terms of diagnostic performance
+% at all, we see that they are mostly coming from
+% the design-based category.
+
+% Comment 2: Note though that implementations
+% of design-based mechanisms can actually
+% be bypassed.
+
+% Comment 3: The above are some extra findings that
 % indicate that there is no standard way to
@@
 \item See j{\sc csrf} for {\sc soma}'s drawbacks.
+\item Discuss about how tools can be easily modified
+to detect other attacks ({\sc sql}rand).
 \end{enumerate}

### 2014-11-05 docs/questioning.tex
some changes / additions

@@
   and can be easily adopted by security experts.
-\item {\it Security} How resilient is the system to
+\item {\it Security} We examine how resilient is the system to
   attackers that know how it works and wants to circumvent it.
-\item {\it Detection Locus}
-\item {\it Availability}
+\item {\it Detection Locus} Based on our exploitation model
+  we examine the location where a mechanism detects an attack.
+\item {\it Availability} We check if the mechanism and its
+  testbed are available on-line.
+available 
 \end{itemize}
@@
 when building security mechanisms that protect
-applications~\cite{A01,A00}. Based on this analysis
+applications~\cite{A01,A00,SPWS13}. Based on this analysis
 we can identify the advantages and disadvantages of the
@@
 Figure~\ref{fig:attacks} also illustrates in which step
-the defenses detect corresponding attacks ({\sc todo}).
+the defenses detect corresponding attacks.
 
@@
 	If no testing has taken place we add a question mark ({\bf ?}).
-    \item[3] The number involve requests.
+    \item[3] The numbers of this quadruple involve requests.
 	\end{footnotesize}
@@
 \end{center}
-\caption{\label{fig:defect_sources}A pie showing where the
-authors reffered to, to find vulnerabilities to test
-their mechanims. We also provide which source was used
-by which publication:
+\caption{\label{fig:defect_sources}A pie showing the sources
+where the authors reffered to, to find vulnerabilities to test
+their mechanisms. We also provide which source was used
+in which publication:
+{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
 {\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
-{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
 {\sc xss}ed.com~\cite{NSS06,APKLM10},

### 2014-11-05 docs/questioning.tex
addressed some comments mentioned in the telco

@@
 
+In this section we categorize and describe the various mechanisms
+developed to detect the attacks described earlier in
+Section~\ref{sec:attacks}. We accompany our descriptions
+with comments related to the following dimensions:
+a) diagnostic performance, b) security, c) ease of use
+and d) detection locus. Regarding the other two
+dimensions we provide general remarks in our upcoming
+``Analysis" section (\ref{sec:analysis}).
+
 Figure~\ref{fig:defenses} presents a taxonomy of the
@@
 Contrary to {\sc sqlg}uard (and other
-mechanisms as we sill observe), {\sc sql}check has been
+mechanisms as we will observe), {\sc sql}check has been
 extensively tested in terms of diagnostic performance
@@
 follow a link that leads to the malicious.com
-web site"). Noxes does not deal with
-JavaScript-driven {\sc xss} attacks and it is a rather
-simplistic approach.
+web site"). The main issue with Noxes is that
+it does not deal with JavaScript-driven {\sc xss}
+attacks which is currently the most popular
+{\sc xss} attack vector.
 
@@
 \section{Analysis}
+\label{sec:analysis}
 

### 2014-11-05 docs/questioning.tex
updated the table's information regarding the overhead (server - client)

@@
 references:
-locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
+locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
 locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,HO06,HO05b,SMS13},
-locus $\Omega$~\cite{BK04,LLW02}.}
+locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+locus $\Omega$~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
@@
 	&&& \bf{TP,TN,FP,FN}\tnote{2}
-	& \bf{Computational Overhead} & \\
+	& \bf{Computational Overhead}\tnote{3} & \\
     \hline
   \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% & {\sc sql} injection \\
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query & {\sc sql} injection \\
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql} injection \\
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql} injection \\
   \hline
@@
   \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% & {\sc xss} \\ 
-  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\bf ?} & {\sc csrf} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} & {\sc xss} \\
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} & {\sc csrf} \\
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
   % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% & {\sc xss} \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% & {\sc xss}, {\sc csrf} \\
+  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
   % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% & {\sc xss} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{3} & {\bf ?} & {\sc csrf} \\
-  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms & {\sc csrf} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms & {\sc xss} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} & {\sc csrf} \\
+  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms ({\sc c}) & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
@@
   \multirow{4}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} & {\sc sql} injection \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} & {\sc sql} injection, {\sc xss} \\
-  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% & {\sc xss} \\ 
-  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} & {\sc xss} \\
+  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql} injection \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql} injection, {\sc xss} \\
+  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
   \hline
@@
 	\multirow{7}{*}{Taint Tracking}
-  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
+  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
+	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
 	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% & {\sc sql} injection, {\sc xss} \\ 
-  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% & {\sc sql} injection, {\sc xss} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} & {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ & {\sc sql} and {\sc php} injection, {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% & {\sc dom}-based {\sc xss} \\
+	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
+  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\
+	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql} and {\sc php} injection, {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc s}) & {\sc dom}-based {\sc xss} \\
 	\hline
@@
   &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} & {\sc sql} injection \\ 
-	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} & {\sc sql} injection \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} &  {\sc xss} \\
-  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% & {\sc xss} \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% & {\sc sql} and {\sc xp}ath injection \\
+	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
+	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} ({\sc s}) & {\sc sql} injection \\
+	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% ({\sc s}) & {\sc xss} \\ 
+	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql} and {\sc xp}ath injection \\
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
@@
   \multirow{3}{*}{Hybrid}
-  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% & {\sc xss} \\
-  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% & {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% & {\sc sql} and No{\sc sql} injection \\
+  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
+  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql} and No{\sc sql} injection \\
 	\hline
@@
 	If no testing has taken place we add a question mark ({\bf ?}).
-    \item[3] The numbers of this quadruple involve requests.
+    \item[3] For every overhead we show if the overhead is applied to the server ({\sc s}) or the client ({\sc c}). 
+    \item[4] The numbers of this quadruple involve requests.
 	\end{footnotesize}

### 2014-11-06 docs/questioning.tex
work on the analysis section

@@
 \begin{IEEEkeywords}
-Security and Protection, Application Security, Code injection Attacks.
+Security and Protection, Application Security, Code injection Attacks,
+Testing, Cross-Site Scripting.
 \end{IEEEkeywords}
@@
 injection attacks alone, has been drastically increased
-as we mentioned in the previous paragraph.
+as we mentioned earlier.
 
@@
 In this section we categorize and describe the various mechanisms
-developed to detect the attacks described earlier in
+developed to detect the attacks described in
 Section~\ref{sec:attacks}. We accompany our descriptions
@@
 
+\subsubsection{Diagnostic Performance}
+
 \begin{figure}
@@
 
+\subsubsection{Computational Performance}
+
+\subsection{Detection Locus}
+
+Given the fact that the final steps of
+{\sc dsl} injection and {\sc csrf} attacks take place
+on the server-side, all the mechanisms that detect
+such attacks are placed in some point within the server.
+
+However, in this case of mechanisms that deal
+with JavaScript-driven {\sc xss} attacks
+we observe that attack detection may take place
+either on the server-side or on the client-side.
+
 \subsection{Ease of Use}
@@
 
-\subsection{Trade-offs}
+\subsection{Availability}
 

### 2014-11-06 docs/questioning.tex
some additions / fixes

@@
 	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql} and {\sc php} injection, {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc s}) & {\sc dom}-based {\sc xss} \\
+	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
 	\hline
@@
 
-However, in this case of mechanisms that deal
+However, in the case of frameworks that deal
 with JavaScript-driven {\sc xss} attacks
@@
 either on the server-side or on the client-side.
+In the first case, a proxy is placed on the server
+to examine the server's responses before they
+reach the user's web browser. In the second
+case a modified browser or a library that
+is securely downloaded from the server,
+checks the responses for potential attacks.
+Our findings indicate that the tendency so far,
+is to create frameworks that perform detection
+on the client side. In particular, 11 out of
+19 frameworks ({\bf 57,8\%}) detect JavaScript-driven
+{\sc xss} attacks at the client's side.
+Note that the majority of the mechanisms that
+detect such attacks on the server-side, can also
+detect
 

### 2014-11-06 docs/questioning.tex
minor addition
minor additions

@@
 such attacks are placed in some point within the server.
+From the mechanisms that detect {\sc dsl} code injection
+attacks, 3 out of 13 ({\bf 23\%}) do so at the level
+of the {\sc rdbms} --- locus $\Omega$.
+The other 11 wrap {\sc api} calls related to output
+vectors --- locus {\sc z}.
 
@@
 detect such attacks on the server-side, can also
-detect
+detect {\sc dsl} code injection attacks (7 out of 8).
 
@@
 
-\subsection{Designing New Mechanisms}
+\section{Discussion}
 

### 2014-11-06 docs/questioning.tex
minor change

@@
 with comments related to the following dimensions:
-a) diagnostic performance, b) security, c) ease of use
-and d) detection locus. Regarding the other two
-dimensions we provide general remarks in our upcoming
-``Analysis" section (\ref{sec:analysis}).
+a) diagnostic performance, b) computational performance,
+c) security, d) ease of use, and e) detection locus.
+Regarding the availability dimension we provide a general
+comment in our upcoming ``Analysis" section (\ref{sec:analysis}).
 

### 2014-11-06 docs/questioning.tex
changes and questions

@@
 developed to detect the attacks described in
-Section~\ref{sec:attacks}. We accompany our descriptions
-with comments related to the following dimensions:
-a) diagnostic performance, b) computational performance,
-c) security, d) ease of use, and e) detection locus.
-Regarding the availability dimension we provide a general
-comment in our upcoming ``Analysis" section (\ref{sec:analysis}).
+Section~\ref{sec:attacks}. We accompany our descriptions with comments
+related to the following dimensions: a) diagnostic performance, b)
+computational performance, c) security, d) ease of use, and e)
+detection locus. We treat f) availability separately in the
+``Analysis" section (\ref{sec:analysis}).
 
@@
 code injection vulnerabilities.
-We can identify three approaches, namely:
+We can identify three approaches:
 {\it design-based}, {\it behavior-based} and {\it hybrid}.
@@
 immune to different attack vectors by design~\cite{JL75,L81}. 
-The behavior-based category incorporates a variety of
-schemes that inspect the behavior of applications
-and detect attacks based on specific criteria~\cite{D76,A00}.
-Hybrid mechanisms borrow characteristics from both categories.
-Table~\ref{tab:comp} groups the various subcategories
-and for every mechanism provides the following:
+%% PL:
+%% Explain what "by design" means.
+The behavior-based category incorporates a variety of schemes that
+inspect the behavior of applications and detect attacks based on
+specific criteria~\cite{D76,A00}, that is, on specific behavioral
+patterns. Hybrid mechanisms borrow characteristics from both
+categories. Table~\ref{tab:comp} groups the various subcategories and
+for every mechanism provides the following:
 
 \begin{enumerate}
-\item The number of citations of the publication(s) where
-the mechanism was presented.
+\item The number of times the corresponding publication has been cited.
 \item Quadruples that show the values of true
@@
 
-Table~\ref{tab:avail} presents
-our findings regarding the availability of the mechanism
-in terms of source code and corresponding executables.
-We also examined the availability of the testbeds mentioned in the paper.
-The check mark (\tick) indicates that at some point within the publication,
-there is a homepage where the reader can refer to, to download the
-corresponding software. {\bf AO} (Available On-line) suggests that
-the software is available on-line but the address was not mentioned
-in the paper, which probably indicates that the authors made
-it available after the publication. The question mark ({\bf ?}),
-indicates that the a homepage for the software was included
+Table~\ref{tab:avail} presents our findings regarding the availability
+of the mechanism in terms of source code and corresponding
+executables. We also examined the availability of the testbeds
+mentioned in the paper. The check mark (\tick) indicates that at some
+point within the publication, there is a homepage where the reader can
+refer to, to download the corresponding software. {\bf AO} (Available
+On-line) suggests that the software is available on-line but the
+address was not mentioned in the paper, which probably indicates that
+the authors made it available after the publication. The question mark
+({\bf ?}), indicates that the a homepage for the software was included
 in the publication but now it is not available.
+%% PL: Do we need this paragraph here? Before we say that we tread
+%% availability in the upcoming ``Analysis'' section.
 
 Finally, as we mentioned in Subsection~\ref{sec:model},
-Figure~\ref{fig:attacks} illustrates for each mechanism
-(found in the figure's caption), the point where
-it detects attacks.
+Figure~\ref{fig:attacks} illustrates for each mechanism (found in the
+figure's caption), the point where it detects attacks.
 
@@
 
-Here we analyze the three basic design-based approaches
-used to protect web applications from the attacks we
-discussed in Section~\ref{sec:attacks}.
+There exist three basic design-based approaches used to protect web
+applications from executable source code injection attacks.
 
@@
 
-The key idea behind this approach, is to compare
+The key idea behind this approach is to compare
 the tree representation of the abstract syntactic
@@
 and detect the attack before a query reaches the
-database (locus {\sc z}).
+database (Locus {\sc z}).
 Contrary to {\sc sqlg}uard (and other
@@
 as we will see in Subsection~\ref{sec:hybrid}.
+%% PL This paragraph repeats the material of the previous one, doesn't
+%% it?
 
@@
 This approach is used to detect attacks that target web users.
+%% PL All of them more or less target web users, correct?
 When using a framework that implements
@@
 specific security policies on the server side.
+%% PL What kind of policies are these? Syntax-based, pattern matching?
 Then the policies are enforced either in the user's
@@
 a set of policies Noxes allows or blocks
-the request (locus {\sc x}). Such policies
+the request (Locus {\sc x}). Such policies
 can be also provided by the server (i.e. ``never
@@
 scripts inside {\sc html} elements like {\tt div}.
-The web browser (locus {\sc x}), parses the
+The web browser (Locus {\sc x}), parses the
 {\sc dom} tree and executes scripts only when they
@@
 many similarities with the {\it return-to-lib}
-attack~\cite{SPPGMMB04}. When performing an
-attack like this the malicious user transfers the
-execution to points that contain script
-code which in turn is used to perform the attack.
+attack~\cite{SPPGMMB04}. 
+%% PL Explain what it does, I guess it's what you go on to say
+%% directly below?
+When performing an attack like this the malicious user transfers the
+execution to points that contain script code which in turn is used to
+perform the attack.
 
@@
 to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
-acts as a proxy on the server side (locus {\sc y}) to
+acts as a proxy on the server side (Locus {\sc y}) to
 parse the {\sc html} of server responses and identifies
 scripts. Then, it rewrites them into safe equivalents
-and protect the web user from exploitations
+and protects the web user from exploits
 that are based on reported browser vulnerabilities.
@@
 JavaScript functions. In both cases, policy enforcement takes
-place on the JavaScript engine of the browser (locus {\sc x}).
+place on the JavaScript engine of the browser (Locus {\sc x}).
+%% PL In which way is this a kind of policy enforcement?
 In this way, {\sc xxs} attacks that take advantage
@@
 {\sc soma}~\cite{OWVS08} are two frameworks that
-can actually detect such an attack (locus {\sc x}).
+can actually detect such an attack (Locus {\sc x}).
 To achieve this, {\sc soma} requires site administrators
@@
 attacks are usually implemented in the form of a
-server-side proxy (locus {\sc y})
+server-side proxy (Locus {\sc y})
 interposing on the client-server communication, and modifying
@@
 examines cross-domain interactions, to design a
-cross-domain policy on the client's side (locus {\sc x}).
+cross-domain policy on the client's side (Locus {\sc x}).
 The policy is based on the concept of a relaxed
@@
 
-Most of the aforementioned frameworks, involve
+Most of the aforementioned frameworks involve
 several deployment issues since they
 require significant source modifications by the
-developers on the server-side, in order to
+developers on the server-side in order to
 introduce the policies.
@@
 
-{\sc isr} is a method that has been applied to counter
-different kinds of application attacks~\cite{K09b,KKP03}.
-The main idea behind it, is to separate code from
-data by randomizing the legitimate code's 
-execution environment. In this way, the malicious code
-injected by the attackers who do not know the randomization
-algorithm, will not get executed.
-
-{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr}
-to detect {\sc sql} injection attacks. It works in the following manner:
-initially, it allows programmers to create {\sc sql} statements
-using randomized instructions instead of standard keywords.
-The modified queries are reconstructed at runtime using
-the same key that is inaccessible to the malicious user.
-{\sc sql}rand is one of the few mechanisms that
-detect {\sc sql} injection attacks on the database
-level (locus $\Omega$).
-
-In the case of {\sc xss} attacks that are based on JavaScript
-or {\sc html}, consider a {\sc xor} function that encodes all source of a web
-page on the server-side and then, on the client-side, the web browser decodes the
-source by applying the same function again (locus {\sc x}).
-Variations of this approach include:
-{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
-which randomize the instruction set of {\sc html} and
-JavaScript respectively.
-Contrary to x{\sc js}, in Noncespaces administrators must set
-specific policies in a manner similar to a firewall
-configuration language. This fact, together with the
-insufficient testing of the mechanism (see Table~\ref{tab:comp})
-brings up questions concerning its diagnostic performance.
-{\it {\sc sm}ask}~\cite{JB07} is another framework
-that was inspired by {\sc isr}. To detect {\sc xss}
-attacks it searches for {\sc html} and JavaScript
-keywords within the application's legitimate code.
-This is done before the processing of an {\sc http}
-request. When it finds one it adds a token to it.
-This results to a ``code mask". Then,
-before sending the resulting {\sc html} data to the
-web user, the framework searches the data for
-illegal code by using the same keywords (locus {\sc y}).
-Since all legitimate code has been ``masked",
-the injected code can be identified.
-The pre- and post-processing of the code though,
-may add a significant overhead to the application.
-Unfortunately, the authors of {\sc sm}ask
-did not provide measurements regarding the
-computational performance of the tool (see Table~\ref{tab:comp}).
-
-{\sc isr} is a deterministic approach that can be applied
-to detect different attacks in an efficient manner.
-However, Sovarel et al.~\cite{SEP05}
-have investigated thoroughly the effectiveness
-of {\sc isr} and showed that a malicious user
-may be able to circumvent it by determining
-the randomization key and their results
-indicate that doing {\sc isr} in a way that
-provides a certain degree of security against a motivated
-attacker is more difficult than previously thought.
-Furthermore, developers who wish to use
-such mechanisms must follow good coding practices
-and never show a randomized code statement in any case
-(i.e. an exception error) because in this way
-they will reveal the encoding key.
-
-Even though the above implementations impose a low
-computational overhead, they impose an infrastructure
-overhead. In particular, in the case of {\sc sql}rand
-the integration of a proxy within the database server
-is required while Noncespaces and x{\sc js} require
-modifications on both the server and the client.
+{\sc isr} is a method that has been applied to counter different kinds
+of application attacks~\cite{K09b,KKP03}. The main idea behind it is
+to separate code from data by randomizing the legitimate code's
+execution environment. In this way, the malicious code injected by the
+attackers who do not know the randomization algorithm, will not get
+executed.
+
+{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr} to detect {\sc
+  sql} injection attacks. It allows programmers to create {\sc sql}
+statements using randomized instructions instead of standard keywords.
+The modified queries are reconstructed at runtime using the same key
+that is inaccessible to the malicious user. {\sc sql}rand is one of
+the few mechanisms that detect {\sc sql} injection attacks on the
+database level (Locus $\Omega$).
+
+In the case of {\sc xss} attacks that are based on JavaScript or {\sc
+  html}, consider a {\sc xor} function that encodes all source of a
+web page on the server-side and then, on the client-side, the web
+browser decodes the source by applying the same function again (Locus
+{\sc x}). Variations of this approach include {\it
+  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
+randomize the instruction set of {\sc html} and JavaScript
+respectively. Contrary to x{\sc js}, in Noncespaces administrators
+must set specific policies in a manner similar to a firewall
+configuration language. This fact, together with the insufficient
+testing of the mechanism (see Table~\ref{tab:comp}) brings up
+questions concerning its diagnostic performance. {\it {\sc
+    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
+  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
+JavaScript keywords within the application's legitimate code. This is
+done before the processing of an {\sc http} request. When it finds one
+it adds a token to it. This results to a ``code mask". Then, before
+sending the resulting {\sc html} data to the web user, the framework
+searches the data for illegal code by using the same keywords (Locus
+{\sc y}). Since all legitimate code has been ``masked", the injected
+code can be identified. The pre- and post-processing of the code
+though, may add a significant overhead to the application.
+Unfortunately, the authors of {\sc sm}ask did not provide measurements
+regarding the computational performance of the tool (see
+Table~\ref{tab:comp}).
+
+{\sc isr} is a deterministic approach that can be applied to detect
+different attacks in an efficient manner. However, Sovarel et
+al.~\cite{SEP05} have investigated thoroughly the effectiveness of
+{\sc isr} and showed that a malicious user may be able to circumvent
+it by determining the randomization key and their results indicate
+that doing {\sc isr} in a way that provides a certain degree of
+security against a motivated attacker is more difficult than
+previously thought. Furthermore, developers who wish to use such
+mechanisms must follow good coding practices and never show a
+randomized code statement in any case (i.e. an exception error)
+because in this way they will reveal the encoding key.
+
+Even though the above implementations impose a low computational
+overhead, they impose an infrastructure overhead. In particular, in
+{\sc sql}rand requires the integration of a proxy within the database
+server, while Noncespaces and x{\sc js} require modifications on both
+the server and the client.
 
@@
 
-Taint tracking is provided as a feature in some
-programming languages, such as Perl and Ruby.
-By enabling the feature, Perl would refuse to run code
-vulnerable to an {\sc sql} injection attack
-(consider a tainted variable being used in a query)
-and exit with an error message.
+Taint tracking is provided as a feature in some programming languages,
+such as Perl and Ruby. By enabling the feature, Perl would refuse to
+run code vulnerable to an {\sc sql} injection attack (consider a
+tainted variable being used in a query) and would exit with an error
+message.
 
@@
 tainted string is used as an argument to a sink method
-then an exception is raised (locus {\sc z}).
+then an exception is raised (Locus {\sc z}).
 However, this is a simplistic approach that may
 lead to many false positives.
-
-The following schemes apply further checks when
-they identify that tainted data have reached a sink
-(locus {\sc z}).
-In particular, {\it Xu et al.}~\cite{XBS06}
-tracks taint information at the level of bytes in memory.
-To distinguish between legitimate and malicious uses
-of untrusted data that reach a sink,
-they search the data for suspicious symbols by using
-regular expressions. {\sc csse}~\cite{PB05} associates
-tainted data with specific metadata. Such metadata include
-the origins of tainted data, its propagation within the application
-and others. When tainted data reaches a sink {\sc csse} performs
-syntactic checks based on the aforementioned metadata
-(locus {\sc z}). {\it {\sc php} Aspis}~\cite{PMP11} works
-in a similar way. To obtain metadata, it takes advantage
-of specific features provided by {\sc php}.
+%% PL better to avoid characterisations and mention only the facts
+%% (that it leads to many false positives, as shown by ...
+
+It is possible to apply further checks when it is established that
+tainted data have reached a sink (Locus {\sc z}). {\it Xu et
+  al.}~\cite{XBS06} track taint information at the level of bytes in
+memory. To distinguish between legitimate and malicious uses of
+untrusted data that reach a sink, they search the data for suspicious
+symbols by using regular expressions. {\sc csse}~\cite{PB05}
+associates tainted data with specific metadata. Such metadata include
+the origins of tainted data, its propagation within the application,
+and others. When tainted data reaches a sink, {\sc csse} performs
+syntactic checks based on the aforementioned metadata (Locus {\sc z}).
+{\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
+metadata, it takes advantage of specific features provided by {\sc
+  php}.
+%% PL Like what?
 % Note that the above schemes detect potential attacks
@@
 if there are tainted data that contain scripts (locus {\sc y}).
-A recent study showed that there are ways to circumvent
-the majority of the above schemes~\cite{NBR14}.
-Furthermore, most of them are not easy to deploy since
-the majority of input vectors, string operations
+
+A recent study showed that there are ways to circumvent the majority
+of the above schemes~\cite{NBR14}. Furthermore, most of them are not
+easy to deploy since the majority of input vectors, string operations
 and output vectors of the application must be instrumented.
 
-{\it Vogt et al.}~\cite{VFJKKV07}
-have developed a tainting scheme that follows a different
-approach. Contrary to the aforementioned schemes that
-operate on the server side, they track sensitive
-information on the client side (locus {\sc x}).
-This is a form of positive taint tracking, where
-taint data is considered to be legitimate.
-Their scheme detects JavaScript-driven {\sc xss}
-attacks by ensuring that a script can send sensitive
-user data only to the site from which it came from.
-This though, may lead to false alarms.
-{\it Stock et al.}~\cite{SLMS14} propose a scheme
-that also operates in the browser (locus {\sc x}).
-The scheme focuses on the detection of
-{\sc dom}-based {\sc xss} attacks.
-In such an attack, the malicious payload is
-executed as a result of the modification of the
-{\sc dom} environment so that the client-side
-code runs in an unanticipated manner even if the
-{\sc http} response that triggers the injection seems legitimate.
-The scheme is different from the previous one because it
-marks and observes data that are considered harmful.
-Specifically, it employs a taint-enhanced JavaScript
-engine that tracks the flow of attacker-controlled data.
-To detect potential attacks the scheme utilizes
-{\sc html} and JavaScript parsers that can
-identify the generation of code coming from
-tainted data.
+{\it Vogt et al.}~\cite{VFJKKV07} have developed a tainting scheme
+that follows a different approach. Contrary to the aforementioned
+schemes that operate on the server side, they track sensitive
+information on the client side (Locus {\sc x}). This is a form of
+positive taint tracking, where taint data is considered to be
+legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
+by ensuring that a script can send sensitive user data only to the
+site from which it came from. This though, may lead to false alarms.
+%% PL You mean a lot of false alarms?
+{\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
+in the browser (Locus {\sc x}). The scheme focuses on the detection of
+{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
+payload is executed as a result of the modification of the {\sc dom}
+environment so that the client-side code runs in an unanticipated
+manner even if the {\sc http} response that triggers the injection
+seems legitimate. The scheme is different from the previous one
+because it marks and observes data that are considered harmful.
+Specifically, it employs a taint-enhanced JavaScript engine that
+tracks the flow of attacker-controlled data. To detect potential
+attacks the scheme utilizes {\sc html} and JavaScript parsers that can
+identify the generation of code coming from tainted data.
 
@@
 Training methods that detect {\sc dsl}-driven injection attacks
-generate and store valid code statements (i.e. {\sc sql}
-or {\sc xp}ath queries) in various forms, and detect attacks
-as outliers from the set of valid code statements.
-An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
-{\sc sql} injection (locus $\Omega$) attacks by recording all database transactions.
-Subsequent refinements by Valeur et al.~\cite{VMV05}
-tagged each transaction with the corresponding application
-as an extension of their anomaly detection framework called
-{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} is
-a signature-based mechanism that prevents {\sc sql} and
-{\sc xp}ath injection attacks. The signatures generated
-during a training phase, are based on features that can
-depend either on the code statement or on its execution
-environment (i.e. the stack trace).
-Then, at runtime, the mechanism checks all statements for compliance
-and can block code statements containing injected elements (locus {\sc z}).
-Furthermore, {\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool
-that also detects {\sc sql} injection attacks (locus {\sc z})
-by associating a query model with the location of every
-{\sc sql} statement within the application.
-Then at runtime, monitors the application's execution to
-detect when {\sc sql} statements diverge from the expected model.
-
-In the case of {\sc xss} attacks the various countermeasures
-follow a similar pattern. {\it {\sc swap}}~\cite{WPLKK09}
-creates a unique identifier ({\it script {\sc id}}) for
-every legitimate script on the server.
-Then, a JavaScript detection component placed in a
-web proxy (locus {\sc y}) searches for injected scripts
-with no corresponding {\sc id} in the server's responses.
-If no injected scripts are found, the proxy forwards the
-request to the client. This mechanism is relatively
-inflexible since it does not support dynamic scripts.
-In addition it imposes a significant overhead (see Table~\ref{tab:comp}).
-The authors of {\it {\sc xssds}}~\cite{JEP08}
-have implemented a similar mechanism that also supports
-dynamic and external scripts. Specifically,
-during training phase they build a list of all benign scripts.
-In the case of external scripts they keep a white list
-of all the valid domain names that contain scripts
-used by the application.
-
-The training subcategory, includes some mechanisms
-that can be easily circumvented. For example,
-consider an application that will send the password 
-for a forgetful user via email by executing
-the following query:
-\bgroup
-\lstset{language=SQL}
+generate and store valid code statements (i.e. {\sc sql} or {\sc
+  xp}ath queries) in various forms, and detect attacks as outliers
+from the set of valid code statements. An early approach, {\it {\sc
+    didafit}}~\cite{LLW02} detects {\sc sql} injection (Locus
+$\Omega$) attacks by recording all database transactions. Subsequent
+refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
+the corresponding application as an extension of their anomaly
+detection framework called {\it libAnomaly}. {\it {\sc
+    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
+that prevents {\sc sql} and {\sc xp}ath injection attacks. The
+signatures generated during a training phase are based on features
+that can depend either on the code statement or on its execution
+environment (i.e. the stack trace). Then, at runtime, the mechanism
+checks all statements for compliance and can block code statements
+containing injected elements (Locus {\sc z}). {\sc
+  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
+  sql} injection attacks (locus {\sc z}) by associating a query model
+with the location of every {\sc sql} statement within the application.
+Then, at runtime, it monitors the application's execution to detect
+when {\sc sql} statements diverge from the expected model.
+
+Various countermeasures against {\sc xss} attacks follow a similar
+pattern. {\it {\sc swap}}~\cite{WPLKK09} creates a unique identifier
+({\it script {\sc id}}) for every legitimate script on the server.
+Then, a JavaScript detection component placed in a web proxy (Locus
+{\sc y}) searches for injected scripts with no corresponding {\sc id}
+in the server's responses. If no injected scripts are found, the proxy
+forwards the request to the client. This mechanism is relatively
+inflexible since it does not support dynamic scripts. In addition it
+imposes a significant overhead (see Table~\ref{tab:comp}). The authors
+of {\it {\sc xssds}}~\cite{JEP08} have implemented a similar mechanism
+that also supports dynamic and external scripts. Specifically, during
+training phase they build a list of all benign scripts. In the case of
+external scripts they keep a white list of all the valid domain names
+that contain scripts used by the application.
+
+Defenses based on training include some mechanisms that can be easily
+circumvented. For example, consider an application that will send the
+password for a forgetful user via email by executing the following
+query: \bgroup \lstset{language=SQL}
 \begin{small}
@@
 \noindent
+%% PL I do not understand what is specific to training here; most
+%% classic SQL injection attacks work in this way.
 However, mechanisms that create signatures that involve
@@
 like the one mentioned in Subsubsection~\ref{sec:policy}.
+%% PL Like the return-to-lib attack?
 
@@
 
-{\sc xss-guard}~\cite{BV08} is a training scheme
-that also employs parse-tree validation.
-During training, the scheme maps legitimate scripts
-to {\sc http} responses. During production
-{\sc xss-guard} retrieves for every script included
-in a response its parsed tree and checks if it
-is one of those previously mapped to this response.
-Apart from the comparison of the parsed trees, {\sc xss-guard}
-checks also for an exact match of lexical entities.
-To achieve this, the scheme utilizes that data structures
-of Firefox's JavaScript engine (locus {\sc x}).
-However, string literals are not compared literally
-thus, a possible false negative result could occur if an
-adversary performs a mimicry attack~\cite{WS02}.
-For example, consider a banner rotator that
-every time it runs, it creates a value that depends on
-the current date and the length of the array that
-contains the references of the various images to be displayed.
-Then, based on this value it shows a specific
-image to a user. In a vulnerable web site that allows
-users to post data and contains this banner
-rotator, a malicious user could create and store a script
-that has the same code structure, with the same JavaScript
-keywords like the above. In this script the
-attacker could also include references to tiny
-images hosted on a web server that is maintained by him in order
-to retrieve the {\sc ip} addresses of the
-users that visit the vulnerable site.
-
-{\it Blueprint}~\cite{LV09} is a policy
-enforcement framework that also utilizes parsed trees
-to detect {\sc xss} attacks. To guarantee
-that untrusted content is not executed, Blueprint generates
-on the server-side a parsed tree from untrusted {\sc html}
-to ensure that it does not contain any dynamic content.
-Then the parsed tree is transfered to the document
-generator of the browser (locus {\sc x}) where untrusted
-browser parsing behavior is ruled out.
-Blueprint is an efficient countermeasure but it
-imposes a significant overhead due to its
-extensive parsing (see Table~\ref{tab:comp}).
-
-{\it Diglossia}~\cite{SMS13} combines positive taint tracking
-(see Subsubsection~\ref{sec:taint}) together with
-parse-tree validation. Diglossia was based on the
-theory of Ray and Ligatti~\cite{RL12b} (also see
-Section~\ref{sec:attacks}) to detect {\sc dsl}
-code injection attacks. In addition, it is actually
-the first, and so far the only framework that detects
-No{\sc sql} injection attacks.
-When an application computes an output string (query),
-Diglossia computes a ``shadow" of this string.
-Specifically, it maps all characters introduced by
-the application to a shadow character set.
-This set does not contain any characters coming
-from the tainted input. Then, the scheme
-creates the tree of the query that
-is about to be executed and compares it with the parsed tree
-of the ``shadow" (locus {\sc z}).
-If the trees are not equal the application is probably
-under attack. Note that, Diglossia can be bypassed in the same
-way as other taint tracking approaches~\cite{NBR14}.
+{\sc xss-guard}~\cite{BV08} is a training scheme that also employs
+parse-tree validation. During training, the scheme maps legitimate
+scripts to {\sc http} responses. During production {\sc xss-guard}
+retrieves for every script included in a response its parsed tree and
+checks if it is one of those previously mapped to this response. Apart
+from the comparison of the parsed trees, {\sc xss-guard} checks also
+for an exact match of lexical entities. To achieve this, the scheme
+utilizes that data structures of Firefox's JavaScript engine (Locus
+{\sc x}). However, string literals are not compared literally and
+therefore a false negative result could occur if an adversary performs
+a mimicry attack~\cite{WS02}. For example, consider a banner rotator
+that every time it runs, it creates a value that depends on the
+current date and the length of the array that contains the references
+of the various images to be displayed. Then, based on this value it
+shows a specific image to a user. In a vulnerable web site that allows
+users to post data and contains this banner rotator, a malicious user
+could create and store a script that has the same code structure, with
+the same JavaScript keywords like the above.
+%% You mean like the rotator?
+In this script the attacker could also include references to tiny
+images hosted on a web server that is maintained by him in order to
+retrieve the {\sc ip} addresses of the users that visit the vulnerable
+site.
+
+{\it Blueprint}~\cite{LV09} is a policy enforcement framework that
+also utilizes parsed trees to detect {\sc xss} attacks. To guarantee
+that untrusted content is not executed, Blueprint generates on the
+server-side a parsed tree from untrusted {\sc html} to ensure that it
+does not contain any dynamic content. Then the parsed tree is
+transfered to the document generator of the browser (Locus {\sc x})
+where untrusted browser parsing behavior is ruled out. Blueprint is an
+efficient countermeasure but it imposes a significant overhead due to
+its extensive parsing (see Table~\ref{tab:comp}).
+
+{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
+Subsubsection~\ref{sec:taint}) together with parse-tree validation.
+Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
+(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
+injection attacks. In addition, it is actually the first, and so far
+the only framework that detects No{\sc sql} injection attacks. When an
+application computes an output string (query), Diglossia computes a
+``shadow" of this string. Specifically, it maps all characters
+introduced by the application to a shadow character set. This set does
+not contain any characters coming from the tainted input. Then, the
+scheme creates the tree of the query that is about to be executed and
+compares it with the parsed tree of the ``shadow" (locus {\sc z}). If
+the trees are not equal the application is probably under attack. Note
+that Diglossia can be bypassed in the same way as other taint
+tracking approaches~\cite{NBR14}.
+%% PL which way is this exactly?
 

### 2014-11-07 docs/questioning.tex
add PL prefix
addressed PL comments

@@
 We can identify three approaches:
-{\it design-based}, {\it behavior-based} and {\it hybrid}.
-The design-based category involves mechanisms that make applications
-immune to different attack vectors by design~\cite{JL75,L81}. 
+{\it etiological}, {\it symptomatic} and {\it hybrid}.
+The etiological category involves mechanisms designed to
+stop attacks based on their causes and origins~\cite{JL75,L81}. 
 %% PL:
 %% Explain what "by design" means.
-The behavior-based category incorporates a variety of schemes that
+The symptomatic category incorporates a variety of schemes that
 inspect the behavior of applications and detect attacks based on
-specific criteria~\cite{D76,A00}, that is, on specific behavioral
-patterns. Hybrid mechanisms borrow characteristics from both
+their undesirable symptoms~\cite{D76,A00}.
+Hybrid mechanisms borrow characteristics from both
 categories. Table~\ref{tab:comp} groups the various subcategories and
@@
 
-Table~\ref{tab:avail} presents our findings regarding the availability
-of the mechanism in terms of source code and corresponding
-executables. We also examined the availability of the testbeds
-mentioned in the paper. The check mark (\tick) indicates that at some
-point within the publication, there is a homepage where the reader can
-refer to, to download the corresponding software. {\bf AO} (Available
-On-line) suggests that the software is available on-line but the
-address was not mentioned in the paper, which probably indicates that
-the authors made it available after the publication. The question mark
-({\bf ?}), indicates that the a homepage for the software was included
-in the publication but now it is not available.
-%% PL: Do we need this paragraph here? Before we say that we tread
-%% availability in the upcoming ``Analysis'' section.
-
 Finally, as we mentioned in Subsection~\ref{sec:model},
@@
 
-\subsection{Design-Based}
+\subsection{Etiological}
 \label{sec:prot}
 
-There exist three basic design-based approaches used to protect web
+There exist three basic etiological approaches used to protect web
 applications from executable source code injection attacks.
@@
 
-As we will see in Subsection~\ref{sec:hybrid},
-there are mechanisms that borrow elements from
-this approach and examine the syntax trees
-of scripts to detect JavaScript-driven {\sc xss} attacks.
-
 Parse-tree validation seems to be an efficient approach
@@
 implementation. This however does not apply in
-the case of the mechanisms that utilize
-this approach to detect JavaScript-driven {\sc xss} attacks
+the case of the mechanisms that borrow elements from
+this approach and examine the syntax trees
+of scripts to detect JavaScript-driven {\sc xss} attacks
 as we will see in Subsection~\ref{sec:hybrid}.
@@
 
-This approach is used to detect attacks that target web users.
+This approach is used to detect {\sc xss} and {\sc csrf} attacks.
 %% PL All of them more or less target web users, correct?
@@
 specific security policies on the server side.
+Policies can be expressed through JavaScript extensions,
+pattern matching or syntax specific settings.
 %% PL What kind of policies are these? Syntax-based, pattern matching?
@@
 injection attacks known as return-to-JavaScript
-attack~\cite{APKLM10} can be used to bypass
-the above mechanisms. Such attacks share
-many similarities with the {\it return-to-lib}
-attack~\cite{SPPGMMB04}. 
+attack can be used to bypass the above mechanisms
+as described extensively in reference~\cite{APKLM10}.
+% Such attacks share
+% many similarities with the {\it return-to-lib}
+% attack~\cite{SPPGMMB04}. 
 %% PL Explain what it does, I guess it's what you go on to say
 %% directly below?
-When performing an attack like this the malicious user transfers the
-execution to points that contain script code which in turn is used to
-perform the attack.
+% When performing an attack like this the malicious user transfers the
+% execution to points that contain script code which in turn is used to
+% perform the attack.
 
@@
 
-\subsection{Behavior-Based}
-
-In this section we examine the two main behavior-based
+\subsection{Symptomatic}
+
+In this section we examine the two main symptomatic
 approaches.
@@
 then an exception is raised (Locus {\sc z}).
-However, this is a simplistic approach that may
-lead to many false positives.
+% However, this is a simplistic approach that may
+% lead to many false positives.
 %% PL better to avoid characterisations and mention only the facts
@@
 {\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
-metadata, it takes advantage of specific features provided by {\sc
-  php}.
+metadata, it takes advantage of {\sc php} arrays data structure.
 %% PL Like what?
@@
 
-A recent study showed that there are ways to circumvent the majority
-of the above schemes~\cite{NBR14}. Furthermore, most of them are not
+A recent study~\cite{NBR14} showed that there are ways to circumvent
+the majority of the above schemes. Furthermore, most of them are not
 easy to deploy since the majority of input vectors, string operations
@@
 by ensuring that a script can send sensitive user data only to the
-site from which it came from. This though, may lead to false alarms.
+site from which it came from.
+% This though, may lead to false alarms.
 %% PL You mean a lot of false alarms?
@@
 Defenses based on training include some mechanisms that can be easily
-circumvented. For example, consider an application that will send the
+circumvented. For example, {\sc didafit} records all database
+transactions without tagging each transaction with the
+corresponding call-site. In this case a false negative result
+is prominent. In particular, consider an application that will send the
 password for a forgetful user via email by executing the following
@@
 {\sc xss} attacks based on JavaScript injection
-would fail to detect a return-to-JavaScript attack
-like the one mentioned in Subsubsection~\ref{sec:policy}.
+would fail to detect a return-to-JavaScript
+attack~\ref{sec:policy}.
 %% PL Like the return-to-lib attack?
@@
 could create and store a script that has the same code structure, with
-the same JavaScript keywords like the above.
-%% You mean like the rotator?
+the same JavaScript keywords contained in the rotator script.
+%% PL You mean like the rotator?
 In this script the attacker could also include references to tiny
@@
 that Diglossia can be bypassed in the same way as other taint
-tracking approaches~\cite{NBR14}.
+tracking approaches and is described in reference~\cite{NBR14}.
 %% PL which way is this exactly?
@@
 % at all, we see that they are mostly coming from
-% the design-based category.
+% the etiological category.
 
 % Comment 2: Note though that implementations
-% of design-based mechanisms can actually
+% of etiological mechanisms can actually
 % be bypassed.
@@
 \subsection{Availability}
+
+Table~\ref{tab:avail} presents our findings regarding the availability
+of the mechanism in terms of source code and corresponding
+executables. We also examined the availability of the testbeds
+mentioned in the paper. The check mark (\tick) indicates that at some
+point within the publication, there is a homepage where the reader can
+refer to, to download the corresponding software. {\bf AO} (Available
+On-line) suggests that the software is available on-line but the
+address was not mentioned in the paper, which probably indicates that
+the authors made it available after the publication. The question mark
+({\bf ?}), indicates that the a homepage for the software was included
+in the publication but now it is not available.
 
@@
 \begin{enumerate}
-\item Note that most mechanisms that implement design-based
+\item Note that most mechanisms that implement etiological
 approaches have not been extensively tested in terms of

### 2014-11-07 docs/questioning.tex
some changes

@@
 content into the page. {\sc html} injection is mainly associated
-with {\sc xss} defects.
+with {\sc xss} defects~\cite{HNSHS12}.
 
@@
     didafit}}~\cite{LLW02} detects {\sc sql} injection (Locus
-$\Omega$) attacks by recording all database transactions. Subsequent
+$\Omega$) attacks by recording all database transactions
+(stripped from user input). Subsequent
 refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
@@
 corresponding call-site. In this case a false negative result
-is prominent. In particular, consider an application that will send the
+is prominent. For instance, consider an application that will send the
 password for a forgetful user via email by executing the following
@@
 \noindent
-A traditional {\sc sql} injection attack protection system like {\sc didafit},
-could be easily escaped since a malicious user, could obtain the
-administrator's password by email by entering on the password retrieval form
+In this case {\sc didafit}, could be easily escaped
+since a malicious user, could obtain the administrator's password
+by email by entering on the password retrieval form
 as his user identifier the following:
@@
 would fail to detect a return-to-JavaScript
-attack~\ref{sec:policy}.
+attack~\ref{APKLM10}.
 %% PL Like the return-to-lib attack?
@@
 	If no testing has taken place we add a question mark ({\bf ?}).
-    \item[3] For every overhead we show if the overhead is applied to the server ({\sc s}) or the client ({\sc c}). 
+    \item[3] Regarding the computational overhead we show if it is applied to the server ({\sc s}) or the client ({\sc c}). 
     \item[4] The numbers of this quadruple involve requests.
@@
 
-% Cite~\cite{HNSHS12}.
-
 \bibliographystyle{IEEEtran}

### 2014-11-07 docs/questioning.tex
some changes

@@
 that Diglossia can be bypassed in the same way as other taint
-tracking approaches and is described in reference~\cite{NBR14}.
+tracking approaches as described in reference~\cite{NBR14}.
 %% PL which way is this exactly?
@@
 	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
-	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & +1{\it ms} ({\sc s}) & {\sc sql} injection \\
+	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & 1{\it ms} ({\sc s}) & {\sc sql} injection \\
 	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & $\sim$180\% ({\sc s}) & {\sc xss} \\ 
+  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
 	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql} and {\sc xp}ath injection \\

### 2014-11-07 docs/questioning.tex
add Nature reference for code sharing

@@
 \subsection{Availability}
+
+To ensure replicability of research results the source code
+implementing a detection mechanism should be available to researchers.
+Ideally the code should be available under an open source license, so
+that it is easy to modify and improve an approach; even when this is
+not possible, for whatever reason, it is important to make sure that
+all computer code and test data is available noting any restrictions
+on accessibility. Availability of computer code has been recognised as
+an important issue outside the computer science field: the journal
+Nature, in a recent editorial, adopted a publication policy stressing
+access to code and data~\cite{nature2014}. At a time and date that the
+merits of open access to code are discussed in non computer science
+journals~\cite{easterbrook2014} we should expect computer scientists
+to lead the way.
 

### 2014-11-07 docs/questioning.tex
minor changes

@@
 when building security mechanisms that protect
-applications~\cite{A01,A00,SPWS13}. Based on this analysis
-we can identify the advantages and disadvantages of the
+applications~\cite{A01,A00,SPWS13,nature2014}.
+Based on this analysis we can identify the advantages
+and disadvantages of the
 various mechanisms and enumerate some of their common
@@
 would fail to detect a return-to-JavaScript
-attack~\ref{APKLM10}.
+attack~\cite{APKLM10}.
 %% PL Like the return-to-lib attack?

### 2014-11-07 docs/questioning.tex
minor correction and addition

@@
 we include protection mechanisms that counter
-such attacks when they take place.
+such attacks when they take place. Static or
+dynamic analyzers that examine applications to
+identify vulnerabilities that may lead to the attacks
+that we described earlier are out of the scope of this paper.
 Also, countermeasures that prevent {\sc sql}
@@
 password for a forgetful user via email by executing the following
-query: \bgroup \lstset{language=SQL}
+query:
+\bgroup
+\lstset{language=SQL}
 \begin{small}
@@
 	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
-	&   {\it libAnomaly}~\cite{VMV05} & 226 & (344,15646,60,0)\_r & 1{\it ms} ({\sc s}) & {\sc sql} injection \\
+	&   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql} injection \\
 	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\

### 2014-11-08 docs/questioning.tex
more work on the analysis section

@@
 Michalis Polychronakis,\IEEEauthorrefmark{1}
-and Angelos Keromytis\IEEEauthorrefmark{1}}
+and Angelos D. Keromytis\IEEEauthorrefmark{1}}
 \IEEEauthorblockA{\IEEEauthorrefmark{1}
@@
 
+Here we comment on how the mechanisms that we
+described earlier, were tested in terms of both
+diagnostic and computational performance.
+
 \subsubsection{Diagnostic Performance}
@@
 
-Table~\ref{tab:comp} indicates that 27 out of
+Table~\ref{tab:comp} indicates that the authors of 3 out of 34
+({\bf 8.8\%}) publications, provided complete quadruples.
+On the other hand, we see that 4 out of
+34 ({\bf 11.7\%}) were not tested at all
+in terms of diagnostic performance. In this cases,
+all the four elements of the quadruples are not
+available ({\sc na}).
+% Maybe we should comment on the fact that these are
+% frameworks coming from the etiological category
+% and detect the attacks ``by design".
+An interesting observation is that 10 out of 34
+({\bf 29.41\%}) of the authors performed only attacks
+during their tests and did not test their mechanisms
+to see if they produce any false alarms. The corresponding
+quadruples in this case, are the ones that contain {\sc tp} and
+{\sc fn} results but {\sc tn} and {\sc fp} results are not
+available ({\sc na}). This stresses the fact that authors
+of these mechanisms were more interested to make sure that
+their mechanisms can detect known attacks than to see how
+they respond under normal conditions.
+In some occasions (where the number of {\sc tp} results
+are not quantified), authors did not mention how many or
+which attacks they performed.
+Moreover, we observe in some cases, that even if
+the authors report the existence of possible
+false positive and negative results, they have not
+quantified them ({\sc nq}).
+
+Furthermore, we see that 27 out of
 34 mechanisms were tested on real-world applications
@@
 
-\section{Discussion}
+Our first observation indicates that only 6
+out of 34 ({\bf 17.6\%}) of the authors provided a homepage for
+their mechanism through their publication.
+2 from these 6 homepages are currently not available.
+Also, in 5 cases, authors made either the source code
+or their executables available after their paper
+got published. Finally, we observe that only 3
+out of 34 ({\bf 8.8\%}) authors have currently
+their testbeds available on-line.
+
+\section{Discussion and Lessons Learned}
+
+Our findings indicate that currently, the testing of
+the diagnostic performance of
+mechanisms that detect top web application attacks
+has not a standard form. In addition,
+there are many mechanisms that are tested in a poor manner.
+
+A reasonable argument would be that many
+mechanisms (especially the ones coming from the
+etiological category), do not need to be established
+purely through testing since they provide systematic
+arguments as to why their design is secure against attacks.
+However, their implementations are not always efficient
+and as we observed they can be circumvented.
 

### 2014-11-08 docs/questioning.tex
Analysis became Discussion - more on the discussion section.

@@
 detection locus. We treat f) availability separately in the
-``Analysis" section (\ref{sec:analysis}).
+``Discussion" section (\ref{sec:discussion}).
 
@@
 
-\section{Analysis}
-\label{sec:analysis}
+\section{Discussion}
+\label{sec:discussion}
 
@@
 On the other hand, we see that 4 out of
-34 ({\bf 11.7\%}) were not tested at all
-in terms of diagnostic performance. In this cases,
-all the four elements of the quadruples are not
-available ({\sc na}).
+34 ({\bf 11.7\%}) were not tested at all.
+In this cases, all the four elements of the
+quadruples are not available ({\sc na}).
 % Maybe we should comment on the fact that these are
@@
 available ({\sc na}). This stresses the fact that authors
-of these mechanisms were more interested to make sure that
-their mechanisms can detect known attacks than to see how
+maybe more interested into making sure that
+their mechanisms can detect known attacks than seeing how
 they respond under normal conditions.
@@
 which attacks they performed.
-Moreover, we observe in some cases, that even if
+Also, in some cases, we observe that even if
 the authors report the existence of possible
@@
 
-\section{Discussion and Lessons Learned}
-
-Our findings indicate that currently, the testing of
-the diagnostic performance of
+\section{Lessons Learned}
+
+In this section we point out our key findings and
+discuss the lessons derived from our research.
+We also argue that some of our observations may be
+good reasons why the mechanisms are not adopted in practice.
+
+One of our key findings indicate that currently,
+the testing of the diagnostic performance of
 mechanisms that detect top web application attacks
 has not a standard form. In addition,
-there are many mechanisms that are tested in a poor manner.
+there are many mechanisms that are tested in a poor
+manner. In many cases researchers tend not to
+provide the false positive and negative results
+that their tools may produce. Discussing
+about the existence of such results and not
+quantifying them may be a good reason to not use
+such a mechanism.
 
@@
 arguments as to why their design is secure against attacks.
-However, their implementations are not always efficient
+However, implementations are not always efficient
 and as we observed they can be circumvented.

### 2014-11-08 docs/questioning.tex
some changes - more on the discussion

@@
 Defenses based on training include some mechanisms that can be easily
-circumvented. For example, {\sc didafit} records all database
-transactions without tagging each transaction with the
-corresponding call-site. In this case a false negative result
+circumvented. For example, {\sc didafit} and {\it libAnomaly}
+do not tag transactions with their corresponding call-sites.
+In this case a false negative result
 is prominent. For instance, consider an application that will send the
@@
 \noindent
-In this case {\sc didafit}, could be easily escaped
+In this case {\sc didafit} and {\it libAnomaly}, could be easily escaped
 since a malicious user, could obtain the administrator's password
@@
 scheme creates the tree of the query that is about to be executed and
-compares it with the parsed tree of the ``shadow" (locus {\sc z}). If
+compares it with the parsed tree of the ``shadow" (Locus {\sc z}). If
 the trees are not equal the application is probably under attack. Note
@@
 Table~\ref{tab:comp} indicates that the authors of 3 out of 34
-({\bf 8.8\%}) publications, provided complete quadruples.
+(8.8\%) publications, provided complete quadruples.
 On the other hand, we see that 4 out of
-34 ({\bf 11.7\%}) were not tested at all.
+34 (11.7\%) were not tested at all.
 In this cases, all the four elements of the
@@
 An interesting observation is that 10 out of 34
-({\bf 29.41\%}) of the authors performed only attacks
+(29.41\%) of the authors performed only attacks
 during their tests and did not test their mechanisms
@@
 their previous research~\cite{LSJ13}.
-Furthermore, in the publications that
+Finally, in the publications that
 {\sc amnesia}~\cite{HO05,HO06,HO05b}
@@
 From the mechanisms that detect {\sc dsl} code injection
-attacks, 3 out of 13 ({\bf 23\%}) do so at the level
+attacks, 3 out of 13 (23\%) do so at the level
 of the {\sc rdbms} --- locus $\Omega$.
@@
 on the client side. In particular, 11 out of
-19 frameworks ({\bf 57,8\%}) detect JavaScript-driven
+19 frameworks (57,8\%) detect JavaScript-driven
 {\sc xss} attacks at the client's side.
@@
 Our first observation indicates that only 6
-out of 34 ({\bf 17.6\%}) of the authors provided a homepage for
+out of 34 (17.6\%) of the authors provided a homepage for
 their mechanism through their publication.
@@
 got published. Finally, we observe that only 3
-out of 34 ({\bf 8.8\%}) authors have currently
+out of 34 (8.8\%) authors have currently
 their testbeds available on-line.
@@
 and as we observed they can be circumvented.
+
+We believe that our research may facilitate researchers
+or practitioners who would like to use one of the
+aforementioned mechanisms and researchers who would like
+to build new ones. Especially in the second case,
+researchers can utilize our exploitation model as a
+starting point to develop their approach.
 

### 2014-11-08 docs/questioning.tex
add material in Section III

@@
   perspective.
-\item We categorize and analyze previously proposed defenses based on
-  criteria that are considered critical when building protection
-  mechanisms.
-\item A worrying observation is that sometimes researchers test the
-  diagnostic performance of their mechanisms in a poor manner. This
-  turns out as very critical because some of these mechanisms can
-  actually be bypassed.
-\item Also worrying is that researchers do not make their mechanisms
+\item We categorize and analyze proposed defenses using a set of
+  criteria that are important for building protection mechanisms.
+\item We find that researchers often test the diagnostic performance
+  of their mechanisms poorly. 
+\item We also find that researchers do not often make their mechanisms
   available to the community, thus no one can either use their
@@
 
+Research on application attack defense mechanisms has a dual
+character. First, a defense mechanism may be important, and therefore
+publishable, because it shows that an attack can be detected in a
+reliable manner. Secondly, a defense mechanism may be important not
+just as a research contribution, but as a practical tool, if it can be
+put to use by administrators and users to shield their applications
+and services against the detected attacks.
+
+The detection of attacks in a reliable manner can be analyzed using
+criteria common with other research fields:
+\begin{itemize}
+\item Statistical measures that show how reliable the detection really
+  is.
+\item Research practices that promote replication of the findings.
+\end{itemize}
+
+Whether a reliable attack defense mechanism has value in a practical
+setting rests on a different set of criteria:
+\begin{itemize}
+\item What are the overheads imposed by the mechanism?
+\item How easy is it to deploy and use the mechanism?
+\item How robust is it against ways to circumvent it?
+\item At which point of the computation flow does it detect an attack?
+\end{itemize}
+
+The first two criteria are \emph{Diagnostic Performance} and
+\emph{Availability}. The other four criteria are \emph{Computational
+  Performance}, \emph{Ease of Use}, \emph{Security}, and
+\emph{Detection Locus}.
+
 \subsection{Diagnostic Performance}
@@
 must demonstrate the presence of an attack. This, however, does not
-make an application attack defense mechanism immediately useful. In
-order for a detection mechanism to be useful it must be accurate, easy to
-use, and economical. The accuracy of a detection mechanism is gauged
-with the following metrics~\cite{TDR2013,GFDLS06,A00}:
+make an application attack defense mechanism immediately useful. A
+detection mechanism must be reliable. The accuracy of a detection
+mechanism is gauged with the following
+metrics~\cite{TDR2013,GFDLS06,A00}:
 \begin{itemize}
@@
 what allows us to derive them based on test data, without using data
-from a real production environment. At the same time, however, this is
-what limits their usefulness. When we obtain a test result in a
-production environment, be it negative or positive, we really want to
-know how much we should be worried, or relaxed. In other words, if an
-attack is detected in a production environment, how much should we be
-worried? If no attack is detected in a production environment, how
-relaxed should we be that no attack has indeed taken place?
+from a real production environment. At the same time, this is what
+limits their usefulness. When we obtain a test result in a production
+environment, be it negative or positive, we really want to know how
+much we should be worried, or relaxed. In other words, if an attack is
+detected in a production environment, how much should we be worried?
+If no attack is detected in a production environment, how relaxed
+should we be that no attack has indeed taken place?
 
@@
 \end{itemize}
-
-\subsection{Computational Performance}
-
-\subsection{Ease of Use}
-
-\subsection{Security}
-
-\subsection{Detection Locus}
 
@@
 to lead the way.
+
+\subsection{Computational Performance}
+
+All detection mechanisms extract a cost for their use, as they
+introduce some amount of extra computation on an existing application.
+The extra computation depends on the exact defense mechanism. For
+example, it may be some form of run-time checking, or some form of
+obfuscation. Also depending on the mechanism, the cost may be incurred
+on different places: it may take place on a server, affecting service
+performance, or it may take place on the client, or both. The
+usefulness of a detection mechanism depends therefore on the
+computational cost it requires and on where it extracts it, as
+different overheads may be acceptable server-side than client-side.
+For example, reporting absolute measurements gives little information
+on the real overhead, unless separate measurements are given for the
+system under study with and without the proposed mechanism. Percentage
+measurements are normally better. Outliers may be important. It is
+always necessary to describe the experimental setup.
+
+Performance evaluation rests on strong foundations~\cite{jain1991} and
+is a vibrant field as new technologies emerge~\cite{gregg2014}.
+Although it may not be necessary to conduct a comprehensive
+performance evaluation analysis for a defense mechanism, the more
+performance evaluation is provided for a mechanism the more valuable
+it becomes as a practical approach.
+
+\subsection{Ease of Use}
+
+\subsection{Security}
+
+\subsection{Detection Locus}
 
@@
 
-In this section we categorize and describe the various mechanisms
-developed to detect the attacks described in
-Section~\ref{sec:attacks}. We accompany our descriptions with comments
-related to the following dimensions: a) diagnostic performance, b)
-computational performance, c) security, d) ease of use, and e)
-detection locus. We treat f) availability separately in the
+We categorize and describe the various mechanisms developed to detect
+the attacks described in Section~\ref{sec:attacks} on the dimensions
+we proposed apart from availability, which we treat separately in the
 ``Discussion" section (\ref{sec:discussion}).

### 2014-11-08 docs/questioning.tex
discussing the overhead

@@
   &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} & {\sc csrf} \\
+  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
   &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
@@
   &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} & {\sc csrf} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} ({\sc c}) & {\sc csrf} \\
   &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
@@
   \multirow{6}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc sql} injection \\
+  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql} injection \\
 	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
@@
 Finally, in the publications that
-{\sc amnesia}~\cite{HO05,HO06,HO05b}
-and {\sc sd}river~\cite{MS09,MKS09,MKLS11} were presented,
+{\sc amnesia} and {\sc sd}river were presented,
 authors managed to break existing application suites
@@
 \subsubsection{Computational Performance}
+
+Table~\ref{tab:comp} shows for every mechanism its
+corresponding overhead. In addition, it indicates
+if the overhead is applied to the server-side ({\sc s}),
+or the client-side ({\sc c}).
+Our first observation, is that there is a differential
+in the way in which the computational overhead of the
+mechanisms is measured. In many cases, 16 out of
+34 (47.05\%), the overhead is provided as a percentage
+while in other cases, 7 our of 34 (20.5\%),
+the authors provide the time (in terms of ms) that
+their mechanisms add to the normal execution time of
+the protecting entity. Surprisingly, in 10 cases (29,4\%),
+the overhead was either not available ({\sc na}) or
+not quantified ({\sc nq}). In the case of {\sc php aspis},
+its authors indicate that with their mechanism,
+the execution time is doubled.
 

### 2014-11-10 docs/questioning.tex
some corrections

@@
 \item The number of times the corresponding publication has been cited.
-\item Quadruples that show the values of true
-positives ({\sc tp}), true negatives ({\sc tn}),
-false positives ({\sc fp}), and false negatives
-({\sc tn}). For every quadruple there is a corresponding
-suffix that indicates whether the testbed was based
-on: real-world applications known to be vulnerable
-(r), synthetic benchmarks (s), both (a).
-If no testing has taken place we add a question
-mark ({\bf ?}).
-\item The computational overhead of the
-mechanism as stated in the publication.
+\item Diagnostic Performance and Computational Overhead measurements.
 \item The attacks that the mechanism detects.
 \end{enumerate}
-
-\noindent
-{\sc na} (Not Available) means that a requirement is not
-mentioned in the paper. {\sc nq} (Not Quantified)
-indicates that a requirement is mentioned in the publication
-but it is not quantified.
 
@@
 	but it is not quantified.
-		\item[2] For every quadruple there is a corresponding suffix that indicates whether the testbed was
+      \item[2] Quadruples contain numbers given for True Positives
+        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
+          fp}) and False Negatives ({\sc fn}). For every quadruple there is a corresponding suffix that indicates whether the testbed was
 	based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic benchmarks ({\it s}), c) both ({\it a}).
@@
 
-\subsection{Testing}
-
-Here we comment on how the mechanisms that we
-described earlier, were tested in terms of both
-diagnostic and computational performance.
-
-\subsubsection{Diagnostic Performance}
+\subsection{Diagnostic Performance}
 
@@
 
-\subsubsection{Computational Performance}
-
-Table~\ref{tab:comp} shows for every mechanism its
-corresponding overhead. In addition, it indicates
-if the overhead is applied to the server-side ({\sc s}),
-or the client-side ({\sc c}).
-Our first observation, is that there is a differential
-in the way in which the computational overhead of the
-mechanisms is measured. In many cases, 16 out of
-34 (47.05\%), the overhead is provided as a percentage
-while in other cases, 7 our of 34 (20.5\%),
-the authors provide the time (in terms of ms) that
-their mechanisms add to the normal execution time of
-the protecting entity. Surprisingly, in 10 cases (29,4\%),
-the overhead was either not available ({\sc na}) or
-not quantified ({\sc nq}). In the case of {\sc php aspis},
-its authors indicate that with their mechanism,
-the execution time is doubled.
-
-\subsection{Detection Locus}
-
-Given the fact that the final steps of
-{\sc dsl} injection and {\sc csrf} attacks take place
-on the server-side, all the mechanisms that detect
-such attacks are placed in some point within the server.
-From the mechanisms that detect {\sc dsl} code injection
-attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms} --- locus $\Omega$.
-The other 11 wrap {\sc api} calls related to output
-vectors --- locus {\sc z}.
-
-However, in the case of frameworks that deal
-with JavaScript-driven {\sc xss} attacks
-we observe that attack detection may take place
-either on the server-side or on the client-side.
-In the first case, a proxy is placed on the server
-to examine the server's responses before they
-reach the user's web browser. In the second
-case a modified browser or a library that
-is securely downloaded from the server,
-checks the responses for potential attacks.
-Our findings indicate that the tendency so far,
-is to create frameworks that perform detection
-on the client side. In particular, 11 out of
-19 frameworks (57,8\%) detect JavaScript-driven
-{\sc xss} attacks at the client's side.
-Note that the majority of the mechanisms that
-detect such attacks on the server-side, can also
-detect {\sc dsl} code injection attacks (7 out of 8).
+\subsection{Availability}
+
+Table~\ref{tab:avail} presents our findings regarding the availability
+of the mechanism in terms of source code and corresponding
+executables. We also examined the availability of the testbeds
+mentioned in the paper. The check mark (\tick) indicates that at some
+point in the publication there is a homepage where the reader can
+refer to, to download the corresponding software. {\bf AO} (Available
+On-line) suggests that the software is available on-line but the
+address was not mentioned in the paper, which probably indicates that
+the authors made it available after the publication. The question mark
+({\bf ?}), indicates that a homepage for the software was given in the
+publication but now it is not available.
+
+We see that only 6 out of 34 (17.6\%) of the authors provided a
+homepage for their mechanism through their publication and 2 from
+these 6 homepages are currently not available. In 5 cases authors made
+either the source code or their executables available after their
+paper got published. Regarding the availability of test materials, we
+see that only 3 out of 34 (8.8\%) authors have currently their
+testbeds available on-line.
+
+\subsection{Computational Performance}
+
+Table~\ref{tab:comp} shows for every mechanism its corresponding
+overhead. In addition, it indicates if the overhead is applied to the
+server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
+the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
+percentage. while in other cases, 7 our of 34 (20.5\%), the authors
+provide the time (in terms of ms) that their mechanisms add to the
+normal execution time of the protecting entity. As they do not provide
+the times of normal executions, it not possible to move from absolute
+time measurements to percentage overheads. In 10 cases (29,4\%), the
+overhead was either not available ({\sc na}) or not quantified ({\sc
+  nq}). In the case of {\sc php aspis}, its authors indicate that with
+their mechanism, the execution time is doubled.
 
@@
 
-\subsection{Availability}
-
-Table~\ref{tab:avail} presents our findings regarding the availability
-of the mechanism in terms of source code and corresponding
-executables. We also examined the availability of the testbeds
-mentioned in the paper. The check mark (\tick) indicates that at some
-point within the publication, there is a homepage where the reader can
-refer to, to download the corresponding software. {\bf AO} (Available
-On-line) suggests that the software is available on-line but the
-address was not mentioned in the paper, which probably indicates that
-the authors made it available after the publication. The question mark
-({\bf ?}), indicates that the a homepage for the software was included
-in the publication but now it is not available.
-
-Our first observation indicates that only 6
-out of 34 (17.6\%) of the authors provided a homepage for
-their mechanism through their publication.
-2 from these 6 homepages are currently not available.
-Also, in 5 cases, authors made either the source code
-or their executables available after their paper
-got published. Finally, we observe that only 3
-out of 34 (8.8\%) authors have currently
-their testbeds available on-line.
+\subsection{Security}
+
+\subsection{Detection Locus}
+
+Given the fact that the final steps of
+{\sc dsl} injection and {\sc csrf} attacks take place
+on the server-side, all the mechanisms that detect
+such attacks are placed in some point within the server.
+From the mechanisms that detect {\sc dsl} code injection
+attacks, 3 out of 13 (23\%) do so at the level
+of the {\sc rdbms}---Locus $\Omega$.
+The other 11 wrap {\sc api} calls related to output
+vectors---Locus {\sc z}.
+
+In frameworks that deal with JavaScript-driven {\sc xss} attacks we
+see that attack detection may take place either on the server-side or
+on the client-side. In the first case, a proxy is placed on the server
+to examine the server's responses before they reach the user's web
+browser. In the second case a modified browser or a library that is
+securely downloaded from the server checks the responses for potential
+attacks. We find that the tendency so far is to create frameworks that
+perform detection on the client side: in particular, 11 out of 19
+frameworks (57,8\%) detect JavaScript-driven {\sc xss} attacks at the
+client's side. Note that the majority of the mechanisms that detect
+such attacks on the server-side can also detect {\sc dsl} code
+injection attacks (7 out of 8).
 

### 2014-11-10 docs/questioning.tex
added material on security and ease of use

@@
 
+The value of a detection mechanism as a practical tool depends on how
+it is to deploy it in a production setting. That is independent of the
+value of a detection mechanism as a research finding. Devising a
+mechanism to detect a hitherto undetectable class of attacks may be an
+excellent research contribution that merits publication; it may also
+be heavily cited and open the road to other, practical
+implementations in the future.
+
+The ease of use, in turn, depends on several factors. The detection
+mechanism may be deployed server-side or client-side, or both.
+Deployments on just the server or the client are easier to handle than
+deployments on both of them. The mechanism may be an add-on, or
+plugin, on existing software, client or server, or it may be tightly
+integrated with existing software, requiring rebuilding from source
+code.
+
+No matter where it gets installed, the means of installation influences
+ease of use. A detection mechanism that comes with ready to install
+packages will trump a detection mechanism that only exists in the form
+of source code.
+
 \subsection{Security}
+
+Defenders and attackers are often caught in a cat-and-mouse game,
+where countermeasures are bypassed by canny attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by cannier
+attacks, and so on. We use Security to refer to the ability of a
+detection mechanism to resist being circumvented.
+
+A mechanism that has not been bypassed is not eternally secure, as it
+is possible that a bypass method will be discovered in the future. We
+examine the various approaches on the knowledge we have to this date,
+that is, whether there are known ways to bypass the detection
+mechanism today.
 

### 2014-11-10 docs/questioning.tex
add detection locus

@@
 \subsection{Detection Locus}
+
+Detection mechanisms vary on the location where they detect an attack.
+There are five different loci where an attack can be caught, as seen
+in Figure~\ref{fig:attacks}:
+\begin{itemize}
+\item At the user's browser (Locus X).
+\item En route from the server to the user's browser (Locus Y).
+\item Embedded in a query, but before it reaches the server's database
+  (Locus Z).
+\item After the malicious code has been executed on the server's
+  database (Locus $\Omega$).
+\end{itemize}
 

### 2014-11-10 docs/questioning.tex
refactor discussion on ppv and npv

@@
 \subsection{Diagnostic Performance}
+\label{ssec:diagnostic-performance}
 
@@
 
-Sensitivity and specifity are defined by way of the $2\times 2$
-Table~\ref{tab:sensitivity-specificity}~\cite{linn2004}. 
-In the cells of
-the table we distinguish:
+We will focus on sensitivity and specificity; we will come back to
+\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
+Sensitivity and specifity are defined using the following~\cite{linn2004}:
 \begin{itemize}
-\item True Positive ($a$), a real attack that raises an alarm.
-\item True Negative ($d$), an event that is not an attack and that does
+\item True Positive (\textsc{tp}), an attack that raises an alarm.
+\item True Negative (\textsc{tn}), an event that is not an attack and that does
   not raise an alarm.
-\item False Positive ($b$), an event that although it is not an attack
+\item False Positive (\textsc{fp}), an event that although it is not an attack
   raises an alarm.
-\item False Negative ($c$), an event that although is as attack does
+\item False Negative (\textsc{fn}), an event that although is as attack does
   not raise an alarm.
@@
 \begin{equation}
-\textrm{SE} = \textrm{Sensitivity} = \frac{a}{a + c}
+  \textsc{se} = \textrm{Sensitivity} = \frac{\textsc{tp}}{\textsc{tp}
+    + \textsc{fn}}
+\label{eq:sensitivity}
 \end{equation}
@@
 \begin{equation}
-\textrm{SP} = \textrm{Specificity} = \frac{d}{b + d}
+  \textsc{sp} = \textrm{Specificity} = \frac{\textsc{tn}}{\textsc{fp}
+    + \textsc{tn}}
+\label{eq:specificity}
 \end{equation}
@@
 events will give us the specificity.
-
-\begin{table}[ht]
-
-\caption{Attacks and Test Outcomes in Test Environment}
-\label{tab:sensitivity-specificity}
-
-\begin{tabular}{l|l|c|c|}
-\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} \\ \cline{3-4}
-\multicolumn{2}{c|}{} & Yes & No \\ \cline{2-4}
-\multirow{2}{*}{Result} &  Yes &  $a = \textrm{True Positive}$ & 
-$b = \textrm{False Positive}$ \\
-& No & $c = \textrm{False Negative}$ & $d = \textrm{True Negative}$ \\ 
-\cline{2-4}
-\multicolumn{2}{r|}{Total} & $a + c$ & $b + d$ \\
-\cline{3-4}
-\end{tabular}
-
-\end{table}
-
-Note that the calculations are carried out vertically in
-Table~\ref{tab:sensitivity-specificity}; the ratio of attack events to
-normal events does not enter into sensitivity and specificity. This is
-what allows us to derive them based on test data, without using data
-from a real production environment. At the same time, this is what
-limits their usefulness. When we obtain a test result in a production
-environment, be it negative or positive, we really want to know how
-much we should be worried, or relaxed. In other words, if an attack is
-detected in a production environment, how much should we be worried?
-If no attack is detected in a production environment, how relaxed
-should we be that no attack has indeed taken place?
-
-\begin{table}[ht]
-
-\caption{Attacks and Test Outcomes in Real Environment}
-\label{tab:ppv-npv}
-
-\begin{tabular}{l|l|c|c|c}
-\multicolumn{2}{c}{} & \multicolumn{2}{c}{Attack} & \\ \cline{3-4}
-\multicolumn{2}{c|}{} & Yes & No & Total \\ \cline{2-5}
-\multirow{2}{*}{Result} &  Yes &  $A = \textrm{True Positive}$ & 
-$B = \textrm{False Positive}$ & \multicolumn{1}{c|}{$A + B$}\\
-& No & $C = \textrm{False Negative}$ & $D = \textrm{True Negative}$ &
-\multicolumn{1}{c|}{$C + D$}\\ 
-\cline{2-5}
-\end{tabular}
-
-\end{table}
-
-The answer to these questions is given by the \textsc{ppv} and the
-\textsc{npv}. These depend not only on the test results, but also on
-the \emph{prevalence} of attacks in real environments. In particular,
-we can calculate them using Table~\ref{tab:ppv-npv}, which tabulates
-results in a real environment, or in an environment where the
-prevalence of attacks is equal to what we expect in the real world. To
-indicate the difference with Table~\ref{tab:sensitivity-specificity}
-we use capital letters for the entries in the table~\cite{linn2004}.
-With this table, \textsc{ppv} and \textsc{npv} are given by the
-following equations:
-
-\begin{equation}
-\textrm{PPV} = \frac{A}{A + C}
-\end{equation}
-
-\begin{equation}
-\textrm{NPV} = \frac{D}{B + D}
-\end{equation}
-
-This time the ratios are taken horizontally; the ratio of attacks to
-innocuous events affects the calculations. In fact, if PR is the
-probability of attacks in the real world, the prevalence, then we
-have~\cite{linn2004,altman1994}:
-
-\begin{equation}
-\textrm{PPV} = \frac{\textrm{SE}\times \textrm{PR}}{
-\textrm{SE}\times \textrm{PR} + (1 - \textrm{SP})\times (1 -
-\textrm{PR})}
-\label{eq:ppv-se-sp}
-\end{equation}
-
-\begin{equation}
-\textrm{NPV} = \frac{\textrm{SP}\times (1 - \textrm{PR})}{
-(1 - \textrm{SE})\times \textrm{PR} + \textrm{SP}\times (1 -
-\textrm{PR})}
-\label{eq:npv-se-sp}
-\end{equation}
-
-The prevalence is the prior probability that an event is an attack,
-based on our understanding of the volume and frequency of attacks; the
-\textsc{ppv} and \textsc{npv} are the revised estimates of the
-probability based on the results of the detection
-mechanism~\cite{altman1994}. The lower the prevalence of an attack,
-the more confident we can be that a negative test result indicates
-that no attack has taken place and the less sure we can be that a
-positive test result indicates a real attack.
-
-If published research does not include figures for Sensitivity and
-Specificity or values for ($a$)--($d$), on test environments, then it
-is not possible to judge the accuracy of the research at all. Even if
-we do have such figures, a good research tool is not necessarily a
-good practical tool. Even if a research tool scores well on
-Sensitivity and Specificity, it may not be very useful in the real
-world if the prevalence of the caught attacks is so low that a
-positive test result is not likely to indicate a real attack.
-
-To sum up, we evaluate diagnostic performance on two criteria:
-
-\begin{itemize}
-\item Reporting of Sensitivity and Specifity, either directly, or
-  indirectly from published values of $a$--$d$.
-\item Reporting of \textsc{ppv} and \textsc{npv}. This can be direct
-  reporting of their values, or indirect from published values of
-  $A$--$D$. Also, since from equations~\ref{eq:ppv-se-sp}
-  and~\ref{eq:npv-se-sp} \textsc{ppv} and \textsc{npv} can be
-  calculated by the sensitity and specifity given the prevalence, it
-  can be via reporting prevalance, sensitivity, specificity.
-\end{itemize}
 
@@
 \section{Lessons Learned}
-
-In this section we point out our key findings and
-discuss the lessons derived from our research.
-We also argue that some of our observations may be
-good reasons why the mechanisms are not adopted in practice.
-
-One of our key findings indicate that currently,
-the testing of the diagnostic performance of
-mechanisms that detect top web application attacks
-has not a standard form. In addition,
-there are many mechanisms that are tested in a poor
-manner. In many cases researchers tend not to
-provide the false positive and negative results
-that their tools may produce. Discussing
-about the existence of such results and not
-quantifying them may be a good reason to not use
-such a mechanism.
-
-A reasonable argument would be that many
-mechanisms (especially the ones coming from the
-etiological category), do not need to be established
-purely through testing since they provide systematic
-arguments as to why their design is secure against attacks.
-However, implementations are not always efficient
-and as we observed they can be circumvented.
+\label{sec:lessons-learned}
+
+One of our key findings indicate that many detect mechanisms are
+tested in a poor manner. In many cases researchers tend not to provide
+the false positive and negative results that their tools may produce.
+Discussing about the existence of such results and not quantifying
+them also blurs the picture.
+
+A reasonable argument would be that many mechanisms (especially the
+ones coming from the etiological category), do not need to be
+established purely through testing since they provide systematic
+arguments as to why their design is secure against attacks. In order
+for this to hold, however, an implementation of a defense mechanism
+may be entirely correct in terms of its specification, which may not
+happen in practice. Moreover, even a mechanism that detects an attack
+based on its root cause, instead of observer behavior, may still be
+circumvented so that attacks will pass undetected.
+
+When we introduced specicifity and sensitivity in
+Section~\ref{ssec:diagnostic-performance} we deferred discussion of
+\textsc{ppv} and \textsc{npv} to this point. These two relate to the
+performance of a detection mechanism in an actual production setting,
+instead of a testbed. If an attack is detected in a production
+environment, how much should we be worried? The answer is provided by
+\textsc{ppv}. If no attack is detected in a production environment,
+how relaxed should we be that no attack has indeed taken place? The
+answer is provided by \textsc{npv}. We can calculate \textsc{ppv} and
+\textsc{npv} with the following equations:
+
+\begin{equation}
+\textsc{ppv} = \frac{\textsc{tp}}{\textsc{tp} + \textsc{fp}}
+\end{equation}
+
+\begin{equation}
+\textsc{npv} = \frac{\textsc{tn}}{\textsc{fn} + \textsc{tn}}
+\end{equation}
+
+Equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} use true and false
+positives and negatives, like equations~\ref{eq:sensitivity}
+and~\ref{eq:specificity}. However, \textsc{tp}, \textsc{tn},
+\textsc{fp}, and \textsc{fn} are not the same in the two cases:
+whereas sensitivity and specificity are measured on a test
+environment, \textsc{ppv} and \textsc{npv} are measured on the real,
+target environment. In fact, if \textsc{pr} is the probability of
+attacks in the real world, the prevalence, then we
+have~\cite{linn2004,altman1994}:
+
+\begin{equation}
+\textsc{ppv} = \frac{\textsc{se}\times \textsc{pr}}{
+\textsc{se}\times \textsc{pr} + (1 - \textsc{sp})\times (1 -
+\textsc{pr})}
+\label{eq:ppv-se-sp}
+\end{equation}
+
+\begin{equation}
+\textsc{npv} = \frac{\textsc{sp}\times (1 - \textsc{pr})}{
+(1 - \textsc{se})\times \textsc{pr} + \textsc{sp}\times (1 -
+\textsc{pr})}
+\label{eq:npv-se-sp}
+\end{equation}
+
+The prevalence is the prior probability that an event is an attack,
+based on our understanding of the volume and frequency of attacks; the
+\textsc{ppv} and \textsc{npv} are the revised estimates of the
+probability based on the results of the detection
+mechanism~\cite{altman1994}. The lower the prevalence of an attack,
+the more confident we can be that a negative test result indicates
+that no attack has taken place and the less sure we can be that a
+positive test result indicates a real attack.
+
+Of course it is not easy, and it may not even be possible, to know how
+prevalent an attack is. Also, attacks on a system may depend on
+factors such as its visibility and popularity, so that the same piece
+of software may be subject to varying attack regimes depending on
+where it is actually deployed. With this in mind it may be unfair to
+ask of researchers to provide \textsc{ppv} and \textsc{npv} values for
+their mechanisms---in fact, we see that nobody does.
+
+That does not mean that deriving \textsc{ppv} and \textsc{npv} is
+altogether impossible. One could deploy a system, armoured with an
+attack detection mechanism, on a honeypot to study what happens over
+a length of time. This could give an indication of the performance of
+the mechanism out in the wild. Alternatively, one could deploy a
+target, unarmoured system, on a honeypot to study the prevalence of
+the class of attacks to be detected. Studying the prevalence of
+classes of attacks could be an interesting area of study on its own,
+which could feed directly on the evaluation of attack detection
+mechanisms as practical tools.
 

### 2014-11-10 docs/questioning.tex
"executable source code" became "source code injection", also grouped table I

@@
 \usepackage{subfigure}
+\usepackage{array}
 
@@
 
+\makeatletter
+\newcommand{\thickhline}{%
+    \noalign {\ifnum 0=`}\fi \hrule height 1pt
+    \futurelet \reserved@a \@xhline
+}
+\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
+\makeatother
+
 \date{}
@@
 \IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
-Panos Louridas,\IEEEauthorrefmark{2},
+Panos Louridas,\IEEEauthorrefmark{2}
 Michalis Polychronakis,\IEEEauthorrefmark{1}
@@
 three consecutive Top Ten lists (2007, 2010, 2013), different
-executable source code-driven injection attacks dominate the top five
+source code-driven injection attacks dominate the top five
 positions. Malicious users find new ways to bypass defense mechanisms
@@
 exploitation model that highlights the following fact: the majority of
-the steps needed to perform application attacks based on executable
+the steps needed to perform application attacks based on
 source code injection are common.\footnote{Note that we leave out
@@
 \item We provide an exploitation model that puts application attacks
-  based on executable source code injection under a common
+  based on source code injection under a common
   perspective.
@@
 \end{center}
-\caption{\label{fig:taxonomy}A taxonomy of executable source
+\caption{\label{fig:taxonomy}A taxonomy of source
 code injection attacks.}
@@
 Code injection attacks can be divided into two categories. The first
-involves binary code and the second executable source code. An
+involves binary code and the second source code. An
 extensive survey on binary code injection attacks can be found
 in~\cite{LC03}. Specific advances in exploiting such vulnerabilities
-(i.e. ``heap smashing", ``arc injection" and others) have been
-presented in~\cite{PB04}. The countermeasures used to detect such
+(i.e. ``heap smashing", ``arc injection" and others) have already
+been presented~\cite{PB04} and the countermeasures used to detect such
 defects have already been surveyed~\cite{YJP12} (many of them are also
@@
 that protect applications against attacks based on the
-executable source code injection category.
-
-\subsection{Executable Source Code Injection Vulnerabilities}
-
-Figure~\ref{fig:taxonomy} presents a taxonomy of executable source
+source code injection category.
+
+\subsection{Source Code Injection Vulnerabilities}
+
+Figure~\ref{fig:taxonomy} presents a taxonomy of source
 code injection attacks. Such attacks may involve source code, either of a
@@
 understand the process of carrying out application attacks based on
-executable source code injection vulnerabilities.
+source code injection vulnerabilities.
 Figure~\ref{fig:attacks} presents the steps of different application
@@
 \caption{\label{fig:attacks}Attack model demonstrating web
-application attacks based on executable source
+application attacks based on source
 code injection vulnerabilities. For every arrow there is a
@@
 \caption{\label{fig:defenses}The basic categories of countermeasures
-against web application attacks, based on executable source code
+against web application attacks, based on source code
 injectiion. For each approach we provide the references
@@
 There exist three basic etiological approaches used to protect web
-applications from executable source code injection attacks.
+applications from source code injection attacks.
 
@@
 \begin{table}
-    \caption{Comparison summary of mechanisms developed to counter application attacks based on executable source code injection.}
+    \caption{Comparison summary of mechanisms developed to counter application attacks based on source code injection.}
     \label{tab:comp}
@@
     \begin{tabular}{l|c|c|cc|c}
-    \hline
+    \thickhline
     \bf{Approach}
@@
 	& \bf{Computational Overhead}\tnote{3} & \\
-    \hline
+    \thickhline
   \multirow{2}{*}{Parse-Tree Validation}
@@
   &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql} injection \\
-  \hline
   \hline
@@
   \hline
-  \hline
   \multirow{4}{*}{{\sc isr}}
@@
   &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
-  \hline
-  \hline
+  \thickhline
+  \thickhline
 	\multirow{7}{*}{Taint Tracking}
@@
 	\hline 
-	\hline  
   \multirow{6}{*}{Training}
@@
 	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-  \hline
-  \hline
+  \thickhline
+  \thickhline
   \multirow{3}{*}{Hybrid}
@@
   &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql} and No{\sc sql} injection \\
-	\hline
+	\thickhline
     \end{tabular}}

### 2014-11-10 docs/questioning.tex
diagnostic performance becomes accuracy - minor change in abstract

@@
   have been developed. Our analysis is based on dimensions such as
-  accuracy, performance, deployment and security. Especially notable
-  is accuracy, as our findings show that there are
+  accuracy, performance, deployment, security and availability.
+  Especially notable is accuracy, as our findings show that there are
   many defense mechanisms that are tested in a poor manner.
-  In addition, we observe that there are many protection mechanisms
+  In addition, we observe that there are protection mechanisms
   that can be bypassed by attackers that know how the mechanisms
-  work. Finally, we see that researchers tend to not make
-  their mechanisms available to the community.
+  work.
 
@@
 \begin{itemize}
-\item {\it Diagnostic Performance} Protection mechanisms are as good
+\item {\it Accuracy} Protection mechanisms are as good
   as their detection capability; this requires low false positive and
@@
   criteria that are important for building protection mechanisms.
-\item We find that researchers often test the diagnostic performance
+\item We find that researchers often test the accuracy
   of their mechanisms poorly. 
@@
 
-The first two criteria are \emph{Diagnostic Performance} and
+The first two criteria are \emph{Accuracy} and
 \emph{Availability}. The other four criteria are \emph{Computational
@@
 
-\subsection{Diagnostic Performance}
+\subsection{Accuracy}
 \label{ssec:diagnostic-performance}
@@
 \item The number of times the corresponding publication has been cited.
-\item Diagnostic Performance and Computational Overhead measurements.
+\item Accuracy and Computational Overhead measurements.
 \item The attacks that the mechanism detects.
@@
 mechanisms as we will observe), {\sc sql}check has been
-extensively tested in terms of diagnostic performance
+extensively tested in terms of accuracy
 as it can be seen in Table~\ref{tab:comp}.
@@
 testing of the mechanism (see Table~\ref{tab:comp}) brings up
-questions concerning its diagnostic performance. {\it {\sc
+questions concerning its accuracy. {\it {\sc
     sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
@@
 
-\subsection{Diagnostic Performance}
+\subsection{Accuracy}
 
@@
 authors managed to break existing application suites
-and then test the diagnostic performance of their tools on them.
+and then test the accuracy of their tools on them.
 
@@
 approaches have not been extensively tested in terms of
-diagnostic performance.
+accuracy.
 \item We need to mention that there are mechanisms that

### 2014-11-10 docs/questioning.tex
from detection locus to point of detection

@@
   new approaches in developing more efficient mechanisms.
-% @dimitro: change the above accordingly.
-
-%In this paper we examine how application attack defense
-%mechanism are developed and presented to
-%the research community.
+% dimitro@dimitro: change the above accordingly.
+
 \end{abstract}
@@
 \section{Introduction Remarks}
-
-%Introduction~\cite{I05}. Also see~\cite{A00}.
 
@@
   attackers that know how it works and wants to circumvent it.
-\item {\it Detection Locus} Based on our exploitation model
+\item {\it Point of Detection} Based on our exploitation model
   we examine the location where a mechanism detects an attack.
@@
 every attack. Note that {\sc xss} attacks can also involve
-{\it phishing}. Every {\it locus} indicates a step where mechanisms
-detect attacks. For every locus we provide the corresponding
+{\it phishing}. Every {\it point} indicates a step where mechanisms
+detect attacks. For every point we provide the corresponding
 references:
-locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
-locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-locus $\Omega$~\cite{BK04,LLW02,VMV05}.}
+Point {\sc ub}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
+Point {\sc sb}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
+Point {\sc eq}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+Point {\sc sdb}~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
@@
   Performance}, \emph{Ease of Use}, \emph{Security}, and
-\emph{Detection Locus}.
+\emph{Point of Detection}.
 
@@
 
-\subsection{Detection Locus}
+\subsection{Point of Detection}
 
 Detection mechanisms vary on the location where they detect an attack.
-There are five different loci where an attack can be caught, as seen
+There are four different points where an attack can be caught, as seen
 in Figure~\ref{fig:attacks}:
 \begin{itemize}
-\item At the user's browser (Locus X).
-\item En route from the server to the user's browser (Locus Y).
+\item At the user's browser (Point {\sc ub}).
+\item En route from the server to the user's browser --- in most cases
+within a proxy (Point {\sc sb}).
 \item Embedded in a query, but before it reaches the server's database
-  (Locus Z).
+  (Point {\sc eq}).
 \item After the malicious code has been executed on the server's
-  database (Locus $\Omega$).
+  database (Point {\sc sdb}).
 \end{itemize}
@@
 and detect the attack before a query reaches the
-database (Locus {\sc z}).
+database (Point {\sc eq}).
 Contrary to {\sc sqlg}uard (and other
@@
 a set of policies Noxes allows or blocks
-the request (Locus {\sc x}). Such policies
+the request (Point {\sc ub}). Such policies
 can be also provided by the server (i.e. ``never
@@
 scripts inside {\sc html} elements like {\tt div}.
-The web browser (Locus {\sc x}), parses the
+The web browser (Point {\sc ub}), parses the
 {\sc dom} tree and executes scripts only when they
@@
 to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
-acts as a proxy on the server side (Locus {\sc y}) to
+acts as a proxy on the server side (Point {\sc SB}) to
 parse the {\sc html} of server responses and identifies
@@
 JavaScript functions. In both cases, policy enforcement takes
-place on the JavaScript engine of the browser (Locus {\sc x}).
+place on the JavaScript engine of the browser (Point {\sc ub}).
 %% PL In which way is this a kind of policy enforcement?
@@
 {\sc soma}~\cite{OWVS08} are two frameworks that
-can actually detect such an attack (Locus {\sc x}).
+can actually detect such an attack (Point {\sc ub}).
 To achieve this, {\sc soma} requires site administrators
@@
 attacks are usually implemented in the form of a
-server-side proxy (Locus {\sc y})
+server-side proxy (Point {\sc SB})
 interposing on the client-server communication, and modifying
@@
 examines cross-domain interactions, to design a
-cross-domain policy on the client's side (Locus {\sc x}).
+cross-domain policy on the client's side (Point {\sc ub}).
 The policy is based on the concept of a relaxed
@@
 the few mechanisms that detect {\sc sql} injection attacks on the
-database level (Locus $\Omega$).
+database level (Point {\sc sdb}).
 
@@
 web page on the server-side and then, on the client-side, the web
-browser decodes the source by applying the same function again (Locus
-{\sc x}). Variations of this approach include {\it
+browser decodes the source by applying the same function again (Point
+{\sc ub}). Variations of this approach include {\it
   Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
@@
 sending the resulting {\sc html} data to the web user, the framework
-searches the data for illegal code by using the same keywords (Locus
-{\sc y}). Since all legitimate code has been ``masked", the injected
+searches the data for illegal code by using the same keywords (Point
+{\sc SB}). Since all legitimate code has been ``masked", the injected
 code can be identified. The pre- and post-processing of the code
@@
 tainted string is used as an argument to a sink method
-then an exception is raised (Locus {\sc z}).
+then an exception is raised (Point {\sc eq}).
 % However, this is a simplistic approach that may
@@
 It is possible to apply further checks when it is established that
-tainted data have reached a sink (Locus {\sc z}). {\it Xu et
+tainted data have reached a sink (Point {\sc eq}). {\it Xu et
   al.}~\cite{XBS06} track taint information at the level of bytes in
@@
 and others. When tainted data reaches a sink, {\sc csse} performs
-syntactic checks based on the aforementioned metadata (Locus {\sc z}).
+syntactic checks based on the aforementioned metadata (Point {\sc eq}).
 {\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
@@
 Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
-if there are tainted data that contain scripts (locus {\sc y}).
+if there are tainted data that contain scripts (Point {\sc sb}).
 
@@
 schemes that operate on the server side, they track sensitive
-information on the client side (Locus {\sc x}). This is a form of
+information on the client side (Point {\sc ub}). This is a form of
 positive taint tracking, where taint data is considered to be
@@
 {\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
-in the browser (Locus {\sc x}). The scheme focuses on the detection of
+in the browser (Point {\sc ub}). The scheme focuses on the detection of
 {\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
@@
 from the set of valid code statements. An early approach, {\it {\sc
-    didafit}}~\cite{LLW02} detects {\sc sql} injection (Locus
-$\Omega$) attacks by recording all database transactions
+    didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
+sdb) attacks by recording all database transactions
 (stripped from user input). Subsequent
@@
 checks all statements for compliance and can block code statements
-containing injected elements (Locus {\sc z}). {\sc
+containing injected elements (Point {\sc eq}). {\sc
   amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
-  sql} injection attacks (locus {\sc z}) by associating a query model
+  sql} injection attacks (Point {\sc eq}) by associating a query model
 with the location of every {\sc sql} statement within the application.
@@
 ({\it script {\sc id}}) for every legitimate script on the server.
-Then, a JavaScript detection component placed in a web proxy (Locus
-{\sc y}) searches for injected scripts with no corresponding {\sc id}
+Then, a JavaScript detection component placed in a web proxy (Point
+{\sc sb}) searches for injected scripts with no corresponding {\sc id}
 in the server's responses. If no injected scripts are found, the proxy
@@
 for an exact match of lexical entities. To achieve this, the scheme
-utilizes that data structures of Firefox's JavaScript engine (Locus
-{\sc x}). However, string literals are not compared literally and
+utilizes that data structures of Firefox's JavaScript engine (Point
+{\sc ub}). However, string literals are not compared literally and
 therefore a false negative result could occur if an adversary performs
@@
 does not contain any dynamic content. Then the parsed tree is
-transfered to the document generator of the browser (Locus {\sc x})
+transfered to the document generator of the browser (Point {\sc ub})
 where untrusted browser parsing behavior is ruled out. Blueprint is an
@@
 scheme creates the tree of the query that is about to be executed and
-compares it with the parsed tree of the ``shadow" (Locus {\sc z}). If
+compares it with the parsed tree of the ``shadow" (Point {\sc eq}). If
 the trees are not equal the application is probably under attack. Note
@@
 
-\subsection{Detection Locus}
+\subsection{Point of Detection}
 
@@
 attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms}---Locus $\Omega$.
+of the {\sc rdbms}---Point {\sc sdb}.
 The other 11 wrap {\sc api} calls related to output
-vectors---Locus {\sc z}.
+vectors---Point {\sc eq}.
 

### 2014-11-10 docs/questioning.tex
changes on the exploitation model

@@
   many defense mechanisms that are tested in a poor manner.
-  In addition, we observe that there are protection mechanisms
+  In addition, we observe that there are mechanisms
   that can be bypassed by attackers that know how the mechanisms
@@
 attacks. For every arrow there is a
-corresponding tuple that includes the step number for
+corresponding tuple that includes the transition number for
 every attack. For the most part, the steps are common in all attacks. This
@@
 the previous section. Most importantly,
-Figure~\ref{fig:attacks} also illustrates in which step
+Figure~\ref{fig:attacks} also illustrates in which transitions
 the defenses detect corresponding attacks.
@@
 and then trick an end user to click on it via social engineering (i.e., phishing ---
-{\sc step}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
+{\it transition}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
 Alternatively, the attacker may be able to inject
@@
 malicious {\sc sql} code to retrieve all the password entries from a
-database ({\sc step}: {\sc dsl} 1 \text{\textbar}
+database ({\it transition}: {\sc dsl} 1 \text{\textbar}
 {\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
@@
 parse and display a page of results, without properly sanitizing the
-request ({\sc step}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
+request ({\sc transition}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
 Thus, in a non-persistent {\sc xss} attack the injected code
@@
 code injection vulnerabilities. For every arrow there is a
-corresponding tuple that includes the step number for
+corresponding tuple that includes a transition number for
 every attack. Note that {\sc xss} attacks can also involve
-{\it phishing}. Every {\it point} indicates a step where mechanisms
+phishing. Every {\it point} indicates a transition where mechanisms
 detect attacks. For every point we provide the corresponding
@@
 % lead to many false positives.
-%% PL better to avoid characterisations and mention only the facts
-%% (that it leads to many false positives, as shown by ...
 
@@
 metadata, it takes advantage of {\sc php} arrays data structure.
-%% PL Like what?
 % Note that the above schemes detect potential attacks
@@
 site from which it came from.
-% This though, may lead to false alarms.
-%% PL You mean a lot of false alarms?
 {\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
@@
 identify the generation of code coming from tainted data.
-
-% @dimitro: move this to the analysis Section:
-% This scheme is an efficient scheme that focuses
-% on a specific category of {\sc xss} attacks and
-% takes into consideration many attack vectors
-% that many of the previous schemes do not.
-% Also: 
-% As the author of {\sc csse} state~\cite{PB05}, the prevention
-% of {\sc xss} attack requires a more complex analysis.
 
@@
 
+% @dimitro: move this to the analysis Section:
+% This scheme is an efficient scheme that focuses
+% on a specific category of {\sc xss} attacks and
+% takes into consideration many attack vectors
+% that many of the previous schemes do not.
+% Also: 
+% As the author of {\sc csse} state~\cite{PB05}, the prevention
+% of {\sc xss} attack requires a more complex analysis.
+
 One of our key findings indicate that many detect mechanisms are

### 2014-11-10 docs/questioning.tex
minor changes

@@
 corresponding tuple that includes the transition number for
-every attack. For the most part, the steps are common in all attacks. This
+every attack. Every number indicates the number of the
+steps taken until we reach this transition.
+For the most part, the steps are common in all attacks. This
 is because they are based on similar attack vectors as we mentioned in
 the previous section. Most importantly,
-Figure~\ref{fig:attacks} also illustrates in which transitions
+Figure~\ref{fig:attacks} illustrates in which transitions
 the defenses detect corresponding attacks.
@@
 parse and display a page of results, without properly sanitizing the
-request ({\sc transition}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
+request ({\it transition}: {\sc p-xss} 7 \text{\textbar} {\sc n-xss} 2).
 Thus, in a non-persistent {\sc xss} attack the injected code
@@
 \item The number of times the corresponding publication has been cited.
-\item Accuracy and Computational Overhead measurements.
+\item Accuracy and computational overhead measurements.
 \item The attacks that the mechanism detects.
@@
 the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
-percentage. while in other cases, 7 our of 34 (20.5\%), the authors
+percentage, while in other cases, 7 our of 34 (20.5\%), the authors
 provide the time (in terms of ms) that their mechanisms add to the
-normal execution time of the protecting entity. As they do not provide
-the times of normal executions, it not possible to move from absolute
+normal execution time of the protecting entity. Note that in some
+cases, the times of normal executions are not provided,
+so it is not possible to move from absolute
 time measurements to percentage overheads. In 10 cases (29,4\%), the

### 2014-11-11 docs/questioning.tex
more on discussion - ease of use

@@
 source code-driven injection attacks dominate the top five
-positions. Malicious users find new ways to bypass defense mechanisms
+positions. Malicious users find new ways~\cite{HNSHS12,DKH14}
+to bypass defense mechanisms
 by using a variety of techniques despite the numerous countermeasures
@@
 corresponding tuple that includes a transition number for
-every attack. Note that {\sc xss} attacks can also involve
-phishing. Every {\it point} indicates a transition where mechanisms
+every attack. Every {\it point} indicates a transition where mechanisms
 detect attacks. For every point we provide the corresponding
@@
 
-As in medical diagnostic tests, application attack defense mechanisms
+Application attack defense mechanisms
 must demonstrate the presence of an attack. This, however, does not
@@
 
+\noindent
 Sensitivity and specificity can be calculated based on test
@@
 \subsection{Ease of Use}
+\label{sec:deployment}
 
@@
     \begin{tabular}{l|c|ccc}
-    \hline
+    \thickhline
     \bf{Approach}
@@
   & \bf{Testbed} \\
-    \hline
+    \thickhline
   \multirow{2}{*}{Parse-Tree Validation}
@@
   &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
-  \hline  
   \hline
@@
   &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \hline 
+  \thickhline
+  \thickhline
   \multirow{7}{*}{Taint Tracking}
@@
   \hline
-  \hline 
   \multirow{6}{*}{Training}
@@
   &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
-  \hline
-  \hline
+  \thickhline
+  \thickhline
   \multirow{3}{*}{Hybrid}
@@
   &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
+  \thickhline
     \end{tabular}}
@@
 quadruples are not available ({\sc na}).
-% Maybe we should comment on the fact that these are
-% frameworks coming from the etiological category
-% and detect the attacks ``by design".
 An interesting observation is that 10 out of 34
@@
 
+As we mentioned in Subsection~\ref{sec:deployment},
+there are various reasons why a mechanism could
+be difficult to deploy.
+
 Consider the majority of mechanisms coming from
-the policy enforcement category. In most cases
+the policy enforcement subcategory. In most cases
 developers should modify multiple components
@@
 both browser vendors and application developers.
+On the other hand, there are cases where the policies
+introduced in the server, are enforced on the client-side,
+via a library embedded in the server's response
+(i.e. Blueprint). Such an approach is really convenient
+since no modifications are needed on the client.
+
+Extensive modifications in the application's source
+code can also be a reason that can make a mechanism
+difficult to use. {\sc sql}rand, {\sc amnesia}
+and mechanisms coming from the taint tracking
+subcategory are such examples.
+In the first two cases, programmers should modify every
+code fragment that involves the execution of a query.
+In the latter case they should also change
+all the code fragments that involve user-input handling. 
+In addition, there are cases (i.e. ConScript and the system
+by Phung et al.) that require many modifications
+by the developers in order to introduce their policies.
+Note also that in many cases, developers are required to
+learn a new {\sc api}.
+
+Finally, a disadvantage of mechanisms that involve training
+({\sc sd}river, {\sc xss-guard}), is that when code statements
+are altered, a new training phase is necessary. However,
+with the increased adoption of the use of automated testing
+and continuous integration frameworks, this phase could be
+easily repeated.
 
@@
 
+Another interesting finding involves the computational overhead.
+We observe that the average overhead that can be extracted from
+the publications that provide the overhead in percentage terms is
+18\%. Relative research on protection mechanisms~\cite{SPWS13}
+has indicated that mechanisms that introduce an overhead
+larger than 10\% do not tend to gain wide adoption in
+production environments which in this case could be a
+reason why some these tools have not been adopted.
+
+Cite~\cite{DKH14}.
+
 We believe that our research may facilitate researchers
@@
 
-Notes on taint tools:
-\begin{enumerate}
-\item The accuracy testing of {\sc csse}~\cite{PB05} was based on 
-defects found in the security mailing
-list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
-\item During their evaluation, the authors of~\cite{HCF05} have only performed
-two attacks in one synthetic benchmark ({\sc owasp}'s
-{\it WebGoat}\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_WebGoat_Project}}).
-\item The testing in~\cite{XBS06} was made based on
-defects with specific {\sc cve id}s.
-\item The authors of {\it {\sc wasc}}~\cite{NLC07}
-mention the vulnerabilities (specific {\sc cve id}s)
-exploited and the corresponding applications but they do not explicitly
-state how many attacks they launched (``{\it [...] launched a variety of
-attacks against it}").
-\item The authors of~\cite{VFJKKV07} do the same.
-However, even if they do not mention specific {\sc cve id}s,
-they browsed applications without performing attacks.
-\item Even if the authors of {\it Noxes}~\cite{KKVJ06,KJKV09} state in
-both papers that ``{\it [...] we are planning to make the tool available as
-a freeware utility}." the tool cannot be found anywhere on the Internet.
-The vulnerabilities exploited during testing were reported
-by {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
-\item {\it {\sc php} Aspis}~\cite{PMP11} was tested on only one
-application (Wordpress 2.9.2) with multiple vulnerabilities (specific {\sc cve id}s).
-\item During their initial tests, the authors of
-managed to bypass the browser-based {\sc xss} filters of the
-73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
-Then they proposed an approach that detected all the attacks they
-found (1169). This is a complex paper --- we need to elaborate.
-\end{enumerate}
-
-Notes on {\sc isr} mechanisms:
-\begin{enumerate}
-\item {\it {\sc sql}rand}~\cite{BK04}: Both exploits from {\sc cve} --- though
-this is not mentioned in the publication.
-\item {\it Noncespaces}~\cite{GC09} was only tested on one
-known vulnerable application (TikiWiki). The authors mention that they performed
-a number of attacks but they do not state how many.
-\item The authors of {\it x{\sc js}}~\cite{APKLM10}, have tested
-their mechanisms based on real-world attacks coming from
-{\sc xss}ed.com.\footnote{www.xssed.com}
-\end{enumerate}
-
-Notes on policy enforcement tools:
-\begin{enumerate}
-\item Just like the authors of {\it x{\sc js}~\cite{APKLM10},
-the authors of {\sc dsi}}~\cite{NSS06}, have tested
-their mechanisms based on real-world attacks coming from
-{\sc xss}ed.com.\footnote{www.xssed.com}
-\item The testing of {\it BrowserShield}~\cite{RDWDE07}
-involved {\sc xss} vulnerabilities reported by Microsoft
-in 2005.\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
-The link currently shows defects for 2014.
-\item {\it CoreScript}~\cite{YCIS07} is more of a programming
-language\footnote{``[...] uses program instrumentation for
-JavaScript where untrusted JavaScript
-code goes through a rewriting process according to a security policy
-before executing them in the browser"~\cite{PSC09}.}
-than an {\sc IDS}.
-\item Surprisingly, {\sc met}~\cite{ELX07} was not tested at all.
-\item {\sc beep}~\cite{TNH07}'s test suite was based on 61 {\sc xss}
-attack vectors published by \url{ha.ckers.org}.
-\item {\sc soma}~\cite{OWVS08} --- all synthetics.
-\item The attacks used for the testing of {\it Blueprint}~\cite{LV09},
-came from \url{ha.ckers.org}.
-\item {\it Phung et al.}~\cite{PSC09} also utilized \url{ha.ckers.org}.
-\item {\it WebJail}~\cite{VDDPJ11} --- not tested at all.
-\item {\it ConScript}~\cite{ML10} --- not tested at all. A scheme
-similar to {\it CoreScript}~\cite{YCIS07}.
-\item {\it j{\sc csrf}}~\cite{PS11} --- based on {\sc csrf}
-defects with specific {\sc cve id}s.
-\item The authors of {\it TreeHouse}~\cite{IW12} have tested
-only the overhead and how easy is to incorporate the mechanism
-into an application.
-\end{enumerate}
-
-Notes on training-based mechanisms:
-\begin{enumerate}
-\item {\it {\sc didafit}}~\cite{LLW02} is one of
-the first {\sc ids}.
-\item {\sc amnesia}~\cite{HO05,HO06,HO05b} was tested
-on applications with known vulnerabilities taken
-from \url{http://gotocode.com} plus two synthetic benchmarks.
-Interestingly, in one of the papers~\cite{HO06},
-the authors mention that the tool can produce both {\sc fp} and
-{\sc fn}.
-\item {\it libAnomaly}~\cite{VMV05} --- one application tested ({\sc php}-Nuke).
-\item {\sc sqlg}uard~\cite{BWS05} --- no testing at all.
-\item {\sc sm}ask~\cite{JB07} was tested on real-world applications
-with exploits from {\sc cve} --- though this is not mentioned in the publication.
-\item {\sc xssds}~\cite{JEP08} --- testing was based on 
-defects found in the security mailing
-list: {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}.
-The authors provide multiple {\sc fp} rates depending on the experiment.
-\item {\sc xss-guard}~\cite{BV08} was tested on real-world applications
-with exploits from {\sc cve}.
-\item {\sc swap}~\cite{WPLKK09} was tested on a real-world application ({\sc phpbb})
-with exploits from {\sc cve} --- though this is not mentioned in the publication.
-%\item {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} have developed a
-%mechanism to detect {\sc sql} and {\sc xp}ath injection attacks
-%only on web services. Their testing involve a real-world benchmark
-%({\sc tpc}-app).\footnote{\url{http://www.tpc.org/}}
-\item {\it Diglossia}~\cite{SMS13} was tested on real-world applications
-with exploits from {\sc cve}.
-\end{enumerate}
-
-Notes:
-\begin{enumerate}
-\item Note that most mechanisms that implement etiological
-approaches have not been extensively tested in terms of
-accuracy.
-\item We need to mention that there are mechanisms that
-do not need to be established purely through testing
-Since they provide systematic arguments as to why
-the design is secure against attacks.
-\item Policy enforcement is the
-only approach that is
-used to prevent {\sc csrf} attacks.
-\item See j{\sc csrf} for {\sc soma}'s drawbacks.
-\item Discuss about how tools can be easily modified
-to detect other attacks ({\sc sql}rand).
-\end{enumerate}
-
 \section{Conclusions}
+
+We believe that forming a
+standard way to test such mechanisms in terms
+of accuracy and computational performance
+would be one of the reasons of adopting them.
 

### 2014-11-11 docs/questioning.tex
material for discussion and lessons learned

@@
 stop attacks based on their causes and origins~\cite{JL75,L81}. 
-%% PL:
-%% Explain what "by design" means.
 The symptomatic category incorporates a variety of schemes that
@@
 as we will see in Subsection~\ref{sec:hybrid}.
-%% PL This paragraph repeats the material of the previous one, doesn't
-%% it?
 
@@
 This approach is used to detect {\sc xss} and {\sc csrf} attacks.
-%% PL All of them more or less target web users, correct?
 When using a framework that implements
@@
 pattern matching or syntax specific settings.
-%% PL What kind of policies are these? Syntax-based, pattern matching?
 Then the policies are enforced either in the user's
@@
 that are based on reported browser vulnerabilities.
-{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
-and the framework by {\it Phung et al.}~\cite{PSC09}
-extend JavaScript with new primitive functions that
-provide safe methods to protect potentially vulnerable
-JavaScript functions. In both cases, policy enforcement takes
-place on the JavaScript engine of the browser (Point {\sc ub}).
-%% PL In which way is this a kind of policy enforcement?
-In this way, {\sc xxs} attacks that take advantage
-functions like {\tt write} and {\tt eval}, which are
-used to assemble innocuous-looking parts into harmful
-strings,\footnote{The infamous Sammy worm that
-infected MySpace in 2005~\cite{SP07,ELX07}
-utilized the {\tt eval} function to assemble a
-script with malicious behavior.} would fail.
-
-A critical issue regarding
-the above frameworks is that they cannot
-define policies that restrict the behavior of third-party
-scripts introduced by script inclusion and {\tt iframe}
-tags. For instance, consider a web page (foo.net)
+An issue regarding this framework (as well as {\sc beep}
+and {\sc dsi}) is that it cannot define policies that
+restrict the behavior of third-party scripts introduced
+by script inclusion and {\tt iframe} tags.
+For instance, consider a web page (foo.net)
 that prints the value of a query parameter ({\tt query})
@@
 \noindent
-{\it WebJail}~\cite{VDDPJ11}, and
-{\sc soma}~\cite{OWVS08} are two frameworks that
-can actually detect such an attack (Point {\sc ub}).
-To achieve this, {\sc soma} requires site administrators
+The following frameworks can actually detect such
+an attack (Point {\sc ub}).
+{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
+and the framework by {\it Phung et al.}~\cite{PSC09}
+extend JavaScript with new primitive functions that
+provide safe methods to protect potentially vulnerable
+JavaScript functions. In both cases, policy enforcement takes
+place on the JavaScript engine of the browser (Point {\sc ub}).
+In this way, {\sc xxs} attacks that take advantage
+functions like {\tt write} and {\tt eval}, which are
+used to assemble innocuous-looking parts into harmful
+strings,\footnote{The infamous Sammy worm that
+infected MySpace in 2005~\cite{SP07,ELX07}
+utilized the {\tt eval} function to assemble a
+script with malicious behavior.} would fail.
+{\it WebJail}~\cite{VDDPJ11}, is a framework similar to
+ConScript. WebJail, contains the functionality of
+third-party scripts by introducing a web component
+integrator that restricts the access that these scripts
+may have to either the data or the functionality of other components
+Finally, {\sc soma}~\cite{OWVS08} requires site administrators
 to specify legitimate, external domains for sending
@@
 {\sc soma} can also detect {\sc csrf} attacks.
-WebJail contains the functionality of third-party scripts
-by introducing a web component integrator that restricts
-the access that these scripts may have to either the data
-or the functionality of other components.
 
@@
 then an exception is raised (Point {\sc eq}).
-% However, this is a simplistic approach that may
-% lead to many false positives.
 
@@
 metadata, it takes advantage of {\sc php} arrays data structure.
-% Note that the above schemes detect potential attacks
-% in locus {\sc z}. This automatically means that they
-% cannot detect non-persistent JavaScript-driven
-% {\sc xss} attacks. Although they can be
-% modified to do so.
 Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
@@
 \subsubsection{Training}
+\label{sec:train}
 
@@
 \noindent
-%% PL I do not understand what is specific to training here; most
-%% classic SQL injection attacks work in this way.
+
 However, mechanisms that create signatures that involve
@@
 attack~\cite{APKLM10}.
-%% PL Like the return-to-lib attack?
 
@@
 
-All the above mechanisms are relatively easy to deploy.
+Most of the mechanisms above are relatively easy to deploy.
 {\sc dsl} injection attack countermeasures
 can be retrofitted to a system typically by changing
-some configuration files. This does not apply
+some configuration files (i.e. {\sc sd}river). This does not apply
 to {\sc amnesia} though, since significant source code
@@
 in which publication:
-{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09,JKK06a},
-{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
+{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
 {\sc xss}ed.com~\cite{NSS06,APKLM10},
@@
 \subsection{Ease of Use}
-
-As we mentioned in Subsection~\ref{sec:deployment},
+\label{sec:deploy2}
+
+As we observed in Subsection~\ref{sec:deployment},
 there are various reasons why a mechanism could
@@
 On the other hand, there are cases where the policies
-introduced in the server, are enforced on the client-side,
+introduced in the server are enforced on the client-side,
 via a library embedded in the server's response
@@
 code can also be a reason that can make a mechanism
-difficult to use. {\sc sql}rand, {\sc amnesia}
-and mechanisms coming from the taint tracking
+difficult to use. {\sc sql}rand, {\sc amnesia},
+mechanisms coming from the parse-tree validation
+subcategory and mechanisms coming from the taint tracking
 subcategory are such examples.
-In the first two cases, programmers should modify every
+In the first three cases, programmers should modify every
 code fragment that involves the execution of a query.
@@
 by the developers in order to introduce their policies.
-Note also that in many cases, developers are required to
-learn a new {\sc api}.
-
-Finally, a disadvantage of mechanisms that involve training
-({\sc sd}river, {\sc xss-guard}), is that when code statements
-are altered, a new training phase is necessary. However,
-with the increased adoption of the use of automated testing
+
+Finally, even though many of the mechanism that involve
+training are easy to deploy, they have a distinct disadvantage.
+When the application is altered, mechanisms like {\sc sd}river
+and {\sc xss-guard} require a new training phase is necessary.
+However, with the increased adoption of automated testing
 and continuous integration frameworks, this phase could be
@@
 \subsection{Security}
+
+While describing the various mechanisms in
+Section~\ref{sec:defs}, we observed that some
+can be bypassed by attackers that know how they
+work.
+
+However, some mechanisms are designed in such a way
+so that they can be extended and become immune to
+the attacks that they are currently vulnerable to. For
+example, policy enforcement frameworks that are
+based on JavaScript or {\sc html} rewriting
+can be extended to detect attacks that leverage
+{\tt iframe} tags (see Subsubsection~\ref{sec:policy}).
+
+This does not apply to all mechanisms though.
+In particular, training mechanisms like {\sc didafit},
+and {\sc xss-guard} must be redesigned
+to detect the attacks that were described in
+Subsubsection~\ref{sec:train} and
+Subsection~\ref{sec:hybrid} respectively.
 
@@
 perform detection on the client side: in particular, 11 out of 19
-frameworks (57,8\%) detect JavaScript-driven {\sc xss} attacks at the
+frameworks (57,8\%) detect JavaScript-driven {\sc xss} attacks on the
 client's side. Note that the majority of the mechanisms that detect
@@
 
+\noindent
 Equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} use true and false
@@
 
+\noindent
 The prevalence is the prior probability that an event is an attack,
@@
 
+Moreover, extensive accuracy tests may lead to more
+well-designed and robust mechanisms. Observe that mechanisms
+that can be circumvented were not extensively tested
+in terms of accuracy. For instance, {\sc didafit}
+was not tested at all and {\sc xss-guard}'s testing involved
+6 known attacks. This also applies to some frameworks coming
+from the taint tracking subcategory.
+Perhaps with more tests the authors would design
+their mechanisms differently.
+
+Limiting the scope of the attacks to
+be detected may lead to an efficient tool.
+Consider the system by Stock et al. It is the only one
+that targets exclusively {\sc dom}-based
+{\sc xss} attacks and detects them in an accurate manner
+as seen in Table~\ref{tab:comp}. Notice also
+its extensive testing in real-world attacks.
+
 Another interesting finding involves the computational overhead.
@@
 18\%. Relative research on protection mechanisms~\cite{SPWS13}
-has indicated that mechanisms that introduce an overhead
+indicates that mechanisms that introduce an overhead
 larger than 10\% do not tend to gain wide adoption in
-production environments which in this case could be a
-reason why some these tools have not been adopted.
-
-Cite~\cite{DKH14}.
-
-We believe that our research may facilitate researchers
+production environments. Hence, the computational overhead
+of some mechanisms could be a reason why they have not been adopted.
+
+We need to mention that the fact that mechanisms come
+sometimes with deployment difficulties does
+not necessarily mean that this is a serious reason
+not to adopt them. The deployment of such frameworks
+is most of the time complex because as we observed
+in Section~\ref{sec:attacks} the attacks that they
+detect are complex too. So every security feature can
+come with such a trade-off and those who intend to use it
+should be aware of this.
+
+Deployment can also depend on the detection point
+of an attack. We saw that many policy enforcement
+mechanisms that detect attacks at Point {\sc ub},
+are not easy to deploy because modifications
+are needed both on the server and the client side.
+We observed though that Blueprint has not such
+deployment issues (see Subsection~\ref{sec:deploy2}).
+Thus, when developing a new countermeasure,
+researchers should consider where they are planning
+to detect attacks, observe the corresponding
+deployment challenges, and try to mitigate them.
+
+% discuss Availability. Finally,
+
+\section{Conclusions}
+
+\begin{itemize}
+\item Cite~\cite{DKH14}.
+\item We believe that our research may facilitate researchers
 or practitioners who would like to use one of the
@@
 starting point to develop their approach.
-
-\section{Conclusions}
-
-We believe that forming a
+\item We believe that forming a
 standard way to test such mechanisms in terms
@@
 would be one of the reasons of adopting them.
+\end{itemize}
 

### 2014-11-11 docs/questioning.tex
a correction in policy enforcement

@@
 that are based on reported browser vulnerabilities.
-An issue regarding this framework (as well as {\sc beep}
-and {\sc dsi}) is that it cannot define policies that
-restrict the behavior of third-party scripts introduced
-by script inclusion and {\tt iframe} tags.
-For instance, consider a web page (foo.net)
-that prints the value of a query parameter ({\tt query})
-from the page's {\sc url} in the web page's content
-without escaping the value. A malicious user
-can take advantage of this and inject an {\tt iframe}
-into the page to steal the user's cookie and
-send it via an image request to a web site
-that he or she controls (malicious.com).
-This could be achieved by including the following
-link to the malicious web site (or send it via phishing
-email) and induce the user to click on it:
-
-\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
-\begin{lstlisting}
-http://foo.net/vulnerable.html?query=
-<iframe src="javascript:document.body.innerHTML=+
-'<img src=\"http://malicious.com/?c=
-'+encodeURIComponent(document.cookie)+'\">'">
-</iframe>
-\end{lstlisting}
-
-\noindent
-The following frameworks can actually detect such
-an attack (Point {\sc ub}).
 {\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
@@
 script with malicious behavior.} would fail.
-{\it WebJail}~\cite{VDDPJ11}, is a framework similar to
-ConScript. WebJail, contains the functionality of
-third-party scripts by introducing a web component
-integrator that restricts the access that these scripts
-may have to either the data or the functionality of other components
-Finally, {\sc soma}~\cite{OWVS08} requires site administrators
+
+An issue regarding the above frameworks
+involves features like script inclusion
+and {\tt iframe} tags. Even though they allow developers
+decide if they will disable them or not,
+this is unpractical because such features are quite popular.
+If developers choose to use them, these frameworks cannot
+define policies that restrict the behavior of third-party
+scripts introduced by such features. For instance,
+consider a web page (foo.net) that prints the value
+of a query parameter ({\tt query}) from the
+page's {\sc url} in the web page's content
+without escaping the value. A malicious user
+can take advantage of this and inject an {\tt iframe}
+into the page to steal the user's cookie and
+send it via an image request to a web site
+that he or she controls (malicious.com).
+This could be achieved by including the following
+link to the malicious web site (or send it via phishing
+email) and induce the user to click on it:
+
+\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
+\begin{lstlisting}
+http://foo.net/vulnerable.html?query=
+<iframe src="javascript:document.body.innerHTML=+
+'<img src=\"http://malicious.com/?c=
+'+encodeURIComponent(document.cookie)+'\">'">
+</iframe>
+\end{lstlisting}
+
+\noindent
+{\it WebJail}~\cite{VDDPJ11}, and
+{\sc soma}~\cite{OWVS08} are two frameworks that
+can actually detect such an attack (Point {\sc ub}).
+To achieve this, {\sc soma} requires site administrators
 to specify legitimate, external domains for sending
@@
 {\sc soma} can also detect {\sc csrf} attacks.
+WebJail, contains the functionality of
+third-party scripts by introducing a web component
+integrator that restricts the access that these scripts
+may have to either the data or the functionality of other components
 

### 2014-11-11 docs/questioning.tex
SB becomes StB and EQ becomes EiQ

@@
 Point {\sc ub}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
-Point {\sc sb}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-Point {\sc eq}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+Point {\sc s}t{\sc b}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
+Point {\sc e}i{\sc q}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
 Point {\sc sdb}~\cite{BK04,LLW02,VMV05}.}
@@
 \item En route from the server to the user's browser --- in most cases
-within a proxy (Point {\sc sb}).
+within a proxy (Point {\sc s}t{\sc b}).
 \item Embedded in a query, but before it reaches the server's database
-  (Point {\sc eq}).
+  (Point {\sc e}i{\sc q}).
 \item After the malicious code has been executed on the server's
@@
 and detect the attack before a query reaches the
-database (Point {\sc eq}).
+database (Point {\sc e}i{\sc q}).
 Contrary to {\sc sqlg}uard (and other
@@
 to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
-acts as a proxy on the server side (Point {\sc SB}) to
+acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
 parse the {\sc html} of server responses and identifies
@@
 attacks are usually implemented in the form of a
-server-side proxy (Point {\sc SB})
+server-side proxy (Point {\sc s}t{\sc b})
 interposing on the client-server communication, and modifying
@@
 searches the data for illegal code by using the same keywords (Point
-{\sc SB}). Since all legitimate code has been ``masked", the injected
+{\sc s}t{\sc b}). Since all legitimate code has been ``masked", the injected
 code can be identified. The pre- and post-processing of the code
@@
 tainted string is used as an argument to a sink method
-then an exception is raised (Point {\sc eq}).
+then an exception is raised (Point {\sc e}i{\sc q}).
 
 It is possible to apply further checks when it is established that
-tainted data have reached a sink (Point {\sc eq}). {\it Xu et
+tainted data have reached a sink (Point {\sc e}i{\sc q}). {\it Xu et
   al.}~\cite{XBS06} track taint information at the level of bytes in
@@
 and others. When tainted data reaches a sink, {\sc csse} performs
-syntactic checks based on the aforementioned metadata (Point {\sc eq}).
+syntactic checks based on the aforementioned metadata (Point {\sc e}i{\sc q}).
 {\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
@@
 Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
-if there are tainted data that contain scripts (Point {\sc sb}).
+if there are tainted data that contain scripts (Point {\sc s}t{\sc b}).
 
@@
 checks all statements for compliance and can block code statements
-containing injected elements (Point {\sc eq}). {\sc
+containing injected elements (Point {\sc e}i{\sc q}). {\sc
   amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
-  sql} injection attacks (Point {\sc eq}) by associating a query model
+  sql} injection attacks (Point {\sc e}i{\sc q}) by associating a query model
 with the location of every {\sc sql} statement within the application.
@@
 Then, a JavaScript detection component placed in a web proxy (Point
-{\sc sb}) searches for injected scripts with no corresponding {\sc id}
+{\sc s}t{\sc b}) searches for injected scripts with no corresponding {\sc id}
 in the server's responses. If no injected scripts are found, the proxy
@@
 scheme creates the tree of the query that is about to be executed and
-compares it with the parsed tree of the ``shadow" (Point {\sc eq}). If
+compares it with the parsed tree of the ``shadow" (Point {\sc e}i{\sc q}). If
 the trees are not equal the application is probably under attack. Note
@@
 The other 11 wrap {\sc api} calls related to output
-vectors---Point {\sc eq}.
+vectors---Point {\sc e}i{\sc q}.
 

### 2014-11-11 docs/questioning.tex
added the last paragraph of the intro

@@
   new approaches in developing more efficient mechanisms.
-% dimitro@dimitro: change the above accordingly.
 
@@
 source code-driven injection attacks dominate the top five
-positions. Malicious users find new ways~\cite{HNSHS12,DKH14}
-to bypass defense mechanisms
+positions. Malicious users find new ways to bypass defense mechanisms
 by using a variety of techniques despite the numerous countermeasures
@@
 
-The rest of the paper is organized as follows. {\sc tba}.
-
-% In the last 15 years there are numerous mechanisms that have
-% been developed to detect one or more of the attacks mentioned
-% above. However, the majority of them are not used in practice.
-% This is due to the following reasons:
-% a) the mechanisms have not been extensively tested in terms
-% of accuracy,
-% b) are hard to deploy because they require many modifications
-% either on the client-side, the server-side, or both,
-% c) they add significant overhead, and
-% d) can be bypassed by attackers that know how they work.
-% The motivation behind this research is to systematize
-% and analyze previously proposed protection mechanisms.
-% In this way we can highlight the advantages
-% and disadvantages of each mechanism, enlist them
-% into different categories, and see how they compare to each other.
+The rest of the paper is organized as follows.
+Section~\ref{sec:attacks} provides the exploitation model
+of application attacks based on source code injection.
+Section~\ref{sec:dimensions} introduces the dimensions
+on which we base the analysis of the various defenses.
+Our categorization and analysis is presented in
+Section~\ref{sec:defs} and a discussion is provided in
+Section~\ref{sec:discussion}. Finally,
+Section~\ref{sec:lessons-learned} highlights
+some lessons learned from our observations
+and Section~\ref{sec:conclusion} concludes the paper.
 
@@
 \section{Conclusions}
+\label{sec:conclusion}
+
+% In the last 15 years there are numerous mechanisms that have
+% been developed to detect one or more of the attacks mentioned
+% above. However, the majority of them are not used in practice.
+% This is due to the following reasons:
+% a) the mechanisms have not been extensively tested in terms
+% of accuracy,
+% b) are hard to deploy because they require many modifications
+% either on the client-side, the server-side, or both,
+% c) they add significant overhead, and
+% d) can be bypassed by attackers that know how they work.
+% The motivation behind this research is to systematize
+% and analyze previously proposed protection mechanisms.
+% In this way we can highlight the advantages
+% and disadvantages of each mechanism, enlist them
+% into different categories, and see how they compare to each other.
 
 \begin{itemize}
-\item Cite~\cite{DKH14}.
+\item Cite~\cite{HNSHS12,DKH14}.
 \item We believe that our research may facilitate researchers

### 2014-11-11 docs/questioning.tex
minor correction

@@
 in which publication:
-{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
 {\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},

### 2014-11-11 docs/questioning.tex
minor changes / fixes

@@
 mechanisms coming from the parse-tree validation
-subcategory and mechanisms coming from the taint tracking
-subcategory are such examples.
+subcategory and mechanisms coming from the taint
+tracking subcategory are such examples.
 In the first three cases, programmers should modify every
@@
 all the code fragments that involve user-input handling.
-In addition, there are cases (i.e. ConScript and the system
-by Phung et al.) that require many modifications
-by the developers in order to introduce their policies.
-
-Finally, even though many of the mechanism that involve
+
+Finally, even though many of the mechanisms that involve
 training are easy to deploy, they have a distinct disadvantage.

### 2014-11-11 docs/questioning.tex
first steps in conclusions

@@
 source code-driven injection attacks dominate the top five
-positions. Malicious users find new ways to bypass defense mechanisms
-by using a variety of techniques despite the numerous countermeasures
+positions. Malicious users find new ways~\cite{HNSHS12,DKH14}
+to bypass defense mechanisms by using a variety of
+techniques despite the numerous countermeasures
 that are being introduced. Note that the number of systems developed
@@
 
-% In the last 15 years there are numerous mechanisms that have
-% been developed to detect one or more of the attacks mentioned
-% above. However, the majority of them are not used in practice.
+Despite many approaches that have been developed,
+application attacks based on source code injection
+have been consistenly present for the last 15 years,
+and it appears that they will continue to be.
+Attackers seem to find new ways to introduce
+source code to applications by using a variety of
+languages and techniques~\cite{HNSHS12,DKH14}.
+Meanwhile, duirng the last decade, there are
+numerous mechanisms that have been developed to
+detect one or more of such attacks. However,
+% even if
+% some of them share characteristics with supported frameworks
+% like Mozilla's Content Security
+% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
+% ({\sc csp}) and Google
+% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
+the majority of them are not used in practice.
+
 % This is due to the following reasons:
@@
 \begin{itemize}
-\item Cite~\cite{HNSHS12,DKH14}.
 \item We believe that our research may facilitate researchers

### 2014-11-11 docs/questioning.tex
some typos

@@
 application attacks based on source code injection
-have been consistenly present for the last 15 years,
+have been consistently present for the last 15 years,
 and it appears that they will continue to be.
@@
 languages and techniques~\cite{HNSHS12,DKH14}.
-Meanwhile, duirng the last decade, there are
+Meanwhile, during the last decade, there are
 numerous mechanisms that have been developed to

### 2014-11-11 docs/questioning.tex
more on conclusions
small fixes and additions in VI

@@
 and then trick an end user to click on it via social engineering (i.e., phishing ---
-{\it transition}: {\sc p-xss}' 1 \text{\textbar} {\sc n-xss}' 1 \text{\textbar} {\sc csrf} 1).
+{\it transition}: {\sc p-xss} 1.1 \text{\textbar} {\sc n-xss} 1.1 \text{\textbar} {\sc csrf} 1).
 Alternatively, the attacker may be able to inject
@@
 
-Moreover, extensive accuracy tests may lead to more
-well-designed and robust mechanisms. Observe that mechanisms
-that can be circumvented were not extensively tested
-in terms of accuracy. For instance, {\sc didafit}
-was not tested at all and {\sc xss-guard}'s testing involved
-6 known attacks. This also applies to some frameworks coming
-from the taint tracking subcategory.
-Perhaps with more tests the authors would design
-their mechanisms differently.
-
-Limiting the scope of the attacks to
-be detected may lead to an efficient tool.
-Consider the system by Stock et al. It is the only one
-that targets exclusively {\sc dom}-based
-{\sc xss} attacks and detects them in an accurate manner
-as seen in Table~\ref{tab:comp}. Notice also
-its extensive testing in real-world attacks.
-
-Another interesting finding involves the computational overhead.
-We observe that the average overhead that can be extracted from
-the publications that provide the overhead in percentage terms is
-18\%. Relative research on protection mechanisms~\cite{SPWS13}
-indicates that mechanisms that introduce an overhead
-larger than 10\% do not tend to gain wide adoption in
-production environments. Hence, the computational overhead
-of some mechanisms could be a reason why they have not been adopted.
+Apart from demonstrating the value of a mechanism, good accuracy tests
+may be beneficial per se, by leading to more well-designed and robust
+mechanisms. Mechanisms that can be circumvented were not extensively
+tested in terms of accuracy. For instance, {\sc didafit} was not
+tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
+This also applies to some frameworks coming from the taint tracking
+subcategory. It is possible that more tests during development would
+have led the authors to wider improvements in design. 
+%% PL: Do we have a reference in Software Engineering correlating
+%% testing with better design?
+
+The accuracy of a tool may be related to the scope of the attacks it
+aims to detect. A more limited scope may allow the development of more
+accurate tools. In this vein, the system by Stock et al~\cite{SLMS14}
+is the only one that targets exclusively {\sc dom}-based {\sc xss}
+attacks and detects them in an accurate manner as seen in
+Table~\ref{tab:comp}. It is also extensively tested in real-world
+attacks.
+
+Apart from testing practices, another area that merits improvement is
+the availability of source code and testbeds. We are not aware of
+specific reasons why authors of attack detection mechanisms seem to be
+wary of releasing online their code and tests. Our finding may reflect
+the status in the current point in time, when authors are urged to
+publish their code and tests, and may start, or may have already
+started doing so, but this does not show yet in the research we
+examined, which goes several years back. We also saw instances where
+material was published, but does not seem to be available any more.
+That points to the importance of curation of research materials. That
+is a problem arising in all scientific fields. It is not enough to
+publish the underlying code and data, but to make sure that it remains
+accessible and to provide the means to test it even as technology
+progresses and operating systems, file formats, and software libraries
+change. That may be too much to ask right now; what seems reasonable,
+though, is to ask of researchers in attack detection mechanisms not to
+buck the trend and to take steps to increase the availability of their
+research.
+
+Another interesting finding involves the computational overhead. We
+observe that the average overhead that can be extracted from the
+publications that provide the overhead in percentage terms is 18\%.
+Relative research on protection mechanisms~\cite{SPWS13} indicates
+that mechanisms that introduce an overhead larger than 10\% do not
+tend to gain wide adoption in production environments. Hence, the
+computational overhead of some mechanisms could be a reason why they
+have not been adopted.
 

### 2014-11-12 docs/questioning.tex
updated Figure 2

@@
 Figure~\ref{fig:attacks} presents the steps of different application
-attacks. For every arrow there is a
-corresponding tuple that includes the transition number for
-every attack. Every number indicates the number of the
+attacks. For every arrow there are
+corresponding transition numbers for every attack.
+Every number indicates the number of the
 steps taken until we reach this transition.
@@
 and then trick an end user to click on it via social engineering (i.e., phishing ---
-{\it transition}: {\sc p-xss} 1.1 \text{\textbar} {\sc n-xss} 1.1 \text{\textbar} {\sc csrf} 1).
+{\it transitions}: {\sc p-xss} 1.1, {\sc n-xss} 1.1, {\sc csrf} 1).
 Alternatively, the attacker may be able to inject
@@
 malicious {\sc sql} code to retrieve all the password entries from a
-database ({\it transition}: {\sc dsl} 1 \text{\textbar}
-{\sc p-xss} 1 \text{\textbar} {\sc n-xss} 1).
+database ({\it transitions}: {\sc dsl} 1,
+{\sc p-xss} 1, {\sc n-xss} 1).
 Note that an {\sc xss} attack can start from both routes.
@@
 parse and display a page of results, without properly sanitizing the
-request ({\it transition}: {\sc p-xss} 7 \text{\textbar} {\sc n-xss} 2).
+request ({\it transitions}: {\sc p-xss} 7, {\sc n-xss} 2).
 Thus, in a non-persistent {\sc xss} attack the injected code
@@
 \leavevmode
-\includegraphics[scale=0.61]{attacks-steps.pdf}
+\includegraphics[scale=0.61]{attacks-steps-new.pdf}
 \end{center}
@@
 application attacks based on source
-code injection vulnerabilities. For every arrow there is a
-corresponding tuple that includes a transition number for
+code injection vulnerabilities. For every arrow there are
+corresponding transition numbers for
 every attack. Every {\it point} indicates a transition where mechanisms
@@
 references:
-Point {\sc ub}~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
-Point {\sc s}t{\sc b}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-Point {\sc e}i{\sc q}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-Point {\sc sdb}~\cite{BK04,LLW02,VMV05}.}
+Point {\sc ub} (at the user's browser):~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
+Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
+Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+Point i{\sc db} (in the database):~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
@@
   (Point {\sc e}i{\sc q}).
-\item After the malicious code has been executed on the server's
-  database (Point {\sc sdb}).
+\item After the malicious code reaches the server's database
+  (Point i{\sc db}).
 \end{itemize}
@@
 that present corresponding mechanisms:
-{\bf 1}~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
-{\bf 2}~\cite{BK04,JB07,GC09,APKLM10},
-{\bf 3}~\cite{BWS05,SW06},
-{\bf 4}~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
-{\bf 5}~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
-{\bf 6}~\cite{BV08,LV09,SMS13}.}
+{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
+{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
+{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
+{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
+{\it Training}:~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
+{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
 \end{figure*}
@@
 the few mechanisms that detect {\sc sql} injection attacks on the
-database level (Point {\sc sdb}).
+database level (Point i{\sc db}).
 
@@
 attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms}---Point {\sc sdb}.
+of the {\sc rdbms}---Point i{\sc db}.
 The other 11 wrap {\sc api} calls related to output
@@
 
+In this paper we first introduced an exploitation model
+that can be a reference point which can be used by
+researchers who wish to develop new countermeasures.
+
 % This is due to the following reasons:

### 2014-11-12 docs/questioning.tex
more stylistic changes

@@
 \item We also find that researchers do not often make their mechanisms
-  available to the community, thus no one can either use their
-  mechanism, or replicate their experiments.
+  available to the community, thus no one can either use them,
+  or replicate their experiments.
 \item We discuss how our observations may be the main reasons why the
@@
 the server and the client.
+
+\begin{table*}
+    \caption{Comparison summary of mechanisms developed to counter application attacks based on source code injection.}
+    \label{tab:comp}
+\centering
+    \begin{threeparttable}
+    \begin{small}
+\scalebox{0.93}{
+    \begin{tabular}{l|c|c|cc|c}
+    \thickhline
+    \bf{Approach}
+  & \bf{Mechanism}
+  & \bf{\# of Citations}
+  & \multicolumn{2}{|c|}{Requirements\tnote{1}}
+  & \bf{Attack}\tnote{4} \\
+  &&& \bf{TP,TN,FP,FN}\tnote{2}
+  & \bf{Computational Overhead}\tnote{3} & \\
+    \thickhline
+  \multirow{2}{*}{Parse-Tree Validation}
+  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
+  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
+  \hline
+  \multirow{12}{*}{Policy Enforcement}
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
+  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
+  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
+  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
+  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
+  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
+  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
+  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
+  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
+  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
+  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms ({\sc c}) & {\sc xss} \\
+  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
+  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
+  % \hline
+  % \hline 
+  % \multirow{3}{*}{Securing Mashups}
+  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
+  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
+  \hline
+  \multirow{4}{*}{{\sc isr}}
+  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
+  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
+  \thickhline
+  \thickhline
+  \multirow{7}{*}{Taint Tracking}
+  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
+  % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
+  &   {\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   {\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
+  &   {\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
+  \hline 
+  \multirow{6}{*}{Training}
+  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
+  &   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
+  &   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
+  &   {\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
+  &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
+  % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
+  \thickhline
+  \thickhline
+  \multirow{3}{*}{Hybrid}
+  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
+  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and No{\sc sql}i \\
+  \thickhline
+    \end{tabular}}
+    \begin{tablenotes}
+  \begin{footnotesize}
+        \item[1] {\sc na} (Not Available) means that a requirement is not mentioned in the paper.
+  {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the\newline publication
+  but it is not quantified.
+      \item[2] Quadruples contain numbers given for True Positives
+        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
+          fp}) and False Negatives ({\sc fn}). For every quadruple\newline there is a corresponding suffix that indicates whether the testbed was
+  based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic\newline benchmarks ({\it s}), c) both ({\it a}).
+  If no testing has taken place we add a question mark ({\bf ?}).
+    \item[3] Regarding the computational overhead we show if it is applied to the server ({\sc s}) or the client ({\sc c}). 
+    \item[4] {\it i} stands for injection.
+    \item[5] The numbers of this quadruple involve requests.
+  \end{footnotesize}
+    \end{tablenotes}
+    \end{small}
+    \end{threeparttable}
+\end{table*}
 
@@
 tracking approaches as described in reference~\cite{NBR14}.
-%% PL which way is this exactly?
-
-\begin{landscape}
-\begin{table}
-    \caption{Comparison summary of mechanisms developed to counter application attacks based on source code injection.}
-    \label{tab:comp}
-\centering
-    \begin{threeparttable}
-    \begin{small}
-\scalebox{0.99}{
-    \begin{tabular}{l|c|c|cc|c}
-    \thickhline
-    \bf{Approach}
-	& \bf{Mechanism}
-	& \bf{\# of Citations}
-  & \multicolumn{2}{|c|}{Requirements\tnote{1}}
-	& \bf{Attack} \\
-	&&& \bf{TP,TN,FP,FN}\tnote{2}
-	& \bf{Computational Overhead}\tnote{3} & \\
-    \thickhline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql} injection \\
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql} injection \\
-  \hline
-  \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
-  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
-  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{4} & {\sc na} ({\sc c}) & {\sc csrf} \\
-  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms ({\sc c}) & {\sc xss} \\
-  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
-  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
-  % \hline
-  % \hline 
-  % \multirow{3}{*}{Securing Mashups}
-  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
-  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  \hline
-  \multirow{4}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql} injection \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql} injection, {\sc xss} \\
-  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc c}) & {\sc xss} \\ 
-  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
-  \thickhline
-  \thickhline
-	\multirow{7}{*}{Taint Tracking}
-  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql} injection, {\sc xp}ath, {\sc xss} \\
-	% &  	{\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-	&  	{\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\ 
-  &  	{\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql} injection, {\sc xss} \\
-	&  	{\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-	&  	{\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql} and {\sc php} injection, {\sc xss} \\
-	& 	{\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
-	\hline 
-  \multirow{6}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql} injection \\
-	&   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql} injection \\ 
-	&   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql} injection \\
-	& 	{\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  & 	{\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
-	& 	{\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql} and {\sc xp}ath injection \\
-	% & 	{\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-  \thickhline
-  \thickhline
-  \multirow{3}{*}{Hybrid}
-  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
-  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql} and No{\sc sql} injection \\
-	\thickhline
-    \end{tabular}}
-    \begin{tablenotes}
-	\begin{footnotesize}
-       	\item[1] {\sc na} (Not Available) means that a requirement is not mentioned in the paper.
-	{\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
-	but it is not quantified.
-      \item[2] Quadruples contain numbers given for True Positives
-        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
-          fp}) and False Negatives ({\sc fn}). For every quadruple there is a corresponding suffix that indicates whether the testbed was
-	based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic benchmarks ({\it s}), c) both ({\it a}).
-	If no testing has taken place we add a question mark ({\bf ?}).
-    \item[3] Regarding the computational overhead we show if it is applied to the server ({\sc s}) or the client ({\sc c}). 
-    \item[4] The numbers of this quadruple involve requests.
-	\end{footnotesize}
-    \end{tablenotes}
-    \end{small}
-    \end{threeparttable}
-\end{table}
-\end{landscape}
 
@@
     \begin{small}
-\scalebox{0.99}{
+\scalebox{0.93}{
     \begin{tabular}{l|c|ccc}

### 2014-11-12 docs/questioning.tex
some corrections

@@
 references:
-Point {\sc ub} (at the user's browser):~\cite{KJKV09,TNH07,NSS06,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
-Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
-Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+Point {\sc ub} (at the user's browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
+Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08,PS11},
+Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
 Point i{\sc db} (in the database):~\cite{BK04,LLW02,VMV05}.}
@@
 and {\sc dsi}~\cite{NSS06}. The main problem with
-the above mechanisms is that they are vulnerable
-to non-persistent {\sc xss} attacks that alter
-the {\sc dom} of an already rendered
-page~\cite{APKLM10}.
-In addition, a recent variation of JavaScript
-injection attacks known as return-to-JavaScript
-attack can be used to bypass the above mechanisms
-as described extensively in reference~\cite{APKLM10}.
+these mechanisms is that they do
+not examine the script's location inside the web
+document. Based on this fact, attackers
+can perform mimicry attacks~\cite{WS02}.
+Specifically, they can execute legitimate scripts,
+but not as intended by the original design of
+the developers. This is extensively described
+in reference~\cite{APKLM10}. In addition,
+the authors of~\cite{APKLM10} describe
+another recent variation of JavaScript
+injection attacks that can be used to bypass the
+above mechanisms, known as return-to-JavaScript
+attacks.
 % Such attacks share
@@
 support cross-origin requests.
-{\it j{\sc csrf}}~\cite{PS11}
-has a very similar functionality and meanwhile
-addresses the above problems.
+{\it j{\sc csrf}}~\cite{PS11} has a similar
+functionality and meanwhile addresses the above problems.
 Finally, {\it CsFire}~\cite{DDHPJ10}
@@
 must set specific policies in a manner similar to a firewall
-configuration language. This fact, together with the insufficient
-testing of the mechanism (see Table~\ref{tab:comp}) brings up
-questions concerning its accuracy. {\it {\sc
-    sm}ask}~\cite{JB07} is another framework that was inspired by {\sc
-  isr}. To detect {\sc xss} attacks it searches for {\sc html} and
+configuration language. {\it {\sc sm}ask}~\cite{JB07} is another
+framework that was inspired by {\sc isr}. To detect {\sc xss}
+attacks it searches for {\sc html} and
 JavaScript keywords within the application's legitimate code. This is
@@
   &   {\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   {\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
   &   {\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
@@
 {\sc xss} attacks based on JavaScript injection
-would fail to detect a return-to-JavaScript
-attack~\cite{APKLM10}.
+would fail to detect mimicry attacks 
+where legitimate scripts can be executed by
+attackers, but not in the way intended by
+the the developers~\cite{APKLM10}.
 
@@
 therefore a false negative result could occur if an adversary performs
-a mimicry attack~\cite{WS02}. For example, consider a banner rotator
+the following attack: Consider a banner rotator
 that every time it runs, it creates a value that depends on the
@@
 transfered to the document generator of the browser (Point {\sc ub})
-where untrusted browser parsing behavior is ruled out. Blueprint is an
-efficient countermeasure but it imposes a significant overhead due to
-its extensive parsing (see Table~\ref{tab:comp}).
+where untrusted browser parsing behavior is ruled out.
+Blueprint is an efficient countermeasure but it imposes an
+overhead due to its extensive parsing (see Table~\ref{tab:comp}).
 
@@
 
-In frameworks that deal with JavaScript-driven {\sc xss} attacks we
+In frameworks that deal with {\sc xss} attacks we
 see that attack detection may take place either on the server-side or
@@
 attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client side: in particular, 11 out of 19
-frameworks (57,8\%) detect JavaScript-driven {\sc xss} attacks on the
+perform detection on the client side: in particular, 14 out of 23
+frameworks (60,8\%) detect {\sc xss} attacks on the
 client's side. Note that the majority of the mechanisms that detect
 such attacks on the server-side can also detect {\sc dsl} code
-injection attacks (7 out of 8).
+injection attacks (6 out of 9).
 

### 2014-11-12 docs/questioning.tex
fixes up to IV

@@
   Scripting and {\sc sql} injection, exploit the oversight of
-  programmers that develop applications which may accept and process
+  programmers that develop applications that may accept and process
   data of uncertain origin without appropriate validation and / or
@@
   various defense mechanisms against source code injection by setting
-  up a model that highlights the key weaknesses behind such attacks and
-  helps us observe defenses from a common perspective.
+  up a model that highlights the key weaknesses behind such attacks
+  and provides a common perspective for the different defenses.
 
   We then categorize and analyze the various defense mechanisms that
-  have been developed. Our analysis is based on dimensions such as
-  accuracy, performance, deployment, security and availability.
-  Especially notable is accuracy, as our findings show that there are
-  many defense mechanisms that are tested in a poor manner.
-  In addition, we observe that there are mechanisms
-  that can be bypassed by attackers that know how the mechanisms
-  work.
+  have been developed. Our analysis is based on accuracy, performance,
+  deployment, security and availability. Especially notable is
+  accuracy, as our findings show that there are many defense
+  mechanisms that are tested in a poor manner. In addition, we observe
+  that there are mechanisms that can be bypassed by attackers that
+  know how the mechanisms work.
 
   By comparing the existing defenses and identifying their common
-  characteristics, we help: a) researchers and practitioners to choose
-  or modify a mechanism according to their needs, and b) designers of
+  characteristics, we help researchers and practitioners to choose or
+  modify a mechanism according to their needs as well as designers of
   new approaches in developing more efficient mechanisms.
@@
 Top Ten project is popular, referenced by numerous researchers. In its
-three consecutive Top Ten lists (2007, 2010, 2013), different
-source code-driven injection attacks dominate the top five
-positions. Malicious users find new ways~\cite{HNSHS12,DKH14}
-to bypass defense mechanisms by using a variety of
-techniques despite the numerous countermeasures
-that are being introduced. Note that the number of systems developed
-to counter {\sc sql} injection attacks until 2006 was more than
-twenty~\cite{HVO06}. Since then the number has doubled. Researchers
-have also indicated that the number of such attacks is steadily
+three consecutive Top Ten lists (2007, 2010, 2013), different source
+code-driven injection attacks dominate the top five positions.
+Malicious users find new ways~\cite{HNSHS12,DKH14} to bypass defense
+mechanisms by using a variety of techniques despite the numerous
+countermeasures that are being introduced. The number of systems
+developed to counter {\sc sql} injection attacks until 2006 was more
+than twenty~\cite{HVO06}. Since then the number has doubled.
+Researchers have indicated that the number of such attacks is steadily
 increasing in recent years~\cite{SSL12}.
 
-In this paper we initially show how the above attacks can be seen from
-a {\it common perspective}. We achieve this by providing an
-exploitation model that highlights the following fact: the majority of
-the steps needed to perform application attacks based on
-source code injection are common.\footnote{Note that we leave out
-  attacks that are based on binary code injection (i.e. buffer
-  overflows --- see Section~\ref{sec:attacks}).} This is validated by
-the fact that there are protection mechanisms that can detect more
-than one of these attacks. Then, we {\it categorize} a selection of
-these protection mechanisms. The selection comprises protection
-mechanisms that detect such attacks and are presented in publications
-cited more than twenty times, and some of the latest mechanisms that
-have been presented in top security conferences that have been cited
-less than twenty times. We included the second group so that we would
-not penalize recent research. Finally, we {\it analyze} each mechanism based
-on the following dimensions:
+In this paper we show how the above attacks can be seen from a {\it
+  common perspective}. We achieve this by providing an exploitation
+model that highlights that the majority of the steps needed to perform
+application attacks based on source code injection are
+common.\footnote{Note that we leave out attacks that are based on
+  binary code injection (i.e. buffer overflows --- see
+  Section~\ref{sec:attacks}).} This is validated by the fact that
+there are protection mechanisms that can detect more than one of these
+attacks. Then, we {\it categorize} a selection of these protection
+mechanisms. In the selection we included protection mechanisms that
+detect such attacks and are presented in publications cited more than
+twenty times. We also added some recent mechanisms that have been
+presented in top security conferences, even though they have been
+cited less than twenty times. We included the second group so that we
+would not penalize recent research. Finally, we {\it analyze} each
+mechanism based on the following dimensions:
 \begin{itemize}
@@
   false negative rates.
-\item {\it Computational Performance} We examine
-  the overhead of the mechanisms
-  that affect the experience of a web user who actually
-  uses the protected application.
+\item {\it Availability} We check if the mechanism and its
+  testbed are available on-line.
+\item {\it Computational Performance} We examine the computational
+  overhead of the mechanisms at their points of deployment.
 \item {\it Ease of use} We examine if the protection
@@
   we examine the location where a mechanism detects an attack.
-\item {\it Availability} We check if the mechanism and its
-  testbed are available on-line.
-available 
 \end{itemize}
@@
 approaches and mechanisms that we report here.
-This is mainly because this work includes countermeasures
+This is mainly because that work includes countermeasures
 that detect such vulnerabilities via program analysis
@@
   program is vulnerable to code injection''}. Ray and
-Ligatti~\cite{RL12b} actually proved the above claim based on formal
-language theory.
+Ligatti~\cite{RL12b} have proved this claim based on formal language
+theory.
 
@@
 subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
-{\sc xml} play an significant role in the development of either web or
+{\sc xml} play an significant role in the development of both web and
 mobile applications. For example, many applications have interfaces
@@
 System ({\sc rdbms}). This input can become part of an {\sc sql} query
-and executed on the target {\sc rdbms}. A code injection attack that
+and get executed on the target {\sc rdbms}. A code injection attack that
 exploits the vulnerabilities of these interfaces by taking advantage
 of input validation issues like incorrectly passed parameters or
-incorrect type handling, is called an {\sc sql} injection
+incorrect type handling is called an {\sc sql} injection
 attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
-malicious users can perform other exploits based on {\sc dsl}s,
+malicious users can perform other exploits based on {\sc dsl}s
 like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
@@
 
-A recent class of {\sc cia}s involve dynamic languages like
-JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
+A recent class of code injection attacks involve dynamic languages
+like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
 injection attacks, in particular, make up a large subset of dynamic
@@
 and alter its execution flow~\cite{ELX07}. JavaScript injection
-attacks are considered as a critical issue in web application security
-mainly because they are associated with major vulnerabilities such as:
-{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{BJM08,LZRL09} and
-Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
-In many cases {\sc xss} attacks involve the injection of
-both {\sc html} and JavaScript code.
+attacks are considered a critical issue in web application security
+mainly because they are associated with major vulnerabilities such as
+{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{BJM08,LZRL09}
+and Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}. In
+many cases {\sc xss} attacks involve the injection of both {\sc html}
+and JavaScript code.
 
@@
 understand the process of carrying out application attacks based on
-source code injection vulnerabilities.
-Figure~\ref{fig:attacks} presents the steps of different application
-attacks. For every arrow there are
-corresponding transition numbers for every attack.
-Every number indicates the number of the
-steps taken until we reach this transition.
-For the most part, the steps are common in all attacks. This
+source code injection vulnerabilities. Figure~\ref{fig:attacks}
+presents the steps of different application attacks. Links between
+steps are labelled with the paths constituting different attacks. The
+sequence of steps for each attack is shown by the numbers next to the
+attack names in the labels. Most steps are common in all attacks. This
 is because they are based on similar attack vectors as we mentioned in
-the previous section. Most importantly,
-Figure~\ref{fig:attacks} illustrates in which transitions
-the defenses detect corresponding attacks.
+the previous section. Large crosses on transitions in
+Figure~\ref{fig:attacks} indicate the points where defenses detect
+attacks.
 
@@
 vehicle, through which the code will be injected in the application.
-For example, the attacker could craft a malicious script into a {\sc url}
-and then trick an end user to click on it via social engineering (i.e., phishing ---
-{\it transitions}: {\sc p-xss} 1.1, {\sc n-xss} 1.1, {\sc csrf} 1).
-Alternatively, the attacker may be able to inject
-directly the malicious code in the application. For example, consider
-a web application that accepts and redisplays user input
-without appropriate validation. An attacker could
-upload data containing a specially crafted script (for example, in a
-blog comment) to steal the cookies of the visiting users or embed
-malicious {\sc sql} code to retrieve all the password entries from a
-database ({\it transitions}: {\sc dsl} 1,
-{\sc p-xss} 1, {\sc n-xss} 1).
-Note that an {\sc xss} attack can start from both routes.
+For example, the attacker could craft a malicious script into a {\sc
+  url} and then trick an end user to click on it via social
+engineering (i.e., phishing, through transition {\sc p-xss} 1.1, {\sc
+  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
+to inject directly the malicious code in the application (through
+transition {\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
+in a web application that accepts and redisplays user input
+without appropriate validation. An attacker could upload data
+containing a specially crafted script (for example, in a blog comment)
+to steal the cookies of the visiting users or embed malicious {\sc
+  sql} code to retrieve all the password entries from a database. Note that
+an {\sc xss} attack can start from both routes.
 
@@
 
-{\sc xss} attacks fall ino two categories, {\it non-persistent} and
+{\sc xss} attacks fall into two categories, {\it non-persistent} and
 {\it persistent}. Non-persistent {\sc xss} attacks take place when the
@@
 parse and display a page of results, without properly sanitizing the
-request ({\it transitions}: {\sc p-xss} 7, {\sc n-xss} 2).
+request (transition {\sc p-xss} 7, {\sc n-xss} 2).
 Thus, in a non-persistent {\sc xss} attack the injected code
@@
 an important issue outside the computer science field: the journal
-Nature, in a recent editorial, adopted a publication policy stressing
+\emph{Nature}, in a recent editorial, adopted a publication policy stressing
 access to code and data~\cite{nature2014}. At a time and date that the
 merits of open access to code are discussed in non computer science
-journals~\cite{easterbrook2014} we should expect computer scientists
+journals~\cite{easterbrook2014}, we should expect computer scientists
 to lead the way.
@@
 different overheads may be acceptable server-side than client-side.
-For example, reporting absolute measurements gives little information
-on the real overhead, unless separate measurements are given for the
-system under study with and without the proposed mechanism. Percentage
-measurements are normally better. Outliers may be important. It is
-always necessary to describe the experimental setup.
+
+Other factors matter as well. Reporting absolute measurements gives
+little information on the real overhead, unless separate measurements
+are given for the system under study with and without the proposed
+mechanism. Percentage measurements are normally better. Outliers may
+be important. It is always necessary to describe the experimental
+setup.
 
@@
 
-The ease of use, in turn, depends on several factors. The detection
-mechanism may be deployed server-side or client-side, or both.
-Deployments on just the server or the client are easier to handle than
-deployments on both of them. The mechanism may be an add-on, or
-plugin, on existing software, client or server, or it may be tightly
-integrated with existing software, requiring rebuilding from source
-code.
+Ease of use depends on the deployment protocol required for the
+mechanism. The detection mechanism may be deployed server-side or
+client-side, or both. Deployments on just the server or the client are
+easier to handle than deployments on both of them. The mechanism may
+be an add-on, or plugin, on existing software, client or server, or it
+may be tightly integrated with existing software, requiring rebuilding
+from source code.
 
@@
 by more sophisticated countermeasures, yet again bypassed by cannier
-attacks, and so on. We use Security to refer to the ability of a
+attacks, and so on. We use security to refer to the ability of a
 detection mechanism to resist being circumvented.

### 2014-11-12 docs/questioning.tex
minor change in Figure 2, NoSQL injection became JSON injection

@@
 like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
-and No{\sc sql}~\cite{SMS13}. With this kind of attacks,
+and {\sc json}~\cite{SMS13}. With this kind of attacks,
 a malicious user can view sensitive information,
@@
   &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and No{\sc sql}i \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
   \thickhline
@@
 injection attacks. In addition, it is actually the first, and so far
-the only framework that detects No{\sc sql} injection attacks. When an
+the only framework that detects {\sc json} injection attacks. When an
 application computes an output string (query), Diglossia computes a

### 2014-11-12 docs/questioning.tex
further fixes to Section VI

--- 2014-11-12 docs/questioning.tex
@@
 
-Other factors matter as well. Reporting absolute measurements gives
-little information on the real overhead, unless separate measurements
-are given for the system under study with and without the proposed
-mechanism. Percentage measurements are normally better. Outliers may
-be important. It is always necessary to describe the experimental
-setup.
+What kind of numbers is reported matters as well. Reporting absolute
+measurements gives little information on the real overhead, unless
+separate measurements are given for the system under study with and
+without the proposed mechanism. Percentage measurements are normally
+better.
 
@@
 against web application attacks, based on source code
-injectiion. For each approach we provide the references
+injection. For each approach we provide the references
 that present corresponding mechanisms:
@@
 we proposed apart from availability, which we treat separately in the
-``Discussion" section (\ref{sec:discussion}).
+discussion in Section (\ref{sec:discussion}).
 
@@
 We can identify three approaches:
-{\it etiological}, {\it symptomatic} and {\it hybrid}.
+{\it etiological}, {\it symptomatic}, and {\it hybrid}.
 The etiological category involves mechanisms designed to
@@
 
-Finally, as we mentioned in Subsection~\ref{sec:model},
-Figure~\ref{fig:attacks} illustrates for each mechanism (found in the
-figure's caption), the point where it detects attacks.
+Recall that the point where attacks are detected is given in the
+caption of Figure~\ref{fig:attacks}.
 
@@
 
-The key idea behind this approach is to compare
-the tree representation of the abstract syntactic
-structure of the source code that is about to be
-executed with the one that was originally intended.
-If the trees diverge, the application is probably
-under attack.
+The key idea behind parse-tree validation is to compare the tree
+representation of the abstract syntactic structure of the source code
+that is about to be executed with the one that was originally
+intended. If the trees diverge, the application is probably under
+attack.
 
@@
 database (Point {\sc e}i{\sc q}).
-Contrary to {\sc sqlg}uard (and other
-mechanisms as we will observe), {\sc sql}check has been
+Contrary to {\sc sqlg}uard and other
+mechanisms, {\sc sql}check has been
 extensively tested in terms of accuracy
-as it can be seen in Table~\ref{tab:comp}.
+as can be seen in Table~\ref{tab:comp}.
 A disadvantage of those mechanisms is that the
@@
 this approach and examine the syntax trees
-of scripts to detect JavaScript-driven {\sc xss} attacks
+of scripts to detect JavaScript-driven {\sc xss} attacks,
 as we will see in Subsection~\ref{sec:hybrid}.
@@
 
-This approach is used to detect {\sc xss} and {\sc csrf} attacks.
-When using a framework that implements
-this approach, developers must define
-specific security policies on the server side.
-Policies can be expressed through JavaScript extensions,
-pattern matching or syntax specific settings.
-Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that intercepts
-server responses.
+This approach is used to detect {\sc xss} and {\sc csrf} attacks. When
+using a framework that implements policy enforcement, developers must
+define specific security policies on the server side. Policies can be
+expressed through JavaScript extensions, pattern matching, or syntax
+specific settings. Then the policies are enforced either in the user's
+browser at runtime or in a server-side proxy that intercepts server
+responses.
 
@@
 it does not deal with JavaScript-driven {\sc xss}
-attacks which is currently the most popular
+attacks, which currently make for the most popular
 {\sc xss} attack vector.
 
-A number of the frameworks define policies
-based on information and features provided by
-the Document Object Model ({\sc dom}) of a web page.
-Specifically, developers must place all legitimate
-scripts inside {\sc html} elements like {\tt div}.
-The web browser (Point {\sc ub}), parses the
-{\sc dom} tree and executes scripts only when they
-are contained in such elements. All other scripts
-are treated according to the policies defined
-on the server. Frameworks that support this
-functionality are {\sc beep}~\cite{TNH07}
-and {\sc dsi}~\cite{NSS06}. The main problem with
-these mechanisms is that they do
-not examine the script's location inside the web
-document. Based on this fact, attackers
-can perform mimicry attacks~\cite{WS02}.
-Specifically, they can execute legitimate scripts,
-but not as intended by the original design of
-the developers. This is extensively described
-in reference~\cite{APKLM10}. In addition,
-the authors of~\cite{APKLM10} describe
-another recent variation of JavaScript
-injection attacks that can be used to bypass the
-above mechanisms, known as return-to-JavaScript
-attacks.
+A number of the frameworks define policies based on information and
+features provided by the Document Object Model ({\sc dom}) of a web
+page. Specifically, developers must place all legitimate scripts
+inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
+  ub}), parses the {\sc dom} tree and executes scripts only when they
+are contained in such elements. All other scripts are treated
+according to the policies defined on the server. Frameworks that
+support this functionality are {\sc beep}~\cite{TNH07} and {\sc
+  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
+they do not examine the script's location inside the web document.
+Based on this fact, attackers can perform mimicry attacks~\cite{WS02}.
+Specifically, they can execute legitimate scripts, but not as intended
+by the original design of the developers. This is extensively
+described by {\it Athanasopoulos et al.}~\cite{APKLM10}, who also describe
+another recent variation of JavaScript injection attacks, known as
+return-to-JavaScript attacks that can be used to bypass the above
+mechanisms.
 % Such attacks share
@@
 acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
-parse the {\sc html} of server responses and identifies
+parse the {\sc html} of server responses and identify
 scripts. Then, it rewrites them into safe equivalents
@@
 
-\noindent
-{\it WebJail}~\cite{VDDPJ11}, and
-{\sc soma}~\cite{OWVS08} are two frameworks that
-can actually detect such an attack (Point {\sc ub}).
-To achieve this, {\sc soma} requires site administrators
-to specify legitimate, external domains for sending
-or receiving information in order to approve interactions
-between them and the protected web site. As a result,
-{\sc soma} can also detect {\sc csrf} attacks.
-WebJail, contains the functionality of
-third-party scripts by introducing a web component
-integrator that restricts the access that these scripts
-may have to either the data or the functionality of other components
+\noindent {\it WebJail}~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
+are two frameworks that can actually detect such an attack (Point {\sc
+  ub}). To achieve this, {\sc soma} requires site administrators to
+specify legitimate, external domains for sending or receiving
+information in order to approve interactions between them and the
+protected web site. As a result, {\sc soma} can also detect {\sc csrf}
+attacks. WebJail contains the functionality of third-party scripts by
+introducing a web component integrator that restricts the access that
+these scripts may have to either the data or the functionality of
+other components.
 
@@
 server-side proxy (Point {\sc s}t{\sc b})
-interposing on the client-server communication, and modifying
+interposed on the client-server communication and modifying
 it. {\it NoForge}~\cite{JKK06a}
@@
 execution environment. In this way, the malicious code injected by the
-attackers who do not know the randomization algorithm, will not get
+attackers who do not know the randomization algorithm will not get
 executed.
@@
 The modified queries are reconstructed at runtime using the same key
-that is inaccessible to the malicious user. {\sc sql}rand is one of
-the few mechanisms that detect {\sc sql} injection attacks on the
-database level (Point i{\sc db}).
+used for randomization, which is inaccessible to the malicious user.
+{\sc sql}rand is one of the few mechanisms that detect {\sc sql}
+injection attacks on the database level (Point i{\sc db}).
 
@@
 {\sc s}t{\sc b}). Since all legitimate code has been ``masked", the injected
-code can be identified. The pre- and post-processing of the code
+code can be identified. The pre- and post-processing of the code,
 though, may add a significant overhead to the application.
@@
 {\sc isr} is a deterministic approach that can be applied to detect
-different attacks in an efficient manner. However, Sovarel et
-al.~\cite{SEP05} have investigated thoroughly the effectiveness of
+different attacks in an efficient manner. However, {\it Sovarel et
+al.}~\cite{SEP05} have investigated thoroughly the effectiveness of
 {\sc isr} and showed that a malicious user may be able to circumvent
-it by determining the randomization key and their results indicate
+it by determining the randomization key. Their results indicate
 that doing {\sc isr} in a way that provides a certain degree of
@@
 mechanisms must follow good coding practices and never show a
-randomized code statement in any case (i.e. an exception error)
+randomized code statement in any case (i.e., an exception error)
 because in this way they will reveal the encoding key.
@@
 Even though the above implementations impose a low computational
-overhead, they impose an infrastructure overhead. In particular, in
+overhead, they impose a deployment infrastructure overhead. In particular, in
 {\sc sql}rand requires the integration of a proxy within the database
@@
 
-In this section we examine the two main symptomatic
-approaches.
+Symptomatic approaches adopt one of two tacks. They either track
+untrusted input and ban certain operations on it, or they first learn what
+code to trust and then approve for execution code that they recognize
+as safe.
 
@@
 
-A taint tracking scheme marks untrusted
-(``tainted") data (for instance, a variable set
-by a field in a web form) and traces its flow through
-the program. If the variable is used in an expression
-that sets another variable, that variable is also
-marked as untrusted and so on. If any of these variables
-is used to execute a potentially risky command (``sink") the
-scheme may act accordingly.
+A taint tracking scheme marks untrusted (``tainted") data (for
+instance, a variable set by a field in a web form) and traces its flow
+through the program. If the variable is used in an expression that
+sets another variable, that variable is also marked as untrusted and
+so on. If any of these variables is used in a potentially risky
+command (for example, send the data to a vulnerable ``sink'', such as
+a database, a file, the network) the scheme may act accordingly.
 
@@
 tainted string is used as an argument to a sink method
-then an exception is raised (Point {\sc e}i{\sc q}).
+an exception is raised (Point {\sc e}i{\sc q}).
 
@@
 {\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
-metadata, it takes advantage of {\sc php} arrays data structure.
+metadata, it takes advantage of the  {\sc php} array data structure.
 Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
@@
 the majority of the above schemes. Furthermore, most of them are not
-easy to deploy since the majority of input vectors, string operations
+easy to deploy since the majority of input vectors, string operations,
 and output vectors of the application must be instrumented.
@@
 mechanism registers all valid legitimate code statements during a
-training phase (mostly in the form of signatures). This can
-be done in various ways according to the implementation. Then, only
-those will be recognized and approved for execution
-during production.
+training phase (mostly in the form of signatures). This can be done in
+various ways according to the implementation. Then, only those
+statements will be recognized and approved for execution during
+production.
 
 Training methods that detect {\sc dsl}-driven injection attacks
-generate and store valid code statements (i.e. {\sc sql} or {\sc
+generate and store valid code statements (i.e., {\sc sql} or {\sc
   xp}ath queries) in various forms, and detect attacks as outliers
@@
     didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
-sdb) attacks by recording all database transactions
-(stripped from user input). Subsequent
+{\sc sdb}) attacks by recording all database transactions
+stripped from user input. Subsequent
 refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
@@
 that can depend either on the code statement or on its execution
-environment (i.e. the stack trace). Then, at runtime, the mechanism
+environment (i.e., the stack trace). Then, at runtime, the mechanism
 checks all statements for compliance and can block code statements
@@
 of {\it {\sc xssds}}~\cite{JEP08} have implemented a similar mechanism
-that also supports dynamic and external scripts. Specifically, during
+that also supports dynamic and external scripts. Specifically, during the
 training phase they build a list of all benign scripts. In the case of
@@
 Defenses based on training include some mechanisms that can be easily
-circumvented. For example, {\sc didafit} and {\it libAnomaly}
-do not tag transactions with their corresponding call-sites.
-In this case a false negative result
-is prominent. For instance, consider an application that will send the
-password for a forgetful user via email by executing the following
-query:
-\bgroup
-\lstset{language=SQL}
+circumvented. For example, {\sc didafit} and {\it libAnomaly} do not
+tag transactions with their corresponding call sites. This can lead
+easily to false negatives. For instance, consider an application that
+will send the password for a forgetful user via email by executing the
+following query: \bgroup \lstset{language=SQL}
 \begin{small}
@@
 \noindent
-In this case {\sc didafit} and {\it libAnomaly}, could be easily escaped
-since a malicious user, could obtain the administrator's password
+In this case {\sc didafit} and {\it libAnomaly}, could be easily bypassed
+since a malicious user could obtain the administrator's password
 by email by entering on the password retrieval form
@@
 \noindent
-
-However, mechanisms that create signatures that involve
-elements not only associated with the code statements
-(i.e. {\sc amnesia} and {\sc sd}river)
-could detect such attacks. Specifically,
-{\sc sd}river associates a complete stack trace with the
-root of an {\sc sql} statement, thus it can correlate
-queries with their call sites and detect attacks
-like the aforementioned one.
-Furthermore, training tools that detect
-{\sc xss} attacks based on JavaScript injection
-would fail to detect mimicry attacks 
-where legitimate scripts can be executed by
-attackers, but not in the way intended by
-the the developers~\cite{APKLM10}.
-
-In general, the detection accuracy of training approaches is
-heavily based on the coverage that is achieved during the
-training phase. If the coverage is insufficient the
-production of false alarms is very likely.
-In addition, when a code statement is altered, a new
-training phase is necessary.
-
-Most of the mechanisms above are relatively easy to deploy.
+The infected query matches the signature of the second one above and
+is therefore accepted. The problem lies with the call location of the
+query, not the query alone.
+
+Mechanisms that create signatures that involve elements not only
+associated with the code statements (i.e., {\sc amnesia} and {\sc
+  sd}river) could detect such attacks. Specifically, {\sc sd}river
+associates a complete stack trace with the root of an {\sc sql}
+statement, thus it can correlate queries with their call sites and
+detect attacks like the aforementioned one. Furthermore, training
+tools that detect {\sc xss} attacks based on JavaScript injection
+would fail to detect mimicry attacks where legitimate scripts can be
+executed by attackers, but not in the way intended by the the
+developers~\cite{APKLM10}.
+
+In general, the detection accuracy of training approaches is heavily
+based on the coverage that is achieved during the training phase. If
+the coverage is insufficient false alarms are very likely. In
+addition, when a code statement is altered, a new training phase is
+necessary.
+
+Most of the training approaches are relatively easy to deploy.
 {\sc dsl} injection attack countermeasures
@@
 This category includes mechanisms that borrow
-characteristics from more than one of the above categories.
+characteristics from both of the above categories.
 Two of them focus on the detection of {\sc xss}
@@
 
-{\sc xss-guard}~\cite{BV08} is a training scheme that also employs
+{\sc xss-guard}~\cite{BV08} is a training scheme that employs
 parse-tree validation. During training, the scheme maps legitimate
@@
 utilizes that data structures of Firefox's JavaScript engine (Point
-{\sc ub}). However, string literals are not compared literally and
-therefore a false negative result could occur if an adversary performs
-the following attack: Consider a banner rotator
-that every time it runs, it creates a value that depends on the
+{\sc ub}). However, string literals are not compared literally, which
+can lead to false negatives. For instance, consider a banner rotator
+that every time it runs it creates a value that depends on the
 current date and the length of the array that contains the references
@@
 {\it Blueprint}~\cite{LV09} is a policy enforcement framework that
-also utilizes parsed trees to detect {\sc xss} attacks. To guarantee
+uses parsed trees to detect {\sc xss} attacks. To guarantee
 that untrusted content is not executed, Blueprint generates on the
@@
 does not contain any dynamic content. Then the parsed tree is
-transfered to the document generator of the browser (Point {\sc ub})
+transfered to the document generator of the browser (Point {\sc ub}),
 where untrusted browser parsing behavior is ruled out.
@@
 
-{\it Diglossia}~\cite{SMS13} combines positive taint tracking (see
-Subsubsection~\ref{sec:taint}) together with parse-tree validation.
-Diglossia was based on the theory of Ray and Ligatti~\cite{RL12b}
-(also see Section~\ref{sec:attacks}) to detect {\sc dsl} code
-injection attacks. In addition, it is actually the first, and so far
-the only framework that detects No{\sc sql} injection attacks. When an
-application computes an output string (query), Diglossia computes a
-``shadow" of this string. Specifically, it maps all characters
-introduced by the application to a shadow character set. This set does
-not contain any characters coming from the tainted input. Then, the
-scheme creates the tree of the query that is about to be executed and
-compares it with the parsed tree of the ``shadow" (Point {\sc e}i{\sc q}). If
-the trees are not equal the application is probably under attack. Note
-that Diglossia can be bypassed in the same way as other taint
-tracking approaches as described in reference~\cite{NBR14}.
+{\it Diglossia}~\cite{SMS13} combines positive taint tracking together
+with parse-tree validation. Diglossia was based on the theory of Ray
+and Ligatti~\cite{RL12b} (which we saw in Section~\ref{sec:attacks})
+to detect {\sc dsl} code injection attacks. In addition, it is
+actually the first, and so far the only framework that detects No{\sc
+  sql} injection attacks. When an application computes an output
+string (query), Diglossia computes a ``shadow" of this string.
+Specifically, it maps all characters introduced by the application to
+a shadow character set. This set does not contain any characters
+coming from the tainted input. Then, the scheme creates the tree of
+the query that is about to be executed and compares it with the parsed
+tree of the ``shadow" (Point {\sc e}i{\sc q}). If the trees are not
+equal the application is probably under attack. Note that Diglossia
+can be bypassed in the same way as other taint tracking
+approaches~\cite{NBR14}.
 
@@
        \item[1] The check mark (\tick) indicates that the publication
-       includes a homepage where the reader can refer to, to
+       includes a homepage where the reader can 
        download the corresponding software. {\bf AO} (Available On-line) suggests
@@
        address was not mentioned in the paper, which probably indicates that
-       the authors made it available after the publication. The question ({\bf ?})
-       mark, indicates that the a homepage for the software was included
+       the authors made it available after the publication. The question 
+       mark ({\bf ?}) indicates that the a homepage for the software
+       was included
        in the publication but now it is not available.
@@
 \end{center}
-\caption{\label{fig:defect_sources}A pie showing the sources
-where the authors reffered to, to find vulnerabilities to test
+\caption{\label{fig:defect_sources}Pie chart showing the sources
+that the used to find vulnerabilities to test
 their mechanisms. We also provide which source was used
@@
 
-Table~\ref{tab:comp} indicates that the authors of 3 out of 34
-(8.8\%) publications, provided complete quadruples.
-On the other hand, we see that 4 out of
-34 (11.7\%) were not tested at all.
-In this cases, all the four elements of the
-quadruples are not available ({\sc na}).
-An interesting observation is that 10 out of 34
-(29.41\%) of the authors performed only attacks
-during their tests and did not test their mechanisms
-to see if they produce any false alarms. The corresponding
-quadruples in this case, are the ones that contain {\sc tp} and
-{\sc fn} results but {\sc tn} and {\sc fp} results are not
-available ({\sc na}). This stresses the fact that authors
-maybe more interested into making sure that
-their mechanisms can detect known attacks than seeing how
-they respond under normal conditions.
-In some occasions (where the number of {\sc tp} results
-are not quantified), authors did not mention how many or
-which attacks they performed.
-Also, in some cases, we observe that even if
-the authors report the existence of possible
-false positive and negative results, they have not
-quantified them ({\sc nq}).
-
-Furthermore, we see that 27 out of
-34 mechanisms were tested on real-world applications
-known to be vulnerable. The vulnerabilities
-associated with these applications are enlisted
-in the following providers: the Common Vulnerabilities
-and Exposures ({\sc cve})
-database,\footnote{\url{https://cve.mitre.org/}}
-the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
-security mailing list, the
-{\sc xss}ed.com\footnote{\url{www.xssed.com}}
+Table~\ref{tab:comp} indicates that the authors of 3 out of 34 (8.8\%)
+publications provided complete quadruples of {\sc tp}, {\sc tn}, 
+{\sc fp}, and {\sc fn}. On the other hand, we
+see that 4 out of 34 (11.7\%) were not tested at all. In these cases,
+all the four elements of the quadruples are not available ({\sc na}).
+An interesting observation is that in 10 out of the 34 (29.41\%)
+publications, the authors performed only attacks during their tests
+and did not test their mechanisms to see if they produce any false
+alarms. The corresponding quadruples contain {\sc tp} and {\sc fn}
+results but {\sc tn} and {\sc fp} results are not available ({\sc
+  na}). This stresses the fact that authors may be more interested in
+making sure that their mechanisms can detect known attacks rather than
+seeing how they respond under normal conditions. In some occasions,
+where the number of {\sc tp} results are not quantified, authors did
+not mention how many or which attacks they performed. Moreover in some
+cases we observe that even if the authors report the existence of
+possible false positive and negative results, they have not quantified
+them ({\sc nq}).
+
+Regarding the subjects of tests, we see that 27 out of 34 mechanisms
+were tested on real-world applications known to be vulnerable. The
+vulnerabilities associated with these applications are enlisted in the
+following providers: the Common Vulnerabilities and Exposures ({\sc
+  cve}) database,\footnote{\url{https://cve.mitre.org/}} the {\it
+  Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}} security
+mailing list, the {\sc xss}ed.com\footnote{\url{www.xssed.com}}
 security bulletin provider, Microsoft's security
 bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
-and the ha.ckers.org\footnote{\url{www.xssed.com}}
-security bulletin provider. Figure~\ref{fig:defect_sources}
-presents how many (in terms of percentages) and which
-(in the figure's caption) authors referred to which source.
-In numerous occassions authors performed tests based
-on the same applications. For example, 12 mechanisms
-were tested on a vulnerable version of
-{\sc phpbb}.\footnote{https://www.phpbb.com/}
+and the ha.ckers.org\footnote{\url{www.xssed.com}} security bulletin
+provider. Figure~\ref{fig:defect_sources} presents how many, in percentage,
+and which, in the figure's caption, authors referred
+to which source. In numerous occassions authors performed tests based
+on the same applications. For example, 12 mechanisms were tested on a
+vulnerable version of {\sc phpbb}.\footnote{https://www.phpbb.com/}
 
@@
 Table~\ref{tab:avail} presents our findings regarding the availability
-of the mechanism in terms of source code and corresponding
+of each mechanism in terms of source code and corresponding
 executables. We also examined the availability of the testbeds
-mentioned in the paper. The check mark (\tick) indicates that at some
-point in the publication there is a homepage where the reader can
-refer to, to download the corresponding software. {\bf AO} (Available
-On-line) suggests that the software is available on-line but the
-address was not mentioned in the paper, which probably indicates that
-the authors made it available after the publication. The question mark
-({\bf ?}), indicates that a homepage for the software was given in the
-publication but now it is not available.
-
-We see that only 6 out of 34 (17.6\%) of the authors provided a
-homepage for their mechanism through their publication and 2 from
-these 6 homepages are currently not available. In 5 cases authors made
-either the source code or their executables available after their
-paper got published. Regarding the availability of test materials, we
-see that only 3 out of 34 (8.8\%) authors have currently their
-testbeds available on-line.
+mentioned in the paper. We see that only 6 out of 34 (17.6\%) of the
+pubications provided a homepage for their mechanism and 2 from these 6
+homepages are currently not available. In 5 cases authors made either
+the source code or their executables available after their paper got
+published. Regarding the availability of test materials, we see that
+only 3 out of 34 (8.8\%) publications have currently their testbeds
+available on-line.
 
@@
 
-As we observed in Subsection~\ref{sec:deployment},
-there are various reasons why a mechanism could
-be difficult to deploy.
-
-Consider the majority of mechanisms coming from
-the policy enforcement subcategory. In most cases
-developers should modify multiple components
-to use each mechanism. Specifically, mechanisms like
-BrowserShield, and {\sc beep} require modifications
-both on the server and the client side.
-Thus, it would be difficult for them to be adopted by
-both browser vendors and application developers.
-On the other hand, there are cases where the policies
-introduced in the server are enforced on the client-side,
-via a library embedded in the server's response
-(i.e. Blueprint). Such an approach is really convenient
+Mechanisms in different categories face different deployment issues.
+
+Consider the majority of mechanisms coming from the policy enforcement
+subcategory. In most cases developers should modify multiple
+components to use each mechanism. Specifically, mechanisms like
+BrowserShield and {\sc beep} require modifications both on the server
+and the client side. Thus, it would be difficult for them to be
+adopted by both browser vendors and application developers. On the
+other hand, there are cases where the policies introduced in the
+server are enforced on the client-side, via a library embedded in the
+server's response (i.e., Blueprint). Such an approach is convenient
 since no modifications are needed on the client.
@@
 
-While describing the various mechanisms in
-Section~\ref{sec:defs}, we observed that some
-can be bypassed by attackers that know how they
-work.
-
-However, some mechanisms are designed in such a way
-so that they can be extended and become immune to
-the attacks that they are currently vulnerable to. For
-example, policy enforcement frameworks that are
-based on JavaScript or {\sc html} rewriting
-can be extended to detect attacks that leverage
-{\tt iframe} tags (see Subsubsection~\ref{sec:policy}).
-
-This does not apply to all mechanisms though.
-In particular, training mechanisms like {\sc didafit},
-and {\sc xss-guard} must be redesigned
-to detect the attacks that were described in
-Subsubsection~\ref{sec:train} and
-Subsection~\ref{sec:hybrid} respectively.
+While describing the various mechanisms in Section~\ref{sec:defs}, we
+observed that some can be bypassed by attackers that know how they
+work. Still, some mechanisms are designed in such a way so that they
+can be extended and become immune to the attacks that they are
+currently vulnerable to. For example, policy enforcement frameworks
+that are based on JavaScript or {\sc html} rewriting can be extended
+to detect attacks that leverage {\tt iframe} tags. This does not apply
+to all mechanisms though. In particular, training mechanisms like {\sc
+  didafit} and {\sc xss-guard} must be redesigned to detect the
+attacks we described in the related sections.
 
@@
 
-Another interesting finding involves the computational overhead. We
-observe that the average overhead that can be extracted from the
-publications that provide the overhead in percentage terms is 18\%.
-Relative research on protection mechanisms~\cite{SPWS13} indicates
-that mechanisms that introduce an overhead larger than 10\% do not
-tend to gain wide adoption in production environments. Hence, the
+Computational overhead comes up as a non-trivial issue. We observe
+that the average overhead that can be extracted from the publications
+that provide the overhead in percentage terms is 18\%. Relative
+research on protection mechanisms~\cite{SPWS13} indicates that
+mechanisms that introduce an overhead larger than 10\% do not tend to
+gain wide adoption in production environments. Hence, the
 computational overhead of some mechanisms could be a reason why they
@@
 
-We need to mention that the fact that mechanisms come
-sometimes with deployment difficulties does
-not necessarily mean that this is a serious reason
-not to adopt them. The deployment of such frameworks
-is most of the time complex because as we observed
-in Section~\ref{sec:attacks} the attacks that they
-detect are complex too. So every security feature can
-come with such a trade-off and those who intend to use it
-should be aware of this.
-
-Deployment can also depend on the detection point
-of an attack. We saw that many policy enforcement
-mechanisms that detect attacks at Point {\sc ub},
-are not easy to deploy because modifications
-are needed both on the server and the client side.
-We observed though that Blueprint has not such
-deployment issues (see Subsection~\ref{sec:deploy2}).
-Thus, when developing a new countermeasure,
-researchers should consider where they are planning
-to detect attacks, observe the corresponding
-deployment challenges, and try to mitigate them.
+We need to mention that the fact that mechanisms come sometimes with
+deployment difficulties does not necessarily mean that this is a
+serious reason not to adopt them. The deployment of such frameworks is
+most of the time complex because as we observed in
+Section~\ref{sec:attacks} the attacks that they detect are complex
+too. So every security feature can come with such a trade-off and
+those who intend to use it should be aware of this.
+
+Deployment can also depend on the detection point of an attack. We saw
+that many policy enforcement mechanisms that detect attacks at Point
+{\sc ub}, are not easy to deploy because modifications are needed both
+on the server and the client side. We observed though that Blueprint
+has not such deployment issues (see Subsection~\ref{sec:deploy2}).
+Thus, when developing a new countermeasure, researchers should
+consider where they are planning to detect attacks, observe the
+corresponding deployment challenges, and try to mitigate them.
 

### 2014-11-12 docs/questioning.tex

@@
 to detect {\sc dsl} code injection attacks. In addition, it is
-actually the first, and so far the only framework that detects No{\sc
-  sql} injection attacks. When an application computes an output
+actually the first, and so far the only framework that detects {\sc
+  json} injection attacks. When an application computes an output
 string (query), Diglossia computes a ``shadow" of this string.

### 2014-11-12 docs/questioning.tex
pass in abstract

@@
 
-  Some of the most dangerous web application attacks, like Cross-Site
-  Scripting and {\sc sql} injection, exploit the oversight of
-  programmers that develop applications that may accept and process
-  data of uncertain origin without appropriate validation and / or
-  filtering. Such attacks, relying on source code injection
-  vulnerabilities, have been constantly topping the lists of the
+  Some of the most dangerous web application attacks, such as Cross-Site
+  Scripting and SQL injection, exploit vulnerabilities
+  in web applications that may accept and process
+  data of uncertain origin without proper validation or
+  filtering, allowing the injection and execution of
+  dynamic or domain-specific language code.
+  These attacks have been constantly topping the lists of
   various security bulletin providers despite the numerous
@@
 
-  In this paper we systematize the existing knowledge regarding
-  various defense mechanisms against source code injection by setting
-  up a model that highlights the key weaknesses behind such attacks
+  In this paper, we systematize the existing knowledge on
+  various defense mechanisms against source code injection attacks by proposing
+  a model that highlights the key weaknesses that enable these attacks,
   and provides a common perspective for the different defenses.
-
   We then categorize and analyze the various defense mechanisms that
-  have been developed. Our analysis is based on accuracy, performance,
-  deployment, security and availability. Especially notable is
-  accuracy, as our findings show that there are many defense
-  mechanisms that are tested in a poor manner. In addition, we observe
-  that there are mechanisms that can be bypassed by attackers that
-  know how the mechanisms work.
-
+  have been developed, based on their accuracy, performance,
+  deployment, security, and availability properties.
+  Accuracy is of particular importance, as our findings show that many defense
+  mechanisms have been tested in a poor manner. In addition, we observe
+  that some mechanisms can be bypassed by attackers with knowledge
+  of how the mechanisms work.
   By comparing the existing defenses and identifying their common
   characteristics, we help researchers and practitioners to choose or
-  modify a mechanism according to their needs as well as designers of
-  new approaches in developing more efficient mechanisms.
+  modify defenses according to their needs, as well as designers of
+  new approaches in developing more effective mechanisms.
 

### 2014-11-12 docs/questioning.tex
work on the conclusions

@@
 
-In this paper we first introduced an exploitation model
-that can be a reference point which can be used by
-researchers who wish to develop new countermeasures.
+In our research we tried to identify some of the reasons
+why this is the case. Some of these reasons include
+poor testing, high overhead, code unavailability,
+deployment and security issues. However, our
+systematization suggests that there are many
+promising cases. For instance there are
+many mechanisms that seem to have been extensively
+tested in terms of accuracy ({\sc sqlc}eck, {\sc amnesia},
+{\sc dsi}, libAnomaly), solve specific
+problems in an efficient way (Blueprint and the system
+by Stock et al.) or have a low computational overhead
+({\sc dsi} and the system by Phung et al.).
+There are also cases that researchers have made their
+code available ({\sc beep} and {\sc sd}river) which
+can be a push towards the development of better mechanisms.
+Apart from making the source code of such mechanisms
+available, we also believe that testing them in
+a production setting could propel their adoption.
+
+% First, we introduced an exploitation model
+% to show how defense mechanisms can be seen
+% from a common point of view. Our model can
+% be a reference point for researchers who wish to develop
+% new countermeasures. Then we categorized the various
+% mechanisms and analyzed them based on specific criteria.
+% We observed that the various mechanisms
 
@@
 
-\begin{itemize}
-\item We believe that our research may facilitate researchers
-or practitioners who would like to use one of the
-aforementioned mechanisms and researchers who would like
-to build new ones. Especially in the second case,
-researchers can utilize our exploitation model as a
-starting point to develop their approach.
-\item We believe that forming a
-standard way to test such mechanisms in terms
-of accuracy and computational performance
-would be one of the reasons of adopting them.
-\end{itemize}
+% \begin{itemize}
+% \item We believe that our research may facilitate researchers
+% or practitioners who would like to use one of the
+% aforementioned mechanisms and researchers who would like
+% to build new ones. Especially in the second case,
+% researchers can utilize our exploitation model as a
+% starting point to develop their approach.
+% \item We believe that forming a
+% standard way to test such mechanisms in terms
+% of accuracy and computational performance
+% would be one of the reasons of adopting them.
+% \end{itemize}
 

### 2014-11-13 docs/questioning.tex
conclusions draft ready

@@
 
-\author{
-\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
-Panos Louridas,\IEEEauthorrefmark{2}
-Michalis Polychronakis,\IEEEauthorrefmark{1}
-and Angelos D. Keromytis\IEEEauthorrefmark{1}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}
-Network Security Lab\\
-Department of Computer Scinence\\
-Columbia University\\
-\{dimitro, mikepo, angelos\}@cs.columbia.edu\\
-\IEEEauthorrefmark{2}
-Software Engineering and Security Lab\\
-Department of Management Science and Technology\\
-Athens University of Economics and Business\\
-louridas@aueb.gr
-}}
+% \author{
+% \IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
+% Panos Louridas,\IEEEauthorrefmark{2}
+% Michalis Polychronakis,\IEEEauthorrefmark{1}
+% and Angelos D. Keromytis\IEEEauthorrefmark{1}}
+% \IEEEauthorblockA{\IEEEauthorrefmark{1}
+% Network Security Lab\\
+% Department of Computer Scinence\\
+% Columbia University\\
+% \{dimitro, mikepo, angelos\}@cs.columbia.edu\\
+% \IEEEauthorrefmark{2}
+% Software Engineering and Security Lab\\
+% Department of Management Science and Technology\\
+% Athens University of Economics and Business\\
+% louridas@aueb.gr
+% }}
+
+\author{Anonymous Submission}
 
@@
 detect one or more of such attacks. However,
-% even if
-% some of them share characteristics with supported frameworks
-% like Mozilla's Content Security
-% Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
-% ({\sc csp}) and Google
-% Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06},
+even if some of them share characteristics
+(for instance, {\sc html} sanitization and {\tt eval} handling)
+with supported frameworks like Mozilla's Content Security
+Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
+({\sc csp}) and Google
+Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06}
 the majority of them are not used in practice.
@@
 promising cases. For instance there are
-many mechanisms that seem to have been extensively
-tested in terms of accuracy ({\sc sqlc}eck, {\sc amnesia},
+mechanisms that have been extensively
+tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
 {\sc dsi}, libAnomaly), solve specific
@@
 code available ({\sc beep} and {\sc sd}river) which
-can be a push towards the development of better mechanisms.
-Apart from making the source code of such mechanisms
-available, we also believe that testing them in
-a production setting could propel their adoption.
+can be a push towards the development of better
+mechanisms. This argument has been raised
+by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
+We believe that testing defenses in
+a production setting could also propel their adoption.
+
+We hope that the exploitation model, analysis
+and observations that emerged from our research
+can be a reference point for researcher who
+wish to develop new countermeasures that
+detect web application attacks.
 

### 2014-11-13 docs/questioning.tex
added an observation concerning Security
some fixes in the Conclusions section

@@
 
+An interesting observation is that mimicry attacks can be
+used to bypass mechanisms coming from the hybrid category and
+the policy enforcement and training subcategories.
+
 \subsection{Point of Detection}
@@
 Attackers seem to find new ways to introduce
-source code to applications by using a variety of
-languages and techniques~\cite{HNSHS12,DKH14}.
+malicious source code to applications by using a
+variety of languages and techniques~\cite{HNSHS12,DKH14}.
 Meanwhile, during the last decade, there are
@@
 ({\sc dsi} and the system by Phung et al.).
-There are also cases that researchers have made their
+There are also cases where researchers have made their
 code available ({\sc beep} and {\sc sd}river) which
@@
 by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
-We believe that testing defenses in
+Finally, we believe that testing defenses in
 a production setting could also propel their adoption.

### 2014-11-13 docs/questioning.tex
a reference from Software Engineering correlating testing with better design
editing conclusions

@@
 observed that some can be bypassed by attackers that know how they
-work. Still, some mechanisms are designed in such a way so that they
+work. Still, some mechanisms are designed in such a way that they
 can be extended and become immune to the attacks that they are
@@
 
-An interesting observation is that mimicry attacks can be
-used to bypass mechanisms coming from the hybrid category and
-the policy enforcement and training subcategories.
+Taking the attackers' point of view, mimicry attacks can affect a
+range of different mechanisms: they can be used to bypass mechanisms
+in the hybrid category, as well as the policy enforcement and training
+subcategories.
 
@@
 
-We need to mention that the fact that mechanisms come sometimes with
-deployment difficulties does not necessarily mean that this is a
-serious reason not to adopt them. The deployment of such frameworks is
-most of the time complex because as we observed in
-Section~\ref{sec:attacks} the attacks that they detect are complex
-too. So every security feature can come with such a trade-off and
-those who intend to use it should be aware of this.
-
-Deployment can also depend on the detection point of an attack. We saw
-that many policy enforcement mechanisms that detect attacks at Point
-{\sc ub}, are not easy to deploy because modifications are needed both
-on the server and the client side. We observed though that Blueprint
-has not such deployment issues (see Subsection~\ref{sec:deploy2}).
-Thus, when developing a new countermeasure, researchers should
-consider where they are planning to detect attacks, observe the
-corresponding deployment challenges, and try to mitigate them.
+The deployment difficulties we have found with many mechanisms are not
+a reason not to adopt them, but they may hinder their widespread use.
+Since source code injection attacks are complex, it may be logical to
+expect that mechanisms to detect them would be complex too. The effort
+to install and use a tool should be weighed against the expected
+benefits. That is one more reason why it is important to report tool
+accuracy, as this provides an immediate indicator to the expected
+benefits.
+
+The issue is more acute when the point of detection is at the client.
+We saw that many policy enforcement mechanisms that detect attacks at
+Point {\sc ub} are not easy to deploy because modifications are needed
+both on the server and the client side. It is unrealistic to expect
+the average web user to go through complicated installation and
+configuration procedures. Conversely, it may be possible to deliver
+the tools to the user unobtrusively; for example, we saw that
+Blueprint enforces policies on the client side by embedding a library
+in the server's response to the client. In general, when developing a
+new countermeasure, researchers should consider where they are
+planning to detect attacks, observe the corresponding deployment
+challenges, and try to mitigate them.
 
@@
 
-In our research we tried to identify some of the reasons
-why this is the case. Some of these reasons include
-poor testing, high overhead, code unavailability,
-deployment and security issues. However, our
-systematization suggests that there are many
-promising cases. For instance there are
-mechanisms that have been extensively
-tested in terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
-{\sc dsi}, libAnomaly), solve specific
-problems in an efficient way (Blueprint and the system
-by Stock et al.) or have a low computational overhead
-({\sc dsi} and the system by Phung et al.).
-There are also cases where researchers have made their
-code available ({\sc beep} and {\sc sd}river) which
-can be a push towards the development of better
-mechanisms. This argument has been raised
-by another {\sc s}o{\sc k} paper too~\cite{SPWS13}.
-Finally, we believe that testing defenses in
-a production setting could also propel their adoption.
-
-We hope that the exploitation model, analysis
-and observations that emerged from our research
-can be a reference point for researcher who
-wish to develop new countermeasures that
-detect web application attacks.
+In order for a security tool to be used in practice it must provide
+some value to the user. In particular, the value should outweigh the
+cost of its use. The cost need not be directly monetary, but may be
+incurred from the time required to use the tool, any inconvenience
+caused, false alarms that it may raise. These costs are related to the
+issues we have been investigating here: poor testing, high overhead,
+unavailabilty of source, deployment difficulties, security issues.
+
+Enhancing any of these would not just increase the value of a piece of
+research as a practical tool, it would increase its research value as
+well. Accurate detection reporting would help in appraising different
+approaches. Performance measurements can point to blind, unpractical,
+alleys and focus effort elsewhere. Availability of source code
+enhances basic scientific tasks like checking and replication. Ease of
+deployment brings ease of experimentation. Secure methods can form the
+basis for developing methods with more extensive coverage.
+
+We saw that there are mechanisms that have been extensively tested in
+terms of accuracy ({\sc sqlc}heck, {\sc amnesia}, {\sc dsi},
+libAnomaly), solve specific problems in an efficient way (Blueprint
+and the system by Stock et al.) or have a low computational overhead
+({\sc dsi} and the system by Phung et al.). There are also cases where
+researchers have made their code available ({\sc beep} and {\sc
+  sd}river) which can be a push towards the development of better
+mechanisms. This argument has been raised by another {\sc s}o{\sc k}
+paper~\cite{SPWS13}. Furthermore, testing defenses in a production
+setting could also propel their adoption.
+
+We hope that the exploitation model, analysis, and observations that
+emerged from our research can be a reference point for researchers who
+wish to develop new countermeasures against web application
+attacks.
 

### 2014-11-13 docs/questioning.tex
add material on confidence intervals

@@
 where a user enters input to interact with the application's data,
-thereby interacting with the underlying Relational Database Management
-System ({\sc rdbms}). This input can become part of an {\sc sql} query
-and get executed on the target {\sc rdbms}. A code injection attack that
-exploits the vulnerabilities of these interfaces by taking advantage
-of input validation issues like incorrectly passed parameters or
-incorrect type handling is called an {\sc sql} injection
-attack~\cite{CERT02,MS09,HVO06,SW06}. By using similar techniques
-malicious users can perform other exploits based on {\sc dsl}s
-like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc xml}~\cite{MSM13}
-and {\sc json}~\cite{SMS13}. With this kind of attacks,
-a malicious user can view sensitive information,
-destroy or modify protected data, or even crash the entire
-application. {\sc html} is another {\sc dsl} that can be used
-for malicious purposes when an application does not properly
-handle user supplied data. Based on this vulnerability
-an attacker can supply valid {\sc html},
-typically via a parameter value, and inject their own
-content into the page. {\sc html} injection is mainly associated
-with {\sc xss} defects~\cite{HNSHS12}.
+thereby interacting with the underlying database. This input can
+become part of an {\sc sql} query and get executed on the target
+database. A code injection attack that exploits the vulnerabilities of
+these interfaces by taking advantage of input validation issues like
+incorrectly passed parameters or incorrect type handling is called an
+{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}. By using
+similar techniques malicious users can perform other exploits based on
+{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
+  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
+attacks, a malicious user can view sensitive information, destroy or
+modify protected data, or even crash the entire application. {\sc
+  html} is another {\sc dsl} that can be used for malicious purposes
+when an application does not properly handle user supplied data. Based
+on this vulnerability an attacker can supply valid {\sc html},
+typically via a parameter value, and inject their own content into the
+page. {\sc html} injection is mainly associated with {\sc xss}
+defects~\cite{HNSHS12}.
 
@@
 
+Even when some numbers are given, they may not be adequate.
+Sensitivity and specificity are statistical measures, and as such
+should be interpreted with suitable confidence intervals. There are
+various methods to calculate confidence intervals, even dispensing
+with the need to have large samples in order to be able to use the
+central limit theorem~\cite{agresti1998,brown2001}. However, sample sizes in the single
+digits are not enough to produce good intervals.
+
 Regarding the subjects of tests, we see that 27 out of 34 mechanisms
@@
 subcategory. It is possible that more tests during development would
-have led the authors to wider improvements in design. 
-%% PL: Do we have a reference in Software Engineering correlating
-%% testing with better design?
+have led the authors to wider improvements in design~\cite{Van14}.
 
@@
 issues we have been investigating here: poor testing, high overhead,
-unavailabilty of source, deployment difficulties, security issues.
+unavailabilty of source, deployment difficulties, compromised security.
 

### 2014-11-13 docs/questioning.tex
minor changes

@@
 
-\title{SoK: The Evolution of Defenses Against Web Application Attacks}
+\title{SoK: Defenses Against Web Application Attacks: From Research
+  Approaches to Practical Tools}
 
@@
   deployment, security, and availability properties.
-  Accuracy is of particular importance, as our findings show that many defense
-  mechanisms have been tested in a poor manner. In addition, we observe
-  that some mechanisms can be bypassed by attackers with knowledge
-  of how the mechanisms work.
-  By comparing the existing defenses and identifying their common
-  characteristics, we help researchers and practitioners to choose or
-  modify defenses according to their needs, as well as designers of
-  new approaches in developing more effective mechanisms.
+  We discuss the results of our analysis, with emphasis on factors
+  that may hinder the widespread adoption of attack detection
+  mechanisms in practice.
 
@@
   criteria that are important for building protection mechanisms.
-\item We find that researchers often test the accuracy
-  of their mechanisms poorly. 
-\item We also find that researchers do not often make their mechanisms
-  available to the community, thus no one can either use them,
-  or replicate their experiments.
-\item We discuss how our observations may be the main reasons why the
-  mechanisms are not adopted in practice.
-\item We discuss what are the necessary criteria for new mechanisms
-  and how our work can help researchers to design new countermeasures.
+\item We discuss the issues that arise from our analysis. We put
+  emphasis on factors that may hinder widespread adoption of
+  approaches and the translation of tools from research to practice.
 \end{enumerate}
@@
 emerged from our research can be a reference point for researchers who
-wish to develop new countermeasures against web application
+wish to develop new, practical countermeasures against web application
 attacks.

### 2014-11-13 docs/questioning.tex
minor change
cross - checks and corrections

@@
 extensive survey on binary code injection attacks can be found
-in~\cite{LC03}. Specific advances in exploiting such vulnerabilities
+in reference~\cite{LC03}. Specific advances in exploiting such vulnerabilities
 (i.e. ``heap smashing", ``arc injection" and others) have already
@@
 references:
-Point {\sc ub} (at the user's browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,VFJKKV07,SLMS14,BV08},
-Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08,PS11},
+Point {\sc ub} (at the user's browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
+Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
 Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
@@
 that present corresponding mechanisms:
-{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,LV09},
+{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08},
 {\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
@@
 web page on the server-side and then, on the client-side, the web
-browser decodes the source by applying the same function again (Point
-{\sc ub}). Variations of this approach include {\it
+browser decodes the source by applying the same function again either
+in a proxy at the server-side (Point {\sc s}t{\sc b}) or in the browser
+(Point {\sc ub}). Variations of this approach include {\it
   Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
@@
   \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},46,15)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
   &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
@@
   &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc c}) & {\sc xss} \\ 
+  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc s}) & {\sc xss} \\ 
   &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
@@
   &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (9,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   {\it Diglossia}~\cite{SMS13} & 4 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
   \thickhline
@@
 attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client side: in particular, 14 out of 23
-frameworks (60,8\%) detect {\sc xss} attacks on the
+perform detection on the client side: in particular, 13 out of 23
+frameworks (56,5\%) detect {\sc xss} attacks on the
 client's side. Note that the majority of the mechanisms that detect
 such attacks on the server-side can also detect {\sc dsl} code
-injection attacks (6 out of 9).
+injection attacks (6 out of 10).
 
@@
 Point {\sc ub} are not easy to deploy because modifications are needed
-both on the server and the client side. It is unrealistic to expect
-the average web user to go through complicated installation and
-configuration procedures. Conversely, it may be possible to deliver
+both on the server and the client side.
+Conversely, it may be possible to deliver
 the tools to the user unobtrusively; for example, we saw that
@@
 We saw that there are mechanisms that have been extensively tested in
-terms of accuracy ({\sc sqlc}heck, {\sc amnesia}, {\sc dsi},
+terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
 libAnomaly), solve specific problems in an efficient way (Blueprint

### 2014-11-13 docs/questioning.tex
more corrections

@@
   &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & $\sim$7ms ({\sc c}) & {\sc xss} \\
+  &   {\it WebJail}~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
@@
   &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   {\it Noncespaces}~\cite{GC09} & 109 & ({\sc nq},{\sc na},{\sc na},0)\_r &  10.3\% ({\sc s}) & {\sc xss} \\ 
+  &   {\it Noncespaces}~\cite{GC09} & 109 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
   &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
@@
 so it is not possible to move from absolute
-time measurements to percentage overheads. In 10 cases (29,4\%), the
+time measurements to percentage overheads. In 10 cases (29.4\%), the
 overhead was either not available ({\sc na}) or not quantified ({\sc
@@
 that the average overhead that can be extracted from the publications
-that provide the overhead in percentage terms is 18\%. Relative
+that provide the overhead in percentage terms is 17.45\%. Relative
 research on protection mechanisms~\cite{SPWS13} indicates that

### 2014-11-13 docs/questioning.tex
changed title
pass in intro

@@
 authentication and session management, or other issues. Some of the
-most dangerous web application attacks are associated with the
-processing of external input data that can contain malicious code, a
-vulnerability known as code injection.
-
-Such attacks include Cross-Site Scripting ({\sc xss})
-attacks~\cite{SG07}, {\sc sql} injection attacks~\cite{RL12b},
-Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, and
-others. Attacks like these have been topping the vulnerability lists
-of numerous bulletin providers like the Open Web Application Security
-Project\footnote{\url{https://www.owasp.org/index.php/Category:OWASP_Top_Ten_Project}}
-({\sc owasp}) and {\sc
-  mitre}\footnote{\url{http://cwe.mitre.org/top25/}} for several
-years. Consider the case of {\sc owasp}'s Top Ten project whose main
-goal is to raise awareness about web application security by
-identifying some of the most critical risks facing organizations. The
-Top Ten project is popular, referenced by numerous researchers. In its
-three consecutive Top Ten lists (2007, 2010, 2013), different source
+most dangerous and prevalent web application attacks, however,
+exploit vulnerabilities associated with improper validation or filtering
+of untrusted inputs, resulting in the injection of malicious
+script or domain-specific language code.
+Attacks of this type include Cross-Site Scripting ({\sc xss})
+attacks~\cite{SG07}, {\sc sql} injection~\cite{RL12b}, and
+Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, among
+others.
+
+For the past several years,
+these attacks have been topping the lists of the most dangerous vulnerabilities
+published by {\sc owasp}~\cite{OWASPtop10},
+{\sc mitre}~\cite{MITREtop25}, and other organizations.
+For instance, consider the case of {\sc owasp}'s popular Top Ten
+project~\cite{OWASPtop10},
+which aims to raise awareness about web application security by
+identifying some of the most critical risks organizations may face.
+In its three consecutive Top Ten lists (2007, 2010, 2013), different source
 code-driven injection attacks dominate the top five positions.
-Malicious users find new ways~\cite{HNSHS12,DKH14} to bypass defense
-mechanisms by using a variety of techniques despite the numerous
-countermeasures that are being introduced. The number of systems
-developed to counter {\sc sql} injection attacks until 2006 was more
-than twenty~\cite{HVO06}. Since then the number has doubled.
-Researchers have indicated that the number of such attacks is steadily
+At the same time,
+attackers find new ways~\cite{HNSHS12,DKH14} to bypass defense
+mechanisms using a variety of techniques, despite the numerous
+countermeasures that are being introduced. As an example, already by 2006,
+there were more than 20 proposed defenses
+against {\sc sql} injection attacks~\cite{HVO06}.
+Since then, the number has doubled, while researchers have indicated that
+the number of {\sc sql} injection attacks has been steadily
 increasing in recent years~\cite{SSL12}.
 
-In this paper we show how the above attacks can be seen from a {\it
-  common perspective}. We achieve this by providing an exploitation
-model that highlights that the majority of the steps needed to perform
-application attacks based on source code injection are
-common.\footnote{Note that we leave out attacks that are based on
-  binary code injection (i.e. buffer overflows --- see
-  Section~\ref{sec:attacks}).} This is validated by the fact that
-there are protection mechanisms that can detect more than one of these
-attacks. Then, we {\it categorize} a selection of these protection
-mechanisms. In the selection we included protection mechanisms that
-detect such attacks and are presented in publications cited more than
-twenty times. We also added some recent mechanisms that have been
+In this paper, we explore how different attacks associated with 
+the exploitation of untrusted input validation errors can be modeled 
+under a {\it common perspective}. To that end, we propose an exploitation
+model which highlights that most of the steps needed to mount
+different types of source code injection attacks are
+common.\footnote{Note that we do not consider lower-level attacks based on
+the exploitation of memory corruption vulnerabilities and the injection
+of binary code---see Section~\ref{sec:attacks}.} This is validated by the fact that
+there are protection mechanisms that can defend against more than one of these
+types of attacks. Then, we categorize a selection of these protection
+mechanisms. In our selection we include approaches that
+have been proposed in publications cited more than
+20 times. We also include some recent mechanisms that have been
 presented in top security conferences, even though they have been
-cited less than twenty times. We included the second group so that we
-would not penalize recent research. Finally, we {\it analyze} each
-mechanism based on the following dimensions:
+cited less than twenty times, so that recent research is not penalized.
+Finally, we analyze each
+mechanism across the following dimensions:
 \begin{itemize}
-\item {\it Accuracy} Protection mechanisms are as good
+\item {\it Accuracy:} protection mechanisms are as good
   as their detection capability; this requires low false positive and
   false negative rates.
-\item {\it Availability} We check if the mechanism and its
-  testbed are available on-line.
-\item {\it Computational Performance} We examine the computational
+\item {\it Availability:} whether the mechanism and its
+  testbed are publicly available.
+\item {\it Computational performance:} the computational
   overhead of the mechanisms at their points of deployment.
-\item {\it Ease of use} We examine if the protection
+\item {\it Ease of use:} whether the protection
   mechanism is practical in terms of deployment
   and can be easily adopted by security experts.
-\item {\it Security} We examine how resilient is the system to
-  attackers that know how it works and wants to circumvent it.
-\item {\it Point of Detection} Based on our exploitation model
-  we examine the location where a mechanism detects an attack.
+\item {\it Security:} the robustness of the protection mechanism against
+  attackers with knowledge of its internals who attempt to circumvent it.
+\item {\it Detection Point:} the location where a mechanism detects an attack
+  based on our exploitation model.
 \end{itemize}
@@
 \noindent
-All the aforementioned requirements are considered critical
-when building security mechanisms that protect
+All the above requirements are considered important
+when building security mechanisms for the protection of
 applications~\cite{A01,A00,SPWS13,nature2014}.
-Based on this analysis we can identify the advantages
+Based on this analysis, we identify the advantages
 and disadvantages of the
 various mechanisms and enumerate some of their common
-characteristics. We can also draw useful conclusions
-about the various categories and see how they compare
+characteristics. We also draw useful conclusions
+about the various protection categories and see how they compare
 to each other.
@@
 in general~\cite{SZ12}. The scope of that
-research is pretty wide and leaves out the majority of the
-approaches and mechanisms that we report here.
+research is much broader and leaves out the majority of the
+approaches and mechanisms that we consider in this work.
 This is mainly because that work includes countermeasures
-that detect such vulnerabilities via program analysis
-(which is done during development or testing), while
-we include protection mechanisms that counter
-such attacks when they take place. Static or
-dynamic analyzers that examine applications to
+that identify vulnerabilities using program analysis
+(which takes place during the development or testing phases), while
+we consider protection mechanisms that counter
+web attacks when they take place. Similarly, static or
+dynamic analysis techniques that examine applications to
 identify vulnerabilities that may lead to the attacks
-that we described earlier are out of the scope of this paper.
-Also, countermeasures that prevent {\sc sql}
-injection attacks~\cite{HVO06}, have already been surveyed.
-However, this survey is quite old and since then
-the number of countermeasures that detect {\sc sql}
-injection attacks alone, has been drastically increased
-as we mentioned earlier.
+that we described earlier are out of scope as well.
+While countermeasures against {\sc sql}
+injection attacks have been previously surveyed in a 2006 paper~\cite{HVO06},
+a significant number of new {\sc sql} injection defenses has been proposed since
+then, as we mentioned earlier.
 
@@
 \begin{enumerate}
-\item We provide an exploitation model that puts application attacks
-  based on source code injection under a common
-  perspective.
+\item We provide a unified exploitation model for different types of
+  web application attacks based on source code injection.
 \item We categorize and analyze proposed defenses using a set of
   criteria that are important for building protection mechanisms.
-\item We discuss the issues that arise from our analysis. We put
-  emphasis on factors that may hinder widespread adoption of
-  approaches and the translation of tools from research to practice.
+\item We provide insight based on the issues that arise from our analysis. We put
+  emphasis on factors that may hinder the widespread deployment of
+  protection mechanisms, and the transition of tools from research to practice.
 \end{enumerate}
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec:attacks} provides the exploitation model
-of application attacks based on source code injection.
+Section~\ref{sec:attacks} presents our proposed model
+of web application attacks based on source code injection.
 Section~\ref{sec:dimensions} introduces the dimensions
-on which we base the analysis of the various defenses.
+across which we analyze the various defenses.
 Our categorization and analysis is presented in

### 2014-11-13 docs/questioning.tex
quick consistency pass: em dash is '---' and should never have space before/after i.e. and e.g. always need a comma after punctuation always goes *before* the closing quote mark(s) never use the inch symbol (") for closing double quotes - always use a double tick ('')

@@
 
-\title{SoK: Defenses Against Web Application Attacks: From Research
+\title{SoK: Defending Against Web Application Attacks: From Research
   Approaches to Practical Tools}
@@
   so-called `weird machine' programmable by the attacker via crafted
-  inputs (a.k.a. `exploits')''}. In particular, {\it ``every
+  inputs (a.k.a. `exploits').''} In particular, {\it ``every
   application that copies untrusted input verbatim into an output
-  program is vulnerable to code injection''}. Ray and
+  program is vulnerable to code injection.''} Ray and
 Ligatti~\cite{RL12b} have proved this claim based on formal language
@@
 in reference~\cite{LC03}. Specific advances in exploiting such vulnerabilities
-(i.e. ``heap smashing", ``arc injection" and others) have already
+(i.e., ``heap smashing,'' ``arc injection,'' and others) have already
 been presented~\cite{PB04} and the countermeasures used to detect such
 defects have already been surveyed~\cite{YJP12} (many of them are also
-included in a book:~\cite{DKZ12} -- Section 13.8). In the present work
+included in a book:~\cite{DKZ12}---Section 13.8). In the present work
 we do not include binary code injection, focusing instead on defenses
@@
 \item At the user's browser (Point {\sc ub}).
-\item En route from the server to the user's browser --- in most cases
+\item En route from the server to the user's browser---in most cases
 within a proxy (Point {\sc s}t{\sc b}).
@@
 the request (Point {\sc ub}). Such policies
-can be also provided by the server (i.e. ``never
+can be also provided by the server (i.e., ``never
 follow a link that leads to the malicious.com
-web site"). The main issue with Noxes is that
+web site''). The main issue with Noxes is that
 it does not deal with JavaScript-driven {\sc xss}
@@
 done before the processing of an {\sc http} request. When it finds one
-it adds a token to it. This results to a ``code mask". Then, before
+it adds a token to it. This results to a ``code mask.'' Then, before
 sending the resulting {\sc html} data to the web user, the framework
 searches the data for illegal code by using the same keywords (Point
-{\sc s}t{\sc b}). Since all legitimate code has been ``masked", the injected
+{\sc s}t{\sc b}). Since all legitimate code has been ``masked,'' the injected
 code can be identified. The pre- and post-processing of the code,
@@
 
-A taint tracking scheme marks untrusted (``tainted") data (for
+A taint tracking scheme marks untrusted (``tainted'') data (for
 instance, a variable set by a field in a web form) and traces its flow
@@
 so on. If any of these variables is used in a potentially risky
-command (for example, send the data to a vulnerable ``sink'', such as
+command (for example, send the data to a vulnerable ``sink,'' such as
 a database, a file, the network) the scheme may act accordingly.
@@
 can be retrofitted to a system typically by changing
-some configuration files (i.e. {\sc sd}river). This does not apply
+some configuration files (i.e., {\sc sd}river). This does not apply
 to {\sc amnesia} though, since significant source code
@@
   json} injection attacks. When an application computes an output
-string (query), Diglossia computes a ``shadow" of this string.
+string (query), Diglossia computes a ``shadow'' of this string.
 Specifically, it maps all characters introduced by the application to
@@
 the query that is about to be executed and compares it with the parsed
-tree of the ``shadow" (Point {\sc e}i{\sc q}). If the trees are not
+tree of the ``shadow'' (Point {\sc e}i{\sc q}). If the trees are not
 equal the application is probably under attack. Note that Diglossia

### 2014-11-14 docs/questioning.tex
1) Changed some section titles. 2) Footnotes became refs. 3) Providing examples in the second section.

@@
 code-driven injection attacks dominate the top five positions.
-At the same time,
-attackers find new ways~\cite{HNSHS12,DKH14} to bypass defense
-mechanisms using a variety of techniques, despite the numerous
-countermeasures that are being introduced. As an example, already by 2006,
+
+At the same time, attackers find new ways~\cite{HNSHS12,DKH14}
+to bypass defense mechanisms using a variety of techniques,
+despite the numerous countermeasures that are being introduced.
+As an example, already by 2006,
 there were more than 20 proposed defenses
@@
 there are protection mechanisms that can defend against more than one of these
-types of attacks. Then, we categorize a selection of these protection
-mechanisms. In our selection we include approaches that
-have been proposed in publications cited more than
-20 times. We also include some recent mechanisms that have been
-presented in top security conferences, even though they have been
-cited less than twenty times, so that recent research is not penalized.
-Finally, we analyze each
-mechanism across the following dimensions:
+types of attacks. Then, we {\it categorize} a selection of representative
+protection mechanisms and finally we {\it analyze} each mechanism across the
+following dimensions:
 \begin{itemize}
@@
 The rest of the paper is organized as follows.
-Section~\ref{sec:attacks} presents our proposed model
-of web application attacks based on source code injection.
+Section~\ref{sec:attacks} provides some insights on
+source code injection attacks and
+Section~\ref{sec:model} presents our proposed model.
 Section~\ref{sec:dimensions} introduces the dimensions
@@
 
-\section{Attacks}
+\section{Source Code Injection on Web Applications}
 \label{sec:attacks}
@@
 
-\subsection{Source Code Injection Vulnerabilities}
-
 Figure~\ref{fig:taxonomy} presents a taxonomy of source
@@
 {\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
+For both categories, we provide examples that will be used
+throughout the whole paper.
 
@@
 incorrectly passed parameters or incorrect type handling is called an
-{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}. By using
-similar techniques malicious users can perform other exploits based on
-{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
-  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
+{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}.
+Consider a trivial example that takes advantage of incorrectly
+filtered quotation characters. In an application that
+will send the password for a forgetful user via email by executing the
+following query:
+
+\bgroup \lstset{language=SQL}
+\begin{small}
+\begin{lstlisting}
+SELECT password from userdata WHERE id = 'Alice'
+\end{lstlisting}
+\end{small}
+\egroup
+
+\noindent
+If an attacker, inputs the string {\tt anything' OR 'x'='x}, he or
+she could could obtain the administrator's password by email.
+Savvy programmers could use a language's libraries, like {\sc php}'s
+{\tt mysql\_real\_escape\_string()} to detect malformed input; or they
+could use prepared {\sc sql} statements, instead of statement
+templates. Unfortunately,
+the increasing number of {\sc sql} injection attacks
+suggest that programmers are not always that careful.
+By using similar techniques malicious users can perform other exploits based on
+{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09},
+{\sc xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
 attacks, a malicious user can view sensitive information, destroy or
-modify protected data, or even crash the entire application. {\sc
-  html} is another {\sc dsl} that can be used for malicious purposes
+modify protected data, or even crash the entire application.
+
+{\sc html} is another {\sc dsl} that can be used for malicious purposes
 when an application does not properly handle user supplied data. Based
@@
 page. {\sc html} injection is mainly associated with {\sc xss}
-defects~\cite{HNSHS12}.
+attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
+vehicle for an {\sc csrf} attack in the following manner:
+Consider a vulnerable bulletin board system where {\tt img} tags are not checked.
+A malicious user could embed a {\sc csrf} request within {\tt img}
+tags in the following manner:
+
+\bgroup \lstset{language=HTML}
+\begin{small}
+\begin{lstlisting}
+<img src='http://www.vulnerable.com/
+  admin.php?edituserwithID=13&addgroup=admin'/>
+\end{lstlisting}
+\end{small}
+\egroup
+
+\noindent
+When the page with this injected code is accessed by an administrator,
+the attacker (with {\sc id} 13) will gain administrative privileges
+while the administrator will have no immediate indication that there
+has been an attack.
 
 A recent class of code injection attacks involve dynamic languages
-like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}. JavaScript
-injection attacks, in particular, make up a large subset of dynamic
+like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
+A simple example of a dynamic language-driven attack is an input string
+that is fed into an {\tt eval()} function call, e.g., in {\sc php}:
+
+\bgroup \lstset{language=PHP}
+\begin{small}
+\begin{lstlisting}
+$variable = $_GET['var']; 
+$input = $_GET['value'];
+eval('$variable = ' . $input . ';')
+\end{lstlisting}
+\end{small}
+\egroup
+
+\noindent
+The user may pass into the {\tt value} parameter code that will
+execute in the server. Hence, if an attacker provides as
+input the following string: {\tt 10 ; system(''touch foo'');}
+then a file will be created on the server; it is easy
+to imagine more detrimental instances.
+
+JavaScript injection attacks, make up a large subset of dynamic
 language-driven attacks. Such attacks are manifested when a web
@@
 can manage to inject a script in the JavaScript engine of a browser
-and alter its execution flow~\cite{ELX07}. JavaScript injection
-attacks are considered a critical issue in web application security
-mainly because they are associated with major vulnerabilities such as
-{\sc xss} attacks~\cite{SG07}, {\sc csrf} attacks~\cite{BJM08,LZRL09}
-and Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}. In
-many cases {\sc xss} attacks involve the injection of both {\sc html}
-and JavaScript code.
-
-% {\sc html} injection --- such attacks pose no threat to cookies and session IDs.
-
-\subsection{Exploitation Model}
+and alter its execution flow~\cite{ELX07}. For instance,
+consider a web page (foo.net) that prints the value
+of a query parameter ({\tt query}) from the
+page's {\sc url} in the web page's content
+without escaping the value. A malicious user
+can take advantage of this and inject an {\tt iframe} tag
+into the page to steal the user's cookie and
+send it via an image request to a web site
+that he or she controls (malicious.com).
+This could be achieved by including the following
+link to the malicious web site (or send it via phishing
+email) and induce the user to click on it:
+
+\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
+\begin{lstlisting}
+http://foo.net/vulnerable.html?query=
+<iframe src="javascript:document.body.innerHTML=+
+'<img src=\"http://malicious.com/?c=
+'+encodeURIComponent(document.cookie)+'\">'">
+</iframe>
+\end{lstlisting}
+
+\noindent
+JavaScript injection is considered a critical issue in web application security
+mainly because it is associated with major vulnerabilities such as
+{\sc xss} attacks~\cite{SG07} and Cross-Channel Scripting
+({\sc xcs}) attacks~\cite{W10,BBB09}. In many cases {\sc xss} attacks
+involve the injection of both {\sc html} and JavaScript code.
+
+\section{Exploitation Model}
 \label{sec:model}
@@
 In this section we provide a step-by-step exploitation model to
-understand the process of carrying out application attacks based on
-source code injection vulnerabilities. Figure~\ref{fig:attacks}
+understand the process of carrying out application attacks associated
+with source code injection. Figure~\ref{fig:attacks}
 presents the steps of different application attacks. Links between
-steps are labelled with the paths constituting different attacks. The
+steps are labeled with the paths constituting different attacks. The
 sequence of steps for each attack is shown by the numbers next to the
@@
 a part of a value represented by a program variable. The target of the
-attack determines the route from now on. In {\sc sql} injection and
-{\sc csrf} attacks the injected code becomes part of a query that
+attack determines the route from now on. In an {\sc sql} injection
+attack the injected code becomes part of a query that
 finally reaches the database where it is executed.
@@
 \caption{\label{fig:attacks}Attack model demonstrating web
-application attacks based on source
-code injection vulnerabilities. For every arrow there are
-corresponding transition numbers for
+application attacks based on source code injection.
+For every arrow there are corresponding transition numbers for
 every attack. Every {\it point} indicates a transition where mechanisms
@@
 all computer code and test data is available noting any restrictions
-on accessibility. Availability of computer code has been recognised as
+on accessibility. Availability of computer code has been recognized as
 an important issue outside the computer science field: the journal
@@
 \caption{\label{fig:defenses}The basic categories of countermeasures
-against web application attacks, based on source code
+against web application attacks based on source code
 injection. For each approach we provide the references
@@
 We categorize and describe the various mechanisms developed to detect
-the attacks described in Section~\ref{sec:attacks} on the dimensions
-we proposed apart from availability, which we treat separately in the
-discussion in Section (\ref{sec:discussion}).
+the attacks described in Section~\ref{sec:attacks} and~\ref{sec:model},
+on the dimensions we proposed apart from availability, which we treat
+separately in the discussion in Section (\ref{sec:discussion}).
+All mechanisms have been proposed in publications cited more than
+20 times. We also include some recent mechanisms that have been
+presented in top security conferences, even though they have been
+cited less than twenty times, so that recent research is not penalized.
 
 Figure~\ref{fig:defenses} presents a taxonomy of the
-defenses that protect web applications against attacks based on
-code injection vulnerabilities.
+defenses that protect web applications against
+source code injection attacks based on.
 We can identify three approaches:
@@
 mechanisms.
-% Such attacks share
-% many similarities with the {\it return-to-lib}
-% attack~\cite{SPPGMMB04}. 
-%% PL Explain what it does, I guess it's what you go on to say
-%% directly below?
-% When performing an attack like this the malicious user transfers the
-% execution to points that contain script code which in turn is used to
-% perform the attack.
 
@@
 define policies that restrict the behavior of third-party
-scripts introduced by such features. For instance,
-consider a web page (foo.net) that prints the value
-of a query parameter ({\tt query}) from the
-page's {\sc url} in the web page's content
-without escaping the value. A malicious user
-can take advantage of this and inject an {\tt iframe}
-into the page to steal the user's cookie and
-send it via an image request to a web site
-that he or she controls (malicious.com).
-This could be achieved by including the following
-link to the malicious web site (or send it via phishing
-email) and induce the user to click on it:
-
-\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
-\begin{lstlisting}
-http://foo.net/vulnerable.html?query=
-<iframe src="javascript:document.body.innerHTML=+
-'<img src=\"http://malicious.com/?c=
-'+encodeURIComponent(document.cookie)+'\">'">
-</iframe>
-\end{lstlisting}
-
+scripts introduced by such features. Thus, they would
+be vulnerable in an attack that utilizes {\tt iframes}
+in the way we described in Section~\ref{sec:attacks}.
 \noindent {\it WebJail}~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
@@
 tag transactions with their corresponding call sites. This can lead
-easily to false negatives. For instance, consider an application that
-will send the password for a forgetful user via email by executing the
-following query: \bgroup \lstset{language=SQL}
+easily to false negatives. For instance, the application
+mentioned in Section~\ref{sec:attacks}, which will send the password
+for a forgetful user via email by executing the following query:
+
+\bgroup \lstset{language=SQL}
 \begin{small}
@@
 \egroup
+
 \noindent
@@
 workstation would be as follows:
+
 \bgroup
@@
 \egroup
+
 \noindent
-In this case {\sc didafit} and {\it libAnomaly}, could be easily bypassed
-since a malicious user could obtain the administrator's password
-by email by entering on the password retrieval form
-as his user identifier the following:
-\bgroup
-\lstset{language=SQL}
-\begin{small}
-\begin{lstlisting}
-nosuchuser' OR id = 'admin
-\end{lstlisting}
-\end{small}
-\egroup
-\noindent
-The infected query matches the signature of the second one above and
-is therefore accepted. The problem lies with the call location of the
-query, not the query alone.
+Even if the application's administrators have chosen to use
+either {\sc didafit} or {\it libAnomaly}, an attacker could bypass
+them and obtain the administrator's password via email,
+by entering on the form the standard string:
+{\tt nosuchuser' OR id = 'admin}. The infected query matches the
+signature of the second one above and is therefore accepted.
+The problem lies with the call location of the query, not the query alone.
 
@@
 
-\section{Discussion}
+\section{Observations}
 \label{sec:discussion}
+
+In this section we enumerate key observations
+based on the dimensions we set in Section~\ref{sec:dimensions}.
 
@@
 following providers: the Common Vulnerabilities and Exposures ({\sc
-  cve}) database,\footnote{\url{https://cve.mitre.org/}} the {\it
-  Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}} security
-mailing list, the {\sc xss}ed.com\footnote{\url{www.xssed.com}}
-security bulletin provider, Microsoft's security
-bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
-and the ha.ckers.org\footnote{\url{www.xssed.com}} security bulletin
-provider. Figure~\ref{fig:defect_sources} presents how many, in percentage,
+  cve}) database~\cite{cve}, the {\it Bugtraq} security
+mailing list~\cite{bugtraq}, the {\sc xss}ed.com
+security bulletin provider~\cite{xssed}, Microsoft's security
+bulletin~\cite{microsoftBulletin} and the
+ha.ckers.org security bulletin provider~\cite{hackers}.
+Figure~\ref{fig:defect_sources} presents how many, in percentage,
 and which, in the figure's caption, authors referred
@@
 
-\section{Lessons Learned}
+\section{Recommendations and Lessons Learned}
 \label{sec:lessons-learned}
+
+In this section we provide some lessons learned from
+our observations and provide some recommendations
+that developers of new mechanisms may find helpful.
 
@@
 % of {\sc xss} attack requires a more complex analysis.
+
+\subsection{Improving Accuracy Tests}
 
@@
 
-When we introduced specicifity and sensitivity in
+When we introduced specificity and sensitivity in
 Section~\ref{ssec:diagnostic-performance} we deferred discussion of
@@
 
+\subsection{On Code Availability}
+
 Apart from testing practices, another area that merits improvement is
@@
 specific reasons why authors of attack detection mechanisms seem to be
-wary of releasing online their code and tests. Our finding may reflect
+wary of releasing on-line their code and tests. Our finding may reflect
 the status in the current point in time, when authors are urged to
@@
 
+\subsection{Computational Overhead and Deployment Remarks}
+
 Computational overhead comes up as a non-trivial issue. We observe
@@
 challenges, and try to mitigate them.
-
-% discuss Availability. Finally,
 
@@
 with supported frameworks like Mozilla's Content Security
-Policy\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}
-({\sc csp}) and Google
-Caja\footnote{\url{https://code.google.com/p/google-caja/}}~\cite{M06}
+Policy~\cite{cspMoz} ({\sc csp}) and Google Caja~\cite{M06,caja}
 the majority of them are not used in practice.

### 2014-11-14 docs/questioning.tex
changes in the exploitation model

@@
 \begin{IEEEkeywords}
-Security and Protection, Application Security, Code injection Attacks,
+Security and Protection, Web Application Security, Code injection Attacks,
 Testing, Cross-Site Scripting.
@@
 like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
-A simple example of a dynamic language-driven attack is an input string
+A simple example of a {\sc php} injection attack is an input string
 that is fed into an {\tt eval()} function call, e.g., in {\sc php}:
@@
 without appropriate validation. An attacker could upload data
-containing a specially crafted script (for example, in a blog comment)
-to steal the cookies of the visiting users or embed malicious {\sc
-  sql} code to retrieve all the password entries from a database. Note that
-an {\sc xss} attack can start from both routes.
+containing a specially crafted script
+to steal the cookies of the visiting users or embed malicious
+{\sc sql} code to retrieve all the password entries from a database.
+Recall the examples we provided in Section~\ref{sec:attacks}.
+Note that an {\sc xss} attack can start from both routes.
 
@@
 finally reaches the database where it is executed.
+In the case of a {\sc csrf} attack the functionality dictated by
+the malicious response is performed.
 
@@
 
-Application attack defense mechanisms
+Web application attack defense mechanisms
 must demonstrate the presence of an attack. This, however, does not
@@
 tag transactions with their corresponding call sites. This can lead
-easily to false negatives. For instance, the application
+easily to false negatives. For instance, recall the application
 mentioned in Section~\ref{sec:attacks}, which will send the password
@@
 Even if the application's administrators have chosen to use
-either {\sc didafit} or {\it libAnomaly}, an attacker could bypass
-them and obtain the administrator's password via email,
+either {\sc didafit} or {\it libAnomaly} as protection,
+an attacker could bypass them and obtain the
+administrator's password via email,
 by entering on the form the standard string:

### 2014-11-14 docs/questioning.tex
pass in II

@@
 
-\section{Introduction Remarks}
+\section{Introduction}
 
@@
 
-\section{Source Code Injection on Web Applications}
+\section{Source Code Injection Attacks\\in Web Applications}
 \label{sec:attacks}
 
-The basic problem behind the most dangerous
+The main vulnerability behind the most dangerous
 web application attacks involves
@@
 this, attackers can inject their code into
-applications to perform malicious tasks. Such
-an exploit can have different forms depending on the
+applications to perform malicious tasks. Exploits
+of this kind can have different forms depending on the
 execution context of the application and the location
@@
 
-Bratus et al.~\cite{BLSPS11} portray the issue in a generic fashion:
+Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
 {\it ``unexpected (and unexpectedly powerful) computational models
@@
 \leavevmode
-\includegraphics[scale=0.47]{attack-tree-uml.pdf}
+\includegraphics[width=\columnwidth]{attack-tree-uml.pdf}
 \end{center}
-\caption{\label{fig:taxonomy}A taxonomy of source
-code injection attacks.}
+\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
+language code injection attacks against web applications.}
 \end{figure}
@@
 Code injection attacks can be divided into two categories. The first
-involves binary code and the second source code. An
-extensive survey on binary code injection attacks can be found
-in reference~\cite{LC03}. Specific advances in exploiting such vulnerabilities
-(i.e., ``heap smashing,'' ``arc injection,'' and others) have already
-been presented~\cite{PB04} and the countermeasures used to detect such
-defects have already been surveyed~\cite{YJP12} (many of them are also
-included in a book:~\cite{DKZ12}---Section 13.8). In the present work
-we do not include binary code injection, focusing instead on defenses
-that protect applications against attacks based on the
-source code injection category.
+involves binary code and the second higher-level language code. An
+extensive survey on binary code injection attacks was conducted by
+Lhee and Chapin~\cite{LC03}. Advances in memory corruption vulnerability
+exploitation have been studied extensively~\cite{PB04, SPWS13}
+and countermeasures to such attacks
+have already been surveyed~\cite{YJP12}\cite[Sec. 13.8]{DKZ12}.
+In this work
+we do not consider binary code injection, focusing instead on defenses
+that protect web applications against attacks based on the
+injection of higher level language code.
 
 Figure~\ref{fig:taxonomy} presents a taxonomy of source
-code injection attacks. Such attacks may involve source code, either of a
+code injection attacks against web applications.
+Such attacks may involve high-level language code, written in either a
 {\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
-For both categories, we provide examples that will be used
-throughout the whole paper.
-
-Application attacks that involve {\sc dsl}s constitute an important
-subset of the code injection problem, as {\sc dsl}s like {\sc sql} and
+In the following, we briefly discuss examples from both categories
+that will be used throughout the paper.
+
+Injection attacks that involve {\sc dsl}s constitute an important
+subset of the code injection problem, as {\sc dsl}s such as {\sc sql} and
 {\sc xml} play an significant role in the development of both web and
 mobile applications. For example, many applications have interfaces
-where a user enters input to interact with the application's data,
+through which a user enters input to interact with the application,
 thereby interacting with the underlying database. This input can
 become part of an {\sc sql} query and get executed on the target
-database. A code injection attack that exploits the vulnerabilities of
-these interfaces by taking advantage of input validation issues like
-incorrectly passed parameters or incorrect type handling is called an
-{\sc sql} injection attack~\cite{CERT02,MS09,HVO06,SW06}.
+database. Code injection attacks that exploit vulnerabilities in database
+interfaces by taking advantage of input validation issues, such as
+incorrectly passed parameters or incorrect type handling, are called
+{\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
 Consider a trivial example that takes advantage of incorrectly
-filtered quotation characters. In an application that
-will send the password for a forgetful user via email by executing the
+filtered quotation characters in an application that
+sends a temporary password for a forgetful user via email by executing the
 following query:
@@
 \noindent
-If an attacker, inputs the string {\tt anything' OR 'x'='x}, he or
-she could could obtain the administrator's password by email.
-Savvy programmers could use a language's libraries, like {\sc php}'s
-{\tt mysql\_real\_escape\_string()} to detect malformed input; or they
-could use prepared {\sc sql} statements, instead of statement
+Attackers that would input the string {\tt anything' OR 'x'='x},
+could obtain the administrator's password by email.
+Savvy programmers can use certain API functions, such as {\sc php}'s
+{\tt mysql\_real\_escape\_string()} to detect malformed input, or
+better use prepared {\sc sql} statements, instead of statement
 templates. Unfortunately,
@@
 suggest that programmers are not always that careful.
-By using similar techniques malicious users can perform other exploits based on
-{\sc dsl}s like {\sc xp}ath~\cite{SW06,CDL07,MKS09},
+Using similar techniques, malicious users can mount other exploits based on
+{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09},
 {\sc xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
@@
 {\sc html} is another {\sc dsl} that can be used for malicious purposes
-when an application does not properly handle user supplied data. Based
-on this vulnerability an attacker can supply valid {\sc html},
+when an application does not properly handle user-supplied data. Based
+on this vulnerability attackers can supply valid {\sc html},
 typically via a parameter value, and inject their own content into the
@@
 attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
-vehicle for an {\sc csrf} attack in the following manner:
+vehicle for cross-site request forgery attacks in the following manner:
 Consider a vulnerable bulletin board system where {\tt img} tags are not checked.
-A malicious user could embed a {\sc csrf} request within {\tt img}
-tags in the following manner:
+A malicious user could embed a {\sc csrf} request within an {\tt img}
+tag in the following manner:
 
@@
 When the page with this injected code is accessed by an administrator,
-the attacker (with {\sc id} 13) will gain administrative privileges
+the attacker (with {\sc id} 13) will gain administrative privileges,
 while the administrator will have no immediate indication that there
@@
 A recent class of code injection attacks involve dynamic languages
-like JavaScript and {\sc php}~\cite{SFVM09,EWKK09,SMS13}.
+such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
 A simple example of a {\sc php} injection attack is an input string
-that is fed into an {\tt eval()} function call, e.g., in {\sc php}:
+that is fed into an {\tt eval()} function call, e.g.:
 
@@
 The user may pass into the {\tt value} parameter code that will
-execute in the server. Hence, if an attacker provides as
-input the following string: {\tt 10 ; system(''touch foo'');}
-then a file will be created on the server; it is easy
-to imagine more detrimental instances.
-
-JavaScript injection attacks, make up a large subset of dynamic
-language-driven attacks. Such attacks are manifested when a web
+be executed on the server. Hence, if an attacker provides as
+input the following string: {\tt 10 ; system("touch foo");}
+then a file will be created on the server---it is easy
+to imagine more detrimental scenarios.
+
+JavaScript injection attacks make up a large subset of dynamic
+language code injection attacks. Such attacks are enabled when a web
 application accepts and redisplays data of uncertain origin without
-appropriate validation and filtering. Based on this flaw, an attacker
+proper validation and filtering. Based on this flaw, an attacker
 can manage to inject a script in the JavaScript engine of a browser
 and alter its execution flow~\cite{ELX07}. For instance,
-consider a web page (foo.net) that prints the value
+consider a web page that prints the value
 of a query parameter ({\tt query}) from the
-page's {\sc url} in the web page's content
-without escaping the value. A malicious user
+page's {\sc url} as part of the page's content
+without escaping the value. Attackers
 can take advantage of this and inject an {\tt iframe} tag
-into the page to steal the user's cookie and
+into the page to steal a user's cookie and
 send it via an image request to a web site
-that he or she controls (malicious.com).
+under their control (malicious.com).
 This could be achieved by including the following
@@
 \begin{lstlisting}
-http://foo.net/vulnerable.html?query=
+http://example.com/vulnerable.html?query=
 <iframe src="javascript:document.body.innerHTML=+

### 2014-11-14 docs/questioning.tex
pass in III

@@
 In this section we provide a step-by-step exploitation model to
-understand the process of carrying out application attacks associated
-with source code injection. Figure~\ref{fig:attacks}
-presents the steps of different application attacks. Links between
-steps are labeled with the paths constituting different attacks. The
-sequence of steps for each attack is shown by the numbers next to the
-attack names in the labels. Most steps are common in all attacks. This
+understand the process of carrying out source code injection attacks
+against web applications.
+Figure~\ref{fig:attacks}
+presents the required steps for different classes of injection attacks.
+Links between steps are labeled with the different attacks that use that path,
+while the numbers next to attack labels denote the 
+sequence of steps for a particular attack.
+Most steps are common in all attacks. This
 is because they are based on similar attack vectors as we mentioned in
-the previous section. Large crosses on transitions in
-Figure~\ref{fig:attacks} indicate the points where defenses detect
-attacks.
-
-A malicious user can initiate the attack through two different routes.
-The attacker may use the browser of an innocent user as an attack
+the previous section. Large `X' marks on transitions 
+indicate the points where defenses detect or prevent attacks.
+
+An attacker can initiate an injection attack through two different main routes.
+One way is to use the browser of a victim as an attack
 vehicle, through which the code will be injected in the application.
 For example, the attacker could craft a malicious script into a {\sc
-  url} and then trick an end user to click on it via social
-engineering (i.e., phishing, through transition {\sc p-xss} 1.1, {\sc
+  url} and then trick a user to click on it through social
+engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
   n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
-to inject directly the malicious code in the application (through
-transition {\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
-in a web application that accepts and redisplays user input
+to inject directly the malicious code on the server through an HTTP request
+({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
+in a web application that accepts and processes user input
 without appropriate validation. An attacker could upload data
 containing a specially crafted script
-to steal the cookies of the visiting users or embed malicious
-{\sc sql} code to retrieve all the password entries from a database.
-Recall the examples we provided in Section~\ref{sec:attacks}.
-Note that an {\sc xss} attack can start from both routes.
+to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1)
+or embed malicious
+{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
+%Recall the examples we provided in Section~\ref{sec:attacks}.
+Note that {\sc xss} attacks can start from both routes.
 
@@
 {\it persistent}. Non-persistent {\sc xss} attacks take place when the
-data provided by a user is used immediately by server-side scripts to
-parse and display a page of results, without properly sanitizing the
-request (transition {\sc p-xss} 7, {\sc n-xss} 2).
-Thus, in a non-persistent {\sc xss} attack the injected code
-is never saved on the server and immediately becomes part of the
+data provided by a user is processed on-the-fly
+by server-side application logic and end up without proper sanitization
+into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
+that is eventually rendered by the user's browser.
+Thus, in a non-persistent {\sc xss} attack, the injected code
+is not saved on the server and immediately becomes part of the
 content that is sent back to a web user.
-
-In persistent {\sc xss} attacks malicious code is saved by the server.
-The injected code that is stored on the server-side re-enters the
+In persistent {\sc xss} attacks, on the other hand,
+malicious code is permanently stored on the server ({\sc p-xss} 5).
+The injected code residing at server-side then re-enters the
 application's execution flow and becomes part of the content that is
-actually sent back afterwards to the user.
+actually sent back to the user as part of a future response.
 
@@
 \end{center}
-\caption{\label{fig:attacks}Attack model demonstrating web
-application attacks based on source code injection.
-For every arrow there are corresponding transition numbers for
-every attack. Every {\it point} indicates a transition where mechanisms
-detect attacks. For every point we provide the corresponding
-references:
-Point {\sc ub} (at the user's browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
-Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-Point i{\sc db} (in the database):~\cite{BK04,LLW02,VMV05}.}
+\caption{\label{fig:attacks}Attack model for dynamic and domain specific
+language code injection in web applications.
+Transitions are labeled with the different attacks that use that path,
+while the numbers next to attack labels denote the 
+sequence of steps for a particular attack.
+Points where different types of defenses
+detect or prevent attacks are marked with an `X' symbol:
+{\sc ub} (browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
+{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
+{\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+Point i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}

### 2014-11-14 docs/questioning.tex
more changes / corrections

@@
 could obtain the administrator's password by email.
-Savvy programmers can use certain API functions, such as {\sc php}'s
+Savvy programmers can use certain {\sc api} functions, such as {\sc php}'s
 {\tt mysql\_real\_escape\_string()} to detect malformed input, or
@@
 JavaScript injection attacks make up a large subset of dynamic
-language code injection attacks. Such attacks are enabled when a web
-application accepts and redisplays data of uncertain origin without
+language code injection attacks. Such attacks are enabled when
+a web application accepts
+and redisplays data of uncertain origin without
 proper validation and filtering. Based on this flaw, an attacker
 can manage to inject a script in the JavaScript engine of a browser
-and alter its execution flow~\cite{ELX07}. For instance,
-consider a web page that prints the value
+and alter its execution flow~\cite{ELX07}.
+JavaScript injection attacks are considered a critical issue
+in web application security mainly because it is associated with
+major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
+Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
+A typical {\sc xss} example that involves JavaScript injection
+is the following: consider a web page that prints the value
 of a query parameter ({\tt query}) from the
@@
 \noindent
-JavaScript injection is considered a critical issue in web application security
-mainly because it is associated with major vulnerabilities such as
-{\sc xss} attacks~\cite{SG07} and Cross-Channel Scripting
-({\sc xcs}) attacks~\cite{W10,BBB09}. In many cases {\sc xss} attacks
+Note that in many cases {\sc xss} attacks
 involve the injection of both {\sc html} and JavaScript code.
@@
 detect or prevent attacks are marked with an `X' symbol:
-{\sc ub} (browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
+{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
 {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-{\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-Point i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
@@
 within a proxy (Point {\sc s}t{\sc b}).
-\item Embedded in a query, but before it reaches the server's database
-  (Point {\sc e}i{\sc q}).
+\item At the database abstraction layer, before it reaches the server's database
+  (Point {\sc dbal}).
 \item After the malicious code reaches the server's database
@@
 and detect the attack before a query reaches the
-database (Point {\sc e}i{\sc q}).
+database (Point {\sc dbal}).
 Contrary to {\sc sqlg}uard and other
@@
 tainted string is used as an argument to a sink method
-an exception is raised (Point {\sc e}i{\sc q}).
+an exception is raised (Point {\sc dbal}).
 
 It is possible to apply further checks when it is established that
-tainted data have reached a sink (Point {\sc e}i{\sc q}). {\it Xu et
+tainted data have reached a sink (Point {\sc dbal}). {\it Xu et
   al.}~\cite{XBS06} track taint information at the level of bytes in
@@
 and others. When tainted data reaches a sink, {\sc csse} performs
-syntactic checks based on the aforementioned metadata (Point {\sc e}i{\sc q}).
+syntactic checks based on the aforementioned metadata (Point {\sc dbal}).
 {\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
@@
 checks all statements for compliance and can block code statements
-containing injected elements (Point {\sc e}i{\sc q}). {\sc
+containing injected elements (Point {\sc dbal}). {\sc
   amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
-  sql} injection attacks (Point {\sc e}i{\sc q}) by associating a query model
+  sql} injection attacks (Point {\sc dbal}) by associating a query model
 with the location of every {\sc sql} statement within the application.
@@
 the query that is about to be executed and compares it with the parsed
-tree of the ``shadow'' (Point {\sc e}i{\sc q}). If the trees are not
+tree of the ``shadow'' (Point {\sc dbal}). If the trees are not
 equal the application is probably under attack. Note that Diglossia

### 2014-11-14 docs/questioning.tex
page numbers
new figure to and description to address the CSRF issue

@@
 \maketitle
+\thispagestyle{plain}
+\pagestyle{plain}
 \begin{abstract}
@@
 finally reaches the database where it is executed.
-In the case of a {\sc csrf} attack the functionality dictated by
-the malicious response is performed.
 
@@
 
+In the case of a {\sc csrf} attack, consider a
+user who visits a page, where attackers have managed
+to inject {\sc html} code that contains a hidden
+request in the way we described in Section~\ref{sec:attacks}.
+If an authenticated user visits this web page, then the
+malicious request will reach the application ({\sc csrf} 2) and
+the functionality dictated by the malicious response will
+be performed.
+
 \begin{figure*}
@@
 \leavevmode
-\includegraphics[scale=0.61]{attacks-steps-new.pdf}
+\includegraphics[scale=0.61]{attacks-steps-newer.pdf}
 \end{center}

### 2014-11-14 docs/questioning.tex
stylistic fixes

--- 2014-11-14 docs/questioning.tex
@@
 
-There is already a survey on mitigating software vulnerabilities
-in general~\cite{SZ12}. The scope of that
-research is much broader and leaves out the majority of the
-approaches and mechanisms that we consider in this work.
-This is mainly because that work includes countermeasures
-that identify vulnerabilities using program analysis
-(which takes place during the development or testing phases), while
-we consider protection mechanisms that counter
-web attacks when they take place. Similarly, static or
-dynamic analysis techniques that examine applications to
-identify vulnerabilities that may lead to the attacks
-that we described earlier are out of scope as well.
-While countermeasures against {\sc sql}
-injection attacks have been previously surveyed in a 2006 paper~\cite{HVO06},
-a significant number of new {\sc sql} injection defenses has been proposed since
-then, as we mentioned earlier.
+There is already a survey on mitigating software vulnerabilities in
+general~\cite{SZ12}. The scope of that research is much broader that
+ours and leaves out the majority of the approaches and mechanisms that
+we consider in this work. This is mainly because that work includes
+countermeasures that identify vulnerabilities using program analysis
+(which takes place during the development or testing phases), while we
+consider protection mechanisms that counter web attacks when they take
+place. Similarly, static or dynamic analysis techniques that examine
+applications to identify vulnerabilities that may lead to the attacks
+that we described earlier are out of scope as well. While
+countermeasures against {\sc sql} injection attacks have been
+previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
+of new {\sc sql} injection defenses has been proposed since then, as
+we mentioned earlier.
 
@@
 
-The main vulnerability behind the most dangerous
-web application attacks involves
-the absence of input validation. By taking advantage of
-this, attackers can inject their code into
-applications to perform malicious tasks. Exploits
-of this kind can have different forms depending on the
-execution context of the application and the location
-of the programming flaw that leads to the attack.
+Lack of input validation is a major vulnerability behind dangerouw web
+application attacks. By taking advantage of this, attackers can inject
+their code into applications to perform malicious tasks. Exploits of
+this kind can have different forms depending on the execution context
+of the application and the location of the programming flaw that leads
+to the attack.
 
@@
 
-Code injection attacks can be divided into two categories. The first
-involves binary code and the second higher-level language code. An
+Code injection attacks can be divided in two categories. The first
+involves binary code and the second source language code. An
 extensive survey on binary code injection attacks was conducted by
@@
 that protect web applications against attacks based on the
-injection of higher level language code.
+injection of source code.
 
@@
 {\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
-In the following, we briefly discuss examples from both categories
-that will be used throughout the paper.
+To illustrate, we briefly discuss examples from both categories.
 
 Injection attacks that involve {\sc dsl}s constitute an important
-subset of the code injection problem, as {\sc dsl}s such as {\sc sql} and
-{\sc xml} play an significant role in the development of both web and
-mobile applications. For example, many applications have interfaces
-through which a user enters input to interact with the application,
-thereby interacting with the underlying database. This input can
-become part of an {\sc sql} query and get executed on the target
-database. Code injection attacks that exploit vulnerabilities in database
-interfaces by taking advantage of input validation issues, such as
-incorrectly passed parameters or incorrect type handling, are called
-{\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
-Consider a trivial example that takes advantage of incorrectly
-filtered quotation characters in an application that
-sends a temporary password for a forgetful user via email by executing the
-following query:
+subset of the source code injection problem, as {\sc dsl}s such as
+{\sc sql} and {\sc xml} play a significant role in the development of
+both web and mobile applications. For example, many applications have
+interfaces through which a user enters input to interact with the
+application, thereby interacting with the underlying database. This
+input can become part of an {\sc sql} query and get executed on the
+target database. Code injection attacks that exploit vulnerabilities
+in database interfaces by taking advantage of input validation issues,
+such as incorrectly passed parameters or incorrect type handling, are
+called {\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
+Consider a trivial exploit that takes advantage of incorrectly
+filtered quotation characters in an application that sends a temporary
+password for a forgetful user via email by executing the following
+query:
 
@@
 \noindent
-Attackers that would input the string {\tt anything' OR 'x'='x},
-could obtain the administrator's password by email.
-Savvy programmers can use certain {\sc api} functions, such as {\sc php}'s
-{\tt mysql\_real\_escape\_string()} to detect malformed input, or
-better use prepared {\sc sql} statements, instead of statement
-templates. Unfortunately,
-the increasing number of {\sc sql} injection attacks
-suggest that programmers are not always that careful.
-Using similar techniques, malicious users can mount other exploits based on
-{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09},
-{\sc xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. With this kind of
-attacks, a malicious user can view sensitive information, destroy or
-modify protected data, or even crash the entire application.
-
-{\sc html} is another {\sc dsl} that can be used for malicious purposes
-when an application does not properly handle user-supplied data. Based
-on this vulnerability attackers can supply valid {\sc html},
-typically via a parameter value, and inject their own content into the
-page. {\sc html} injection is mainly associated with {\sc xss}
-attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
-vehicle for cross-site request forgery attacks in the following manner:
-Consider a vulnerable bulletin board system where {\tt img} tags are not checked.
-A malicious user could embed a {\sc csrf} request within an {\tt img}
-tag in the following manner:
+Attackers that would input the string {\tt anything' OR 'x'='x}
+thereby obtaining the administrator's password by email. Savvy
+programmers can use certain {\sc api} functions, such as {\sc php}'s
+{\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
+better, use prepared {\sc sql} statements instead of statement
+templates. Unfortunately, the increasing number of {\sc sql} injection
+attacks suggests that programmers are not always that careful. Using
+similar techniques, malicious users can mount other exploits based on
+{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
+  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
+wide-ranging. A malicious user can view sensitive information, destroy
+or modify protected data, or even crash the entire application.
+
+{\sc html} is another {\sc dsl} that can be used for malicious
+purposes when an application does not properly handle user-supplied
+data. Based on this vulnerability attackers can supply valid {\sc
+  html}, typically via a parameter value, and inject their own content
+into the page. {\sc html} injection is mainly associated with {\sc
+  xss} attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
+vehicle for cross-site request forgery ({\sc csrf}) attacks in the
+following manner: Consider a vulnerable bulletin board system where
+{\tt img} tags are not checked. A malicious user could embed a {\sc
+  csrf} request within an {\tt img} tag in the following manner:
 
@@
 Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
-A typical {\sc xss} example that involves JavaScript injection
-is the following: consider a web page that prints the value
+For a typical {\sc xss} example that involves JavaScript injection
+consider a web page that prints the value
 of a query parameter ({\tt query}) from the
@@
 This could be achieved by including the following
-link to the malicious web site (or send it via phishing
-email) and induce the user to click on it:
+link to the malicious web site (or sending it via phishing
+email) and inducing the user to click on it:
 
@@
 
-In this section we provide a step-by-step exploitation model to
-understand the process of carrying out source code injection attacks
-against web applications.
-Figure~\ref{fig:attacks}
-presents the required steps for different classes of injection attacks.
-Links between steps are labeled with the different attacks that use that path,
-while the numbers next to attack labels denote the 
-sequence of steps for a particular attack.
-Most steps are common in all attacks. This
-is because they are based on similar attack vectors as we mentioned in
-the previous section. Large `X' marks on transitions 
-indicate the points where defenses detect or prevent attacks.
+We provide a step-by-step exploitation model to understand the process
+of carrying out source code injection attacks against web
+applications. Figure~\ref{fig:attacks} presents the required steps for
+different classes of injection attacks. Links between steps are
+labeled with the different attacks that use that path, while the
+numbers next to attack labels denote the sequence of steps for a
+particular attack. Most steps are common in all attacks. This is
+because they are based on similar attack vectors as we mentioned in
+the previous section. Large `X' marks on transitions indicate the
+points where defenses detect or prevent attacks.
 
@@
 
-In this section we enumerate key observations
-based on the dimensions we set in Section~\ref{sec:dimensions}.
+We group our key observations on the~34 publications along the
+dimensions we identified in Section~\ref{sec:dimensions}.
 
@@
 
-In this section we provide some lessons learned from
-our observations and provide some recommendations
-that developers of new mechanisms may find helpful.
+Our observations lead to some lessons and recommendations that
+developers of new mechanisms may find helpful. In particular, they
+call for improving accuracy tests and code availability, while
+aiming to reduce computational and deployment overheads.
 

### 2014-11-14 docs/questioning.tex
minor fixes

@@
 stripped from user input. Subsequent
-refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
+refinements by {\it Valeur et al.}~\cite{VMV05} tagged each transaction with
 the corresponding application as an extension of their anomaly
@@
 
-\subsection{On Code Availability}
+\subsection{Code Availability}
 

### 2014-11-14 docs/questioning.tex
removed some italics, from source code injection to code injection

@@
   In this paper, we systematize the existing knowledge on
-  various defense mechanisms against source code injection attacks by proposing
+  various defense mechanisms against code injection attacks by proposing
   a model that highlights the key weaknesses that enable these attacks,
@@
 model which highlights that most of the steps needed to mount
-different types of source code injection attacks are
+different types of code injection attacks are
 common.\footnote{Note that we do not consider lower-level attacks based on
@@
 \item We provide a unified exploitation model for different types of
-  web application attacks based on source code injection.
+  web application attacks based on code injection.
 \item We categorize and analyze proposed defenses using a set of
@@
 Section~\ref{sec:attacks} provides some insights on
-source code injection attacks and
+code injection attacks and
 Section~\ref{sec:model} presents our proposed model.
@@
 
-\section{Source Code Injection Attacks\\in Web Applications}
+\section{Code Injection Attacks\\in Web Applications}
 \label{sec:attacks}
@@
 Code injection attacks can be divided in two categories. The first
-involves binary code and the second source language code. An
+involves binary code and the second higher-level language code. An
 extensive survey on binary code injection attacks was conducted by
@@
 that protect web applications against attacks based on the
-injection of source code.
+injection of higher-level language code.
 
@@
 Injection attacks that involve {\sc dsl}s constitute an important
-subset of the source code injection problem, as {\sc dsl}s such as
+subset of the code injection problem, as {\sc dsl}s such as
 {\sc sql} and {\sc xml} play a significant role in the development of
@@
 We provide a step-by-step exploitation model to understand the process
-of carrying out source code injection attacks against web
+of carrying out code injection attacks against web
 applications. Figure~\ref{fig:attacks} presents the required steps for
@@
 \caption{\label{fig:defenses}The basic categories of countermeasures
-against web application attacks based on source code
+against web application attacks based on code
 injection. For each approach we provide the references
@@
 Figure~\ref{fig:defenses} presents a taxonomy of the
-defenses that protect web applications against
-source code injection attacks based on.
+defenses that protect web applications against code injection attacks.
 We can identify three approaches:
@@
 There exist three basic etiological approaches used to protect web
-applications from source code injection attacks.
+applications from code injection attacks.
 
@@
 
-{\it Noxes}~\cite{KKVJ06,KJKV09} is the only
+Noxes~\cite{KKVJ06,KJKV09} is the only
 framework that partially allows the web
@@
 by the original design of the developers. This is extensively
-described by {\it Athanasopoulos et al.}~\cite{APKLM10}, who also describe
+described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
 another recent variation of JavaScript injection attacks, known as
@@
 policies directly either in {\sc html} or JavaScript code
-to confine their behavior. {\it BrowserShield}~\cite{RDWDE07}
+to confine their behavior. BrowserShield~\cite{RDWDE07}
 acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
@@
 that are based on reported browser vulnerabilities.
-{\it ConScript}~\cite{ML10}, {\it CoreScript}~\cite{YCIS07}
-and the framework by {\it Phung et al.}~\cite{PSC09}
+ConScript~\cite{ML10}, CoreScript~\cite{YCIS07}
+and the framework by Phung et al.~\cite{PSC09}
 extend JavaScript with new primitive functions that
@@
 in the way we described in Section~\ref{sec:attacks}.
-\noindent {\it WebJail}~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
+\noindent WebJail~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
 are two frameworks that can actually detect such an attack (Point {\sc
@@
 interposed on the client-server communication and modifying
-it. {\it NoForge}~\cite{JKK06a}
+it. NoForge~\cite{JKK06a}
 parses the {\sc html} server responses
@@
 support cross-origin requests.
-{\it j{\sc csrf}}~\cite{PS11} has a similar
+j{\sc csrf}~\cite{PS11} has a similar
 functionality and meanwhile addresses the above problems.
-Finally, {\it CsFire}~\cite{DDHPJ10}
+Finally, CsFire~\cite{DDHPJ10}
 examines cross-domain interactions, to design a
@@
 
-{\it {\sc sql}rand}~\cite{BK04} implements {\sc isr} to detect {\sc
+{\sc sql}rand~\cite{BK04} implements {\sc isr} to detect {\sc
   sql} injection attacks. It allows programmers to create {\sc sql}
@@
 in a proxy at the server-side (Point {\sc s}t{\sc b}) or in the browser
-(Point {\sc ub}). Variations of this approach include {\it
-  Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}, which
+(Point {\sc ub}). Variations of this approach include
+Noncespaces~\cite{GC09} and x{\sc js}~\cite{APKLM10}, which
 randomize the instruction set of {\sc html} and JavaScript
@@
 must set specific policies in a manner similar to a firewall
-configuration language. {\it {\sc sm}ask}~\cite{JB07} is another
+configuration language. {\sc sm}ask~\cite{JB07} is another
 framework that was inspired by {\sc isr}. To detect {\sc xss}
@@
 {\sc isr} is a deterministic approach that can be applied to detect
-different attacks in an efficient manner. However, {\it Sovarel et
-al.}~\cite{SEP05} have investigated thoroughly the effectiveness of
+different attacks in an efficient manner. However, Sovarel et
+al.~\cite{SEP05} have investigated thoroughly the effectiveness of
 {\sc isr} and showed that a malicious user may be able to circumvent
@@
 \begin{table*}
-    \caption{Comparison summary of mechanisms developed to counter application attacks based on source code injection.}
+    \caption{Comparison summary of mechanisms developed to counter application attacks based on code injection.}
     \label{tab:comp}
@@
   \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlg}uard~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlc}heck~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
   \hline
   \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & 135 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   {\it NoForge}~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
+  &   {\sc dsi}~\cite{NSS06} & 135 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   NoForge~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
+  &   Noxes~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
   % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\it {\sc beep}}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
-  &   {\it CoreScript}~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\sc beep}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
+  &   BrowserShield~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
+  &   CoreScript~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
   &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
   % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   {\it Phung et al.}~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
-  &   {\it ConScript}~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
-  &   {\it j{\sc csrf}}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
+  &   Phung et al.~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
+  &   ConScript~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
+  &   CsFire~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
+  &   j{\sc csrf}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
+  &   WebJail~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
@@
   \multirow{4}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   {\it Noncespaces}~\cite{GC09} & 109 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
-  &   {\it x{\sc js}}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
+  &   {\sc sql}rand~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
+  &   {\sc sm}ask~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Noncespaces~\cite{GC09} & 109 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
+  &   x{\sc js}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
   \thickhline
@@
   \multirow{7}{*}{Taint Tracking}
-  &   {\it Haldar et al.}~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   Haldar et al.~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
   &   {\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
   % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-  &   {\it Xu et al.}~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\it {\sc wasc}}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   {\it Vogt et al.}~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\it {\sc php} Aspis}~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
-  &   {\it Stock et al.}~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
+  &   Xu et al.~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc wasc}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Vogt et al.~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\sc php} Aspis~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
+  &   Stock et al.~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
   \hline 
   \multirow{6}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
-  &   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
-  &   {\it libAnomaly}~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
-  &   {\it {\sc xssds}}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  &   {\it {\sc swap}}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
-  &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
+  &   {\sc didafit}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
+  &   {\sc amnesia}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
+  &   libAnomaly~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc xssds}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\sc swap}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
+  &   {\sc sd}river~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
   % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
@@
   \multirow{3}{*}{Hybrid}
-  &   {\it {\sc xss-guard}}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
-  &   {\it Blueprint}~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   {\it Diglossia}~\cite{SMS13} & 4 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   {\sc xss-guard}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
+  &   Blueprint~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
+  &   Diglossia~\cite{SMS13} & 4 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
   \thickhline
@@
 and how attacks are detected.
-For example, {\it Haldar et al.}~\cite{HCF05} have implemented
+For example, Haldar et al.~\cite{HCF05} have implemented
 their scheme for the Java Virtual Machine ({\sc jvm})
@@
 It is possible to apply further checks when it is established that
-tainted data have reached a sink (Point {\sc dbal}). {\it Xu et
-  al.}~\cite{XBS06} track taint information at the level of bytes in
+tainted data have reached a sink (Point {\sc dbal}).
+Xu et al.~\cite{XBS06} track taint information at the level of bytes in
 memory. To distinguish between legitimate and malicious uses of
@@
 syntactic checks based on the aforementioned metadata (Point {\sc dbal}).
-{\it {\sc php} Aspis}~\cite{PMP11} works in a similar way. To obtain
+{\sc php} Aspis~\cite{PMP11} works in a similar way. To obtain
 metadata, it takes advantage of the  {\sc php} array data structure.
@@
 
-{\it Vogt et al.}~\cite{VFJKKV07} have developed a tainting scheme
+Vogt et al.~\cite{VFJKKV07} have developed a tainting scheme
 that follows a different approach. Contrary to the aforementioned
@@
 site from which it came from.
-{\it Stock et al.}~\cite{SLMS14} propose a scheme that also operates
+Stock et al.~\cite{SLMS14} propose a scheme that also operates
 in the browser (Point {\sc ub}). The scheme focuses on the detection of
@@
   xp}ath queries) in various forms, and detect attacks as outliers
-from the set of valid code statements. An early approach, {\it {\sc
-    didafit}}~\cite{LLW02} detects {\sc sql} injection (Point
+from the set of valid code statements. An early approach,
+{\sc didafit}~\cite{LLW02} detects {\sc sql} injection (Point
 {\sc sdb}) attacks by recording all database transactions
 stripped from user input. Subsequent
-refinements by {\it Valeur et al.}~\cite{VMV05} tagged each transaction with
+refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
 the corresponding application as an extension of their anomaly
-detection framework called {\it libAnomaly}. {\it {\sc
-    sd}river}~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
+detection framework called libAnomaly.
+{\sc sd}river~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
 that prevents {\sc sql} and {\sc xp}ath injection attacks. The
@@
 Various countermeasures against {\sc xss} attacks follow a similar
-pattern. {\it {\sc swap}}~\cite{WPLKK09} creates a unique identifier
+pattern. {\sc swap}~\cite{WPLKK09} creates a unique identifier
 ({\it script {\sc id}}) for every legitimate script on the server.
@@
 imposes a significant overhead (see Table~\ref{tab:comp}). The authors
-of {\it {\sc xssds}}~\cite{JEP08} have implemented a similar mechanism
+of {\sc xssds}~\cite{JEP08} have implemented a similar mechanism
 that also supports dynamic and external scripts. Specifically, during the
@@
 Defenses based on training include some mechanisms that can be easily
-circumvented. For example, {\sc didafit} and {\it libAnomaly} do not
+circumvented. For example, {\sc didafit} and libAnomaly do not
 tag transactions with their corresponding call sites. This can lead
@@
 Even if the application's administrators have chosen to use
-either {\sc didafit} or {\it libAnomaly} as protection,
+either {\sc didafit} or libAnomaly as protection,
 an attacker could bypass them and obtain the
@@
 
-{\it Blueprint}~\cite{LV09} is a policy enforcement framework that
+Blueprint~\cite{LV09} is a policy enforcement framework that
 uses parsed trees to detect {\sc xss} attacks. To guarantee
@@
 
-{\it Diglossia}~\cite{SMS13} combines positive taint tracking together
+Diglossia~\cite{SMS13} combines positive taint tracking together
 with parse-tree validation. Diglossia was based on the theory of Ray
@@
   \multirow{2}{*}{Parse-Tree Validation}
-  &   {\it {\sc sqlc}heck}~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sqlg}uard}~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
+  &   {\sc sqlc}heck~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc sqlg}uard~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
   \hline
   \multirow{12}{*}{Policy Enforcement}
-  &   {\it {\sc dsi}}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it NoForge}~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
-  &   {\it Noxes}~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc dsi}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
+  &   NoForge~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
+  &   Noxes~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
   % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc beep}}~\cite{TNH07} & \tick & \tick & \tick \\
-  &   {\it BrowserShield}~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it CoreScript}~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc beep}~\cite{TNH07} & \tick & \tick & \tick \\
+  &   BrowserShield~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   CoreScript~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   {\sc soma}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
   % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Phung et al.}~\cite{PSC09} & \tick & \tick & \tick \\
-  &   {\it ConScript}~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   {\it CsFire}~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
-  &   {\it j{\sc csrf}}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it WebJail}~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Phung et al.~\cite{PSC09} & \tick & \tick & \tick \\
+  &   ConScript~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
+  &   CsFire~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
+  &   j{\sc csrf}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
+  &   WebJail~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
     % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
@@
   \multirow{4}{*}{{\sc isr}}
-  &   {\it {\sc sql}rand}~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sm}ask}~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Noncespaces}~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it x{\sc js}}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc sql}rand~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc sm}ask~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Noncespaces~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
+  &   x{\sc js}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
   \thickhline
@@
   \multirow{7}{*}{Taint Tracking}
-  &   {\it Haldar et al.}~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   Haldar et al.~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
   &   {\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Xu et al.}~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc wasc}}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Vogt et al.}~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc php} Aspis}~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
-  &   {\it Stock et al.}~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Xu et al.~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc wasc}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Vogt et al.~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc php} Aspis~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
+  &   Stock et al.~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
   \hline
   \multirow{6}{*}{Training}
-  &   {\it {\sc didafit}}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc amnesia}}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
-  &   {\it libAnomaly}~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
-  &   {\it {\sc xssds}}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc swap}}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
+  &   {\sc didafit}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc amnesia}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
+  &   libAnomaly~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  &   {\sc xssds}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc swap}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc sd}river~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
   \thickhline
@@
   \multirow{3}{*}{Hybrid}
-  &   {\it {\sc xss-guard}}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\it Blueprint}~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-  &   {\it Diglossia}~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc xss-guard}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Blueprint~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
+  &   Diglossia~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
   \thickhline
@@
 following providers: the Common Vulnerabilities and Exposures ({\sc
-  cve}) database~\cite{cve}, the {\it Bugtraq} security
+  cve}) database~\cite{cve}, the Bugtraq security
 mailing list~\cite{bugtraq}, the {\sc xss}ed.com
@@
 a reason not to adopt them, but they may hinder their widespread use.
-Since source code injection attacks are complex, it may be logical to
+Since code injection attacks are complex, it may be logical to
 expect that mechanisms to detect them would be complex too. The effort
@@
 Despite many approaches that have been developed,
-application attacks based on source code injection
+application attacks based on code injection
 have been consistently present for the last 15 years,

### 2014-11-14 docs/questioning.tex
some changes / corrections

@@
 
-Lack of input validation is a major vulnerability behind dangerouw web
+Lack of input validation is a major vulnerability behind dangerous web
 application attacks. By taking advantage of this, attackers can inject
@@
 {\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
-To illustrate, we briefly discuss examples from both categories.
+To illustrate, we briefly discuss examples from both categories
+that will be used throughout the paper.
 
@@
 The key idea behind Noxes is to parse
-the {\sc html} that reaches the browser to
+the {\sc html} response that reaches the browser to
 find static {\sc url} references. Then, based on
@@
 web site''). The main issue with Noxes is that
-it does not deal with JavaScript-driven {\sc xss}
-attacks, which currently make for the most popular
-{\sc xss} attack vector.
+{\sc url}s can be dynamically assembled by scripts
+which may lead to false alarms.
 

### 2014-11-14 docs/questioning.tex
updated picture to cover CSRF properly. Also added corresponding description in the model.

@@
 engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
-  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
-to inject directly the malicious code on the server through an HTTP request
-({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
+  n-xss} 1.1). Alternatively, the attacker may be able
+to inject directly the malicious code on the server through an {\sc http} request
+({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc csrf} 1). This would happen
 in a web application that accepts and processes user input
@@
 containing a specially crafted script
-to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1)
+to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
+an {\tt img} tag including a malicious {\sc http} request ({\sc csrf}),
 or embed malicious
@@
 
-In the case of a {\sc csrf} attack, consider a
-user who visits a page, where attackers have managed
-to inject {\sc html} code that contains a hidden
-request in the way we described in Section~\ref{sec:attacks}.
-If an authenticated user visits this web page, then the
-malicious request will reach the application ({\sc csrf} 2) and
-the functionality dictated by the malicious response will
-be performed.
+A common {\sc csrf} attack could involve just a
+{\sc url} containing a malicious {\sc http} request
+which in turn must be clicked by the user
+(via social engineering again).
+However, this technique does not involve code injection
+and it is not described in Figure~\ref{fig:attacks}.
+The {\sc csrf} attack illustrated here could
+involve an attacker that manages to inject
+{\sc html} code that contains a hidden request
+in the way we described in Section~\ref{sec:attacks}.
+This code will be stored in the database ({\sc csrf} 5)
+and then it will re-enter the application if
+a user visits a page ({\sc csrf} 6). When the
+content reaches the browser the functionality
+dictated by the malicious request will be performed.
 

### 2014-11-14 docs/questioning.tex
new model - now illustrating CSRF properly, also rearranged the dynamic detection attacks paragraph

@@
 vehicle for cross-site request forgery ({\sc csrf}) attacks in the
-following manner: Consider a vulnerable bulletin board system where
+following manner: Consider a bulletin board system where
 {\tt img} tags are not checked. A malicious user could embed a {\sc
@@
 When the page with this injected code is accessed by an administrator,
-the attacker (with {\sc id} 13) will gain administrative privileges,
-while the administrator will have no immediate indication that there
-has been an attack.
+the attacker (with {\sc id} 13) will gain administrative privileges
+over the vulnerable.com web page,
+while the administrator of the bulletin board system
+will have no immediate indication that there has been an attack.
 
@@
 such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
-A simple example of a {\sc php} injection attack is an input string
-that is fed into an {\tt eval()} function call, e.g.:
-
-\bgroup \lstset{language=PHP}
-\begin{small}
-\begin{lstlisting}
-$variable = $_GET['var']; 
-$input = $_GET['value'];
-eval('$variable = ' . $input . ';')
-\end{lstlisting}
-\end{small}
-\egroup
-
-\noindent
-The user may pass into the {\tt value} parameter code that will
-be executed on the server. Hence, if an attacker provides as
-input the following string: {\tt 10 ; system("touch foo");}
-then a file will be created on the server---it is easy
-to imagine more detrimental scenarios.
-
 JavaScript injection attacks make up a large subset of dynamic
-language code injection attacks. Such attacks are enabled when
-a web application accepts
+language code injection attacks and are considered a critical issue
+in web application security mainly because they are associated with
+major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
+Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}
+Such attacks are enabled when a web application accepts
 and redisplays data of uncertain origin without
@@
 and alter its execution flow~\cite{ELX07}.
-JavaScript injection attacks are considered a critical issue
-in web application security mainly because it is associated with
-major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
-Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
 For a typical {\sc xss} example that involves JavaScript injection
@@
 involve the injection of both {\sc html} and JavaScript code.
+
+A simple example of a {\sc php} injection attack is an input string
+that is fed into an {\tt eval()} function call, e.g.:
+
+\bgroup \lstset{language=PHP}
+\begin{small}
+\begin{lstlisting}
+$variable = $_GET['var']; 
+$input = $_GET['value'];
+eval('$variable = ' . $input . ';')
+\end{lstlisting}
+\end{small}
+\egroup
+
+\noindent
+The user may pass into the {\tt value} parameter code that will
+be executed on the server. Hence, if an attacker provides as
+input the following string: {\tt 10 ; system("touch foo");}
+then a file will be created on the server---it is easy
+to imagine more detrimental scenarios.
 
@@
 which in turn must be clicked by the user
-(via social engineering again).
-However, this technique does not involve code injection
-and it is not described in Figure~\ref{fig:attacks}.
-The {\sc csrf} attack illustrated here could
-involve an attacker that manages to inject
-{\sc html} code that contains a hidden request
-in the way we described in Section~\ref{sec:attacks}.
-This code will be stored in the database ({\sc csrf} 5)
+via social engineering again ({\sc csrf} 1).
+Note, that this case does not involve code injection
+and it never reaches the server that is vulnerable
+to code injection (Server 1).
+The {\sc i-csrf} attack involves an attacker
+that manages to inject {\sc html} code that contains
+a hidden request in the way we described in
+Section~\ref{sec:attacks}. This code will be stored
+in the database ({\sc i-csrf} 5)
 and then it will re-enter the application if
-a user visits a page ({\sc csrf} 6). When the
+a user visits a page ({\sc i-csrf} 6). When the
 content reaches the browser the functionality
@@
 \leavevmode
-\includegraphics[scale=0.61]{attacks-steps-newer.pdf}
+\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
 \end{center}

### 2014-11-14 docs/questioning.tex
added POI attacks

@@
 into the page. {\sc html} injection is mainly associated with {\sc
-  xss} attacks~\cite{BJM08,LZRL09}. However, it can also be used as a
-vehicle for cross-site request forgery ({\sc csrf}) attacks in the
-following manner: Consider a bulletin board system where
+  xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
+{\sc html} injection though, can also be used as a
+vehicle for a {\sc csrf} attack. Consider a bulletin board system where
 {\tt img} tags are not checked. A malicious user could embed a {\sc
@@
 to imagine more detrimental scenarios.
+
+A recent attack called {\sc php} Object Injection
+({\sc poi})~\cite{DKH14} does not directly involve code
+injection and is performed by injecting malicious
+payloads (for example cookies) that when deserialized
+by the application, arbitrary code execution can be
+achieved. Note that the exploitation model that we propose
+in the following Section can represent such attacks too.
 

### 2014-11-14 docs/questioning.tex
pass in IV

@@
 character. First, a defense mechanism may be important, and therefore
-publishable, because it shows that an attack can be detected in a
-reliable manner. Secondly, a defense mechanism may be important not
+publishable, because it shows that an attack can be detected or prevented in a
+reliable manner. Second, a defense mechanism may be important not
 just as a research contribution, but as a practical tool, if it can be
-put to use by administrators and users to shield their applications
-and services against the detected attacks.
-
-The detection of attacks in a reliable manner can be analyzed using
+used by administrators and users to shield their applications
+and services against the supported attacks.
+
+The detection and prevention of attacks
+in a reliable manner can be analyzed using
 criteria common with other research fields:
 \begin{itemize}
-\item Statistical measures that show how reliable the detection really
+\item Statistical measurements that show how reliable the detection really
   is.
-\item Research practices that promote replication of the findings.
+\item Research practices that promote replication and validation
+of the findings.
 \end{itemize}
 
-Whether a reliable attack defense mechanism has value in a practical
+Whether a reliable defense mechanism has value in a practical
 setting rests on a different set of criteria:
@@
 \item How robust is it against ways to circumvent it?
-\item At which point of the computation flow does it detect an attack?
+\item At which point throughout the system does it block an attack?
 \end{itemize}
 
-The first two criteria are \emph{Accuracy} and
-\emph{Availability}. The other four criteria are \emph{Computational
+The first two criteria correspond to \emph{Accuracy} and
+\emph{Availability}. The other four criteria correspond to \emph{Computational
   Performance}, \emph{Ease of Use}, \emph{Security}, and
@@
 
-Web application attack defense mechanisms
-must demonstrate the presence of an attack. This, however, does not
-make an application attack defense mechanism immediately useful. A
-detection mechanism must be reliable. The accuracy of a detection
-mechanism is gauged with the following
-metrics~\cite{TDR2013,GFDLS06,A00}:
+Web application defenses 
+crucially have to capture the presence of an attack. This, however, does not
+make a defense mechanism immediately useful. A
+detection mechanism must also be reliable.
+Detection accuracy is gauged with the following
+metrics~\cite{TDR2013,GFDLS06,A00}.
 \begin{itemize}
-\item {\bf Sensitivity}, the probability that an attack will be
+\item {\bf Sensitivity}: the probability that an attack will be
   caught.
-\item {\bf Specificity}, the probability that a normal interaction
-  will test negative.
-\item {\bf Positive Predictive Value} ({\sc ppv}), the probability that a
+\item {\bf Specificity}: the probability that a normal interaction
+  will not be flagged.
+\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
   reported attack is a real attack. It is the conditional probability
@@
   such. 
-\item {\bf Negative Predictive Value} ({\sc npv}), the probability that if
-  nothing is reported no attack has taken place. It is the conditional
+\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
+  nothing is reported, no attack has taken place. It is the conditional
   probability that an event is not an attack given that the detection
@@
 \textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
-Sensitivity and specifity are defined using the following~\cite{linn2004}:
+Sensitivity and specifity are defined as follows~\cite{linn2004}.
 \begin{itemize}
-\item True Positive (\textsc{tp}), an attack that raises an alarm.
-\item True Negative (\textsc{tn}), an event that is not an attack and that does
+\item True Positive (\textsc{tp}): an attack that raises an alarm.
+\item True Negative (\textsc{tn}): an event that is not an attack and that does
   not raise an alarm.
-\item False Positive (\textsc{fp}), an event that although it is not an attack
+\item False Positive (\textsc{fp}): an event that although it is not an attack,
   raises an alarm.
-\item False Negative (\textsc{fn}), an event that although is as attack does
+\item False Negative (\textsc{fn}): an event that although is an attack, does
   not raise an alarm.
@@
 Sensitivity and specificity can be calculated based on test
-data alone. To calculate the sensitivity, we run the test on a
+data alone. To calculate sensitivity, we run the test on a
 controlled environment where we allow only attack events to reach the
@@
 
-To ensure replicability of research results the source code
+To ensure reproducibility of research results, the source code
 implementing a detection mechanism should be available to researchers.
@@
 
-All detection mechanisms extract a cost for their use, as they
-introduce some amount of extra computation on an existing application.
-The extra computation depends on the exact defense mechanism. For
-example, it may be some form of run-time checking, or some form of
-obfuscation. Also depending on the mechanism, the cost may be incurred
-on different places: it may take place on a server, affecting service
-performance, or it may take place on the client, or both. The
+Detection mechanisms may impose a cost due to their use, as they
+typically introduce some amount of extra computation on a existing applications.
+The overhead depends on the specifics of each mechanism. For
+example, it may be due to some form of run-time checking, or some form of
+obfuscation. Also, depending on the approach, the cost may be incurred
+on different places: it may affect a server
+(e.g., its memory or CPU usage, processing throughput, or response latency),
+it may affect the client, or both. The
 usefulness of a detection mechanism depends therefore on the
-computational cost it requires and on where it extracts it, as
-different overheads may be acceptable server-side than client-side.
+computational cost it requires and on where it imposes it, as
+different overheads may be acceptable at the server side than the client side.
 
 What kind of numbers is reported matters as well. Reporting absolute
-measurements gives little information on the real overhead, unless
+measurements gives little information on the actual overhead, unless
 separate measurements are given for the system under study with and
@@
 performance evaluation analysis for a defense mechanism, the more
-performance evaluation is provided for a mechanism the more valuable
+evaluation results are provided for a mechanism, the more valuable
 it becomes as a practical approach.
@@
 The value of a detection mechanism as a practical tool depends on how
-it is to deploy it in a production setting. That is independent of the
+easy it is to deploy it in a production setting. This aspect is
+orthogonal to the
 value of a detection mechanism as a research finding. Devising a
-mechanism to detect a hitherto undetectable class of attacks may be an
+technique to detect a hitherto undetectable class of attacks may be an
 excellent research contribution that merits publication; it may also
@@
 
-Ease of use depends on the deployment protocol required for the
-mechanism. The detection mechanism may be deployed server-side or
-client-side, or both. Deployments on just the server or the client are
+Ease of use depends on the deployment process required for the
+mechanism. The detection mechanism may be deployed at either or both
+the server and the client side. Deployments on just the server or the client are
 easier to handle than deployments on both of them. The mechanism may
-be an add-on, or plugin, on existing software, client or server, or it
+be an add-on or plugin for existing software, client or server, or it
 may be tightly integrated with existing software, requiring rebuilding
@@
 
-No matter where it gets installed, the means of installation influences
-ease of use. A detection mechanism that comes with ready to install
-packages will trump a detection mechanism that only exists in the form
+No matter where it is installed, the means of installation influences
+ease of use. A detection mechanism that is available as a ready-to-install
+package will trump others that only exist in the form
 of source code.
@@
 attacks, and so on. We use security to refer to the ability of a
-detection mechanism to resist being circumvented.
+detection mechanism to resist circumvention.
 
@@
 is possible that a bypass method will be discovered in the future. We
-examine the various approaches on the knowledge we have to this date,
-that is, whether there are known ways to bypass the detection
+examine the various approaches based on the knowledge we have so far,
+that is, whether there are any known ways to bypass the detection
 mechanism today.

### 2014-11-14 docs/questioning.tex
moved fig2 to be closer to secIII
pass in V.A

@@
 
+\begin{figure*}[t]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
+\end{center}
+\caption{\label{fig:attacks}Attack model for dynamic and domain specific
+language code injection in web applications.
+Transitions are labeled with the different attacks that use that path,
+while the numbers next to attack labels denote the 
+sequence of steps for a particular attack.
+Points where different types of defenses
+detect or prevent attacks are marked with an `X' symbol:
+{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
+{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
+{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+\end{figure*}
+
 We provide a step-by-step exploitation model to understand the process
@@
 dictated by the malicious request will be performed.
-
-\begin{figure*}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
-\end{center}
-\caption{\label{fig:attacks}Attack model for dynamic and domain specific
-language code injection in web applications.
-Transitions are labeled with the different attacks that use that path,
-while the numbers next to attack labels denote the 
-sequence of steps for a particular attack.
-Points where different types of defenses
-detect or prevent attacks are marked with an `X' symbol:
-{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
-{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
-\end{figure*}
 
@@
 
-\subsection{Ease of Use}
-\label{sec:deployment}
-
-The value of a detection mechanism as a practical tool depends on how
-easy it is to deploy it in a production setting. This aspect is
-orthogonal to the
-value of a detection mechanism as a research finding. Devising a
-technique to detect a hitherto undetectable class of attacks may be an
-excellent research contribution that merits publication; it may also
-be heavily cited and open the road to other, practical
-implementations in the future.
-
-Ease of use depends on the deployment process required for the
-mechanism. The detection mechanism may be deployed at either or both
-the server and the client side. Deployments on just the server or the client are
-easier to handle than deployments on both of them. The mechanism may
-be an add-on or plugin for existing software, client or server, or it
-may be tightly integrated with existing software, requiring rebuilding
-from source code.
-
-No matter where it is installed, the means of installation influences
-ease of use. A detection mechanism that is available as a ready-to-install
-package will trump others that only exist in the form
-of source code.
-
-\subsection{Security}
-
-Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by canny attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by cannier
-attacks, and so on. We use security to refer to the ability of a
-detection mechanism to resist circumvention.
-
-A mechanism that has not been bypassed is not eternally secure, as it
-is possible that a bypass method will be discovered in the future. We
-examine the various approaches based on the knowledge we have so far,
-that is, whether there are any known ways to bypass the detection
-mechanism today.
-
-\subsection{Point of Detection}
-
-Detection mechanisms vary on the location where they detect an attack.
-There are four different points where an attack can be caught, as seen
-in Figure~\ref{fig:attacks}:
-\begin{itemize}
-\item At the user's browser (Point {\sc ub}).
-\item En route from the server to the user's browser---in most cases
-within a proxy (Point {\sc s}t{\sc b}).
-\item At the database abstraction layer, before it reaches the server's database
-  (Point {\sc dbal}).
-\item After the malicious code reaches the server's database
-  (Point i{\sc db}).
-\end{itemize}
-
-\section{Defenses}
-\label{sec:defs}
-
-\begin{figure*} [ht]
+\begin{figure*}[t]
 \begin{center}
@@
 
-We categorize and describe the various mechanisms developed to detect
-the attacks described in Section~\ref{sec:attacks} and~\ref{sec:model},
-on the dimensions we proposed apart from availability, which we treat
-separately in the discussion in Section (\ref{sec:discussion}).
-All mechanisms have been proposed in publications cited more than
-20 times. We also include some recent mechanisms that have been
-presented in top security conferences, even though they have been
-cited less than twenty times, so that recent research is not penalized.
-
-Figure~\ref{fig:defenses} presents a taxonomy of the
-defenses that protect web applications against code injection attacks.
-We can identify three approaches:
-{\it etiological}, {\it symptomatic}, and {\it hybrid}.
-The etiological category involves mechanisms designed to
-stop attacks based on their causes and origins~\cite{JL75,L81}. 
-The symptomatic category incorporates a variety of schemes that
-inspect the behavior of applications and detect attacks based on
-their undesirable symptoms~\cite{D76,A00}.
-Hybrid mechanisms borrow characteristics from both
-categories. Table~\ref{tab:comp} groups the various subcategories and
-for every mechanism provides the following:
-
-\begin{enumerate}
-\item The number of times the corresponding publication has been cited.
-\item Accuracy and computational overhead measurements.
-\item The attacks that the mechanism detects.
-\end{enumerate}
-
-Recall that the point where attacks are detected is given in the
-caption of Figure~\ref{fig:attacks}.
-
-\subsection{Etiological}
-\label{sec:prot}
-
-There exist three basic etiological approaches used to protect web
-applications from code injection attacks.
-
-\subsubsection{Parse-Tree Validation}
-\label{sec:tree}
-
-The key idea behind parse-tree validation is to compare the tree
-representation of the abstract syntactic structure of the source code
-that is about to be executed with the one that was originally
-intended. If the trees diverge, the application is probably under
-attack.
-
-In the case of {\sc dsl} injection attacks, mechanisms check 
-the query before the inclusion of user input with the one
-resulting after the inclusion of user input.
-Both mechanisms that implement this approach,
-{\sc sqlg}uard~\cite{BWS05} and
-{\sc sql}check~\cite{SW06} are pretty similar
-and detect the attack before a query reaches the
-database (Point {\sc dbal}).
-Contrary to {\sc sqlg}uard and other
-mechanisms, {\sc sql}check has been
-extensively tested in terms of accuracy
-as can be seen in Table~\ref{tab:comp}.
-A disadvantage of those mechanisms is that the
-application must be modified in every code fragment
-that sends an {\sc sql} query to the database for execution.
-
-Parse-tree validation seems to be an efficient approach
-to detect {\sc dsl} code injection attack,
-especially in the case of the {\sc sql}check
-implementation. This however does not apply in
-the case of the mechanisms that borrow elements from
-this approach and examine the syntax trees
-of scripts to detect JavaScript-driven {\sc xss} attacks,
-as we will see in Subsection~\ref{sec:hybrid}.
-
-\subsubsection{Policy Enforcement}
-\label{sec:policy}
-
-This approach is used to detect {\sc xss} and {\sc csrf} attacks. When
-using a framework that implements policy enforcement, developers must
-define specific security policies on the server side. Policies can be
-expressed through JavaScript extensions, pattern matching, or syntax
-specific settings. Then the policies are enforced either in the user's
-browser at runtime or in a server-side proxy that intercepts server
-responses.
-
-Noxes~\cite{KKVJ06,KJKV09} is the only
-framework that partially allows the web
-user to specify policies to prevent {\sc xss} attacks.
-The key idea behind Noxes is to parse
-the {\sc html} response that reaches the browser to
-find static {\sc url} references. Then, based on
-a set of policies Noxes allows or blocks
-the request (Point {\sc ub}). Such policies
-can be also provided by the server (i.e., ``never
-follow a link that leads to the malicious.com
-web site''). The main issue with Noxes is that
-{\sc url}s can be dynamically assembled by scripts
-which may lead to false alarms.
-
-A number of the frameworks define policies based on information and
-features provided by the Document Object Model ({\sc dom}) of a web
-page. Specifically, developers must place all legitimate scripts
-inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
-  ub}), parses the {\sc dom} tree and executes scripts only when they
-are contained in such elements. All other scripts are treated
-according to the policies defined on the server. Frameworks that
-support this functionality are {\sc beep}~\cite{TNH07} and {\sc
-  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
-they do not examine the script's location inside the web document.
-Based on this fact, attackers can perform mimicry attacks~\cite{WS02}.
-Specifically, they can execute legitimate scripts, but not as intended
-by the original design of the developers. This is extensively
-described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
-another recent variation of JavaScript injection attacks, known as
-return-to-JavaScript attacks that can be used to bypass the above
-mechanisms.
-
-Another policy enforcement approach introduces
-policies directly either in {\sc html} or JavaScript code
-to confine their behavior. BrowserShield~\cite{RDWDE07}
-acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
-parse the {\sc html} of server responses and identify
-scripts. Then, it rewrites them into safe equivalents
-and protects the web user from exploits
-that are based on reported browser vulnerabilities.
-ConScript~\cite{ML10}, CoreScript~\cite{YCIS07}
-and the framework by Phung et al.~\cite{PSC09}
-extend JavaScript with new primitive functions that
-provide safe methods to protect potentially vulnerable
-JavaScript functions. In both cases, policy enforcement takes
-place on the JavaScript engine of the browser (Point {\sc ub}).
-In this way, {\sc xxs} attacks that take advantage
-functions like {\tt write} and {\tt eval}, which are
-used to assemble innocuous-looking parts into harmful
-strings,\footnote{The infamous Sammy worm that
-infected MySpace in 2005~\cite{SP07,ELX07}
-utilized the {\tt eval} function to assemble a
-script with malicious behavior.} would fail.
-
-An issue regarding the above frameworks
-involves features like script inclusion
-and {\tt iframe} tags. Even though they allow developers
-decide if they will disable them or not,
-this is unpractical because such features are quite popular.
-If developers choose to use them, these frameworks cannot
-define policies that restrict the behavior of third-party
-scripts introduced by such features. Thus, they would
-be vulnerable in an attack that utilizes {\tt iframes}
-in the way we described in Section~\ref{sec:attacks}.
-\noindent WebJail~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
-are two frameworks that can actually detect such an attack (Point {\sc
-  ub}). To achieve this, {\sc soma} requires site administrators to
-specify legitimate, external domains for sending or receiving
-information in order to approve interactions between them and the
-protected web site. As a result, {\sc soma} can also detect {\sc csrf}
-attacks. WebJail contains the functionality of third-party scripts by
-introducing a web component integrator that restricts the access that
-these scripts may have to either the data or the functionality of
-other components.
-
-Policy enforcement mechanisms that detect {\sc csrf}
-attacks are usually implemented in the form of a
-server-side proxy (Point {\sc s}t{\sc b})
-interposed on the client-server communication and modifying
-it. NoForge~\cite{JKK06a}
-parses the {\sc html} server responses
-and adds a token to every {\sc url} referring to this
-server. Then it associates the token with the cookie
-representing the session {\sc id} for the application.
-When a request is received, the mechanism checks
-if the request contains the token related
-to the session {\sc id}. A disadvantage of NoForge
-is that {\sc html} that is dynamically created within
-the browser will not include the token.
-Thus, sites that create their {\sc html} on the client
-will remain vulnerable. In addition, it does not
-support cross-origin requests.
-j{\sc csrf}~\cite{PS11} has a similar
-functionality and meanwhile addresses the above problems.
-Finally, CsFire~\cite{DDHPJ10}
-examines cross-domain interactions, to design a
-cross-domain policy on the client's side (Point {\sc ub}).
-The policy is based on the concept of a relaxed
-same-origin policy that allows communication between
-sub-domains of the same registered domain.
-
-Most of the aforementioned frameworks involve
-several deployment issues since they
-require significant source modifications by the
-developers on the server-side in order to
-introduce the policies.
-
-\subsubsection{Instruction Set Randomization (ISR)}
-
-{\sc isr} is a method that has been applied to counter different kinds
-of application attacks~\cite{K09b,KKP03}. The main idea behind it is
-to separate code from data by randomizing the legitimate code's
-execution environment. In this way, the malicious code injected by the
-attackers who do not know the randomization algorithm will not get
-executed.
-
-{\sc sql}rand~\cite{BK04} implements {\sc isr} to detect {\sc
-  sql} injection attacks. It allows programmers to create {\sc sql}
-statements using randomized instructions instead of standard keywords.
-The modified queries are reconstructed at runtime using the same key
-used for randomization, which is inaccessible to the malicious user.
-{\sc sql}rand is one of the few mechanisms that detect {\sc sql}
-injection attacks on the database level (Point i{\sc db}).
-
-In the case of {\sc xss} attacks that are based on JavaScript or {\sc
-  html}, consider a {\sc xor} function that encodes all source of a
-web page on the server-side and then, on the client-side, the web
-browser decodes the source by applying the same function again either
-in a proxy at the server-side (Point {\sc s}t{\sc b}) or in the browser
-(Point {\sc ub}). Variations of this approach include
-Noncespaces~\cite{GC09} and x{\sc js}~\cite{APKLM10}, which
-randomize the instruction set of {\sc html} and JavaScript
-respectively. Contrary to x{\sc js}, in Noncespaces administrators
-must set specific policies in a manner similar to a firewall
-configuration language. {\sc sm}ask~\cite{JB07} is another
-framework that was inspired by {\sc isr}. To detect {\sc xss}
-attacks it searches for {\sc html} and
-JavaScript keywords within the application's legitimate code. This is
-done before the processing of an {\sc http} request. When it finds one
-it adds a token to it. This results to a ``code mask.'' Then, before
-sending the resulting {\sc html} data to the web user, the framework
-searches the data for illegal code by using the same keywords (Point
-{\sc s}t{\sc b}). Since all legitimate code has been ``masked,'' the injected
-code can be identified. The pre- and post-processing of the code,
-though, may add a significant overhead to the application.
-Unfortunately, the authors of {\sc sm}ask did not provide measurements
-regarding the computational performance of the tool (see
-Table~\ref{tab:comp}).
-
-{\sc isr} is a deterministic approach that can be applied to detect
-different attacks in an efficient manner. However, Sovarel et
-al.~\cite{SEP05} have investigated thoroughly the effectiveness of
-{\sc isr} and showed that a malicious user may be able to circumvent
-it by determining the randomization key. Their results indicate
-that doing {\sc isr} in a way that provides a certain degree of
-security against a motivated attacker is more difficult than
-previously thought. Furthermore, developers who wish to use such
-mechanisms must follow good coding practices and never show a
-randomized code statement in any case (i.e., an exception error)
-because in this way they will reveal the encoding key.
-
-Even though the above implementations impose a low computational
-overhead, they impose a deployment infrastructure overhead. In particular, in
-{\sc sql}rand requires the integration of a proxy within the database
-server, while Noncespaces and x{\sc js} require modifications on both
-the server and the client.
-
-\begin{table*}
+\subsection{Ease of Use}
+\label{sec:deployment}
+
+The value of a detection mechanism as a practical tool depends on how
+easy it is to deploy it in a production setting. This aspect is
+orthogonal to the
+value of a detection mechanism as a research finding. Devising a
+technique to detect a hitherto undetectable class of attacks may be an
+excellent research contribution that merits publication; it may also
+be heavily cited and open the road to other, practical
+implementations in the future.
+
+Ease of use depends on the deployment process required for the
+mechanism. The detection mechanism may be deployed at either or both
+the server and the client side. Deployments on just the server or the client are
+easier to handle than deployments on both of them. The mechanism may
+be an add-on or plugin for existing software, client or server, or it
+may be tightly integrated with existing software, requiring rebuilding
+from source code.
+
+No matter where it is installed, the means of installation influences
+ease of use. A detection mechanism that is available as a ready-to-install
+package will trump others that only exist in the form
+of source code.
+
+\subsection{Security}
+
+Defenders and attackers are often caught in a cat-and-mouse game,
+where countermeasures are bypassed by canny attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by cannier
+attacks, and so on. We use security to refer to the ability of a
+detection mechanism to resist circumvention.
+
+A mechanism that has not been bypassed is not eternally secure, as it
+is possible that a bypass method will be discovered in the future. We
+examine the various approaches based on the knowledge we have so far,
+that is, whether there are any known ways to bypass the detection
+mechanism today.
+
+\subsection{Point of Detection}
+
+Detection mechanisms vary on the location where they detect an attack.
+There are four different points where an attack can be caught, as seen
+in Figure~\ref{fig:attacks}:
+\begin{itemize}
+\item At the user's browser (Point {\sc ub}).
+\item En route from the server to the user's browser---in most cases
+within a proxy (Point {\sc s}t{\sc b}).
+\item At the database abstraction layer, before it reaches the server's database
+  (Point {\sc dbal}).
+\item After the malicious code reaches the server's database
+  (Point i{\sc db}).
+\end{itemize}
+
+\section{Defenses}
+\label{sec:defs}
+
+\begin{table*}[t]
+  \renewcommand{\baselinestretch}{1.12}
     \caption{Comparison summary of mechanisms developed to counter application attacks based on code injection.}
@@
   \begin{footnotesize}
-        \item[1] {\sc na} (Not Available) means that a requirement is not mentioned in the paper.
+        \item[1] {\sc na} (Not Available) indicates that a requirement is not mentioned in the paper.
   {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the\newline publication
-  but it is not quantified.
-      \item[2] Quadruples contain numbers given for True Positives
+  but is not quantified.
+      \item[2] Tuples contain numbers given for True Positives
         ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
-          fp}) and False Negatives ({\sc fn}). For every quadruple\newline there is a corresponding suffix that indicates whether the testbed was
-  based on: a) real-world applications known to be vulnerable ({\it r}), b) synthetic\newline benchmarks ({\it s}), c) both ({\it a}).
-  If no testing has taken place we add a question mark ({\bf ?}).
-    \item[3] Regarding the computational overhead we show if it is applied to the server ({\sc s}) or the client ({\sc c}). 
+          fp}) and False Negatives ({\sc fn}). For every tuple\newline there is a corresponding suffix that indicates whether the testbed was
+  based on: real-world applications known to be vulnerable ({\it r}),
+  synthetic\newline benchmarks ({\it s}), or both ({\it a}).
+  A question mark ({\bf ?}) denotes that no test results are reported.
+    \item[3] Whether the overhead is incurred on the server ({\sc s}) or the client ({\sc c}). 
     \item[4] {\it i} stands for injection.
-    \item[5] The numbers of this quadruple involve requests.
+    \item[5] The numbers in this particular case involve requests.
   \end{footnotesize}
@@
 \end{table*}
+
+We categorize and analyze a large set of defenses developed to detect
+and prevent
+the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
+We perform our analysis across
+the dimensions discussed in the previous section,
+except from availability, which we treat
+separately in Section~\ref{sec:discussion}.
+Due to the immense number of published works in the area, we only consider
+defenses that have been proposed in publications cited more than
+20 times according to Google Scholar.
+We also include some recent works that have been
+presented in top security conferences, even though they have been
+cited less than twenty times, so that recent research is not penalized.
+
+Figure~\ref{fig:defenses} presents a taxonomy of 
+web application defenses against injection attacks.
+We can identify three broad categories:
+{\it etiological}, {\it symptomatic}, and {\it hybrid}.
+The etiological category involves mechanisms designed to
+block attacks based on their causes and origins~\cite{JL75,L81}. 
+The symptomatic category incorporates a variety of schemes that
+inspect the behavior of applications and detect attacks based on
+their undesirable symptoms~\cite{D76,A00}.
+Hybrid mechanisms borrow characteristics from both
+categories. Table~\ref{tab:comp} lists the specific mechanisms we consider
+in this work, grouped according to the subcategories shown in
+Figure~\ref{fig:defenses}, and for each mechanism
+provides the following information:
+
+\begin{enumerate}
+\item Number of citations of the corresponding publication(s).
+\item Accuracy and computational overhead measurements.
+\item Types of attacks handled.
+\end{enumerate}
+
+\noindent
+Recall that the point of operation for each mechanism is provided
+in the caption of Figure~\ref{fig:attacks}.
+
+\subsection{Etiological}
+\label{sec:prot}
+
+There are three main categories of etiological approaches used to protect web
+applications against injection attacks:
+\emph{Parse-Tree Validation},
+\emph{Policy Enforcement}, and
+\emph{Instruction Set Randomization (ISR)}.
+
+\subsubsection{Parse-Tree Validation}
+\label{sec:tree}
+
+The key idea behind parse-tree validation is to compare the tree
+representation of the abstract syntactic structure of the source code
+that is about to be executed with the one that was originally
+intended. If the trees diverge, the application is probably under
+attack.
+
+For domain-specific language code injection attacks, mechanisms check 
+the query before the inclusion of user input with the one
+resulting after the inclusion of user input.
+Two mechanisms that implement this approach for protection against {\sc SQL}
+injection attacks,
+{\sc sqlg}uard~\cite{BWS05} and
+{\sc sql}check~\cite{SW06}, are quite similar
+and detect the attack before a query reaches the
+database (Point {\sc dbal}).
+Contrary to {\sc sqlg}uard,
+% mikepo: if others exist, cite them
+%and other mechanisms,
+{\sc sql}check has been
+extensively tested in terms of accuracy,
+as can be seen in Table~\ref{tab:comp}.
+A disadvantage of these mechanisms is that the
+application must be modified in every code fragment
+that sends an {\sc sql} query to the database for execution.
+
+Parse-tree validation is an effective approach
+for the detection of {\sc dsl} code injection attacks,
+especially as implemented in {\sc sql}check.
+This is not however the case
+for mechanisms that borrow elements from
+this approach and examine the syntax trees
+of scripts to detect JavaScript-driven {\sc xss} attacks,
+as we will see in Section~\ref{sec:hybrid}.
+
+\subsubsection{Policy Enforcement}
+\label{sec:policy}
+
+This approach is used to prevent {\sc xss} and {\sc csrf} attacks. When
+using a framework that implements policy enforcement, developers must
+define specific security policies on the server side. Policies can be
+expressed through JavaScript extensions, pattern matching, or
+syntax-specific settings. The policies are then enforced either in the user's
+browser at runtime, or on a server-side proxy that intercepts server
+responses.
+
+Noxes~\cite{KKVJ06,KJKV09} is the only
+framework that partially allows
+users to specify policies for the prevention of {\sc xss} attacks.
+The key idea behind Noxes is to parse
+the {\sc html} response that reaches the browser and
+find static {\sc url} references. Then, based on
+a set of policies, Noxes allows or blocks
+any generated requests (Point {\sc ub}). Such policies
+can also be provided by the server (i.e., ``never
+follow a link that leads to the malicious.com
+web site''). The main issue with Noxes is that
+{\sc url}s can be dynamically assembled by scripts,
+which may lead to false alarms.
+
+Some frameworks define policies based on information and
+features provided by the Document Object Model ({\sc dom}) of a web
+page. Specifically, developers must place all legitimate scripts
+inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
+  ub}) parses the {\sc dom} tree and executes scripts only when they
+are contained in such elements. All other scripts are treated
+according to the policies defined on the server. Frameworks that
+support this functionality include {\sc beep}~\cite{TNH07} and {\sc
+  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
+they do not examine the script's location inside the web document.
+Attackers can take advantage of this fact to perform mimicry attacks~\cite{WS02}.
+Specifically, they can execute legitimate scripts, but not as intended
+by the original design of the developers. This is extensively
+described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
+another recent variation of JavaScript injection attacks, known as
+return-to-JavaScript attacks, which can be used to bypass the above
+mechanisms.
+
+Another policy enforcement approach introduces
+policies directly either in {\sc html} or JavaScript code
+to confine their behavior. BrowserShield~\cite{RDWDE07}
+acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
+parse the {\sc html} of server responses and identify
+scripts. Then, it rewrites them into safe equivalents
+and protects the web user from exploits
+that are based on reported browser vulnerabilities.
+ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
+and the framework by Phung et al.~\cite{PSC09}
+extend JavaScript with new primitive functions that
+provide safe methods to protect potentially vulnerable
+JavaScript functions. In both cases, policy enforcement takes
+place at client side, in the JavaScript engine of the browser (Point {\sc ub}).
+In this way, {\sc xxs} attacks that take advantage
+of functions such as {\tt write} and {\tt eval}, which are
+used to assemble innocuous-looking parts into harmful
+strings,\footnote{The infamous Sammy worm that
+infected MySpace in 2005~\cite{SP07,ELX07}
+utilized the {\tt eval} function to assemble a
+malicious script.} would fail.
+
+An issue regarding the above frameworks
+involves features like script inclusion
+and {\tt iframe} tags. Even though they allow developers
+to decide if they will disable them or not,
+this is impractical because such features are quite popular and widely used.
+If developers choose to use them, these frameworks cannot
+define policies that restrict the behavior of third-party
+scripts introduced by such features. Thus, they would
+be vulnerable to attacks that use {\tt iframes}
+in the way described in Section~\ref{sec:attacks}.
+WebJail~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
+are two frameworks that can actually detect such attacks (Point {\sc
+  ub}). To achieve this, {\sc soma} requires site administrators to
+specify legitimate, external domains for sending or receiving
+information in order to approve interactions between them and the
+protected web site. As a result, {\sc soma} can also detect {\sc csrf}
+attacks. WebJail contains the functionality of third-party scripts by
+introducing a web component integrator that restricts the access that
+these scripts may have to either the data or the functionality of
+other components.
+
+Policy enforcement mechanisms that detect {\sc csrf}
+attacks are usually implemented in the form of a
+server-side proxy (Point {\sc s}t{\sc b})
+interposed at the client-server communication path.
+NoForge~\cite{JKK06a}
+parses the {\sc html} server responses
+and adds a token to every {\sc url} referring to that particular
+server. Then, it associates the token with the cookie
+representing the session {\sc id} for the application.
+When a request is received, the mechanism checks
+if the request contains the token related
+to the session {\sc id}. A disadvantage of NoForge
+is that  dynamically created {\sc html} within
+the browser will not include the token.
+Thus, sites that create part of their {\sc html} code at client side
+will remain vulnerable. In addition, it does not
+support cross-origin requests.
+The above problems ar addressed by j{\sc csrf}~\cite{PS11},
+which shares similar functionality.
+Finally, CsFire~\cite{DDHPJ10}
+examines cross-domain interactions to design a
+cross-domain policy at the client side (Point {\sc ub}).
+The policy is based on the concept of a relaxed
+same-origin policy that allows communication between
+sub-domains of the same registered domain.
+
+Most of the above frameworks involve
+several deployment hurdles, as they
+require significant source code modifications by the
+developers on the server side to introduce and enforce the applied policies.
+
+\subsubsection{Instruction Set Randomization (ISR)}
+
+{\sc isr} is a method that has been applied to counter different kinds
+of application attacks~\cite{K09b}, and was originally applied for the
+prevention of binary code injection attacks~\cite{KKP03, isr03forrest}.
+The main idea behind {\sc isr} is
+to change the representation of code
+based on a randomly chosen transformation,
+and randomizing the execution environment accordingly.
+In this way, any malicious code injected as part of untrusted input data,
+by attackers who do not know the randomization algorithm,
+will not be executed.
+
+{\sc sql}rand~\cite{BK04} applies the concept of {\sc isr} for the prevention
+of {\sc sql} injection attacks. It allows programmers to create {\sc sql}
+statements using randomized instructions instead of standard keywords.
+The modified queries are reconstructed at runtime using the same key
+used for randomization, which is inaccessible to a malicious user.
+{\sc sql}rand is one of the few mechanisms that prevent {\sc sql}
+injection attacks at the database level (Point i{\sc db}).
+
+The same concept can be applied for protection against
+{\sc xss} attacks that inject JavaScript or {\sc html} code.
+Initially, the trusted code of a web page can be transformed
+to a random representation using a simple function such as {\sc xor}.
+Before being sent to the client (Point {\sc s}t{\sc b}),
+or being processed by the browser (Point {\sc ub}),
+the legitimate code is transformed back to its original form,
+while any additional injected code will be transformed into junk code.
+Variations of this approach include
+Noncespaces~\cite{GC09} and x{\sc js}~\cite{APKLM10}, which
+randomize the instruction set of {\sc html} and JavaScript,
+respectively. Contrary to x{\sc js}, in Noncespaces administrators
+must set specific policies in a manner similar to a firewall
+configuration language. {\sc sm}ask~\cite{JB07} is another
+framework that was inspired by {\sc isr}. To detect {\sc xss}
+attacks, it searches for {\sc html} and
+JavaScript keywords within the application's legitimate code. This is
+done before the processing of any {\sc http} request. When a keyword is found,
+it adds a token to it, resulting in a ``code mask.'' Then, before
+sending the resulting {\sc html} data to the user, the framework
+searches the data for illegal code using the same keywords (Point
+{\sc s}t{\sc b}). Since all legitimate code has been ``masked,'' the injected
+code can be identified. The need for 
+pre-processing and post-processing the code,
+however, may add a significant overhead to the application.
+Unfortunately, the authors of {\sc sm}ask did not provide measurements
+regarding the runtime overhead of the tool (see
+Table~\ref{tab:comp}).
+
+{\sc isr} is a deterministic approach that can be applied to prevent
+different attacks in an effective manner. However, Sovarel et
+al.~\cite{SEP05} have investigated thoroughly the effectiveness of
+{\sc isr} and showed that a malicious user may be able to circumvent
+it by determining the randomization key. Their results indicate
+that applying {\sc isr} in a way that provides a certain degree of
+security against a motivated attacker is more difficult than
+previously thought. Furthermore, developers who wish to use such
+mechanisms must follow good coding practices and make sure that
+randomized code statement are never leaked
+(e.g., as part of an exception error),
+as this may be used to reveal the encoding key.
+
+Even though the above implementations impose a low computational
+overhead, they require significant deployment effort. In particular,
+{\sc sql}rand requires the integration of a proxy within the database
+server, while Noncespaces and x{\sc js} require modifications on both
+the server and the client.
 
@@
 
-\begin{figure}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.47]{defect-percentages.png}
-\end{center}
-\caption{\label{fig:defect_sources}Pie chart showing the sources
-that the used to find vulnerabilities to test
-their mechanisms. We also provide which source was used
-in which publication:
-{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
-{\sc xss}ed.com~\cite{NSS06,APKLM10},
-ha.ckers.org~\cite{TNH07,PSC09,LV09},
-Microsoft~\cite{RDWDE07}.}
-\end{figure}
-
 Table~\ref{tab:comp} indicates that the authors of 3 out of 34 (8.8\%)
@@
 
+\begin{figure}[t]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.47]{defect-percentages.png}
+\end{center}
+\caption{\label{fig:defect_sources}Pie chart showing the sources
+that the used to find vulnerabilities to test
+their mechanisms. We also provide which source was used
+in which publication:
+{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
+{\sc xss}ed.com~\cite{NSS06,APKLM10},
+ha.ckers.org~\cite{TNH07,PSC09,LV09},
+Microsoft~\cite{RDWDE07}.}
+\end{figure}
+
 There are also authors that took a different approach.

### 2014-11-15 docs/questioning.tex
done with V

@@
 
-Symptomatic approaches adopt one of two tacks. They either track
+Symptomatic techniques follow two main approaches. They either track
 untrusted input and ban certain operations on it, or they first learn what
@@
 
-A taint tracking scheme marks untrusted (``tainted'') data (for
-instance, a variable set by a field in a web form) and traces its flow
-through the program. If the variable is used in an expression that
+A taint tracking scheme marks untrusted (``tainted'') data, such as
+a variable set by a field in a web form, and traces its propagation
+throughout the program. If the variable is used in an expression that
 sets another variable, that variable is also marked as untrusted and
 so on. If any of these variables is used in a potentially risky
-command (for example, send the data to a vulnerable ``sink,'' such as
-a database, a file, the network) the scheme may act accordingly.
+operation (e.g., sending the data to a vulnerable ``sink,'' such as
+a database, a file, or the network), the scheme may act accordingly.
 
 Taint tracking is provided as a feature in some programming languages,
-such as Perl and Ruby. By enabling the feature, Perl would refuse to
+such as Perl and Ruby. By enabling this feature, Perl would refuse to
 run code vulnerable to an {\sc sql} injection attack (consider a
@@
 There are different implementations of this approach
-in terms of how the tainted data is marked and observed,
+in terms of how the tainted data is marked and tracked,
 and how attacks are detected.
 For example, Haldar et al.~\cite{HCF05} have implemented
-their scheme for the Java Virtual Machine ({\sc jvm})
+their scheme for the Java Virtual Machine ({\sc jvm}),
 where they instrument various classes. When a
@@
 untrusted data that reach a sink, they search the data for suspicious
-symbols by using regular expressions. {\sc csse}~\cite{PB05}
+symbols using regular expressions. {\sc csse}~\cite{PB05}
 associates tainted data with specific metadata. Such metadata include
@@
 and others. When tainted data reaches a sink, {\sc csse} performs
-syntactic checks based on the aforementioned metadata (Point {\sc dbal}).
+syntactic checks based on its metadata (Point {\sc dbal}).
 {\sc php} Aspis~\cite{PMP11} works in a similar way. To obtain
@@
 Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
-if there are tainted data that contain scripts (Point {\sc s}t{\sc b}).
+if there is any tainted data that contains scripts (Point {\sc s}t{\sc b}).
 
@@
 Vogt et al.~\cite{VFJKKV07} have developed a tainting scheme
-that follows a different approach. Contrary to the aforementioned
-schemes that operate on the server side, they track sensitive
-information on the client side (Point {\sc ub}). This is a form of
-positive taint tracking, where taint data is considered to be
+that follows a different approach. In contrast to the above
+schemes, which operate on the server side, their technique tracks sensitive
+information at the client side (Point {\sc ub}). This is a form of
+positive data flow tracking, where tagged data is considered to be
 legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
@@
 site from which it came from.
+
 Stock et al.~\cite{SLMS14} propose a scheme that also operates
@@
 environment so that the client-side code runs in an unanticipated
-manner even if the {\sc http} response that triggers the injection
-seems legitimate. The scheme is different from the previous one
+manner, even if the {\sc http} response that triggers the injection
+seems legitimate. This scheme is different from the previous one
 because it marks and observes data that are considered harmful.
@@
 tracks the flow of attacker-controlled data. To detect potential
-attacks the scheme utilizes {\sc html} and JavaScript parsers that can
+attacks, the scheme uses {\sc html} and JavaScript parsers that can
 identify the generation of code coming from tainted data.
@@
 intrusion detection framework~\cite{Den87}. In particular, a training
-mechanism registers all valid legitimate code statements during a
+mechanism learns all valid legitimate code statements during a
 training phase (mostly in the form of signatures). This can be done in
-various ways according to the implementation. Then, only those
+various ways depending on the implementation. Then, only those
 statements will be recognized and approved for execution during
@@
 Training methods that detect {\sc dsl}-driven injection attacks
-generate and store valid code statements (i.e., {\sc sql} or {\sc
+generate and store valid code statements (e.g., {\sc sql} or {\sc
   xp}ath queries) in various forms, and detect attacks as outliers
 from the set of valid code statements. An early approach,
-{\sc didafit}~\cite{LLW02} detects {\sc sql} injection (Point
-{\sc sdb}) attacks by recording all database transactions
+{\sc didafit}~\cite{LLW02}, detects {\sc sql} injection attacks (Point
+{\sc sdb}) by recording all database transactions
 stripped from user input. Subsequent
-refinements by Valeur et al.~\cite{VMV05} tagged each transaction with
+refinements by Valeur et al.~\cite{VMV05} tag each transaction with
 the corresponding application as an extension of their anomaly
@@
 signatures generated during a training phase are based on features
-that can depend either on the code statement or on its execution
-environment (i.e., the stack trace). Then, at runtime, the mechanism
+that can depend either on code statements or on their execution
+environment (e.g., the stack trace). Then, at runtime, the mechanism
 checks all statements for compliance and can block code statements
@@
 forwards the request to the client. This mechanism is relatively
-inflexible since it does not support dynamic scripts. In addition it
+inflexible since it does not support dynamic scripts. In addition, it
 imposes a significant overhead (see Table~\ref{tab:comp}). The authors
@@
 that also supports dynamic and external scripts. Specifically, during the
-training phase they build a list of all benign scripts. In the case of
-external scripts they keep a white list of all the valid domain names
+training phase, they build a list of all benign scripts. For
+external scripts, they keep a whitelist of all the valid domain names
 that contain scripts used by the application.
@@
 
-Mechanisms that create signatures that involve elements not only
-associated with the code statements (i.e., {\sc amnesia} and {\sc
+Mechanisms based on signatures that involve elements not only
+associated with code statements (e.g., {\sc amnesia} and {\sc
   sd}river) could detect such attacks. Specifically, {\sc sd}river
@@
 statement, thus it can correlate queries with their call sites and
-detect attacks like the aforementioned one. Furthermore, training
+detect attacks like the above. Furthermore, training
 tools that detect {\sc xss} attacks based on JavaScript injection
 would fail to detect mimicry attacks where legitimate scripts can be
-executed by attackers, but not in the way intended by the the
+executed by attackers, but not in the way intended by the
 developers~\cite{APKLM10}.
@@
 In general, the detection accuracy of training approaches is heavily
-based on the coverage that is achieved during the training phase. If
+influenced by the coverage that is achieved during the training phase. If
 the coverage is insufficient false alarms are very likely. In
@@
 This category includes mechanisms that borrow
-characteristics from both of the above categories.
+characteristics from both etiological and symptomatic approaches.
 Two of them focus on the detection of {\sc xss}
-attacks and one of them focuses on {\sc dsl} code
-injection attacks.
+attacks and one focuses on {\sc dsl} code injection attacks.
 
@@
 current date and the length of the array that contains the references
-of the various images to be displayed. Then, based on this value it
+of the various images to be displayed. Then, based on this value, it
 shows a specific image to a user. In a vulnerable web site that allows
@@
 %% PL You mean like the rotator?
-In this script the attacker could also include references to tiny
-images hosted on a web server that is maintained by him in order to
+In this script, attackers could also include references to tiny
+images hosted on a web server that is maintained by them in order to
 retrieve the {\sc ip} addresses of the users that visit the vulnerable
@@
 uses parsed trees to detect {\sc xss} attacks. To guarantee
-that untrusted content is not executed, Blueprint generates on the
-server-side a parsed tree from untrusted {\sc html} to ensure that it
-does not contain any dynamic content. Then the parsed tree is
+that untrusted content is not executed, Blueprint generates at the
+server side a parsed tree from untrusted {\sc html} to ensure that it
+does not contain any dynamic content. Then, the parsed tree is
 transfered to the document generator of the browser (Point {\sc ub}),
 where untrusted browser parsing behavior is ruled out.
-Blueprint is an efficient countermeasure but it imposes an
+Blueprint is an efficient countermeasure but imposes non-negligible
 overhead due to its extensive parsing (see Table~\ref{tab:comp}).
@@
   json} injection attacks. When an application computes an output
-string (query), Diglossia computes a ``shadow'' of this string.
+string (query), Diglossia computes a ``shadow'' of that string.
 Specifically, it maps all characters introduced by the application to
@@
 the query that is about to be executed and compares it with the parsed
-tree of the ``shadow'' (Point {\sc dbal}). If the trees are not
-equal the application is probably under attack. Note that Diglossia
+tree of the ``shadow'' (Point {\sc dbal}). If the trees do not match,
+the application is probably under attack. Note that Diglossia
 can be bypassed in the same way as other taint tracking

### 2014-11-15 docs/questioning.tex
adding CSP - the observations should be updated though

@@
 detect or prevent attacks are marked with an `X' symbol:
-{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
+{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
 {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
@@
 that present corresponding mechanisms:
-{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08},
+{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
 {\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
@@
   \hline
-  \multirow{12}{*}{Policy Enforcement}
+  \multirow{13}{*}{Policy Enforcement}
   &   {\sc dsi}~\cite{NSS06} & 135 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
@@
   &   CsFire~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
+  &   {\sc csp}~\cite{SSM10} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
   &   j{\sc csrf}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
@@
 
+A policy enforcement technique developed by Mozilla,
+called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
+is currently supported by many browsers to detect
+{\sc xss} and {\sc csrf} attacks. To eliminate such
+attacks, web site administrators
+can specify which domains the browser should treat
+as valid sources of script and which not. Then, the browser
+(Point {\sc ub}) will only execute scripts that exist in
+source files from white-listed domains.
+
 Another policy enforcement approach introduces
@@
 require significant source code modifications by the
-developers on the server side to introduce and enforce the applied policies.
+developers on the server side to introduce and enforce
+the applied policies.
 
@@
   \hline
-  \multirow{12}{*}{Policy Enforcement}
+  \multirow{13}{*}{Policy Enforcement}
   &   {\sc dsi}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
@@
   &   CsFire~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
+  &   {\sc csp}~\cite{SSM10} & {\bf AO} & {\bf AO} & {\sc na} \\
   &   j{\sc csrf}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
@@
 
-We group our key observations on the~34 publications along the
+We group our key observations on the~35 publications along the
 dimensions we identified in Section~\ref{sec:dimensions}.
@@
 (for instance, {\sc html} sanitization and {\tt eval} handling)
-with supported frameworks like Mozilla's Content Security
-Policy~\cite{cspMoz} ({\sc csp}) and Google Caja~\cite{M06,caja}
+with supported frameworks like Mozilla's {\sc csp}
+and Google Caja~\cite{M06,caja}
 the majority of them are not used in practice.

### 2014-11-15 docs/questioning.tex
table II fixes

--- 2014-11-15 docs/questioning.tex
@@
 \begin{table*}
-\caption{Availability of the corresponding mechanisms.}
+\caption{Availability of the studied defenses.}
     \label{tab:avail}
@@
   \thickhline
-    \end{tabular}}
-    \begin{tablenotes}
+
+    \multicolumn{5}{p{13cm}}{%
   \begin{footnotesize}
-       \item[1] The check mark (\tick) indicates that the publication
+       $^\textsuperscript{1}$The check mark (\tick) indicates that the publication
        includes a homepage where the reader can 
@@
        in the publication but now it is not available.
-  \end{footnotesize}
-    \end{tablenotes}
+  \end{footnotesize} } \\
+    \end{tabular}}
     \end{small}
@@
 
-We group our key observations on the~34 publications along the
+We group our key observations on the~34 publications that
+we considered in this work along the
 dimensions we identified in Section~\ref{sec:dimensions}.

### 2014-11-15 docs/questioning.tex

@@
 
-We group our key observations on the~34 publications that
+We group our key observations on the~35 publications that
 we considered in this work along the

### 2014-11-15 docs/questioning.tex
tweaks in listings

@@
 \usepackage{array}
+\usepackage{courier}
 
 \usepackage[numbers,sort]{natbib}
+
 \lstset{columns=flexible,showstringspaces=false}
+\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
 
@@
 
-\section{Code Injection Attacks\\in Web Applications}
+\section{Code Injection Attacks in Web Applications}
 \label{sec:attacks}
@@
 
-\bgroup \lstset{language=SQL}
-\begin{small}
+\lstset{language=SQL}
 \begin{lstlisting}
@@
 \end{lstlisting}
-\end{small}
-\egroup
 
@@
 
-\bgroup \lstset{language=HTML}
-\begin{small}
+\lstset{language=HTML}
 \begin{lstlisting}
-<img src='http://www.vulnerable.com/
-  admin.php?edituserwithID=13&addgroup=admin'/>
+<img src='http://www.vulnerable.com/admin.php?edituserwithID=13&addgroup=admin'/>
 \end{lstlisting}
-\end{small}
-\egroup
 
@@
 
-\lstset{language=VBScript, basicstyle=\footnotesize\ttfamily,}
+\lstset{language=HTML}
 \begin{lstlisting}
-http://example.com/vulnerable.html?query=
-<iframe src="javascript:document.body.innerHTML=+
-'<img src=\"http://malicious.com/?c=
-'+encodeURIComponent(document.cookie)+'\">'">
-</iframe>
+http://example.com/vulnerable.html?query=<iframe src="javascript:document.body.innerHTML=+'<img src=\"http://malicious.com/?c='+encodeURIComponent(document.cookie)+'\">'"></iframe>
 \end{lstlisting}
@@
 
-\bgroup \lstset{language=PHP}
-\begin{small}
+\lstset{language=PHP}
 \begin{lstlisting}
@@
 
-\bgroup
 \lstset{language=SQL}
-\begin{small}
 \begin{lstlisting}
-SELECT password from userdata WHERE id = 'Alice' OR
-id = 'admin'
+SELECT password from userdata WHERE id = 'Alice' OR id = 'admin'
 \end{lstlisting}
-\end{small}
-\egroup
 

### 2014-11-15 docs/questioning.tex
updated observations - now with CSP

@@
 {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
@@
 
+\noindent
 We will focus on sensitivity and specificity; we will come back to
@@
 on different places: it may affect a server
-(e.g., its memory or CPU usage, processing throughput, or response latency),
+(e.g., its memory or {\sc cpu} usage, processing throughput, or response latency),
 it may affect the client, or both. The
@@
 \item After the malicious code reaches the server's database
-  (Point i{\sc db}).
+  (Point {\sc db}).
 \end{itemize}
@@
 {\sc sql}rand is one of the few mechanisms that prevent {\sc sql}
-injection attacks at the database level (Point i{\sc db}).
+injection attacks at the database level (Point {\sc db}).
 
@@
 
-Table~\ref{tab:comp} indicates that the authors of 3 out of 34 (8.8\%)
+Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
 publications provided complete quadruples of {\sc tp}, {\sc tn}, 
 {\sc fp}, and {\sc fn}. On the other hand, we
-see that 4 out of 34 (11.7\%) were not tested at all. In these cases,
-all the four elements of the quadruples are not available ({\sc na}).
-An interesting observation is that in 10 out of the 34 (29.41\%)
+see that 4 out of 35 (11.4\%) were not tested at all.
+In these cases, all the four elements of the quadruples
+are not available ({\sc na}). An interesting observation is
+that in 10 out of the 35 (28.5\%)
 publications, the authors performed only attacks during their tests
@@
 with the need to have large samples in order to be able to use the
-central limit theorem~\cite{agresti1998,brown2001}. However, sample sizes in the single
+central limit theorem~\cite{agresti1998,brown2001}.
+However, sample sizes in the single
 digits are not enough to produce good intervals.
 
-Regarding the subjects of tests, we see that 27 out of 34 mechanisms
-were tested on real-world applications known to be vulnerable. The
-vulnerabilities associated with these applications are enlisted in the
-following providers: the Common Vulnerabilities and Exposures ({\sc
-  cve}) database~\cite{cve}, the Bugtraq security
-mailing list~\cite{bugtraq}, the {\sc xss}ed.com
+Regarding the subjects of tests, we see that 27 out of 35 (77.1\%)
+mechanisms were tested on real-world applications known to be
+vulnerable. The vulnerabilities associated with these applications
+are enlisted in the following providers: the Common
+Vulnerabilities and Exposures ({\sc cve}) database~\cite{cve},
+the Bugtraq security mailing list~\cite{bugtraq}, the {\sc xss}ed.com
 security bulletin provider~\cite{xssed}, Microsoft's security
@@
 
-% Comment 1: Regarding the frameworks that were
-% not tested in terms of diagnostic performance
-% at all, we see that they are mostly coming from
-% the etiological category.
-
-% Comment 2: Note though that implementations
-% of etiological mechanisms can actually
-% be bypassed.
-
-% Comment 3: The above are some extra findings that
-% indicate that there is no standard way to
-% test such mechanisms. Perhaps, forming a
-% standard way to test such tools in terms
-% of diagnostic and computational performance
-% would be one of the reasons of adopting them.
-
 \subsection{Availability}
@@
 executables. We also examined the availability of the testbeds
-mentioned in the paper. We see that only 6 out of 34 (17.6\%) of the
+mentioned in the paper. We see that only 6 out of 35 (17.1\%) of the
 pubications provided a homepage for their mechanism and 2 from these 6
@@
 the source code or their executables available after their paper got
-published. Regarding the availability of test materials, we see that
-only 3 out of 34 (8.8\%) publications have currently their testbeds
+published. In one case ({\sc csp}) the source was available before the
+publication through the Mozilla community.
+Regarding the availability of test materials, we see that
+only 3 out of 35 (8.5\%) publications have currently their testbeds
 available on-line.
@@
 server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
-the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
-percentage, while in other cases, 7 our of 34 (20.5\%), the authors
+the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
+percentage, while in other cases, 7 our of 35 (20\%), the authors
 provide the time (in terms of ms) that their mechanisms add to the
@@
 so it is not possible to move from absolute
-time measurements to percentage overheads. In 10 cases (29.4\%), the
+time measurements to percentage overheads. In 10 cases (28.5\%), the
 overhead was either not available ({\sc na}) or not quantified ({\sc
@@
 attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms}---Point i{\sc db}.
+of the {\sc rdbms}---Point {\sc db}.
 The other 11 wrap {\sc api} calls related to output
@@
 attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client side: in particular, 13 out of 23
-frameworks (56,5\%) detect {\sc xss} attacks on the
+perform detection on the client side: in particular, 14 out of 24
+frameworks (58,3\%) detect {\sc xss} attacks on the
 client's side. Note that the majority of the mechanisms that detect

### 2014-11-15 docs/questioning.tex
from the BSD to Wordpress

@@
 resulting after the inclusion of user input.
-Two mechanisms that implement this approach for protection against {\sc SQL}
-injection attacks,
+Two mechanisms that implement this approach for protection
+against {\sc sql} injection attacks,
 {\sc sqlg}uard~\cite{BWS05} and
@@
 \noindent
-This same application could allow users to lock their terminal,
-but allow the unlocking either with the user's password or with
-the administrator password (the 4.3 {\sc bsd} {\em lock} command
-behaved in this peculiar way).
-The corresponding query to verify the password on the locked
-workstation would be as follows:
+This same application could allow users to
+login to the site using just their password via a custom login form
+(like the ``Password only login" plugin of
+Wordpress\footnote{\url{https://wordpress.org/plugins/password-only-login/}})
+but allow the login either with the user's password or with
+the administrator password. The corresponding query to verify
+the password on the login form would be as follows:
 

### 2014-11-15 docs/questioning.tex
pass in VI

--- 2014-11-15 docs/questioning.tex
@@
   testbed are publicly available.
-\item {\it Computational performance:} the computational
-  overhead of the mechanisms at their points of deployment.
+\item {\it Performance overhead:} the 
+  overhead imposed by the mechanisms at their points of deployment.
 \item {\it Ease of use:} whether the protection
@@
 The first two criteria correspond to \emph{Accuracy} and
-\emph{Availability}. The other four criteria correspond to \emph{Computational
+\emph{Availability}. The other four criteria correspond to \emph{Runtime
   Performance}, \emph{Ease of Use}, \emph{Security}, and
@@
 
-\subsection{Computational Performance}
+\subsection{Performance Overhead}
 
 Detection mechanisms may impose a cost due to their use, as they
-typically introduce some amount of extra computation on a existing applications.
+typically introduce some amount of extra computation on existing applications.
 The overhead depends on the specifics of each mechanism. For
@@
   &&& \bf{TP,TN,FP,FN}\tnote{2}
-  & \bf{Computational Overhead}\tnote{3} & \\
+  & \bf{Performance Overhead}\tnote{3} & \\
     \thickhline
@@
 
+\section{Observations}
+\label{sec:discussion}
+
+We group our key observations on the~35 publications that
+we consider in this work along the
+dimensions we identified in Section~\ref{sec:dimensions}.
+
+\subsection{Accuracy}
+
+Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
+publications provided a complete tuple of {\sc tp}, {\sc tn}, 
+{\sc fp}, and {\sc fn}. On the other hand, we
+see that 4 out of 35 (11.4\%) were not tested at all.
+In these cases, all four elements of the tuple
+are not available ({\sc na}). An interesting observation is
+that in 10 out of the 35 (28.5\%)
+publications, the evaluation focused on only on attack detection,
+and there was no test focusing on false positives.
+The corresponding tuples contain {\sc tp} and {\sc fn}
+results, but {\sc tn} and {\sc fp} results are not available ({\sc
+  na}). This stresses the fact that authors may be more interested in
+making sure that their mechanisms can detect known attacks rather than
+seeing how they respond under normal conditions. In some occasions,
+where the number of {\sc tp} results are not quantified, authors did
+not mention how many or which attacks they performed. Moreover, in some
+cases we observe that even if the authors report the existence of
+possible false positive and negative results, they have not quantified
+them ({\sc nq}).
+
+Even when some numbers are given, they may not be adequate.
+Sensitivity and specificity are statistical measures, and as such,
+they should be interpreted with suitable confidence intervals. There are
+various methods to calculate confidence intervals, even without
+the need to have large sets of samples in order to be able to use the
+central limit theorem~\cite{agresti1998,brown2001}.
+However, sample sizes in the single
+digits are not enough to produce good intervals.
+
+Regarding the subjects of tests, we see that 27 out of 35 (77.1\%)
+mechanisms were tested with real-world applications known to be
+vulnerable. The vulnerabilities associated with these applications
+are enlisted in the following providers: the Common
+Vulnerabilities and Exposures ({\sc cve}) database~\cite{cve},
+the Bugtraq security mailing list~\cite{bugtraq}, the {\sc xss}ed.com
+security bulletin provider~\cite{xssed}, Microsoft's security
+bulletin~\cite{microsoftBulletin} and the
+ha.ckers.org security bulletin provider~\cite{hackers}.
+Figure~\ref{fig:defect_sources} presents how many, in percentage,
+and which, in the figure's caption, publications referred
+to which source. In numerous occasions authors performed tests based
+on the same applications. For example, 12 mechanisms were tested on a
+vulnerable version of the {\sc phpbb} bulletin board software.
+
+\begin{figure}[t]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.47]{defect-percentages.png}
+\end{center}
+\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
+used for testing of web attack defenses.
+Specifically, the publications that used a particular source are as follows:
+{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
+{\sc xss}ed.com~\cite{NSS06,APKLM10},
+ha.ckers.org~\cite{TNH07,PSC09,LV09},
+Microsoft~\cite{RDWDE07}.}
+\end{figure}
+
+There are also authors that took a different approach.
+For instance, during their initial tests,
+Stock et al.~\cite{SLMS14} managed to bypass
+the browser-based {\sc xss} filters of
+73\% out of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
+These vulnerabilities were actually found as part of
+their previous research~\cite{LSJ13}.
+Finally, in the {\sc amnesia}~\cite{HO05,HO06,HO05b} and
+{\sc sd}river~\cite{MS09,MKS09,MKLS11} publications,
+the authors managed to break existing application suites
+and then test the accuracy of their tools on them.
+
+\subsection{Availability}
+
 \begin{table*}
@@
 
-    \multicolumn{5}{p{13cm}}{%
+    \multicolumn{5}{p{12.4cm}}{%
   \begin{footnotesize}
-       $^\textsuperscript{1}$The check mark (\tick) indicates that the publication
-       includes a homepage where the reader can 
-       download the corresponding software. {\bf AO} (Available On-line) suggests
+       $^\textsuperscript{1}$A check mark (\tick) indicates that the publication
+       includes a link to a page where the software is available.
+       {\bf AO} (Available On-line) indicates
        that the software is available on-line but the
-       address was not mentioned in the paper, which probably indicates that
-       the authors made it available after the publication. The question 
-       mark ({\bf ?}) indicates that the a homepage for the software
-       was included
-       in the publication but now it is not available.
+       address is not mentioned in the paper, which probably means that
+       the it was made available after the publication. A question 
+       mark ({\bf ?}) indicates that a link to the software
+       was included in the publication but is now inaccessible.
   \end{footnotesize} } \\
@@
 
-\section{Observations}
-\label{sec:discussion}
-
-We group our key observations on the~35 publications that
-we considered in this work along the
-dimensions we identified in Section~\ref{sec:dimensions}.
-
-\subsection{Accuracy}
-
-Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
-publications provided complete quadruples of {\sc tp}, {\sc tn}, 
-{\sc fp}, and {\sc fn}. On the other hand, we
-see that 4 out of 35 (11.4\%) were not tested at all.
-In these cases, all the four elements of the quadruples
-are not available ({\sc na}). An interesting observation is
-that in 10 out of the 35 (28.5\%)
-publications, the authors performed only attacks during their tests
-and did not test their mechanisms to see if they produce any false
-alarms. The corresponding quadruples contain {\sc tp} and {\sc fn}
-results but {\sc tn} and {\sc fp} results are not available ({\sc
-  na}). This stresses the fact that authors may be more interested in
-making sure that their mechanisms can detect known attacks rather than
-seeing how they respond under normal conditions. In some occasions,
-where the number of {\sc tp} results are not quantified, authors did
-not mention how many or which attacks they performed. Moreover in some
-cases we observe that even if the authors report the existence of
-possible false positive and negative results, they have not quantified
-them ({\sc nq}).
-
-Even when some numbers are given, they may not be adequate.
-Sensitivity and specificity are statistical measures, and as such
-should be interpreted with suitable confidence intervals. There are
-various methods to calculate confidence intervals, even dispensing
-with the need to have large samples in order to be able to use the
-central limit theorem~\cite{agresti1998,brown2001}.
-However, sample sizes in the single
-digits are not enough to produce good intervals.
-
-Regarding the subjects of tests, we see that 27 out of 35 (77.1\%)
-mechanisms were tested on real-world applications known to be
-vulnerable. The vulnerabilities associated with these applications
-are enlisted in the following providers: the Common
-Vulnerabilities and Exposures ({\sc cve}) database~\cite{cve},
-the Bugtraq security mailing list~\cite{bugtraq}, the {\sc xss}ed.com
-security bulletin provider~\cite{xssed}, Microsoft's security
-bulletin~\cite{microsoftBulletin} and the
-ha.ckers.org security bulletin provider~\cite{hackers}.
-Figure~\ref{fig:defect_sources} presents how many, in percentage,
-and which, in the figure's caption, authors referred
-to which source. In numerous occassions authors performed tests based
-on the same applications. For example, 12 mechanisms were tested on a
-vulnerable version of {\sc phpbb}.\footnote{https://www.phpbb.com/}
-
-\begin{figure}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.47]{defect-percentages.png}
-\end{center}
-\caption{\label{fig:defect_sources}Pie chart showing the sources
-that the used to find vulnerabilities to test
-their mechanisms. We also provide which source was used
-in which publication:
-{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
-{\sc xss}ed.com~\cite{NSS06,APKLM10},
-ha.ckers.org~\cite{TNH07,PSC09,LV09},
-Microsoft~\cite{RDWDE07}.}
-\end{figure}
-
-There are also authors that took a different approach.
-For instance, during their initial tests,
-Stock et al.~\cite{SLMS14} managed to bypass
-the browser-based {\sc xss} filters of the
-73\% of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
-These vulnerabilities were actually found during
-their previous research~\cite{LSJ13}.
-Finally, in the publications that
-{\sc amnesia} and {\sc sd}river were presented,
-authors managed to break existing application suites
-and then test the accuracy of their tools on them.
-
-\subsection{Availability}
-
 Table~\ref{tab:avail} presents our findings regarding the availability
@@
 executables. We also examined the availability of the testbeds
-mentioned in the paper. We see that only 6 out of 35 (17.1\%) of the
-pubications provided a homepage for their mechanism and 2 from these 6
-homepages are currently not available. In 5 cases authors made either
+mentioned in each paper. We see that only 6 out of 35 (17.1\%) of the
+publications provided a link to their mechanism and, 2 from these 6
+web pages are currently not available. In 5 cases authors made either
 the source code or their executables available after their paper got
-published. In one case ({\sc csp}) the source was available before the
+published. In one case ({\sc csp}), the source was available before the
 publication through the Mozilla community.
@@
 
-\subsection{Computational Performance}
-
-Table~\ref{tab:comp} shows for every mechanism its corresponding
-overhead. In addition, it indicates if the overhead is applied to the
-server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
+\subsection{Performance Overhead}
+
+Table~\ref{tab:comp} shows the performance overhead of each mechanism.
+In addition, it indicates if the overhead is incurred at the
+server ({\sc s}) or at the client side ({\sc c}). In almost half of
 the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
 percentage, while in other cases, 7 our of 35 (20\%), the authors
-provide the time (in terms of ms) that their mechanisms add to the
-normal execution time of the protecting entity. Note that in some
+provide the latency (in ms) that their mechanisms add to the
+normal execution time of the protected application. Note that in some
 cases, the times of normal executions are not provided,
-so it is not possible to move from absolute
+so it is not possible to convert absolute
 time measurements to percentage overheads. In 10 cases (28.5\%), the
 overhead was either not available ({\sc na}) or not quantified ({\sc
-  nq}). In the case of {\sc php aspis}, its authors indicate that with
+  nq}). For {\sc php aspis}, its authors indicate that with
 their mechanism, the execution time is doubled.
@@
 Mechanisms in different categories face different deployment issues.
-
-Consider the majority of mechanisms coming from the policy enforcement
-subcategory. In most cases developers should modify multiple
+Consider the majority of mechanisms in the policy enforcement
+subcategory. In most cases, developers should modify multiple
 components to use each mechanism. Specifically, mechanisms like
 BrowserShield and {\sc beep} require modifications both on the server
-and the client side. Thus, it would be difficult for them to be
+and at the client. Thus, it would be difficult to be
 adopted by both browser vendors and application developers. On the
-other hand, there are cases where the policies introduced in the
-server are enforced on the client-side, via a library embedded in the
+other hand, there are cases where the policies introduced at the
+server are enforced at the client side, via a library embedded in the
 server's response (i.e., Blueprint). Such an approach is convenient
-since no modifications are needed on the client.
+as no modifications are needed at the client.
 
@@
 difficult to use. {\sc sql}rand, {\sc amnesia},
-mechanisms coming from the parse-tree validation
-subcategory and mechanisms coming from the taint
+mechanisms of the parse-tree validation
+subcategory, and mechanisms of the taint
 tracking subcategory are such examples.
@@
 In the latter case they should also change
-all the code fragments that involve user-input handling.
+all the code fragments that involve user input handling.
 
@@
 When the application is altered, mechanisms like {\sc sd}river
-and {\sc xss-guard} require a new training phase is necessary.
+and {\sc xss-guard} require a new training phase.
 However, with the increased adoption of automated testing
@@
 
-While describing the various mechanisms in Section~\ref{sec:defs}, we
-observed that some can be bypassed by attackers that know how they
-work. Still, some mechanisms are designed in such a way that they
-can be extended and become immune to the attacks that they are
+In our discussion of the various mechanisms in Section~\ref{sec:defs}, we
+observed that some of them can be bypassed by attackers that know
+the internals of their operation.
+Still, the design of some mechanisms allows them to
+be extended and become immune to the circumvention attacks they are
 currently vulnerable to. For example, policy enforcement frameworks
-that are based on JavaScript or {\sc html} rewriting can be extended
+based on JavaScript or {\sc html} rewriting can be extended
 to detect attacks that leverage {\tt iframe} tags. This does not apply
@@
 {\sc dsl} injection and {\sc csrf} attacks take place
-on the server-side, all the mechanisms that detect
-such attacks are placed in some point within the server.
+at the server side, all mechanisms that detect
+such attacks are placed at some point within the server-side infrastructure.
 From the mechanisms that detect {\sc dsl} code injection
 attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms}---Point {\sc db}.
-The other 11 wrap {\sc api} calls related to output
-vectors---Point {\sc e}i{\sc q}.
-
-In frameworks that deal with {\sc xss} attacks we
-see that attack detection may take place either on the server-side or
-on the client-side. In the first case, a proxy is placed on the server
-to examine the server's responses before they reach the user's web
-browser. In the second case a modified browser or a library that is
+of the {\sc rdbms} (Point {\sc db}).
+The other 11 are based on interposing on {\sc api} calls related to output
+vectors (Point {\sc e}i{\sc q}).
+
+For frameworks that deal with {\sc xss} attacks, we
+see that attack detection and prevention may take place either at the server or
+the client side. In the first case, a proxy is typically placed in front of the server
+to examine the server's responses before they reach a user's 
+browser. In the second case, a modified browser or a library that is
 securely downloaded from the server checks the responses for potential
@@
 perform detection on the client side: in particular, 14 out of 24
-frameworks (58,3\%) detect {\sc xss} attacks on the
-client's side. Note that the majority of the mechanisms that detect
-such attacks on the server-side can also detect {\sc dsl} code
+frameworks (58,3\%) detect {\sc xss} attacks at the
+client side. Note that the majority of the mechanisms that detect
+such attacks on the server can also detect {\sc dsl} code
 injection attacks (6 out of 10).
@@
 call for improving accuracy tests and code availability, while
-aiming to reduce computational and deployment overheads.
+aiming to reduce performance and deployment overheads.
 
@@
 
-\subsection{Computational Overhead and Deployment Remarks}
-
-Computational overhead comes up as a non-trivial issue. We observe
+\subsection{Performance Overhead and Deployment Remarks}
+
+Performance overhead comes up as a non-trivial issue. We observe
 that the average overhead that can be extracted from the publications

### 2014-11-15 docs/questioning.tex
minor changes

@@
 Detection accuracy is gauged with the following
-metrics~\cite{TDR2013,GFDLS06,A00}.
+metrics~\cite{TDR2013,GFDLS06,A00}:
 \begin{itemize}
@@
 \textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
-Sensitivity and specifity are defined as follows~\cite{linn2004}.
+Sensitivity and specifity are defined as follows~\cite{linn2004}:
 \begin{itemize}
@@
       \item[2] Tuples contain numbers given for True Positives
-        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc
+        ({\sc tp}), True Negatives ({\sc tn}), False Positives ({\sc
           fp}) and False Negatives ({\sc fn}). For every tuple\newline there is a corresponding suffix that indicates whether the testbed was
@@
 defenses that have been proposed in publications cited more than
-20 times according to Google Scholar.
+20 times according to Google Scholar~\cite{googleScholar}.
 We also include some recent works that have been
@@
 \emph{Policy Enforcement}, and
-\emph{Instruction Set Randomization (ISR)}.
+\emph{Instruction Set Randomization} ({\sc isr})}.
 

### 2014-11-15 docs/questioning.tex
tiny fix
some changes / fixes in the intro

@@
 \begin{IEEEkeywords}
-Security and Protection, Web Application Security, Code injection Attacks,
+Protection Mechanisms, Web Application Security, Code injection Attacks,
 Testing, Cross-Site Scripting.
@@
 There is already a survey on mitigating software vulnerabilities in
-general~\cite{SZ12}. The scope of that research is much broader that
+general~\cite{SZ12}. The scope of that research is much broader than
 ours and leaves out the majority of the approaches and mechanisms that
@@
 application, thereby interacting with the underlying database. This
-input can become part of an {\sc sql} query and get executed on the
+input can become part of an {\sc sql} query and gets executed on the
 target database. Code injection attacks that exploit vulnerabilities
@@
 Attackers that would input the string {\tt anything' OR 'x'='x}
-thereby obtaining the administrator's password by email. Savvy
+would obtain the administrator's password by email. Savvy
 programmers can use certain {\sc api} functions, such as {\sc php}'s
@@
   html}, typically via a parameter value, and inject their own content
-into the page. {\sc html} injection is mainly associated with {\sc
+into the application's page. {\sc html} injection is mainly associated with {\sc
   xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
@@
 \emph{Policy Enforcement}, and
-\emph{Instruction Set Randomization} ({\sc isr})}.
+\emph{Instruction Set Randomization} ({\sc isr}).
 

### 2014-11-15 docs/questioning.tex
pass in VII

--- 2014-11-15 docs/questioning.tex
@@
 Our observations lead to some lessons and recommendations that
-developers of new mechanisms may find helpful. In particular, they
-call for improving accuracy tests and code availability, while
-aiming to reduce performance and deployment overheads.
+developers of new mechanisms may find helpful. In particular,
+our observations
+call for improvements in the accuracy of experimental testing
+and code availability, while
+aiming to reduce performance overheads and deployment hurdles.
 
@@
 
-\subsection{Improving Accuracy Tests}
-
-One of our key findings indicate that many detect mechanisms are
-tested in a poor manner. In many cases researchers tend not to provide
-the false positive and negative results that their tools may produce.
-Discussing about the existence of such results and not quantifying
+\subsection{Improving Testing Accuracy}
+
+One of our key findings indicates that many proposed defenses are
+tested in a poor manner. In many cases, researchers tend to not providing
+results on false positives or false negatives for their detection mechanisms
+(where applicable).
+Mere discussion on the existence of such results without quantifying
 them also blurs the picture.
@@
 ones coming from the etiological category), do not need to be
-established purely through testing since they provide systematic
+established purely through testing, since they provide systematic
 arguments as to why their design is secure against attacks. In order
-for this to hold, however, an implementation of a defense mechanism
-may be entirely correct in terms of its specification, which may not
-happen in practice. Moreover, even a mechanism that detects an attack
-based on its root cause, instead of observer behavior, may still be
-circumvented so that attacks will pass undetected.
+for this to hold, however, their implementation should be flawless
+and precisely follow its specification, which may not
+be the case in practice. Moreover, even mechanisms that detect attacks
+based on their root cause, instead of their observed behavior, may still be
+circumvented by evasive attacks.
 
 When we introduced specificity and sensitivity in
-Section~\ref{ssec:diagnostic-performance} we deferred discussion of
+Section~\ref{ssec:diagnostic-performance}, we deferred discussion of
 \textsc{ppv} and \textsc{npv} to this point. These two relate to the
-performance of a detection mechanism in an actual production setting,
+effectiveness of a detection mechanism in an actual production setting,
 instead of a testbed. If an attack is detected in a production
@@
 and~\ref{eq:specificity}. However, \textsc{tp}, \textsc{tn},
-\textsc{fp}, and \textsc{fn} are not the same in the two cases:
-whereas sensitivity and specificity are measured on a test
-environment, \textsc{ppv} and \textsc{npv} are measured on the real,
-target environment. In fact, if \textsc{pr} is the probability of
-attacks in the real world, the prevalence, then we
+\textsc{fp}, and \textsc{fn} are not qualitatively the same in these two cases:
+whereas sensitivity and specificity are measured on a testing
+environment, \textsc{ppv} and \textsc{npv} are measured on a real,
+production environment. In fact, if \textsc{pr} is the probability of
+a particular class of attacks in the real world,
+i.e., its prevalence, then we
 have~\cite{linn2004,altman1994}:
@@
 \noindent
-The prevalence is the prior probability that an event is an attack,
-based on our understanding of the volume and frequency of attacks; the
-\textsc{ppv} and \textsc{npv} are the revised estimates of the
+Prevalence is the prior probability that an event might be an attack,
+based on our understanding of the volume and frequency of a particular
+class of attacks; 
+\textsc{ppv} and \textsc{npv} are the revised estimates of that
 probability based on the results of the detection
@@
 Of course it is not easy, and it may not even be possible, to know how
-prevalent an attack is. Also, attacks on a system may depend on
-factors such as its visibility and popularity, so that the same piece
-of software may be subject to varying attack regimes depending on
-where it is actually deployed. With this in mind it may be unfair to
-ask of researchers to provide \textsc{ppv} and \textsc{npv} values for
-their mechanisms---in fact, we see that nobody does.
-
-That does not mean that deriving \textsc{ppv} and \textsc{npv} is
-altogether impossible. One could deploy a system, armoured with an
-attack detection mechanism, on a honeypot to study what happens over
-a length of time. This could give an indication of the performance of
-the mechanism out in the wild. Alternatively, one could deploy a
+prevalent an attack class is. Also, attacks against a system may depend on
+factors such as its visibility and popularity, and thus the same
+software may be subject to varying attack intensity depending on
+where it is actually deployed. With this in mind, it may be unfair to
+ask researchers to provide \textsc{ppv} and \textsc{npv} values for
+their mechanisms.
+%---in fact, we observe that nobody does.
+
+This does not mean though that deriving \textsc{ppv} and \textsc{npv} is
+altogether impossible. One could deploy a system armoured with an
+attack detection mechanism on a honeypot to study what happens over
+a time period. This could give an indication about the performance of
+the mechanism in a realistic setting. Alternatively, one could deploy a
 target, unarmoured system, on a honeypot to study the prevalence of
 the class of attacks to be detected. Studying the prevalence of
-classes of attacks could be an interesting area of study on its own,
-which could feed directly on the evaluation of attack detection
+classes of attacks is an interesting area of study on its own,
+and could feed directly on the evaluation of attack detection
 mechanisms as practical tools.
@@
 Apart from demonstrating the value of a mechanism, good accuracy tests
-may be beneficial per se, by leading to more well-designed and robust
-mechanisms. Mechanisms that can be circumvented were not extensively
+may be beneficial per se, leading to more well-designed and robust
+defenses. Mechanisms that can be circumvented were not extensively
 tested in terms of accuracy. For instance, {\sc didafit} was not
@@
 subcategory. It is possible that more tests during development would
-have led the authors to wider improvements in design~\cite{Van14}.
+have led the authors to larger design improvements~\cite{Van14}.
 
@@
 is the only one that targets exclusively {\sc dom}-based {\sc xss}
-attacks and detects them in an accurate manner as seen in
-Table~\ref{tab:comp}. It is also extensively tested in real-world
+attacks and detects them in an accurate manner, as seen in
+Table~\ref{tab:comp}. It is also extensively tested with real-world
 attacks.
@@
 Apart from testing practices, another area that merits improvement is
-the availability of source code and testbeds. We are not aware of
+the availability of prototypes and testbeds. We are not aware of
 specific reasons why authors of attack detection mechanisms seem to be
-wary of releasing on-line their code and tests. Our finding may reflect
+wary of publicly releasing their code and tests. Our finding may reflect
 the status in the current point in time, when authors are urged to
@@
 material was published, but does not seem to be available any more.
-That points to the importance of curation of research materials. That
-is a problem arising in all scientific fields. It is not enough to
+That points to the importance of reproducibility of research materials, 
+an issue arising in all scientific fields. It is not enough to
 publish the underlying code and data, but to make sure that it remains
-accessible and to provide the means to test it even as technology
-progresses and operating systems, file formats, and software libraries
+accessible, and to provide the means to test it even as technology
+advances and operating systems, file formats, and software libraries
 change. That may be too much to ask right now; what seems reasonable,
-though, is to ask of researchers in attack detection mechanisms not to
+though, is to ask of researchers working on attack detection mechanisms not to
 buck the trend and to take steps to increase the availability of their
@@
 We saw that many policy enforcement mechanisms that detect attacks at
-Point {\sc ub} are not easy to deploy because modifications are needed
+the browser are not easy to deploy because modifications are needed
 both on the server and the client side.
@@
 the tools to the user unobtrusively; for example, we saw that
-Blueprint enforces policies on the client side by embedding a library
+Blueprint enforces policies at the client side by embedding a library
 in the server's response to the client. In general, when developing a
-new countermeasure, researchers should consider where they are
-planning to detect attacks, observe the corresponding deployment
+new countermeasure, researchers should consider where it
+will detect attacks, observe the corresponding deployment
 challenges, and try to mitigate them.

### 2014-11-15 docs/questioning.tex

@@
 \emph{Policy Enforcement}, and
-\emph{Instruction Set Randomization (ISR)}.
+\emph{Instruction Set Randomization} ({\sc isr}).
 

### 2014-11-15 docs/questioning.tex
pass in conclusion

@@
 
-\section{Conclusions}
+\section{Conclusion}
 \label{sec:conclusion}
@@
 Despite many approaches that have been developed,
-application attacks based on code injection
+attacks based on code injection against web applications
 have been consistently present for the last 15 years,
@@
 Attackers seem to find new ways to introduce
-malicious source code to applications by using a
+malicious code to applications using a
 variety of languages and techniques~\cite{HNSHS12,DKH14}.
-Meanwhile, during the last decade, there are
-numerous mechanisms that have been developed to
-detect one or more of such attacks. However,
-even if some of them share characteristics
+Meanwhile, during the last decade, there have been
+numerous mechanisms designed to
+detect one or more of types of such attacks.
+Although some deployed and widely used frameworks, 
+such as Mozilla's {\sc csp} and Google Caja~\cite{M06,caja},
+share characteristics
 (for instance, {\sc html} sanitization and {\tt eval} handling)
-with supported frameworks like Mozilla's {\sc csp}
-and Google Caja~\cite{M06,caja}
-the majority of them are not used in practice.
-
-In order for a security tool to be used in practice it must provide
+with previous proposals, 
+most research works are still not used in practice.
+
+In order for a security tool to be used in practice, it must provide
 some value to the user. In particular, the value should outweigh the
-cost of its use. The cost need not be directly monetary, but may be
+cost of its use. The cost is not necessarily monetary, but may be
 incurred from the time required to use the tool, any inconvenience
-caused, false alarms that it may raise. These costs are related to the
+caused, false alarms that may raise, and so on. These costs are related to the
 issues we have been investigating here: poor testing, high overhead,
-unavailabilty of source, deployment difficulties, compromised security.
-
-Enhancing any of these would not just increase the value of a piece of
-research as a practical tool, it would increase its research value as
-well. Accurate detection reporting would help in appraising different
-approaches. Performance measurements can point to blind, unpractical,
-alleys and focus effort elsewhere. Availability of source code
-enhances basic scientific tasks like checking and replication. Ease of
+lack of publicly available prototypes,
+deployment difficulties, compromised security.
+
+Improving any of these aspects would not just increase the value of a 
+research work as a practical tool, but it would also increase its
+research value as well.
+Accurate detection reporting would help in evaluating different
+approaches. Extensive performance measurements can reveal impractical
+designs and focus effort elsewhere. Availability of source code
+enhances basic scientific tasks like verification and reproducibility. Ease of
 deployment brings ease of experimentation. Secure methods can form the
@@
 
-We saw that there are mechanisms that have been extensively tested in
+To the positive side, some defenses have been extensively tested in
 terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
-libAnomaly), solve specific problems in an efficient way (Blueprint
+libAnomaly), solve specific problems in an effective way (Blueprint
 and the system by Stock et al.) or have a low computational overhead
@@
 researchers have made their code available ({\sc beep} and {\sc
-  sd}river) which can be a push towards the development of better
+  sd}river), which can promote the development of better
 mechanisms. This argument has been raised by another {\sc s}o{\sc k}
@@
 emerged from our research can be a reference point for researchers who
-wish to develop new, practical countermeasures against web application
+aim to develop new, practical countermeasures against web application
 attacks.

### 2014-11-15 docs/questioning.tex
minor changes

@@
 we consider in this work. This is mainly because that work includes
-countermeasures that identify vulnerabilities using program analysis
+countermeasures that identify vulnerabilities using static program analysis
 (which takes place during the development or testing phases), while we
 consider protection mechanisms that counter web attacks when they take
-place. Similarly, static or dynamic analysis techniques that examine
+place. Similarly, dynamic analysis techniques that examine
 applications to identify vulnerabilities that may lead to the attacks
@@
 called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
-is currently supported by many browsers to detect
+is currently supported by many browsers to prevent
 {\sc xss} and {\sc csrf} attacks. To eliminate such

### 2014-11-15 docs/questioning.tex
adding refs in the text, fix in Fig 2

@@
   deployment, security, and availability properties.
-  We discuss the results of our analysis, with emphasis on factors
-  that may hinder the widespread adoption of attack detection
-  mechanisms in practice.
+  Accuracy is of particular importance, as our findings show that many defense
+  mechanisms have been tested in a poor manner. In addition, we observe
+  that some mechanisms can be bypassed by attackers with knowledge
+  of how the mechanisms work. Finally, we discuss the results
+  of our analysis, with emphasis on factors that may hinder
+  the widespread adoption of attack detection mechanisms
+  in practice.
 
@@
 overhead, they require significant deployment effort. In particular,
-{\sc sql}rand requires the integration of a proxy within the database
-server, while Noncespaces and x{\sc js} require modifications on both
-the server and the client.
+{\sc sql}rand~\cite{BK04} requires the integration of
+a proxy within the database
+server, while Noncespaces and x{\sc js}~\cite{APKLM10}
+require modifications on both the server and the client.
 
@@
 Defenses based on training include some mechanisms that can be easily
-circumvented. For example, {\sc didafit} and libAnomaly do not
-tag transactions with their corresponding call sites. This can lead
+circumvented. For example, {\sc didafit}~\cite{LLW02}
+and libAnomaly~\cite{VMV05} do not tag transactions with their
+corresponding call sites. This can lead
 easily to false negatives. For instance, recall the application
@@
 Even if the application's administrators have chosen to use
-either {\sc didafit} or libAnomaly as protection,
+either {\sc didafit}~\cite{LLW02} or
+libAnomaly~\cite{VMV05} as protection,
 an attacker could bypass them and obtain the
@@
 Mechanisms based on signatures that involve elements not only
-associated with code statements (e.g., {\sc amnesia} and {\sc
-  sd}river) could detect such attacks. Specifically, {\sc sd}river
+associated with code statements (e.g.,
+{\sc amnesia}~\cite{HO05,HO06,HO05b} and
+{\sc sd}river~\cite{MS09,MKS09,MKLS11})
+could detect such attacks. Specifically, {\sc sd}river
 associates a complete stack trace with the root of an {\sc sql}
@@
 can be retrofitted to a system typically by changing
-some configuration files (i.e., {\sc sd}river). This does not apply
-to {\sc amnesia} though, since significant source code
+some configuration files (i.e., {\sc sd}river).
+This does not apply to {\sc amnesia}
+though, since significant source code
 modifications are required for every query that exists
@@
 overhead was either not available ({\sc na}) or not quantified ({\sc
-  nq}). For {\sc php aspis}, its authors indicate that with
+  nq}). For {\sc php aspis}~\cite{PMP11}, its authors indicate that with
 their mechanism, the execution time is doubled.
@@
 components to use each mechanism. Specifically, mechanisms like
-BrowserShield and {\sc beep} require modifications both on the server
+BrowserShield~\cite{RDWDE07} and {\sc beep}~\cite{TNH07}
+require modifications both on the server
 and at the client. Thus, it would be difficult to be
@@
 server are enforced at the client side, via a library embedded in the
-server's response (i.e., Blueprint). Such an approach is convenient
+server's response (i.e., Blueprint~\cite{LV09}).
+Such an approach is convenient
 as no modifications are needed at the client.
@@
 code can also be a reason that can make a mechanism
-difficult to use. {\sc sql}rand, {\sc amnesia},
+difficult to use. {\sc sql}rand~\cite{BK04},
+{\sc amnesia}~\cite{HO05,HO06,HO05b},
 mechanisms of the parse-tree validation
@@
 training are easy to deploy, they have a distinct disadvantage.
-When the application is altered, mechanisms like {\sc sd}river
-and {\sc xss-guard} require a new training phase.
+When the application is altered, mechanisms like
+{\sc sd}river~\cite{MS09,MKS09,MKLS11}
+and {\sc xss-guard}~\cite{BV08} require a new training phase.
 However, with the increased adoption of automated testing
@@
 to all mechanisms though. In particular, training mechanisms like {\sc
-  didafit} and {\sc xss-guard} must be redesigned to detect the
-attacks we described in the related sections.
+  didafit}~\cite{LLW02} and {\sc xss-guard}~\cite{BV08} must be
+redesigned to detect the atacks we described in the related sections.
 
@@
 defenses. Mechanisms that can be circumvented were not extensively
-tested in terms of accuracy. For instance, {\sc didafit} was not
-tested at all and {\sc xss-guard}'s testing involved 6 known attacks.
+tested in terms of accuracy. For instance, {\sc didafit}~\cite{LLW02}
+was not tested at all and {\sc xss-guard}'s~\cite{BV08}
+testing involved 6 known attacks.
 This also applies to some frameworks coming from the taint tracking
@@
 the tools to the user unobtrusively; for example, we saw that
-Blueprint enforces policies at the client side by embedding a library
+Blueprint~\cite{LV09} enforces policies at the client side by embedding a library
 in the server's response to the client. In general, when developing a
@@
 To the positive side, some defenses have been extensively tested in
-terms of accuracy ({\sc sqlc}heck, {\sc amnesia},
-libAnomaly), solve specific problems in an effective way (Blueprint
-and the system by Stock et al.) or have a low computational overhead
-({\sc dsi} and the system by Phung et al.). There are also cases where
-researchers have made their code available ({\sc beep} and {\sc
-  sd}river), which can promote the development of better
+terms of accuracy ({\sc sqlc}heck~\cite{SW06},
+{\sc amnesia}~\cite{HO05,HO06,HO05b}, libAnomaly~\cite{VMV05}),
+solve specific problems in an effective way
+(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}) or
+have a low computational overhead
+({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
+There are also cases where
+researchers have made their code available ({\sc beep}~\cite{TNH07}
+and {\sc sd}river~\cite{MS09,MKS09,MKLS11}),
+which can promote the development of better
 mechanisms. This argument has been raised by another {\sc s}o{\sc k}

### 2014-11-15 docs/questioning.tex
removed the text about average overhead
csrf

--- 2014-11-15 docs/questioning.tex
@@
 
-We provide a step-by-step exploitation model to understand the process
+We provide a step-by-step exploitation model to aid in understanding the process
 of carrying out code injection attacks against web
-applications. Figure~\ref{fig:attacks} presents the required steps for
-different classes of injection attacks. Links between steps are
+applications. Figure~\ref{fig:attacks} illustrates the required steps for
+different classes of injection attacks,
+such as SQL injection, XSS, and CSRF. Links between steps are
 labeled with the different attacks that use that path, while the
 numbers next to attack labels denote the sequence of steps for a
-particular attack. Most steps are common in all attacks. This is
-because they are based on similar attack vectors as we mentioned in
-the previous section. Large `X' marks on transitions indicate the
-points where defenses detect or prevent attacks.
-
-An attacker can initiate an injection attack through two different main routes.
+particular attack. Most steps are common in all attacks, as different attack
+types follow similar exploitation paths, as mentioned in
+the previous section. Large `X' marks on transitions correspond to the
+points where the defenses we consider in this work detect or prevent attacks.
+
+An attacker can initiate an injection attack through two main routes.
 One way is to use the browser of a victim as an attack
 vehicle, through which the code will be injected in the application.
-For example, the attacker could craft a malicious script into a {\sc
+For example, the attacker could embed a malicious script into a {\sc
   url} and then trick a user to click on it through social
 engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
-  n-xss} 1.1). Alternatively, the attacker may be able
+  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
 to inject directly the malicious code on the server through an {\sc http} request
-({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc csrf} 1). This would happen
+({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
 in a web application that accepts and processes user input
@@
 to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
-an {\tt img} tag including a malicious {\sc http} request ({\sc csrf}),
+an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
+i-csrf 1}),
 or embed malicious
-{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
+{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
 %Recall the examples we provided in Section~\ref{sec:attacks}.
-Note that {\sc xss} attacks can start from both routes.
+Note that {\sc xss} and {\sc csrf} attacks can start from both routes.
 
@@
 a part of a value represented by a program variable. The target of the
-attack determines the route from now on. In an {\sc sql} injection
-attack the injected code becomes part of a query that
-finally reaches the database where it is executed.
-
-{\sc xss} attacks fall into two categories, {\it non-persistent} and
-{\it persistent}. Non-persistent {\sc xss} attacks take place when the
+attack determines the route from that point and on. In an {\sc sql} injection
+attack, the injected code becomes part of a query that
+eventually reaches the database where it is executed.
+
+Cross-site scripting attacks fall into two categories, {\it non-persistent}
+(also known as \emph{reflected}) {\sc xss}
+and {\it persistent} (also known as \emph{stored}) {\sc XSS}.
+Non-persistent {\sc xss} attacks take place when the
 data provided by a user is processed on-the-fly
-by server-side application logic and end up without proper sanitization
+by server-side application logic and ends up without proper sanitization
 into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
@@
 Thus, in a non-persistent {\sc xss} attack, the injected code
-is not saved on the server and immediately becomes part of the
-content that is sent back to a web user.
+is not saved on the server, but immediately becomes part of the
+content that is sent back to a user.
 In persistent {\sc xss} attacks, on the other hand,
 malicious code is permanently stored on the server ({\sc p-xss} 5).
-The injected code residing at server-side then re-enters the
+The injected code residing at server side then re-enters the
 application's execution flow and becomes part of the content that is
-actually sent back to the user as part of a future response.
-
-A common {\sc csrf} attack could involve just a
-{\sc url} containing a malicious {\sc http} request
-which in turn must be clicked by the user
-via social engineering again ({\sc csrf} 1).
-Note, that this case does not involve code injection
-and it never reaches the server that is vulnerable
-to code injection (Server 1).
-The {\sc i-csrf} attack involves an attacker
-that manages to inject {\sc html} code that contains
-a hidden request in the way we described in
-Section~\ref{sec:attacks}. This code will be stored
+eventually sent to the user as part of a future response.
+
+Cross-site request forgery attacks typically involve just a
+URL or page that contains a malicious request towards
+a site vulnerable to {\sc csrf}.
+An attacker can entice a victim to click on the URL or visit the page
+through social engineering ({\sc csrf} 1), which will the result in a malicious
+request towards the vulnerable site ({\sc csrf} 2}).
+Note that this scenario does not involve the injection of any code through the
+exploitation of some server-side vulnerability (as is the case with Server 1).
+On the other hand, {\sc csrf} is also possible through injection
+({\sc i-csrf}). In this attack, an attacker
+manages to inject {\sc html} code that contains
+a malicious {\sc csrf} request in the way we described in
+Section~\ref{sec:attacks}.
+This code will be stored
 in the database ({\sc i-csrf} 5)
-and then it will re-enter the application if
+and then it will re-enter the application when
 a user visits a page ({\sc i-csrf} 6). When the
-content reaches the browser the functionality
-dictated by the malicious request will be performed.
+content reaches the browser, a malicious request will be generated
+towards the site that is vulnerable to {\sc csrf}.
 

### 2014-11-15 docs/questioning.tex

--- 2014-11-15 docs/questioning.tex
@@
 Performance overhead comes up as a non-trivial issue. We observe
-that the average overhead that can be extracted from the publications
-that provide the overhead in percentage terms is 17.45\%. Relative
+that there are some mechanisms that introduce an overhead
+that is more than 10\%. Relative
 research on protection mechanisms~\cite{SPWS13} indicates that

### 2014-11-15 docs/questioning.tex
oops

@@
 through social engineering ({\sc csrf} 1), which will the result in a malicious
-request towards the vulnerable site ({\sc csrf} 2}).
+request towards the vulnerable site ({\sc csrf} 2).
 Note that this scenario does not involve the injection of any code through the

### 2014-11-15 docs/questioning.tex
more on the refs

@@
 associated with code statements (e.g.,
-{\sc amnesia}~\cite{HO05,HO06,HO05b} and
-{\sc sd}river~\cite{MS09,MKS09,MKLS11})
+{\sc amnesia}~\cite{HO06} and
+{\sc sd}river~\cite{MS09})
 could detect such attacks. Specifically, {\sc sd}river
@@
 their previous research~\cite{LSJ13}.
-Finally, in the {\sc amnesia}~\cite{HO05,HO06,HO05b} and
-{\sc sd}river~\cite{MS09,MKS09,MKLS11} publications,
+Finally, in the {\sc amnesia}~\cite{HO06} and
+{\sc sd}river~\cite{MS09} publications,
 the authors managed to break existing application suites
@@
 the source code or their executables available after their paper got
-published. In one case ({\sc csp}), the source was available before the
+published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
 publication through the Mozilla community.
@@
 difficult to use. {\sc sql}rand~\cite{BK04},
-{\sc amnesia}~\cite{HO05,HO06,HO05b},
+{\sc amnesia}~\cite{HO06},
 mechanisms of the parse-tree validation
@@
 When the application is altered, mechanisms like
-{\sc sd}river~\cite{MS09,MKS09,MKLS11}
+{\sc sd}river~\cite{MS09}
 and {\sc xss-guard}~\cite{BV08} require a new training phase.
@@
 Although some deployed and widely used frameworks, 
-such as Mozilla's {\sc csp} and Google Caja~\cite{M06,caja},
-share characteristics
+such as Mozilla's {\sc csp}~\cite{SSM10} and
+Google Caja~\cite{M06,caja}, share characteristics
 (for instance, {\sc html} sanitization and {\tt eval} handling)
@@
 terms of accuracy ({\sc sqlc}heck~\cite{SW06},
-{\sc amnesia}~\cite{HO05,HO06,HO05b}, libAnomaly~\cite{VMV05}),
+{\sc amnesia}~\cite{HO06}, libAnomaly~\cite{VMV05}),
 solve specific problems in an effective way
@@
 researchers have made their code available ({\sc beep}~\cite{TNH07}
-and {\sc sd}river~\cite{MS09,MKS09,MKLS11}),
+and {\sc sd}river~\cite{MS09}),
 which can promote the development of better

### 2014-11-15 docs/questioning.tex
minor fixes

@@
 (also known as \emph{reflected}) {\sc xss}
-and {\it persistent} (also known as \emph{stored}) {\sc XSS}.
+and {\it persistent} (also known as \emph{stored}) {\sc xss}.
 Non-persistent {\sc xss} attacks take place when the
@@
 Cross-site request forgery attacks typically involve just a
-URL or page that contains a malicious request towards
+{\sc url} or page that contains a malicious request towards
 a site vulnerable to {\sc csrf}.
-An attacker can entice a victim to click on the URL or visit the page
+An attacker can entice a victim to click on the {\sc url} or visit the page
 through social engineering ({\sc csrf} 1), which will the result in a malicious

### 2014-11-15 docs/questioning.tex
pass in abstract

--- 2014-11-15 docs/questioning.tex
@@
 
-  Some of the most dangerous web application attacks, such as Cross-Site
+  Some of the most dangerous web attacks, such as Cross-Site
   Scripting and SQL injection, exploit vulnerabilities
@@
   In this paper, we systematize the existing knowledge on
-  various defense mechanisms against code injection attacks by proposing
-  a model that highlights the key weaknesses that enable these attacks,
-  and provides a common perspective for the different defenses.
-  We then categorize and analyze the various defense mechanisms that
-  have been developed, based on their accuracy, performance,
-  deployment, security, and availability properties.
-  Accuracy is of particular importance, as our findings show that many defense
+  various defense mechanisms against web injection attacks. We propose
+  a model that highlights the key weaknesses enabling these attacks,
+  and that provides a common perspective for studying the available defenses.
+  We then categorize and analyze a set of 35 previously proposed defenses 
+  based on their accuracy, performance,
+  deployment, security, and availability characteristics.
+  Detection accuracy is of particular importance,
+  as our findings show that many defense
   mechanisms have been tested in a poor manner. In addition, we observe
@@
   of our analysis, with emphasis on factors that may hinder
-  the widespread adoption of attack detection mechanisms
-  in practice.
+  the widespread adoption of defenses in practice.
 
@@
 \begin{IEEEkeywords}
-Protection Mechanisms, Web Application Security, Code injection Attacks,
-Testing, Cross-Site Scripting.
+Protection mechanisms, web application security,
+SQL injection, XSS, CSRF.
 \end{IEEEkeywords}

### 2014-11-15 docs/questioning.tex

--- 2014-11-15 docs/questioning.tex
@@
 
-% @dimitro: move this to the analysis Section:
-% This scheme is an efficient scheme that focuses
-% on a specific category of {\sc xss} attacks and
-% takes into consideration many attack vectors
-% that many of the previous schemes do not.
-% Also: 
-% As the author of {\sc csse} state~\cite{PB05}, the prevention
-% of {\sc xss} attack requires a more complex analysis.
-
 \subsection{Improving Testing Accuracy}

### 2014-11-15 docs/questioning.tex
removed a comment
POI fixes

@@
 Attackers that would input the string {\tt anything' OR 'x'='x}
-would obtain the administrator's password by email. Savvy
+could obtain a user's password by email. Savvy
 programmers can use certain {\sc api} functions, such as {\sc php}'s
@@
   html}, typically via a parameter value, and inject their own content
-into the application's page. {\sc html} injection is mainly associated with {\sc
-  xss} attacks~\cite{BJM08,LZRL09}. An {\sc xss} attack based on
-{\sc html} injection though, can also be used as a
-vehicle for a {\sc csrf} attack. Consider a bulletin board system where
-{\tt img} tags are not checked. A malicious user could embed a {\sc
-  csrf} request within an {\tt img} tag in the following manner:
+into the application's page. {\sc html} injection is mainly associated
+with {\sc xss} attacks~\cite{BJM08,LZRL09}. However, {\sc html} injection,
+can also be used as a vehicle for a {\sc csrf} attack.
+Consider a bulletin board system where {\tt img} tags are not checked.
+A malicious user could embed a {\sc csrf} request within an
+{\tt img} tag in the following manner:
 
@@
 A recent attack called {\sc php} Object Injection
-({\sc poi})~\cite{DKH14} does not directly involve code
-injection and is performed by injecting malicious
-payloads (for example cookies) that when deserialized
-by the application, arbitrary code execution can be
-achieved. Note that the exploitation model that we propose
-in the following Section can represent such attacks too.
+({\sc poi})~\cite{DKH14} does not directly involve
+the injection of code, but still achieves arbitrary code execution
+in the context of a {\sc php} application through the
+injection of specially crafted objects.
+These objects are injected as part of cookies,
+which, when deserialized
+by the application, result in arbitrary code execution.
+Note that the exploitation model we propose
+in the following Section also captures such attacks.
 

### 2014-11-15 docs/questioning.tex
small changes
submitted version

@@
   In this paper, we systematize the existing knowledge on
-  various defense mechanisms against web injection attacks. We propose
+  various defense mechanisms against web code injection attacks. We propose
   a model that highlights the key weaknesses enabling these attacks,
@@
 script or domain-specific language code.
-Attacks of this type include Cross-Site Scripting ({\sc xss})
-attacks~\cite{SG07}, {\sc sql} injection~\cite{RL12b}, and
-Cross-Site Request Forgery ({\sc csrf}) attacks~\cite{LZRL09}, among
-others.
+Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SG07},
+{\sc sql} injection~\cite{RL12b}, and Cross-Site Request Forgery
+({\sc csrf}) attacks~\cite{LZRL09}, among others.
 
@@
 identifying some of the most critical risks organizations may face.
-In its three consecutive Top Ten lists (2007, 2010, 2013), different source
-code-driven injection attacks dominate the top five positions.
+In its three consecutive Top Ten lists (2007, 2010, 2013), different
+injection attacks dominate the top five positions.
 
@@
 of binary code---see Section~\ref{sec:attacks}.} This is validated by the fact that
-there are protection mechanisms that can defend against more than one of these
+some protection mechanisms defend against more than one of these
 types of attacks. Then, we {\it categorize} a selection of representative
@@
 with {\sc xss} attacks~\cite{BJM08,LZRL09}. However, {\sc html} injection,
-can also be used as a vehicle for a {\sc csrf} attack.
-Consider a bulletin board system where {\tt img} tags are not checked.
+can also be used as a vehicle for {\sc csrf} attacks.
+Consider a bulletin board system where {\tt img} tags are allowed.
 A malicious user could embed a {\sc csrf} request within an
@@
 different classes of injection attacks,
-such as SQL injection, XSS, and CSRF. Links between steps are
+such as {\sc sql} injection, {\sc xss}, and {\sc csrf}. Links between steps are
 labeled with the different attacks that use that path, while the
@@
 pattern. {\sc swap}~\cite{WPLKK09} creates a unique identifier
-({\it script {\sc id}}) for every legitimate script on the server.
+(script {\sc id}) for every legitimate script on the server.
 Then, a JavaScript detection component placed in a web proxy (Point
@@
 (like the ``Password only login" plugin of
-Wordpress\footnote{\url{https://wordpress.org/plugins/password-only-login/}})
+Wordpress~\cite{password})
 but allow the login either with the user's password or with
@@
 on the same applications. For example, 12 mechanisms were tested on a
-vulnerable version of the {\sc phpbb} bulletin board software.
+vulnerable version of the {\sc phpbb} bulletin board software~\cite{phpbb}.
 

### 2015-01-15 docs/rebuttal.txt
work on the first reviewer

- General Remarks:

We want to thank the reviewers for their meaningful comments.

- Reviewer 1:

# dimitro: I do not know exactly what to say about the following comment:
# "The sensitivity and specificity metrics are questionable (need
# justification and relation to standard techniques), and anyway not
# used much in Table I."
# What does he mean by justification? We provide the corresponding citations
# for the metrics. Finally, we can say that we can say that ce can calculate
# them and add them to the Table.

# dimitro: I do not know what to say about this...
# "The paper is tutorial-like and broad, which is not so bad by itself,
# but it is desirable of a SoK paper to contain more insight than a
# typical survey."

It is true that there are to many N/As in both Tables and especially in
Table II. However, we believe that issues concerning code availability and
accuracy testing are instantly identified by a casual reader.

We are planning to change the paper's title into: "Defending Against Code
Injection Attacks that target Web Applications: From Research Approaches
to Practical Tools".

# dimitro: or ""Defending Against Code Injection Attacks on the Web:
# From Research Approaches to Practical Tools"."
# If you have any other ideas let me know.

As we mention in the paper, we analyze and categorize mechanisms that have
been described in research papers. Still, we can include ADsafe,
Facebook JavaScript, and Secure EcmaScript in the paper in the way
we include Google Caja. In addition, we agree that we should include
FlowFox and JSand (both have >20 citations which is our threshold),
and the paper presenting IFC in WebKit's JavaScript Bytecode (which is
a recent work presented in a top venue). We could also include AdSentry, Contego
and JSFlow too but currently, they do not reach the citation threshold.

# dimitro: is POST (Conference on Principles of Security and Trust)
# a top venue?

We agree that some of the presented approaches utilize either static or
dynamic analysis. As we explain in the paper though, we dismiss the
static and dynamic approaches that identify vulnerabilities that
may lead to the attacks that we refer to and cover protection
mechanisms that stop such attacks when they are launched.

# dimitro: I do not fully understand the following:
# "The security discussion (Section IV) is somewhat minimalistic.
# Further, more insight would be helpful on the security of the systems
# and the attack surfaces covered beyond what is reported in Table I
# (which talks about the classical SQL injection, XSS, CSRF and known
# DOM-based, JSON injection, and XPath injection attacks)."

We can update our model to show where the language-level and web
framework-level protection mechanisms detect an attack. In particular
we can show that this is done at the application level within the server.

The comments concerning Firing Range, XCS attacks, scriptless attacks
and attacks that involve plug-ins are totally valid and we are
planning to address them in the next version of the paper.

- Reviewer 2:

- Reviewer 3:

- Reviewer 4:

### 2015-01-15 docs/reviewers_response.txt
add PL reviewers' response

Reviewer 1
==========

> -The sensitivity and specificity metrics are questionable (need
> justification and relation to standard techniques), and anyway not
> used much in Table I.

That's exactly what we try to highlight in the paper. Sensitivity and
specificity should be more widely applicable, but they are not,
because not enough data is given in the original publications. In
general, as we remark in VII.A, "In many cases researchers tend not to
provide the false positive and negative results that their tools may
produce."

Concerning the usefullness of sensitivity and specicifity as metrics
per se, their use in computer security has been advocated by other
researchers as well, for example ***.

Reviewer 2
==========

> The paper essentially provides only information that is directly
> available from other publications. This applies especially to the
> categories accuracy and performance overhead, where several mechanisms
> do not provide data. The authors of the paper did not perform any
> original tests.

Please note that even if we wanted to perform original tests on the
systems we studied, or even if we wanted to validate the existing
tests, we would not be able to do so in the vast majority of cases, as
indicated in Table II; this is in fact one of our main findings, as we
explain in VII.B.

Reviewer 3
==========

> From my understanding, sensitivity and specificity could also be
> expressed in terms of conditional probability: sensitivity is the
> conditional probability that the detection mechanism flags an attack,
> given that an attack is taking place, and specificity is the
> conditional probability that the mechanism does not report an attack,
> given that no attack takes place.

Correct. We can of course add that to the power; we just thought that
it might not be necessary to explain it.

> This would help in discerning and relating these measures from and to
> the positive and negative predictive values, and also explains
> formulas (5) and (6) on page 13.

Correct, as above we can easily add the explanations.

> Moreover, the discussion seems to be confusing experiment measurements
> and abstract probabilities.
> On page 2 [actually it's on p. 5], it is stated that "sensitivity
> and specificity can be calculated on test data alone".
> On page 13, it is said that "PPV and NPV ... relate to the
> effectiveness in an actual production environment".

This is to highlight that we cannot carry out a set of measurements,
calculate sensitity and specificity, and then using the {True | False
} {Positives | Negatives} calculate the PPV and the NPV from equations
3 and 4 directly. One has to go instead through equations 5 and 6.

> Obviously, any measurement of true and false positives and negatives
> on test data can be skewed, if the test data is skewed.
> Hence, if the sensitivity and specificity are measured using tests
> that do not relate to "the production environment", the calculated
> values are meaningless.

Definitely, we can highlight that.

> Yet this holds true for all four measures; it is simply related to the
> way they are estimated.
> The advantage of PPV and NPV is that they answer the question of
> "given a detection result, how much can you trust it?", which is more
> interesting in the "production environment".
>
> This part of the paper should be revised to give a clearer picture.

Taking into account all your related comments, we will do that, taking
care not to go through the paper length limits. The gist is that,
indeed, PPV and NPV answer the question you state; it is not always
possible to get data for them (since we may not know the prevalence),
but it may worth to try and get it, or this could be a new research
direction. Of course, if we do have such data, it is a way to
operationalize the protection a system provides.

The validity of test data is in fact important independently of
sensitivity and specificity; skewed test data will give a wrong
picture anyway, even if nobody bothers to calculate sensitivity and
specificity. We do not know in the papers we studies whether test data
were skewed. We do find, however, that: more tests could have been
carried out (cf. Table I and VII.A ) and the means to conduct tests should be
made available to third parties (cf. Table II and VII.B).

Reviewer 4
==========

> Similarly, the demand on taking the prevalence into consideration when
> evaluating false positives and false negatives may be an undue burden
> on security researchers, who would have a hard time collecting these
> probabilities. On the other hand, this might call for a common attack
> dataset.

That is why we state, in p. 13, that "With this in mind it may be
unfair to ask of researchers to provide PPV and NPV values for
their mechanisms---in fact, we see that nobody does." In the following
paragraph (last paragraph of first column in p. 13) we explore what
this would require. We can make it more clear.

### 2015-01-15 docs/rebuttal.txt
on Reviewer 2

@@
 
+# dimitro: maybe we need to mention that we cover only mechanisms
+# that have been presented in a research publication as a general
+# remark in the beginning of our response.
+
+We tried to equally cover every mechanism and then as the paper
+progresses we highlight the reasons why a mechanism may be widely
+used or not. In our conclusion section, we particularly mention
+that CSP is one of the few mechanisms that contrary to other approaches,
+has been presented in a research publication and at the same time
+is widely used. Furthermore, it is true that if a programmer uses
+secure coding practices (for instance prepared statements) then
+a mechanism that counters SQLIAs is not necessarily needed.
+However, as we mention in the paper, programmers are not always
+that careful and this is why protection mechanisms like SQLrand
+have been proposed in the first place.
+
+In the description of our model, we state that there are two
+ways to initiate the majority of the presented attacks.
+In both cases, the first steps will result to the same path.
+To distinguish these first step we use the 1 - 1.1 notation.
+The point concerning the PHP injection attack is valid. In general,
+we tried to illustrate the most known web injection attacks in our
+model. Still, with can easily incorporate such an attack in our model
+with minor modifications (the same applies to POI attacks as we
+already mention in the paper).
+
+Finally, our model covers attacks that utilize DSL languages in general
+(including SQL, XPath etc.), while in our categorization there is
+more than one countermeasure that protects from XPath injection attacks.
+
 - Reviewer 3:

### 2015-01-15 docs/rebuttal.txt
work on reviewer 3

@@
 
+As we mention in the introduction of our paper, we did not cover static
+analysis tools that detect vulnerabilities that lead to the covered attacks
+because there is a corresponding survey by that does exactly that [14].
+
+# dimitro: here we go again.
+
+As we also mentioned to the previous responses, we did not include
+in our categorization, mechanisms that have not been presented in
+a research paper. However, Caja is a very important mechanism
+and this is why we reference it in our paper and particularly as
+a framework that is widely used.
+
+We do agree with the comment on the "ease of use" dimension and we will
+address it in our next revision. Also, the comment about the EiQ is
+correct: it is DBAL. Finally, we will update our SQL injection
+example to make it clearer.
+
 - Reviewer 4:

### 2015-01-15 docs/rebuttal_merged.txt
merged two files

--- 2015-01-15 docs/rebuttal.txt
@@
 
-# dimitro: I do not know exactly what to say about the following comment:
-# "The sensitivity and specificity metrics are questionable (need
-# justification and relation to standard techniques), and anyway not
-# used much in Table I."
-# What does he mean by justification? We provide the corresponding citations
-# for the metrics. Finally, we can say that we can say that ce can calculate
-# them and add them to the Table.
+# --- Panos ---
+
+> -The sensitivity and specificity metrics are questionable (need
+> justification and relation to standard techniques), and anyway not
+> used much in Table I.
+
+That's exactly what we try to highlight in the paper. Sensitivity and
+specificity should be more widely applicable, but they are not,
+because not enough data is given in the original publications. In
+general, as we remark in VII.A, "In many cases researchers tend not to
+provide the false positive and negative results that their tools may
+produce."
+
+Concerning the usefullness of sensitivity and specicifity as metrics
+per se, their use in computer security has been advocated by other
+researchers as well, for example ***.
+
+# --- Dimitro ---
 
@@
 
+--- Panos ---
+
+> The paper essentially provides only information that is directly
+> available from other publications. This applies especially to the
+> categories accuracy and performance overhead, where several mechanisms
+> do not provide data. The authors of the paper did not perform any
+> original tests.
+
+Please note that even if we wanted to perform original tests on the
+systems we studied, or even if we wanted to validate the existing
+tests, we would not be able to do so in the vast majority of cases, as
+indicated in Table II; this is in fact one of our main findings, as we
+explain in VII.B.
+
+--- Dimitro ---
+
 # dimitro: maybe we need to mention that we cover only mechanisms
@@
 
+--- Dimitro ----
+
 As we mention in the introduction of our paper, we did not cover static
@@
 
+--- Panos ----
+
+> From my understanding, sensitivity and specificity could also be
+> expressed in terms of conditional probability: sensitivity is the
+> conditional probability that the detection mechanism flags an attack,
+> given that an attack is taking place, and specificity is the
+> conditional probability that the mechanism does not report an attack,
+> given that no attack takes place.
+
+Correct. We can of course add that to the power; we just thought that
+it might not be necessary to explain it.
+
+> This would help in discerning and relating these measures from and to
+> the positive and negative predictive values, and also explains
+> formulas (5) and (6) on page 13.
+
+Correct, as above we can easily add the explanations.
+
+> Moreover, the discussion seems to be confusing experiment measurements
+> and abstract probabilities.
+> On page 2 [actually it's on p. 5], it is stated that "sensitivity
+> and specificity can be calculated on test data alone".
+> On page 13, it is said that "PPV and NPV ... relate to the
+> effectiveness in an actual production environment".
+
+This is to highlight that we cannot carry out a set of measurements,
+calculate sensitity and specificity, and then using the {True | False
+} {Positives | Negatives} calculate the PPV and the NPV from equations
+3 and 4 directly. One has to go instead through equations 5 and 6.
+
+> Obviously, any measurement of true and false positives and negatives
+> on test data can be skewed, if the test data is skewed.
+> Hence, if the sensitivity and specificity are measured using tests
+> that do not relate to "the production environment", the calculated
+> values are meaningless.
+
+Definitely, we can highlight that.
+
+> Yet this holds true for all four measures; it is simply related to the
+> way they are estimated.
+> The advantage of PPV and NPV is that they answer the question of
+> "given a detection result, how much can you trust it?", which is more
+> interesting in the "production environment".
+>
+> This part of the paper should be revised to give a clearer picture.
+
+Taking into account all your related comments, we will do that, taking
+care not to go through the paper length limits. The gist is that,
+indeed, PPV and NPV answer the question you state; it is not always
+possible to get data for them (since we may not know the prevalence),
+but it may worth to try and get it, or this could be a new research
+direction. Of course, if we do have such data, it is a way to
+operationalize the protection a system provides.
+
+The validity of test data is in fact important independently of
+sensitivity and specificity; skewed test data will give a wrong
+picture anyway, even if nobody bothers to calculate sensitivity and
+specificity. We do not know in the papers we studies whether test data
+were skewed. We do find, however, that: more tests could have been
+carried out (cf. Table I and VII.A ) and the means to conduct tests should be
+made available to third parties (cf. Table II and VII.B).
+
 - Reviewer 4:
+
+--- Dimitro ---
+
+We need to make clear that we do not want to criticize the lack of testing
+in etiological mechanisms. We try to investigate the reason why such mechanisms
+are not widely used and we suggest that this is one reason.
+
+--- Panos ---
+
+> Similarly, the demand on taking the prevalence into consideration when
+> evaluating false positives and false negatives may be an undue burden
+> on security researchers, who would have a hard time collecting these
+> probabilities. On the other hand, this might call for a common attack
+> dataset.
+
+That is why we state, in p. 13, that "With this in mind it may be
+unfair to ask of researchers to provide PPV and NPV values for
+their mechanisms---in fact, we see that nobody does." In the following
+paragraph (last paragraph of first column in p. 13) we explore what
+this would require. We can make it more clear.

### 2015-01-16 docs/rebuttal_merged.txt
more on the response --- still there are too many words

--- 2015-01-15 docs/rebuttal.txt
@@
-- General Remarks:
-
 We want to thank the reviewers for their meaningful comments.
 
-- Reviewer 1:
+As a general remark we need to say that as we state in the
+paper, we did not include in our categorization mechanisms that
+have not been presented in a research paper. However, Caja
+is an important mechanism and this is why we reference it
+as a framework that is widely used. Also, we are aware
+that some of the presented approaches utilize
+either static or dynamic analysis. As we explain in the paper though,
+we dismiss static and dynamic approaches that identify
+vulnerabilities that may lead to injection attacks
+(there is a corresponding survey that covers this area [14])
+and cover protection mechanisms that counter such attacks when
+they take place.
 
-# dimitro: I do not know exactly what to say about the following comment:
-# "The sensitivity and specificity metrics are questionable (need
-# justification and relation to standard techniques), and anyway not
-# used much in Table I."
-# What does he mean by justification? We provide the corresponding citations
-# for the metrics. Finally, we can say that we can say that ce can calculate
-# them and add them to the Table.
+Rev1:
 
-# dimitro: I do not know what to say about this...
-# "The paper is tutorial-like and broad, which is not so bad by itself,
-# but it is desirable of a SoK paper to contain more insight than a
-# typical survey."
+Concerning the skepticism on the sensitivity and specificity metrics
+we need to mention that these metrics should be more widely applicable,
+but they are not, because not enough data is given in the
+original publications as we remark in VII.A. Also, the
+usefulness of such metrics in computer security has been advocated
+by other researchers as well, as we discuss in the same Section.
 
@@
 
-We are planning to change the paper's title into: "Defending Against Code
-Injection Attacks that target Web Applications: From Research Approaches
-to Practical Tools".
+We agree that we should (and we will) incorporate the term "injection"
+into the paper's title.
 
-# dimitro: or ""Defending Against Code Injection Attacks on the Web:
-# From Research Approaches to Practical Tools"."
-# If you have any other ideas let me know.
+We can include ADsafe etc. in the paper in the way we
+include Google Caja. Also, we will include FlowFox and
+JSand (both have >20 citations --- our threshold),
+and the paper presenting IFC in WebKit's
+JavaScript Bytecode (which is a recent paper presented in a
+respected venue) in the paper. We could also include AdSentry,
+Contego and JSFlow too, but they do not reach our citation threshold.
 
-As we mention in the paper, we analyze and categorize mechanisms that have
-been described in research papers. Still, we can include ADsafe,
-Facebook JavaScript, and Secure EcmaScript in the paper in the way
-we include Google Caja. In addition, we agree that we should include
-FlowFox and JSand (both have >20 citations which is our threshold),
-and the paper presenting IFC in WebKit's JavaScript Bytecode (which is
-a recent work presented in a top venue). We could also include AdSentry, Contego
-and JSFlow too but currently, they do not reach the citation threshold.
+We agree that using "security" as a term for one of our dimensions
+may be misleading since it is a generic term and in this case
+we need to make it more specific.
 
-# dimitro: is POST (Conference on Principles of Security and Trust)
-# a top venue?
+The point about the minimalism of the security discussion is actually
+pretty good and we will try to enrich this part. A first attempt
+would be to say that approaches that provide systematic
+arguments on why their designs are secure, are not as
+by-passable as the approaches coming from the other
+category.
 
-We agree that some of the presented approaches utilize either static or
-dynamic analysis. As we explain in the paper though, we dismiss the
-static and dynamic approaches that identify vulnerabilities that
-may lead to the attacks that we refer to and cover protection
-mechanisms that stop such attacks when they are launched.
-
-# dimitro: I do not fully understand the following:
-# "The security discussion (Section IV) is somewhat minimalistic.
-# Further, more insight would be helpful on the security of the systems
-# and the attack surfaces covered beyond what is reported in Table I
-# (which talks about the classical SQL injection, XSS, CSRF and known
-# DOM-based, JSON injection, and XPath injection attacks)."
-
-We can update our model to show where the language-level and web
-framework-level protection mechanisms detect an attack. In particular
-we can show that this is done at the application level within the server.
+We can update our model to show where the language and web
+framework-level protection mechanisms detect an attack
+(the point would be at the application level within the server).
 
 The comments concerning Firing Range, XCS attacks, scriptless attacks
-and attacks that involve plug-ins are totally valid and we are
-planning to address them in the next version of the paper.
+and attacks that involve plug-ins are valid and we are
+planning to address them.
 
-- Reviewer 2:
+Rev2:
 
-# dimitro: maybe we need to mention that we cover only mechanisms
-# that have been presented in a research publication as a general
-# remark in the beginning of our response.
+Please note that even if we wanted to perform original tests on the
+systems we studied, or even if we wanted to validate the existing
+tests, we would not be able to do so in the vast majority of cases, as
+indicated in Table II; this is in fact one of our main findings, as we
+explain in VII.B.
 
@@
 used or not. In our conclusion section, we particularly mention
-that CSP is one of the few mechanisms that contrary to other approaches,
+that CSP is one of the few mechanisms that contrary to others,
 has been presented in a research publication and at the same time
 is widely used. Furthermore, it is true that if a programmer uses
-secure coding practices (for instance prepared statements) then
+secure coding practices like prepared statements, then
 a mechanism that counters SQLIAs is not necessarily needed.
@@
 
-In the description of our model, we state that there are two
+In our model description, we state that there are two
 ways to initiate the majority of the presented attacks.
 In both cases, the first steps will result to the same path.
-To distinguish these first step we use the 1 - 1.1 notation.
+To distinguish these first steps we use the 1 - 1.1 notation.
 The point concerning the PHP injection attack is valid. In general,
-we tried to illustrate the most known web injection attacks in our
-model. Still, with can easily incorporate such an attack in our model
-with minor modifications (the same applies to POI attacks as we
-already mention in the paper).
+we tried to illustrate the most known injection attacks in our
+model. Still, we can incorporate such an attack in our model
+with minor modifications.
 
-Finally, our model covers attacks that utilize DSL languages in general
-(including SQL, XPath etc.), while in our categorization there is
-more than one countermeasure that protects from XPath injection attacks.
+Finally, our model covers attacks that utilize DSL languages in general,
+while in our categorization there is more than one countermeasures that
+protects from XPath injection attacks.
 
-- Reviewer 3:
+Rev3:
 
-- Reviewer 4:
+We do agree with the comment on the "ease of use" dimension and we will
+address it in our next revision. Also, the comment about the EiQ is
+correct: it is DBAL. Finally, we will update our SQL injection
+example to make it clearer.
+
+We fully agree with the the fact that the sensitivity and specificity
+metrics could also be expressed in terms of conditional probability
+and we can add that to the power.
+
+With our discussion in page 2 and 13 respectively we
+want to highlight that we cannot carry out a set of measurements,
+calculate sensitivity and specificity, and then using the {True | False
+} {Positives | Negatives} calculate the PPV and the NPV from equations
+3 and 4 directly. One has to go instead through equations 5 and 6.
+
+Taking into account all the related comments, we will
+update the paper to highlight the advantages of PPV and NPV.
+The gist is that, indeed, PPV and NPV answer the question
+about trusting a detection result; it is not always
+possible to get data for them (since we may not know the prevalence),
+but it may worth to try and get it, or this could be a new research
+direction. Of course, if we do have such data, it is a way to
+operationalize the protection a system provides.
+
+The comment on the skewed data is valid and we can
+elaborate on it more. The validity of test data is in fact
+important independently of sensitivity and specificity;
+skewed test data will give a wrong picture anyway, even if nobody
+bothers to calculate the metrics. We do not know in the
+papers we studied whether test data were skewed. We do find,
+however, that: more tests could have been
+carried out (Table I and VII.A) and the means to conduct tests should be
+made available to third parties (Table II and VII.B).
+
+Rev4:
+
+We need to make clear that we do not want to criticize the lack of testing
+in etiological mechanisms. In fact, we try to investigate
+the reason why such mechanisms are not widely used and we suggest
+that this is one reason.
+
+Regarding the comment about demanding prevalence, we need to say that
+as we state in the paper, it may be unfair to ask of
+researchers to provide PPV and NPV values for
+their mechanisms---in fact, nobody does. In the
+last paragraph of first column in p.13 we explore what
+this would require. We can elaborate more.

### 2015-01-16 docs/rebuttal_merged.txt
minor addition
squeezing

@@
-We want to thank the reviewers for their meaningful comments.
+We thank the reviewers for their insightful comments.
 
-As a general remark we need to say that as we state in the
-paper, we did not include in our categorization mechanisms that
-have not been presented in a research paper. However, Caja
-is an important mechanism and this is why we reference it
-as a framework that is widely used. Also, we are aware
-that some of the presented approaches utilize
-either static or dynamic analysis. As we explain in the paper though,
-we dismiss static and dynamic approaches that identify
-vulnerabilities that may lead to injection attacks
-(there is a corresponding survey that covers this area [14])
-and cover protection mechanisms that counter such attacks when
-they take place.
+Overall, we did not consider mechanisms that
+have not been presented in research papers. We mention Caja
+due to its importance and popularity.  Also, although
+some of the presented works use
+static/dynamic analysis, we do not
+consider the broader area of static/dynamic analysis for
+vulnerability detection (another paper covers that area [14]),
+but focus only on protections against attacks
+that might exploit such vulnerabilities.
 
@@
 
-Concerning the skepticism on the sensitivity and specificity metrics
-we need to mention that these metrics should be more widely applicable,
-but they are not, because not enough data is given in the
-original publications as we remark in VII.A. Also, the
+Sensitivity and specificity should be more widely applicable,
+but not enough data is given in the
+original publications, as mentioned in VII.A. The
 usefulness of such metrics in computer security has been advocated
-by other researchers as well, as we discuss in the same Section.
+by other researchers as mentioned in the same section.
 
-It is true that there are to many N/As in both Tables and especially in
-Table II. However, we believe that issues concerning code availability and
-accuracy testing are instantly identified by a casual reader.
+It is true that there are too many N/As, especially
+Table II, but this actually highlights the issues regarding
+code availability and accuracy testing.
 
-We agree that we should (and we will) incorporate the term "injection"
-into the paper's title.
+We agree that "injection" should be part of the title,
+and we will incorporate it.
 
-We can include ADsafe etc. in the paper in the way we
-include Google Caja. Also, we will include FlowFox and
-JSand (both have >20 citations --- our threshold),
-and the paper presenting IFC in WebKit's
-JavaScript Bytecode (which is a recent paper presented in a
-respected venue) in the paper. We could also include AdSentry,
-Contego and JSFlow too, but they do not reach our citation threshold.
+We will include FlowFox and JSand (both have >20 citations),
+the paper presenting IFC in WebKit's
+JavaScript Bytecode (a recent paper)
+and discuss ADsafe etc. in the same way as Google Caja.
+AdSentry, Contego, and JSFlow 
+do not reach our citation threshold.
 
-We agree that using "security" as a term for one of our dimensions
-may be misleading since it is a generic term and in this case
-we need to make it more specific.
+We agree that using "security" as a dimension
+is misleading---we use it in the sense of "bypassability", which is 
+orthogonal to "accuracy". We will replace it with a more specific term.
 
-The point about the minimalism of the security discussion is actually
-pretty good and we will try to enrich this part. A first attempt
-would be to say that approaches that provide systematic
+We fully agree with the point about the minimalism of the security discussion,
+and will try to enrich this part. For instance,
+approaches that provide systematic
 arguments on why their designs are secure, are not as
-by-passable as the approaches coming from the other
-category.
+"bypassable" as heuristic/threshold-based approaches.
 
@@
 
-The comments concerning Firing Range, XCS attacks, scriptless attacks
-and attacks that involve plug-ins are valid and we are
-planning to address them.
+The comments about Firing Range, XCS attacks, scriptless attacks,
+and attacks that involve plug-ins are valid and we will address them.
 
@@
 
-Please note that even if we wanted to perform original tests on the
-systems we studied, or even if we wanted to validate the existing
-tests, we would not be able to do so in the vast majority of cases, as
-indicated in Table II; this is in fact one of our main findings, as we
-explain in VII.B.
+The lack of code availability for most systems 
+makes performing original tests challenging.
+This is in fact one of our findings, as we explain in VII.B.
 
-We tried to equally cover every mechanism and then as the paper
-progresses we highlight the reasons why a mechanism may be widely
+We attempted to equally cover every mechanism and then
+highlight the reasons why a mechanism may be widely
 used or not. In our conclusion section, we particularly mention
-that CSP is one of the few mechanisms that contrary to others,
-has been presented in a research publication and at the same time
-is widely used. Furthermore, it is true that if a programmer uses
+that CSP is one of the few that 
+has been published and is widely used.
+It is true that if a programmer uses
 secure coding practices like prepared statements, then
-a mechanism that counters SQLIAs is not necessarily needed.
-However, as we mention in the paper, programmers are not always
-that careful and this is why protection mechanisms like SQLrand
-have been proposed in the first place.
+SQLi protections are not required.
+However, best programming practices are not always followed,
+and this motivates proposals like SQLrand,
+which might be easier to retrofit in existing code bases.
 
-In our model description, we state that there are two
-ways to initiate the majority of the presented attacks.
-In both cases, the first steps will result to the same path.
-To distinguish these first steps we use the 1 - 1.1 notation.
-The point concerning the PHP injection attack is valid. In general,
-we tried to illustrate the most known injection attacks in our
-model. Still, we can incorporate such an attack in our model
-with minor modifications.
-
-Finally, our model covers attacks that utilize DSL languages in general,
-while in our categorization there is more than one countermeasures that
-protects from XPath injection attacks.
+We use the 1/1.1 notation to distinguish some shared states by the two main ways
+attacks in our model can be initiated---we will explore a more clear representation.
+The point regarding PHP injection attacks is valid.
+We tried to capture the most known injection attacks,
+and we will incorporate this attack with a few minor modifications to the model.
+Our model covers attacks that utilize DSL languages in general,
+and in our categorization there are more than one countermeasures that
+protect from XPath injection attacks.
 
@@
 
-We do agree with the comment on the "ease of use" dimension and we will
-address it in our next revision. Also, the comment about the EiQ is
-correct: it is DBAL. Finally, we will update our SQL injection
-example to make it clearer.
+We agree with the comment on the "ease of use" dimension and we will
+address it. Also, the comment about the EiQ is
+correct: it is DBAL. We will make our SQLi example clearer.
 
-We fully agree with the the fact that the sensitivity and specificity
-metrics could also be expressed in terms of conditional probability
-and we can add that to the power.
+We fully agree that sensitivity and specificity
+could be expressed in terms of a conditional probability---we will
+include this in the paper.
 
-With our discussion in page 2 and 13 respectively we
-want to highlight that we cannot carry out a set of measurements,
-calculate sensitivity and specificity, and then using the {True | False
-} {Positives | Negatives} calculate the PPV and the NPV from equations
+Our discussion in pages 2 and 13 respectively
+highlights that we cannot carry out a set of measurements,
+calculate sensitivity and specificity, and then using {True|False}
+{Positives|Negatives} calculate PPV and NPV from equations
 3 and 4 directly. One has to go instead through equations 5 and 6.
 
-Taking into account all the related comments, we will
-update the paper to highlight the advantages of PPV and NPV.
+Taking into account all related comments, we will
+highlight the advantages of PPV and NPV.
 The gist is that, indeed, PPV and NPV answer the question
@@
 possible to get data for them (since we may not know the prevalence),
-but it may worth to try and get it, or this could be a new research
+but it may be worth it to try and get it, or this could be a new research
 direction. Of course, if we do have such data, it is a way to
@@
 
-We need to make clear that we do not want to criticize the lack of testing
-in etiological mechanisms. In fact, we try to investigate
-the reason why such mechanisms are not widely used and we suggest
+We do not intend to criticize the lack of testing
+in etiological mechanisms. We attempt to 
+explore why such mechanisms are not widely used, and suggest
 that this is one reason.
 
-Regarding the comment about demanding prevalence, we need to say that
-as we state in the paper, it may be unfair to ask of
-researchers to provide PPV and NPV values for
+Regarding the comment about demanding prevalence,
+it may be unfair to ask of researchers to provide PPV and NPV values for
 their mechanisms---in fact, nobody does. In the
-last paragraph of first column in p.13 we explore what
-this would require. We can elaborate more.
+p.13 we explore what this would require---we will elaborate more.
+
+Finally, we will discuss more incentives
+that the community could provide to improve code availability.

### 2015-01-16 docs/rebuttal_merged.txt
cutting down

@@
 
-It is true that there are too many N/As, especially
-Table II, but this actually highlights the issues regarding
-code availability and accuracy testing.
+There are too many N/As, especially Table II, but this actually
+highlights the issues regarding code availability and accuracy
+testing.
 
@@
 
-We fully agree with the point about the minimalism of the security discussion,
-and will try to enrich this part. For instance,
-approaches that provide systematic
-arguments on why their designs are secure, are not as
+We fully agree about the minimalism of the security discussion, and
+will try to enrich this part. For instance, approaches that provide
+systematic arguments on why their designs are secure, are not as
 "bypassable" as heuristic/threshold-based approaches.
@@
 
-The lack of code availability for most systems 
-makes performing original tests challenging.
-This is in fact one of our findings, as we explain in VII.B.
+The lack of code availability for most systems makes performing
+original tests challenging. This is in fact one of our findings, as we
+explain in VII.B.
 
@@
 
-We use the 1/1.1 notation to distinguish some shared states by the two main ways
-attacks in our model can be initiated---we will explore a more clear representation.
-The point regarding PHP injection attacks is valid.
-We tried to capture the most known injection attacks,
-and we will incorporate this attack with a few minor modifications to the model.
-Our model covers attacks that utilize DSL languages in general,
+We use the 1/1.1 notation to distinguish some shared states by the two
+main ways attacks in our model can be initiated---we will explore a
+clearer representation. The point regarding PHP injection attacks
+is valid. We tried to capture the most known injection attacks, and we
+will incorporate this attack with a few minor modifications to the
+model. Our model covers attacks that utilize DSL languages in general,
 and in our categorization there are more than one countermeasures that
@@
 
-We fully agree that sensitivity and specificity
-could be expressed in terms of a conditional probability---we will
-include this in the paper.
+Of course sensitivity and specificity could be expressed in terms of a
+conditional probability---we will include this in the paper.
 
-Our discussion in pages 2 and 13 respectively
-highlights that we cannot carry out a set of measurements,
-calculate sensitivity and specificity, and then using {True|False}
-{Positives|Negatives} calculate PPV and NPV from equations
-3 and 4 directly. One has to go instead through equations 5 and 6.
+Our discussion in pages 2 and 13 respectively highlights that we
+cannot carry out a set of measurements, calculate sensitivity and
+specificity, and then using {True|False} {Positives|Negatives}
+calculate PPV and NPV from equations 3 and 4 directly. One has to go
+instead through equations 5 and 6.
 
-Taking into account all related comments, we will
-highlight the advantages of PPV and NPV.
-The gist is that, indeed, PPV and NPV answer the question
-about trusting a detection result; it is not always
-possible to get data for them (since we may not know the prevalence),
-but it may be worth it to try and get it, or this could be a new research
-direction. Of course, if we do have such data, it is a way to
-operationalize the protection a system provides.
+We will expand on the advantages of PPV and NPV. PPV and NPV answer
+the question about trusting a detection result; however,it is not
+always possible to get data for them as we indicate in p. 13.
 
-The comment on the skewed data is valid and we can
-elaborate on it more. The validity of test data is in fact
-important independently of sensitivity and specificity;
-skewed test data will give a wrong picture anyway, even if nobody
-bothers to calculate the metrics. We do not know in the
-papers we studied whether test data were skewed. We do find,
-however, that: more tests could have been
-carried out (Table I and VII.A) and the means to conduct tests should be
-made available to third parties (Table II and VII.B).
+The comment on the skewed data is valid. The validity of test data is
+important independently of sensitivity and specificity. We do not know
+in the papers we studied whether test data were skewed. We do find,
+however, that: more tests could have been carried out (Table I and
+VII.A) and the means to conduct tests should be made available to
+third parties (Table II and VII.B).
 
@@
 
-Regarding the comment about demanding prevalence,
-it may be unfair to ask of researchers to provide PPV and NPV values for
-their mechanisms---in fact, nobody does. In the
-p.13 we explore what this would require---we will elaborate more.
+Regarding the comment about demanding prevalence, it may be unfair to
+ask of researchers to provide PPV and NPV values for their mechanisms.
+In the p.13 we explore what this would require---we will elaborate
+more.
 

### 2015-01-16 docs/rebuttal_merged.txt
now 720

@@
 
-Overall, we did not consider mechanisms that
-have not been presented in research papers. We mention Caja
+Overall, we didn't consider mechanisms that
+haven't been presented in research papers. We mention Caja
 due to its importance and popularity.  Also, although
 some of the presented works use
-static/dynamic analysis, we do not
+static/dynamic analysis, we don't
 consider the broader area of static/dynamic analysis for
@@
 
+In general, we will update our text and our model
+to address the various issues indicated by the
+the reviewers like the paper's title,
+the point where language protection mechanisms detect an attack,
+the "ease of use" dimension, the SQLi example,
+and the code availability discussion.
+
 Rev1:
@@
 but not enough data is given in the
-original publications, as mentioned in VII.A. The
-usefulness of such metrics in computer security has been advocated
-by other researchers as mentioned in the same section.
+original publications (see VII.A).
+The usefulness of such metrics in computer security
+has been advocated by other researchers too, such as
+Pfleeger and Pfleeger (Analyzing Computer Security:
+A Threat/Vulnerability/Countermeasure Approach,
+Prentice Hall, 2011); we’ll add the citations.
 
@@
 
-We agree that "injection" should be part of the title,
-and we will incorporate it.
-
 We will include FlowFox and JSand (both have >20 citations),
@@
 JavaScript Bytecode (a recent paper)
-and discuss ADsafe etc. in the same way as Google Caja.
+and discuss ADsafe etc. in the same way as Caja.
 AdSentry, Contego, and JSFlow 
-do not reach our citation threshold.
+don't reach our citation threshold.
 
@@
 will try to enrich this part. For instance, approaches that provide
-systematic arguments on why their designs are secure, are not as
+systematic arguments on why their designs are secure, aren't as
 "bypassable" as heuristic/threshold-based approaches.
-
-We can update our model to show where the language and web
-framework-level protection mechanisms detect an attack
-(the point would be at the application level within the server).
-
-The comments about Firing Range, XCS attacks, scriptless attacks,
-and attacks that involve plug-ins are valid and we will address them.
 
@@
 The lack of code availability for most systems makes performing
-original tests challenging. This is in fact one of our findings, as we
+original tests challenging, which is one of our findings, as we
 explain in VII.B.
@@
 has been published and is widely used.
-It is true that if a programmer uses
+It is true that if programmers use
 secure coding practices like prepared statements, then
-SQLi protections are not required.
-However, best programming practices are not always followed,
+SQLi protections aren't required.
+However, best programming practices aren't always followed,
 and this motivates proposals like SQLrand,
@@
 We use the 1/1.1 notation to distinguish some shared states by the two
-main ways attacks in our model can be initiated---we will explore a
+main ways attacks in our model can be initiated---we'll explore a
 clearer representation. The point regarding PHP injection attacks
@@
 and in our categorization there are more than one countermeasures that
-protect from XPath injection attacks.
+protect from XPathi.
 
 Rev3:
-
-We agree with the comment on the "ease of use" dimension and we will
-address it. Also, the comment about the EiQ is
-correct: it is DBAL. We will make our SQLi example clearer.
 
@@
 
-Our discussion in pages 2 and 13 respectively highlights that we
+Our discussion in pages 2 and 13 highlights that we
 cannot carry out a set of measurements, calculate sensitivity and
@@
 We will expand on the advantages of PPV and NPV. PPV and NPV answer
-the question about trusting a detection result; however,it is not
+the question about trusting a detection result; however,it isn't
 always possible to get data for them as we indicate in p. 13.
@@
 The comment on the skewed data is valid. The validity of test data is
-important independently of sensitivity and specificity. We do not know
+important independently of sensitivity and specificity. We don't know
 in the papers we studied whether test data were skewed. We do find,
@@
 
-We do not intend to criticize the lack of testing
+We don't intend to criticize the lack of testing
 in etiological mechanisms. We attempt to 
-explore why such mechanisms are not widely used, and suggest
+explore why such mechanisms aren't widely used, and suggest
 that this is one reason.
@@
 more.
-
-Finally, we will discuss more incentives
-that the community could provide to improve code availability.

### 2015-01-16 docs/rebuttal_merged.txt
664 words

@@
 haven't been presented in research papers. We mention Caja
-due to its importance and popularity.  Also, although
-some of the presented works use
+due to its importance.
+
+Although some of the presented works use
 static/dynamic analysis, we don't
@@
 but focus only on protections against attacks
-that might exploit such vulnerabilities.
+that exploit such vulnerabilities.
 
-In general, we will update our text and our model
-to address the various issues indicated by the
-the reviewers like the paper's title,
+We will update our paper
+to address the issues indicated by the
+the reviewers, i.e. the title,
 the point where language protection mechanisms detect an attack,
 the "ease of use" dimension, the SQLi example,
-and the code availability discussion.
+the fact that we fail to capture PHP injection in our model,
+the 1/1.1 notation in our model, and
+the code availability discussion.
 
@@
 Sensitivity and specificity should be more widely applicable,
-but not enough data is given in the
-original publications (see VII.A).
+but not enough data is given in the publications (see VII.A).
 The usefulness of such metrics in computer security
-has been advocated by other researchers too, such as
+has been advocated by other researchers too, i.e.
 Pfleeger and Pfleeger (Analyzing Computer Security:
@@
 
-We fully agree about the minimalism of the security discussion, and
+We agree about the minimalism of the security discussion, and
 will try to enrich this part. For instance, approaches that provide
@@
 
-We attempted to equally cover every mechanism and then
+We attempt to equally cover every mechanism and then
 highlight the reasons why a mechanism may be widely
@@
 
-We use the 1/1.1 notation to distinguish some shared states by the two
-main ways attacks in our model can be initiated---we'll explore a
-clearer representation. The point regarding PHP injection attacks
-is valid. We tried to capture the most known injection attacks, and we
-will incorporate this attack with a few minor modifications to the
-model. Our model covers attacks that utilize DSL languages in general,
-and in our categorization there are more than one countermeasures that
-protect from XPathi.
+Our model covers attacks that utilize DSL languages in
+general, and in our categorization there are more than
+one countermeasures that protect from XPathi.
 
@@
 Our discussion in pages 2 and 13 highlights that we
-cannot carry out a set of measurements, calculate sensitivity and
-specificity, and then using {True|False} {Positives|Negatives}
+cannot perform a set of measurements, calculate sensitivity and
+specificity, and then using {True|False} {Positives|Negatives},
 calculate PPV and NPV from equations 3 and 4 directly. One has to go
@@
 We will expand on the advantages of PPV and NPV. PPV and NPV answer
-the question about trusting a detection result; however,it isn't
-always possible to get data for them as we indicate in p. 13.
+the question about trusting a detection result; however, it isn't
+always possible to get data for them as we indicate in p.13.
 
@@
 important independently of sensitivity and specificity. We don't know
-in the papers we studied whether test data were skewed. We do find,
-however, that: more tests could have been carried out (Table I and
+in the papers we studied if test data were skewed. We do find,
+though, that: more tests could have been performed (Table I and
 VII.A) and the means to conduct tests should be made available to
@@
 ask of researchers to provide PPV and NPV values for their mechanisms.
-In the p.13 we explore what this would require---we will elaborate
+In p.13 we explore what this would require---we will elaborate
 more.

### 2015-01-16 docs/rebuttal_merged.txt
reduce further

@@
 
-Overall, we didn't consider mechanisms that
-haven't been presented in research papers. We mention Caja
-due to its importance.
+Some general points:
 
-Although some of the presented works use
-static/dynamic analysis, we don't
-consider the broader area of static/dynamic analysis for
-vulnerability detection (another paper covers that area [14]),
-but focus only on protections against attacks
-that exploit such vulnerabilities.
+* We didn't consider mechanisms that haven't been presented in
+research papers. We mention Caja due to its importance.
 
-We will update our paper
-to address the issues indicated by the
-the reviewers, i.e. the title,
-the point where language protection mechanisms detect an attack,
-the "ease of use" dimension, the SQLi example,
-the fact that we fail to capture PHP injection in our model,
-the 1/1.1 notation in our model, and
-the code availability discussion.
+* Although some of the presented works use static/dynamic analysis, we
+ don't consider that area (another paper covers it [14]), but
+ focus only on protections against attacks that exploit such
+ vulnerabilities.
+
+* We will update our paper to address the issues indicated by the the
+  reviewers, i.e. the title, the point where language protection
+  mechanisms detect an attack, the "ease of use" dimension, the SQLi
+  example, the fact that we fail to capture PHP injection in our
+  model, the 1/1.1 notation in our model, and the code availability
+  discussion.
 
@@
 
-Sensitivity and specificity should be more widely applicable,
-but not enough data is given in the publications (see VII.A).
-The usefulness of such metrics in computer security
-has been advocated by other researchers too, i.e.
-Pfleeger and Pfleeger (Analyzing Computer Security:
-A Threat/Vulnerability/Countermeasure Approach,
-Prentice Hall, 2011); we’ll add the citations.
+Sensitivity and specificity should be more widely applicable, but not
+enough data is given in the publications (see VII.A). The usefulness
+of such metrics in computer security has been advocated by others,
+i.e. Pfleeger and Pfleeger (Analyzing Computer Security: A
+Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011);
+we’ll add the citation.
 
-There are too many N/As, especially Table II, but this actually
-highlights the issues regarding code availability and accuracy
-testing.
+There are too many N/As in Table II, but this actually highlights the
+issues regarding code availability and accuracy testing.
 
-We will include FlowFox and JSand (both have >20 citations),
-the paper presenting IFC in WebKit's
-JavaScript Bytecode (a recent paper)
-and discuss ADsafe etc. in the same way as Caja.
-AdSentry, Contego, and JSFlow 
-don't reach our citation threshold.
+We will include FlowFox and JSand, the paper presenting IFC in
+WebKit's JavaScript Bytecode and discuss ADsafe etc. and Caja.
+AdSentry, Contego, and JSFlow don't reach our citation threshold.
 
-We agree that using "security" as a dimension
-is misleading---we use it in the sense of "bypassability", which is 
-orthogonal to "accuracy". We will replace it with a more specific term.
+Using "security" as a dimension is misleading---we mean ease of
+circunvention, which is orthogonal to "accuracy". We
+will replace it with a more specific term.
 
-We agree about the minimalism of the security discussion, and
-will try to enrich this part. For instance, approaches that provide
-systematic arguments on why their designs are secure, aren't as
-"bypassable" as heuristic/threshold-based approaches.
+We'll enrich the security discussion. For instance, approaches that
+provide systematic arguments on why their designs are secure, cannot
+be circumvented like heuristic/threshold-based approaches.
 
@@
 The lack of code availability for most systems makes performing
-original tests challenging, which is one of our findings, as we
-explain in VII.B.
+original tests challenging, which is one of our findings (VII.B).
 
-We attempt to equally cover every mechanism and then
-highlight the reasons why a mechanism may be widely
-used or not. In our conclusion section, we particularly mention
-that CSP is one of the few that 
-has been published and is widely used.
-It is true that if programmers use
-secure coding practices like prepared statements, then
-SQLi protections aren't required.
-However, best programming practices aren't always followed,
-and this motivates proposals like SQLrand,
-which might be easier to retrofit in existing code bases.
+We attempt to cover mechanisms and then highlight reasons why a
+mechanism may not be widely used. In the conclusions we mention that
+CSP is one of the few that has been published and is widely used. It
+is true that if programmers use secure coding practices like prepared
+statements, then SQLi protections aren't required. However, that may
+not happen, and this motivates proposals like SQLrand, which might be
+easier to retrofit in existing code bases.
 
-Our model covers attacks that utilize DSL languages in
-general, and in our categorization there are more than
-one countermeasures that protect from XPathi.
+Our model covers attacks that utilize DSL languages in general, and in
+our categorization there are more than one countermeasures that
+protect from XPathi.
 
@@
 
-Of course sensitivity and specificity could be expressed in terms of a
+Sensitivity and specificity could be expressed in terms of a
 conditional probability---we will include this in the paper.
 
-Our discussion in pages 2 and 13 highlights that we
-cannot perform a set of measurements, calculate sensitivity and
-specificity, and then using {True|False} {Positives|Negatives},
-calculate PPV and NPV from equations 3 and 4 directly. One has to go
-instead through equations 5 and 6.
+Pages 2 and 13 highlight that we cannot perform a set of measurements,
+calculate sensitivity and specificity, and then using {True|False}
+{Positives|Negatives}, calculate PPV and NPV from equations 3 and 4
+directly. One has to go instead through equations 5 and 6.
 
@@
 
-The comment on the skewed data is valid. The validity of test data is
-important independently of sensitivity and specificity. We don't know
-in the papers we studied if test data were skewed. We do find,
-though, that: more tests could have been performed (Table I and
-VII.A) and the means to conduct tests should be made available to
-third parties (Table II and VII.B).
+The comment on the skewed data is valid. We don't know in the papers
+we studied if test data were skewed. We do find, though, that: more
+tests could have been performed (Table I and VII.A) and the means to
+conduct tests should be made available to third parties (Table II and
+VII.B).
 
@@
 
-We don't intend to criticize the lack of testing
-in etiological mechanisms. We attempt to 
-explore why such mechanisms aren't widely used, and suggest
-that this is one reason.
+We don't intend to criticize the lack of testing in etiological
+mechanisms. We attempt to explore why such mechanisms aren't widely
+used, and suggest that this is one reason.
 
@@
 ask of researchers to provide PPV and NPV values for their mechanisms.
-In p.13 we explore what this would require---we will elaborate
-more.
+In p.13 we explore what this would require---we will elaborate.

### 2015-01-16 docs/rebuttal_merged.txt
581 with correct format

@@
 
-* We didn't consider mechanisms that haven't been presented in
-research papers. We mention Caja due to its importance.
+We didn't consider mechanisms that haven't been presented in research papers. We mention Caja due to its importance.
 
-* Although some of the presented works use static/dynamic analysis, we
- don't consider that area (another paper covers it [14]), but
- focus only on protections against attacks that exploit such
- vulnerabilities.
+Although some of the presented works use static/dynamic analysis, we don't consider that area (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.
 
-* We will update our paper to address the issues indicated by the the
-  reviewers, i.e. the title, the point where language protection
-  mechanisms detect an attack, the "ease of use" dimension, the SQLi
-  example, the fact that we fail to capture PHP injection in our
-  model, the 1/1.1 notation in our model, and the code availability
-  discussion.
+We'll update our paper to address the issues indicated by the the reviewers, i.e.
+the title, the point where language protection mechanisms detect an attack, the "ease of use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.
 
@@
 
-Sensitivity and specificity should be more widely applicable, but not
-enough data is given in the publications (see VII.A). The usefulness
-of such metrics in computer security has been advocated by others,
-i.e. Pfleeger and Pfleeger (Analyzing Computer Security: A
-Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011);
-we’ll add the citation.
+Sensitivity and specificity should be more applicable, but not enough data is given in the publications (see VII.A).
+The usefulness of such metrics in computer security has been advocated by others, i.e.
+Pfleeger and Pfleeger (Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011); we’ll add the citation.
 
-There are too many N/As in Table II, but this actually highlights the
-issues regarding code availability and accuracy testing.
+There are too many N/As (especially in Table II), but this actually highlights the issues regarding code availability and accuracy testing.
 
-We will include FlowFox and JSand, the paper presenting IFC in
-WebKit's JavaScript Bytecode and discuss ADsafe etc. and Caja.
-AdSentry, Contego, and JSFlow don't reach our citation threshold.
+We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.
 
-Using "security" as a dimension is misleading---we mean ease of
-circunvention, which is orthogonal to "accuracy". We
-will replace it with a more specific term.
+Using "security" as a dimension is misleading---we mean ease of circunvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.
 
-We'll enrich the security discussion. For instance, approaches that
-provide systematic arguments on why their designs are secure, cannot
-be circumvented like heuristic/threshold-based approaches.
+We'll enrich the security discussion. For instance, approaches that provide systematic arguments on why their designs are secure, cannot be circumvented like heuristic/threshold-based approaches.
 
@@
 
-The lack of code availability for most systems makes performing
-original tests challenging, which is one of our findings (VII.B).
+The lack of code availability for most systems makes performing original tests challenging, which is one of our findings (VII.B).
 
-We attempt to cover mechanisms and then highlight reasons why a
-mechanism may not be widely used. In the conclusions we mention that
-CSP is one of the few that has been published and is widely used. It
-is true that if programmers use secure coding practices like prepared
-statements, then SQLi protections aren't required. However, that may
-not happen, and this motivates proposals like SQLrand, which might be
-easier to retrofit in existing code bases.
+We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used.
+In the conclusions we mention that CSP is one of the few that has been published and is widely used.
+It is true that if programmers use secure coding practices like prepared statements, then SQLi protections aren't required.
+However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing code bases.
 
-Our model covers attacks that utilize DSL languages in general, and in
-our categorization there are more than one countermeasures that
-protect from XPathi.
+Our model covers attacks that utilize DSL languages in general, and in our categorization there are more than one countermeasures that protect from XPathi.
 
@@
 
-Sensitivity and specificity could be expressed in terms of a
-conditional probability---we will include this in the paper.
+Sensitivity and specificity could be expressed in terms of a conditional probability---we'll include this in the paper.
 
-Pages 2 and 13 highlight that we cannot perform a set of measurements,
-calculate sensitivity and specificity, and then using {True|False}
-{Positives|Negatives}, calculate PPV and NPV from equations 3 and 4
-directly. One has to go instead through equations 5 and 6.
+Pages 2 and 13 highlight that we cannot perform a set of measurements, calculate sensitivity and specificity, and then using {True|False} {Positives|Negatives}, calculate PPV and NPV from equations 3 and 4 directly.
+One has to go instead through equations 5 and 6.
 
-We will expand on the advantages of PPV and NPV. PPV and NPV answer
-the question about trusting a detection result; however, it isn't
-always possible to get data for them as we indicate in p.13.
+We'll expand on the advantages of PPV and NPV. PPV and NPV answer the question about trusting a detection result; however, it isn't always possible to get data for them as we indicate in p.13.
 
-The comment on the skewed data is valid. We don't know in the papers
-we studied if test data were skewed. We do find, though, that: more
-tests could have been performed (Table I and VII.A) and the means to
-conduct tests should be made available to third parties (Table II and
-VII.B).
+The comment on the skewed data is valid.
+We don't know in the papers we studied if test data were skewed.
+We do find, though, that: more tests could have been performed (Table I and VII.A) and the means to conduct tests should be made available to third parties (Table II and VII.B).
 
@@
 
-We don't intend to criticize the lack of testing in etiological
-mechanisms. We attempt to explore why such mechanisms aren't widely
-used, and suggest that this is one reason.
+We don't intend to criticize the lack of testing in etiological mechanisms. We attempt to explore why such mechanisms aren't widely used, and suggest that this is one reason.
 
-Regarding the comment about demanding prevalence, it may be unfair to
-ask of researchers to provide PPV and NPV values for their mechanisms.
-In p.13 we explore what this would require---we will elaborate.
+About demanding prevalence: it may be unfair to ask of researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.

### 2015-01-16 docs/rebuttal_merged.txt
570 words

@@
 
-Some general points:
+General points:
 
@@
 
-Although some of the presented works use static/dynamic analysis, we don't consider that area (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.
+Although some of the presented works use static/dynamic analysis, we don't consider the area of static/dynamic analysis for vulnerability detection (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.
 
 We'll update our paper to address the issues indicated by the the reviewers, i.e.
-the title, the point where language protection mechanisms detect an attack, the "ease of use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.
+the title, the point where language-protection mechanisms detect an attack, the "ease-of-use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.
 
@@
 The usefulness of such metrics in computer security has been advocated by others, i.e.
-Pfleeger and Pfleeger (Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach, Prentice Hall, 2011); we’ll add the citation.
+Pfleeger and Pfleeger in "Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach"---we’ll add the citation.
 
@@
 
-We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.
+We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript-Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.
 
-Using "security" as a dimension is misleading---we mean ease of circunvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.
+Using "security" as a dimension is indeed misleading---we mean ease-of-circumvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.
 
@@
 
-The lack of code availability for most systems makes performing original tests challenging, which is one of our findings (VII.B).
+The lack of code availability makes performing original tests challenging, which is one of our findings (VII.B).
 
-We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used.
-In the conclusions we mention that CSP is one of the few that has been published and is widely used.
+We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used. In the conclusions we mention that CSP is one of the few that has been published and is used.
+
 It is true that if programmers use secure coding practices like prepared statements, then SQLi protections aren't required.
-However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing code bases.
+However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing codebases.
 
-Our model covers attacks that utilize DSL languages in general, and in our categorization there are more than one countermeasures that protect from XPathi.
+Our model covers attacks that utilize DSLs in general, and in our categorization there are more than one countermeasures that protect from XPathi.
 
@@
 
-Pages 2 and 13 highlight that we cannot perform a set of measurements, calculate sensitivity and specificity, and then using {True|False} {Positives|Negatives}, calculate PPV and NPV from equations 3 and 4 directly.
+P.2 and p.13 highlight that we cannot perform a set of measurements, calculate sensitivity and specificity, and then using {True|False} {Positives|Negatives}, calculate PPV and NPV from equations 3 and 4 directly.
 One has to go instead through equations 5 and 6.
@@
 
-About demanding prevalence: it may be unfair to ask of researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.
+About demanding prevalence: it may be unfair to ask researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.

### 2015-01-17 docs/rebuttal_merged.txt
squeezing

@@
 
-General points:
+General remarks:
 
-We didn't consider mechanisms that haven't been presented in research papers. We mention Caja due to its importance.
+We didn't consider mechanisms that haven't been presented in research papers. We
+mention Caja due to its importance.
 
-Although some of the presented works use static/dynamic analysis, we don't consider the area of static/dynamic analysis for vulnerability detection (another paper covers it [14]), but focus only on protections against attacks that exploit such vulnerabilities.
+Although some of the presented works use static/dynamic analysis, we don't
+consider the area of static/dynamic analysis for vulnerability detection
+(another paper covers it [14]), but focus on protections against attacks that
+exploit such vulnerabilities.
 
-We'll update our paper to address the issues indicated by the the reviewers, i.e.
-the title, the point where language-protection mechanisms detect an attack, the "ease-of-use" dimension, the SQLi example, the fact that we fail to capture PHP injection in our model and the model's 1/1.1 notation.
+We'll address the issues indicated by the reviewers, e.g., the title, the point
+where language-protection mechanisms detect an attack, the "ease-of-use"
+dimension, the SQLi example, the failure of capturing PHPi in our model and the
+model's 1/1.1 notation.
 
@@
 
-Sensitivity and specificity should be more applicable, but not enough data is given in the publications (see VII.A).
-The usefulness of such metrics in computer security has been advocated by others, i.e.
-Pfleeger and Pfleeger in "Analyzing Computer Security: A Threat/Vulnerability/Countermeasure Approach"---we’ll add the citation.
+Sensitivity and specificity should be more applicable, but not enough data is
+available (see VII.A). The usefulness of such metrics in has been advocated
+before (Pfleeger and Pfleeger, "Analyzing Computer Security: A
+Threat/Vulnerability/Countermeasure Approach"---will be cited).
 
-There are too many N/As (especially in Table II), but this actually highlights the issues regarding code availability and accuracy testing.
+The many N/As (especially in Table II) actually highlight the code availability
+and accuracy testing issues.
 
-We'll include FlowFox and JSand, the paper presenting IFC in WebKit's JavaScript-Bytecode and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't reach our citation threshold.
+We'll include FlowFox and JSand, the paper presenting IFC in WebKit's
+JavaScript-Bytecode, and discuss ADsafe etc. AdSentry, Contego, and JSFlow don't
+reach our citation threshold.
 
-Using "security" as a dimension is indeed misleading---we mean ease-of-circumvention, which is orthogonal to "accuracy". We'll replace it with a more specific term.
+Using "security" as a dimension is indeed misleading---we mean
+ease-of-circumvention, which is orthogonal to "accuracy". We'll replace it with
+a more specific term.
 
-We'll enrich the security discussion. For instance, approaches that provide systematic arguments on why their designs are secure, cannot be circumvented like heuristic/threshold-based approaches.
+We'll enrich the security discussion. For instance, approaches that provide
+systematic arguments on their design's security cannot be circumvented like
+heuristic/threshold-based approaches.
 
@@
 
-The lack of code availability makes performing original tests challenging, which is one of our findings (VII.B).
+The lack of code availability makes performing original tests challenging, which
+is one of our findings (VII.B).
 
-We attempt to cover mechanisms and then highlight reasons why a mechanism may not be widely used. In the conclusions we mention that CSP is one of the few that has been published and is used.
+We attempt to cover mechanisms and then highlight reasons why they may not be
+widely used. In the conclusions we mention that CSP is one of the few that has
+been published and is used.
 
-It is true that if programmers use secure coding practices like prepared statements, then SQLi protections aren't required.
-However, that may not happen, and this motivates proposals like SQLrand, which might be easier to retrofit in existing codebases.
+It is true that if programmers use secure coding practices like prepared
+statements, then SQLi protections aren't required. However, that may not happen,
+and this motivates proposals like SQLrand, which might be easier to retrofit in
+existing codebases.
 
-Our model covers attacks that utilize DSLs in general, and in our categorization there are more than one countermeasures that protect from XPathi.
+Our model covers attacks that utilize DSLs in general, and in our categorization
+there are more than one countermeasures that protect from XPathi.
 
@@
 
-Sensitivity and specificity could be expressed in terms of a conditional probability---we'll include this in the paper.
+Sensitivity and specificity could be expressed in terms of a conditional
+probability---we'll include this in the paper.
 
-P.2 and p.13 highlight that we cannot perform a set of measurements, calculate sensitivity and specificity, and then using {True|False} {Positives|Negatives}, calculate PPV and NPV from equations 3 and 4 directly.
-One has to go instead through equations 5 and 6.
+P.2 and p.13 highlight that we cannot perform a set of measurements, calculate
+sensitivity and specificity, and then using {True|False} {Positives|Negatives},
+calculate PPV and NPV from equations 3+4. One has to go instead through
+equations 5+6.
 
-We'll expand on the advantages of PPV and NPV. PPV and NPV answer the question about trusting a detection result; however, it isn't always possible to get data for them as we indicate in p.13.
+We'll expand on the advantages of PPV and NPV. They answer the question about
+trusting a detection result; however, it isn't always possible to get data for
+them as we indicate in p.13.
 
-The comment on the skewed data is valid.
-We don't know in the papers we studied if test data were skewed.
-We do find, though, that: more tests could have been performed (Table I and VII.A) and the means to conduct tests should be made available to third parties (Table II and VII.B).
+The comment on the skewed data is valid. We don't know in the studied papers
+if test data was skewed. We do find, though, that: more tests could have been
+performed (Table I and VII.A) and the means to conduct tests should be made
+available to third parties (Table II and VII.B).
 
@@
 
-We don't intend to criticize the lack of testing in etiological mechanisms. We attempt to explore why such mechanisms aren't widely used, and suggest that this is one reason.
+We don't intend to criticize the lack of testing in etiological mechanisms. We
+attempt to explore why such mechanisms aren't widely used, and suggest that this
+is one reason.
 
-About demanding prevalence: it may be unfair to ask researchers to provide PPV and NPV values for their mechanisms. In p.13 we explore what this would require---we'll elaborate.
+About demanding prevalence: it may be unfair to ask researchers to provide PPV
+and NPV values for their mechanisms. In p.13 we explore what this would
+require---we'll elaborate.

### 2015-01-17 docs/rebuttal_merged.txt
squeezing

@@
 Although some of the presented works use static/dynamic analysis, we don't
-consider the area of static/dynamic analysis for vulnerability detection
-(another paper covers it [14]), but focus on protections against attacks that
-exploit such vulnerabilities.
+consider the area of vulnerability detection (it's been covered [14]), but focus
+on protections against attacks that exploit such vulnerabilities.
 
@@
 Sensitivity and specificity should be more applicable, but not enough data is
-available (see VII.A). The usefulness of such metrics in has been advocated
-before (Pfleeger and Pfleeger, "Analyzing Computer Security: A
-Threat/Vulnerability/Countermeasure Approach"---will be cited).
+available (see VII.A). Their use has been advocated before ("Analyzing Computer
+Security: A Threat/Vulnerability/Countermeasure Approach"---will be cited).
 
@@
 
-It is true that if programmers use secure coding practices like prepared
-statements, then SQLi protections aren't required. However, that may not happen,
-and this motivates proposals like SQLrand, which might be easier to retrofit in
-existing codebases.
+When programmers use secure coding practices like prepared statements, then SQLi
+protections aren't required. However, that may not happen, and this motivates
+proposals like SQLrand, which might be easier to retrofit.
 
@@
 sensitivity and specificity, and then using {True|False} {Positives|Negatives},
-calculate PPV and NPV from equations 3+4. One has to go instead through
-equations 5+6.
+calculate PPV and NPV from equations 3&4. One has to go instead through
+equations 5&6.
 
@@
 
-The comment on the skewed data is valid. We don't know in the studied papers
-if test data was skewed. We do find, though, that: more tests could have been
-performed (Table I and VII.A) and the means to conduct tests should be made
-available to third parties (Table II and VII.B).
+The comment on the skewed data is valid. We don't know if data was skewed but we
+find, that: more tests could have been performed (Table I and VII.A) and testbed
+details should be available (Table II and VII.B).
 
@@
 We don't intend to criticize the lack of testing in etiological mechanisms. We
-attempt to explore why such mechanisms aren't widely used, and suggest that this
-is one reason.
+attempt to explore why such mechanisms aren't used, and suggest that this is one
+reason.
 
 About demanding prevalence: it may be unfair to ask researchers to provide PPV
-and NPV values for their mechanisms. In p.13 we explore what this would
-require---we'll elaborate.
+and NPV values. In p.13 we explore what this would require---we'll elaborate.

### 2016-02-25 docs/Oakland Paper, Reviews and Rebuttal/rebuttal_merged.txt
changed style

--- 2015-01-17 docs/rebuttal_merged.txt
@@
 Although some of the presented works use static/dynamic analysis, we don't
-consider the area of vulnerability detection (it's been covered [14]), but focus
+consider the area of vulnerability detection (covered before [14]), but focus
 on protections against attacks that exploit such vulnerabilities.
@@
 We'll address the issues indicated by the reviewers, e.g., the title, the point
-where language-protection mechanisms detect an attack, the "ease-of-use"
+where language-protection mechanisms detect attacks, the "ease-of-use"
 dimension, the SQLi example, the failure of capturing PHPi in our model and the
@@
 Sensitivity and specificity should be more applicable, but not enough data is
-available (see VII.A). Their use has been advocated before ("Analyzing Computer
-Security: A Threat/Vulnerability/Countermeasure Approach"---will be cited).
+available (see VII.A). Their use has been advocated before (Pfleeger and Pfleeger,
+"Analyzing Computer Security:A Threat/Vulnerability/Countermeasure Approach"---will
+be cited).
 

### 2016-02-25 docs/questioning.tex
changed style

@@
-\documentclass[conference]{IEEEtran}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
+\let\chapter\section
+
+\usepackage[ruled]{algorithm2e}
+\renewcommand{\algorithmcfname}{ALGORITHM}
+\SetAlFnt{\small}
+\SetAlCapFnt{\small}
+\SetAlCapNameFnt{\small}
+\SetAlCapHSkip{0pt}
+\IncMargin{-\parindent}
 
@@
 \usepackage{pifont}
-\usepackage{acronym}
+\usepackage{acronym}%
 \usepackage{algpseudocode}
-\usepackage{algorithm}
+%\usepackage{algorithm}
 \usepackage{supertabular}
@@
 \usepackage{threeparttable}
+\usepackage{enumitem}
 \usepackage{pdflscape}
@@
 \usepackage{courier}
+\usepackage{draftwatermark}
+\SetWatermarkText{Confidential}
+\SetWatermarkScale{0.4}
 
@@
 
-\date{}
 \begin{document}
 
-% \author{
-% \IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
-% Panos Louridas,\IEEEauthorrefmark{2}
-% Michalis Polychronakis,\IEEEauthorrefmark{1}
-% and Angelos D. Keromytis\IEEEauthorrefmark{1}}
-% \IEEEauthorblockA{\IEEEauthorrefmark{1}
-% Network Security Lab\\
-% Department of Computer Scinence\\
-% Columbia University\\
-% \{dimitro, mikepo, angelos\}@cs.columbia.edu\\
-% \IEEEauthorrefmark{2}
-% Software Engineering and Security Lab\\
-% Department of Management Science and Technology\\
-% Athens University of Economics and Business\\
-% louridas@aueb.gr
-% }}
-
-\author{Anonymous Submission}
-
-\title{SoK: Defending Against Web Application Attacks: From Research
-  Approaches to Practical Tools}
-
-\maketitle
-\thispagestyle{plain}
-\pagestyle{plain}
+\title{Defending Against Web Application Attacks: Research Approaches, Challenges and Implications}
+
+\author{
+\IEEEauthorblockN{Dimitris Mitropoulos,\IEEEauthorrefmark{1}
+Panos Louridas,\IEEEauthorrefmark{2}
+Michalis Polychronakis,\IEEEauthorrefmark{3}
+and Angelos D. Keromytis\IEEEauthorrefmark{1}}\\
+\IEEEauthorblockA{\IEEEauthorrefmark{1}
+\scriptsize Network Security Lab\\
+Department of Computer Scinence\\
+Columbia University\\
+\{dimitro, angelos\}@cs.columbia.edu\\
+\IEEEauthorrefmark{2}
+Software Engineering and Security Lab\\
+Department of Management Science and Technology\\
+Athens University of Economics and Business\\
+louridas@aueb.gr\\
+\IEEEauthorrefmark{3}
+Computer Science Department\\
+Stony Brook University\\
+mikepo@cs.stonybrook.edu
+}}
+
+% \markboth{\footnotesize D. Mitropoulos et al.}{\footnotesize Defending Against Web Application Attacks:
+% Research Approaches, Challenges and Implications}
+
+\markboth{D. Mitropoulos et al., Defending Against Web Application Attacks}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+
+\IEEEtitleabstractindextext{
 \begin{abstract}
-
 Some of the most dangerous web attacks, such as Cross-Site
-  Scripting and SQL injection, exploit vulnerabilities
+Scripting and {\sc sql} injection, exploit vulnerabilities
 in web applications that may accept and process
@@
 countermeasures that have been proposed over the past 15 years.
-
-  In this paper, we systematize the existing knowledge on
+In this paper, we provide an analysis on
 various defense mechanisms against web code injection attacks. We propose
@@
 \begin{IEEEkeywords}
-Protection mechanisms, web application security,
-SQL injection, XSS, CSRF.
-\end{IEEEkeywords}
+Web Application Security, Protection Mechanisms, Exploitation Models, Software Testing,
+SQL Injection, XSS.
+\end{IEEEkeywords}}
+
+\maketitle
+
+\IEEEdisplaynontitleabstractindextext
 
@@
 Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SG07},
-{\sc sql} injection~\cite{RL12b}, and Cross-Site Request Forgery
-({\sc csrf}) attacks~\cite{LZRL09}, among others.
+and {\sc sql} injection attacks~\cite{RL12b},
+%and Cross-Site Request Forgery
+% ({\sc csrf}) attacks~\cite{LZRL09},
+among others.
 
@@
 these attacks have been topping the lists of the most dangerous vulnerabilities
-published by {\sc owasp}~\cite{OWASPtop10},
-{\sc mitre}~\cite{MITREtop25}, and other organizations.
+published by
+{\sc owasp},\footnote{\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
+%~\cite{OWASPtop10},
+{\sc mitre},\footnote{\url{http://cwe.mitre.org/top25/}}
+%~\cite{MITREtop25},
+and other organizations.
 For instance, consider the case of {\sc owasp}'s popular Top Ten
-project~\cite{OWASPtop10},
+project,%\footnote{\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
+%~\cite{OWASPtop10},
 which aims to raise awareness about web application security by
@@
 some protection mechanisms defend against more than one of these
-types of attacks. Then, we {\it categorize} a selection of representative
-protection mechanisms and finally we {\it analyze} each mechanism across the
+types of attacks.
+
+Then, we {\it categorize} a selection of representative
+protection mechanisms. Specifically, we include protection
+mechanisms that counter web attacks when they take place,
+while we do not consider countermeasures that identify
+vulnerabilities using static program analysis~\cite{SZ12}
+(which takes place during the development or testing
+phases). Similarly, dynamic analysis techniques that examine
+applications to identify vulnerabilities that may lead to the attacks
+that we described earlier are out of scope as well. Note also, that we
+didn't consider mechanisms that haven't been presented in research papers.
+
+Finally, we {\it analyze} each mechanism across the
 following dimensions:
@@
 
-There is already a survey on mitigating software vulnerabilities in
-general~\cite{SZ12}. The scope of that research is much broader than
-ours and leaves out the majority of the approaches and mechanisms that
-we consider in this work. This is mainly because that work includes
-countermeasures that identify vulnerabilities using static program analysis
-(which takes place during the development or testing phases), while we
-consider protection mechanisms that counter web attacks when they take
-place. Similarly, dynamic analysis techniques that examine
-applications to identify vulnerabilities that may lead to the attacks
-that we described earlier are out of scope as well. While
-countermeasures against {\sc sql} injection attacks have been
-previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
-of new {\sc sql} injection defenses has been proposed since then, as
-we mentioned earlier.
+% There is already a survey on mitigating software vulnerabilities in
+% general~\cite{SZ12}. The scope of that research is much broader than
+% ours and leaves out the majority of the approaches and mechanisms that
+% we consider in this work. This is mainly because that work includes
+% countermeasures that identify vulnerabilities using static program analysis
+% (which takes place during the development or testing phases), while we
+% consider protection mechanisms that counter web attacks when they take
+% place. Similarly, dynamic analysis techniques that examine
+% applications to identify vulnerabilities that may lead to the attacks
+% that we described earlier are out of scope as well. While
+% countermeasures against {\sc sql} injection attacks have been
+% previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
+% of new {\sc sql} injection defenses has been proposed since then, as
+% we mentioned earlier.
 
@@
 \item We categorize and analyze proposed defenses using a set of
-  criteria that are important for building protection mechanisms.
+  criteria that are important for building protection mechanisms on the web.
 \item We provide insight based on the issues that arise from our analysis. We put
@@
 
-The rest of the paper is organized as follows.
+The rest of the paper is organized as follows:
 Section~\ref{sec:attacks} provides some insights on
@@
 \leavevmode
-\includegraphics[width=\columnwidth]{attack-tree-uml.pdf}
+\includegraphics[scale=0.55]{attack-tree-uml.pdf}
 \end{center}
@@
 and countermeasures to such attacks
-have already been surveyed~\cite{YJP12}\cite[Sec. 13.8]{DKZ12}.
-In this work
-we do not consider binary code injection, focusing instead on defenses
+have already been analyzed~\cite{YJP12}\cite[Sec. 13.8]{DKZ12}.
+In this work we do not consider binary code injection,
+focusing instead on defenses
 that protect web applications against attacks based on the
@@
 Consider a trivial exploit that takes advantage of incorrectly
-filtered quotation characters in an application that sends a temporary
-password for a forgetful user via email by executing the following
+filtered quotation characters in an application that shows the
+password of a forgetful user by executing the following
 query:
@@
 Attackers that would input the string {\tt anything' OR 'x'='x}
-could obtain a user's password by email. Savvy
-programmers can use certain {\sc api} functions, such as {\sc php}'s
+could view every item in the table.
+%obtain a user's password by email.
+Savvy programmers can use certain {\sc api} functions, such as {\sc php}'s
 {\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
@@
 into the application's page. {\sc html} injection is mainly associated
-with {\sc xss} attacks~\cite{BJM08,LZRL09}. However, {\sc html} injection,
-can also be used as a vehicle for {\sc csrf} attacks.
+with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection,
+can also be used as a vehicle for {\sc csrf} attacks~\cite{BJM08, LZRL09}
+(even though a common {\sc csrf} attack does not necessarily
+involve code injection).
 Consider a bulletin board system where {\tt img} tags are allowed.
@@
 
-\section{Exploitation Model}
-\label{sec:model}
-
 \begin{figure*}[t]
@@
 \leavevmode
-\includegraphics[scale=0.55]{attacks-steps-CSRF.pdf}
+\includegraphics[scale=0.50]{attacks-steps-CSRF.pdf}
 \end{center}
@@
 detect or prevent attacks are marked with an `X' symbol:
-{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
-{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
-{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
+(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
+(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
 \end{figure*}
+
+\section{Exploitation Model}
+\label{sec:model}
 
@@
 {\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
-%Recall the examples we provided in Section~\ref{sec:attacks}.
-Note that {\sc xss} and {\sc csrf} attacks can start from both routes.
+Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
 
@@
 
-Research on application attack defense mechanisms has a dual
+Research on web application attack defense mechanisms has a dual
 character. First, a defense mechanism may be important, and therefore
@@
 
+Note that the use of sensitivity and specificity in this context
+has been advocated before~\cite{PP12}.
+
 \subsection{Availability}
@@
 \leavevmode
-\includegraphics[scale=0.65]{defenses.pdf}
+\includegraphics[scale=0.60]{defenses.pdf}
 \end{center}
@@
 \subsection{Point of Detection}
+\label{sec:point}
 
@@
 in Figure~\ref{fig:attacks}:
-\begin{itemize}
+
+\begin{enumerate}
 \item At the user's browser (Point {\sc ub}).
@@
   (Point {\sc db}).
-\end{itemize}
-
-\section{Defenses}
-\label{sec:defs}
+\end{enumerate}
 
@@
     \begin{small}
-\scalebox{0.93}{
+\scalebox{0.83}{
     \begin{tabular}{l|c|c|cc|c}
@@
 
+\section{Defenses}
+\label{sec:defs}
+
 We categorize and analyze a large set of defenses developed to detect
@@
 defenses that have been proposed in publications cited more than
-20 times according to Google Scholar~\cite{googleScholar}.
+20 times according to Google Scholar.\footnote{\url{scholar.google.gr}}
 We also include some recent works that have been
@@
 A policy enforcement technique developed by Mozilla,
-called {\sc csp} (Content Security Policy)~\cite{cspMoz,SSM10}
+called {\sc csp} (Content Security
+Policy)\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
 is currently supported by many browsers to prevent
@@
 support cross-origin requests.
-The above problems ar addressed by j{\sc csrf}~\cite{PS11},
+The above problems are addressed by j{\sc csrf}~\cite{PS11},
 which shares similar functionality.
@@
 
+An issue that involves all taint tracking schemes involves
+the difficulty of maintaining accurate taint~\cite{GMPS11}
+(e.g. implicit flows~\cite{ME07}).
+In such cases, certain, tainted inputs can escape the tracking mechanism.
+Keeping track of such input maybe impractical not only because of the
+various technical difficulties, but also because it would raise false alarms.
+
 \subsubsection{Training}
@@
 {\sc didafit}~\cite{LLW02}, detects {\sc sql} injection attacks (Point
-{\sc sdb}) by recording all database transactions
+{\sc dbal}) by recording all database transactions
 stripped from user input. Subsequent
@@
 easily to false negatives. For instance, recall the application
-mentioned in Section~\ref{sec:attacks}, which will send the password
-for a forgetful user via email by executing the following query:
+mentioned in Section~\ref{sec:attacks}, which will show the password
+for a forgetful user by executing the following query:
 
@@
 (like the ``Password only login" plugin of
-Wordpress~\cite{password})
+Wordpress\footnote{\url{wordpress.org/plugins/password-only-login/}})
+%~\cite{password})
 but allow the login either with the user's password or with
@@
 are enlisted in the following providers: the Common
-Vulnerabilities and Exposures ({\sc cve}) database~\cite{cve},
-the Bugtraq security mailing list~\cite{bugtraq}, the {\sc xss}ed.com
-security bulletin provider~\cite{xssed}, Microsoft's security
-bulletin~\cite{microsoftBulletin} and the
-ha.ckers.org security bulletin provider~\cite{hackers}.
+Vulnerabilities and Exposures ({\sc cve})
+database,\footnote{\url{https://cve.mitre.org/}}
+%~\cite{cve},
+the Bugtraq\footnote{\url{http://seclists.org/bugtraq/}}
+security mailing list,
+%~\cite{bugtraq},
+the {\sc xss}ed.com
+security bulletin provider,\footnote{\url{www.xssed.com}}
+%~\cite{xssed},
+Microsoft's security
+bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
+%~\cite{microsoftBulletin}
+and the
+ha.ckers.org\footnote{\url{http://ha.ckers.org/}}
+security bulletin provider.
+%~\cite{hackers}.
 Figure~\ref{fig:defect_sources} presents how many, in percentage,
@@
 on the same applications. For example, 12 mechanisms were tested on a
-vulnerable version of the {\sc phpbb} bulletin board software~\cite{phpbb}.
-
-\begin{figure}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.47]{defect-percentages.png}
-\end{center}
-\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
-used for testing of web attack defenses.
-Specifically, the publications that used a particular source are as follows:
-{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-{\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
-{\sc xss}ed.com~\cite{NSS06,APKLM10},
-ha.ckers.org~\cite{TNH07,PSC09,LV09},
-Microsoft~\cite{RDWDE07}.}
-\end{figure}
+vulnerable version of the {\sc phpbb} bulletin board
+software.\footnote{\url{https://www.phpbb.com/}}
+%~\cite{phpbb}.
+
+% \begin{figure}[t]
+% \begin{center}
+% \leavevmode
+% \includegraphics[scale=0.47]{defect-percentages.png}
+% \end{center}
+% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
+% used for testing of web attack defenses.
+% Specifically, the publications that used a particular source are as follows:
+% {\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+% {\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
+% {\sc xss}ed.com~\cite{NSS06,APKLM10},
+% ha.ckers.org~\cite{TNH07,PSC09,LV09},
+% Microsoft~\cite{RDWDE07}.}
+% \end{figure}
+
+% \begin{figure}[t]
+% \begin{center}
+% \leavevmode
+% \includegraphics[scale=0.57]{defect-percentages.png}
+% \end{center}
+% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
+% used for testing of web attack defenses.
+% Specifically, the publications that used a particular source are as follows:}
+% \scriptsize \Note{{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},}
+% \scriptsize \Note{Bugtraq~\cite{PB05,KKVJ06,JEP08},}
+% \scriptsize \Note{{\sc xss}ed.com~\cite{NSS06,APKLM10},}
+% \scriptsize \Note{ha.ckers.org~\cite{TNH07,PSC09,LV09},}
+% \scriptsize \Note{Microsoft~\cite{RDWDE07}.}
+% \end{figure}
 
@@
 
-\begin{table*}
+\begin{table}
 \caption{Availability of the studied defenses.}
@@
     \begin{small}
-\scalebox{0.93}{
+\scalebox{0.69}{
     \begin{tabular}{l|c|ccc}
@@
   & \bf{Mechanism}
-  & \multicolumn{3}{|c|}{Availability\tnote{1}} \\
+  & \multicolumn{3}{|c}{Availability\tnote{1}} \\
   && \bf{Source Code}
@@
     \end{threeparttable}
-\end{table*}
+\end{table}
 
@@
 The other 11 are based on interposing on {\sc api} calls related to output
-vectors (Point {\sc e}i{\sc q}).
+vectors (Point {\sc dbal}).
 
@@
 such as Mozilla's {\sc csp}~\cite{SSM10} and
-Google Caja~\cite{M06,caja}, share characteristics
+Google Caja,\footnote{\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
+share characteristics
 (for instance, {\sc html} sanitization and {\tt eval} handling)
@@
 which can promote the development of better
-mechanisms. This argument has been raised by another {\sc s}o{\sc k}
-paper~\cite{SPWS13}. Furthermore, testing defenses in a production
+mechanisms. This argument has been raised by others
+researchers too~\cite{SPWS13}.
+Furthermore, testing defenses in a production
 setting could also propel their adoption.
@@
 
-% First, we introduced an exploitation model
-% to show how defense mechanisms can be seen
-% from a common point of view. Our model can
-% be a reference point for researchers who wish to develop
-% new countermeasures. Then we categorized the various
-% mechanisms and analyzed them based on specific criteria.
-% We observed that the various mechanisms
-
-% This is due to the following reasons:
-% a) the mechanisms have not been extensively tested in terms
-% of accuracy,
-% b) are hard to deploy because they require many modifications
-% either on the client-side, the server-side, or both,
-% c) they add significant overhead, and
-% d) can be bypassed by attackers that know how they work.
-% The motivation behind this research is to systematize
-% and analyze previously proposed protection mechanisms.
-% In this way we can highlight the advantages
-% and disadvantages of each mechanism, enlist them
-% into different categories, and see how they compare to each other.
-
-% \begin{itemize}
-% \item We believe that our research may facilitate researchers
-% or practitioners who would like to use one of the
-% aforementioned mechanisms and researchers who would like
-% to build new ones. Especially in the second case,
-% researchers can utilize our exploitation model as a
-% starting point to develop their approach.
-% \item We believe that forming a
-% standard way to test such mechanisms in terms
-% of accuracy and computational performance
-% would be one of the reasons of adopting them.
-% \end{itemize}
-
 \bibliographystyle{IEEEtran}

### 2016-02-25 docs/questioning.tex
minor changes

@@
 
-Regarding the subjects of tests, we see that 27 out of 35 (77.1\%)
-mechanisms were tested with real-world applications known to be
-vulnerable. The vulnerabilities associated with these applications
+Regarding the subjects of tests,
+we see that 27 out of 35 (77.1\%)
+mechanisms were tested with real-world
+applications known to be vulnerable.
+The vulnerabilities associated with these applications
 are enlisted in the following providers: the Common
@@
 and which, in the figure's caption, publications referred
-to which source. In numerous occasions authors performed tests based
-on the same applications. For example, 12 mechanisms were tested on a
+to which source.
+In numerous occasions authors performed tests based
+on the same applications.
+For example, 12 mechanisms were tested on a
 vulnerable version of the {\sc phpbb} bulletin board
@@
 
-% \begin{figure}[t]
-% \begin{center}
-% \leavevmode
-% \includegraphics[scale=0.47]{defect-percentages.png}
-% \end{center}
-% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
-% used for testing of web attack defenses.
-% Specifically, the publications that used a particular source are as follows:
-% {\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-% {\it Bugtraq}~\cite{PB05,KKVJ06,JEP08},
-% {\sc xss}ed.com~\cite{NSS06,APKLM10},
-% ha.ckers.org~\cite{TNH07,PSC09,LV09},
-% Microsoft~\cite{RDWDE07}.}
-% \end{figure}
-
-% \begin{figure}[t]
-% \begin{center}
-% \leavevmode
-% \includegraphics[scale=0.57]{defect-percentages.png}
-% \end{center}
-% \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
-% used for testing of web attack defenses.
-% Specifically, the publications that used a particular source are as follows:}
-% \scriptsize \Note{{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},}
-% \scriptsize \Note{Bugtraq~\cite{PB05,KKVJ06,JEP08},}
-% \scriptsize \Note{{\sc xss}ed.com~\cite{NSS06,APKLM10},}
-% \scriptsize \Note{ha.ckers.org~\cite{TNH07,PSC09,LV09},}
-% \scriptsize \Note{Microsoft~\cite{RDWDE07}.}
-% \end{figure}
+\begin{figure}[t]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.47]{defect-percentages.png}
+\end{center}
+\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
+used for testing of web attack defenses.
+Specifically, the publications that used a particular source are as follows:
+{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+Bugtraq~\cite{PB05,KKVJ06,JEP08},
+{\sc xss}ed.com~\cite{NSS06,APKLM10},
+ha.ckers.org~\cite{TNH07,PSC09,LV09},
+Microsoft~\cite{RDWDE07}.}
+\end{figure}
 

### 2016-02-25 docs/questioning.tex
citations' updates

@@
   &   {\sc csp}~\cite{SSM10} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
-  &   j{\sc csrf}~\cite{PS11} & 2 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
+  &   j{\sc csrf}~\cite{PS11} & 4 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
   &   WebJail~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
@@
   &   {\sc php} Aspis~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
-  &   Stock et al.~\cite{SLMS14} & 0 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
+  &   Stock et al.~\cite{SLMS14} & 14 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
   \hline 
@@
   &   {\sc swap}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
-  &   {\sc sd}river~\cite{MS09,MKS09,MKLS11} & 21,8,5 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
+  &   {\sc sd}river~\cite{MS09,MKLS11} & 22,6 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
   % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
@@
   &   Blueprint~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   Diglossia~\cite{SMS13} & 4 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   Diglossia~\cite{SMS13} & 12 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
   \thickhline
@@
 detection framework called libAnomaly.
-{\sc sd}river~\cite{MS09,MKS09,MKLS11} is a signature-based mechanism
+{\sc sd}river~\cite{MS09,MKLS11} is a signature-based mechanism
 that prevents {\sc sql} and {\sc xp}ath injection attacks. The
@@
 checks all statements for compliance and can block code statements
-containing injected elements (Point {\sc dbal}). {\sc
-  amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects {\sc
-  sql} injection attacks (Point {\sc dbal}) by associating a query model
+containing injected elements (Point {\sc dbal}).
+{\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects
+{\sc sql} injection attacks (Point {\sc dbal}) by associating a query model
 with the location of every {\sc sql} statement within the application.

### 2016-02-25 docs/questioning.tex
shrinking

@@
 
-\title{Defending Against Web Application Attacks: Research Approaches, Challenges and Implications}
+\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications}
 
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{1}
-\scriptsize Network Security Lab\\
-Department of Computer Scinence\\
-Columbia University\\
+\scriptsize Department of Computer Scinence,
+Columbia University,
 \{dimitro, angelos\}@cs.columbia.edu\\
 \IEEEauthorrefmark{2}
-Software Engineering and Security Lab\\
-Department of Management Science and Technology\\
-Athens University of Economics and Business\\
+Department of Management Science and Technology,
+Athens University of Economics and Business,
 louridas@aueb.gr\\
 \IEEEauthorrefmark{3}
-Computer Science Department\\
-Stony Brook University\\
+Computer Science Department,
+Stony Brook University,
 mikepo@cs.stonybrook.edu
@@
 published by
-{\sc owasp},\footnote{\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
+{\sc owasp},\footnote{\scriptsize\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
 %~\cite{OWASPtop10},
-{\sc mitre},\footnote{\url{http://cwe.mitre.org/top25/}}
+{\sc mitre},\footnote{\scriptsize\url{http://cwe.mitre.org/top25/}}
 %~\cite{MITREtop25},
@@
 different types of code injection attacks are
-common.\footnote{Note that we do not consider lower-level attacks based on
+common.\footnote{\scriptsize Note that we do not consider lower-level attacks based on
 the exploitation of memory corruption vulnerabilities and the injection
@@
 defenses that have been proposed in publications cited more than
-20 times according to Google Scholar.\footnote{\url{scholar.google.gr}}
+20 times according to Google Scholar.\footnote{\scriptsize\url{scholar.google.gr}}
 We also include some recent works that have been
@@
 called {\sc csp} (Content Security
-Policy)\footnote{\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
+Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
 is currently supported by many browsers to prevent
@@
 used to assemble innocuous-looking parts into harmful
-strings,\footnote{The infamous Sammy worm that
+strings,\footnote{\scriptsize The infamous Sammy worm that
 infected MySpace in 2005~\cite{SP07,ELX07}
@@
 (like the ``Password only login" plugin of
-Wordpress\footnote{\url{wordpress.org/plugins/password-only-login/}})
+Wordpress\footnote{\scriptsize\url{wordpress.org/plugins/password-only-login/}})
 %~\cite{password})
@@
 Vulnerabilities and Exposures ({\sc cve})
-database,\footnote{\url{https://cve.mitre.org/}}
+database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
 %~\cite{cve},
-the Bugtraq\footnote{\url{http://seclists.org/bugtraq/}}
+the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
 security mailing list,
@@
 the {\sc xss}ed.com
-security bulletin provider,\footnote{\url{www.xssed.com}}
+security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
 %~\cite{xssed},
 Microsoft's security
-bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
+bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
 %~\cite{microsoftBulletin}
 and the
-ha.ckers.org\footnote{\url{http://ha.ckers.org/}}
+ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
 security bulletin provider.
@@
 vulnerable version of the {\sc phpbb} bulletin board
-software.\footnote{\url{https://www.phpbb.com/}}
+software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
 %~\cite{phpbb}.
@@
 \leavevmode
-\includegraphics[scale=0.47]{defect-percentages.png}
+\includegraphics[scale=0.45]{defect-percentages.png}
 \end{center}
@@
 such as Mozilla's {\sc csp}~\cite{SSM10} and
-Google Caja,\footnote{\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
+Google Caja,\footnote{\scriptsize\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
 share characteristics

### 2016-02-26 docs/questioning.tex
minor change
new bar chart

@@
 
+\setlist[itemize]{noitemsep, leftmargin=1em}
+\setlist[enumerate]{noitemsep, leftmargin=1em}
+
 \lstset{columns=flexible,showstringspaces=false}
@@
 
-\markboth{D. Mitropoulos et al., Defending Against Web Application Attacks}%
+\markboth{Mitropoulos et al.}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
@@
 to each other.
-
-% There is already a survey on mitigating software vulnerabilities in
-% general~\cite{SZ12}. The scope of that research is much broader than
-% ours and leaves out the majority of the approaches and mechanisms that
-% we consider in this work. This is mainly because that work includes
-% countermeasures that identify vulnerabilities using static program analysis
-% (which takes place during the development or testing phases), while we
-% consider protection mechanisms that counter web attacks when they take
-% place. Similarly, dynamic analysis techniques that examine
-% applications to identify vulnerabilities that may lead to the attacks
-% that we described earlier are out of scope as well. While
-% countermeasures against {\sc sql} injection attacks have been
-% previously surveyed in a 2006 paper~\cite{HVO06}, a significant number
-% of new {\sc sql} injection defenses has been proposed since then, as
-% we mentioned earlier.
-
 The main contributions of this paper are the following:
@@
 
-The rest of the paper is organized as follows:
-Section~\ref{sec:attacks} provides some insights on
-code injection attacks and
-Section~\ref{sec:model} presents our proposed model.
-Section~\ref{sec:dimensions} introduces the dimensions
-across which we analyze the various defenses.
-Our categorization and analysis is presented in
-Section~\ref{sec:defs} and a discussion is provided in
-Section~\ref{sec:discussion}. Finally,
-Section~\ref{sec:lessons-learned} highlights
-some lessons learned from our observations
-and Section~\ref{sec:conclusion} concludes the paper.
+% The rest of the paper is organized as follows:
+% Section~\ref{sec:attacks} provides some insights on
+% code injection attacks and
+% Section~\ref{sec:model} presents our proposed model.
+% Section~\ref{sec:dimensions} introduces the dimensions
+% across which we analyze the various defenses.
+% Our categorization and analysis is presented in
+% Section~\ref{sec:defs} and a discussion is provided in
+% Section~\ref{sec:discussion}. Finally,
+% Section~\ref{sec:lessons-learned} highlights
+% some lessons learned from our observations
+% and Section~\ref{sec:conclusion} concludes the paper.
 
@@
 and countermeasures to such attacks
-have already been analyzed~\cite{YJP12}\cite[Sec. 13.8]{DKZ12}.
+have already been analyzed~\cite{YJP12}.
+% \cite[Sec. 13.8]{DKZ12}.
 In this work we do not consider binary code injection,
@@
 such as incorrectly passed parameters or incorrect type handling, are
-called {\sc sql} injection attacks~\cite{CERT02,MS09,HVO06,SW06}.
+called {\sc sql} injection attacks~\cite{MS09,HVO06,SW06}.
 Consider a trivial exploit that takes advantage of incorrectly
@@
 %~\cite{hackers}.
-Figure~\ref{fig:defect_sources} presents how many, in percentage,
+Figure~\ref{fig:defect_sources},
+presents how many,
 and which, in the figure's caption, publications referred
@@
 \leavevmode
-\includegraphics[scale=0.45]{defect-percentages.png}
+\includegraphics[scale=0.39]{barchart.pdf}
 \end{center}
@@
   &   {\sc swap}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc sd}river~\cite{MS09,MKS09,MKLS11} & \tick & \tick & {\sc na} \\
+  &   {\sc sd}river~\cite{MS09,MKLS11} & \tick & \tick & {\sc na} \\
   \thickhline
@@
 Although some deployed and widely used frameworks, 
-such as Mozilla's {\sc csp}~\cite{SSM10} and
-Google Caja,\footnote{\scriptsize\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
+such as {\sc csp}~\cite{SSM10},
+% and
+% Google Caja,\footnote{\scriptsize\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
 share characteristics

### 2016-02-26 docs/questioning.tex
attack on CSP

@@
 In this paper, we provide an analysis on
-various defense mechanisms against web code injection attacks. We propose
-a model that highlights the key weaknesses enabling these attacks,
+various defense mechanisms against web code injection attacks.
+We propose a model that highlights the key weaknesses enabling these attacks,
 and that provides a common perspective for studying the available defenses.
@@
 
-\section{Code Injection Attacks in Web Applications}
+\section{Code Injection in Web Applications}
 \label{sec:attacks}
@@
 applications. Figure~\ref{fig:attacks} illustrates the required steps for
-different classes of injection attacks,
+different classes of attacks,
 such as {\sc sql} injection, {\sc xss}, and {\sc csrf}. Links between steps are
@@
 On the other hand, {\sc csrf} is also possible through injection
-({\sc i-csrf}). In this attack, an attacker
+({\sc i-csrf}---recall our example in the previous section).
+In this attack, an attacker
 manages to inject {\sc html} code that contains
@@
 source files from white-listed domains.
+Note that,
+if an application involves
+embedded scripts, developers must utilize
+{\sc csp}'s {\em nonce} concept.
+This is an unpredictable,
+random value indicated in
+the {\tt script-src} directive which in turn,
+is applied as a nonce attribute to
+{\tt <script>} elements.
+As a result, only those elements that have the
+correct nonce will execute.
+Even if an attacker
+is able to inject markup into the page,
+the attack will be prevented by the attacker's
+inability to guess the nonce value.
+However, attackers may still bypass this feature
+and invoke a script from a non-whitelisted source.
+To do so, their injected code must
+be crafted in a way that the nonce is handled
+by the browser as an attribute of the payload~\cite{jigsaw}.
 

### 2016-03-15 docs/questioning.tex
minor fix

@@
 major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
-Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}
+Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
 Such attacks are enabled when a web application accepts

### 2016-03-16 docs/questioning.tex
more space

@@
 
+\noindent\begin{minipage}{0.5\linewidth}
 \begin{equation}
@@
 \end{equation}
-
+\end{minipage}%
+\begin{minipage}{0.5\linewidth}
 \begin{equation}
@@
 \end{equation}
+\end{minipage}\par\vspace{\belowdisplayskip}
 
@@
 
-\begin{figure*}[t]
+\begin{figure}[t]
 \begin{center}
 \leavevmode
-\includegraphics[scale=0.60]{defenses.pdf}
+\includegraphics[scale=0.56]{defenses.pdf}
 \end{center}
@@
 {\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
-{\it Training}:~\cite{LLW02,HO05,HO06,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
+{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\end{figure*}
+\end{figure}
 
@@
     \begin{small}
-\scalebox{0.83}{
+\scalebox{0.80}{
     \begin{tabular}{l|c|c|cc|c}
@@
   & \bf{\# of Citations}
-  & \multicolumn{2}{|c|}{Requirements\tnote{1}}
+  & \multicolumn{2}{c|}{Requirements\tnote{1}}
   & \bf{Attack}\tnote{4} \\
@@
   &   {\sc didafit}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
-  &   {\sc amnesia}~\cite{HO05,HO06,HO05b} & 118,66,376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
+  &   {\sc amnesia}~\cite{HO05b} & 376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
   &   libAnomaly~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
@@
 of application attacks~\cite{K09b}, and was originally applied for the
-prevention of binary code injection attacks~\cite{KKP03, isr03forrest}.
+prevention of binary code injection attacks~\cite{KKP03}.
 The main idea behind {\sc isr} is
@@
 containing injected elements (Point {\sc dbal}).
-{\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool that also detects
+{\sc amnesia}~\cite{HO05b} is a tool that also detects
 {\sc sql} injection attacks (Point {\sc dbal}) by associating a query model
@@
 associated with code statements (e.g.,
-{\sc amnesia}~\cite{HO06} and
+{\sc amnesia}~\cite{HO05b} and
 {\sc sd}river~\cite{MS09})
@@
 the need to have large sets of samples in order to be able to use the
-central limit theorem~\cite{agresti1998,brown2001}.
+central limit theorem~\cite{brown2001}.
 However, sample sizes in the single
@@
 their previous research~\cite{LSJ13}.
-Finally, in the {\sc amnesia}~\cite{HO06} and
+Finally, in the {\sc amnesia}~\cite{HO05b} and
 {\sc sd}river~\cite{MS09} publications,
@@
   &   {\sc didafit}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc amnesia}~\cite{HO05,HO06,HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
+  &   {\sc amnesia}~\cite{HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
   &   libAnomaly~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
@@
 difficult to use. {\sc sql}rand~\cite{BK04},
-{\sc amnesia}~\cite{HO06},
+{\sc amnesia}~\cite{HO05b},
 mechanisms of the parse-tree validation
@@
 terms of accuracy ({\sc sqlc}heck~\cite{SW06},
-{\sc amnesia}~\cite{HO06}, libAnomaly~\cite{VMV05}),
+{\sc amnesia}~\cite{HO05b}, libAnomaly~\cite{VMV05}),
 solve specific problems in an effective way

### 2016-03-16 docs/questioning.tex
squeezing

@@
 \usepackage{courier}
+\newcommand{\subparagraph}{}
+\usepackage{titlesec}
+
+\titlespacing*{\section}
+{0pt}{1ex}{0.8ex}
+\titlespacing*{\subsection}
+{0pt}{1ex}{0.8ex}
+\titlespacing*{\subsubsection}
+{0pt}{1ex}{0.8ex}
+
+\setlength{\footnotesep}{0.3cm}
+\setlength{\skip\footins}{0.1cm}
+
 \usepackage{draftwatermark}
@@
 
-\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications}
+\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}}
 
@@
 mikepo@cs.stonybrook.edu
+\vspace{-3mm}
 }}
@@
 the widespread adoption of defenses in practice.
-
+\vspace{-3mm}
 \end{abstract}
@@
 SQL Injection, XSS.
+\vspace{-1mm}
 \end{IEEEkeywords}}
@@
 of the application and the location of the programming flaw that leads
-to the attack.
-
-Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
-{\it ``unexpected (and unexpectedly powerful) computational models
-  inside targeted systems, which turn a part of the target into a
-  so-called `weird machine' programmable by the attacker via crafted
-  inputs (a.k.a. `exploits').''} In particular, {\it ``every
-  application that copies untrusted input verbatim into an output
-  program is vulnerable to code injection.''} Ray and
-Ligatti~\cite{RL12b} have proved this claim based on formal language
-theory.
+to the attack~\cite{RL12b}.
+
+% Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
+% {\it ``unexpected (and unexpectedly powerful) computational models
+%   inside targeted systems, which turn a part of the target into a
+%   so-called `weird machine' programmable by the attacker via crafted
+%   inputs (a.k.a. `exploits').''} In particular, {\it ``every
+%   application that copies untrusted input verbatim into an output
+%   program is vulnerable to code injection.''} Ray and
+% Ligatti~\cite{RL12b} have proved this claim based on formal language
+% theory.
 
@@
 \end{center}
+\vspace{-3mm}
 \caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
 language code injection attacks against web applications.}
+\vspace{-5mm}
 \end{figure}
@@
 \leavevmode
-\includegraphics[scale=0.50]{attacks-steps-CSRF.pdf}
+\includegraphics[scale=0.48]{attacks-steps-CSRF.pdf}
 \end{center}
+\vspace{-7mm}
 \caption{\label{fig:attacks}Attack model for dynamic and domain specific
@@
 (4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+\vspace{-4mm}
 \end{figure*}
@@
 \end{center}
+\vspace{-3mm}
 \caption{\label{fig:defenses}The basic categories of countermeasures
@@
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
+\vspace{-4mm}
 \end{figure}
@@
     \label{tab:comp}
+    \vspace{-3mm}
 \centering
@@
     \end{threeparttable}
+    \vspace{-4mm}
 \end{table*}
@@
 The etiological category involves mechanisms designed to
-block attacks based on their causes and origins~\cite{JL75,L81}. 
+block attacks based on their causes and origins~\cite{L81}. 
 The symptomatic category incorporates a variety of schemes that
@@
 strings,\footnote{\scriptsize The infamous Sammy worm that
-infected MySpace in 2005~\cite{SP07,ELX07}
+infected MySpace in 2005~\cite{ELX07}
 utilized the {\tt eval} function to assemble a
@@
 \end{center}
+\vspace{-3mm}
 \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
@@
 Microsoft~\cite{RDWDE07}.}
+\vspace{-4mm}
 \end{figure}
@@
 \caption{Availability of the studied defenses.}
+\vspace{-3mm}
     \label{tab:avail}
@@
   & \bf{Mechanism}
-  & \multicolumn{3}{|c}{Availability\tnote{1}} \\
+  & \multicolumn{3}{c}{Availability\tnote{1}} \\
   && \bf{Source Code}
@@
     \multicolumn{5}{p{12.4cm}}{%
-  \begin{footnotesize}
        $^\textsuperscript{1}$A check mark (\tick) indicates that the publication
@@
        was included in the publication but is now inaccessible.
-  \end{footnotesize} } \\
+} \\
     \end{tabular}}
@@
     \end{threeparttable}
+    \vspace{-4mm}
 \end{table}
@@
 \end{equation}
-\end{minipage}%
+\end{minipage}
 \begin{minipage}{0.5\linewidth}
@@
 i.e., its prevalence, then we
-have~\cite{linn2004,altman1994}:
+have~\cite{linn2004}:
 
@@
 probability based on the results of the detection
-mechanism~\cite{altman1994}. The lower the prevalence of an attack,
+mechanism. The lower the prevalence of an attack,
 the more confident we can be that a negative test result indicates
@@
 the availability of prototypes and testbeds. We are not aware of
-specific reasons why authors of attack detection mechanisms seem to be
+specific reasons why authors of detection mechanisms seem to be
 wary of publicly releasing their code and tests. Our finding may reflect
@@
 change. That may be too much to ask right now; what seems reasonable,
-though, is to ask of researchers working on attack detection mechanisms not to
+though, is to ask of researchers working on defenses not to
 buck the trend and to take steps to increase the availability of their
@@
 setting could also propel their adoption.
-
 We hope that the exploitation model, analysis, and observations that
@@
 
+\vspace{-2mm}
+
 \bibliographystyle{IEEEtran}

### 2016-03-17 docs/questioning.tex
more squeezing

@@
 didn't consider mechanisms that haven't been presented in research papers.
-
 Finally, we {\it analyze} each mechanism across the
@@
   false negative rates.
-\item {\it Availability:} whether the mechanism and its
+\item {\it Availability:} whether the protection mechanism and its
   testbed are publicly available.
@@
   overhead imposed by the mechanisms at their points of deployment.
-\item {\it Ease of use:} whether the protection
+\item {\it Ease of use:} whether the
   mechanism is practical in terms of deployment
@@
 \item We categorize and analyze proposed defenses using a set of
-  criteria that are important for building protection mechanisms on the web.
+  criteria that are important for building protection mechanisms.
 \item We provide insight based on the issues that arise from our analysis. We put
@@
 {\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
-To illustrate, we briefly discuss examples from both categories
+To illustrate, we discuss examples from both categories
 that will be used throughout the paper.
@@
 similar techniques, malicious users can mount other exploits based on
-{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07,MKS09}, {\sc
+{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07}, {\sc
   xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
@@
 with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection,
-can also be used as a vehicle for {\sc csrf} attacks~\cite{BJM08, LZRL09}
+can also be used as a vehicle for Cross-Site Request Forgery
+({\sc csrf}) attacks~\cite{BJM08, LZRL09}
 (even though a common {\sc csrf} attack does not necessarily
@@
 to imagine more detrimental scenarios.
-
 A recent attack called {\sc php} Object Injection
@@
 (2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
+(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
 (4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
-\vspace{-4mm}
+\vspace{-5mm}
 \end{figure*}
@@
 Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
-
 Once the injected code reaches the vulnerable application, it becomes
@@
 
-Cross-site request forgery attacks typically involve just a
+{\sc csrf} attacks typically involve just a
 {\sc url} or page that contains a malicious request towards
@@
 used by administrators and users to shield their applications
-and services against the supported attacks.
+against the supported attacks.
 
@@
 
+\noindent
 Whether a reliable defense mechanism has value in a practical
@@
 Detection accuracy is gauged with the following
-metrics~\cite{TDR2013,GFDLS06,A00}:
+metrics~\cite{GFDLS06,A00}:
 \begin{itemize}
@@
 events will give us the specificity.
-
 Note that the use of sensitivity and specificity in this context
@@
 it becomes as a practical approach.
+
+\subsection{Ease of Use}
+\label{sec:deployment}
+
+The value of a detection mechanism as a practical tool depends on how
+easy it is to deploy it in a production setting. This aspect is
+orthogonal to the
+value of a detection mechanism as a research finding. Devising a
+technique to detect a hitherto undetectable class of attacks may be an
+excellent research contribution that merits publication; it may also
+be heavily cited and open the road to other, practical
+implementations in the future.
+
+Ease of use depends on the deployment process required for the
+mechanism. The detection mechanism may be deployed at either or both
+the server and the client side. Deployments on just the server or the client are
+easier to handle than deployments on both of them. The mechanism may
+be an add-on or plugin for existing software, client or server, or it
+may be tightly integrated with existing software, requiring rebuilding
+from source code.
+
+No matter where it is installed, the means of installation influences
+ease of use. A detection mechanism that is available as a ready-to-install
+package will trump others that only exist in the form
+of source code.
+
+\subsection{Security}
+
+Defenders and attackers are often caught in a cat-and-mouse game,
+where countermeasures are bypassed by canny attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by cannier
+attacks, and so on. We use security to refer to the ability of a
+detection mechanism to resist circumvention.
+
+A mechanism that has not been bypassed is not eternally secure, as it
+is possible that a bypass method will be discovered in the future. We
+examine the various approaches based on the knowledge we have so far,
+that is, whether there are any known ways to bypass the detection
+mechanism today.
+
+\subsection{Point of Detection}
+\label{sec:point}
+
+Detection mechanisms vary on the location where they detect an attack.
+There are four different points where an attack can be caught, as seen
+in Figure~\ref{fig:attacks}:
+
+\begin{enumerate}
+\item At the user's browser (Point {\sc ub}).
+\item En route from the server to the user's browser---in most cases
+within a proxy (Point {\sc s}t{\sc b}).
+\item At the database abstraction layer, before it reaches the server's database
+  (Point {\sc dbal}).
+\item After the malicious code reaches the server's database
+  (Point {\sc db}).
+\end{enumerate}
 
@@
 {\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
-{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKS09,MKLS11},
+{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\vspace{-4mm}
+\vspace{-5mm}
 \end{figure}
-
-\subsection{Ease of Use}
-\label{sec:deployment}
-
-The value of a detection mechanism as a practical tool depends on how
-easy it is to deploy it in a production setting. This aspect is
-orthogonal to the
-value of a detection mechanism as a research finding. Devising a
-technique to detect a hitherto undetectable class of attacks may be an
-excellent research contribution that merits publication; it may also
-be heavily cited and open the road to other, practical
-implementations in the future.
-
-Ease of use depends on the deployment process required for the
-mechanism. The detection mechanism may be deployed at either or both
-the server and the client side. Deployments on just the server or the client are
-easier to handle than deployments on both of them. The mechanism may
-be an add-on or plugin for existing software, client or server, or it
-may be tightly integrated with existing software, requiring rebuilding
-from source code.
-
-No matter where it is installed, the means of installation influences
-ease of use. A detection mechanism that is available as a ready-to-install
-package will trump others that only exist in the form
-of source code.
-
-\subsection{Security}
-
-Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by canny attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by cannier
-attacks, and so on. We use security to refer to the ability of a
-detection mechanism to resist circumvention.
-
-A mechanism that has not been bypassed is not eternally secure, as it
-is possible that a bypass method will be discovered in the future. We
-examine the various approaches based on the knowledge we have so far,
-that is, whether there are any known ways to bypass the detection
-mechanism today.
-
-\subsection{Point of Detection}
-\label{sec:point}
-
-Detection mechanisms vary on the location where they detect an attack.
-There are four different points where an attack can be caught, as seen
-in Figure~\ref{fig:attacks}:
-
-\begin{enumerate}
-\item At the user's browser (Point {\sc ub}).
-\item En route from the server to the user's browser---in most cases
-within a proxy (Point {\sc s}t{\sc b}).
-\item At the database abstraction layer, before it reaches the server's database
-  (Point {\sc dbal}).
-\item After the malicious code reaches the server's database
-  (Point {\sc db}).
-\end{enumerate}
 
@@
     \end{threeparttable}
-    \vspace{-4mm}
+    \vspace{-5mm}
 \end{table*}
@@
 
-We categorize and analyze a large set of defenses developed to detect
-and prevent
+We categorize and analyze a large set of defenses developed to prevent
 the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
@@
 The key idea behind parse-tree validation is to compare the tree
-representation of the abstract syntactic structure of the source code
+representation of the abstract syntactic structure of the code
 that is about to be executed with the one that was originally
@@
 site from which it came from.
-
 Stock et al.~\cite{SLMS14} propose a scheme that also operates
@@
 
+\begin{figure}[t]
+\begin{center}
+\leavevmode
+\includegraphics[scale=0.39]{barchart.pdf}
+\end{center}
+\vspace{-5mm}
+\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
+used for testing of web attack defenses.
+Specifically, the publications that used a particular source are as follows:
+{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
+Bugtraq~\cite{PB05,KKVJ06,JEP08},
+{\sc xss}ed.com~\cite{NSS06,APKLM10},
+ha.ckers.org~\cite{TNH07,PSC09,LV09},
+Microsoft~\cite{RDWDE07}.}
+\vspace{-5mm}
+\end{figure}
+
 Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
@@
 making sure that their mechanisms can detect known attacks rather than
-seeing how they respond under normal conditions. In some occasions,
+seeing how they respond under normal conditions. In some cases,
 where the number of {\sc tp} results are not quantified, authors did
@@
 %~\cite{phpbb}.
-
-\begin{figure}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.39]{barchart.pdf}
-\end{center}
-\vspace{-3mm}
-\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
-used for testing of web attack defenses.
-Specifically, the publications that used a particular source are as follows:
-{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-Bugtraq~\cite{PB05,KKVJ06,JEP08},
-{\sc xss}ed.com~\cite{NSS06,APKLM10},
-ha.ckers.org~\cite{TNH07,PSC09,LV09},
-Microsoft~\cite{RDWDE07}.}
-\vspace{-4mm}
-\end{figure}
 
@@
     \end{threeparttable}
-    \vspace{-4mm}
+    \vspace{-5mm}
 \end{table}
@@
 only 3 out of 35 (8.5\%) publications have currently their testbeds
-available on-line.
+available.
 
@@
 
-\vspace{-2mm}
+\vspace{-4.5mm}
 

### 2016-03-17 docs/questioning.tex
now 14 pages. Also updated citation numbers

@@
 
-\setlength{\footnotesep}{0.3cm}
+\setlength{\footnotesep}{0.28cm}
 \setlength{\skip\footins}{0.1cm}
@@
 All the above requirements are considered important
-when building security mechanisms for the protection of
+when building mechanisms for the protection of
 applications~\cite{A01,A00,SPWS13,nature2014}.
@@
 \end{center}
-\vspace{-3mm}
+\vspace{-4mm}
 \caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
@@
 \end{center}
-\vspace{-7mm}
+\vspace{-5mm}
 \caption{\label{fig:attacks}Attack model for dynamic and domain specific
@@
 malicious code is permanently stored on the server ({\sc p-xss} 5).
-The injected code residing at server side then re-enters the
+The injected code residing at server-side then re-enters the
 application's execution flow and becomes part of the content that is
@@
 it may affect the client, or both. The
-usefulness of a detection mechanism depends therefore on the
+usefulness of a mechanism depends therefore on the
 computational cost it requires and on where it imposes it, as
-different overheads may be acceptable at the server side than the client side.
+different overheads may be acceptable at the server-side than the client-side.
 
@@
 mechanism. The detection mechanism may be deployed at either or both
-the server and the client side. Deployments on just the server or the client are
+the server and the client-side. Deployments on just the server or the client are
 easier to handle than deployments on both of them. The mechanism may
@@
 \leavevmode
-\includegraphics[scale=0.56]{defenses.pdf}
+\includegraphics[scale=0.54]{defenses.pdf}
 \end{center}
-\vspace{-3mm}
+\vspace{-4.5mm}
 \caption{\label{fig:defenses}The basic categories of countermeasures
@@
 that present corresponding mechanisms:
-{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KKVJ06,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
+{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
 {\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
@@
     \label{tab:comp}
-    \vspace{-3mm}
+    \vspace{-4mm}
 \centering
@@
     \begin{small}
-\scalebox{0.80}{
+\scalebox{0.78}{
     \begin{tabular}{l|c|c|cc|c}
@@
   \multirow{2}{*}{Parse-Tree Validation}
-  &   {\sc sqlg}uard~\cite{BWS05} & 243 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
-  &   {\sc sqlc}heck~\cite{SW06} & 402 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlg}uard~\cite{BWS05} & 305 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlc}heck~\cite{SW06} & 473 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
   \hline
   \multirow{13}{*}{Policy Enforcement}
-  &   {\sc dsi}~\cite{NSS06} & 135 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   NoForge~\cite{JKK06a} & 35 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
-  &   Noxes~\cite{KKVJ06,KJKV09} & 268,40 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
+  &   {\sc dsi}~\cite{NSS06} & 168 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   NoForge~\cite{JKK06a} & 151 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
+  &   Noxes~\cite{KJKV09} & 58 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
   % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\sc beep}~\cite{TNH07} & 282 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
-  &   BrowserShield~\cite{RDWDE07} & 219 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
-  &   CoreScript~\cite{YCIS07} & 181 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 46 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
+  &   {\sc beep}~\cite{TNH07} & 335 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
+  &   BrowserShield~\cite{RDWDE07} & 263 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
+  &   CoreScript~\cite{YCIS07} & 199 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 56 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
   % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   Phung et al.~\cite{PSC09} & 75 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
-  &   ConScript~\cite{ML10} & 122 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   CsFire~\cite{DDHPJ10} & 35 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
-  &   {\sc csp}~\cite{SSM10} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
+  &   Phung et al.~\cite{PSC09} & 101 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
+  &   ConScript~\cite{ML10} & 152 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
+  &   CsFire~\cite{DDHPJ10} & 46 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
+  &   {\sc csp}~\cite{SSM10} & 117 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
   &   j{\sc csrf}~\cite{PS11} & 4 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   WebJail~\cite{VDDPJ11} & 25 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
+  &   WebJail~\cite{VDDPJ11} & 45 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
@@
   \multirow{4}{*}{{\sc isr}}
-  &   {\sc sql}rand~\cite{BK04} & 286 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
-  &   {\sc sm}ask~\cite{JB07} & 27 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Noncespaces~\cite{GC09} & 109 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
-  &   x{\sc js}~\cite{APKLM10} & 18 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
+  &   {\sc sql}rand~\cite{BK04} & 365 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
+  &   {\sc sm}ask~\cite{JB07} & 28 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
+  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
   \thickhline
@@
   \multirow{7}{*}{Taint Tracking}
-  &   Haldar et al.~\cite{HCF05} & 177 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc csse}~\cite{PB05} & 312 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
+  &   Haldar et al.~\cite{HCF05} & 208 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc csse}~\cite{PB05} & 347 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
   % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-  &   Xu et al.~\cite{XBS06} & 297 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc wasc}~\cite{NLC07} & 31 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Vogt et al.~\cite{VFJKKV07} & 322 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\sc php} Aspis~\cite{PMP11} & 12 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
-  &   Stock et al.~\cite{SLMS14} & 14 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
+  &   Xu et al.~\cite{XBS06} & 346 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc wasc}~\cite{NLC07} & 32 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Vogt et al.~\cite{VFJKKV07} & 400 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\sc php} Aspis~\cite{PMP11} & 20 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
+  &   Stock et al.~\cite{SLMS14} & 15 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
   \hline 
   \multirow{6}{*}{Training}
-  &   {\sc didafit}~\cite{LLW02} & 85 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
-  &   {\sc amnesia}~\cite{HO05b} & 376 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
-  &   libAnomaly~\cite{VMV05} & 226 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
-  &   {\sc xssds}~\cite{JEP08} & 64 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  &   {\sc swap}~\cite{WPLKK09} & 52 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
-  &   {\sc sd}river~\cite{MS09,MKLS11} & 22,6 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
+  &   {\sc didafit}~\cite{LLW02} & 190 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
+  &   {\sc amnesia}~\cite{HO05b} & 474 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
+  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc xssds}~\cite{JEP08} & 85 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
+  &   {\sc sd}river~\cite{MS09,MKLS11} & 28 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
   % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
@@
   \multirow{3}{*}{Hybrid}
-  &   {\sc xss-guard}~\cite{BV08} & 97 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
-  &   Blueprint~\cite{LV09} & 110 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   Diglossia~\cite{SMS13} & 12 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   {\sc xss-guard}~\cite{BV08} & 132 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
+  &   Blueprint~\cite{LV09} & 152 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
+  &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
   \thickhline
@@
     \end{threeparttable}
-    \vspace{-5mm}
+    \vspace{-5.5mm}
 \end{table*}
@@
 using a framework that implements policy enforcement, developers must
-define specific security policies on the server side. Policies can be
+define specific security policies on the server-side. Policies can be
 expressed through JavaScript extensions, pattern matching, or
@@
 
-Noxes~\cite{KKVJ06,KJKV09} is the only
+Noxes~\cite{KJKV09} is the only
 framework that partially allows
@@
 to confine their behavior. BrowserShield~\cite{RDWDE07}
-acts as a proxy on the server side (Point {\sc s}t{\sc b}) to
+acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
 parse the {\sc html} of server responses and identify
@@
 JavaScript functions. In both cases, policy enforcement takes
-place at client side, in the JavaScript engine of the browser (Point {\sc ub}).
+place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
 In this way, {\sc xxs} attacks that take advantage
@@
 the browser will not include the token.
-Thus, sites that create part of their {\sc html} code at client side
+Thus, sites that create part of their {\sc html} code at client-side
 will remain vulnerable. In addition, it does not
@@
 examines cross-domain interactions to design a
-cross-domain policy at the client side (Point {\sc ub}).
+cross-domain policy at the client-side (Point {\sc ub}).
 The policy is based on the concept of a relaxed
@@
 require significant source code modifications by the
-developers on the server side to introduce and enforce
+developers on the server-side to introduce and enforce
 the applied policies.
@@
 that follows a different approach. In contrast to the above
-schemes, which operate on the server side, their technique tracks sensitive
-information at the client side (Point {\sc ub}). This is a form of
+schemes, which operate on the server-side, their technique tracks sensitive
+information at the client-side (Point {\sc ub}). This is a form of
 positive data flow tracking, where tagged data is considered to be
@@
 that untrusted content is not executed, Blueprint generates at the
-server side a parsed tree from untrusted {\sc html} to ensure that it
+server-side a parsed tree from untrusted {\sc html} to ensure that it
 does not contain any dynamic content. Then, the parsed tree is
@@
 \end{center}
-\vspace{-5mm}
+\vspace{-5.7mm}
 \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
@@
 {\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-Bugtraq~\cite{PB05,KKVJ06,JEP08},
+Bugtraq~\cite{PB05,KJKV09,JEP08},
 {\sc xss}ed.com~\cite{NSS06,APKLM10},
@@
 Microsoft~\cite{RDWDE07}.}
-\vspace{-5mm}
+\vspace{-6.3mm}
 \end{figure}
@@
 \caption{Availability of the studied defenses.}
-\vspace{-3mm}
+\vspace{-4mm}
     \label{tab:avail}
@@
   &   NoForge~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
-  &   Noxes~\cite{KKVJ06,KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
+  &   Noxes~\cite{KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
   % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
@@
 In addition, it indicates if the overhead is incurred at the
-server ({\sc s}) or at the client side ({\sc c}). In almost half of
+server ({\sc s}) or at the client-side ({\sc c}). In almost half of
 the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
@@
 other hand, there are cases where the policies introduced at the
-server are enforced at the client side, via a library embedded in the
+server are enforced at the client-side, via a library embedded in the
 server's response (i.e., Blueprint~\cite{LV09}).
@@
 {\sc dsl} injection and {\sc csrf} attacks take place
-at the server side, all mechanisms that detect
+at the server-side, all mechanisms that detect
 such attacks are placed at some point within the server-side infrastructure.
@@
 see that attack detection and prevention may take place either at the server or
-the client side. In the first case, a proxy is typically placed in front of the server
+the client-side. In the first case, a proxy is typically placed in front of the server
 to examine the server's responses before they reach a user's 
@@
 attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client side: in particular, 14 out of 24
+perform detection on the client-side: in particular, 14 out of 24
 frameworks (58,3\%) detect {\sc xss} attacks at the
-client side. Note that the majority of the mechanisms that detect
+client-side. Note that the majority of the mechanisms that detect
 such attacks on the server can also detect {\sc dsl} code
@@
 tested in a poor manner. In many cases, researchers tend to not providing
-results on false positives or false negatives for their detection mechanisms
+results on false positives or false negatives for their mechanisms
 (where applicable).
@@
 the browser are not easy to deploy because modifications are needed
-both on the server and the client side.
+both on the server and the client-side.
 Conversely, it may be possible to deliver
 the tools to the user unobtrusively; for example, we saw that
-Blueprint~\cite{LV09} enforces policies at the client side by embedding a library
+Blueprint~\cite{LV09} enforces policies at the client-side by embedding a library
 in the server's response to the client. In general, when developing a
@@
 
-\vspace{-4.5mm}
+\vspace{-3.5mm}
 

### 2016-03-17 docs/questioning.tex
even better, with more original content

@@
 \titlespacing*{\section}
-{0pt}{1ex}{0.8ex}
+{0pt}{1ex}{0.6ex}
 \titlespacing*{\subsection}
-{0pt}{1ex}{0.8ex}
+{0pt}{1ex}{0.6ex}
 \titlespacing*{\subsubsection}
-{0pt}{1ex}{0.8ex}
+{0pt}{1ex}{0.6ex}
 
@@
 
-% The rest of the paper is organized as follows:
-% Section~\ref{sec:attacks} provides some insights on
-% code injection attacks and
-% Section~\ref{sec:model} presents our proposed model.
-% Section~\ref{sec:dimensions} introduces the dimensions
-% across which we analyze the various defenses.
-% Our categorization and analysis is presented in
-% Section~\ref{sec:defs} and a discussion is provided in
-% Section~\ref{sec:discussion}. Finally,
-% Section~\ref{sec:lessons-learned} highlights
-% some lessons learned from our observations
-% and Section~\ref{sec:conclusion} concludes the paper.
+The rest of the paper is organized as follows:
+Section~\ref{sec:attacks} provides some insights on
+web application attacks and
+Section~\ref{sec:model} presents our proposed model.
+Section~\ref{sec:dimensions} introduces the dimensions
+across which we analyze the various defenses.
+Our categorization and analysis is presented in
+Section~\ref{sec:defs} and our observations are
+provided in Section~\ref{sec:discussion}.
+Finally, Section~\ref{sec:lessons-learned}
+highlights some lessons learned from our observations
+and Section~\ref{sec:conclusion} concludes the paper.
 
@@
 of the application and the location of the programming flaw that leads
-to the attack~\cite{RL12b}.
-
-% Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
-% {\it ``unexpected (and unexpectedly powerful) computational models
-%   inside targeted systems, which turn a part of the target into a
-%   so-called `weird machine' programmable by the attacker via crafted
-%   inputs (a.k.a. `exploits').''} In particular, {\it ``every
-%   application that copies untrusted input verbatim into an output
-%   program is vulnerable to code injection.''} Ray and
-% Ligatti~\cite{RL12b} have proved this claim based on formal language
-% theory.
+to the attack.
+Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
+{\it ``unexpected (and unexpectedly powerful) computational models
+  inside targeted systems, which turn a part of the target into a
+  so-called `weird machine' programmable by the attacker via crafted
+  inputs (a.k.a. `exploits').''} In particular, {\it ``every
+  application that copies untrusted input verbatim into an output
+  program is vulnerable to code injection.''} Ray and
+Ligatti~\cite{RL12b} have proved this claim based on formal language
+theory.
 
@@
 different overheads may be acceptable at the server-side than the client-side.
-
 What kind of numbers is reported matters as well. Reporting absolute
@@
 \end{center}
-\vspace{-4.5mm}
+\vspace{-5mm}
 \caption{\label{fig:defenses}The basic categories of countermeasures
@@
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\vspace{-5mm}
+\vspace{-6mm}
 \end{figure}
@@
        mark ({\bf ?}) indicates that a link to the software
-       was included in the publication but is now inaccessible.
-} \\
+       was included in the publication but is now inaccessible.} \\
     \end{tabular}}
@@
     \end{threeparttable}
-    \vspace{-5mm}
+    \vspace{-7mm}
 \end{table}
@@
 For frameworks that deal with {\sc xss} attacks, we
-see that attack detection and prevention may take place either at the server or
+see that attack prevention may take place either at the server or
 the client-side. In the first case, a proxy is typically placed in front of the server

### 2016-03-18 docs/questioning.tex
minor fix
minor changes
enriched the introduction section

@@
 \lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
+\lstset{aboveskip=3.5pt,belowskip=3.5pt}
 
@@
 didn't consider mechanisms that haven't been presented in research papers.
-Finally, we {\it analyze} each mechanism across the
+
+Furthermore, we {\it analyze} each mechanism across the
 following dimensions:
@@
 \end{itemize}
-
 \noindent
@@
 to each other.
+In addition, we attempt to shed light on the factors
+that may impede the adoption of defenses in practice.
+Finally,
+we provide some lessons and recommendations that
+developers of new defenses may find helpful.
+
 The main contributions of this paper are the following:
@@
   criteria that are important for building protection mechanisms.
-\item We provide insight based on the issues that arise from our analysis. We put
-  emphasis on factors that may hinder the widespread deployment of
+\item We provide insight based on the issues that arise from our analysis.
+  We put emphasis on factors that may hinder the widespread deployment of
   protection mechanisms, and the transition of tools from research to practice.
 \end{enumerate}
+\vspace{-0.05mm}
 
@@
 
-\section{Code Injection in Web Applications}
+\section{Code Injection Attacks in Web Applications}
 \label{sec:attacks}
@@
 to the attack.
+
 Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
@@
 \end{center}
-\vspace{-4mm}
+\vspace{-5mm}
 \caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
@@
 to imagine more detrimental scenarios.
+
 A recent attack called {\sc php} Object Injection
@@
 \end{center}
-\vspace{-5mm}
+\vspace{-5.5mm}
 \caption{\label{fig:attacks}Attack model for dynamic and domain specific
@@
 (4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
-\vspace{-5mm}
+\vspace{-6mm}
 \end{figure*}
@@
 \begin{itemize}
-\item Statistical measurements that show how reliable the detection really
-  is.
+\item Statistical measurements that show how
+reliable the detection really is.
 \item Research practices that promote replication and validation
@@
 
+\vspace{0.5mm}
 \noindent\begin{minipage}{0.5\linewidth}
@@
 \end{center}
-\vspace{-5mm}
+\vspace{-5.4mm}
 \caption{\label{fig:defenses}The basic categories of countermeasures
@@
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\vspace{-6mm}
+\vspace{-5.6mm}
 \end{figure}
@@
     \begin{small}
-\scalebox{0.78}{
+\scalebox{0.77}{
     \begin{tabular}{l|c|c|cc|c}
@@
     \end{threeparttable}
-    \vspace{-5.5mm}
+    \vspace{-6mm}
 \end{table*}
@@
 
-For domain-specific language code injection attacks, mechanisms check 
+For {\sc dsl} code injection attacks, mechanisms check 
 the query before the inclusion of user input with the one
@@
     \end{threeparttable}
-    \vspace{-7mm}
+    \vspace{-6mm}
 \end{table}
@@
 
-\vspace{-3.5mm}
-
 \bibliographystyle{IEEEtran}

### 2016-03-18 docs/questioning.tex
minor change

@@
 Section~\ref{sec:attacks} provides some insights on
-web application attacks and
+web code injection attacks and
 Section~\ref{sec:model} presents our proposed model.
@@
 setting could also propel their adoption.
+
 We hope that the exploitation model, analysis, and observations that

### 2016-03-18 docs/questioning.tex
minor fixes

@@
 Then, we {\it categorize} a selection of representative
-protection mechanisms. Specifically, we include protection
+protection mechanisms. In our selection we include protection
 mechanisms that counter web attacks when they take place,
@@
 into the application's page. {\sc html} injection is mainly associated
-with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection,
+with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection
 can also be used as a vehicle for Cross-Site Request Forgery
@@
 not possible, for whatever reason, it is important to make sure that
-all computer code and test data is available noting any restrictions
+all computer code and test data is available, noting any restrictions
 on accessibility. Availability of computer code has been recognized as
@@
 defenses that have been proposed in publications cited more than
-20 times according to Google Scholar.\footnote{\scriptsize\url{scholar.google.gr}}
+20 times according to Google Scholar.
 We also include some recent works that have been
@@
 embedded scripts, developers must utilize
-{\sc csp}'s {\em nonce} concept.
+the {\sc csp}'s {\em nonce} concept.
 This is an unpredictable,
@@
 mechanisms must follow good coding practices and make sure that
-randomized code statement are never leaked
+randomized code statements are never leaked
 (e.g., as part of an exception error),
@@
 An issue that involves all taint tracking schemes involves
-the difficulty of maintaining accurate taint~\cite{GMPS11}
+the difficulty of maintaining accurate taints~\cite{GMPS11}
 (e.g. implicit flows~\cite{ME07}).
@@
 One of our key findings indicates that many proposed defenses are
-tested in a poor manner. In many cases, researchers tend to not providing
+tested in a poor manner. In many cases, researchers tend to not provide
 results on false positives or false negatives for their mechanisms

### 2016-07-19 docs/comments/comments.tex
first steps of the revision

--- 2016-03-18 docs/questioning.tex
@@
 \titlespacing*{\section}
-{0pt}{1ex}{0.6ex}
+{0pt}{1ex}{0.55ex}
 \titlespacing*{\subsection}
-{0pt}{1ex}{0.6ex}
+{0pt}{1ex}{0.55ex}
 \titlespacing*{\subsubsection}
-{0pt}{1ex}{0.6ex}
+{0pt}{1ex}{0.55ex}
 
@@
 \lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
-\lstset{aboveskip=3.5pt,belowskip=3.5pt}
+\lstset{aboveskip=3.3pt,belowskip=3.3pt}
 
@@
 
-\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}}
+\title{Defending Against Web Application Attacks: Approaches, Challenges and Implications
+\newline\newline
+\small{\textbf{Response to Review Comments}}}
 
@@
 
-\section{Introduction}
+\section{General Remarks}
+\label{sec:rem}
 
-Web application attacks may involve security misconfigurations, broken
-authentication and session management, or other issues. Some of the
-most dangerous and prevalent web application attacks, however,
-exploit vulnerabilities associated with improper validation or filtering
-of untrusted inputs, resulting in the injection of malicious
-script or domain-specific language code.
-Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SG07},
-and {\sc sql} injection attacks~\cite{RL12b},
-%and Cross-Site Request Forgery
-% ({\sc csrf}) attacks~\cite{LZRL09},
-among others.
+We are thankful to the reviewers for their thorough reviews.
+We have revised our research paper based on their suggestions and comments.
+All additions and changes are highlighted in yellow
+in the revised manuscript.
+Number wise answers to their specific
+comments / suggestions / queries are as follows.
 
-For the past several years,
-these attacks have been topping the lists of the most dangerous vulnerabilities
-published by
-{\sc owasp},\footnote{\scriptsize\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
-%~\cite{OWASPtop10},
-{\sc mitre},\footnote{\scriptsize\url{http://cwe.mitre.org/top25/}}
-%~\cite{MITREtop25},
-and other organizations.
-For instance, consider the case of {\sc owasp}'s popular Top Ten
-project,%\footnote{\url{https://www.owasp.org/index.php/Top_10_2013-Top_10}}
-%~\cite{OWASPtop10},
-which aims to raise awareness about web application security by
-identifying some of the most critical risks organizations may face.
-In its three consecutive Top Ten lists (2007, 2010, 2013), different
-injection attacks dominate the top five positions.
+\section{AE Comments}
+\label{sec:ae}
 
-At the same time, attackers find new ways~\cite{HNSHS12,DKH14}
-to bypass defense mechanisms using a variety of techniques,
-despite the numerous countermeasures that are being introduced.
-As an example, already by 2006,
-there were more than 20 proposed defenses
-against {\sc sql} injection attacks~\cite{HVO06}.
-Since then, the number has doubled, while researchers have indicated that
-the number of {\sc sql} injection attacks has been steadily
-increasing in recent years~\cite{SSL12}.
-
-In this paper, we explore how different attacks associated with 
-the exploitation of untrusted input validation errors can be modeled 
-under a {\it common perspective}. To that end, we propose an exploitation
-model which highlights that most of the steps needed to mount
-different types of code injection attacks are
-common.\footnote{\scriptsize Note that we do not consider lower-level attacks based on
-the exploitation of memory corruption vulnerabilities and the injection
-of binary code---see Section~\ref{sec:attacks}.} This is validated by the fact that
-some protection mechanisms defend against more than one of these
-types of attacks.
-
-Then, we {\it categorize} a selection of representative
-protection mechanisms. In our selection we include protection
-mechanisms that counter web attacks when they take place,
-while we do not consider countermeasures that identify
-vulnerabilities using static program analysis~\cite{SZ12}
-(which takes place during the development or testing
-phases). Similarly, dynamic analysis techniques that examine
-applications to identify vulnerabilities that may lead to the attacks
-that we described earlier are out of scope as well. Note also, that we
-didn't consider mechanisms that haven't been presented in research papers.
-
-Furthermore, we {\it analyze} each mechanism across the
-following dimensions:
-\begin{itemize}
-\item {\it Accuracy:} protection mechanisms are as good
-  as their detection capability; this requires low false positive and
-  false negative rates.
-\item {\it Availability:} whether the protection mechanism and its
-  testbed are publicly available.
-\item {\it Performance overhead:} the 
-  overhead imposed by the mechanisms at their points of deployment.
-\item {\it Ease of use:} whether the
-  mechanism is practical in terms of deployment
-  and can be easily adopted by security experts.
-\item {\it Security:} the robustness of the protection mechanism against
-  attackers with knowledge of its internals who attempt to circumvent it.
-\item {\it Detection Point:} the location where a mechanism detects an attack
-  based on our exploitation model.
-\end{itemize}
-\noindent
-All the above requirements are considered important
-when building mechanisms for the protection of
-applications~\cite{A01,A00,SPWS13,nature2014}.
-Based on this analysis, we identify the advantages
-and disadvantages of the
-various mechanisms and enumerate some of their common
-characteristics. We also draw useful conclusions
-about the various protection categories and see how they compare
-to each other.
-In addition, we attempt to shed light on the factors
-that may impede the adoption of defenses in practice.
-Finally,
-we provide some lessons and recommendations that
-developers of new defenses may find helpful.
-
-The main contributions of this paper are the following:
-
-\begin{enumerate}
-\item We provide a unified exploitation model for different types of
-  web application attacks based on code injection.
-\item We categorize and analyze proposed defenses using a set of
-  criteria that are important for building protection mechanisms.
-\item We provide insight based on the issues that arise from our analysis.
-  We put emphasis on factors that may hinder the widespread deployment of
-  protection mechanisms, and the transition of tools from research to practice.
-\end{enumerate}
-\vspace{-0.05mm}
-
-The rest of the paper is organized as follows:
-Section~\ref{sec:attacks} provides some insights on
-web code injection attacks and
-Section~\ref{sec:model} presents our proposed model.
-Section~\ref{sec:dimensions} introduces the dimensions
-across which we analyze the various defenses.
-Our categorization and analysis is presented in
-Section~\ref{sec:defs} and our observations are
-provided in Section~\ref{sec:discussion}.
-Finally, Section~\ref{sec:lessons-learned}
-highlights some lessons learned from our observations
-and Section~\ref{sec:conclusion} concludes the paper.
-
-\section{Code Injection Attacks in Web Applications}
-\label{sec:attacks}
-
-Lack of input validation is a major vulnerability behind dangerous web
-application attacks. By taking advantage of this, attackers can inject
-their code into applications to perform malicious tasks. Exploits of
-this kind can have different forms depending on the execution context
-of the application and the location of the programming flaw that leads
-to the attack.
-
-Bratus et al.~\cite{BLSPS11} portray the issue in a more generic way:
-{\it ``unexpected (and unexpectedly powerful) computational models
-  inside targeted systems, which turn a part of the target into a
-  so-called `weird machine' programmable by the attacker via crafted
-  inputs (a.k.a. `exploits').''} In particular, {\it ``every
-  application that copies untrusted input verbatim into an output
-  program is vulnerable to code injection.''} Ray and
-Ligatti~\cite{RL12b} have proved this claim based on formal language
-theory.
-
-\begin{figure}
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.55]{attack-tree-uml.pdf}
-\end{center}
-\vspace{-5mm}
-\caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
-language code injection attacks against web applications.}
-\vspace{-5mm}
-\end{figure}
-
-Code injection attacks can be divided in two categories. The first
-involves binary code and the second higher-level language code. An
-extensive survey on binary code injection attacks was conducted by
-Lhee and Chapin~\cite{LC03}. Advances in memory corruption vulnerability
-exploitation have been studied extensively~\cite{PB04, SPWS13}
-and countermeasures to such attacks
-have already been analyzed~\cite{YJP12}.
-% \cite[Sec. 13.8]{DKZ12}.
-In this work we do not consider binary code injection,
-focusing instead on defenses
-that protect web applications against attacks based on the
-injection of higher-level language code.
-
-Figure~\ref{fig:taxonomy} presents a taxonomy of source
-code injection attacks against web applications.
-Such attacks may involve high-level language code, written in either a
-{\it Domain Specific Language} ({\sc dsl}) or a {\it Dynamic Language}.
-To illustrate, we discuss examples from both categories
-that will be used throughout the paper.
-
-Injection attacks that involve {\sc dsl}s constitute an important
-subset of the code injection problem, as {\sc dsl}s such as
-{\sc sql} and {\sc xml} play a significant role in the development of
-both web and mobile applications. For example, many applications have
-interfaces through which a user enters input to interact with the
-application, thereby interacting with the underlying database. This
-input can become part of an {\sc sql} query and gets executed on the
-target database. Code injection attacks that exploit vulnerabilities
-in database interfaces by taking advantage of input validation issues,
-such as incorrectly passed parameters or incorrect type handling, are
-called {\sc sql} injection attacks~\cite{MS09,HVO06,SW06}.
-Consider a trivial exploit that takes advantage of incorrectly
-filtered quotation characters in an application that shows the
-password of a forgetful user by executing the following
-query:
-
-\lstset{language=SQL}
-\begin{lstlisting}
-SELECT password from userdata WHERE id = 'Alice'
-\end{lstlisting}
+{\bf Comment} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.".\\
 
 \noindent
-Attackers that would input the string {\tt anything' OR 'x'='x}
-could view every item in the table.
-%obtain a user's password by email.
-Savvy programmers can use certain {\sc api} functions, such as {\sc php}'s
-{\tt mysql\_real\_escape\_string()}, to detect malformed input, or,
-better, use prepared {\sc sql} statements instead of statement
-templates. Unfortunately, the increasing number of {\sc sql} injection
-attacks suggests that programmers are not always that careful. Using
-similar techniques, malicious users can mount other exploits based on
-{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07}, {\sc
-  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
-wide-ranging. A malicious user can view sensitive information, destroy
-or modify protected data, or even crash the entire application.
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
 
-{\sc html} is another {\sc dsl} that can be used for malicious
-purposes when an application does not properly handle user-supplied
-data. Based on this vulnerability attackers can supply valid {\sc
-  html}, typically via a parameter value, and inject their own content
-into the application's page. {\sc html} injection is mainly associated
-with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection
-can also be used as a vehicle for Cross-Site Request Forgery
-({\sc csrf}) attacks~\cite{BJM08, LZRL09}
-(even though a common {\sc csrf} attack does not necessarily
-involve code injection).
-Consider a bulletin board system where {\tt img} tags are allowed.
-A malicious user could embed a {\sc csrf} request within an
-{\tt img} tag in the following manner:
+\section{Reviewer \#1}
+\label{sec:r1}
 
-\lstset{language=HTML}
-\begin{lstlisting}
-<img src='http://www.vulnerable.com/admin.php?edituserwithID=13&addgroup=admin'/>
-\end{lstlisting}
+{\bf Comment 1:} ``Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum.
+Lorem Ipsum".\\
 
 \noindent
-When the page with this injected code is accessed by an administrator,
-the attacker (with {\sc id} 13) will gain administrative privileges
-over the vulnerable.com web page,
-while the administrator of the bulletin board system
-will have no immediate indication that there has been an attack.
-
-A recent class of code injection attacks involve dynamic languages
-such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
-JavaScript injection attacks make up a large subset of dynamic
-language code injection attacks and are considered a critical issue
-in web application security mainly because they are associated with
-major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
-Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
-Such attacks are enabled when a web application accepts
-and redisplays data of uncertain origin without
-proper validation and filtering. Based on this flaw, an attacker
-can manage to inject a script in the JavaScript engine of a browser
-and alter its execution flow~\cite{ELX07}.
-For a typical {\sc xss} example that involves JavaScript injection
-consider a web page that prints the value
-of a query parameter ({\tt query}) from the
-page's {\sc url} as part of the page's content
-without escaping the value. Attackers
-can take advantage of this and inject an {\tt iframe} tag
-into the page to steal a user's cookie and
-send it via an image request to a web site
-under their control (malicious.com).
-This could be achieved by including the following
-link to the malicious web site (or sending it via phishing
-email) and inducing the user to click on it:
-
-\lstset{language=HTML}
-\begin{lstlisting}
-http://example.com/vulnerable.html?query=<iframe src="javascript:document.body.innerHTML=+'<img src=\"http://malicious.com/?c='+encodeURIComponent(document.cookie)+'\">'"></iframe>
-\end{lstlisting}
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
 
 \noindent
-Note that in many cases {\sc xss} attacks
-involve the injection of both {\sc html} and JavaScript code.
-
-A simple example of a {\sc php} injection attack is an input string
-that is fed into an {\tt eval()} function call, e.g.:
-
-\lstset{language=PHP}
-\begin{lstlisting}
-$variable = $_GET['var']; 
-$input = $_GET['value'];
-eval('$variable = ' . $input . ';')
-\end{lstlisting}
+{\bf Comment 2:} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
 
 \noindent
-The user may pass into the {\tt value} parameter code that will
-be executed on the server. Hence, if an attacker provides as
-input the following string: {\tt 10 ; system("touch foo");}
-then a file will be created on the server---it is easy
-to imagine more detrimental scenarios.
-
-A recent attack called {\sc php} Object Injection
-({\sc poi})~\cite{DKH14} does not directly involve
-the injection of code, but still achieves arbitrary code execution
-in the context of a {\sc php} application through the
-injection of specially crafted objects.
-These objects are injected as part of cookies,
-which, when deserialized
-by the application, result in arbitrary code execution.
-Note that the exploitation model we propose
-in the following Section also captures such attacks.
-
-\begin{figure*}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.48]{attacks-steps-CSRF.pdf}
-\end{center}
-\vspace{-5.5mm}
-\caption{\label{fig:attacks}Attack model for dynamic and domain specific
-language code injection in web applications.
-Transitions are labeled with the different attacks that use that path,
-while the numbers next to attack labels denote the 
-sequence of steps for a particular attack.
-Points where different types of defenses
-detect or prevent attacks are marked with an `X' symbol:
-(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
-(2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
-(3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
-(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
-\vspace{-6mm}
-\end{figure*}
-
-\section{Exploitation Model}
-\label{sec:model}
-
-We provide a step-by-step exploitation model to aid in understanding the process
-of carrying out code injection attacks against web
-applications. Figure~\ref{fig:attacks} illustrates the required steps for
-different classes of attacks,
-such as {\sc sql} injection, {\sc xss}, and {\sc csrf}. Links between steps are
-labeled with the different attacks that use that path, while the
-numbers next to attack labels denote the sequence of steps for a
-particular attack. Most steps are common in all attacks, as different attack
-types follow similar exploitation paths, as mentioned in
-the previous section. Large `X' marks on transitions correspond to the
-points where the defenses we consider in this work detect or prevent attacks.
-
-An attacker can initiate an injection attack through two main routes.
-One way is to use the browser of a victim as an attack
-vehicle, through which the code will be injected in the application.
-For example, the attacker could embed a malicious script into a {\sc
-  url} and then trick a user to click on it through social
-engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
-  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
-to inject directly the malicious code on the server through an {\sc http} request
-({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
-in a web application that accepts and processes user input
-without appropriate validation. An attacker could upload data
-containing a specially crafted script
-to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
-an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
-i-csrf 1}),
-or embed malicious
-{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
-Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
-Once the injected code reaches the vulnerable application, it becomes
-a part of a value represented by a program variable. The target of the
-attack determines the route from that point and on. In an {\sc sql} injection
-attack, the injected code becomes part of a query that
-eventually reaches the database where it is executed.
-
-Cross-site scripting attacks fall into two categories, {\it non-persistent}
-(also known as \emph{reflected}) {\sc xss}
-and {\it persistent} (also known as \emph{stored}) {\sc xss}.
-Non-persistent {\sc xss} attacks take place when the
-data provided by a user is processed on-the-fly
-by server-side application logic and ends up without proper sanitization
-into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
-that is eventually rendered by the user's browser.
-Thus, in a non-persistent {\sc xss} attack, the injected code
-is not saved on the server, but immediately becomes part of the
-content that is sent back to a user.
-In persistent {\sc xss} attacks, on the other hand,
-malicious code is permanently stored on the server ({\sc p-xss} 5).
-The injected code residing at server-side then re-enters the
-application's execution flow and becomes part of the content that is
-eventually sent to the user as part of a future response.
-
-{\sc csrf} attacks typically involve just a
-{\sc url} or page that contains a malicious request towards
-a site vulnerable to {\sc csrf}.
-An attacker can entice a victim to click on the {\sc url} or visit the page
-through social engineering ({\sc csrf} 1), which will the result in a malicious
-request towards the vulnerable site ({\sc csrf} 2).
-Note that this scenario does not involve the injection of any code through the
-exploitation of some server-side vulnerability (as is the case with Server 1).
-On the other hand, {\sc csrf} is also possible through injection
-({\sc i-csrf}---recall our example in the previous section).
-In this attack, an attacker
-manages to inject {\sc html} code that contains
-a malicious {\sc csrf} request in the way we described in
-Section~\ref{sec:attacks}.
-This code will be stored
-in the database ({\sc i-csrf} 5)
-and then it will re-enter the application when
-a user visits a page ({\sc i-csrf} 6). When the
-content reaches the browser, a malicious request will be generated
-towards the site that is vulnerable to {\sc csrf}.
-
-\section{Analysis Dimensions}
-\label{sec:dimensions}
-
-Research on web application attack defense mechanisms has a dual
-character. First, a defense mechanism may be important, and therefore
-publishable, because it shows that an attack can be detected or prevented in a
-reliable manner. Second, a defense mechanism may be important not
-just as a research contribution, but as a practical tool, if it can be
-used by administrators and users to shield their applications
-against the supported attacks.
-
-The detection and prevention of attacks
-in a reliable manner can be analyzed using
-criteria common with other research fields:
-\begin{itemize}
-\item Statistical measurements that show how
-reliable the detection really is.
-\item Research practices that promote replication and validation
-of the findings.
-\end{itemize}
-
-\noindent
-Whether a reliable defense mechanism has value in a practical
-setting rests on a different set of criteria:
-\begin{itemize}
-\item What are the overheads imposed by the mechanism?
-\item How easy is it to deploy and use the mechanism?
-\item How robust is it against ways to circumvent it?
-\item At which point throughout the system does it block an attack?
-\end{itemize}
-
-The first two criteria correspond to \emph{Accuracy} and
-\emph{Availability}. The other four criteria correspond to \emph{Runtime
-  Performance}, \emph{Ease of Use}, \emph{Security}, and
-\emph{Point of Detection}.
-
-\subsection{Accuracy}
-\label{ssec:diagnostic-performance}
-
-Web application defenses 
-crucially have to capture the presence of an attack. This, however, does not
-make a defense mechanism immediately useful. A
-detection mechanism must also be reliable.
-Detection accuracy is gauged with the following
-metrics~\cite{GFDLS06,A00}:
-\begin{itemize}
-\item {\bf Sensitivity}: the probability that an attack will be
-  caught.
-\item {\bf Specificity}: the probability that a normal interaction
-  will not be flagged.
-\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
-  reported attack is a real attack. It is the conditional probability
-  that an event is an attack if the detection mechanism flags it as
-  such. 
-\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
-  nothing is reported, no attack has taken place. It is the conditional
-  probability that an event is not an attack given that the detection
-  mechanism flags it as normal.
-\end{itemize}
-
-\noindent
-We will focus on sensitivity and specificity; we will come back to
-\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
-Sensitivity and specifity are defined as follows~\cite{linn2004}:
-\begin{itemize}
-\item True Positive (\textsc{tp}): an attack that raises an alarm.
-\item True Negative (\textsc{tn}): an event that is not an attack and that does
-  not raise an alarm.
-\item False Positive (\textsc{fp}): an event that although it is not an attack,
-  raises an alarm.
-\item False Negative (\textsc{fn}): an event that although is an attack, does
-  not raise an alarm.
-\end{itemize}
-
-\noindent
-With these we can calculate:
-
-\vspace{0.5mm}
-\noindent\begin{minipage}{0.5\linewidth}
-\begin{equation}
-  \textsc{se} = \textrm{Sensitivity} = \frac{\textsc{tp}}{\textsc{tp}
-    + \textsc{fn}}
-\label{eq:sensitivity}
-\end{equation}
-\end{minipage}%
-\begin{minipage}{0.5\linewidth}
-\begin{equation}
-  \textsc{sp} = \textrm{Specificity} = \frac{\textsc{tn}}{\textsc{fp}
-    + \textsc{tn}}
-\label{eq:specificity}
-\end{equation}
-\end{minipage}\par\vspace{\belowdisplayskip}
-
-\noindent
-Sensitivity and specificity can be calculated based on test
-data alone. To calculate sensitivity, we run the test on a
-controlled environment where we allow only attack events to reach the
-system. The ratio of reported attacks over all attacks will give us
-the sensitivity. Similarly, to calculate the specificity we can run
-the test on a controlled environment where we allow only innocuous
-events to reach the system. The ratio of non-reported events over all
-events will give us the specificity.
-Note that the use of sensitivity and specificity in this context
-has been advocated before~\cite{PP12}.
-
-\subsection{Availability}
-
-To ensure reproducibility of research results, the source code
-implementing a detection mechanism should be available to researchers.
-Ideally the code should be available under an open source license, so
-that it is easy to modify and improve an approach; even when this is
-not possible, for whatever reason, it is important to make sure that
-all computer code and test data is available, noting any restrictions
-on accessibility. Availability of computer code has been recognized as
-an important issue outside the computer science field: the journal
-\emph{Nature}, in a recent editorial, adopted a publication policy stressing
-access to code and data~\cite{nature2014}. At a time and date that the
-merits of open access to code are discussed in non computer science
-journals~\cite{easterbrook2014}, we should expect computer scientists
-to lead the way.
-
-\subsection{Performance Overhead}
-
-Detection mechanisms may impose a cost due to their use, as they
-typically introduce some amount of extra computation on existing applications.
-The overhead depends on the specifics of each mechanism. For
-example, it may be due to some form of run-time checking, or some form of
-obfuscation. Also, depending on the approach, the cost may be incurred
-on different places: it may affect a server
-(e.g., its memory or {\sc cpu} usage, processing throughput, or response latency),
-it may affect the client, or both. The
-usefulness of a mechanism depends therefore on the
-computational cost it requires and on where it imposes it, as
-different overheads may be acceptable at the server-side than the client-side.
-What kind of numbers is reported matters as well. Reporting absolute
-measurements gives little information on the actual overhead, unless
-separate measurements are given for the system under study with and
-without the proposed mechanism. Percentage measurements are normally
-better.
-
-Performance evaluation rests on strong foundations~\cite{jain1991} and
-is a vibrant field as new technologies emerge~\cite{gregg2014}.
-Although it may not be necessary to conduct a comprehensive
-performance evaluation analysis for a defense mechanism, the more
-evaluation results are provided for a mechanism, the more valuable
-it becomes as a practical approach.
-
-\subsection{Ease of Use}
-\label{sec:deployment}
-
-The value of a detection mechanism as a practical tool depends on how
-easy it is to deploy it in a production setting. This aspect is
-orthogonal to the
-value of a detection mechanism as a research finding. Devising a
-technique to detect a hitherto undetectable class of attacks may be an
-excellent research contribution that merits publication; it may also
-be heavily cited and open the road to other, practical
-implementations in the future.
-
-Ease of use depends on the deployment process required for the
-mechanism. The detection mechanism may be deployed at either or both
-the server and the client-side. Deployments on just the server or the client are
-easier to handle than deployments on both of them. The mechanism may
-be an add-on or plugin for existing software, client or server, or it
-may be tightly integrated with existing software, requiring rebuilding
-from source code.
-
-No matter where it is installed, the means of installation influences
-ease of use. A detection mechanism that is available as a ready-to-install
-package will trump others that only exist in the form
-of source code.
-
-\subsection{Security}
-
-Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by canny attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by cannier
-attacks, and so on. We use security to refer to the ability of a
-detection mechanism to resist circumvention.
-
-A mechanism that has not been bypassed is not eternally secure, as it
-is possible that a bypass method will be discovered in the future. We
-examine the various approaches based on the knowledge we have so far,
-that is, whether there are any known ways to bypass the detection
-mechanism today.
-
-\subsection{Point of Detection}
-\label{sec:point}
-
-Detection mechanisms vary on the location where they detect an attack.
-There are four different points where an attack can be caught, as seen
-in Figure~\ref{fig:attacks}:
-
-\begin{enumerate}
-\item At the user's browser (Point {\sc ub}).
-\item En route from the server to the user's browser---in most cases
-within a proxy (Point {\sc s}t{\sc b}).
-\item At the database abstraction layer, before it reaches the server's database
-  (Point {\sc dbal}).
-\item After the malicious code reaches the server's database
-  (Point {\sc db}).
-\end{enumerate}
-
-\begin{figure}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.54]{defenses.pdf}
-\end{center}
-\vspace{-5.4mm}
-\caption{\label{fig:defenses}The basic categories of countermeasures
-against web application attacks based on code
-injection. For each approach we provide the references
-that present corresponding mechanisms:
-{\it Policy Enforcement}:~\cite{NSS06,JKK06a,KJKV09,TNH07,RDWDE07,YCIS07,OWVS08,PSC09,ML10,DDHPJ10,PS11,VDDPJ11,BV08,SSM10},
-{\sc isr}:~\cite{BK04,JB07,GC09,APKLM10},
-{\it Parse-Tree Validation}:~\cite{BWS05,SW06},
-{\it Taint Tracking}:~\cite{HCF05,PB05,XBS06,NLC07,VFJKKV07,PMP11,SLMS14},
-{\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
-{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\vspace{-5.6mm}
-\end{figure}
-
-\begin{table*}[t]
-  \renewcommand{\baselinestretch}{1.12}
-    \caption{Comparison summary of mechanisms developed to counter application attacks based on code injection.}
-    \label{tab:comp}
-    \vspace{-4mm}
-\centering
-    \begin{threeparttable}
-    \begin{small}
-\scalebox{0.77}{
-    \begin{tabular}{l|c|c|cc|c}
-    \thickhline
-    \bf{Approach}
-  & \bf{Mechanism}
-  & \bf{\# of Citations}
-  & \multicolumn{2}{c|}{Requirements\tnote{1}}
-  & \bf{Attack}\tnote{4} \\
-  &&& \bf{TP,TN,FP,FN}\tnote{2}
-  & \bf{Performance Overhead}\tnote{3} & \\
-    \thickhline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\sc sqlg}uard~\cite{BWS05} & 305 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
-  &   {\sc sqlc}heck~\cite{SW06} & 473 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
-  \hline
-  \multirow{13}{*}{Policy Enforcement}
-  &   {\sc dsi}~\cite{NSS06} & 168 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   NoForge~\cite{JKK06a} & 151 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
-  &   Noxes~\cite{KJKV09} & 58 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
-  % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\sc beep}~\cite{TNH07} & 335 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
-  &   BrowserShield~\cite{RDWDE07} & 263 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
-  &   CoreScript~\cite{YCIS07} & 199 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 56 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
-  % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   Phung et al.~\cite{PSC09} & 101 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
-  &   ConScript~\cite{ML10} & 152 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   CsFire~\cite{DDHPJ10} & 46 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
-  &   {\sc csp}~\cite{SSM10} & 117 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
-  &   j{\sc csrf}~\cite{PS11} & 4 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   WebJail~\cite{VDDPJ11} & 45 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
-  % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
-  % &   {\it {\sc js}and}~\cite{AVBPDP12} & 22 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & up to 31.2\% & {\sc xss}\\
-  % \hline
-  % \hline 
-  % \multirow{3}{*}{Securing Mashups}
-  % &   {\it {\sc om}ash}~\cite{CHC08} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} & {\sc csrf} \\
-  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & 149 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 1--59\% & {\sc xss} \\
-  \hline
-  \multirow{4}{*}{{\sc isr}}
-  &   {\sc sql}rand~\cite{BK04} & 365 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
-  &   {\sc sm}ask~\cite{JB07} & 28 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
-  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
-  \thickhline
-  \thickhline
-  \multirow{7}{*}{Taint Tracking}
-  &   Haldar et al.~\cite{HCF05} & 208 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc csse}~\cite{PB05} & 347 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
-  % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-  &   Xu et al.~\cite{XBS06} & 346 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc wasc}~\cite{NLC07} & 32 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Vogt et al.~\cite{VFJKKV07} & 400 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\sc php} Aspis~\cite{PMP11} & 20 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
-  &   Stock et al.~\cite{SLMS14} & 15 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
-  \hline 
-  \multirow{6}{*}{Training}
-  &   {\sc didafit}~\cite{LLW02} & 190 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
-  &   {\sc amnesia}~\cite{HO05b} & 474 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
-  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
-  &   {\sc xssds}~\cite{JEP08} & 85 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
-  &   {\sc sd}river~\cite{MS09,MKLS11} & 28 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
-  % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
-  \thickhline
-  \thickhline
-  \multirow{3}{*}{Hybrid}
-  &   {\sc xss-guard}~\cite{BV08} & 132 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
-  &   Blueprint~\cite{LV09} & 152 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
-  \thickhline
-    \end{tabular}}
-    \begin{tablenotes}
-  \begin{footnotesize}
-        \item[1] {\sc na} (Not Available) indicates that a requirement is not mentioned in the paper.
-  {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the\newline publication
-  but is not quantified.
-      \item[2] Tuples contain numbers given for True Positives
-        ({\sc tp}), True Negatives ({\sc tn}), False Positives ({\sc
-          fp}) and False Negatives ({\sc fn}). For every tuple\newline there is a corresponding suffix that indicates whether the testbed was
-  based on: real-world applications known to be vulnerable ({\it r}),
-  synthetic\newline benchmarks ({\it s}), or both ({\it a}).
-  A question mark ({\bf ?}) denotes that no test results are reported.
-    \item[3] Whether the overhead is incurred on the server ({\sc s}) or the client ({\sc c}). 
-    \item[4] {\it i} stands for injection.
-    \item[5] The numbers in this particular case involve requests.
-  \end{footnotesize}
-    \end{tablenotes}
-    \end{small}
-    \end{threeparttable}
-    \vspace{-6mm}
-\end{table*}
-
-\section{Defenses}
-\label{sec:defs}
-
-We categorize and analyze a large set of defenses developed to prevent
-the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
-We perform our analysis across
-the dimensions discussed in the previous section,
-except from availability, which we treat
-separately in Section~\ref{sec:discussion}.
-Due to the immense number of published works in the area, we only consider
-defenses that have been proposed in publications cited more than
-20 times according to Google Scholar.
-We also include some recent works that have been
-presented in top security conferences, even though they have been
-cited less than twenty times, so that recent research is not penalized.
-
-Figure~\ref{fig:defenses} presents a taxonomy of 
-web application defenses against injection attacks.
-We can identify three broad categories:
-{\it etiological}, {\it symptomatic}, and {\it hybrid}.
-The etiological category involves mechanisms designed to
-block attacks based on their causes and origins~\cite{L81}. 
-The symptomatic category incorporates a variety of schemes that
-inspect the behavior of applications and detect attacks based on
-their undesirable symptoms~\cite{D76,A00}.
-Hybrid mechanisms borrow characteristics from both
-categories. Table~\ref{tab:comp} lists the specific mechanisms we consider
-in this work, grouped according to the subcategories shown in
-Figure~\ref{fig:defenses}, and for each mechanism
-provides the following information:
-
-\begin{enumerate}
-\item Number of citations of the corresponding publication(s).
-\item Accuracy and computational overhead measurements.
-\item Types of attacks handled.
-\end{enumerate}
-
-\noindent
-Recall that the point of operation for each mechanism is provided
-in the caption of Figure~\ref{fig:attacks}.
-
-\subsection{Etiological}
-\label{sec:prot}
-
-There are three main categories of etiological approaches used to protect web
-applications against injection attacks:
-\emph{Parse-Tree Validation},
-\emph{Policy Enforcement}, and
-\emph{Instruction Set Randomization} ({\sc isr}).
-
-\subsubsection{Parse-Tree Validation}
-\label{sec:tree}
-
-The key idea behind parse-tree validation is to compare the tree
-representation of the abstract syntactic structure of the code
-that is about to be executed with the one that was originally
-intended. If the trees diverge, the application is probably under
-attack.
-
-For {\sc dsl} code injection attacks, mechanisms check 
-the query before the inclusion of user input with the one
-resulting after the inclusion of user input.
-Two mechanisms that implement this approach for protection
-against {\sc sql} injection attacks,
-{\sc sqlg}uard~\cite{BWS05} and
-{\sc sql}check~\cite{SW06}, are quite similar
-and detect the attack before a query reaches the
-database (Point {\sc dbal}).
-Contrary to {\sc sqlg}uard,
-% mikepo: if others exist, cite them
-%and other mechanisms,
-{\sc sql}check has been
-extensively tested in terms of accuracy,
-as can be seen in Table~\ref{tab:comp}.
-A disadvantage of these mechanisms is that the
-application must be modified in every code fragment
-that sends an {\sc sql} query to the database for execution.
-
-Parse-tree validation is an effective approach
-for the detection of {\sc dsl} code injection attacks,
-especially as implemented in {\sc sql}check.
-This is not however the case
-for mechanisms that borrow elements from
-this approach and examine the syntax trees
-of scripts to detect JavaScript-driven {\sc xss} attacks,
-as we will see in Section~\ref{sec:hybrid}.
-
-\subsubsection{Policy Enforcement}
-\label{sec:policy}
-
-This approach is used to prevent {\sc xss} and {\sc csrf} attacks. When
-using a framework that implements policy enforcement, developers must
-define specific security policies on the server-side. Policies can be
-expressed through JavaScript extensions, pattern matching, or
-syntax-specific settings. The policies are then enforced either in the user's
-browser at runtime, or on a server-side proxy that intercepts server
-responses.
-
-Noxes~\cite{KJKV09} is the only
-framework that partially allows
-users to specify policies for the prevention of {\sc xss} attacks.
-The key idea behind Noxes is to parse
-the {\sc html} response that reaches the browser and
-find static {\sc url} references. Then, based on
-a set of policies, Noxes allows or blocks
-any generated requests (Point {\sc ub}). Such policies
-can also be provided by the server (i.e., ``never
-follow a link that leads to the malicious.com
-web site''). The main issue with Noxes is that
-{\sc url}s can be dynamically assembled by scripts,
-which may lead to false alarms.
-
-Some frameworks define policies based on information and
-features provided by the Document Object Model ({\sc dom}) of a web
-page. Specifically, developers must place all legitimate scripts
-inside {\sc html} elements like {\tt div}. The web browser (Point {\sc
-  ub}) parses the {\sc dom} tree and executes scripts only when they
-are contained in such elements. All other scripts are treated
-according to the policies defined on the server. Frameworks that
-support this functionality include {\sc beep}~\cite{TNH07} and {\sc
-  dsi}~\cite{NSS06}. The main problem with these mechanisms is that
-they do not examine the script's location inside the web document.
-Attackers can take advantage of this fact to perform mimicry attacks~\cite{WS02}.
-Specifically, they can execute legitimate scripts, but not as intended
-by the original design of the developers. This is extensively
-described by Athanasopoulos et al.~\cite{APKLM10}, who also describe
-another recent variation of JavaScript injection attacks, known as
-return-to-JavaScript attacks, which can be used to bypass the above
-mechanisms.
-
-A policy enforcement technique developed by Mozilla,
-called {\sc csp} (Content Security
-Policy)\footnote{\scriptsize\url{https://developer.mozilla.org/en-US/docs/Web/Security/CSP}}~\cite{SSM10}
-is currently supported by many browsers to prevent
-{\sc xss} and {\sc csrf} attacks. To eliminate such
-attacks, web site administrators
-can specify which domains the browser should treat
-as valid sources of script and which not. Then, the browser
-(Point {\sc ub}) will only execute scripts that exist in
-source files from white-listed domains.
-Note that,
-if an application involves
-embedded scripts, developers must utilize
-the {\sc csp}'s {\em nonce} concept.
-This is an unpredictable,
-random value indicated in
-the {\tt script-src} directive which in turn,
-is applied as a nonce attribute to
-{\tt <script>} elements.
-As a result, only those elements that have the
-correct nonce will execute.
-Even if an attacker
-is able to inject markup into the page,
-the attack will be prevented by the attacker's
-inability to guess the nonce value.
-However, attackers may still bypass this feature
-and invoke a script from a non-whitelisted source.
-To do so, their injected code must
-be crafted in a way that the nonce is handled
-by the browser as an attribute of the payload~\cite{jigsaw}.
-
-Another policy enforcement approach introduces
-policies directly either in {\sc html} or JavaScript code
-to confine their behavior. BrowserShield~\cite{RDWDE07}
-acts as a proxy on the server-side (Point {\sc s}t{\sc b}) to
-parse the {\sc html} of server responses and identify
-scripts. Then, it rewrites them into safe equivalents
-and protects the web user from exploits
-that are based on reported browser vulnerabilities.
-ConScript~\cite{ML10}, CoreScript~\cite{YCIS07},
-and the framework by Phung et al.~\cite{PSC09}
-extend JavaScript with new primitive functions that
-provide safe methods to protect potentially vulnerable
-JavaScript functions. In both cases, policy enforcement takes
-place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
-In this way, {\sc xxs} attacks that take advantage
-of functions such as {\tt write} and {\tt eval}, which are
-used to assemble innocuous-looking parts into harmful
-strings,\footnote{\scriptsize The infamous Sammy worm that
-infected MySpace in 2005~\cite{ELX07}
-utilized the {\tt eval} function to assemble a
-malicious script.} would fail.
-
-An issue regarding the above frameworks
-involves features like script inclusion
-and {\tt iframe} tags. Even though they allow developers
-to decide if they will disable them or not,
-this is impractical because such features are quite popular and widely used.
-If developers choose to use them, these frameworks cannot
-define policies that restrict the behavior of third-party
-scripts introduced by such features. Thus, they would
-be vulnerable to attacks that use {\tt iframes}
-in the way described in Section~\ref{sec:attacks}.
-WebJail~\cite{VDDPJ11}, and {\sc soma}~\cite{OWVS08}
-are two frameworks that can actually detect such attacks (Point {\sc
-  ub}). To achieve this, {\sc soma} requires site administrators to
-specify legitimate, external domains for sending or receiving
-information in order to approve interactions between them and the
-protected web site. As a result, {\sc soma} can also detect {\sc csrf}
-attacks. WebJail contains the functionality of third-party scripts by
-introducing a web component integrator that restricts the access that
-these scripts may have to either the data or the functionality of
-other components.
-
-Policy enforcement mechanisms that detect {\sc csrf}
-attacks are usually implemented in the form of a
-server-side proxy (Point {\sc s}t{\sc b})
-interposed at the client-server communication path.
-NoForge~\cite{JKK06a}
-parses the {\sc html} server responses
-and adds a token to every {\sc url} referring to that particular
-server. Then, it associates the token with the cookie
-representing the session {\sc id} for the application.
-When a request is received, the mechanism checks
-if the request contains the token related
-to the session {\sc id}. A disadvantage of NoForge
-is that  dynamically created {\sc html} within
-the browser will not include the token.
-Thus, sites that create part of their {\sc html} code at client-side
-will remain vulnerable. In addition, it does not
-support cross-origin requests.
-The above problems are addressed by j{\sc csrf}~\cite{PS11},
-which shares similar functionality.
-Finally, CsFire~\cite{DDHPJ10}
-examines cross-domain interactions to design a
-cross-domain policy at the client-side (Point {\sc ub}).
-The policy is based on the concept of a relaxed
-same-origin policy that allows communication between
-sub-domains of the same registered domain.
-
-Most of the above frameworks involve
-several deployment hurdles, as they
-require significant source code modifications by the
-developers on the server-side to introduce and enforce
-the applied policies.
-
-\subsubsection{Instruction Set Randomization (ISR)}
-
-{\sc isr} is a method that has been applied to counter different kinds
-of application attacks~\cite{K09b}, and was originally applied for the
-prevention of binary code injection attacks~\cite{KKP03}.
-The main idea behind {\sc isr} is
-to change the representation of code
-based on a randomly chosen transformation,
-and randomizing the execution environment accordingly.
-In this way, any malicious code injected as part of untrusted input data,
-by attackers who do not know the randomization algorithm,
-will not be executed.
-
-{\sc sql}rand~\cite{BK04} applies the concept of {\sc isr} for the prevention
-of {\sc sql} injection attacks. It allows programmers to create {\sc sql}
-statements using randomized instructions instead of standard keywords.
-The modified queries are reconstructed at runtime using the same key
-used for randomization, which is inaccessible to a malicious user.
-{\sc sql}rand is one of the few mechanisms that prevent {\sc sql}
-injection attacks at the database level (Point {\sc db}).
-
-The same concept can be applied for protection against
-{\sc xss} attacks that inject JavaScript or {\sc html} code.
-Initially, the trusted code of a web page can be transformed
-to a random representation using a simple function such as {\sc xor}.
-Before being sent to the client (Point {\sc s}t{\sc b}),
-or being processed by the browser (Point {\sc ub}),
-the legitimate code is transformed back to its original form,
-while any additional injected code will be transformed into junk code.
-Variations of this approach include
-Noncespaces~\cite{GC09} and x{\sc js}~\cite{APKLM10}, which
-randomize the instruction set of {\sc html} and JavaScript,
-respectively. Contrary to x{\sc js}, in Noncespaces administrators
-must set specific policies in a manner similar to a firewall
-configuration language. {\sc sm}ask~\cite{JB07} is another
-framework that was inspired by {\sc isr}. To detect {\sc xss}
-attacks, it searches for {\sc html} and
-JavaScript keywords within the application's legitimate code. This is
-done before the processing of any {\sc http} request. When a keyword is found,
-it adds a token to it, resulting in a ``code mask.'' Then, before
-sending the resulting {\sc html} data to the user, the framework
-searches the data for illegal code using the same keywords (Point
-{\sc s}t{\sc b}). Since all legitimate code has been ``masked,'' the injected
-code can be identified. The need for 
-pre-processing and post-processing the code,
-however, may add a significant overhead to the application.
-Unfortunately, the authors of {\sc sm}ask did not provide measurements
-regarding the runtime overhead of the tool (see
-Table~\ref{tab:comp}).
-
-{\sc isr} is a deterministic approach that can be applied to prevent
-different attacks in an effective manner. However, Sovarel et
-al.~\cite{SEP05} have investigated thoroughly the effectiveness of
-{\sc isr} and showed that a malicious user may be able to circumvent
-it by determining the randomization key. Their results indicate
-that applying {\sc isr} in a way that provides a certain degree of
-security against a motivated attacker is more difficult than
-previously thought. Furthermore, developers who wish to use such
-mechanisms must follow good coding practices and make sure that
-randomized code statements are never leaked
-(e.g., as part of an exception error),
-as this may be used to reveal the encoding key.
-
-Even though the above implementations impose a low computational
-overhead, they require significant deployment effort. In particular,
-{\sc sql}rand~\cite{BK04} requires the integration of
-a proxy within the database
-server, while Noncespaces and x{\sc js}~\cite{APKLM10}
-require modifications on both the server and the client.
-
-\subsection{Symptomatic}
-
-Symptomatic techniques follow two main approaches. They either track
-untrusted input and ban certain operations on it, or they first learn what
-code to trust and then approve for execution code that they recognize
-as safe.
-
-\subsubsection{Taint Tracking}
-\label{sec:taint}
-
-A taint tracking scheme marks untrusted (``tainted'') data, such as
-a variable set by a field in a web form, and traces its propagation
-throughout the program. If the variable is used in an expression that
-sets another variable, that variable is also marked as untrusted and
-so on. If any of these variables is used in a potentially risky
-operation (e.g., sending the data to a vulnerable ``sink,'' such as
-a database, a file, or the network), the scheme may act accordingly.
-
-Taint tracking is provided as a feature in some programming languages,
-such as Perl and Ruby. By enabling this feature, Perl would refuse to
-run code vulnerable to an {\sc sql} injection attack (consider a
-tainted variable being used in a query) and would exit with an error
-message.
-
-There are different implementations of this approach
-in terms of how the tainted data is marked and tracked,
-and how attacks are detected.
-For example, Haldar et al.~\cite{HCF05} have implemented
-their scheme for the Java Virtual Machine ({\sc jvm}),
-where they instrument various classes. When a
-tainted string is used as an argument to a sink method
-an exception is raised (Point {\sc dbal}).
-
-It is possible to apply further checks when it is established that
-tainted data have reached a sink (Point {\sc dbal}).
-Xu et al.~\cite{XBS06} track taint information at the level of bytes in
-memory. To distinguish between legitimate and malicious uses of
-untrusted data that reach a sink, they search the data for suspicious
-symbols using regular expressions. {\sc csse}~\cite{PB05}
-associates tainted data with specific metadata. Such metadata include
-the origins of tainted data, its propagation within the application,
-and others. When tainted data reaches a sink, {\sc csse} performs
-syntactic checks based on its metadata (Point {\sc dbal}).
-{\sc php} Aspis~\cite{PMP11} works in a similar way. To obtain
-metadata, it takes advantage of the  {\sc php} array data structure.
-Finally, {\sc wasc}~\cite{NLC07} analyzes {\sc html} responses to check
-if there is any tainted data that contains scripts (Point {\sc s}t{\sc b}).
-
-A recent study~\cite{NBR14} showed that there are ways to circumvent
-the majority of the above schemes. Furthermore, most of them are not
-easy to deploy since the majority of input vectors, string operations,
-and output vectors of the application must be instrumented.
-
-Vogt et al.~\cite{VFJKKV07} have developed a tainting scheme
-that follows a different approach. In contrast to the above
-schemes, which operate on the server-side, their technique tracks sensitive
-information at the client-side (Point {\sc ub}). This is a form of
-positive data flow tracking, where tagged data is considered to be
-legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
-by ensuring that a script can send sensitive user data only to the
-site from which it came from.
-Stock et al.~\cite{SLMS14} propose a scheme that also operates
-in the browser (Point {\sc ub}). The scheme focuses on the detection of
-{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
-payload is executed as a result of the modification of the {\sc dom}
-environment so that the client-side code runs in an unanticipated
-manner, even if the {\sc http} response that triggers the injection
-seems legitimate. This scheme is different from the previous one
-because it marks and observes data that are considered harmful.
-Specifically, it employs a taint-enhanced JavaScript engine that
-tracks the flow of attacker-controlled data. To detect potential
-attacks, the scheme uses {\sc html} and JavaScript parsers that can
-identify the generation of code coming from tainted data.
-
-An issue that involves all taint tracking schemes involves
-the difficulty of maintaining accurate taints~\cite{GMPS11}
-(e.g. implicit flows~\cite{ME07}).
-In such cases, certain, tainted inputs can escape the tracking mechanism.
-Keeping track of such input maybe impractical not only because of the
-various technical difficulties, but also because it would raise false alarms.
-
-\subsubsection{Training}
-\label{sec:train}
-
-Training techniques are based on the ideas of Denning's original
-intrusion detection framework~\cite{Den87}. In particular, a training
-mechanism learns all valid legitimate code statements during a
-training phase (mostly in the form of signatures). This can be done in
-various ways depending on the implementation. Then, only those
-statements will be recognized and approved for execution during
-production.
-
-Training methods that detect {\sc dsl}-driven injection attacks
-generate and store valid code statements (e.g., {\sc sql} or {\sc
-  xp}ath queries) in various forms, and detect attacks as outliers
-from the set of valid code statements. An early approach,
-{\sc didafit}~\cite{LLW02}, detects {\sc sql} injection attacks (Point
-{\sc dbal}) by recording all database transactions
-stripped from user input. Subsequent
-refinements by Valeur et al.~\cite{VMV05} tag each transaction with
-the corresponding application as an extension of their anomaly
-detection framework called libAnomaly.
-{\sc sd}river~\cite{MS09,MKLS11} is a signature-based mechanism
-that prevents {\sc sql} and {\sc xp}ath injection attacks. The
-signatures generated during a training phase are based on features
-that can depend either on code statements or on their execution
-environment (e.g., the stack trace). Then, at runtime, the mechanism
-checks all statements for compliance and can block code statements
-containing injected elements (Point {\sc dbal}).
-{\sc amnesia}~\cite{HO05b} is a tool that also detects
-{\sc sql} injection attacks (Point {\sc dbal}) by associating a query model
-with the location of every {\sc sql} statement within the application.
-Then, at runtime, it monitors the application's execution to detect
-when {\sc sql} statements diverge from the expected model.
-
-Various countermeasures against {\sc xss} attacks follow a similar
-pattern. {\sc swap}~\cite{WPLKK09} creates a unique identifier
-(script {\sc id}) for every legitimate script on the server.
-Then, a JavaScript detection component placed in a web proxy (Point
-{\sc s}t{\sc b}) searches for injected scripts with no corresponding {\sc id}
-in the server's responses. If no injected scripts are found, the proxy
-forwards the request to the client. This mechanism is relatively
-inflexible since it does not support dynamic scripts. In addition, it
-imposes a significant overhead (see Table~\ref{tab:comp}). The authors
-of {\sc xssds}~\cite{JEP08} have implemented a similar mechanism
-that also supports dynamic and external scripts. Specifically, during the
-training phase, they build a list of all benign scripts. For
-external scripts, they keep a whitelist of all the valid domain names
-that contain scripts used by the application.
-
-Defenses based on training include some mechanisms that can be easily
-circumvented. For example, {\sc didafit}~\cite{LLW02}
-and libAnomaly~\cite{VMV05} do not tag transactions with their
-corresponding call sites. This can lead
-easily to false negatives. For instance, recall the application
-mentioned in Section~\ref{sec:attacks}, which will show the password
-for a forgetful user by executing the following query:
-
-\lstset{language=SQL}
-\begin{lstlisting}
-SELECT password from userdata WHERE id = 'Alice'
-\end{lstlisting}
-
-\noindent
-This same application could allow users to
-login to the site using just their password via a custom login form
-(like the ``Password only login" plugin of
-Wordpress\footnote{\scriptsize\url{wordpress.org/plugins/password-only-login/}})
-%~\cite{password})
-but allow the login either with the user's password or with
-the administrator password. The corresponding query to verify
-the password on the login form would be as follows:
-
-\lstset{language=SQL}
-\begin{lstlisting}
-SELECT password from userdata WHERE id = 'Alice' OR id = 'admin'
-\end{lstlisting}
-
-\noindent
-Even if the application's administrators have chosen to use
-either {\sc didafit}~\cite{LLW02} or
-libAnomaly~\cite{VMV05} as protection,
-an attacker could bypass them and obtain the
-administrator's password via email,
-by entering on the form the standard string:
-{\tt nosuchuser' OR id = 'admin}. The infected query matches the
-signature of the second one above and is therefore accepted.
-The problem lies with the call location of the query, not the query alone.
-
-Mechanisms based on signatures that involve elements not only
-associated with code statements (e.g.,
-{\sc amnesia}~\cite{HO05b} and
-{\sc sd}river~\cite{MS09})
-could detect such attacks. Specifically, {\sc sd}river
-associates a complete stack trace with the root of an {\sc sql}
-statement, thus it can correlate queries with their call sites and
-detect attacks like the above. Furthermore, training
-tools that detect {\sc xss} attacks based on JavaScript injection
-would fail to detect mimicry attacks where legitimate scripts can be
-executed by attackers, but not in the way intended by the
-developers~\cite{APKLM10}.
-
-In general, the detection accuracy of training approaches is heavily
-influenced by the coverage that is achieved during the training phase. If
-the coverage is insufficient false alarms are very likely. In
-addition, when a code statement is altered, a new training phase is
-necessary.
-
-Most of the training approaches are relatively easy to deploy.
-{\sc dsl} injection attack countermeasures
-can be retrofitted to a system typically by changing
-some configuration files (i.e., {\sc sd}river).
-This does not apply to {\sc amnesia}
-though, since significant source code
-modifications are required for every query that exists
-in the application. Finally, {\sc swap} and {\sc xssds}
-are implemented within a proxy on the server-side.
-
-\subsection{Hybrid}
-\label{sec:hybrid}
-
-This category includes mechanisms that borrow
-characteristics from both etiological and symptomatic approaches.
-Two of them focus on the detection of {\sc xss}
-attacks and one focuses on {\sc dsl} code injection attacks.
-
-{\sc xss-guard}~\cite{BV08} is a training scheme that employs
-parse-tree validation. During training, the scheme maps legitimate
-scripts to {\sc http} responses. During production {\sc xss-guard}
-retrieves for every script included in a response its parsed tree and
-checks if it is one of those previously mapped to this response. Apart
-from the comparison of the parsed trees, {\sc xss-guard} checks also
-for an exact match of lexical entities. To achieve this, the scheme
-utilizes that data structures of Firefox's JavaScript engine (Point
-{\sc ub}). However, string literals are not compared literally, which
-can lead to false negatives. For instance, consider a banner rotator
-that every time it runs it creates a value that depends on the
-current date and the length of the array that contains the references
-of the various images to be displayed. Then, based on this value, it
-shows a specific image to a user. In a vulnerable web site that allows
-users to post data and contains this banner rotator, a malicious user
-could create and store a script that has the same code structure, with
-the same JavaScript keywords contained in the rotator script.
-%% PL You mean like the rotator?
-In this script, attackers could also include references to tiny
-images hosted on a web server that is maintained by them in order to
-retrieve the {\sc ip} addresses of the users that visit the vulnerable
-site.
-
-Blueprint~\cite{LV09} is a policy enforcement framework that
-uses parsed trees to detect {\sc xss} attacks. To guarantee
-that untrusted content is not executed, Blueprint generates at the
-server-side a parsed tree from untrusted {\sc html} to ensure that it
-does not contain any dynamic content. Then, the parsed tree is
-transfered to the document generator of the browser (Point {\sc ub}),
-where untrusted browser parsing behavior is ruled out.
-Blueprint is an efficient countermeasure but imposes non-negligible
-overhead due to its extensive parsing (see Table~\ref{tab:comp}).
-
-Diglossia~\cite{SMS13} combines positive taint tracking together
-with parse-tree validation. Diglossia was based on the theory of Ray
-and Ligatti~\cite{RL12b} (which we saw in Section~\ref{sec:attacks})
-to detect {\sc dsl} code injection attacks. In addition, it is
-actually the first, and so far the only framework that detects {\sc
-  json} injection attacks. When an application computes an output
-string (query), Diglossia computes a ``shadow'' of that string.
-Specifically, it maps all characters introduced by the application to
-a shadow character set. This set does not contain any characters
-coming from the tainted input. Then, the scheme creates the tree of
-the query that is about to be executed and compares it with the parsed
-tree of the ``shadow'' (Point {\sc dbal}). If the trees do not match,
-the application is probably under attack. Note that Diglossia
-can be bypassed in the same way as other taint tracking
-approaches~\cite{NBR14}.
-
-\section{Observations}
-\label{sec:discussion}
-
-We group our key observations on the~35 publications that
-we consider in this work along the
-dimensions we identified in Section~\ref{sec:dimensions}.
-
-\subsection{Accuracy}
-
-\begin{figure}[t]
-\begin{center}
-\leavevmode
-\includegraphics[scale=0.39]{barchart.pdf}
-\end{center}
-\vspace{-5.7mm}
-\caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
-used for testing of web attack defenses.
-Specifically, the publications that used a particular source are as follows:
-{\sc cve}~\cite{XBS06,NLC07,PMP11,BK04,BV08,JB07,SMS13,WPLKK09,JKK06a,PS11},
-Bugtraq~\cite{PB05,KJKV09,JEP08},
-{\sc xss}ed.com~\cite{NSS06,APKLM10},
-ha.ckers.org~\cite{TNH07,PSC09,LV09},
-Microsoft~\cite{RDWDE07}.}
-\vspace{-6.3mm}
-\end{figure}
-
-Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
-publications provided a complete tuple of {\sc tp}, {\sc tn}, 
-{\sc fp}, and {\sc fn}. On the other hand, we
-see that 4 out of 35 (11.4\%) were not tested at all.
-In these cases, all four elements of the tuple
-are not available ({\sc na}). An interesting observation is
-that in 10 out of the 35 (28.5\%)
-publications, the evaluation focused on only on attack detection,
-and there was no test focusing on false positives.
-The corresponding tuples contain {\sc tp} and {\sc fn}
-results, but {\sc tn} and {\sc fp} results are not available ({\sc
-  na}). This stresses the fact that authors may be more interested in
-making sure that their mechanisms can detect known attacks rather than
-seeing how they respond under normal conditions. In some cases,
-where the number of {\sc tp} results are not quantified, authors did
-not mention how many or which attacks they performed. Moreover, in some
-cases we observe that even if the authors report the existence of
-possible false positive and negative results, they have not quantified
-them ({\sc nq}).
-
-Even when some numbers are given, they may not be adequate.
-Sensitivity and specificity are statistical measures, and as such,
-they should be interpreted with suitable confidence intervals. There are
-various methods to calculate confidence intervals, even without
-the need to have large sets of samples in order to be able to use the
-central limit theorem~\cite{brown2001}.
-However, sample sizes in the single
-digits are not enough to produce good intervals.
-
-Regarding the subjects of tests,
-we see that 27 out of 35 (77.1\%)
-mechanisms were tested with real-world
-applications known to be vulnerable.
-The vulnerabilities associated with these applications
-are enlisted in the following providers: the Common
-Vulnerabilities and Exposures ({\sc cve})
-database,\footnote{\scriptsize\url{https://cve.mitre.org/}}
-%~\cite{cve},
-the Bugtraq\footnote{\scriptsize\url{http://seclists.org/bugtraq/}}
-security mailing list,
-%~\cite{bugtraq},
-the {\sc xss}ed.com
-security bulletin provider,\footnote{\scriptsize\url{www.xssed.com}}
-%~\cite{xssed},
-Microsoft's security
-bulletin\footnote{\scriptsize\url{https://technet.microsoft.com/en-us/security/bulletin}}
-%~\cite{microsoftBulletin}
-and the
-ha.ckers.org\footnote{\scriptsize\url{http://ha.ckers.org/}}
-security bulletin provider.
-%~\cite{hackers}.
-Figure~\ref{fig:defect_sources},
-presents how many,
-and which, in the figure's caption, publications referred
-to which source.
-In numerous occasions authors performed tests based
-on the same applications.
-For example, 12 mechanisms were tested on a
-vulnerable version of the {\sc phpbb} bulletin board
-software.\footnote{\scriptsize\url{https://www.phpbb.com/}}
-%~\cite{phpbb}.
-
-There are also authors that took a different approach.
-For instance, during their initial tests,
-Stock et al.~\cite{SLMS14} managed to bypass
-the browser-based {\sc xss} filters of
-73\% out of 1,602 real-world {\sc dom}-based {\sc xss} vulnerabilities.
-These vulnerabilities were actually found as part of
-their previous research~\cite{LSJ13}.
-Finally, in the {\sc amnesia}~\cite{HO05b} and
-{\sc sd}river~\cite{MS09} publications,
-the authors managed to break existing application suites
-and then test the accuracy of their tools on them.
-
-\subsection{Availability}
-
-\begin{table}
-\caption{Availability of the studied defenses.}
-\vspace{-4mm}
-    \label{tab:avail}
-\centering
-    \begin{threeparttable}
-    \begin{small}
-\scalebox{0.69}{
-    \begin{tabular}{l|c|ccc}
-    \thickhline
-    \bf{Approach}
-  & \bf{Mechanism}
-  & \multicolumn{3}{c}{Availability\tnote{1}} \\
-  && \bf{Source Code}
-  & \bf{Executable}
-  & \bf{Testbed} \\
-    \thickhline
-  \multirow{2}{*}{Parse-Tree Validation}
-  &   {\sc sqlc}heck~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc sqlg}uard~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
-  \hline
-  \multirow{13}{*}{Policy Enforcement}
-  &   {\sc dsi}~\cite{NSS06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   NoForge~\cite{JKK06a} & {\bf AO} & {\bf AO} & {\sc na} \\
-  &   Noxes~\cite{KJKV09}  & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it {\sc met}}~\cite{ELX07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc beep}~\cite{TNH07} & \tick & \tick & \tick \\
-  &   BrowserShield~\cite{RDWDE07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   CoreScript~\cite{YCIS07} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   {\sc soma}~\cite{OWVS08} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it Barth et al.}~\cite{BJM08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   Phung et al.~\cite{PSC09} & \tick & \tick & \tick \\
-  &   ConScript~\cite{ML10} & {\bf AO} & {\sc na} & {\sc na} \\
-  &   CsFire~\cite{DDHPJ10} & \tick & {\sc na} & {\sc na} \\
-  &   {\sc csp}~\cite{SSM10} & {\bf AO} & {\bf AO} & {\sc na} \\
-  &   j{\sc csrf}~\cite{PS11} & {\sc na} & {\sc na} & {\sc na} \\
-  &   WebJail~\cite{VDDPJ11} & {\sc na} & {\sc na} & {\sc na} \\
-    % &   {\it {\sc js}and}~\cite{AVBPDP12} & {\sc na} & {\sc na} & {\sc na} \\
-  % \hline
-  % \hline 
-  % \multirow{3}{*}{Securing Mashups}
-  % &   {\it {\sc om}ash}~\cite{CHC08} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it Mashup{\sc os}}~\cite{WFHJ07} & {\sc na} & {\sc na} & {\sc na} \\
-  % &   {\it TreeHouse}~\cite{IW12} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \multirow{4}{*}{{\sc isr}}
-  &   {\sc sql}rand~\cite{BK04} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc sm}ask~\cite{JB07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   Noncespaces~\cite{GC09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   x{\sc js}~\cite{APKLM10} & {\sc na} & {\sc na} & {\sc na} \\
-  \thickhline
-  \thickhline
-  \multirow{7}{*}{Taint Tracking}
-  &   Haldar et al.~\cite{HCF05}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc csse}~\cite{PB05} & {\sc na} & {\sc na} & {\sc na} \\
-  &   Xu et al.~\cite{XBS06}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc wasc}~\cite{NLC07} & {\sc na} & {\sc na} & {\sc na} \\
-  &   Vogt et al.~\cite{VFJKKV07}  & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc php} Aspis~\cite{PMP11} & {\bf AO} & {\sc na} & {\bf AO} \\
-  &   Stock et al.~\cite{SLMS14} & {\sc na} & {\sc na} & {\sc na} \\
-  \hline
-  \multirow{6}{*}{Training}
-  &   {\sc didafit}~\cite{LLW02} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc amnesia}~\cite{HO05b} & {\sc na} & {\bf AO} & {\sc na} \\
-  &   libAnomaly~\cite{VMV05} & {\bf ?} & {\bf ?} & {\bf ?} \\
-  &   {\sc xssds}~\cite{JEP08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc swap}~\cite{WPLKK09} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc sd}river~\cite{MS09,MKLS11} & \tick & \tick & {\sc na} \\
-  \thickhline
-  \thickhline
-  \multirow{3}{*}{Hybrid}
-  &   {\sc xss-guard}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
-  &   Blueprint~\cite{LV09} & {\bf ?} & {\bf ?} & {\bf ?} \\
-  &   Diglossia~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
-  \thickhline
-
-    \multicolumn{5}{p{12.4cm}}{%
-       $^\textsuperscript{1}$A check mark (\tick) indicates that the publication
-       includes a link to a page where the software is available.
-       {\bf AO} (Available On-line) indicates
-       that the software is available on-line but the
-       address is not mentioned in the paper, which probably means that
-       the it was made available after the publication. A question 
-       mark ({\bf ?}) indicates that a link to the software
-       was included in the publication but is now inaccessible.} \\
-    \end{tabular}}
-    \end{small}
-    \end{threeparttable}
-    \vspace{-6mm}
-\end{table}
-
-Table~\ref{tab:avail} presents our findings regarding the availability
-of each mechanism in terms of source code and corresponding
-executables. We also examined the availability of the testbeds
-mentioned in each paper. We see that only 6 out of 35 (17.1\%) of the
-publications provided a link to their mechanism and, 2 from these 6
-web pages are currently not available. In 5 cases authors made either
-the source code or their executables available after their paper got
-published. In one case ({\sc csp}~\cite{SSM10}), the source was available before the
-publication through the Mozilla community.
-Regarding the availability of test materials, we see that
-only 3 out of 35 (8.5\%) publications have currently their testbeds
-available.
-
-\subsection{Performance Overhead}
-
-Table~\ref{tab:comp} shows the performance overhead of each mechanism.
-In addition, it indicates if the overhead is incurred at the
-server ({\sc s}) or at the client-side ({\sc c}). In almost half of
-the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
-percentage, while in other cases, 7 our of 35 (20\%), the authors
-provide the latency (in ms) that their mechanisms add to the
-normal execution time of the protected application. Note that in some
-cases, the times of normal executions are not provided,
-so it is not possible to convert absolute
-time measurements to percentage overheads. In 10 cases (28.5\%), the
-overhead was either not available ({\sc na}) or not quantified ({\sc
-  nq}). For {\sc php aspis}~\cite{PMP11}, its authors indicate that with
-their mechanism, the execution time is doubled.
-
-\subsection{Ease of Use}
-\label{sec:deploy2}
-
-Mechanisms in different categories face different deployment issues.
-Consider the majority of mechanisms in the policy enforcement
-subcategory. In most cases, developers should modify multiple
-components to use each mechanism. Specifically, mechanisms like
-BrowserShield~\cite{RDWDE07} and {\sc beep}~\cite{TNH07}
-require modifications both on the server
-and at the client. Thus, it would be difficult to be
-adopted by both browser vendors and application developers. On the
-other hand, there are cases where the policies introduced at the
-server are enforced at the client-side, via a library embedded in the
-server's response (i.e., Blueprint~\cite{LV09}).
-Such an approach is convenient
-as no modifications are needed at the client.
-
-Extensive modifications in the application's source
-code can also be a reason that can make a mechanism
-difficult to use. {\sc sql}rand~\cite{BK04},
-{\sc amnesia}~\cite{HO05b},
-mechanisms of the parse-tree validation
-subcategory, and mechanisms of the taint
-tracking subcategory are such examples.
-In the first three cases, programmers should modify every
-code fragment that involves the execution of a query.
-In the latter case they should also change
-all the code fragments that involve user input handling.
-
-Finally, even though many of the mechanisms that involve
-training are easy to deploy, they have a distinct disadvantage.
-When the application is altered, mechanisms like
-{\sc sd}river~\cite{MS09}
-and {\sc xss-guard}~\cite{BV08} require a new training phase.
-However, with the increased adoption of automated testing
-and continuous integration frameworks, this phase could be
-easily repeated.
-
-\subsection{Security}
-
-In our discussion of the various mechanisms in Section~\ref{sec:defs}, we
-observed that some of them can be bypassed by attackers that know
-the internals of their operation.
-Still, the design of some mechanisms allows them to
-be extended and become immune to the circumvention attacks they are
-currently vulnerable to. For example, policy enforcement frameworks
-based on JavaScript or {\sc html} rewriting can be extended
-to detect attacks that leverage {\tt iframe} tags. This does not apply
-to all mechanisms though. In particular, training mechanisms like {\sc
-  didafit}~\cite{LLW02} and {\sc xss-guard}~\cite{BV08} must be
-redesigned to detect the atacks we described in the related sections.
-
-Taking the attackers' point of view, mimicry attacks can affect a
-range of different mechanisms: they can be used to bypass mechanisms
-in the hybrid category, as well as the policy enforcement and training
-subcategories.
-
-\subsection{Point of Detection}
-
-Given the fact that the final steps of
-{\sc dsl} injection and {\sc csrf} attacks take place
-at the server-side, all mechanisms that detect
-such attacks are placed at some point within the server-side infrastructure.
-From the mechanisms that detect {\sc dsl} code injection
-attacks, 3 out of 13 (23\%) do so at the level
-of the {\sc rdbms} (Point {\sc db}).
-The other 11 are based on interposing on {\sc api} calls related to output
-vectors (Point {\sc dbal}).
-
-For frameworks that deal with {\sc xss} attacks, we
-see that attack prevention may take place either at the server or
-the client-side. In the first case, a proxy is typically placed in front of the server
-to examine the server's responses before they reach a user's 
-browser. In the second case, a modified browser or a library that is
-securely downloaded from the server checks the responses for potential
-attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client-side: in particular, 14 out of 24
-frameworks (58,3\%) detect {\sc xss} attacks at the
-client-side. Note that the majority of the mechanisms that detect
-such attacks on the server can also detect {\sc dsl} code
-injection attacks (6 out of 10).
-
-\section{Recommendations and Lessons Learned}
-\label{sec:lessons-learned}
-
-Our observations lead to some lessons and recommendations that
-developers of new mechanisms may find helpful. In particular,
-our observations
-call for improvements in the accuracy of experimental testing
-and code availability, while
-aiming to reduce performance overheads and deployment hurdles.
-
-\subsection{Improving Testing Accuracy}
-
-One of our key findings indicates that many proposed defenses are
-tested in a poor manner. In many cases, researchers tend to not provide
-results on false positives or false negatives for their mechanisms
-(where applicable).
-Mere discussion on the existence of such results without quantifying
-them also blurs the picture.
-
-A reasonable argument would be that many mechanisms (especially the
-ones coming from the etiological category), do not need to be
-established purely through testing, since they provide systematic
-arguments as to why their design is secure against attacks. In order
-for this to hold, however, their implementation should be flawless
-and precisely follow its specification, which may not
-be the case in practice. Moreover, even mechanisms that detect attacks
-based on their root cause, instead of their observed behavior, may still be
-circumvented by evasive attacks.
-
-When we introduced specificity and sensitivity in
-Section~\ref{ssec:diagnostic-performance}, we deferred discussion of
-\textsc{ppv} and \textsc{npv} to this point. These two relate to the
-effectiveness of a detection mechanism in an actual production setting,
-instead of a testbed. If an attack is detected in a production
-environment, how much should we be worried? The answer is provided by
-\textsc{ppv}. If no attack is detected in a production environment,
-how relaxed should we be that no attack has indeed taken place? The
-answer is provided by \textsc{npv}. We can calculate \textsc{ppv} and
-\textsc{npv} with the following equations:
-
-\vspace{0.5mm}
-\noindent\begin{minipage}{0.5\linewidth}
-\begin{equation}
-\textsc{ppv} = \frac{\textsc{tp}}{\textsc{tp} + \textsc{fp}}
-\end{equation}
-\end{minipage}
-\begin{minipage}{0.5\linewidth}
-\begin{equation}
-\textsc{npv} = \frac{\textsc{tn}}{\textsc{fn} + \textsc{tn}}
-\end{equation}
-\end{minipage}\par\vspace{\belowdisplayskip}
-
-\noindent
-Equations~\ref{eq:ppv-se-sp} and~\ref{eq:npv-se-sp} use true and false
-positives and negatives, like equations~\ref{eq:sensitivity}
-and~\ref{eq:specificity}. However, \textsc{tp}, \textsc{tn},
-\textsc{fp}, and \textsc{fn} are not qualitatively the same in these two cases:
-whereas sensitivity and specificity are measured on a testing
-environment, \textsc{ppv} and \textsc{npv} are measured on a real,
-production environment. In fact, if \textsc{pr} is the probability of
-a particular class of attacks in the real world,
-i.e., its prevalence, then we
-have~\cite{linn2004}:
-
-\begin{equation}
-\textsc{ppv} = \frac{\textsc{se}\times \textsc{pr}}{
-\textsc{se}\times \textsc{pr} + (1 - \textsc{sp})\times (1 -
-\textsc{pr})}
-\label{eq:ppv-se-sp}
-\end{equation}
-
-\begin{equation}
-\textsc{npv} = \frac{\textsc{sp}\times (1 - \textsc{pr})}{
-(1 - \textsc{se})\times \textsc{pr} + \textsc{sp}\times (1 -
-\textsc{pr})}
-\label{eq:npv-se-sp}
-\end{equation}
-
-\noindent
-Prevalence is the prior probability that an event might be an attack,
-based on our understanding of the volume and frequency of a particular
-class of attacks; 
-\textsc{ppv} and \textsc{npv} are the revised estimates of that
-probability based on the results of the detection
-mechanism. The lower the prevalence of an attack,
-the more confident we can be that a negative test result indicates
-that no attack has taken place and the less sure we can be that a
-positive test result indicates a real attack.
-
-Of course it is not easy, and it may not even be possible, to know how
-prevalent an attack class is. Also, attacks against a system may depend on
-factors such as its visibility and popularity, and thus the same
-software may be subject to varying attack intensity depending on
-where it is actually deployed. With this in mind, it may be unfair to
-ask researchers to provide \textsc{ppv} and \textsc{npv} values for
-their mechanisms.
-%---in fact, we observe that nobody does.
-
-This does not mean though that deriving \textsc{ppv} and \textsc{npv} is
-altogether impossible. One could deploy a system armoured with an
-attack detection mechanism on a honeypot to study what happens over
-a time period. This could give an indication about the performance of
-the mechanism in a realistic setting. Alternatively, one could deploy a
-target, unarmoured system, on a honeypot to study the prevalence of
-the class of attacks to be detected. Studying the prevalence of
-classes of attacks is an interesting area of study on its own,
-and could feed directly on the evaluation of attack detection
-mechanisms as practical tools.
-
-Apart from demonstrating the value of a mechanism, good accuracy tests
-may be beneficial per se, leading to more well-designed and robust
-defenses. Mechanisms that can be circumvented were not extensively
-tested in terms of accuracy. For instance, {\sc didafit}~\cite{LLW02}
-was not tested at all and {\sc xss-guard}'s~\cite{BV08}
-testing involved 6 known attacks.
-This also applies to some frameworks coming from the taint tracking
-subcategory. It is possible that more tests during development would
-have led the authors to larger design improvements~\cite{Van14}.
-
-The accuracy of a tool may be related to the scope of the attacks it
-aims to detect. A more limited scope may allow the development of more
-accurate tools. In this vein, the system by Stock et al~\cite{SLMS14}
-is the only one that targets exclusively {\sc dom}-based {\sc xss}
-attacks and detects them in an accurate manner, as seen in
-Table~\ref{tab:comp}. It is also extensively tested with real-world
-attacks.
-
-\subsection{Code Availability}
-
-Apart from testing practices, another area that merits improvement is
-the availability of prototypes and testbeds. We are not aware of
-specific reasons why authors of detection mechanisms seem to be
-wary of publicly releasing their code and tests. Our finding may reflect
-the status in the current point in time, when authors are urged to
-publish their code and tests, and may start, or may have already
-started doing so, but this does not show yet in the research we
-examined, which goes several years back. We also saw instances where
-material was published, but does not seem to be available any more.
-That points to the importance of reproducibility of research materials, 
-an issue arising in all scientific fields. It is not enough to
-publish the underlying code and data, but to make sure that it remains
-accessible, and to provide the means to test it even as technology
-advances and operating systems, file formats, and software libraries
-change. That may be too much to ask right now; what seems reasonable,
-though, is to ask of researchers working on defenses not to
-buck the trend and to take steps to increase the availability of their
-research.
-
-\subsection{Performance Overhead and Deployment Remarks}
-
-Performance overhead comes up as a non-trivial issue. We observe
-that there are some mechanisms that introduce an overhead
-that is more than 10\%. Relative
-research on protection mechanisms~\cite{SPWS13} indicates that
-mechanisms that introduce an overhead larger than 10\% do not tend to
-gain wide adoption in production environments. Hence, the
-computational overhead of some mechanisms could be a reason why they
-have not been adopted.
-
-The deployment difficulties we have found with many mechanisms are not
-a reason not to adopt them, but they may hinder their widespread use.
-Since code injection attacks are complex, it may be logical to
-expect that mechanisms to detect them would be complex too. The effort
-to install and use a tool should be weighed against the expected
-benefits. That is one more reason why it is important to report tool
-accuracy, as this provides an immediate indicator to the expected
-benefits.
-
-The issue is more acute when the point of detection is at the client.
-We saw that many policy enforcement mechanisms that detect attacks at
-the browser are not easy to deploy because modifications are needed
-both on the server and the client-side.
-Conversely, it may be possible to deliver
-the tools to the user unobtrusively; for example, we saw that
-Blueprint~\cite{LV09} enforces policies at the client-side by embedding a library
-in the server's response to the client. In general, when developing a
-new countermeasure, researchers should consider where it
-will detect attacks, observe the corresponding deployment
-challenges, and try to mitigate them.
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-Despite many approaches that have been developed,
-attacks based on code injection against web applications
-have been consistently present for the last 15 years,
-and it appears that they will continue to be.
-Attackers seem to find new ways to introduce
-malicious code to applications using a
-variety of languages and techniques~\cite{HNSHS12,DKH14}.
-Meanwhile, during the last decade, there have been
-numerous mechanisms designed to
-detect one or more of types of such attacks.
-Although some deployed and widely used frameworks, 
-such as {\sc csp}~\cite{SSM10},
-% and
-% Google Caja,\footnote{\scriptsize\url{https://code.google.com/p/google-caja/}}%~\cite{M06},
-share characteristics
-(for instance, {\sc html} sanitization and {\tt eval} handling)
-with previous proposals, 
-most research works are still not used in practice.
-
-In order for a security tool to be used in practice, it must provide
-some value to the user. In particular, the value should outweigh the
-cost of its use. The cost is not necessarily monetary, but may be
-incurred from the time required to use the tool, any inconvenience
-caused, false alarms that may raise, and so on. These costs are related to the
-issues we have been investigating here: poor testing, high overhead,
-lack of publicly available prototypes,
-deployment difficulties, compromised security.
-
-Improving any of these aspects would not just increase the value of a 
-research work as a practical tool, but it would also increase its
-research value as well.
-Accurate detection reporting would help in evaluating different
-approaches. Extensive performance measurements can reveal impractical
-designs and focus effort elsewhere. Availability of source code
-enhances basic scientific tasks like verification and reproducibility. Ease of
-deployment brings ease of experimentation. Secure methods can form the
-basis for developing methods with more extensive coverage.
-
-To the positive side, some defenses have been extensively tested in
-terms of accuracy ({\sc sqlc}heck~\cite{SW06},
-{\sc amnesia}~\cite{HO05b}, libAnomaly~\cite{VMV05}),
-solve specific problems in an effective way
-(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}) or
-have a low computational overhead
-({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
-There are also cases where
-researchers have made their code available ({\sc beep}~\cite{TNH07}
-and {\sc sd}river~\cite{MS09}),
-which can promote the development of better
-mechanisms. This argument has been raised by others
-researchers too~\cite{SPWS13}.
-Furthermore, testing defenses in a production
-setting could also propel their adoption.
-
-We hope that the exploitation model, analysis, and observations that
-emerged from our research can be a reference point for researchers who
-aim to develop new, practical countermeasures against web application
-attacks.
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
 
 \bibliographystyle{IEEEtran}
-\bibliography{questioning}
+\bibliography{comments}
 

### 2016-07-19 docs/paper/questioning.tex
first steps of the revision

--- 2016-03-18 docs/questioning.tex
@@
 following dimensions:
+\vspace{-1.5mm}
 \begin{itemize}
@@
 \end{itemize}
+\vspace{-1.5mm} 
 \noindent
@@
 \end{enumerate}
-\vspace{-0.05mm}
+\vspace{-0.5mm}
 
@@
 \leavevmode
-\includegraphics[scale=0.55]{attack-tree-uml.pdf}
+\includegraphics[scale=0.52]{attack-tree-uml.pdf}
 \end{center}
-\vspace{-5mm}
+\vspace{-6mm}
 \caption{\label{fig:taxonomy}A taxonomy of dynamic and domain-specific
 language code injection attacks against web applications.}
-\vspace{-5mm}
+\vspace{-5.8mm}
 \end{figure}
@@
 such as incorrectly passed parameters or incorrect type handling, are
-called {\sc sql} injection attacks~\cite{MS09,HVO06,SW06}.
+called {\sc sql} injection attacks~\cite{HVO06,SW06}.
 Consider a trivial exploit that takes advantage of incorrectly
@@
 similar techniques, malicious users can mount other exploits based on
-{\sc dsl}s such as {\sc xp}ath~\cite{SW06,CDL07}, {\sc
+{\sc dsl}s such as {\sc xp}ath~\cite{SW06}, {\sc
   xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
@@
 into the application's page. {\sc html} injection is mainly associated
-with {\sc xss} attacks~\cite{SP11, SLMS14}. However, {\sc html} injection
+with {\sc xss} attacks~\cite{SLMS14}. However, {\sc html} injection
 can also be used as a vehicle for Cross-Site Request Forgery
-({\sc csrf}) attacks~\cite{BJM08, LZRL09}
+({\sc csrf}) attacks~\cite{LZRL09}
 (even though a common {\sc csrf} attack does not necessarily
@@
 A recent class of code injection attacks involve dynamic languages
-such as JavaScript and {\sc php}~\cite{SFVM09,SMS13}.
+such as JavaScript and {\sc php}~\cite{SMS13}.
 JavaScript injection attacks make up a large subset of dynamic
@@
 major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
-Cross-Channel Scripting ({\sc xcs}) attacks~\cite{W10,BBB09}.
+Cross-Channel Scripting ({\sc xcs}) attacks~\cite{BBB09}.
 Such attacks are enabled when a web application accepts
@@
 in Figure~\ref{fig:attacks}:
-
+\vspace{-0.5mm}
 \begin{enumerate}
@@
 \end{enumerate}
+\vspace{-0.5mm}
 
@@
 \leavevmode
-\includegraphics[scale=0.54]{defenses.pdf}
+\includegraphics[scale=0.53]{defenses.pdf}
 \end{center}
-\vspace{-5.4mm}
+\vspace{-5.8mm}
 \caption{\label{fig:defenses}The basic categories of countermeasures
@@
 {\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
-\vspace{-5.6mm}
+\vspace{-5.5mm}
 \end{figure}
@@
     \label{tab:comp}
-    \vspace{-4mm}
+    \vspace{-4.5mm}
 \centering
@@
     \begin{small}
-\scalebox{0.77}{
+\scalebox{0.78}{
     \begin{tabular}{l|c|c|cc|c}
@@
     \end{threeparttable}
-    \vspace{-6mm}
+    \vspace{-6.7mm}
 \end{table*}
@@
 
+\vspace{-0.5mm}
 \begin{enumerate}
@@
 \end{enumerate}
-
+\vspace{-0.5mm}
 \noindent
@@
 mechanisms.
+\vspace{-0.5mm}
 
@@
 by the browser as an attribute of the payload~\cite{jigsaw}.
+\vspace{-0.5mm}
 
@@
 in the server's responses. If no injected scripts are found, the proxy
-forwards the request to the client. This mechanism is relatively
+forwards the response to the client. This mechanism is relatively
 inflexible since it does not support dynamic scripts. In addition, it
@@
 approaches~\cite{NBR14}.
+\vspace{-1mm}
 
@@
 \leavevmode
-\includegraphics[scale=0.39]{barchart.pdf}
+\includegraphics[scale=0.40]{barchart.pdf}
 \end{center}
@@
     \end{threeparttable}
-    \vspace{-6mm}
+    \vspace{-6.5mm}
 \end{table}
@@
 
+\section*{Author Biographies}
+\noindent
+{\bf Dimitris Mitropoulos} is a Postdoctoral Researcher
+in the Computer Science Department
+at Columbia University in the City of New York.
+He holds a PhD ('14) in Cyber Security from the
+Athens University of Economics and Business.
+He is an {\sc ieee} member, a member of SysSec,
+and an official writer for the
+{\sc xrds}: Crossroads blog of {\sc acm}.
+His research interests include application security,
+systems security and software engineering.
+
+\noindent
+{\bf Panos Louridas} is an Associate Professor at
+the Athens University of Economics and Business.
+He has published in many areas of software engineering
+and is actively involved in the application of security
+research for the development of high-stakes production
+systems, such as e-voting.
+
+\noindent
+{\bf Michalis Polychronakis} is an Assistant Professor
+at Stony Brook University.
+He received the B.Sc. ('03), M.Sc. ('05), and Ph.D. ('09)
+degrees in Computer Science from the University of Crete, Greece.
+% while working as a research assistant in the Distributed
+% Computing Systems Lab at {\sc forth-ics}.
+Before joining Stony Brook, he was an Associate Research
+Scientist at Columbia University in the City of New York.
+His research interests include
+network and system security and network monitoring and measurement.
+
+\noindent
+{\bf Angelos D. Keromytis} is an Associate Professor
+of Computer Science at Columbia University in the City
+of New York, and the director of the Network Security Lab.
+He is currently serving as  Program Manager with the
+Information Innovation Office ({\sc i}2O) at the Defense Advanced
+Research Projects Agency ({\sc darpa}),
+part of the Department of Defense.
+His research interests are in systems
+and network security,
+and cryptography.
+He is an {\sc acm} Distinguished Scientist since 2012,
+and a founder of Allure Security Technology Inc.
+
 \end{document}

### 2016-07-23 docs/comments/comments.tex
setting up the response

@@
 
-\markboth{Mitropoulos et al.}%
+\markboth{Response to Review Comments.}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
@@
 We are thankful to the reviewers for their thorough reviews.
-We have revised our research paper based on their suggestions and comments.
+We have revised our paper based on their suggestions and comments.
 All additions and changes are highlighted in yellow
@@
 
-{\bf Comment} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.".\\
+{\bf Comment} ``The second and third reviewers have pointed out problems in missing related work and
+descriptions that need to polished. Please address them carefully in the next revision
+for the next round of review."\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
 
@@
 
-{\bf Comment 1:} ``Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum.
-Lorem Ipsum".\\
+{\bf Comment 1:} ``One downside of this work is that it was not clear from the
+description what constitutes a defense against a web application
+attack. The authors do say that vulnerability analysis techniques are
+out-of-bounds (which I agree with), but what about related
+technologies such as Web Application Firewalls? Where does one draw
+the line? What are the criteria to evaluate new techniques to see if
+they fit into your defenses (so that the authors can evaluate using
+your techniques)?"\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+
+\noindent
+{\bf Comment 2:} ``Also, I felt that the focus on studying ``popular" defenses (those with
+greater than 20 citations or published recently) ignores one of the	
+main benefits of a survey paper: to help the community discover
+overlooked yet quality research. I appreciate that surveying the 35
+papers is a good contribution, but I wonder if the results of the
+evaluation would be more impactful (in terms of finding overlooked
+research) if the survey was more inclusive."\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+
+\noindent
+{\bf Comment 3:} ``Some minor comments for the authors:
+\begin{itemize}
+\item Introduction ``didn't" $\rightarrow$ did not
+\item Introduction ``haven't" $\rightarrow$ have not
+\item Section 2: PHP Object Injection vulnerabilities do not have to be
+ ``part of cookies". These could come any user input, not necessarily
+ cookies (similar to other code injection vulnerabilities).
+\item Section 4.5 ``canny attacks" and ``cannier attacker" should probably
+ be ``savvy" or a different word.
+\item Section 5.1.2 it is not clear from your description that the CSP
+ policy is communicated via HTTP header. This may not be clear to
+ those readers that aren't familiar with CSP.
+\item Section 5.1.2 ``XXS" $\rightarrow$ ``XSS".
+\item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
+\end{itemize}
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+
+\section{Reviewer \#2}
+\label{sec:r2}
+
+{\bf Comment 1:} ``Τhe analysis on the accuracy and performance overhead is not reasonable.
+The paper presents metrics that were originally reported in other papers, which were evaluated under different assumptions and settings.
+Simply listing the numbers found in those papers in a table might be misleading.
+However, the reviewer acknowledges that it is very difficult to have access to those systems for a fair comparison, and agrees with the recommendation on improving the availability of the source code and dataset in future research."\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+
+\noindent
+{\bf Comment 2:} ``Admittedly, transition from scientific research to real product
+is challenging due to availability, usability, performance and deployment issues.
+Except for that, the paper does not thorouly discuss why many previous works
+cannot stop attacks against web applications, nor provide useful guidance on
+how future research could improve upon existing works. Are there any fundamental
+limitations in previous works that make them not suitable for defending against
+some specific (if not all) attacks? Can we integrate multiple solutions to build
+stronger defense mechanisms?"\\
 
@@
 \noindent
-{\bf Comment 2:} ``Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+{\bf Comment 3:} ``Some recent works in the (or related) 
+ield are not discussed in this paper.
+For example, information flow control solutions and
+proposals that confine or isolate JavaScript could
+be used to defend against code injection attacks.
+Examples are: {\sc jsf}low: Tracking information
+flow in JavaScript and its {\sc api}s ({\sc sac}'14).
+Protecting users by confining JavaScript with {\sc cowl} ({\sc osdi} '14).
+Runtime monitoring and formal analysis of information fows in Chromium ({\sc ndss} '15)."\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+
+\section{Reviewer \#3}
+\label{sec:r3}
+
+{\bf Comment 1:} ``The biggest omission that I see, however, is that the
+exploitation model does not consider inter-frame attacks, where an attacker
+e.g., lures victims to framed vulnerable sites and performs cross-frame code
+injection.  Granted, this is a relatively newer update to the pantheon of
+web application attacks, but given the rising prevalence of client-side
+web application code it's in my estimation an important one.  And, postMessage
+security research dates back to at least the late 2000s, so it's actually not
+*that* new."\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+
+\noindent
+{\bf Comment 2:} ``Similarly, {\sc xss} is introduced as an attack that has two forms, reflected and
+persistent.  However, even though it's mentioned later on, how would DOM-based
+{\sc xss} fit into this breakdown?  I don't believe it does (neatly), and am of the
+view that it constitutes a third category since it can be performed on-demand
+and purely client-side across frames without persistence, combining aspects of
+both of the above categories."\\
+
+\noindent
+{\bf Response:}
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+
+\noindent
+{\bf Comment 3:} ``Aside from those issues, one could take issue with a lack of coverage of some
+(in my opinion) important approaches that hew towards the
+secure-by-construction ideology. For instance, there is work from the {\sc pl}
+community (e.g., Ur/Web) that makes certain attacks impossible by design.
+There is other {\sc pl} work I didn't see mentioned that also takes a
+secure-by-design approach (e.g., {\sc jif}/{\sc sif}). There is work from the systems
+community focused on {\sc difc} (e.g., Hails, Aeolus).  I anticipate that these
+wouldn't rate highly on the ease-of-use metrics, but it would have been nice
+to see them mentioned.  I did notice that static analyses were specifically
+called out as not being in-scope, but other work that was mentioned does
+require application modification (e.g., {\sc js} confinement).  So, while I'm sure
+there's a line one should draw, it's not clearly defined here and some of the
+above could, in the current presentation, be considered missing."\\
 

### 2016-07-23 docs/paper/questioning.tex
addressed comment 3 of R1

@@
 that we described earlier are out of scope as well. Note also, that we
-didn't consider mechanisms that haven't been presented in research papers.
+did not consider mechanisms that have not been presented in research papers.
 
@@
 in the context of a {\sc php} application through the
-injection of specially crafted objects.
-These objects are injected as part of cookies,
-which, when deserialized
-by the application, result in arbitrary code execution.
+injection of specially crafted objects
+(e.g. as part of cookies).
+When deserialized
+by the application, these objects result in
+arbitrary code execution.
 Note that the exploitation model we propose
@@
 Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by canny attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by cannier
+where countermeasures are bypassed by savvy attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by savvier
 attacks, and so on. We use security to refer to the ability of a
@@
 can specify which domains the browser should treat
-as valid sources of script and which not. Then, the browser
+as valid sources of script and which not.
+These policies are communicated via the {\sc http} header.
+Then, the browser
 (Point {\sc ub}) will only execute scripts that exist in
@@
 place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
-In this way, {\sc xxs} attacks that take advantage
+In this way, {\sc xss} attacks that take advantage
 of functions such as {\tt write} and {\tt eval}, which are
@@
 In such cases, certain, tainted inputs can escape the tracking mechanism.
-Keeping track of such input maybe impractical not only because of the
+Keeping track of such input may be impractical not only because of the
 various technical difficulties, but also because it would raise false alarms.

### 2016-07-25 docs/comments/comments.tex
addressed comment 3 of R1
addressed R1's comment 1, also the updated text in the paper is now in yellow color

@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+Indeed,
+an application firewall is actually a defense
+mechanism that fits in our study.
+Besides,
+in reference~\cite{DPJV06}
+the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
+that we include in our study as
+application firewalls.
+Such mechanisms though,
+can be seen as host-based application firewalls
+which are different from the network-based
+application firewalls.
+Mechanisms coming from the later category
+operate directly at the application
+layer of the protocol stack and
+in most cases they are modules
+of the web server
+(e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
+Even though we do not include such mechanisms
+(note also that {\tt modsecurity} is
+not a research approach),
+they can be analyzed based on our criteria.\\
+% note: I do not know if we must update the text
+% of the paper to address the above comment.
 
@@
 {\bf Comment 3:} ``Some minor comments for the authors:
-\begin{itemize}
-\item Introduction ``didn't" $\rightarrow$ did not
-\item Introduction ``haven't" $\rightarrow$ have not
+\begin{enumerate}
+\item Introduction: ``didn't" $\rightarrow$ did not
+\item Introduction: ``haven't" $\rightarrow$ have not
 \item Section 2: PHP Object Injection vulnerabilities do not have to be
@@
 \item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
-\end{itemize}
+\end{enumerate}
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+We have updated the text accordingly.\\
 

### 2016-07-25 docs/paper/questioning.tex
addressed R1's comment 1, also the updated text in the paper is now in yellow color

--- 2016-07-19 docs/paper/questioning.tex
@@
 
+\usepackage{fixltx2e}
+\usepackage{soul,color}
+\usepackage[dvipsnames]{xcolor}
+
+\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }
+
 \titlespacing*{\section}
@@
 that we described earlier are out of scope as well. Note also, that we
-didn't consider mechanisms that haven't been presented in research papers.
+\hlc[yellow]{did not} consider mechanisms that
+\hlc[yellow]{have not} been presented in research papers.
 
@@
 
-A recent attack called {\sc php} Object Injection
-({\sc poi})~\cite{DKH14} does not directly involve
+\hlc[yellow]{A recent attack called {\sc php} Object Injection
+({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
 the injection of code, but still achieves arbitrary code execution
 in the context of a {\sc php} application through the
-injection of specially crafted objects.
-These objects are injected as part of cookies,
-which, when deserialized
-by the application, result in arbitrary code execution.
+injection of specially crafted objects
+(e.g. as part of cookies).
+When deserialized
+by the application, these objects result in
+arbitrary code execution.}
 Note that the exploitation model we propose
@@
 Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by canny attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by cannier
+where countermeasures are bypassed by \hlc[yellow]{savvy} attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by \hlc[yellow]{savvier}
 attacks, and so on. We use security to refer to the ability of a
@@
 can specify which domains the browser should treat
-as valid sources of script and which not. Then, the browser
+as valid sources of script and which not.
+\hlc[yellow]{These policies are communicated via the {\sc http} header.}
+Then, the browser
 (Point {\sc ub}) will only execute scripts that exist in
@@
 place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
-In this way, {\sc xxs} attacks that take advantage
+In this way, \hlc[yellow]{{\sc xss}} attacks that take advantage
 of functions such as {\tt write} and {\tt eval}, which are
@@
 In such cases, certain, tainted inputs can escape the tracking mechanism.
-Keeping track of such input maybe impractical not only because of the
+Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
 various technical difficulties, but also because it would raise false alarms.

### 2016-07-25 docs/comments/comments.tex
minor changes

@@
 
-{\bf Comment} ``The second and third reviewers have pointed out problems in missing related work and
-descriptions that need to polished. Please address them carefully in the next revision
+{\bf Comment} ``The second and third reviewers
+have pointed out problems in missing related work and
+descriptions that need to polished.
+Please address them carefully in the next revision
 for the next round of review."\\
@@
 \noindent
-{\bf Comment 2:} ``Also, I felt that the focus on studying ``popular" defenses (those with
+{\bf Comment 2:} ``Also, I felt that the focus on
+studying ``popular" defenses (those with
 greater than 20 citations or published recently) ignores one of the	
@@
 
-{\bf Comment 1:} ``Τhe analysis on the accuracy and performance overhead is not reasonable.
-The paper presents metrics that were originally reported in other papers, which were evaluated under different assumptions and settings.
-Simply listing the numbers found in those papers in a table might be misleading.
-However, the reviewer acknowledges that it is very difficult to have access to those systems for a fair comparison, and agrees with the recommendation on improving the availability of the source code and dataset in future research."\\
+{\bf Comment 1:} ``The analysis on the accuracy
+and performance overhead is not reasonable.
+The paper presents metrics that were originally
+reported in other papers,
+which were evaluated under different
+assumptions and settings.
+Simply listing the numbers found in those papers
+in a table might be misleading.
+However,
+the reviewer acknowledges that it is very
+difficult to have access to those systems for a fair comparison,
+and agrees with the recommendation on improving
+the availability of the source code and dataset
+in future research."\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum.\\
 
 \noindent
-{\bf Comment 2:} ``Admittedly, transition from scientific research to real product
-is challenging due to availability, usability, performance and deployment issues.
-Except for that, the paper does not thorouly discuss why many previous works
-cannot stop attacks against web applications, nor provide useful guidance on
-how future research could improve upon existing works. Are there any fundamental
-limitations in previous works that make them not suitable for defending against
-some specific (if not all) attacks? Can we integrate multiple solutions to build
+{\bf Comment 2:} ``Admittedly, transition
+from scientific research to real product
+is challenging due to availability, usability,
+performance and deployment issues.
+Except for that, the paper does not thorouly
+discuss why many previous works
+cannot stop attacks against web applications,
+nor provide useful guidance on
+how future research could improve upon existing works.
+Are there any fundamental
+limitations in previous works that make
+them not suitable for defending against
+some specific (if not all) attacks?
+Can we integrate multiple solutions to build
 stronger defense mechanisms?"\\
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum".\\
 
@@
 Protecting users by confining JavaScript with {\sc cowl} ({\sc osdi} '14).
-Runtime monitoring and formal analysis of information fows in Chromium ({\sc ndss} '15)."\\
+Runtime monitoring and formal analysis of information
+fows in Chromium ({\sc ndss} '15)."\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum.\\
 
@@
 
-{\bf Comment 1:} ``The biggest omission that I see, however, is that the
-exploitation model does not consider inter-frame attacks, where an attacker
-e.g., lures victims to framed vulnerable sites and performs cross-frame code
-injection.  Granted, this is a relatively newer update to the pantheon of
-web application attacks, but given the rising prevalence of client-side
-web application code it's in my estimation an important one.  And, postMessage
-security research dates back to at least the late 2000s, so it's actually not
-*that* new."\\
+{\bf Comment 1:} ``The biggest omission that I see,
+however,
+is that the exploitation model does not consider
+inter-frame attacks, where an attacker
+e.g., lures victims to framed vulnerable
+sites and performs cross-frame code
+injection.  Granted, this is a relatively
+newer update to the pantheon of
+web application attacks, but given the rising
+prevalence of client-side
+web application code it's in my
+estimation an important one. 
+And,
+postMessage
+security research dates back to at least the late 2000s,
+so it's actually not *that* new."\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum".\\
 
 \noindent
-{\bf Comment 2:} ``Similarly, {\sc xss} is introduced as an attack that has two forms, reflected and
-persistent.  However, even though it's mentioned later on, how would DOM-based
-{\sc xss} fit into this breakdown?  I don't believe it does (neatly), and am of the
-view that it constitutes a third category since it can be performed on-demand
-and purely client-side across frames without persistence, combining aspects of
-both of the above categories."\\
+{\bf Comment 2:} ``Similarly, {\sc xss} is introduced
+as an attack that has two forms,
+reflected and persistent.
+However,
+even though it's mentioned later on,
+how would {\sc dom}-based {\sc xss} fit into this breakdown?
+I don't believe it does (neatly),
+and am of the view that it constitutes a third
+category since it can be performed on-demand
+and purely client-side across frames without persistence,
+combining aspects of both of the above categories."\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum".\\
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
+Lorem Ipsum. Lorem Ipsum".\\
 
 \noindent
-{\bf Comment 3:} ``Aside from those issues, one could take issue with a lack of coverage of some
+{\bf Comment 3:} ``Aside from those issues,
+one could take issue with a lack of coverage of some
 (in my opinion) important approaches that hew towards the
-secure-by-construction ideology. For instance, there is work from the {\sc pl}
-community (e.g., Ur/Web) that makes certain attacks impossible by design.
-There is other {\sc pl} work I didn't see mentioned that also takes a
-secure-by-design approach (e.g., {\sc jif}/{\sc sif}). There is work from the systems
-community focused on {\sc difc} (e.g., Hails, Aeolus).  I anticipate that these
-wouldn't rate highly on the ease-of-use metrics, but it would have been nice
-to see them mentioned.  I did notice that static analyses were specifically
-called out as not being in-scope, but other work that was mentioned does
-require application modification (e.g., {\sc js} confinement).  So, while I'm sure
-there's a line one should draw, it's not clearly defined here and some of the
-above could, in the current presentation, be considered missing."\\
+secure-by-construction ideology.
+For instance,
+there is work from the {\sc pl} community (e.g., Ur/Web)
+that makes certain attacks impossible by design.
+There is other {\sc pl} work I didn't
+see mentioned that also takes a
+secure-by-design approach (e.g., {\sc jif}/{\sc sif}).
+There is work from the systems
+community focused on {\sc difc} (e.g., Hails, Aeolus).
+I anticipate that these
+wouldn't rate highly on the ease-of-use metrics,
+but it would have been nice to see them mentioned.
+I did notice that static analyses were specifically
+called out as not being in-scope,
+but other work that was mentioned does
+require application modification (e.g., {\sc js} confinement).
+So, while I'm sure there's a line one should draw,
+it's not clearly defined here and some of the
+above could, in the current presentation,
+be considered missing."\\
 

### 2016-07-26 docs/comments/comments.tex
some notes on R2's 1st comment

@@
 \usepackage{titlesec}
-
-\titlespacing*{\section}
-{0pt}{1ex}{0.55ex}
-\titlespacing*{\subsection}
-{0pt}{1ex}{0.55ex}
-\titlespacing*{\subsubsection}
-{0pt}{1ex}{0.55ex}
-
-\setlength{\footnotesep}{0.28cm}
-\setlength{\skip\footins}{0.1cm}
 
@@
 \item Introduction: ``haven't" $\rightarrow$ have not
-\item Section 2: PHP Object Injection vulnerabilities do not have to be
+\item Section 2: {\sc php} Object Injection vulnerabilities do not have to be
  ``part of cookies". These could come any user input, not necessarily
@@
  be ``savvy" or a different word.
-\item Section 5.1.2 it is not clear from your description that the CSP
- policy is communicated via HTTP header. This may not be clear to
- those readers that aren't familiar with CSP.
-\item Section 5.1.2 ``XXS" $\rightarrow$ ``XSS".
+\item Section 5.1.2 it is not clear from your description that the {\sc csp}
+ policy is communicated via {\sc http} header. This may not be clear to
+ those readers that aren't familiar with {\sc csp}.
+\item Section 5.1.2 ``{\sc xxs}" $\rightarrow$ ``{\sc xss}".
 \item Section 5.2.1 ``maybe" $\rightarrow$ ``may be"".
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum.\\
+Initial note:
+This is an interesting comment.
+We need to mention that we did not intend to
+compare the mechanisms with each other.
+Our intention was to highlight that currently there
+are many different testing setups and
+environments for defenses that counter
+similar attacks (see Subsection 6.1).\\
 
@@
 {\bf Comment 3:} ``Some recent works in the (or related) 
-ield are not discussed in this paper.
+field are not discussed in this paper.
 For example, information flow control solutions and

### 2016-07-29 docs/comments/comments.tex
added IFC mechanisms and frameworks to address the 3rd comment of R2 and R3 respectively
As a result, the Observations section, Figure 2 and Figure 3 were
updated too.

@@
 and that provides a common perspective for studying the available defenses.
-We then categorize and analyze a set of 35 previously proposed defenses 
+We then categorize and analyze a set of 41 previously proposed defenses 
 based on their accuracy, performance,
@@
 \noindent
+Second note:
+We also changed the caption of Table 1.\\
+
+\noindent
 {\bf Comment 2:} ``Admittedly, transition
@@
 performance and deployment issues.
-Except for that, the paper does not thorouly
+Except for that, the paper does not thoroughly
 discuss why many previous works
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum.\\
+We have updated our paper to include the
+aforementioned mechanisms
+(see Subsection 5.3, Figure 2 and 3).
+The 3rd reviewer also
+indicated that some representative
+{\sc ifc} frameworks were missing.
+Hence, we have added those too.
+Note that,
+those mechanisms are not
+always easy to adopt because
+developers need to learn new constructs
+to utilize them.
+We mention that in Subsection 6.4
+(``Ease of Use").
+Finally,
+the addition of {\sc ifc} mechanisms
+in our study affects many of our results
+throughout Section 6 (``Observations").
+Consequently,
+we have updated this section too.\\
 
@@
 I don't believe it does (neatly),
-and am of the view that it constitutes a third
+and I am of the view that it constitutes a third
 category since it can be performed on-demand
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum".\\
+The 2nd reviewer has also indicated that
+information flow control solutions
+were missing from our study.
+Our paper now includes six solutions
+that follow this approach
+including {\sc sif}~\cite{CVMA07},
+Hails~\cite{GLSTMMR12}
+and Aeolus~\cite{CPSPBCCSL12}
+(see Subsection 5.3, Figure 2 and 3).
+Nevertheless,
+we did not include Ur/Web~\cite{C10b}
+in our study because it is a static 
+analysis mechanism
+(recall that we only consider defenses
+that prevent attacks when they take place).
+
+Note that,
+most of these mechanisms were not
+extensively tested in terms of security.
+However,
+such solutions do not need to be
+established purely through testing,
+since they provide systematic
+arguments as to why their design is
+secure against application attacks.
+We stress this issue in Subsection
+7.1 (``Improving Testing Accuracy").
+Furthermore,
+we discuss the usability issues of
+{\sc ifc} solutions in Subsection 6.4
+(``Ease of Use").
+
+As we pointed out in our
+response to the 2nd reviewer,
+the addition of {\sc ifc} mechanisms
+in our paper affects many of our results
+throughout Section 6 (``Observations").
+Consequently,
+we have updated this section too.\\
 

### 2016-07-29 docs/paper/questioning.tex
added IFC mechanisms and frameworks to address the 3rd comment of R2 and R3 respectively
As a result, the Observations section, Figure 2 and Figure 3 were
updated too.

@@
 and that provides a common perspective for studying the available defenses.
-We then categorize and analyze a set of 35 previously proposed defenses 
+We then categorize and analyze a set of \hlc[yellow]{41} previously proposed defenses 
 based on their accuracy, performance,
@@
 detect or prevent attacks are marked with an `X' symbol:
-(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10},
+(1) {\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,
+PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08,SSM10,HBBS14,SYMRHKM14,BCJPST15,GLSTMMR12},
 (2) {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
 (3) {\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05b,SMS13},
-(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
+(4) {\sc db} (at the database):~\cite{BK04,LLW02,VMV05,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
 \vspace{-6mm}
@@
 {\it Training}:~\cite{LLW02,HO05b,VMV05,JEP08,WPLKK09,MS09,MKLS11},
-{\it Hybrid}:~\cite{BV08,LV09,SMS13}.}
+{\it Hybrid}:~\cite{BV08,LV09,SMS13,HBBS14,SYMRHKM14,BCJPST15,CVMA07,GLSTMMR12,CPSPBCCSL12}.}
 \vspace{-5.5mm}
@@
   \renewcommand{\baselinestretch}{1.12}
-    \caption{Comparison summary of mechanisms developed to counter application attacks based on code injection.}
+    \caption{\hlc[yellow]{Summary of mechanisms developed to counter application
+    attacks based on code injection. The different results does not necessarily
+    % \newline
+    % \hspace{\linewidth}
+    indicate that one mechanism is more effective than the other.
+    This is because most of them were evaluated under different assumptions
+    and settings.}}
     \label{tab:comp}
-    \vspace{-4.5mm}
+    \vspace{-5.2mm}
 \centering
@@
     \begin{small}
-\scalebox{0.78}{
+\scalebox{0.76}{
     \begin{tabular}{l|c|c|cc|c}
@@
   &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
-  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40{\it ms} ({\sc c}) & {\sc xss} \\
+  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40ms ({\sc c}) & {\sc xss} \\
   \thickhline
@@
   &   {\sc amnesia}~\cite{HO05b} & 474 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
-  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1{\it ms} per query ({\sc s}) & {\sc sql}i \\
+  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1ms per query ({\sc s}) & {\sc sql}i \\
   &   {\sc xssds}~\cite{JEP08} & 85 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261 {\it ms} ({\sc s}) & {\sc xss} \\ 
+  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261ms ({\sc s}) & {\sc xss} \\ 
   &   {\sc sd}river~\cite{MS09,MKLS11} & 28 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
@@
   \thickhline
-  \multirow{3}{*}{Hybrid}
+  \multirow{9}{*}{Hybrid}
   &   {\sc xss-guard}~\cite{BV08} & 132 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
@@
   &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{62} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
+  & \hlc[yellow]{2$\times$ ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
+  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} & \hlc[yellow]{27} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
+  & \hlc[yellow]{16\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
+  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} & \hlc[yellow]{5} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
+  & \hlc[yellow]{average 55\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
+  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{146} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
+  & \hlc[yellow]{26\% ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
+  % &   \hlc[yellow]{Ur/Web}~\cite{C10b} & \hlc[yellow]{59} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s}
+  % & \hlc[yellow]{average 55\% ({\sc s})} & \hlc[yellow]{{\sc sql}i} \\
+  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} & \hlc[yellow]{78} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
+  & \hlc[yellow]{28\% ({\sc s},{\sc c})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
+  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} & \hlc[yellow]{52} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
+  & \hlc[yellow]{323.5ms per request ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
   \thickhline
     \end{tabular}}
+    \vspace{-0.5mm}
     \begin{tablenotes}
-  \begin{footnotesize}
+  \begin{tiny}
         \item[1] {\sc na} (Not Available) indicates that a requirement is not mentioned in the paper.
-  {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the\newline publication
+  {\sc nq} (Not Quantified) indicates that a requirement is mentioned in the publication
   but is not quantified.
@@
   based on: real-world applications known to be vulnerable ({\it r}),
-  synthetic\newline benchmarks ({\it s}), or both ({\it a}).
+  synthetic benchmarks ({\it s}), or both ({\it a}).
   A question mark ({\bf ?}) denotes that no test results are reported.
@@
     \item[4] {\it i} stands for injection.
+    \vspace{-1.8mm}
     \item[5] The numbers in this particular case involve requests.
-  \end{footnotesize}
+  \end{tiny}
     \end{tablenotes}
@@
 characteristics from both etiological and symptomatic approaches.
-Two of them focus on the detection of {\sc xss}
+\hlc[yellow]{Five} of them focus on the detection of {\sc xss}
 attacks and one focuses on {\sc dsl} code injection attacks.
@@
 approaches~\cite{NBR14}.
+
+\hlc[yellow]{Information Flow Control ({\sc ifc})
+mechanisms combine positive taint tracking and
+policy enforcement to prevent {\sc xss} attacks on the
+client-side (Point {\sc ub}).
+Representative implementations such as
+{\sc jsf}low}~\cite{HBBS14}\hlc[yellow]{, {\sc cowl}}~\cite{SYMRHKM14}
+\hlc[yellow]{and the framework by Bauer et al.}~\cite{BCJPST15}
+\hlc[yellow]{allow developers to express information flow
+policies be extending the type system of JavaScript.
+Then,
+the policies are enforced by the JavaScript interpreter
+through dynamic checks.}
+\hlc[yellow]{{\sc ifc} frameworks do not
+focus explicitly on JavaScript and they
+have a broader scope.
+They can be used to build secure
+distributed applications,
+thus preventing different attacks,
+including {\sc xss} and {\sc dsl}-driven
+code injection.
+Such frameworks include {\sc sif}
+(Servlet Information Flow)}~\cite{CVMA07}\hlc[yellow]{,
+% Ur/Web}~\cite{C10b}\hlc[yellow]{,
+Hails}~\cite{GLSTMMR12}
+\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}\hlc[yellow]{.
+Policies can be provided either as compile-time
+program annotations,
+or as run-time requirements defined by the user.}
+
 \vspace{-1mm}
@@
 
-We group our key observations on the~35 publications that
+We group our key observations on the \hlc[yellow]{41} publications that
 we consider in this work along the
@@
 
-Table~\ref{tab:comp} indicates that the authors of 3 out of 35 (8.5\%)
+Table~\ref{tab:comp} indicates that the authors of 3 out of \hlc[yellow]{41 (7.3\%)}
 publications provided a complete tuple of {\sc tp}, {\sc tn}, 
 {\sc fp}, and {\sc fn}. On the other hand, we
-see that 4 out of 35 (11.4\%) were not tested at all.
+see that \hlc[yellow]{7} out of \hlc[yellow]{41 (17\%)} were not tested at all.
 In these cases, all four elements of the tuple
 are not available ({\sc na}). An interesting observation is
-that in 10 out of the 35 (28.5\%)
+that in 10 out of the \hlc[yellow]{41 (24.3\%)}
 publications, the evaluation focused on only on attack detection,
@@
 Regarding the subjects of tests,
-we see that 27 out of 35 (77.1\%)
+we see that \hlc[yellow]{30} out of \hlc[yellow]{41 (73.1\%)}
 mechanisms were tested with real-world
@@
   \thickhline
-  \multirow{3}{*}{Hybrid}
+  \multirow{9}{*}{Hybrid}
   &   {\sc xss-guard}~\cite{BV08} & {\sc na} & {\sc na} & {\sc na} \\
@@
   &   Diglossia~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
+  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\
+  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
+  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
+  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
+  % &   \hlc[yellow]{Ur/Web}~\cite{C10b} & \hlc[yellow]{59} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s}
+  % & \hlc[yellow]{average 55\% ({\sc s})} & \hlc[yellow]{{\sc sql}i} \\
+  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} &  \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\bf AO}} \\
+  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} &  \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\
   \thickhline
@@
 executables. We also examined the availability of the testbeds
-mentioned in each paper. We see that only 6 out of 35 (17.1\%) of the
+mentioned in each paper. We see that only \hlc[yellow]{8} out of \hlc[yellow]{41 (19.5\%)} of the
 publications provided a link to their mechanism and, 2 from these 6
-web pages are currently not available. In 5 cases authors made either
+web pages are currently not available. In \hlc[yellow]{7} cases authors made either
 the source code or their executables available after their paper got
@@
 Regarding the availability of test materials, we see that
-only 3 out of 35 (8.5\%) publications have currently their testbeds
+only \hlc[yellow]{4} out of \hlc[yellow]{41 (9.7\%)} publications have currently their testbeds
 available.
@@
 server ({\sc s}) or at the client-side ({\sc c}). In almost half of
-the approaches, 16 out of 35 (45.7\%), the overhead is provided as a
-percentage, while in other cases, 7 our of 35 (20\%), the authors
+the approaches, \hlc[yellow]{20} out of \hlc[yellow]{41 (48.7\%)}, the overhead is provided as a
+percentage, while in other cases, \hlc[yellow]{8} our of \hlc[yellow]{41 (19.5\%)}, the authors
 provide the latency (in ms) that their mechanisms add to the
@@
 so it is not possible to convert absolute
-time measurements to percentage overheads. In 10 cases (28.5\%), the
-overhead was either not available ({\sc na}) or not quantified ({\sc
-  nq}). For {\sc php aspis}~\cite{PMP11}, its authors indicate that with
-their mechanism, the execution time is doubled.
+time measurements to percentage overheads. In 10 cases (\hlc[yellow]{24.3\%}), the
+overhead was either not available ({\sc na})
+or not quantified ({\sc nq}).
+\hlc[yellow]{For \textsc{php} Aspis}~\cite{PMP11}
+\hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
+\hlc[yellow]{, the authors indicate that with
+their mechanisms, the execution time is doubled.}
 
@@
 
+\hlc[yellow]{
+By design,
+{\sc ifc} frameworks provide
+limited support for securing legacy applications
+and they are not always easy to adopt
+because developers need to learn new constructs
+to use them.
+However,
+there are attempts to overcome such issues.
+For instance,
+the authors of
+Aeolus}~\cite{CPSPBCCSL12}
+\hlc[yellow]{provide a simple security model
+that tries to match the way programmers understand
+authorization and access control
+with the tracking of the information flow.}
+
 Finally, even though many of the mechanisms that involve
@@
 From the mechanisms that detect {\sc dsl} code injection
-attacks, 3 out of 13 (23\%) do so at the level
+attacks, 3 out of \hlc[yellow]{16 (18.7\%)} do so at the level
 of the {\sc rdbms} (Point {\sc db}).
-The other 11 are based on interposing on {\sc api} calls related to output
+The other \hlc[yellow]{13} are based on interposing on {\sc api} calls related to output
 vectors (Point {\sc dbal}).
@@
 attacks. We find that the tendency so far is to create frameworks that
-perform detection on the client-side: in particular, 14 out of 24
-frameworks (58,3\%) detect {\sc xss} attacks at the
+perform detection on the client-side: in particular,
+\hlc[yellow]{18} out of \hlc[yellow]{30}
+frameworks (\hlc[yellow]{60\%}) detect {\sc xss} attacks at the
 client-side. Note that the majority of the mechanisms that detect
 such attacks on the server can also detect {\sc dsl} code
-injection attacks (6 out of 10).
+injection attacks (\hlc[yellow]{9 out of 13}).
 
@@
 
-A reasonable argument would be that many mechanisms (especially the
-ones coming from the etiological category), do not need to be
+\hlc[yellow]{A reasonable argument would be that many mechanisms
+(e.g. many mechanisms coming from the etiological category,
+or the {\sc ifc} frameworks), do not need to be
 established purely through testing, since they provide systematic
-arguments as to why their design is secure against attacks. In order
-for this to hold, however, their implementation should be flawless
+arguments as to why their design is secure against attacks.
+In order for this to hold,
+however, their implementation should be flawless
 and precisely follow its specification, which may not
@@
 based on their root cause, instead of their observed behavior, may still be
-circumvented by evasive attacks.
+circumvented by evasive attacks.}
 

### 2016-07-29 docs/comments/comments.tex
work on comments 1 and 2 of R3, 2 of R1 and 1 of R2

@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+This is a valid comment.
+However,
+in order to avoid penalizing recent research,
+we have also included recent papers
+even though they have been cited less than twenty times.
+
+In addition,
+to address the comments of the 2nd and the 3rd reviewer,
+we have included six more mechanisms,
+thus making our study more extended.
+Notably,
+one of the mechanisms is presented in a recent
+paper with less than 20 citations.
+This increases the number of such papers
+incorporated in our study (6).\\
 
@@
 {\bf Response:}
-Initial note:
 This is an interesting comment.
 We need to mention that we did not intend to
-compare the mechanisms with each other.
-Our intention was to highlight that currently there
+compare the mechanisms with each other
+but to highlight factors that may hinder
+the widespread deployment of protection mechanisms
+(we state this early on in the
+``Introduction" section).
+
+Indeed,
+the caption of Table 1 actually
+started with the phrase ``comparison summary"
+which is misleading.
+To avoid any further misunderstandings
+we have changed the caption of Table 1
+to make clear that there
 are many different testing setups and
@@
 similar attacks (see Subsection 6.1).\\
-
-\noindent
-Second note:
-We also changed the caption of Table 1.\\
 
@@
 Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum".\\
+Lorem Ipsum. Lorem Ipsum.\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum".\\
+Indeed,
+Cross Frame Scripting (\textsc{xfs}) attacks
+are comprise a novel category worth mentioning.
+We now refer to \textsc{xfs} attacks
+at the end of Section 3 (``Exploitation Model").
+We also provide a corresponding example.\\
 
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum".\\
+We have updated Section 3 (``Exploitation Model")
+to include {\sc dom}-based {\sc xss} attacks
+as a the third basic category of {\sc xss}
+attacks.\\
 

### 2016-07-29 docs/paper/questioning.tex
work on comments 1 and 2 of R3, 2 of R1 and 1 of R2

@@
 
-Cross-site scripting attacks fall into two categories, {\it non-persistent}
-(also known as \emph{reflected}) {\sc xss}
-and {\it persistent} (also known as \emph{stored}) {\sc xss}.
+Cross-site scripting
+attacks fall into \hlc[yellow]{three} categories,
+{\it non-persistent}
+(also known as \emph{reflected}) {\sc xss},
+{\it persistent} (also known as \emph{stored}) {\sc xss}
+\hlc[yellow]{and {\sc dom}\textit{-based} \textsc{xss}.}
 Non-persistent {\sc xss} attacks take place when the
@@
 eventually sent to the user as part of a future response.
+\hlc[yellow]{In a {\sc dom}-based {\sc xss} attack,
+the malicious payload is executed as a result of
+the modification of the {\sc dom}
+environment so that the client-side code runs
+in an unanticipated manner,
+even if the {\sc http} response that
+triggers the injection seems legitimate.
+Notably,
+a {\sc dom}-based {\sc xss} attack
+can follow a path of either a persistent {\sc xss}
+attack or a non-persistent {\sc xss} attack.
+Also,
+it can be performed on-demand and purely client-side
+across frames.}
 
@@
 towards the site that is vulnerable to {\sc csrf}.
+
+\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
+attack is a recent threat that combines
+a malicious script with
+an {\tt iframe} that loads a legitimate page in
+an effort to steal data from a user.
+Consider an attacker that lures
+a user to navigate to a web page the attacker controls
+via social engineering.
+The attacker's page then loads JavaScript
+and an HTML {\tt iframe} pointing to a legitimate site.
+Once the user enters his or her
+credentials into the legitimate site,
+the malicious script records all keystrokes.
+An {\sc xfs} attack can be also captured by our model
+because the steps are pretty similar to the steps of
+a non-persistent \textsc{xss} attack.}
 
@@
 in the browser (Point {\sc ub}). The scheme focuses on the detection of
-{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
-payload is executed as a result of the modification of the {\sc dom}
-environment so that the client-side code runs in an unanticipated
-manner, even if the {\sc http} response that triggers the injection
-seems legitimate. This scheme is different from the previous one
+{\sc dom}-based {\sc xss} attacks.
+This scheme is different from the previous one
 because it marks and observes data that are considered harmful.

### 2016-07-30 docs/comments/comments.tex
addressed comment 2 of R2

@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
-Lorem Ipsum. Lorem Ipsum.\\
+In our study,
+we observed that there are cases where
+mechanisms coming from the same category
+can be bypassed by similar attack patterns.
+This denotes that there are issues
+found in the design of each approach.
+We also observed that mechanisms which
+combine characteristics
+from different categories,
+could deal with these threats.
+This indicates that when solutions
+borrow elements from other categories
+could be more effective.
+Mechanisms can also work together
+to defend against different attacks.
+For instance,
+developers could use {\sc csp}
+and \textsc{sql}rand
+together to deal with {\sc xss} and
+{\sc sql} injection respectively.
+We have updated Subsection 7.3
+(now named ``Performance Overhead,
+Deployment and Security Remarks")
+to include all the above remarks.\\
 

### 2016-07-30 docs/paper/questioning.tex
addressed comment 2 of R2

@@
 \leavevmode
-\includegraphics[scale=0.48]{attacks-steps-CSRF.pdf}
+\includegraphics[scale=0.46]{attacks-steps-CSRF.pdf}
 \end{center}
@@
 the same JavaScript keywords contained in the rotator script.
-%% PL You mean like the rotator?
 In this script, attackers could also include references to tiny
@@
 
-\subsection{Performance Overhead and Deployment Remarks}
+\subsection{\hlc[yellow]{Performance Overhead,
+Deployment and Security Remarks}}
 
@@
 challenges, and try to mitigate them.
+
+\hlc[yellow]{From a security perspective,
+we saw that there are cases where
+mechanisms coming from the same category
+can be bypassed by similar attack patterns.
+This denotes that there are issues
+found in the design of each approach.
+Recall for instance,
+that implicit flows can be used against
+many taint tracking solutions,
+and mimicry attacks can be launched
+to bypass training and policy enforcement defenses.
+{\sc ifc} mechanisms though,
+could deal with such attacks because they
+combine characteristics from different categories.
+This indicates that when solutions
+borrow elements from other categories
+could be more effective.
+Taking one step further,
+we could say that different mechanisms could
+be used together to defend different attacks.
+For instance,
+developers could use {\sc csp}}~\cite{SSM10}
+\hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
+\hlc[yellow]{ together
+to deal with {\sc xss} and {\sc sql} injection
+respectively.}
 
@@
 in the Computer Science Department
-at Columbia University in the City of New York.
+at Columbia University.
 He holds a PhD ('14) in Cyber Security from the
 Athens University of Economics and Business.
-He is an {\sc ieee} member, a member of SysSec,
-and an official writer for the
-{\sc xrds}: Crossroads blog of {\sc acm}.
 His research interests include application security,
@@
 at Stony Brook University.
-He received the B.Sc. ('03), M.Sc. ('05), and Ph.D. ('09)
-degrees in Computer Science from the University of Crete, Greece.
+He received a Ph.D. ('09)
+degree in Computer Science from the University of Crete, Greece.
 % while working as a research assistant in the Distributed
@@
 Before joining Stony Brook, he was an Associate Research
-Scientist at Columbia University in the City of New York.
+Scientist at Columbia University.
 His research interests include
@@
 {\bf Angelos D. Keromytis} is an Associate Professor
-of Computer Science at Columbia University in the City
-of New York, and the director of the Network Security Lab.
+of Computer Science at Columbia University,
+and the director of the Network Security Lab.
 He is currently serving as  Program Manager with the
@@
 and cryptography.
-He is an {\sc acm} Distinguished Scientist since 2012,
-and a founder of Allure Security Technology Inc.
 

### 2016-07-30 docs/comments/comments.tex
lots of shrinking, now 14 pages

@@
 
-\section{General Remarks}
-\label{sec:rem}
-
-We are thankful to the reviewers for their thorough reviews.
-We have revised our paper based on their suggestions and comments.
-All additions and changes are highlighted in yellow
-in the revised manuscript.
-Number wise answers to their specific
-comments / suggestions / queries are as follows.
-
 \section{AE Comments}
@@
 {\bf Response:}
-Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.\\
+We are thankful to the reviewers for their thorough reviews.
+We have revised our paper based on their suggestions and comments.
+All additions and changes are highlighted in yellow
+in the revised manuscript.
+Number wise answers to their specific
+comments / suggestions / queries are as follows.\\
 
@@
 In addition,
-to address the comments of the 2nd and the 3rd reviewer,
-we have included six more mechanisms,
-thus making our study more extended.
+to address the comments of the second
+and the third reviewer,
+we have extended our study by
+including six more mechanisms.
 Notably,
-one of the mechanisms is presented in a recent
+one of the mechanisms was presented in a recent
 paper with less than 20 citations.
-This increases the number of such papers
-incorporated in our study (6).\\
+This increases the number of such cases
+in our paper (6).\\
 
@@
 compare the mechanisms with each other
-but to highlight factors that may hinder
-the widespread deployment of protection mechanisms
+but to analyze and categorize them,
+and highlight factors that may hinder
+their widespread deployment
 (we state this early on in the
@@
 For instance,
-developers could use {\sc csp}
+developers could employ both {\sc csp}
 and \textsc{sql}rand
-together to deal with {\sc xss} and
+to deal with {\sc xss} and
 {\sc sql} injection respectively.
@@
 Cross Frame Scripting (\textsc{xfs}) attacks
-are comprise a novel category worth mentioning.
-We now refer to \textsc{xfs} attacks
-at the end of Section 3 (``Exploitation Model").
+comprise a novel category worth mentioning.
+We now describe \textsc{xfs} attacks
+in Section 3 (``Exploitation Model").
 We also provide a corresponding example.\\

### 2016-07-30 docs/paper/questioning.tex
lots of shrinking, now 14 pages

@@
 \lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
-\lstset{aboveskip=3.3pt,belowskip=3.3pt}
+\lstset{aboveskip=3.2pt,belowskip=3.1pt}
 
@@
 \title{Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}}
-
+\vspace{-1mm}
 \author{
@@
 script or domain-specific language code.
-Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SG07},
+Attacks of this type include Cross-Site Scripting ({\sc xss})~\cite{SW06},
 and {\sc sql} injection attacks~\cite{RL12b},
@@
 when building mechanisms for the protection of
-applications~\cite{A01,A00,SPWS13,nature2014}.
+applications~\cite{A00,SPWS13,nature2014}.
 Based on this analysis, we identify the advantages
@@
 language code injection attacks against web applications.}
-\vspace{-5.8mm}
+\vspace{-6.5mm}
 \end{figure}
@@
 Lhee and Chapin~\cite{LC03}. Advances in memory corruption vulnerability
-exploitation have been studied extensively~\cite{PB04, SPWS13}
+exploitation have been studied extensively~\cite{SPWS13}
 and countermeasures to such attacks
@@
 \end{lstlisting}
-
+\vspace{-1mm}
 \noindent
@@
 similar techniques, malicious users can mount other exploits based on
-{\sc dsl}s such as {\sc xp}ath~\cite{SW06}, {\sc
-  xml}~\cite{MSM13} and {\sc json}~\cite{SMS13}. The effects can be
+{\sc dsl}s such as {\sc xp}ath~\cite{SW06},
+{\sc xml} and {\sc json}~\cite{SMS13}. The effects can be
 wide-ranging. A malicious user can view sensitive information, destroy
@@
 {\tt img} tag in the following manner:
-
+\vspace{-0.5mm}
 \lstset{language=HTML}
@@
 in web application security mainly because they are associated with
-major vulnerabilities such as {\sc xss} attacks~\cite{SG07} and
+major vulnerabilities such as {\sc xss} attacks and
 Cross-Channel Scripting ({\sc xcs}) attacks~\cite{BBB09}.
@@
 can manage to inject a script in the JavaScript engine of a browser
-and alter its execution flow~\cite{ELX07}.
+and alter its execution flow.
 For a typical {\sc xss} example that involves JavaScript injection
@@
 email) and inducing the user to click on it:
-
+\vspace{-0.5mm}
 \lstset{language=HTML}
@@
 that is fed into an {\tt eval()} function call, e.g.:
-
+\vspace{-0.5mm}
 \lstset{language=PHP}
@@
 \end{lstlisting}
-
+\vspace{-0.5mm}
 \noindent
@@
 a {\sc dom}-based {\sc xss} attack
-can follow a path of either a persistent {\sc xss}
+can follow the path of either a persistent {\sc xss}
 attack or a non-persistent {\sc xss} attack.
@@
 across frames.}
+
+\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
+attack is a recent threat that combines
+a malicious script with
+an {\tt iframe} that loads a legitimate page in
+an effort to steal data from a user.
+Consider an attacker that lures
+a user to navigate to a web page the attacker controls
+via social engineering.
+The attacker's page then loads JavaScript
+and an {\sc html} {\tt iframe} pointing to a legitimate site.
+Once the user enters his or her
+credentials into the legitimate site,
+the malicious script records all keystrokes.
+An {\sc xfs} attack can be captured by our model
+because the steps needed are pretty similar to the steps of
+a non-persistent \textsc{xss} attack.}
 
@@
 
-\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
-attack is a recent threat that combines
-a malicious script with
-an {\tt iframe} that loads a legitimate page in
-an effort to steal data from a user.
-Consider an attacker that lures
-a user to navigate to a web page the attacker controls
-via social engineering.
-The attacker's page then loads JavaScript
-and an HTML {\tt iframe} pointing to a legitimate site.
-Once the user enters his or her
-credentials into the legitimate site,
-the malicious script records all keystrokes.
-An {\sc xfs} attack can be also captured by our model
-because the steps are pretty similar to the steps of
-a non-persistent \textsc{xss} attack.}
-
 \section{Analysis Dimensions}
@@
 \begin{itemize}
+\vspace{-1mm}
 \item Statistical measurements that show how
@@
 of the findings.
+\vspace{-1mm}
 \end{itemize}
-
 \noindent
@@
 \begin{itemize}
+\vspace{-0.5mm}
 \item What are the overheads imposed by the mechanism?
@@
 \item At which point throughout the system does it block an attack?
+\vspace{-0.5mm}
 \end{itemize}
@@
 metrics~\cite{GFDLS06,A00}:
+\vspace{-0.7mm}
 \begin{itemize}
@@
 \end{itemize}
-
+\vspace{-0.7mm}
 \noindent
@@
 Sensitivity and specifity are defined as follows~\cite{linn2004}:
+\vspace{-0.7mm}
 \begin{itemize}
@@
 \label{sec:deployment}
+\vspace{-0.5mm}
 
@@
 
+\vspace{-0.5mm}
 \subsection{Security}
+\vspace{-0.5mm}
 
@@
 \label{sec:point}
+\vspace{-0.5mm}
 
@@
 in Figure~\ref{fig:attacks}:
-\vspace{-0.5mm}
+\vspace{-1mm}
 \begin{enumerate}
@@
 \end{enumerate}
-\vspace{-0.5mm}
+\vspace{-0.8mm}
 
@@
 \leavevmode
-\includegraphics[scale=0.53]{defenses.pdf}
+\includegraphics[scale=0.50]{defenses.pdf}
 \end{center}
@@
 \begin{table*}[t]
-  \renewcommand{\baselinestretch}{1.12}
+  \renewcommand{\baselinestretch}{1.10}
     \caption{\hlc[yellow]{Summary of mechanisms developed to counter application
@@
     \begin{tablenotes}
-  \begin{tiny}
+  \begin{scriptsize}
         \item[1] {\sc na} (Not Available) indicates that a requirement is not mentioned in the paper.
@@
     \item[4] {\it i} stands for injection.
-    \vspace{-1.8mm}
     \item[5] The numbers in this particular case involve requests.
-  \end{tiny}
+  \end{scriptsize}
     \end{tablenotes}
@@
     \end{threeparttable}
-    \vspace{-6.7mm}
+    \vspace{-7mm}
 \end{table*}
@@
 \label{sec:defs}
+\vspace{-0.5mm}
 
@@
 The etiological category involves mechanisms designed to
-block attacks based on their causes and origins~\cite{L81}. 
+block attacks based on their causes and origins. 
 The symptomatic category incorporates a variety of schemes that
@@
 \label{sec:prot}
+\vspace{-0.5mm}
 
@@
 \emph{Policy Enforcement}, and
-\emph{Instruction Set Randomization} ({\sc isr}).
+\emph{Instruction Set Randomization}.
+\vspace{-3.5mm}
 
@@
 \label{sec:tree}
+\vspace{-1mm}
 
@@
 as we will see in Section~\ref{sec:hybrid}.
+\vspace{-0.5mm}
 
@@
 \label{sec:policy}
+\vspace{-0.5mm}
 
@@
 
+\vspace{-1mm}
 Some frameworks define policies based on information and
@@
 mechanisms.
-\vspace{-0.5mm}
-
+
+\vspace{-1.5mm}
 A policy enforcement technique developed by Mozilla,
@@
 by the browser as an attribute of the payload~\cite{jigsaw}.
-\vspace{-0.5mm}
 
@@
 strings,\footnote{\scriptsize The infamous Sammy worm that
-infected MySpace in 2005~\cite{ELX07}
+infected MySpace in 2005
 utilized the {\tt eval} function to assemble a
@@
 sub-domains of the same registered domain.
-
 Most of the above frameworks involve
@@
 
+\vspace{-0.3mm}
 \subsubsection{Instruction Set Randomization (ISR)}
+\vspace{-0.8mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Symptomatic}
+\vspace{-0.8mm}
 
@@
 \label{sec:taint}
+\vspace{-0.3mm}
 
@@
 \label{sec:train}
+\vspace{-0.7mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Hybrid}
 \label{sec:hybrid}
+\vspace{-0.8mm}
 
@@
 have a broader scope.
-They can be used to build secure
-distributed applications,
-thus preventing different attacks,
-including {\sc xss} and {\sc dsl}-driven
-code injection.
+They can be used to build secure applications,
+thus preventing different attacks.
+Policies can be provided either as compile-time
+program annotations,
+or as run-time requirements defined by the user.
 Such frameworks include {\sc sif}
@@
 Hails}~\cite{GLSTMMR12}
-\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}\hlc[yellow]{.
-Policies can be provided either as compile-time
-program annotations,
-or as run-time requirements defined by the user.}
+\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}.
 
 \vspace{-1mm}
-
 \section{Observations}
 \label{sec:discussion}
+\vspace{-1.25mm}
 
@@
 
+\vspace{-1mm}
 \subsection{Accuracy}
+\vspace{-0.8mm}
 
@@
 \end{center}
-\vspace{-5.7mm}
+\vspace{-6mm}
 \caption{\label{fig:defect_sources}Most common sources of real-world vulnerabilities
@@
 Microsoft~\cite{RDWDE07}.}
-\vspace{-6.3mm}
+\vspace{-6mm}
 \end{figure}
@@
 \subsection{Availability}
+\vspace{-0.8mm}
 
 \begin{table}
+\renewcommand{\baselinestretch}{1.10}
 \caption{Availability of the studied defenses.}
@@
     \end{threeparttable}
-    \vspace{-6.5mm}
+    \vspace{-7.5mm}
 \end{table}
@@
 
+\vspace{-0.3mm}
 \subsection{Performance Overhead}
+\vspace{-0.5mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Ease of Use}
 \label{sec:deploy2}
+\vspace{-0.4mm}
 
@@
 authorization and access control
-with the tracking of the information flow.}
+with the tracking of information flow.}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Security}
+\vspace{-0.5mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Point of Detection}
+\vspace{-0.5mm}
 
@@
 such attacks on the server can also detect {\sc dsl} code
-injection attacks (\hlc[yellow]{9 out of 13}).
-
+injection (\hlc[yellow]{9 out of 13}).
+
+\vspace{-0.3mm}
 \section{Recommendations and Lessons Learned}
 \label{sec:lessons-learned}
+\vspace{-0.3mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Improving Testing Accuracy}
+\vspace{-0.3mm}
 
@@
 have~\cite{linn2004}:
-
+\vspace{-1mm}
 \begin{equation}
@@
 \end{equation}
+\vspace{-4mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{Code Availability}
+\vspace{-0.7mm}
 
@@
 
+\vspace{-0.3mm}
 \subsection{\hlc[yellow]{Performance Overhead,
 Deployment and Security Remarks}}
+\vspace{-0.3mm}
 
@@
 {\sc ifc} mechanisms though,
-could deal with such attacks because they
-combine characteristics from different categories.
+can deal with such attacks.
 This indicates that when solutions
 borrow elements from other categories
+(recall that {\sc ifc} mechanisms
+belong to the hybrid category)
 could be more effective.
-Taking one step further,
+Also,
 we could say that different mechanisms could
@@
 For instance,
-developers could use {\sc csp}}~\cite{SSM10}
+developers could employ both {\sc csp}}~\cite{SSM10}
 \hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
-\hlc[yellow]{ together
-to deal with {\sc xss} and {\sc sql} injection
-respectively.}
-
+\hlc[yellow]{to deal with {\sc xss}
+and {\sc sql} injection respectively.}
+
+\vspace{-0.3mm}
 \section{Conclusion}
 \label{sec:conclusion}
+\vspace{-0.3mm}
 
@@
 
+\vspace{-3mm}
+
 \bibliographystyle{IEEEtran}
 \bibliography{questioning}
+\vspace{-0.5mm}
 
 \section*{Author Biographies}
+\vspace{-0.5mm}
 \noindent
@@
 Information Innovation Office ({\sc i}2O) at the Defense Advanced
-Research Projects Agency ({\sc darpa}),
-part of the Department of Defense.
+Research Projects Agency ({\sc darpa}).
 His research interests are in systems

### 2016-09-02 docs/comments/comments.tex
nits

@@
 in the revised manuscript.
-Number wise answers to their specific
-comments / suggestions / queries are as follows.\\
+In the following we provide answers to specific
+comments/suggestions/queries.\\
 
@@
 borrow elements from other categories
-could be more effective.
+they could become more effective.
 Mechanisms can also work together
@@
 Our paper now includes six solutions
-that follow this approach
+that follow this approach,
 including {\sc sif}~\cite{CVMA07},

### 2016-09-17 docs/comments/comments.tex
minor fix based on Mike's comment
some changes in the 1st comment of the 1st reviewer

@@
 {\bf Response:}
-Indeed,
-an application firewall is actually a defense
-mechanism that fits in our study.
+In general,
+a way to check if a mechanism can be examined
+based on our criteria,
+is to see if and how it fits into our
+exploitation model (point of detection).
+Specifically,
+application firewalls
+fit into our study.
 Besides,
@@
 the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
-that we include in our study as
-application firewalls.
-Such mechanisms though,
-can be seen as host-based application firewalls
-which are different from the network-based
-application firewalls.
-Mechanisms coming from the later category
-operate directly at the application
-layer of the protocol stack and
-in most cases they are modules
-of the web server
-(e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
-Even though we do not include such mechanisms
-(note also that {\tt modsecurity} is
-not a research approach),
-they can be analyzed based on our criteria.\\
+that we include in our analysis as
+application firewalls.\\
+
+% Such mechanisms though,
+% can be seen as host-based application firewalls
+% which are different from the network-based
+% application firewalls.
+% Mechanisms coming from the later category
+% operate directly at the application
+% layer of the protocol stack and
+% in most cases they are modules
+% of the web server
+% (e.g. {\tt modsecurity})\footnote{\url{https://www.modsecurity.org/}}.
+% Even though we do not include such mechanisms
+% in our study,
+% they can be analyzed based on our criteria.\\
 % note: I do not know if we must update the text

### 2016-09-17 docs/comments/comments.tex
updated the "response to reviewers" doc per Panos comments

@@
 fit into our study.
-Besides,
+Indeed,
 in reference~\cite{DPJV06}
@@
 This is a valid comment.
-However,
+Indeed,
 in order to avoid penalizing recent research,
@@
 found in the design of each approach.
-We also observed that mechanisms which
+We also observed that mechanisms that
 combine characteristics
-from different categories,
+from different categories
 could deal with these threats.

### 2016-09-19 docs/paper/questioning.tex
updated the paper based on Panos' comments

@@
 injection of specially crafted objects
-(e.g. as part of cookies).
+(e.g., as part of cookies).
 When deserialized
@@
 {\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
-Note that, {\sc xss} and {\sc csrf} attacks can start from both routes.
+Note that {\sc xss} and {\sc csrf} attacks can start from both routes.
 Once the injected code reaches the vulnerable application, it becomes
@@
 {\it persistent} (also known as \emph{stored}) {\sc xss}
-\hlc[yellow]{and {\sc dom}\textit{-based} \textsc{xss}.}
+\hlc[yellow]{and \textit{Document Object Model} ({\sc dom})
+\textit{-based} \textsc{xss}.}
 Non-persistent {\sc xss} attacks take place when the
@@
 eventually sent to the user as part of a future response.
-\hlc[yellow]{In a {\sc dom}-based {\sc xss} attack,
-the malicious payload is executed as a result of
-the modification of the {\sc dom}
-environment so that the client-side code runs
-in an unanticipated manner,
-even if the {\sc http} response that
-triggers the injection seems legitimate.
-Notably,
-a {\sc dom}-based {\sc xss} attack
-can follow the path of either a persistent {\sc xss}
-attack or a non-persistent {\sc xss} attack.
-Also,
-it can be performed on-demand and purely client-side
-across frames.}
+\hlc[yellow]{{\sc dom}-based {\sc xss} attacks involve
+the modification of the {\sc dom} of a webpage.
+The {\sc dom} treats an {\sc html} document
+as a tree structure where each node is an
+object representing a part of the document.
+Each object can be accessed and manipulated
+programmatically and any visible changes
+may then be reflected in the browser.
+In a {\sc dom}-based {\sc xss} attack,
+the malicious payload
+(e.g., hidden in a well-crafted {\sc url}
+that is sent to a user via phishing:
+\textsc{n-xss} 1.1)
+is executed as a result of
+the manipulation of the {\sc dom}
+environment
+(e.g., when another flawed script accesses the
+modified {\sc dom} object)
+and is not contained in
+the {\sc http} response.
+That is,
+the malicious payload never reaches the server.
+Such an attack can be performed
+purely client-side across {\sc html} frames.
+Hence,
+server-side defenses might not be effective
+in this case.}
 
@@
 an effort to steal data from a user.
-Consider an attacker that lures
-a user to navigate to a web page the attacker controls
-via social engineering.
+Consider an attacker that lures via social engineering
+a user to navigate to a web page the attacker controls.
 The attacker's page then loads JavaScript
@@
 credentials into the legitimate site,
-the malicious script records all keystrokes.
-An {\sc xfs} attack can be captured by our model
-because the steps needed are pretty similar to the steps of
-a non-persistent \textsc{xss} attack.}
+the malicious script records all keystrokes.}
 
@@
 \textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
-Sensitivity and specifity are defined as follows~\cite{linn2004}:
+Sensitivity and specifity are defined using the following~\cite{linn2004}:
 \vspace{-0.7mm}
@@
 \noindent
-With these we can calculate:
+So that we can calculate:
 
@@
 an important issue outside the computer science field: the journal
-\emph{Nature}, in a recent editorial, adopted a publication policy stressing
+\emph{Nature} has adopted a publication policy stressing
 access to code and data~\cite{nature2014}. At a time and date that the
@@
 presented in top security conferences, even though they have been
-cited less than twenty times, so that recent research is not penalized.
+cited less than 20 times, so that recent research is not penalized.
 
@@
 Some frameworks define policies based on information and
-features provided by the Document Object Model ({\sc dom}) of a web
+features provided by the {\sc dom} of a web
 page. Specifically, developers must place all legitimate scripts
@@
 as valid sources of script and which not.
-\hlc[yellow]{These policies are communicated via the {\sc http} header.}
+\hlc[yellow]{These policies are communicated via the {\sc http} headers.}
 Then, the browser
@@
 random value indicated in
-the {\tt script-src} directive which in turn,
-is applied as a nonce attribute to
+the {\tt script-src} directive,
+which in turn is applied as a nonce attribute to
 {\tt <script>} elements.
@@
 based on a randomly chosen transformation,
-and randomizing the execution environment accordingly.
+and randomize the execution environment accordingly.
 In this way, any malicious code injected as part of untrusted input data,
@@
 the difficulty of maintaining accurate taints~\cite{GMPS11}
-(e.g. implicit flows~\cite{ME07}).
+(e.g., implicit flows~\cite{ME07}).
 In such cases, certain, tainted inputs can escape the tracking mechanism.
@@
 influenced by the coverage that is achieved during the training phase. If
-the coverage is insufficient false alarms are very likely. In
+the coverage is insufficient,
+false alarms are very likely. In
 addition, when a code statement is altered, a new training phase is
@@
 \hlc[yellow]{allow developers to express information flow
-policies be extending the type system of JavaScript.
+policies extending the type system of JavaScript.
 Then,
@@
 %~\cite{hackers}.
-Figure~\ref{fig:defect_sources},
+Figure~\ref{fig:defect_sources}
 presents how many,
-and which, in the figure's caption, publications referred
+and which publications referred
 to which source.
@@
 
+\vspace{-0.5mm}
 \subsection{Availability}
@@
 publications provided a link to their mechanism and, 2 from these 6
-web pages are currently not available. In \hlc[yellow]{7} cases authors made either
+web pages are currently not available.
+In \hlc[yellow]{7} cases the authors made either
 the source code or their executables available after their paper got
@@
 provide the latency (in ms) that their mechanisms add to the
-normal execution time of the protected application. Note that in some
-cases, the times of normal executions are not provided,
+normal execution time of the protected application.
+Note that in some
+cases, the times of normal executions are not provided
 so it is not possible to convert absolute
@@
 \hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
-\hlc[yellow]{, the authors indicate that with
-their mechanisms, the execution time is doubled.}
+\hlc[yellow]{the authors indicate that with
+their mechanisms the execution time is doubled.}
 
@@
 
-\hlc[yellow]{A reasonable argument would be that many mechanisms
-(e.g. many mechanisms coming from the etiological category,
+\hlc[yellow]{A reasonable argument would be that many defenses
+(e.g., many mechanisms coming from the etiological category,
 or the {\sc ifc} frameworks), do not need to be
-established purely through testing, since they provide systematic
+validated purely through testing, since they provide systematic
 arguments as to why their design is secure against attacks.
@@
 found in the design of each approach.
-Recall for instance,
+Recall,
+for instance,
 that implicit flows can be used against
@@
 borrow elements from other categories
-(recall that {\sc ifc} mechanisms
+({\sc ifc} mechanisms
 belong to the hybrid category)
@@
 
-To the positive side, some defenses have been extensively tested in
+On the positive side, some defenses have been extensively tested in
 terms of accuracy ({\sc sqlc}heck~\cite{SW06},
@@
 solve specific problems in an effective way
-(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}) or
-have a low computational overhead
+(Blueprint~\cite{LV09} and the system by Stock et al.~\cite{SLMS14}),
+or have a low computational overhead
 ({\sc dsi}~\cite{NSS06} and the system by Phung et al.~\cite{PSC09}).
@@
 
-\vspace{-3mm}
+\vspace{-4mm}
 

### 2016-09-19 docs/comments/comments.tex
minor changes and proofs

@@
 
-{\bf Comment} ``The second and third reviewers
+{\bf Comment:} ``The second and third reviewers
 have pointed out problems in missing related work and
@@
 such solutions do not need to be
-established purely through testing,
+validated purely through testing,
 since they provide systematic

### 2017-02-01 docs/paper/questioning.tex
no yellow and watermarks. Also fixed a typo

@@
 
-\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }
-
 \titlespacing*{\section}
@@
 
-\usepackage{draftwatermark}
-\SetWatermarkText{Confidential}
-\SetWatermarkScale{0.4}
+% \usepackage{draftwatermark}
+% \SetWatermarkText{Confidential}
+% \SetWatermarkScale{0.4}
 
@@
 and that provides a common perspective for studying the available defenses.
-We then categorize and analyze a set of \hlc[yellow]{41} previously proposed defenses 
+We then categorize and analyze a set of 41 previously proposed defenses 
 based on their accuracy, performance,
@@
 that we described earlier are out of scope as well. Note also, that we
-\hlc[yellow]{did not} consider mechanisms that
-\hlc[yellow]{have not} been presented in research papers.
+did not consider mechanisms that
+have not been presented in research papers.
 
@@
 
-\hlc[yellow]{A recent attack called {\sc php} Object Injection
-({\sc poi})}~\cite{DKH14} \hlc[yellow]{does not directly involve
+A recent attack called {\sc php} Object Injection
+({\sc poi})~\cite{DKH14} does not directly involve
 the injection of code, but still achieves arbitrary code execution
@@
 by the application, these objects result in
-arbitrary code execution.}
+arbitrary code execution.
 Note that the exploitation model we propose
@@
 Cross-site scripting
-attacks fall into \hlc[yellow]{three} categories,
+attacks fall into three categories,
 {\it non-persistent}
@@
 {\it persistent} (also known as \emph{stored}) {\sc xss}
-\hlc[yellow]{and \textit{Document Object Model} ({\sc dom})
-\textit{-based} \textsc{xss}.}
+and \textit{Document Object Model} ({\sc dom})
+\textit{-based} \textsc{xss}.
 Non-persistent {\sc xss} attacks take place when the
@@
 eventually sent to the user as part of a future response.
-\hlc[yellow]{{\sc dom}-based {\sc xss} attacks involve
+{\sc dom}-based {\sc xss} attacks involve
 the modification of the {\sc dom} of a webpage.
@@
 server-side defenses might not be effective
-in this case.}
-
-\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
+in this case.
+
+A Cross Frame Scripting (\textsc{xfs})
 attack is a recent threat that combines
@@
 credentials into the legitimate site,
-the malicious script records all keystrokes.}
+the malicious script records all keystrokes.
 
@@
 Defenders and attackers are often caught in a cat-and-mouse game,
-where countermeasures are bypassed by \hlc[yellow]{savvy} attacks, which are caught
-by more sophisticated countermeasures, yet again bypassed by \hlc[yellow]{savvier}
+where countermeasures are bypassed by savvy attacks, which are caught
+by more sophisticated countermeasures, yet again bypassed by savvier
 attacks, and so on. We use security to refer to the ability of a
@@
   \renewcommand{\baselinestretch}{1.10}
-    \caption{\hlc[yellow]{Summary of mechanisms developed to counter application
+    \caption{Summary of mechanisms developed to counter application
     attacks based on code injection. The different results does not necessarily
@@
     This is because most of them were evaluated under different assumptions
-    and settings.}}
+    and settings.}
     \label{tab:comp}
-    \vspace{-5.2mm}
+    \vspace{-4.8mm}
 \centering
@@
   &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
-  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{62} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
-  & \hlc[yellow]{2$\times$ ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
-  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} & \hlc[yellow]{27} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
-  & \hlc[yellow]{16\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
-  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} & \hlc[yellow]{5} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
-  & \hlc[yellow]{average 55\% ({\sc c})} & \hlc[yellow]{{\sc xss}} \\
-  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{146} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
-  & \hlc[yellow]{26\% ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
+  &   {\sc jsf}low~\cite{HBBS14} & 62 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   2$\times$ ({\sc c}) & {\sc xss} \\
+  &   {\sc cowl}~\cite{SYMRHKM14} & 27 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   16\% ({\sc c}) & {\sc xss} \\
+  &   Bauer et al.~\cite{BCJPST15} & 5 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   average 55\% ({\sc c}) & {\sc xss} \\
+  &   {\sc sif}~\cite{CVMA07} & 146 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   26\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
   % &   \hlc[yellow]{Ur/Web}~\cite{C10b} & \hlc[yellow]{59} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s}
   % & \hlc[yellow]{average 55\% ({\sc s})} & \hlc[yellow]{{\sc sql}i} \\
-  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} & \hlc[yellow]{78} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r}
-  & \hlc[yellow]{28\% ({\sc s},{\sc c})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
-  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} & \hlc[yellow]{52} & \hlc[yellow]{({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}}
-  & \hlc[yellow]{323.5ms per request ({\sc s})} & \hlc[yellow]{{\sc sql}i, {\sc xss}} \\
+  &   Hails~\cite{GLSTMMR12} & 78 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   28\% ({\sc s},{\sc c}) & {\sc sql}i, {\sc xss} \\
+  &   Aeolus~\cite{CPSPBCCSL12} & 52 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   323.5ms per request ({\sc s}) & {\sc sql}i, {\sc xss} \\
   \thickhline
@@
 as valid sources of script and which not.
-\hlc[yellow]{These policies are communicated via the {\sc http} headers.}
+These policies are communicated via the {\sc http} headers.
 Then, the browser
@@
 place at client-side, in the JavaScript engine of the browser (Point {\sc ub}).
-In this way, \hlc[yellow]{{\sc xss}} attacks that take advantage
+In this way, {\sc xss} attacks that take advantage
 of functions such as {\tt write} and {\tt eval}, which are
@@
 In such cases, certain, tainted inputs can escape the tracking mechanism.
-Keeping track of such input \hlc[yellow]{may be} impractical not only because of the
+Keeping track of such input may be impractical not only because of the
 various technical difficulties, but also because it would raise false alarms.
@@
 characteristics from both etiological and symptomatic approaches.
-\hlc[yellow]{Five} of them focus on the detection of {\sc xss}
+Five of them focus on the detection of {\sc xss}
 attacks and one focuses on {\sc dsl} code injection attacks.
@@
 
-\hlc[yellow]{Information Flow Control ({\sc ifc})
+Information Flow Control ({\sc ifc})
 mechanisms combine positive taint tracking and
@@
 Representative implementations such as
-{\sc jsf}low}~\cite{HBBS14}\hlc[yellow]{, {\sc cowl}}~\cite{SYMRHKM14}
-\hlc[yellow]{and the framework by Bauer et al.}~\cite{BCJPST15}
-\hlc[yellow]{allow developers to express information flow
-policies extending the type system of JavaScript.
+{\sc jsf}low~\cite{HBBS14}, {\sc cowl}~\cite{SYMRHKM14}
+and the framework by Bauer et al.~\cite{BCJPST15}
+allow developers to express information flow
+policies by extending the type system of JavaScript.
 Then,
 the policies are enforced by the JavaScript interpreter
-through dynamic checks.}
-\hlc[yellow]{{\sc ifc} frameworks do not
+through dynamic checks.
+{\sc ifc} frameworks do not
 focus explicitly on JavaScript and they
@@
 Such frameworks include {\sc sif}
-(Servlet Information Flow)}~\cite{CVMA07}\hlc[yellow]{,
+(Servlet Information Flow)~\cite{CVMA07},
 % Ur/Web}~\cite{C10b}\hlc[yellow]{,
-Hails}~\cite{GLSTMMR12}
-\hlc[yellow]{, and Aeolus}~\cite{CPSPBCCSL12}.
+Hails~\cite{GLSTMMR12},
+and Aeolus~\cite{CPSPBCCSL12}.
 
@@
 
-We group our key observations on the \hlc[yellow]{41} publications that
+We group our key observations on the 41 publications that
 we consider in this work along the
@@
 
-Table~\ref{tab:comp} indicates that the authors of 3 out of \hlc[yellow]{41 (7.3\%)}
+Table~\ref{tab:comp} indicates that the authors of 3 out of 41 (7.3\%)
 publications provided a complete tuple of {\sc tp}, {\sc tn}, 
 {\sc fp}, and {\sc fn}. On the other hand, we
-see that \hlc[yellow]{7} out of \hlc[yellow]{41 (17\%)} were not tested at all.
+see that 7 out of 41 (17\%) were not tested at all.
 In these cases, all four elements of the tuple
 are not available ({\sc na}). An interesting observation is
-that in 10 out of the \hlc[yellow]{41 (24.3\%)}
+that in 10 out of the 41 (24.3\%)
 publications, the evaluation focused on only on attack detection,
@@
 Regarding the subjects of tests,
-we see that \hlc[yellow]{30} out of \hlc[yellow]{41 (73.1\%)}
+we see that 30 out of 41 (73.1\%)
 mechanisms were tested with real-world
@@
   &   Diglossia~\cite{SMS13} & {\sc na} & {\sc na} & {\sc na} \\
-  &   \hlc[yellow]{{\sc jsf}low}~\cite{HBBS14} & \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\
-  &   \hlc[yellow]{{\sc cowl}}~\cite{SYMRHKM14} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
-  &   \hlc[yellow]{Bauer et al.}~\cite{BCJPST15} &  \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
-  &   \hlc[yellow]{{\sc sif}}~\cite{CVMA07} & \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\sc na}} \\
+  &   {\sc jsf}low~\cite{HBBS14} & \tick & \tick & {\sc na} \\
+  &   {\sc cowl}~\cite{SYMRHKM14} & {\sc na} & {\sc na} & {\sc na} \\
+  &   Bauer et al.~\cite{BCJPST15} & {\sc na} & {\sc na} & {\sc na} \\
+  &   {\sc sif}~\cite{CVMA07} & {\bf AO} & {\sc na} & {\sc na} \\
   % &   \hlc[yellow]{Ur/Web}~\cite{C10b} & \hlc[yellow]{59} & \hlc[yellow]{({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s}
   % & \hlc[yellow]{average 55\% ({\sc s})} & \hlc[yellow]{{\sc sql}i} \\
-  &   \hlc[yellow]{Hails}~\cite{GLSTMMR12} &  \hlc[yellow]{{\bf AO}} & \hlc[yellow]{{\sc na}} & \hlc[yellow]{{\bf AO}} \\
-  &   \hlc[yellow]{Aeolus}~\cite{CPSPBCCSL12} &  \hlc[yellow]{\tick} & \hlc[yellow]{\tick} & \hlc[yellow]{{\sc na}} \\
+  &   Hails~\cite{GLSTMMR12} &  {\bf AO} & {\sc na} & {\bf AO} \\
+  &   Aeolus~\cite{CPSPBCCSL12} &  \tick & \tick & {\sc na} \\
   \thickhline
@@
 executables. We also examined the availability of the testbeds
-mentioned in each paper. We see that only \hlc[yellow]{8} out of \hlc[yellow]{41 (19.5\%)} of the
+mentioned in each paper. We see that only 8 out of 41 (19.5\%) of the
 publications provided a link to their mechanism and, 2 from these 6
 web pages are currently not available.
-In \hlc[yellow]{7} cases the authors made either
+In 7 cases the authors made either
 the source code or their executables available after their paper got
@@
 Regarding the availability of test materials, we see that
-only \hlc[yellow]{4} out of \hlc[yellow]{41 (9.7\%)} publications have currently their testbeds
+only 4 out of 41 (9.7\%) publications have currently their testbeds
 available.
@@
 server ({\sc s}) or at the client-side ({\sc c}). In almost half of
-the approaches, \hlc[yellow]{20} out of \hlc[yellow]{41 (48.7\%)}, the overhead is provided as a
-percentage, while in other cases, \hlc[yellow]{8} our of \hlc[yellow]{41 (19.5\%)}, the authors
+the approaches, 20 out of 41 (48.7\%), the overhead is provided as a
+percentage, while in other cases, 8 our of 41 (19.5\%), the authors
 provide the latency (in ms) that their mechanisms add to the
@@
 so it is not possible to convert absolute
-time measurements to percentage overheads. In 10 cases (\hlc[yellow]{24.3\%}), the
+time measurements to percentage overheads. In 10 cases (24.3\%), the
 overhead was either not available ({\sc na})
 or not quantified ({\sc nq}).
-\hlc[yellow]{For \textsc{php} Aspis}~\cite{PMP11}
-\hlc[yellow]{and {\sc jsf}low}~\cite{HBBS14}
-\hlc[yellow]{the authors indicate that with
-their mechanisms the execution time is doubled.}
+For \textsc{php} Aspis~\cite{PMP11}
+and {\sc jsf}low~\cite{HBBS14}
+the authors indicate that with
+their mechanisms the execution time is doubled.
 
@@
 
-\hlc[yellow]{
 By design,
@@
 the authors of
-Aeolus}~\cite{CPSPBCCSL12}
-\hlc[yellow]{provide a simple security model
+Aeolus~\cite{CPSPBCCSL12}
+provide a simple security model
 that tries to match the way programmers understand
 authorization and access control
-with the tracking of information flow.}
+with the tracking of information flow.
 
@@
 From the mechanisms that detect {\sc dsl} code injection
-attacks, 3 out of \hlc[yellow]{16 (18.7\%)} do so at the level
+attacks, 3 out of 16 (18.7\%) do so at the level
 of the {\sc rdbms} (Point {\sc db}).
-The other \hlc[yellow]{13} are based on interposing on {\sc api} calls related to output
+The other 13 are based on interposing on {\sc api} calls related to output
 vectors (Point {\sc dbal}).
@@
 perform detection on the client-side: in particular,
-\hlc[yellow]{18} out of \hlc[yellow]{30}
-frameworks (\hlc[yellow]{60\%}) detect {\sc xss} attacks at the
+18 out of 30
+frameworks (60\%) detect {\sc xss} attacks at the
 client-side. Note that the majority of the mechanisms that detect
 such attacks on the server can also detect {\sc dsl} code
-injection (\hlc[yellow]{9 out of 13}).
+injection (9 out of 13).
 
@@
 
-\hlc[yellow]{A reasonable argument would be that many defenses
+A reasonable argument would be that many defenses
 (e.g., many mechanisms coming from the etiological category,
@@
 based on their root cause, instead of their observed behavior, may still be
-circumvented by evasive attacks.}
+circumvented by evasive attacks.
 
@@
 \vspace{-0.3mm}
-\subsection{\hlc[yellow]{Performance Overhead,
-Deployment and Security Remarks}}
+\subsection{Performance Overhead,
+Deployment and Security Remarks}
 \vspace{-0.3mm}
@@
 
-\hlc[yellow]{From a security perspective,
+From a security perspective,
 we saw that there are cases where
@@
 For instance,
-developers could employ both {\sc csp}}~\cite{SSM10}
-\hlc[yellow]{and \textsc{sql}rand}~\cite{BK04}
-\hlc[yellow]{to deal with {\sc xss}
-and {\sc sql} injection respectively.}
+developers could employ both {\sc csp}~\cite{SSM10}
+and \textsc{sql}rand~\cite{BK04}
+to deal with {\sc xss}
+and {\sc sql} injection respectively.
 

### 2017-02-01 docs/paper/questioning.tex
preprint version

@@
 {\it persistent} (also known as \emph{stored}) {\sc xss}
-and \textit{Document Object Model} ({\sc dom})
-\textit{-based} \textsc{xss}.
+and \textit{Document Object Model} ({\sc dom}) -
+\textit{based} \textsc{xss}~\cite{SLMS14}.
 Non-persistent {\sc xss} attacks take place when the
@@
     \label{tab:comp}
-    \vspace{-4.8mm}
+    \vspace{-4.6mm}
 \centering
@@
 \caption{Availability of the studied defenses.}
-\vspace{-4mm}
+\vspace{-4.4mm}
     \label{tab:avail}
@@
 
-\vspace{-0.3mm}
+\vspace{-0.5mm}
 \section{Recommendations and Lessons Learned}
 \label{sec:lessons-learned}
-\vspace{-0.3mm}
+\vspace{-0.5mm}
 
@@
 \end{minipage}\par\vspace{\belowdisplayskip}
+\vspace{-1.5mm}
 
@@
 have~\cite{linn2004}:
-\vspace{-1mm}
+\vspace{-1.5mm}
 \begin{equation}
@@
 \end{equation}
-\vspace{-4mm}
+\vspace{-4.5mm}
 
@@
 
-\vspace{-0.3mm}
+\vspace{-0.6mm}
 \subsection{Code Availability}
@@
 
-\vspace{-0.3mm}
+\vspace{-0.8mm}
 \subsection{Performance Overhead,
 Deployment and Security Remarks}
-\vspace{-0.3mm}
+\vspace{-1.3mm}
 
@@
 
-\vspace{-0.3mm}
+\vspace{-1mm}
 \section{Conclusion}
 \label{sec:conclusion}
-\vspace{-0.3mm}
+\vspace{-1mm}
 
@@
 
-\vspace{-4mm}
+\vspace{-1.5mm}
+
+\section*{Acknowledgements}
+\vspace{-1mm}
+We would like to thank the anonymous reviewers
+for their suggestions and comments.
+This work was supported by {\sc nsf} Grant No. {\sc cns}-13-18415.
+
+\vspace{-8mm}
 
@@
 \bibliography{questioning}
-\vspace{-0.5mm}
+\vspace{-1.2mm}
 
 \section*{Author Biographies}
-\vspace{-0.5mm}
+\vspace{-1.1mm}
 \noindent

### 2017-02-03 docs/paper/questioning.tex
updated figs (png) and citation numbers

@@
 \leavevmode
-\includegraphics[scale=0.52]{attack-tree-uml.pdf}
+\includegraphics[scale=0.52]{attack-tree.png}
 \end{center}
@@
 \leavevmode
-\includegraphics[scale=0.46]{attacks-steps-CSRF.pdf}
+\includegraphics[scale=0.46]{attacks-steps.png}
 \end{center}
@@
 \leavevmode
-\includegraphics[scale=0.50]{defenses.pdf}
+\includegraphics[scale=0.50]{defenses.png}
 \end{center}
@@
   \multirow{2}{*}{Parse-Tree Validation}
-  &   {\sc sqlg}uard~\cite{BWS05} & 305 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
-  &   {\sc sqlc}heck~\cite{SW06} & 473 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlg}uard~\cite{BWS05} & 368 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 3\% ({\sc s}) & {\sc sql}i \\
+  &   {\sc sqlc}heck~\cite{SW06} & 547 & (36848,7648,0,0)\_r & 3ms per query ({\sc s}) & {\sc sql}i \\
   \hline
   \multirow{13}{*}{Policy Enforcement}
-  &   {\sc dsi}~\cite{NSS06} & 168 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
-  &   NoForge~\cite{JKK06a} & 151 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
-  &   Noxes~\cite{KJKV09} & 58 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
+  &   {\sc dsi}~\cite{NSS06} & 188 & (5268,{\sc nq},{\sc nq},85)\_r & 1.85\% ({\sc c}) & {\sc xss} \\ 
+  &   NoForge~\cite{JKK06a} & 166 & (7,{\sc nq},{\sc nq},0)\_r & {\sc na} ({\sc s}) & {\sc csrf} \\
+  &   Noxes~\cite{KJKV09} & 69 & (3,{\sc na},{\sc na},0)\_r & {\sc na} ({\sc c}) & {\sc xss} \\
   % &   {\it {\sc met}}~\cite{ELX07} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} & {\sc xss} \\ 
-  &   {\sc beep}~\cite{TNH07} & 335 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
-  &   BrowserShield~\cite{RDWDE07} & 263 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
-  &   CoreScript~\cite{YCIS07} & 199 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\it {\sc soma}}~\cite{OWVS08} & 56 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
+  &   {\sc beep}~\cite{TNH07} & 362 & (61,{\sc na},{\sc na},0)\_r & 14.4\% ({\sc c}) & {\sc xss} \\
+  &   BrowserShield~\cite{RDWDE07} & 273 & (19,{\sc nq},0,0,)\_r & 8\% ({\sc s}) & {\sc xss} \\ 
+  &   CoreScript~\cite{YCIS07} & 212 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_s & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\it {\sc soma}}~\cite{OWVS08} & 65 & (5,{\sc na},{\sc na},0)\_s & 5.58\% ({\sc c}) & {\sc xss}, {\sc csrf} \\
   % &   {\it Barth et al.}~\cite{BJM08} & 271 & & {\bf ?} & {\sc csrf} \\
-  &   Phung et al.~\cite{PSC09} & 101 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
+  &   Phung et al.~\cite{PSC09} & 124 & (37,{\sc na},{\sc na},4)\_r & 5.37\% ({\sc c}) & {\sc xss} \\
   &   ConScript~\cite{ML10} & 152 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 7\% ({\sc c}) & {\sc xss} \\
-  &   CsFire~\cite{DDHPJ10} & 46 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
-  &   {\sc csp}~\cite{SSM10} & 117 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
+  &   CsFire~\cite{DDHPJ10} & 52 & (419582,1141807,0,3)\_r\tnote{5} & {\sc na} ({\sc c}) & {\sc csrf} \\
+  &   {\sc csp}~\cite{SSM10} & 143 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc nq} ({\sc c}) & {\sc xss}, {\sc csrf} \\
   &   j{\sc csrf}~\cite{PS11} & 4 & (2,{\sc na},{\sc na},0)\_r & 2ms ({\sc s}) & {\sc csrf} \\
-  &   WebJail~\cite{VDDPJ11} & 45 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
+  &   WebJail~\cite{VDDPJ11} & 53 & (2,{\sc na},{\sc na},1)\_{\bf ?} & $\sim$6.89ms ({\sc c}) & {\sc xss} \\
   % &   {\it TreeHouse}~\cite{IW12} & 18 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & 757–-1218ms & {\sc xss} \\
@@
   \multirow{4}{*}{{\sc isr}}
-  &   {\sc sql}rand~\cite{BK04} & 365 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
-  &   {\sc sm}ask~\cite{JB07} & 28 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Noncespaces~\cite{GC09} & 132 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
-  &   x{\sc js}~\cite{APKLM10} & 20 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40ms ({\sc c}) & {\sc xss} \\
+  &   {\sc sql}rand~\cite{BK04} & 428 & (3,{\sc na},{\sc na},0)\_a & $\le$6.5{\it ms} ({\sc s}) & {\sc sql}i \\
+  &   {\sc sm}ask~\cite{JB07} & 31 & (5,{\sc nq},{\sc nq},{\sc nq})\_r  & {\sc na} ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Noncespaces~\cite{GC09} & 146 & (6,{\sc na},{\sc na},0)\_r &  2\% ({\sc s}) & {\sc xss} \\ 
+  &   x{\sc js}~\cite{APKLM10} & 29 & (1380,{\sc na},{\sc na},1)\_r & 1.6--40ms ({\sc c}) & {\sc xss} \\
   \thickhline
@@
   \multirow{7}{*}{Taint Tracking}
-  &   Haldar et al.~\cite{HCF05} & 208 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc csse}~\cite{PB05} & 347 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
+  &   Haldar et al.~\cite{HCF05} & 234 & (2,{\sc na},{\sc na},0)\_s & {\sc nq} ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc csse}~\cite{PB05} & 387 & (7,{\sc nq},{\sc nq},{\sc nq})\_r & 2--10\% ({\sc s}) & {\sc sql}i, {\sc xp}athi, {\sc xss} \\
   % &   {\it SecuriFly}~\cite{MLL05} & 31 & \xmark,\tick & 9--125\% & {\sc sql} injection, {\sc xss} \\ 
-  &   Xu et al.~\cite{XBS06} & 346 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
-  &   {\sc wasc}~\cite{NLC07} & 32 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
-  &   Vogt et al.~\cite{VFJKKV07} & 400 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
-  &   {\sc php} Aspis~\cite{PMP11} & 20 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
-  &   Stock et al.~\cite{SLMS14} & 15 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
+  &   Xu et al.~\cite{XBS06} & 368 & (9,{\sc nq},0,{\sc nq})\_r & average 76\% ({\sc s}) & {\sc sql}i, {\sc xss} \\ 
+  &   {\sc wasc}~\cite{NLC07} & 37 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 30\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
+  &   Vogt et al.~\cite{VFJKKV07} & 490 & ({\sc nq},{\sc nq},{\sc nq},{\sc na})\_r & {\sc nq} ({\sc c}) & {\sc xss} \\
+  &   {\sc php} Aspis~\cite{PMP11} & 26 & (12,{\sc nq},{\sc nq},2)\_r & 2.2$\times$ ({\sc s}) & {\sc sql}i and {\sc php}i, {\sc xss} \\
+  &   Stock et al.~\cite{SLMS14} & 23 & (1169,{\sc na},{\sc na},0)\_r & 7--17\% ({\sc c}) & {\sc dom}-based {\sc xss} \\
   \hline 
   \multirow{6}{*}{Training}
-  &   {\sc didafit}~\cite{LLW02} & 190 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
-  &   {\sc amnesia}~\cite{HO05b} & 474 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
-  &   libAnomaly~\cite{VMV05} & 259 & (9,15987,60,0)\_r & 0.20--1ms per query ({\sc s}) & {\sc sql}i \\
-  &   {\sc xssds}~\cite{JEP08} & 85 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
-  &   {\sc swap}~\cite{WPLKK09} & 68 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261ms ({\sc s}) & {\sc xss} \\ 
-  &   {\sc sd}river~\cite{MS09,MKLS11} & 28 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
+  &   {\sc didafit}~\cite{LLW02} & 208 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?} & {\sc na} ({\sc s}) & {\sc sql}i \\
+  &   {\sc amnesia}~\cite{HO05b} & 551 & (1470,{\sc nq},0,0)\_a & {\sc nq} ({\sc s}) & {\sc sql}i \\ 
+  &   libAnomaly~\cite{VMV05} & 310 & (9,15987,60,0)\_r & 0.20--1ms per query ({\sc s}) & {\sc sql}i \\
+  &   {\sc xssds}~\cite{JEP08} & 96 & ({\sc nq},{\sc nq},{\sc nq},0)\_r & {\sc nq} ({\sc s}) & {\sc xss} \\
+  &   {\sc swap}~\cite{WPLKK09} & 83 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r & up to 261ms ({\sc s}) & {\sc xss} \\ 
+  &   {\sc sd}river~\cite{MS09,MKLS11} & 36 & (241,{\sc nq},0,0)\_a & 39\% ({\sc s}) & {\sc sql}i and {\sc xp}athi \\
   % &   {\it Laranjeiro et al.}~\cite{LVM09,ALVM09,LVM10} & 9,40,1 & \xmark,\xmark  & \xmark & {\sc sql} and {\sc xp}ath injection \\
@@
   \multirow{9}{*}{Hybrid}
-  &   {\sc xss-guard}~\cite{BV08} & 132 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
-  &   Blueprint~\cite{LV09} & 152 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
-  &   Diglossia~\cite{SMS13} & 13 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
-  &   {\sc jsf}low~\cite{HBBS14} & 62 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   {\sc xss-guard}~\cite{BV08} & 153 & (8,{\sc nq},{\sc nq},{\sc nq})\_r & 5--24\% ({\sc c}) & {\sc xss} \\
+  &   Blueprint~\cite{LV09} & 187 & (94,{\sc na},{\sc na},0)\_r & 13.6\% ({\sc c}) & {\sc xss} \\
+  &   Diglossia~\cite{SMS13} & 23 & (25,{\sc nq},{\sc nq},{\sc nq})\_r & 13\% ({\sc s}) & {\sc sql}i and {\sc json}i \\
+  &   {\sc jsf}low~\cite{HBBS14} & 72 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
   &   2$\times$ ({\sc c}) & {\sc xss} \\
-  &   {\sc cowl}~\cite{SYMRHKM14} & 27 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   {\sc cowl}~\cite{SYMRHKM14} & 41 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
   &   16\% ({\sc c}) & {\sc xss} \\
-  &   Bauer et al.~\cite{BCJPST15} & 5 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   Bauer et al.~\cite{BCJPST15} & 10 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
   &   average 55\% ({\sc c}) & {\sc xss} \\
-  &   {\sc sif}~\cite{CVMA07} & 146 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   {\sc sif}~\cite{CVMA07} & 155 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
   &   26\% ({\sc s}) & {\sc sql}i, {\sc xss} \\
@@
   % & \hlc[yellow]{average 55\% ({\sc s})} & \hlc[yellow]{{\sc sql}i} \\
-  &   Hails~\cite{GLSTMMR12} & 78 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
+  &   Hails~\cite{GLSTMMR12} & 92 & ({\sc nq},{\sc nq},{\sc nq},{\sc nq})\_r
   &   28\% ({\sc s},{\sc c}) & {\sc sql}i, {\sc xss} \\
-  &   Aeolus~\cite{CPSPBCCSL12} & 52 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
+  &   Aeolus~\cite{CPSPBCCSL12} & 58 & ({\sc na},{\sc na},{\sc na},{\sc na})\_{\bf ?}
   &   323.5ms per request ({\sc s}) & {\sc sql}i, {\sc xss} \\
@@
 \leavevmode
-\includegraphics[scale=0.40]{barchart.pdf}
+\includegraphics[scale=0.40]{barchart.png}
 \end{center}
@@
   \multirow{2}{*}{Parse-Tree Validation}
+  &   {\sc sqlg}uard~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
   &   {\sc sqlc}heck~\cite{SW06} & {\sc na} & {\sc na} & {\sc na} \\
-  &   {\sc sqlg}uard~\cite{BWS05} & {\bf AO} & {\bf AO} & {\sc na} \\
   \hline
@@
 \bibliography{questioning}
-\vspace{-1.2mm}
+\vspace{-1.6mm}
 
 \section*{Author Biographies}
-\vspace{-1.1mm}
+\vspace{-0.7mm}
 \noindent
